### 2023-01-14 MasterThesis.tex
Template setup

\documentclass[a4paper,12pt,twoside]{report}
\usepackage[left=3cm,right=3cm,top=3cm,bottom=3cm]{geometry} %Margins
\usepackage{pdfpages}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{setspace}
\usepackage{tocloft}
\usepackage{amsmath}
\usepackage{chngcntr }
\usepackage[toc,page]{appendix}
\usepackage[T1]{fontenc}
\usepackage[nottoc]{tocbibind}
\usepackage[compact]{titlesec}
\titlespacing{\section}{0pt}{1ex}{0ex}
\titlespacing{\subsection}{0pt}{1ex}{0ex}
\titlespacing{\subsubsection}{0pt}{1ex}{0ex}

\counterwithout{figure}{chapter}
\counterwithout{table}{chapter}

\include{thesis.preamble}

\begin{document}

\newgeometry{left=2cm,right=2cm} %Only for the title new margins

%Title parameters
\title{Multi-level audio-based music structure analysis}
\author{Oriol Colomé Font}
\submitdate{July 2023}
\supervisor{Carlos Lordelo and Carl Thomé}
\cosupervisor{Frederic Font}

\maketitle

\maketitle
\restoregeometry

\preface
\cleardoublepage 
\input{dedication/dedication}
\input{acknowledgements/acknowledgements}
\input{abstract/abstract}

\body

%Introduction of the project
\input{introduction/introduction}
\input{methods/methods}
\input{results/results}
\input{discussion/discussion}

\listoffigures
\newpage
\listoftables

% appendices come here
\bibliographystyle{naturemag}
\bibliography{bibliography}

\input{appendix/appendix}

\end{document}

### 2023-01-14 abstract/abstract.tex
Template setup

%\addcontentsline{toc}{chapter}{Abstract}

\begin{abstract}
\pagenumbering{gobble}

The abstract should have at least 200 but not more than 600 words. Placed on the right page next to a blank left page. A list of keywords (approximately 3 to 5) should be just below the abstract, preceded by the word "Keywords". Keywords should be separated by ";".

\bigskip
Keywords: Music Information Retrieval; Music Structure Analysis; Deep Learning

\newpage
\end{abstract}

### 2023-01-14 acknowledgements/acknowledgements.tex
Template setup

%\addcontentsline{toc}{chapter}{Acknowledgement}

\begin{acknowledgement}
\pagenumbering{gobble}% Remove page numbers (and reset to 1)
(Optional, if used, placed on a right page next to an empty left page)

I want to express my sincere gratitude to:

\begin{itemize}
 \item My supervisor
 \vspace*{3mm}
 \item My co-supervisor
 \vspace*{3mm}
 \item My family
 \vspace*{3mm}
\end{itemize}

\newpage
\end{acknowledgement}

### 2023-01-14 results/results.tex
Template setup

\chapter{Results}

This is an example paragraph. As you can see, the main text uses a font size of 12 pt and a line spacing of 1.5. Neither the paragraphs nor the first lines of paragraphs should be indented.

There is no very strict page limit. Your number of pages will be strongly influenced by the size and total number of your figures and tables. It is recommended staying within 30-50 pages. Do not try to fill as many pages as you can. Longer theses are not necessarily of higher quality and of more non-redundant content than shorter theses. Certainly, a master thesis of 15 pages is too short, and a master thesis of 100 pages is too long.

\section{Tables and graphics}

This is an example paragraph. As you can see, the main text uses a font size of 12 pt and a line spacing of 1.5. Neither the paragraphs nor the first lines of paragraphs should be indented.

There is no very strict page limit. Your number of pages will be strongly influenced by the size and total number of your figures and tables. It is recommended staying within 30-50 pages. Do not try to fill as many pages as you can. Longer theses are not necessarily of higher quality and of more non-redundant content than shorter theses. Certainly, a master thesis of 15 pages is too short, and a master thesis of 100 pages is too long.

\begin{figure}[!ht]
\includegraphics[clip,width=\columnwidth]{Figures/PlotTimeSeriesResult}% 
\caption{This is an example of a figure and its caption.}
\label{fig:timeseries}
\end{figure}

\begin{table}[!ht]
\renewcommand{\arraystretch}{1.50}
\caption{This is an example of a table and its caption.}
\label{tablePCA}
\centering
\begin{tabular}{| c | c |}
\hline
\bfseries PCA & \bfseries Residual mean (in absolute values) \\
\hline\hline
Original PCA & 0.1267  \\
\hline
PCA on Centroid 1 & 0.1249\\
\hline
PCA on Centroid 2 & 0.1214  \\
\hline
\end{tabular}
\end{table}

\newpage

### 2023-01-14 introduction/introduction.tex
Template update

\normallinespacing

\chapter{Introduction}

Music Structure Analysis (MSA) is a field of study that aims to understand music's underlying organization and structure. This can include analyzing elements such as melody, harmony, rhythm, and timbre, as well as the relationships and interactions between these elements. MSA aims to identify patterns and regularities in music and develop computational models that can replicate and generate musical structures.

MSA is a multidisciplinary field that draws on techniques from music theory, signal processing, machine learning, and other fields. It can be applied to various musical styles and genres and has been used for tasks such as music transcription, music generation, and music similarity. \cite{rodriguez2005bilateral}
\section{Motivation}

\section{Objectives}
\section{Structure of the Report}

\newpage

### 2023-01-14 MasterThesis.tex
Template update
Third update

@@
 %Title parameters
-\title{Multi-level audio-based music structure analysis}
-\author{Oriol Colomé Font}
+\title{Audio-based multi-level music structure analysis using deep learning}
+\author{\href{oriol.colome.font@epidemicsound.com}{Oriol Colomé Font}}
 \submitdate{July 2023}
@@
 
+\hypersetup{
+pdftitle={Your PDF title},
+pdfsubject={Your PDF subject},
+pdfauthor={Oriol Colomé Font},
+pdfkeywords={Music Information Retrieval; Music Structure Analysis; Deep Learning}
+}
+
 \maketitle
 
-\maketitle
+%\maketitle
 \restoregeometry

### 2023-01-14 acknowledgements/acknowledgements.tex
Third update

@@
 \pagenumbering{gobble}% Remove page numbers (and reset to 1)
-(Optional, if used, placed on a right page next to an empty left page)
-
-I want to express my sincere gratitude to:
 
 \begin{itemize}
- \item My supervisor
+\item I want to express my sincerest gratitude to Carlos Lordelo, and Carl Thomé for their invaluable guidance and support throughout my thesis.
+Your expertise in MIR helped shape the direction of my research and make it a success.
+Your unwavering support and encouragement helped me overcome any difficulties I encountered during the process.
+I also appreciate the time and effort you invested in mentoring me.
+Your dedication to your students is truly inspiring, and I am honored to have had the opportunity to work with you.
 \vspace*{3mm}
@@
 \vspace*{3mm}
+\item The Music Technology Group (MTG)
+\vspace*{3mm}
+\item I would also like to thank my colleague and superior at My Sheet Music Transcriptions, Oriol López, for his exceptional support and flexibility throughout my thesis.
+His understanding and willingness to accommodate my academic commitments effectively allowed me to balance my work and research responsibilities.
+His guidance and advice on professional matters have been instrumental in my growth as a professional.
+I am genuinely grateful for his unwavering support and encouragement and for being a great mentor.
+\vspace*{3mm}
+Thank you all for being excellent advisors and playing a crucial role in completing my thesis.
+I sincerely appreciate everything you have done for me and will always cherish the knowledge and experience I have gained under your guidance.
+\vspace*{3mm}
 \item My family
+\vspace*{3mm}
+\item My girlfriend
 \vspace*{3mm}

### 2023-01-14 introduction/introduction.tex
Third update

@@
 
+The fundamental concept behind MSA is the ability to divide a song into distinct, non-overlapping segments, assigning a label to each segment that defines its type.
+This segmentation and labeling process aims to capture a human's perception or analysis of the song.
+
 MSA is a multidisciplinary field that draws on techniques from music theory, signal processing, machine learning, and other fields.
 It can be applied to various musical styles and genres and has been used for tasks such as music transcription, music generation, and music similarity.
-\cite{rodriguez2005bilateral}
+
+%\cite{rodriguez2005bilateral}
+
 \section{Motivation}
+
+In preview work, an overview of the current state of the art in MSA has been presented, including the most effective methods, principles, evaluation metrics, datasets, and performance \cite{Nieto2020}.
+Additionally, we have examined the primary challenges that MSA currently faces, particularly in regards to subjectivity, ambiguity, and hierarchy.
 

### 2023-01-14 Figures/Figures CNN/Multi-layer_NN.tex
Updates from Overleaf

\begin{figure}[h]
	\centering
	\begin{tikzpicture}[shorten >=1pt]
		\tikzstyle{unit}=[draw,shape=circle,minimum size=1.15cm]
		%\tikzstyle{hidden}=[draw,shape=circle,fill=black!25,minimum size=1.15cm]
		\tikzstyle{hidden}=[draw,shape=circle,minimum size=1.15cm]

		\node[unit](x0) at (0,3.5){$x_0$};
		\node[unit](x1) at (0,2){$x_1$};
		\node at (0,1){\vdots};
		\node[unit](xd) at (0,0){$x_D$};

		\node[hidden](h10) at (3,4){$y_0^{(1)}$};
		\node[hidden](h11) at (3,2.5){$y_1^{(1)}$};
		\node at (3,1.5){\vdots};
		\node[hidden](h1m) at (3,-0.5){$y_{m^{(1)}}^{(1)}$};

		\node(h22) at (5,0){};
		\node(h21) at (5,2){};
		\node(h20) at (5,4){};

		\node(d3) at (6,0){$\ldots$};
		\node(d2) at (6,2){$\ldots$};
		\node(d1) at (6,4){$\ldots$};

		\node(hL12) at (7,0){};
		\node(hL11) at (7,2){};
		\node(hL10) at (7,4){};

		\node[hidden](hL0) at (9,4){$y_0^{(L)}$};
		\node[hidden](hL1) at (9,2.5){$y_1^{(L)}$};
		\node at (9,1.5){\vdots};
		\node[hidden](hLm) at (9,-0.5){$y_{m^{(L)}}^{(L)}$};

		\node[unit](y1) at (12,3.5){$y_1^{(L+1)}$};
		\node[unit](y2) at (12,2){$y_2^{(L+1)}$};
		\node at (12,1){\vdots};	
		\node[unit](yc) at (12,0){$y_C^{(L+1)}$};

		\draw[->] (x0) -- (h11);
		\draw[->] (x0) -- (h1m);

		\draw[->] (x1) -- (h11);
		\draw[->] (x1) -- (h1m);

		\draw[->] (xd) -- (h11);
		\draw[->] (xd) -- (h1m);

		\draw[->] (hL0) -- (y1);
		\draw[->] (hL0) -- (yc);
		\draw[->] (hL0) -- (y2);

		\draw[->] (hL1) -- (y1);
		\draw[->] (hL1) -- (yc);
		\draw[->] (hL1) -- (y2);

		\draw[->] (hLm) -- (y1);
		\draw[->] (hLm) -- (y2);
		\draw[->] (hLm) -- (yc);

		\draw[->,path fading=east] (h10) -- (h21);
		\draw[->,path fading=east] (h10) -- (h22);

		\draw[->,path fading=east] (h11) -- (h21);
		\draw[->,path fading=east] (h11) -- (h22);

		\draw[->,path fading=east] (h1m) -- (h21);
		\draw[->,path fading=east] (h1m) -- (h22);

		\draw[->,path fading=west] (hL10) -- (hL1);
		\draw[->,path fading=west] (hL11) -- (hL1);
		\draw[->,path fading=west] (hL12) -- (hL1);

		\draw[->,path fading=west] (hL10) -- (hLm);
		\draw[->,path fading=west] (hL11) -- (hLm);
		\draw[->,path fading=west] (hL12) -- (hLm);

		\draw [decorate,decoration={brace,amplitude=10pt},xshift=-4pt,yshift=0pt] (-0.5,4) -- (0.75,4) node [black,midway,yshift=+0.6cm]{input layer};
		\draw [decorate,decoration={brace,amplitude=10pt},xshift=-4pt,yshift=0pt] (2.5,4.5) -- (3.75,4.5) node [black,midway,yshift=+0.6cm]{$1^{\text{st}}$ hidden layer};
		\draw [decorate,decoration={brace,amplitude=10pt},xshift=-4pt,yshift=0pt] (8.5,4.5) -- (9.75,4.5) node [black,midway,yshift=+0.6cm]{$L^{\text{th}}$ hidden layer};
		\draw [decorate,decoration={brace,amplitude=10pt},xshift=-4pt,yshift=0pt] (11.5,4) -- (12.75,4) node [black,midway,yshift=+0.6cm]{output layer};
	\end{tikzpicture}
	\caption[Network graph for a $(L+1)$-layer perceptron.]{Network graph of a $(L+1)$-layer perceptron with $D$ input units and $C$ output units. The $l^{\text{th}}$ hidden layer contains $m^{(l)}$ hidden units.}
	\label{fig:multilayer-perceptron}
\end{figure}

### 2023-01-14 Figures/Figures CNN/Network_graph.tex
Updates from Overleaf

\begin{SCfigure}[12][h]
	\centering
    \begin{tikzpicture}[shorten >=1pt]
        \tikzstyle{unit}=[draw,shape=circle,minimum size=1.15cm]

        \node[unit](x0) at (0,3.5){$x_0$};
        \node[unit](x1) at (0,2){$x_1$};
        \node(dots) at (0,1){\vdots};
        \node[unit](xd) at (0,0){$x_D$};

        \node[unit](y1) at (4,2.5){$y_1$};
        \node(dots) at (4,1.5){\vdots};
        \node[unit](yc) at (4,0.5){$y_C$};

        \draw[->] (x0) -- (y1);
        \draw[->] (x0) -- (yc);

        \draw[->] (x1) -- (y1);
        \draw[->] (x1) -- (yc);

        \draw[->] (xd) -- (y1);
        \draw[->] (xd) -- (yc);

        \draw [decorate,decoration={brace,amplitude=10pt},xshift=-4pt,yshift=0pt] (-0.5,4) -- (0.75,4) node [black,midway,yshift=+0.6cm]{input layer};
        \draw [decorate,decoration={brace,amplitude=10pt},xshift=-4pt,yshift=0pt] (3.5,3) -- (4.75,3) node [black,midway,yshift=+0.6cm]{output layer};
    \end{tikzpicture}
    \caption[Network graph of a perceptron with $D$ input units and $C$ output units.]{The perceptron consists of $D$ input units and $C$ output units. All units are labeled according to their output: $y_i = f(z_i)$ in the case of output units; $x_i$ in the case of input units. The input values $x_i$ are propagated to each output unit using the weighted sum propagation rule. The additional input value $x_0 := 1$ is used to include the biases as weights.}
    \label{fig:perceptron}
\end{SCfigure}

### 2023-01-14 Figures/Figures CNN/Single Neuron.tex
Updates from Overleaf

\begin{SCfigure}[2\sidecaptionrelwidth][h]
	\centering
	\begin{tikzpicture}[shorten >=1pt,->]
		\tikzstyle{unit}=[draw,shape=circle,minimum size=1.15cm]

		\node[unit](p) at (2,1){$y$};
		\node(dots) at (-0.25,1){\vdots};

		\draw (0,2.5) node[xshift=-10]{$w_0$} -- (p);
		\draw (0,1.75) node[xshift=-10]{$x_1$} --(p);
		\draw (0,0) node[xshift=-10]{$x_D$} -- (p);
		\draw (p) -- (3,1) node[xshift=30]{$y := f(z)$};
	\end{tikzpicture}
	\caption[Single processing units and its components.]{Single processing unit and its components. The activation function is denoted by $f$ and applied to the actual input $z$ of the unit to form its output $y = f(z)$. $x_1, \ldots, x_D$ represent input from other units within the network; $w_0$ is called bias and represents an external input to the unit. All inputs are mapped onto the actual input $z$ using the propagation rule.}
	\label{fig:processing-unit}
\end{SCfigure}

### 2023-01-14 Figures/Figures CNN/Single_CNN.tex
Updates from Overleaf

\begin{SCfigure}[2\sidecaptionrelwidth][h]
	\centering
	\begin{tikzpicture}
		\node at (1.5,4){\begin{tabular}{c}input image\\or input feature map\end{tabular}};

		\draw (0,0) -- (3,0) -- (3,3) -- (0,3) -- (0,0);

		\draw (2,2) -- (2.5,2) -- (2.5,2.5) -- (2,2.5) -- (2,2);
		\draw (2,0.5) -- (2.5,0.5) -- (2.5,1) -- (2,1) -- (2,0.5);
		\draw (1,1) -- (1.5,1) -- (1.5,1.5) -- (1,1.5) -- (1,1);

		\draw (2.5,2) -- (7,3.25);
		\draw (2.5,2.5) -- (7,3.25);

		\draw (2.5,1) -- (5.75,0.25);
		\draw (2.5,0.5) -- (5.75,0.25);

		\draw (1.5,1.5) -- (5.5,1.25);
		\draw (1.5,1) -- (5.5,1.25);

		\node at (5.75,4){\begin{tabular}{c}output feature maps\end{tabular}};

		\draw[fill=black,opacity=0.2,draw=black] (5.5,1.5) -- (7.5,1.5) -- (7.5,3.5) -- (5.5,3.5) -- (5.5,1.5);
		\draw[fill=black,opacity=0.2,draw=black] (5,1) -- (7,1) -- (7,3) -- (5,3) -- (5,1);
		\draw[fill=black,opacity=0.2,draw=black] (4.5,0.5) -- (6.5,0.5) -- (6.5,2.5) -- (4.5,2.5) -- (4.5,0.5);
		\draw[fill=black,opacity=0.2,draw=black] (4,0) -- (6,0) -- (6,2) -- (4,2) -- (4,0);
	\end{tikzpicture}
	\caption[Illustration of a convolutional layer.]{Illustration of a single convolutional layer. If layer $l$ is a convolutional layer, the input image (if $l = 1$) or a feature map of the previous layer is convolved by different filters to yield the output feature maps of layer $l$.}
	\label{fig:convolutional-layer}
\end{SCfigure}

### 2023-01-14 acknowledgements/acknowledgements.tex
Updates from Overleaf

@@
 
+I want to express my sincerest gratitude to...
+
 \begin{itemize}
-\item I want to express my sincerest gratitude to Carlos Lordelo, and Carl Thomé for their invaluable guidance and support throughout my thesis.
+\item Carlos Lordelo, and Carl Thomé for their invaluable guidance and support throughout my thesis.
 Your expertise in MIR helped shape the direction of my research and make it a success.
@@
 \vspace*{3mm}
-\item I would also like to thank my colleague and superior at My Sheet Music Transcriptions, Oriol López, for his exceptional support and flexibility throughout my thesis.
+\item My colleague at My Sheet Music Transcriptions, Oriol López, for his exceptional support and flexibility throughout my thesis.
 His understanding and willingness to accommodate my academic commitments effectively allowed me to balance my work and research responsibilities.

### 2023-01-14 introduction/introduction.tex
Updates from Overleaf

--- 2023-01-14 introduction/introduction.tex
@@
 
+The fundamental concept behind MSA is the ability to divide a song into distinct, non-overlapping segments, assigning a label to each segment that defines its type.
+This segmentation and labeling process aims to capture a human's perception or analysis of the song.
+
 MSA is a multidisciplinary field that draws on techniques from music theory, signal processing, machine learning, and other fields.
 It can be applied to various musical styles and genres and has been used for tasks such as music transcription, music generation, and music similarity.
-\cite{rodriguez2005bilateral}
+
 \section{Motivation}
 
+In previous work, an overview of the current state of the art in MSA has been presented, including the most effective methods, principles, evaluation metrics, datasets, and performance \cite{Nieto2020}.
+
 \section{Objectives}
+
 \section{Structure of the Report}

### 2023-01-14 methods/methods.tex
Updates from Overleaf

\chapter{Methods}

\section{Materials}

\section{Convolutional Neural Network (CNN)}

A CNN, or Convolutional Neural Network, is a deep-learning neural network. The architecture of a CNN is composed of several layers, including:

\begin{itemize}

\item Convolutional layers: These layers apply a convolution operation to the input data, effectively learning local patterns and features in the image. The raw audio data is typically transformed into a spectrogram or a Mel-spectrogram representation, which can be considered an image-like 2D representation of the audio data. The convolutional layers are designed to learn local patterns and features in the audio data
\vspace*{3mm}

\item Pooling layers: These layers downsample the data, reducing the spatial dimensions of the input while retaining important information. They can also be used to downsample the data and reduce the temporal dimensions of the input while retaining important information. 
\vspace*{3mm}

\item Fully connected layers: These layers connect every neuron in one layer to every neuron in another layer, allowing the network to learn non-linear combinations of the features learned in the previous layers.
\vspace*{3mm}

\item Output layer: The output layer produces the final predictions of the network.
\end{itemize}

Compared to a traditional neural network, CNNs are more computationally efficient and have less number of parameters to train. This makes them more feasible for large-scale datasets and real-world problems.

On top of that, one of the main advantages of using CNNs for audio analysis is that they can automatically and adaptively learn temporal hierarchies of features from audio data, which traditional audio processing methods may not be able to do effectively.

\subsection{Neural Network (NN)}

%Single
\input{Figures/Figures CNN/Single Neuron}
%NN
\input{Figures/Figures CNN/Network_graph}

%Backpropagation
\input{Figures/Figures CNN/Multi-layer_NN}

%CNN
A high-level illustration of a simple convolutional neural network indicating convolutional layers, pooling layers, and fully-connected layers without details (number of channels or neurons per layer or the input image size) can be seen in XXX.
\input{Figures/Figures CNN/CNN_diagram}

%Single CNN
\input{Figures/Figures CNN/Single_CNN}

%Single pooling layer
\input{Figures/Figures CNN/Single_Pooling_Layer}

%Backpropagation
\input{Figures/Figures CNN/Back_propagation}

\newpage

### 2023-01-14 preface/preface.tex
Updates from Overleaf

%\addcontentsline{toc}{chapter}{Acknowledgement}
\begin{preface}
\pagenumbering{gobble}% Remove page numbers (and reset to 1)
(Optional, if used placed on a right page next to an empty left page)

I would like to dedicate this work to...
\newpage

\end{preface}

### 2023-01-16 music analysis/bernstein_harvard.tex
Updates from Overleaf

What we're trying for is a very high overview of musical development in terms of a vocabulary constantly being enriched by more and more remote and chromatic overtones. It's as if we could see the whole of music developing from prehistory to the present in two minutes. Let's again pretend we're hominids, and that the smash hit of the moment is, let's say, Fear Harvard. Here we are in our hominid hut, crooning, Fear Harvard relations to age, and now maybe our wives and maybe our prepubescent sons join in, and automatically we're singing not in unison, but in octaves, since men's and women's voices are naturally an octave apart. Now that octave interval, I wish I could sing an octave so I could really show you what I mean, but that octave interval happens to be the first interval of the harmonic series as you remember, right? Okay, now centuries pass, and the next interval of the harmonic series is assimilated by humanity. Namely, the fifth. And now we can be singing this, by those festival rides on the horizon. Now, of course, this little change brings us forward a mere 10 million years into the 10th century AD and into a fairly sophisticated musical culture. But now we admit the next interval of the series, the fourth, and now we can mix intervals of the octave and the fifth and the fourth. That's beginning to sound like polyphony. And again comes a great leap as music absorbs the next overtone, the third, and just listen to the difference. It's a whole new music, richer, mellower, with a new coloristic warmth, and as we know, this new interval of the third, because I like the older sound better, but anyway, as we know, this new interval of the third introduces into music the phenomenon of the triad so that now, fair Harvard, can begin to sound more like its Victorian self. And so there is born what we now call tonal music, a stable tonal language firmly rooted in the basic notes of the harmonic series, the fundamental and its first different overtone, the fifth, now and forever more to be known as the tonic and the dominant. And that fifth interval really does dominate, because once this tonic-dominant relationship is established, it's a field day for composers. There can now be fifths of fifths of fifths of fifths, each one of them a new tonic producing a new dominant, a whole circle of fifths, 12 of them in fact, always winding up with the starting tone, where the preceding upwards, let's say from the low C, G, D, A, E, B, F, sharp, C sharp, G sharp, D sharp, B flat, F, C, that's again C, believe it or not. Or preceding downwards, starting from that, C, F, B flat, E flat, E flat, G flat, G flat, C, back to C. That's a circle of 12 fifths, and that's the answer I promised you. That's how we get the 12 different tones of our chromatic scale. In other words, if you take all those 12 of the circle of fifths and put them together in scale order, you'll get this. And what's more, those 12 notes generate a circle of 12 keys, through which, thanks to the perfecting of the temperate system, composers can now go freewheeling at their own chromatic pleasure. Now this means that ultimately, fair Harvard can sound like this. Now that's chromatic porridge, and in our own century it's going to become goulash. How does music contain this loose, runny chromaticism? By the basic principle of diatonicism, that stable relationship of tonics, and dominant, subdominants, and supertonics, and new dominants, and new tonics. We can now modulate as freely as we want, as chromatically as we want, and still have complete tonal control. This great system of tonal controls was perfected and codified by Bach, Johann Sebastian Bach, whose genius was to balance so delicately and so justly these two forces of chromaticism and diatonicism, forces that were equally powerful and presumably contradictory in nature.

### 2023-01-16 music analysis/music_analysis.tex
Updates from Overleaf

\chapter{About Musical Analysis}

\section{Heinrich Schenker}

Heinrich Schenker was a prominent figure in music theory, known for developing the analytical method called "Schenkerian Analysis." This method is primarily applied to the study of tonal music. It is based on the concept of "the Ursatz," or fundamental structure, which consists of three levels: foreground, middle-ground, and background.

The foreground level is the surface structure of the musical composition, comprising the melody and harmony. The middle-ground level is the next structural level beneath the surface, while the background level represents the underlying tonal structure of the piece.

Schenker's approach to analysis postulates that all tonal music can be understood as a series of "preparations" and "resolutions" of tonal tensions. This approach emphasizes the horizontal dimension of music, specifically melody, and the relationship between individual notes and the piece's overall structure, as opposed to the vertical dimension of harmony.

Schenker's ideas have significantly impacted the field of music theory and analysis, and his method is still widely applied in the study of tonal music. Schenkerian Analysis is employed in musicology, composition, and music education and is considered a valuable tool for comprehending the structure and meaning of musical compositions.

Schenkerian Analysis can be considered a type of multi-level analysis, as it breaks down a piece of music into different levels of structure, with each level representing a different level of complexity and abstraction.

This hierarchical approach to analysis, where different levels of structure are examined, is a characteristic of multi-level analysis in general. Therefore, Schenkerian Analysis can be considered as a form of multi-level analysis, as it analyses the piece of music on multiple levels of structure and abstraction.

While Schenkerian Analysis is primarily a theoretical approach to music analysis that relies on human interpretation and notation, it is possible to use computer algorithms, such as convolutional neural networks (CNNs), to analyze music similarly.

It is important to note that even though it is possible to use CNNs for music analysis, Schenkerian Analysis is a highly theoretical and interpretive approach that relies on human expertise and interpretation. It's hard to replicate the same results using a machine learning model like CNNs.

\section{George Russell}

"The Lydian Chromatic Concept of Tonal Organization" is a theoretical treatise by George Russell, a jazz musician, and composer. First published in 1953, the book presents a system of tonal organization based on the Lydian mode. Russell asserts that the Lydian mode, characterized by its raised fourth scale degree, is the most natural and fundamental tonal system and that all other modes and scales can be derived from it. Furthermore, he claims that the Lydian mode is the only tonal system to organize the various pitch collections utilized in contemporary music appropriately.

The book provides a methodology for arranging chords and scales based on their relationship to the Lydian mode and includes a technique for improvisation and composition utilizing this system. The book's purpose is to present a new approach to music theory that would benefit jazz musicians and composers, as well as other musicians.

The book is considered a seminal work in jazz education and has significantly impacted jazz harmony and education development. Many jazz musicians and educators have studied and applied Russell's concepts in their work.

In summary, "The Lydian Chromatic Concept of Tonal Organization" is a theoretical work that posits the Lydian mode as the most fundamental and natural tonal system and organizes chords, scales, and improvisation based on this mode.

### 2023-02-05 introduction/introduction.tex
5-2-2023 commit

@@
 
-In previous work, an overview of the current state of the art in MSA has been presented, including the most effective methods, principles, evaluation metrics, datasets, and performance \cite{Nieto2020}.
+In previous work, an overview of the current state of the art in MSA has been presented, including the most effective methods, principles, evaluation metrics, datasets, and performance~\cite{Nieto2020}~\cite{Chaki2021}.
 

### 2023-02-05 music analysis/authors.tex
5-2-2023 commit

--- 2023-01-16 music analysis/bernstein_harvard.tex
@@
+\chapter{About Musical Analysis}
+
+\section{Heinrich Schenker}
+
+Heinrich Schenker was a prominent figure in music theory, known for developing the analytical method called "Schenkerian Analysis." This method is primarily applied to the study of tonal music.
+It is based on the concept of "the Ursatz," or fundamental structure, which consists of three levels: foreground, middle-ground, and background.
+
+The foreground level is the surface structure of the musical composition, comprising the melody and harmony.
+The middle-ground level is the next structural level beneath the surface, while the background level represents the underlying tonal structure of the piece.
+
+Schenker's approach to analysis postulates that all tonal music can be understood as a series of "preparations" and "resolutions" of tonal tensions.
+This approach emphasizes the horizontal dimension of music, specifically melody, and the relationship between individual notes and the piece's overall structure, as opposed to the vertical dimension of harmony.
+
+Schenker's ideas have significantly impacted the field of music theory and analysis, and his method is still widely applied in the study of tonal music.
+Schenkerian Analysis is employed in musicology, composition, and music education and is considered a valuable tool for comprehending the structure and meaning of musical compositions.
+
+Schenkerian Analysis can be considered a type of multi-level analysis, as it breaks down a piece of music into different levels of structure, with each level representing a different level of complexity and abstraction.
+
+This hierarchical approach to analysis, where different levels of structure are examined, is a characteristic of multi-level analysis in general.
+Therefore, Schenkerian Analysis can be considered as a form of multi-level analysis, as it analyses the piece of music on multiple levels of structure and abstraction.
+
+While Schenkerian Analysis is primarily a theoretical approach to music analysis that relies on human interpretation and notation, it is possible to use computer algorithms, such as convolutional neural networks (CNNs), to analyze music similarly.
+
+It is important to note that even though it is possible to use CNNs for music analysis, Schenkerian Analysis is a highly theoretical and interpretive approach that relies on human expertise and interpretation.
+It's hard to replicate the same results using a machine learning model like CNNs.
+
+\section{George Russell}
+
+"The Lydian Chromatic Concept of Tonal Organization" is a theoretical treatise by George Russell, a jazz musician, and composer.
+First published in 1953, the book presents a system of tonal organization based on the Lydian mode.
+Russell asserts that the Lydian mode, characterized by its raised fourth scale degree, is the most natural and fundamental tonal system and that all other modes and scales can be derived from it.
+Furthermore, he claims that the Lydian mode is the only tonal system to organize the various pitch collections utilized in contemporary music appropriately.
+
+The book provides a methodology for arranging chords and scales based on their relationship to the Lydian mode and includes a technique for improvisation and composition utilizing this system.
+The book's purpose is to present a new approach to music theory that would benefit jazz musicians and composers, as well as other musicians.
+
+The book is considered a seminal work in jazz education and has significantly impacted jazz harmony and education development.
+Many jazz musicians and educators have studied and applied Russell's concepts in their work.
+
+In summary, "The Lydian Chromatic Concept of Tonal Organization" is a theoretical work that posits the Lydian mode as the most fundamental and natural tonal system and organizes chords, scales, and improvisation based on this mode.
+
+\section{Leonard Bernstein}
+
 What we're trying for is a very high overview of musical development in terms of a vocabulary constantly being enriched by more and more remote and chromatic overtones.

### 2023-02-05 music analysis/music structure analysis.tex
5-2-2023 commit

\chapter{A little bit of theory on Music Structure Analysis (MSA)}

\section{Fundamental structure}

In Schenkerian analysis, the fundamental structure, also known as Ursatz, represents the underlying structure of a tonal work at the most remote or background level, in the most abstract form. It comprises an essential elaboration of the tonic triad, including the fundamental line and accompanying bass arpeggiation. The fundamental structure, like the fundamental line, takes one of three forms, depending on which pitch of the tonic triad serves as the primary tone. For example, in the key of C major, the fundamental structure would be represented by the descending fundamental line from scale degree 3.

The Urlinie, or fundamental line, unfolds the basic triad and presents tonality on horizontal paths. The tonal system also flows into this to bring a sense of purposeful order to chords by selecting harmonic degrees. Voice leading serves as the mediator between the horizontal formulation of tonality presented by the Urlinie and the vertical formulation presented by the harmonic degrees.

The upper voice of the fundamental structure, represented by the fundamental line, utilizes a descending direction. In contrast, the lower voice, the bass arpeggiation through the fifth, takes an ascending direction (as shown in figure 1). The combination of the fundamental line and bass arpeggiation constitutes a unity, and neither can exist alone; it is only through their unification in a contrapuntal structure that they produce art.

\section{Structural levels}

In Schenkerian analysis, structural levels refer to the representation of a piece of music at different levels of abstraction. These levels typically include the foreground, middle ground, and background. Schenker posits that musical form, as represented through these structural levels, can be understood as an energy transformation, specifically as the transformation of forces that flow from the background to the foreground through the various levels.

\section{Meter}

In music, meter refers to the recurring patterns of accentuation and the organization of those accents into regular units, such as bars and beats. These patterns are implied by the performer and expected by the listener, even if they are not necessarily sounded.

Different cultures have developed various systems for organizing and performing metrical music, such as the Indian tala system and similar systems in Arabic and African music. Western music inherited meter from poetry, where it denotes the number of lines in a verse, the number of syllables in each line, and the arrangement of those syllables as long or short and accented or unaccented. The first systematic method of notating rhythm in Western music was derived from rhythmic modes, based on the basic types of metrical units in the quantitative meter of classical ancient Greek and Latin poetry.

\section{Music form}

Music form refers to the structural organization of a musical composition or performance. This can include elements such as the arrangement of musical units (such as rhythm, melody, and harmony) that exhibit repetition or variation, the arrangement of instruments, or the orchestration of a symphonic piece. These elements interact to shape the composition and create a meaningful musical experience for the listener. The organizational elements can be further broken down into smaller units called phrases, which express a musical idea but lack the sufficient weight to stand alone. The form of a composition unfolds over time through the expansion and development of these ideas. In tonal harmony, form is primarily articulated through cadences, phrases, and periods.

### 2023-02-05 introduction/introduction.tex

--- 2023-01-14 introduction/introduction.tex
@@
 MSA is a multidisciplinary field that draws on techniques from music theory, signal processing, machine learning, and other fields.
-It can be applied to various musical styles and genres and has been used for tasks such as music transcription, music generation, and music similarity.
+It can be applied to various musical styles and genres and has been used for tasks such as music transcription, generation, and similarity.
+
+\section{Historical overview}
+
+Music Structure Analysis (MSA) has a long history, with its roots dating back to music theory and composition studies.
+In the 18th and 19th centuries, music theorists such as Rameau~\cite{christensen2004rameau} and Schenker~\cite{schenkerdocumentsonline} developed analytical frameworks for understanding the structure of music in terms of harmony, melody, and form.
 
@@
 
-In previous work, an overview of the current state of the art in MSA has been presented, including the most effective methods, principles, evaluation metrics, datasets, and performance \cite{Nieto2020}.
+In previous work, an overview of the current state of the art in MSA has been presented, including the most effective methods, principles, evaluation metrics, datasets, and algorithm performance~\cite{Nieto2020}~\cite{Chaki2021}.
+
+As a music lover and connoisseur, I am interested in gaining a deeper understanding of the fundamental building blocks of musical composition and the various techniques used to create musical works~\cite{choi2017convolutional}.
+I am deeply interested in learning how to retrieve embedded and encoded information within music.
+The study of music structure analysis provides a means to systematically analyze and understand musical pieces.
+It has traditionally been approached through music theory, formal musical notation, and musical analysis techniques.
+
+However, with the advent of artificial intelligence and machine learning, the field of music structure analysis has expanded to encompass the use of musically motivated neural network architectures.
+These networks are designed to incorporate musical concepts and perceptual approaches and use this knowledge to analyze and understand the structure of musical pieces in a way that goes beyond traditional music analysis techniques.
+
+By studying music structure analysis using musically motivated neural networks, you will gain an in-depth understanding of the latest advancements in the field and how these techniques are being used to revolutionize our understanding of music.
+Additionally, you will be able to contribute to developing new and innovative methods for musical analysis~\cite{Huang2019MusicTG}
 

### 2023-02-05 introduction/introduction.tex
Updates from Overleaf

@@
 
-Music Structure Analysis (MSA) is a field of study that aims to understand music's underlying organization and structure.
+Music Structure Analysis (MSA) is the field of study that aims to understand music's underlying organization and structure.
 This can include analyzing elements such as melody, harmony, rhythm, and timbre, as well as the relationships and interactions between these elements.
@@
 
-The fundamental concept behind MSA is the ability to divide a song into distinct, non-overlapping segments, assigning a label to each segment that defines its type.
+The fundamental concept behind MSA is the ability to divide a song into distinct, non-overlapping segments, assigning a label to each component that defines its type.
 This segmentation and labeling process aims to capture a human's perception or analysis of the song.
 
-MSA is a multidisciplinary field that draws on techniques from music theory, signal processing, machine learning, and other fields.
+MSA is a multidisciplinary field that draws on techniques from music theory, signal processing, machine learning, and other areas.
 It can be applied to various musical styles and genres and has been used for tasks such as music transcription, generation, and similarity.
 
-\section{Historical overview}
+\section{Topic overview}
 
-Music Structure Analysis (MSA) has a long history, with its roots dating back to music theory and composition studies.
+Music Structure Analysis (MSA) has a long history, dating back to music theory and composition studies.
 In the 18th and 19th centuries, music theorists such as Rameau~\cite{christensen2004rameau} and Schenker~\cite{schenkerdocumentsonline} developed analytical frameworks for understanding the structure of music in terms of harmony, melody, and form.
@@
 
+As a music lover and connoisseur, I am interested in gaining a deeper understanding of the fundamental building of musical composition and the various techniques used to create musical works~\cite{choi2017convolutional}.
+I am deeply interested in learning how to retrieve embedded and encoded information within the music.
+The study of music structure analysis provides a means to systematically analyze and understand musical pieces.
+It has traditionally been approached through music theory, formal musical notation, musical analysis techniques, and machine learning, which I plan to blend.
+
+With the advent of artificial intelligence and machine learning, the field of music structure analysis has expanded to encompass the use of musically motivated neural network architectures.
+These networks are designed to incorporate musical concepts and perceptual approaches and use this knowledge to analyze and understand the structure of musical pieces in a way that goes beyond traditional music analysis techniques.
+
+As a professional music transcriber, you are interested in understanding how deep neural networks (DNNs) filter musical features.
+In other words, I am eager to learn how DNNs listen~\cite{7500246} to music.
+
+By studying music structure analysis using musically motivated neural networks, you will gain an in-depth understanding of the latest advancements in the field and how these techniques are being used to revolutionize our understanding of music.
+Additionally, we will be able to contribute to developing new and innovative methods for musical analysis~\cite{Huang2019MusicTG}
+
+\section{Objectives}
+
 In previous work, an overview of the current state of the art in MSA has been presented, including the most effective methods, principles, evaluation metrics, datasets, and algorithm performance~\cite{Nieto2020}~\cite{Chaki2021}.
 
-As a music lover and connoisseur, I am interested in gaining a deeper understanding of the fundamental building blocks of musical composition and the various techniques used to create musical works~\cite{choi2017convolutional}.
-I am deeply interested in learning how to retrieve embedded and encoded information within music.
-The study of music structure analysis provides a means to systematically analyze and understand musical pieces.
-It has traditionally been approached through music theory, formal musical notation, and musical analysis techniques.
-
-However, with the advent of artificial intelligence and machine learning, the field of music structure analysis has expanded to encompass the use of musically motivated neural network architectures.
-These networks are designed to incorporate musical concepts and perceptual approaches and use this knowledge to analyze and understand the structure of musical pieces in a way that goes beyond traditional music analysis techniques.
-
-By studying music structure analysis using musically motivated neural networks, you will gain an in-depth understanding of the latest advancements in the field and how these techniques are being used to revolutionize our understanding of music.
-Additionally, you will be able to contribute to developing new and innovative methods for musical analysis~\cite{Huang2019MusicTG}
-
-\section{Objectives}
+As a professional music transcriber, I aim to understand how deep neural networks (DNNs) filter musical features, listen to the NN layers from a musician's perspective and analyze the resulting data.
+My goal is to approach the technology from both a technical and musical standpoint to understand how DNNs process and extract musical information.
+By doing so, you aim to enhance the accuracy and efficiency of the process and contribute to developing AI technology for music analysis.
+By combining my expertise in music with my -not fully developed- knowledge of DNNs, I hope to bring a unique perspective to the field and contribute to the advancement of music analysis.
 

### 2023-02-05 music analysis/authors.tex
Updates from Overleaf

--- 2023-01-16 music analysis/bernstein_harvard.tex
@@
-What we're trying for is a very high overview of musical development in terms of a vocabulary constantly being enriched by more and more remote and chromatic overtones.
-It's as if we could see the whole of music developing from prehistory to the present in two minutes.
-Let's again pretend we're hominids, and that the smash hit of the moment is, let's say, Fear Harvard.
-Here we are in our hominid hut, crooning, Fear Harvard relations to age, and now maybe our wives and maybe our prepubescent sons join in, and automatically we're singing not in unison, but in octaves, since men's and women's voices are naturally an octave apart.
-Now that octave interval, I wish I could sing an octave so I could really show you what I mean, but that octave interval happens to be the first interval of the harmonic series as you remember, right?
-Okay, now centuries pass, and the next interval of the harmonic series is assimilated by humanity.
-Namely, the fifth.
-And now we can be singing this, by those festival rides on the horizon.
-Now, of course, this little change brings us forward a mere 10 million years into the 10th century AD and into a fairly sophisticated musical culture.
-But now we admit the next interval of the series, the fourth, and now we can mix intervals of the octave and the fifth and the fourth.
-That's beginning to sound like polyphony.
-And again comes a great leap as music absorbs the next overtone, the third, and just listen to the difference.
-It's a whole new music, richer, mellower, with a new coloristic warmth, and as we know, this new interval of the third, because I like the older sound better, but anyway, as we know, this new interval of the third introduces into music the phenomenon of the triad so that now, fair Harvard, can begin to sound more like its Victorian self.
-And so there is born what we now call tonal music, a stable tonal language firmly rooted in the basic notes of the harmonic series, the fundamental and its first different overtone, the fifth, now and forever more to be known as the tonic and the dominant.
-And that fifth interval really does dominate, because once this tonic-dominant relationship is established, it's a field day for composers.
-There can now be fifths of fifths of fifths of fifths, each one of them a new tonic producing a new dominant, a whole circle of fifths, 12 of them in fact, always winding up with the starting tone, where the preceding upwards, let's say from the low C, G, D, A, E, B, F, sharp, C sharp, G sharp, D sharp, B flat, F, C, that's again C, believe it or not.
-Or preceding downwards, starting from that, C, F, B flat, E flat, E flat, G flat, G flat, C, back to C.
-That's a circle of 12 fifths, and that's the answer I promised you.
-That's how we get the 12 different tones of our chromatic scale.
-In other words, if you take all those 12 of the circle of fifths and put them together in scale order, you'll get this.
-And what's more, those 12 notes generate a circle of 12 keys, through which, thanks to the perfecting of the temperate system, composers can now go freewheeling at their own chromatic pleasure.
-Now this means that ultimately, fair Harvard can sound like this.
-Now that's chromatic porridge, and in our own century it's going to become goulash.
-How does music contain this loose, runny chromaticism?
-By the basic principle of diatonicism, that stable relationship of tonics, and dominant, subdominants, and supertonics, and new dominants, and new tonics.
-We can now modulate as freely as we want, as chromatically as we want, and still have complete tonal control.
-This great system of tonal controls was perfected and codified by Bach, Johann Sebastian Bach, whose genius was to balance so delicately and so justly these two forces of chromaticism and diatonicism, forces that were equally powerful and presumably contradictory in nature.
+\chapter{Music Structure Analysis (MSA)}
+
+\section{The music structure analysis problem}
+Audio-based Music Structural Analysis (MSA) identifies adjacent and non-overlapping musical segments in an audio signal and labels them based on similarity.
+Segments can occur at various time scales, from short motives to longer sections.
+Flat MSA focuses on non-hierarchical structures, while hierarchical MSA considers multiple time scales.
+However, MSA faces challenges such as boundary placement ambiguity and similarity quantification.
+Segments must be non-overlapping for a given hierarchical level, although some musicological approaches allow for overlap.
+
+\subsection{Problem definition}
+
+The musical structure analysis (MSA) challenges the definition due to subjectivity, ambiguity, and data scarcity.
+A flat structural analysis of an audio signal consists of a set of contiguous, non-overlapping, and labeled time intervals that span the entire duration of the audio signal.
+Given a musical recording of T audio samples, a flat segmentation is defined by a set of segment boundaries B, a set of k unique labels Y, and a mapping of segment starting points to labels S.
+This leads to the label assignment L, which assigns a label to each time point.
+The segment boundaries are usually sampled at a rate of 10 Hz to achieve a balance between resolution and computational efficiency.
+
+As an art form, music is open to interpretation and can evoke different emotions and meanings in different listeners.
+This subjectivity makes it difficult to objectively analyze the structure of a piece of music, as different annotators may place boundaries between segments differently based on their perception and interpretation of the music.
+It can also have multiple structures, including hierarchical structures that make it difficult to untangle the truth.
+
+\subsection{Segmentation principles}
+The principles of musical structure analysis (MSA) were initially defined as homogeneity, novelty, and repetition, with the addition of regularity later on.
+To analyze the structure of a musical recording, a self-similarity matrix (SSM) is often used to visualize the degree of similarity between audio frames.
+The SSM results in a square matrix with the highest degree of similarity on the diagonal.
+
+\subsubsection{Homogeneity and novelty}
+Homogeneity assumes that segments are homogeneous in musical attributes, with boundaries between dissimilar segments being points of novelty.
+
+\subsubsection{Repetition}
+Repetition assumes that segments with the same label are similar sequences, with boundaries defined by repeated sequences' start and endpoints.
+The structure of the music is represented using a self-similarity matrix to make its structure visually apparent.
+Homogeneous blocks may be challenging to subdivide, while repeated sequences appear as paths in the self-similarity matrix.
+MSA approaches focus on identifying these repeated sequences.
+
+\subsubsection{Regularity}
+The regularity principle in music structure analysis aims to exploit the regularities present in musical segments, such as the log-normally distributed length across the track and the tendency for the duration of two equally labeled segments to span an integer ratio of beats.
+
+\section{Theoretical approach}
+\subsection{Heinrich Schenker}
+
+Heinrich Schenker~\cite{schenkerdocumentsonline} was a prominent music theorist who developed \textit{Schenkerian Analysis}, a method for analyzing tonal music.
+This method is based on the concept of "the Ursatz," a fundamental structure of three levels: foreground, middle-ground, and background.
+Schenker's approach emphasizes the horizontal dimension of music, specifically melody, and the relationships between individual notes and the piece's overall structure.
+His ideas have significantly impacted the field of music theory and analysis, and the method is still widely used today.
+While the approach is primarily theoretical and relies on human interpretation, it can also be approached through computer algorithms such as CNNs; the results are not the same as human interpretation.
+
+\subsection{Schenkerian analysis}
+
+Schenkerian analysis is a musical analysis method that examines tonal music using the theories of Heinrich Schenker.
+The purpose is to showcase the organic unity of a piece by highlighting the relationship between the foreground (all musical notes in the score) and the deep abstract structure known as the \textit{Ursatz}.
+The Ursatz, roughly the same for all tonal music, is then developed into a unique foreground in each work.
+The concept of tonal space, defined as the intervals between the notes of the tonic triad in the background, is crucial to the analysis.
+The tonal space is filled with passing and neighbor tones, creating new triads and tonal spaces for further elaboration.
+
+Schenkerian analysis uses specialized musical notation and is either presented in a generative manner, starting from the Ursatz and ending at the score or in a reductive manner, starting from the score and reducing it to its fundamental structure.
+The Ursatz is presented in an arrhythmic graph, and rhythmic signs display hierarchical relationships between pitch events.
+
+While complex and challenging, Schenkerian analysis is designed to reveal the internal coherence of a work, which ultimately lies in its tonality.
+The analysis's results may reflect the analyst's perceptions and intuitions.

### 2023-02-05 music analysis/music structure analysis.tex
Updates from Overleaf

@@
 In Schenkerian analysis, the fundamental structure, also known as Ursatz, represents the underlying structure of a tonal work at the most remote or background level, in the most abstract form.
-It comprises an essential elaboration of the tonic triad, including the fundamental line and accompanying bass arpeggiation.
+It comprises an essential elaboration of the tonic triad, including the entire line and accompanying bass arpeggiation.
 The fundamental structure, like the fundamental line, takes one of three forms, depending on which pitch of the tonic triad serves as the primary tone.
-For example, in the key of C major, the fundamental structure would be represented by the descending fundamental line from scale degree 3.
+For example, in the key of C major, the fundamental structure would be represented by the fundamental descending line from scale degree 3.
 
@@
 
-The upper voice of the fundamental structure, represented by the fundamental line, utilizes a descending direction.
+The upper voice of the fundamental structure, represented by the whole line, utilizes a descending direction.
 In contrast, the lower voice, the bass arpeggiation through the fifth, takes an ascending direction (as shown in figure 1).
@@
 These levels typically include the foreground, middle ground, and background.
-Schenker posits that musical form, as represented through these structural levels, can be understood as an energy transformation, specifically as the transformation of forces that flow from the background to the foreground through the various levels.
+Schenker posits that musical form, as represented through these structural levels, can be understood as an energy transformation, specifically the transformation of forces that flow from the background to the foreground through the various levels.
 
@@
 These elements interact to shape the composition and create a meaningful musical experience for the listener.
-The organizational elements can be further broken down into smaller units called phrases, which express a musical idea but lack the sufficient weight to stand alone.
+The organizational elements can be further broken down into smaller units called phrases, which express a musical idea but lack sufficient weight to stand alone.
 The form of a composition unfolds over time through the expansion and development of these ideas.

### 2023-02-06 introduction/introduction.tex
Updates from Overleaf

@@
 
-As a music lover and connoisseur, I am interested in gaining a deeper understanding of the fundamental building of musical composition and the various techniques used to create musical works~\cite{choi2017convolutional}.
+As a music lover and connoisseur, I am interested in gaining a deeper understanding of the fundamental building of musical composition and the various techniques used to create musical works.
 I am deeply interested in learning how to retrieve embedded and encoded information within the music.
@@
 
-In previous work, an overview of the current state of the art in MSA has been presented, including the most effective methods, principles, evaluation metrics, datasets, and algorithm performance~\cite{Nieto2020}~\cite{Chaki2021}.
-
 As a professional music transcriber, I aim to understand how deep neural networks (DNNs) filter musical features, listen to the NN layers from a musician's perspective and analyze the resulting data.
-My goal is to approach the technology from both a technical and musical standpoint to understand how DNNs process and extract musical information.
-By doing so, you aim to enhance the accuracy and efficiency of the process and contribute to developing AI technology for music analysis.
+I aim to approach the technology from a technical and musical standpoint to understand how DNNs process and extract musical information.
+By doing so, I aim to enhance the accuracy and efficiency of the process and contribute to developing AI technology for music analysis.
 By combining my expertise in music with my -not fully developed- knowledge of DNNs, I hope to bring a unique perspective to the field and contribute to the advancement of music analysis.

### 2023-02-06 music analysis/authors.tex
Updates from Overleaf

@@
 
+~\cite{Nieto2020}~\cite{Chaki2021}
+
 \section{The music structure analysis problem}
+
 Audio-based Music Structural Analysis (MSA) identifies adjacent and non-overlapping musical segments in an audio signal and labels them based on similarity.
@@
 This subjectivity makes it difficult to objectively analyze the structure of a piece of music, as different annotators may place boundaries between segments differently based on their perception and interpretation of the music.
-It can also have multiple structures, including hierarchical structures that make it difficult to untangle the truth.
+It can also have multiple structures, including hierarchical structures, that make it difficult to untangle the truth.
 
@@
 \section{Theoretical approach}
+\subsection{Music form}
+
+Music form refers to the structural organization of a musical composition or performance.
+This can include elements such as the arrangement of musical units (such as rhythm, melody, and harmony) that exhibit repetition or variation, the arrangement of instruments, or the orchestration of a symphonic piece.
+These elements interact to shape the composition and create a meaningful musical experience for the listener.
+The organizational elements can be further broken down into smaller units called phrases, which express a musical idea but lack sufficient weight to stand alone.
+The form of a composition unfolds over time through the expansion and development of these ideas.
+In tonal harmony, form is primarily articulated through cadences, phrases, and periods.
+
 \subsection{Heinrich Schenker}

### 2023-02-06 music analysis/music structure analysis.tex
Updates from Overleaf

@@
 The fundamental structure, like the fundamental line, takes one of three forms, depending on which pitch of the tonic triad serves as the primary tone.
-For example, in the key of C major, the fundamental structure would be represented by the fundamental descending line from scale degree 3.
+For example, the key of C major would represent the fundamental structure by the fundamental descending line from scale degree 3.
 
@@
 The first systematic method of notating rhythm in Western music was derived from rhythmic modes, based on the basic types of metrical units in the quantitative meter of classical ancient Greek and Latin poetry.
-
-\section{Music form}
-
-Music form refers to the structural organization of a musical composition or performance.
-This can include elements such as the arrangement of musical units (such as rhythm, melody, and harmony) that exhibit repetition or variation, the arrangement of instruments, or the orchestration of a symphonic piece.
-These elements interact to shape the composition and create a meaningful musical experience for the listener.
-The organizational elements can be further broken down into smaller units called phrases, which express a musical idea but lack sufficient weight to stand alone.
-The form of a composition unfolds over time through the expansion and development of these ideas.
-In tonal harmony, form is primarily articulated through cadences, phrases, and periods.

### 2023-02-06 results/results.tex
Updates from Overleaf

@@
 
-There is no very strict page limit.
-Your number of pages will be strongly influenced by the size and total number of your figures and tables.
-It is recommended staying within 30-50 pages.
+There is no stringent page limit.
+The size and the total number of your figures and tables will strongly influence your number of pages.
+It is recommended to stay within 30-50 pages.
 Do not try to fill as many pages as you can.
-Longer theses are not necessarily of higher quality and of more non-redundant content than shorter theses.
-Certainly, a master thesis of 15 pages is too short, and a master thesis of 100 pages is too long.
+Longer theses are not necessarily of higher quality and have more non-redundant content than shorter theses.
+Indeed, a master thesis of 15 pages is too short, and a master thesis of 100 pages is too long.
 

### 2023-02-09 music analysis/MSA.tex
Updates from Overleaf

--- 2023-02-06 music analysis/authors.tex
@@
 \chapter{Music Structure Analysis (MSA)}
+
+MSA encompasses various aspects of music analysis, including algorithms, current practices, and trends in technology.
+This field aims to comprehensively understand music structure by applying musicological theories and principles and music signal processing algorithms.
+MSA considers the interplay between technical and musical aspects, focusing on improving our understanding of music signals and the music itself.
+
+In the following section, we will examine the state of MSA, including its challenges and potential for future advancements.
+Topics such as data representation, computational complexity, and evaluation metrics will be discussed to provide a nuanced summary of the field.
+Additionally, we will consider the impact of new trends and technological advancements on MSA and the directions in which the field is likely to evolve.
+Through this examination, we aim to provide a thorough understanding of the technical and musical aspects of MSA and its challenges.
 
@@
 \subsubsection{Homogeneity and novelty}
-Homogeneity assumes that segments are homogeneous in musical attributes, with boundaries between dissimilar segments being points of novelty.
+Homogeneity assumes that segments are homogeneous in musical attributes, with boundaries between distinct segments being points of novelty.
 
@@
 The analysis's results may reflect the analyst's perceptions and intuitions.
+
+\subsection{Aural skills}
+
+Aural music skills are the capacity to comprehend and analyze musical compositions through listening.
+These skills encompass a wide range of abilities, including identifying musical elements such as rhythm, melody, harmony, timbre, and form, performing music from memory, and transcribing audio recordings into written musical scores.
+
+In the context of music, having strong aural skills is crucial for achieving a complete understanding of the art form.
+It enables musicians to make knowledgeable decisions about their playing and interpretation, as well as to evaluate the playing of others critically.
+Additionally, aural skills are an integral part of music education, playing a role in deepening one's appreciation of music and promoting creativity and musical expression.
+
+Aural skills can be honed through various activities, such as listening to music, singing, playing musical instruments, and analyzing music through written or visual means.
+Formal music education teaches aural skills through ear training, dictation, and sight-reading exercises.
+
+Aural music skills are crucial not only for an individual's personal musical growth but also for gaining a deeper understanding of the underlying musical structure of a piece.
+Identifying and analyzing musical elements through listening allows one to comprehend the relationships between these elements and how they contribute to the overall musical structure.
+This ability to perceive and understand musical structure is fundamental to making informed decisions and interpretations.
+
+In addition, solid aural skills enable musicians to communicate their musical ideas to others effectively, as well as to more fully comprehend the musical ideas of others.
+They provide a common ground for musical discussion and collaboration, allowing musicians to create and perform music at a higher level.
+
+Moreover, aural skills also play an essential role in preserving and continuing musical traditions, as they allow musicians to accurately pass down and preserve the musical heritage of their culture.
+By recognizing and understanding the underlying musical structures of traditional music, musicians can maintain the authenticity of the music and ensure its continuation for future generations.
+
+In conclusion, aural music skills are crucial for personal musical growth and for gaining a deeper understanding of the musical structure, effective musical communication and collaboration, and the preservation of musical traditions.

### 2023-02-09 introduction/introduction.tex
Updates from Overleaf

@@
 
-Music Structure Analysis (MSA) is the field of study that aims to understand music's underlying organization and structure.
-This can include analyzing elements such as melody, harmony, rhythm, and timbre, as well as the relationships and interactions between these elements.
-MSA aims to identify patterns and regularities in music and develop computational models that can replicate and generate musical structures.
-
-The fundamental concept behind MSA is the ability to divide a song into distinct, non-overlapping segments, assigning a label to each component that defines its type.
-This segmentation and labeling process aims to capture a human's perception or analysis of the song.
+Music\footnote{The term "music" used in this context refers specifically to Western tonal music tradition.
+It is assumed that the musical structures and elements discussed are based on this tradition and may not apply to other musical styles or cultures.} Structure Analysis (MSA) is the field of study that aims to understand music's underlying organization and structure.
 
@@
 
-\section{Topic overview}
-
-Music Structure Analysis (MSA) has a long history, dating back to music theory and composition studies.
-In the 18th and 19th centuries, music theorists such as Rameau~\cite{christensen2004rameau} and Schenker~\cite{schenkerdocumentsonline} developed analytical frameworks for understanding the structure of music in terms of harmony, melody, and form.
-
 \section{Motivation}
 
-As a music lover and connoisseur, I am interested in gaining a deeper understanding of the fundamental building of musical composition and the various techniques used to create musical works.
-I am deeply interested in learning how to retrieve embedded and encoded information within the music.
+As a music lover and connoisseur, I am interested in gaining a deeper understanding of the fundamental building of musical composition, the various techniques used to create musical works, and the underlying relationship among them.
+I am deeply interested in learning how to retrieve embedded information within music.
 The study of music structure analysis provides a means to systematically analyze and understand musical pieces.
@@
 
-With the advent of artificial intelligence and machine learning, the field of music structure analysis has expanded to encompass the use of musically motivated neural network architectures.
+With the advent of artificial intelligence and machine learning, Music Information Retrieval (MIR) has expanded to encompass musically motivated neural network architectures.
 These networks are designed to incorporate musical concepts and perceptual approaches and use this knowledge to analyze and understand the structure of musical pieces in a way that goes beyond traditional music analysis techniques.
 
-As a professional music transcriber, you are interested in understanding how deep neural networks (DNNs) filter musical features.
+As a professional music transcriber, I am interested in understanding how deep neural networks (DNNs) filter musical features.
 In other words, I am eager to learn how DNNs listen~\cite{7500246} to music.
@@
 
+In this report, we have organized the information into several sections and sub-sections to provide a clear and comprehensive overview of the topic. The structure of the report is as follows:
+
+\begin{itemize}
+\item Introduction
+  \begin{itemize}
+  \item Purpose
+  \item Methodology
+  \item Scope
+  \end{itemize}
+\item Main Body
+  \begin{itemize}
+  \item Section 1
+  \item Section 2
+  \item Section 3
+  \end{itemize}
+\item Conclusion
+  \begin{itemize}
+  \item Summary
+  \item Recommendations
+  \end{itemize}
+\item References
+  \begin{itemize}
+  \item Sources Cited
+  \end{itemize}
+\end{itemize}
+
 \newpage

### 2023-02-09 music analysis/Equations/Novelty equation.tex
Updates from Overleaf

\begin{equation}
n_i = \frac{\sum\limits_{j=1}^{N} S_{ij} - N\cdot S_{ii}}{\sqrt{\sum\limits_{j=1}^{N} (S_{ij} - S_{ii})^2}}
\end{equation}

% N is the number of time frames, S_{ij} is the similarity between time frames i and j, S_{ii} is the similarity between time frame i and itself, and n_i is the novelty value for time frame i. The numerator of the expression represents the sum of similarities between time frame i and all other time frames, minus the average similarity across all time frames. The denominator of the expression is the standard deviation of the similarities, which is used to normalize the values to ensure that the novelty values are between -1 and 1.%

### 2023-02-09 music analysis/MSA.tex
Updates from Overleaf

@@
 MSA encompasses various aspects of music analysis, including algorithms, current practices, and trends in technology.
-This field aims to comprehensively understand music structure by applying musicological theories and principles and music signal processing algorithms.
+This field aims to comprehensively understand music structure by applying musicological theories, principles, and signal processing algorithms.
 MSA considers the interplay between technical and musical aspects, focusing on improving our understanding of music signals and the music itself.
@@
 Additionally, we will consider the impact of new trends and technological advancements on MSA and the directions in which the field is likely to evolve.
-Through this examination, we aim to provide a thorough understanding of the technical and musical aspects of MSA and its challenges.
+Through this examination, we aim to provide an overview of MSA's technical and musical aspects and its challenges~\cite{Nieto2020}~\cite{Chaki2021}.
 
-~\cite{Nieto2020}~\cite{Chaki2021}
+\section{Concept definition}
+
+Musical structure and form refer to the organization and arrangement of musical elements in a piece of music. They describe how the music is put together and how it unfolds over time.
+
+Musical structure hierarchically arranges various elements of music, such as melody, harmony, rhythm, timbre, and texture\footnote{Musical texture refers to the arrangement and combination of musical elements, including melody, harmony, rhythm, timbre, and dynamics, in a piece of music.
+Different textures, such as monophonic, homophonic, polyphonic, and heterophonic, can affect a piece's overall character and mood.
+Understanding musical texture is vital for music analysis and appreciation.}.
+This hierarchy can take different forms, such as melody being the most critical element, harmony playing a supportive role, or rhythm being the driving force behind the music.
+The structure of a piece of music is often characterized by its elements' repetition, development, and variation.
+
+Music form, however, refers to the larger-scale organization of musical structure over time.
+It describes how music sections are repeated, varied, and put together to create a complete piece.
+Music form can be thought of as the plan or design that underlies a piece of music.
+Many forms are used in music, such as binary, ternary, rondo, sonata, and theme and variations.
+
+Musicologists and theorists have developed various analytical tools and methods for understanding musical structure and form, including Schenkerian analysis, set theory, and formal function analysis.
+These tools and methods help uncover the underlying musical relationships and patterns in a piece of music and provide a framework for understanding how it is put together and how it develops over time.
 
@@
 
-The musical structure analysis (MSA) challenges the definition due to subjectivity, ambiguity, and data scarcity.
+The musical structure analysis (MSA) challenges the definition due to subjectivity, ambiguity\footnote{Perception and interpretation of musical structure can vary widely between individuals and depend on factors such as personal background, cultural context, and individual preferences.
+This is due to the complex interplay between individual differences in perception and interpretation and how the auditory system processes sound.
+These factors highlight the importance of considering individual and cultural context in analyzing and interpreting musical structure.}, and data scarcity.
 A flat structural analysis of an audio signal consists of a set of contiguous, non-overlapping, and labeled time intervals that span the entire duration of the audio signal.
@@
 This subjectivity makes it difficult to objectively analyze the structure of a piece of music, as different annotators may place boundaries between segments differently based on their perception and interpretation of the music.
-It can also have multiple structures, including hierarchical structures, that make it difficult to untangle the truth.
+It can also have multiple structures, including hierarchical structures ~\cite{hiererchical}, that makes it difficult to untangle the underlying structure.
 
 \subsection{Segmentation principles}
-The principles of musical structure analysis (MSA) were initially defined as homogeneity, novelty, and repetition, with the addition of regularity later on.
-To analyze the structure of a musical recording, a self-similarity matrix (SSM) is often used to visualize the degree of similarity between audio frames.
-The SSM results in a square matrix with the highest degree of similarity on the diagonal.
+The main principles of musical structure analysis (MSA) were initially defined as homogeneity, novelty, and repetition, with the addition of regularity later on.
 
@@
 
-\section{Theoretical approach}
-\subsection{Music form}
+\section{Common methods}
 
-Music form refers to the structural organization of a musical composition or performance.
-This can include elements such as the arrangement of musical units (such as rhythm, melody, and harmony) that exhibit repetition or variation, the arrangement of instruments, or the orchestration of a symphonic piece.
-These elements interact to shape the composition and create a meaningful musical experience for the listener.
-The organizational elements can be further broken down into smaller units called phrases, which express a musical idea but lack sufficient weight to stand alone.
-The form of a composition unfolds over time through the expansion and development of these ideas.
-In tonal harmony, form is primarily articulated through cadences, phrases, and periods.
+To analyze the structure of a musical recording, a self-similarity matrix (SSM) is often used to visualize the degree of similarity between audio frames.
+The SSM results in a square matrix with the highest degree of similarity on the diagonal.
+
+It can be computed by representing the audio signal as a spectrogram (or any other suitable representation) and then calculating the similarity between all pairs of time frames in the spectrogram.
+
+One common approach is to use a dot product, where the similarity between two-time frames is equal to the dot product of their vectors. The dot product of two vectors x and y is given by:
+
+\input{music analysis/Equations/SSM equation}
+
+The resulting matrix will be symmetric, with the diagonal elements representing the similarity between a time frame and itself and the off-diagonal elements representing the similarity between two different time frames.
+
+It's also common to normalize the similarity values by dividing each entry by the Euclidean norm of the compared vectors to ensure that the self-similarity matrix has values between -1 and 1.
+
+Given a self-similarity matrix S, the novelty curve can be computed by taking the row-wise sum of the self-similarity matrix and normalizing the values.
+The novelty curve measures the deviation from the average similarity across time frames and can be used for various audio analysis tasks such as beat tracking or segmentation.
+
+\input{music analysis/Equations/Novelty equation}
+
+This representation is used for various tasks, such as identifying repeating patterns in the audio, detecting structural changes in the audio, or for music classification.
+
+\section{Musicological approach}
+\section{Topic overview}
+
+MSA has a long history, dating back to music theory and composition studies.
+In the 18th and 19th centuries, music theorists such as Rameau~\cite{christensen2004rameau} and Schenker~\cite{schenkerdocumentsonline} developed analytical frameworks for understanding the structure of music in terms of harmony, melody, and form.
 
@@
 While the approach is primarily theoretical and relies on human interpretation, it can also be approached through computer algorithms such as CNNs; the results are not the same as human interpretation.
+
+The fundamental structure, also known as \textit{Ursatz}, represents the underlying structure of a tonal work at the most remote or background level, in the most abstract form.
+It comprises an essential elaboration of the tonic triad, including the entire line and accompanying bass arpeggiation.
+The fundamental structure, like the fundamental line, takes one of three forms, depending on which pitch of the tonic triad serves as the primary tone.
+For example, the key of C major would represent the fundamental structure by the fundamental descending line from scale degree 3.
+
+The \textit{Urlinie}, or fundamental line, unfolds the basic triad and presents tonality on horizontal paths.
+The tonal system also flows into this to bring a sense of purposeful order to chords by selecting harmonic degrees.
+Voice leading serves as the mediator between the horizontal formulation of tonality presented by the Urlinie and the vertical formulation presented by the harmonic degrees.
+
+The upper voice of the fundamental structure, represented by the whole line, utilizes a descending direction.
+In contrast, the lower voice, the bass arpeggiation through the fifth, takes an ascending direction (as shown in figure 1).
+The combination of the fundamental line and bass arpeggiation constitutes a unity, and neither can exist alone; it is only through their unification in a contrapuntal structure that they produce art.
 
@@
 Schenkerian analysis uses specialized musical notation and is either presented in a generative manner, starting from the Ursatz and ending at the score or in a reductive manner, starting from the score and reducing it to its fundamental structure.
-The Ursatz is presented in an arrhythmic graph, and rhythmic signs display hierarchical relationships between pitch events.
+The Ursatz is presented in an arrhythmic graph, and rhythmic signs display hierarchical relationships between events.\footnote{In Schenkerian analysis, structural levels refer to the representation of a piece of music at different levels of abstraction.
+These levels typically include the foreground, middle ground, and background.
+Schenker posits that musical form, as represented through these structural levels, can be understood as an energy transformation, specifically the transformation of forces that flow from the background to the foreground through the various levels.}
 

### 2023-02-09 MasterThesis.tex
Updates from Overleaf
5-2-2023 commit

--- 2023-01-14 MasterThesis.tex
@@
 \documentclass[a4paper,12pt,twoside]{report}
+
 \usepackage[left=3cm,right=3cm,top=3cm,bottom=3cm]{geometry} %Margins
@@
 \usepackage[compact]{titlesec}
+\usepackage{float}
+
+\usepackage[utf8]{inputenc}
+\usepackage{amsmath, amssymb, latexsym}
+\usepackage{sidecap}
+%---tikz---
+\usepackage{tikz}
+\usetikzlibrary{decorations.pathreplacing}
+\usetikzlibrary{fadings}
+
 \titlespacing{\section}{0pt}{1ex}{0ex}
@@
 %Title parameters
-\title{Multi-level audio-based music structure analysis}
-\author{Oriol Colomé Font}
+\title{Capturing underlying musical structure: an audio-based approach using deep learning}
+\author{\href{oriol.colome.font@epidemicsound.com}{Oriol Colomé Font}}
 \submitdate{July 2023}
@@
 
+\hypersetup{
+pdftitle={Your PDF title},
+pdfsubject={Your PDF subject},
+pdfauthor={Oriol Colomé Font},
+pdfkeywords={Music; 
+Music Theory; 
+Music Information Retrieval; 
+Music Structure Analysis; 
+Machine Learning; 
+Neural Networks; 
+Deep Learning}
+}
+
 \maketitle
 
-\maketitle
+%\maketitle
 \restoregeometry
@@
 \input{acknowledgements/acknowledgements}
+\input{preface/preface}
 \input{abstract/abstract}
@@
 \input{introduction/introduction}
+%Music analysis explanation
+\input{music analysis/MSA}
+%Methods
 \input{methods/methods}
+%Results
 \input{results/results}
+%Discussion
 \input{discussion/discussion}

### 2023-02-09 abstract/abstract.tex
Updates from Overleaf

@@
 
-The abstract should have at least 200 but not more than 600 words.
-Placed on the right page next to a blank left page.
-A list of keywords (approximately 3 to 5) should be just below the abstract, preceded by the word "Keywords".
-Keywords should be separated by ";".
+The abstract should have at least 200 but not more than 600 words. Placed on the right page next to a blank left page.
 
 \bigskip
-Keywords: Music Information Retrieval; Music Structure Analysis; Deep Learning
+Keywords: Music; Music Theory; Music Information Retrieval; Music Structure Analysis; Machine Learning; Neural Networks; Deep Learning
 

### 2023-02-09 introduction/introduction.tex
Updates from Overleaf

@@
 
-As a music lover and connoisseur, I am interested in gaining a deeper understanding of the fundamental building of musical composition, the various techniques used to create musical works, and the underlying relationship among them.
+As a music lover and connoisseur, I am interested in gaining a deeper understanding of the fundamental building of musical composition, the various techniques used to create musical works, and capturing underlying relationship among them.
 I am deeply interested in learning how to retrieve embedded information within music.

### 2023-02-10 introduction/introduction.tex
Updates from Overleaf

--- 2023-02-09 introduction/introduction.tex
@@
 
-Music\footnote{The term "music" used in this context refers specifically to Western tonal music tradition.
-It is assumed that the musical structures and elements discussed are based on this tradition and may not apply to other musical styles or cultures.} Structure Analysis (MSA) is the field of study that aims to understand music's underlying organization and structure.
+This master thesis investigates the interrelationship between music\footnote{The term "music" used in this context refers specifically to Western tonal music tradition.
+It is assumed that the musical structures and elements discussed are based on this tradition and may not apply to other musical styles or cultures.} structure analysis, aural skills, and the underlying musical structure in musical composition.
+Musical elements, including melody, harmony, rhythm, and form, constitute music structure analysis.
 
-MSA is a multidisciplinary field that draws on techniques from music theory, signal processing, machine learning, and other areas.
-It can be applied to various musical styles and genres and has been used for tasks such as music transcription, generation, and similarity.
+Aural skills encompass perceptual and cognitive abilities, enabling individuals to comprehend musical works through listening.
+These skills encompass the ability to differentiate musical elements, comprehend relationships between them, and discern the structure of a musical composition.
+
+The underlying musical structure refers to the systematic arrangement of musical elements that results in a coherent and expressive musical work.
+
+This master thesis investigates the interplay between music structure analysis, aural skills, and the underlying musical structure through a comprehensive analysis of musical works from diverse styles and genres.
+By utilizing computational techniques from Music Information Retrieval (MIR) and incorporating a musicological perspective to contextualize the findings, this thesis aspires to offer a fresh and insightful examination of these components of musical composition and further our understanding of their relationships.
 
@@
 
-As a music lover and connoisseur, I am interested in gaining a deeper understanding of the fundamental building of musical composition, the various techniques used to create musical works, and the underlying relationship among them.
+As a music lover and connoisseur, I am interested in gaining a deeper understanding of the fundamental building of musical composition, the various techniques used to create musical works, and capturing underlying relationships among them.
 I am deeply interested in learning how to retrieve embedded information within music.
@@
 
-As a professional music transcriber, I am interested in understanding how deep neural networks (DNNs) filter musical features.
+As a professional musician and music transcriber, I am interested in understanding how deep neural networks (DNNs) filter musical features.
 In other words, I am eager to learn how DNNs listen~\cite{7500246} to music.
 
-By studying music structure analysis using musically motivated neural networks, you will gain an in-depth understanding of the latest advancements in the field and how these techniques are being used to revolutionize our understanding of music.
+By studying music structure analysis using musically motivated neural networks, we will gain an in-depth understanding of the latest advancements in the field and how these techniques are being used to revolutionize our understanding of music.
 Additionally, we will be able to contribute to developing new and innovative methods for musical analysis~\cite{Huang2019MusicTG}

### 2023-02-10 music analysis/MSA.tex
Updates from Overleaf

@@
 Given a self-similarity matrix S, the novelty curve can be computed by taking the row-wise sum of the self-similarity matrix and normalizing the values.
-The novelty curve measures the deviation from the average similarity across time frames and can be used for various audio analysis tasks such as beat tracking or segmentation.
+The novelty curve measures the deviation from the average similarity across time frames.
 
@@
 Schenkerian analysis uses specialized musical notation and is either presented in a generative manner, starting from the Ursatz and ending at the score or in a reductive manner, starting from the score and reducing it to its fundamental structure.
-The Ursatz is presented in an arrhythmic graph, and rhythmic signs display hierarchical relationships between events.\footnote{In Schenkerian analysis, structural levels refer to the representation of a piece of music at different levels of abstraction.
+The Ursatz is presented in an arrhythmic graph, and rhythmic signs display hierarchical relationships between events.
+\footnote{In Schenkerian analysis, structural levels refer to the representation of a piece of music at different levels of abstraction.
 These levels typically include the foreground, middle ground, and background.
@@
 Aural music skills are the capacity to comprehend and analyze musical compositions through listening.
-These skills encompass a wide range of abilities, including identifying musical elements such as rhythm, melody, harmony, timbre, and form, performing music from memory, and transcribing audio recordings into written musical scores.
+These skills include identifying musical elements such as rhythm, melody, harmony, timbre, and form, performing music from memory, and transcribing audio recordings into written musical scores.
 
@@
 Aural music skills are crucial not only for an individual's personal musical growth but also for gaining a deeper understanding of the underlying musical structure of a piece.
-Identifying and analyzing musical elements through listening allows one to comprehend the relationships between these elements and how they contribute to the overall musical structure.
+Identifying and analyzing musical elements through listening allows one to comprehend their relationships and how they contribute to the overall musical structure.
 This ability to perceive and understand musical structure is fundamental to making informed decisions and interpretations.
@@
 Moreover, aural skills also play an essential role in preserving and continuing musical traditions, as they allow musicians to accurately pass down and preserve the musical heritage of their culture.
-By recognizing and understanding the underlying musical structures of traditional music, musicians can maintain the authenticity of the music and ensure its continuation for future generations.
+By recognizing and understanding the underlying musical structures of traditional music, musicians can maintain its authenticity and ensure its continuation for future generations.
 
-In conclusion, aural music skills are crucial for personal musical growth and for gaining a deeper understanding of the musical structure, effective musical communication and collaboration, and the preservation of musical traditions.
+In conclusion, aural music skills are crucial for personal musical growth and a deeper understanding of the musical structure, effective musical communication, collaboration, and preserving musical traditions.

### 2023-02-16 introduction/introduction.tex
Updates from Overleaf

@@
 
-This master thesis investigates the interrelationship between music\footnote{The term "music" used in this context refers specifically to Western tonal music tradition.
-It is assumed that the musical structures and elements discussed are based on this tradition and may not apply to other musical styles or cultures.} structure analysis, aural skills, and the underlying musical structure in musical composition.
-Musical elements, including melody, harmony, rhythm, and form, constitute music structure analysis.
+Music is a complex and fascinating art form that has been studied by scholars and musicians for centuries.
+Music theory plays a crucial role in understanding the underlying principles of how music is organized and composed, and analyzing the structure of music is a challenging task.
 
-Aural skills encompass perceptual and cognitive abilities, enabling individuals to comprehend musical works through listening.
-These skills encompass the ability to differentiate musical elements, comprehend relationships between them, and discern the structure of a musical composition.
+Recently, the field of Music Structure Analysis (MSA) has emerged as a subfield of Music Information Retrieval (MIR), aiming to develop computational methods to analyze the structure of music.
+This master thesis investigates the relationship between MSA, aural skills, and the underlying musical structure in musical composition.
 
+The thesis explores the musical elements that constitute music\footnote{The term "music" used in this context refers specifically to Western tonal music tradition.
+It is assumed that the musical structures and elements discussed are based on this tradition and may not apply to other musical styles or cultures.} structure analysis, including melody, harmony, rhythm, and form.
+Aural skills involve perceptual and cognitive abilities that enable individuals to comprehend musical works through listening.
 The underlying musical structure refers to the systematic arrangement of musical elements that results in a coherent and expressive musical work.
 
-This master thesis investigates the interplay between music structure analysis, aural skills, and the underlying musical structure through a comprehensive analysis of musical works from diverse styles and genres.
-By utilizing computational techniques from Music Information Retrieval (MIR) and incorporating a musicological perspective to contextualize the findings, this thesis aspires to offer a fresh and insightful examination of these components of musical composition and further our understanding of their relationships.
+This thesis provides a comprehensive analysis of musical works from diverse styles and genres, utilizing computational techniques from MIR and incorporating a musicological perspective to contextualize the findings.
+
+The goal of this research is to offer fresh insights into these components of musical composition and advance our understanding of their relationships.
 
@@
 
+Music is a complex and multi-faceted phenomenon, and implementing a model that mimics human aural music skills is challenging.
+However, using the latest deep learning techniques, we aim to build a model that achieves good results for a specific task in the domain of music.
+
 \section{Structure of the Report}
@@
 \begin{itemize}
-\item Introduction
+\item Chapter 1
   \begin{itemize}
@@
   \end{itemize}
-\item Main Body
+\item Chapter 2
   \begin{itemize}
@@
   \end{itemize}
-\item Conclusion
+\item Chapter 3
   \begin{itemize}

### 2023-02-16 music analysis/MSA.tex
Updates from Overleaf

@@
 
-The musical structure analysis (MSA) challenges the definition due to subjectivity, ambiguity\footnote{Perception and interpretation of musical structure can vary widely between individuals and depend on factors such as personal background, cultural context, and individual preferences.
+MSA challenges its definition due to subjectivity, ambiguity\footnote{Perception and interpretation of musical structure can vary widely between individuals and depend on factors such as personal background, cultural context, and individual preferences.
 This is due to the complex interplay between individual differences in perception and interpretation and how the auditory system processes sound.

### 2023-02-18 introduction/introduction.tex
Updates from Overleaf

@@
 
-Music is a complex and fascinating art form that has been studied by scholars and musicians for centuries.
+Music is a complex and fascinating art form studied by scholars and musicians for centuries.
 Music theory plays a crucial role in understanding the underlying principles of how music is organized and composed, and analyzing the structure of music is a challenging task.
 
-Recently, the field of Music Structure Analysis (MSA) has emerged as a subfield of Music Information Retrieval (MIR), aiming to develop computational methods to analyze the structure of music.
+Recently, Music Structure Analysis (MSA) has emerged as a subfield of Music Information Retrieval (MIR), aiming to develop computational methods to analyze the structure of music.
 This master thesis investigates the relationship between MSA, aural skills, and the underlying musical structure in musical composition.
+
+In recent years, the utilization of neural networks has allowed for the creation of low-dimensional musical embeddings that capture important musical features and enable the computation of semantic similarity between musical passages.
+By learning an embedding function $f(x) \in \mathbb{R}^d$ that maps a given passage $x$ to a vector in the real space $\mathbb{R}^d$, researchers can quantify the semantic similarity between two musical passages using the Euclidean distance, which is represented by the formula $D_{i,j} = ||f(x_i) - f(x_j)||^2$.
+Adequate embedding space is essential in ensuring that the generated output aligns with human expectations, especially in interactive applications where a human performer influences the machine's response.
+The success of such systems depends on the embedding space's ability to interpret music in a way that aligns with human perception.
 
@@
 
-The goal of this research is to offer fresh insights into these components of musical composition and advance our understanding of their relationships.
+This research aims to offer fresh insights into these components of musical composition and advance our understanding of their relationships.
 

### 2023-03-03 introduction/Subsections/Introduction.tex
Updates from Overleaf

--- 2023-02-18 introduction/introduction.tex
@@
-\normallinespacing
-
 \chapter{Introduction}
@@
 This research aims to offer fresh insights into these components of musical composition and advance our understanding of their relationships.
-
-\section{Motivation}
-
-As a music lover and connoisseur, I am interested in gaining a deeper understanding of the fundamental building of musical composition, the various techniques used to create musical works, and capturing underlying relationships among them.
-I am deeply interested in learning how to retrieve embedded information within music.
-The study of music structure analysis provides a means to systematically analyze and understand musical pieces.
-It has traditionally been approached through music theory, formal musical notation, musical analysis techniques, and machine learning, which I plan to blend.
-
-With the advent of artificial intelligence and machine learning, Music Information Retrieval (MIR) has expanded to encompass musically motivated neural network architectures.
-These networks are designed to incorporate musical concepts and perceptual approaches and use this knowledge to analyze and understand the structure of musical pieces in a way that goes beyond traditional music analysis techniques.
-
-As a professional musician and music transcriber, I am interested in understanding how deep neural networks (DNNs) filter musical features.
-In other words, I am eager to learn how DNNs listen~\cite{7500246} to music.
-
-By studying music structure analysis using musically motivated neural networks, we will gain an in-depth understanding of the latest advancements in the field and how these techniques are being used to revolutionize our understanding of music.
-Additionally, we will be able to contribute to developing new and innovative methods for musical analysis~\cite{Huang2019MusicTG}
-
-\section{Objectives}
-
-As a professional music transcriber, I aim to understand how deep neural networks (DNNs) filter musical features, listen to the NN layers from a musician's perspective and analyze the resulting data.
-I aim to approach the technology from a technical and musical standpoint to understand how DNNs process and extract musical information.
-By doing so, I aim to enhance the accuracy and efficiency of the process and contribute to developing AI technology for music analysis.
-By combining my expertise in music with my -not fully developed- knowledge of DNNs, I hope to bring a unique perspective to the field and contribute to the advancement of music analysis.
-
-Music is a complex and multi-faceted phenomenon, and implementing a model that mimics human aural music skills is challenging.
-However, using the latest deep learning techniques, we aim to build a model that achieves good results for a specific task in the domain of music.
-
-\section{Structure of the Report}
-
-In this report, we have organized the information into several sections and sub-sections to provide a clear and comprehensive overview of the topic. The structure of the report is as follows:
-
-\begin{itemize}
-\item Chapter 1
-  \begin{itemize}
-  \item Purpose
-  \item Methodology
-  \item Scope
-  \end{itemize}
-\item Chapter 2
-  \begin{itemize}
-  \item Section 1
-  \item Section 2
-  \item Section 3
-  \end{itemize}
-\item Chapter 3
-  \begin{itemize}
-  \item Summary
-  \item Recommendations
-  \end{itemize}
-\item References
-  \begin{itemize}
-  \item Sources Cited
-  \end{itemize}
-\end{itemize}
-
-\newpage

### 2023-03-03 introduction/Subsections/Motivation.tex
Updates from Overleaf

--- 2023-02-10 introduction/introduction.tex
@@
-\normallinespacing
-
-\chapter{Introduction}
-
-This master thesis investigates the interrelationship between music\footnote{The term "music" used in this context refers specifically to Western tonal music tradition.
-It is assumed that the musical structures and elements discussed are based on this tradition and may not apply to other musical styles or cultures.} structure analysis, aural skills, and the underlying musical structure in musical composition.
-Musical elements, including melody, harmony, rhythm, and form, constitute music structure analysis.
-
-Aural skills encompass perceptual and cognitive abilities, enabling individuals to comprehend musical works through listening.
-These skills encompass the ability to differentiate musical elements, comprehend relationships between them, and discern the structure of a musical composition.
-
-The underlying musical structure refers to the systematic arrangement of musical elements that results in a coherent and expressive musical work.
-
-This master thesis investigates the interplay between music structure analysis, aural skills, and the underlying musical structure through a comprehensive analysis of musical works from diverse styles and genres.
-By utilizing computational techniques from Music Information Retrieval (MIR) and incorporating a musicological perspective to contextualize the findings, this thesis aspires to offer a fresh and insightful examination of these components of musical composition and further our understanding of their relationships.
-
 \section{Motivation}
@@
 Additionally, we will be able to contribute to developing new and innovative methods for musical analysis~\cite{Huang2019MusicTG}
-
-\section{Objectives}
-
-As a professional music transcriber, I aim to understand how deep neural networks (DNNs) filter musical features, listen to the NN layers from a musician's perspective and analyze the resulting data.
-I aim to approach the technology from a technical and musical standpoint to understand how DNNs process and extract musical information.
-By doing so, I aim to enhance the accuracy and efficiency of the process and contribute to developing AI technology for music analysis.
-By combining my expertise in music with my -not fully developed- knowledge of DNNs, I hope to bring a unique perspective to the field and contribute to the advancement of music analysis.
-
-\section{Structure of the Report}
-
-In this report, we have organized the information into several sections and sub-sections to provide a clear and comprehensive overview of the topic. The structure of the report is as follows:
-
-\begin{itemize}
-\item Introduction
-  \begin{itemize}
-  \item Purpose
-  \item Methodology
-  \item Scope
-  \end{itemize}
-\item Main Body
-  \begin{itemize}
-  \item Section 1
-  \item Section 2
-  \item Section 3
-  \end{itemize}
-\item Conclusion
-  \begin{itemize}
-  \item Summary
-  \item Recommendations
-  \end{itemize}
-\item References
-  \begin{itemize}
-  \item Sources Cited
-  \end{itemize}
-\end{itemize}
-
-\newpage

### 2023-03-03 introduction/Subsections/Objectives.tex
Updates from Overleaf

--- 2023-02-16 introduction/introduction.tex
@@
-\normallinespacing
-
-\chapter{Introduction}
-
-Music is a complex and fascinating art form that has been studied by scholars and musicians for centuries.
-Music theory plays a crucial role in understanding the underlying principles of how music is organized and composed, and analyzing the structure of music is a challenging task.
-
-Recently, the field of Music Structure Analysis (MSA) has emerged as a subfield of Music Information Retrieval (MIR), aiming to develop computational methods to analyze the structure of music.
-This master thesis investigates the relationship between MSA, aural skills, and the underlying musical structure in musical composition.
-
-The thesis explores the musical elements that constitute music\footnote{The term "music" used in this context refers specifically to Western tonal music tradition.
-It is assumed that the musical structures and elements discussed are based on this tradition and may not apply to other musical styles or cultures.} structure analysis, including melody, harmony, rhythm, and form.
-Aural skills involve perceptual and cognitive abilities that enable individuals to comprehend musical works through listening.
-The underlying musical structure refers to the systematic arrangement of musical elements that results in a coherent and expressive musical work.
-
-This thesis provides a comprehensive analysis of musical works from diverse styles and genres, utilizing computational techniques from MIR and incorporating a musicological perspective to contextualize the findings.
-
-The goal of this research is to offer fresh insights into these components of musical composition and advance our understanding of their relationships.
-
-\section{Motivation}
-
-As a music lover and connoisseur, I am interested in gaining a deeper understanding of the fundamental building of musical composition, the various techniques used to create musical works, and capturing underlying relationships among them.
-I am deeply interested in learning how to retrieve embedded information within music.
-The study of music structure analysis provides a means to systematically analyze and understand musical pieces.
-It has traditionally been approached through music theory, formal musical notation, musical analysis techniques, and machine learning, which I plan to blend.
-
-With the advent of artificial intelligence and machine learning, Music Information Retrieval (MIR) has expanded to encompass musically motivated neural network architectures.
-These networks are designed to incorporate musical concepts and perceptual approaches and use this knowledge to analyze and understand the structure of musical pieces in a way that goes beyond traditional music analysis techniques.
-
-As a professional musician and music transcriber, I am interested in understanding how deep neural networks (DNNs) filter musical features.
-In other words, I am eager to learn how DNNs listen~\cite{7500246} to music.
-
-By studying music structure analysis using musically motivated neural networks, we will gain an in-depth understanding of the latest advancements in the field and how these techniques are being used to revolutionize our understanding of music.
-Additionally, we will be able to contribute to developing new and innovative methods for musical analysis~\cite{Huang2019MusicTG}
-
 \section{Objectives}
@@
 However, using the latest deep learning techniques, we aim to build a model that achieves good results for a specific task in the domain of music.
-
-\section{Structure of the Report}
-
-In this report, we have organized the information into several sections and sub-sections to provide a clear and comprehensive overview of the topic. The structure of the report is as follows:
-
-\begin{itemize}
-\item Chapter 1
-  \begin{itemize}
-  \item Purpose
-  \item Methodology
-  \item Scope
-  \end{itemize}
-\item Chapter 2
-  \begin{itemize}
-  \item Section 1
-  \item Section 2
-  \item Section 3
-  \end{itemize}
-\item Chapter 3
-  \begin{itemize}
-  \item Summary
-  \item Recommendations
-  \end{itemize}
-\item References
-  \begin{itemize}
-  \item Sources Cited
-  \end{itemize}
-\end{itemize}
-
-\newpage

### 2023-03-03 introduction/Subsections/Structure of the report.tex
Updates from Overleaf

--- 2023-02-10 introduction/introduction.tex
@@
-\normallinespacing
-
-\chapter{Introduction}
-
-This master thesis investigates the interrelationship between music\footnote{The term "music" used in this context refers specifically to Western tonal music tradition.
-It is assumed that the musical structures and elements discussed are based on this tradition and may not apply to other musical styles or cultures.} structure analysis, aural skills, and the underlying musical structure in musical composition.
-Musical elements, including melody, harmony, rhythm, and form, constitute music structure analysis.
-
-Aural skills encompass perceptual and cognitive abilities, enabling individuals to comprehend musical works through listening.
-These skills encompass the ability to differentiate musical elements, comprehend relationships between them, and discern the structure of a musical composition.
-
-The underlying musical structure refers to the systematic arrangement of musical elements that results in a coherent and expressive musical work.
-
-This master thesis investigates the interplay between music structure analysis, aural skills, and the underlying musical structure through a comprehensive analysis of musical works from diverse styles and genres.
-By utilizing computational techniques from Music Information Retrieval (MIR) and incorporating a musicological perspective to contextualize the findings, this thesis aspires to offer a fresh and insightful examination of these components of musical composition and further our understanding of their relationships.
-
-\section{Motivation}
-
-As a music lover and connoisseur, I am interested in gaining a deeper understanding of the fundamental building of musical composition, the various techniques used to create musical works, and capturing underlying relationships among them.
-I am deeply interested in learning how to retrieve embedded information within music.
-The study of music structure analysis provides a means to systematically analyze and understand musical pieces.
-It has traditionally been approached through music theory, formal musical notation, musical analysis techniques, and machine learning, which I plan to blend.
-
-With the advent of artificial intelligence and machine learning, Music Information Retrieval (MIR) has expanded to encompass musically motivated neural network architectures.
-These networks are designed to incorporate musical concepts and perceptual approaches and use this knowledge to analyze and understand the structure of musical pieces in a way that goes beyond traditional music analysis techniques.
-
-As a professional musician and music transcriber, I am interested in understanding how deep neural networks (DNNs) filter musical features.
-In other words, I am eager to learn how DNNs listen~\cite{7500246} to music.
-
-By studying music structure analysis using musically motivated neural networks, we will gain an in-depth understanding of the latest advancements in the field and how these techniques are being used to revolutionize our understanding of music.
-Additionally, we will be able to contribute to developing new and innovative methods for musical analysis~\cite{Huang2019MusicTG}
-
-\section{Objectives}
-
-As a professional music transcriber, I aim to understand how deep neural networks (DNNs) filter musical features, listen to the NN layers from a musician's perspective and analyze the resulting data.
-I aim to approach the technology from a technical and musical standpoint to understand how DNNs process and extract musical information.
-By doing so, I aim to enhance the accuracy and efficiency of the process and contribute to developing AI technology for music analysis.
-By combining my expertise in music with my -not fully developed- knowledge of DNNs, I hope to bring a unique perspective to the field and contribute to the advancement of music analysis.
-
 \section{Structure of the Report}
@@
 \end{itemize}
-
-\newpage

### 2023-03-03 introduction/introduction.tex
Updates from Overleaf

--- 2023-02-10 introduction/introduction.tex
@@
 
-\chapter{Introduction}
-
-This master thesis investigates the interrelationship between music\footnote{The term "music" used in this context refers specifically to Western tonal music tradition.
-It is assumed that the musical structures and elements discussed are based on this tradition and may not apply to other musical styles or cultures.} structure analysis, aural skills, and the underlying musical structure in musical composition.
-Musical elements, including melody, harmony, rhythm, and form, constitute music structure analysis.
-
-Aural skills encompass perceptual and cognitive abilities, enabling individuals to comprehend musical works through listening.
-These skills encompass the ability to differentiate musical elements, comprehend relationships between them, and discern the structure of a musical composition.
-
-The underlying musical structure refers to the systematic arrangement of musical elements that results in a coherent and expressive musical work.
-
-This master thesis investigates the interplay between music structure analysis, aural skills, and the underlying musical structure through a comprehensive analysis of musical works from diverse styles and genres.
-By utilizing computational techniques from Music Information Retrieval (MIR) and incorporating a musicological perspective to contextualize the findings, this thesis aspires to offer a fresh and insightful examination of these components of musical composition and further our understanding of their relationships.
-
-\section{Motivation}
-
-As a music lover and connoisseur, I am interested in gaining a deeper understanding of the fundamental building of musical composition, the various techniques used to create musical works, and capturing underlying relationships among them.
-I am deeply interested in learning how to retrieve embedded information within music.
-The study of music structure analysis provides a means to systematically analyze and understand musical pieces.
-It has traditionally been approached through music theory, formal musical notation, musical analysis techniques, and machine learning, which I plan to blend.
-
-With the advent of artificial intelligence and machine learning, Music Information Retrieval (MIR) has expanded to encompass musically motivated neural network architectures.
-These networks are designed to incorporate musical concepts and perceptual approaches and use this knowledge to analyze and understand the structure of musical pieces in a way that goes beyond traditional music analysis techniques.
-
-As a professional musician and music transcriber, I am interested in understanding how deep neural networks (DNNs) filter musical features.
-In other words, I am eager to learn how DNNs listen~\cite{7500246} to music.
-
-By studying music structure analysis using musically motivated neural networks, we will gain an in-depth understanding of the latest advancements in the field and how these techniques are being used to revolutionize our understanding of music.
-Additionally, we will be able to contribute to developing new and innovative methods for musical analysis~\cite{Huang2019MusicTG}
-
-\section{Objectives}
-
-As a professional music transcriber, I aim to understand how deep neural networks (DNNs) filter musical features, listen to the NN layers from a musician's perspective and analyze the resulting data.
-I aim to approach the technology from a technical and musical standpoint to understand how DNNs process and extract musical information.
-By doing so, I aim to enhance the accuracy and efficiency of the process and contribute to developing AI technology for music analysis.
-By combining my expertise in music with my -not fully developed- knowledge of DNNs, I hope to bring a unique perspective to the field and contribute to the advancement of music analysis.
-
-\section{Structure of the Report}
-
-In this report, we have organized the information into several sections and sub-sections to provide a clear and comprehensive overview of the topic. The structure of the report is as follows:
-
-\begin{itemize}
-\item Introduction
-  \begin{itemize}
-  \item Purpose
-  \item Methodology
-  \item Scope
-  \end{itemize}
-\item Main Body
-  \begin{itemize}
-  \item Section 1
-  \item Section 2
-  \item Section 3
-  \end{itemize}
-\item Conclusion
-  \begin{itemize}
-  \item Summary
-  \item Recommendations
-  \end{itemize}
-\item References
-  \begin{itemize}
-  \item Sources Cited
-  \end{itemize}
-\end{itemize}
+\input{introduction/Subsections/Introduction}
+\input{introduction/Subsections/Motivation}
+\input{introduction/Subsections/Objectives}
+\input{introduction/Subsections/Structure of the report}
 

### 2023-03-04 introduction/Subsections/Introduction.tex
Updates from Overleaf

@@
 
-Music is a complex and fascinating art form studied by scholars and musicians for centuries.
-Music theory plays a crucial role in understanding the underlying principles of how music is organized and composed, and analyzing the structure of music is a challenging task.
+The purpose of this work is to generalize the fundamental harmonic structure of music to facilitate its application in downstream tasks.
+Music, being a complex and fascinating art form, has been extensively studied by scholars and musicians for centuries.
+Understanding how music is organized and composed is critical, and music theory plays a vital role in this regard.
+Analyzing music structure poses a significant challenge as it comprises several elements, including melody, harmony, rhythm, and form.
 
-Recently, Music Structure Analysis (MSA) has emerged as a subfield of Music Information Retrieval (MIR), aiming to develop computational methods to analyze the structure of music.
-This master thesis investigates the relationship between MSA, aural skills, and the underlying musical structure in musical composition.
+In recent years, the utilization of neural networks has made it possible to create low-dimensional musical embeddings that capture crucial musical features and enable the computation of semantic similarity between musical passages.
+By acquiring an embedding function $f(x) \in \mathbb{R}^d$ that maps a given passage $x$ to a vector in the real space $\mathbb{R}^d$, researchers can measure the semantic similarity between two musical passages using the Euclidean distance, as represented by the formula $D_{i,j} = ||f(x_i) - f(x_j)||^2$.
+The effectiveness of such systems depends on the embedding space's ability to interpret music in a way that aligns with human perception.
+Therefore, a suitable embedding space is crucial to ensure that the output aligns with human expectations.
 
-In recent years, the utilization of neural networks has allowed for the creation of low-dimensional musical embeddings that capture important musical features and enable the computation of semantic similarity between musical passages.
-By learning an embedding function $f(x) \in \mathbb{R}^d$ that maps a given passage $x$ to a vector in the real space $\mathbb{R}^d$, researchers can quantify the semantic similarity between two musical passages using the Euclidean distance, which is represented by the formula $D_{i,j} = ||f(x_i) - f(x_j)||^2$.
-Adequate embedding space is essential in ensuring that the generated output aligns with human expectations, especially in interactive applications where a human performer influences the machine's response.
-The success of such systems depends on the embedding space's ability to interpret music in a way that aligns with human perception.
-
-The thesis explores the musical elements that constitute music\footnote{The term "music" used in this context refers specifically to Western tonal music tradition.
-It is assumed that the musical structures and elements discussed are based on this tradition and may not apply to other musical styles or cultures.} structure analysis, including melody, harmony, rhythm, and form.
-Aural skills involve perceptual and cognitive abilities that enable individuals to comprehend musical works through listening.
+The thesis under discussion explores the various musical elements that constitute music structure analysis, which includes melody, harmony, rhythm, and form.
+Aural skills are required to comprehend musical works through listening, as they involve perceptual and cognitive abilities.
 The underlying musical structure refers to the systematic arrangement of musical elements that results in a coherent and expressive musical work.
 
-This thesis provides a comprehensive analysis of musical works from diverse styles and genres, utilizing computational techniques from MIR and incorporating a musicological perspective to contextualize the findings.
+To provide a comprehensive analysis of musical works from diverse styles and genres, the thesis employs computational techniques from MIR and incorporates a musicological perspective to contextualize the findings.
+The objective is to offer fresh insights into these components of musical composition and advance our understanding of their relationships.
 
-This research aims to offer fresh insights into these components of musical composition and advance our understanding of their relationships.
+The study investigates the correlation between MSA, aural skills, and the underlying musical structure in musical composition.
+Through this research, the thesis aims to provide a better understanding of musical composition components, their relationships, and their practical applications.

### 2023-03-04 introduction/Subsections/Motivation.tex
Updates from Overleaf

@@
 
-As a music lover and connoisseur, I am interested in gaining a deeper understanding of the fundamental building of musical composition, the various techniques used to create musical works, and capturing underlying relationships among them.
+As a music lover, professional musician, and connoisseur, I am interested in gaining a deeper understanding of the fundamental building of musical composition, the various techniques used to create musical works, and capturing underlying relationships among them.
 I am deeply interested in learning how to retrieve embedded information within music.
@@
 
-With the advent of artificial intelligence and machine learning, Music Information Retrieval (MIR) has expanded to encompass musically motivated neural network architectures.
+With the advent of Artificial Intelligence (AI) and Machine Learning (ML), Music Information Retrieval (MIR) has expanded to encompass musically motivated neural network architectures.
 These networks are designed to incorporate musical concepts and perceptual approaches and use this knowledge to analyze and understand the structure of musical pieces in a way that goes beyond traditional music analysis techniques.
 
-As a professional musician and music transcriber, I am interested in understanding how deep neural networks (DNNs) filter musical features.
-In other words, I am eager to learn how DNNs listen~\cite{7500246} to music.
+As a professional musician and music transcriber, I am interested in understanding how Deep Neural Networks (DNNs) filter musical features.
+In other words, I am eager to learn how DNNs listen to music.
 
 By studying music structure analysis using musically motivated neural networks, we will gain an in-depth understanding of the latest advancements in the field and how these techniques are being used to revolutionize our understanding of music.
-Additionally, we will be able to contribute to developing new and innovative methods for musical analysis~\cite{Huang2019MusicTG}
+Additionally, we will be able to contribute to developing new and innovative methods for musical analysis.

### 2023-03-04 music analysis/Equations/Novelty equation.tex
Updates from Overleaf

@@
 
-% N is the number of time frames, S_{ij} is the similarity between time frames i and j, S_{ii} is the similarity between time frame i and itself, and n_i is the novelty value for time frame i.
-The numerator of the expression represents the sum of similarities between time frame i and all other time frames, minus the average similarity across all time frames.
-The denominator of the expression is the standard deviation of the similarities, which is used to normalize the values to ensure that the novelty values are between -1 and 1.%
+Where:
+\begin{itemize}
+\item $N$ is the number of time frames.
+\item $S_{ij}$ is the similarity between time frames $i$ and $j$.
+\item $S_{ii}$ is the similarity between time frame $i$ and itself.
+\item $n_i$ is the novelty value for time frame $i$.
+\end{itemize}
+
+The numerator of the expression represents the sum of similarities between time frame $i$ and all other time frames, minus the average similarity across all time frames.
+The denominator of the expression is the standard deviation of the similarities, which is used to normalize the values to ensure that the novelty values are between -1 and 1.

### 2023-03-04 music analysis/MSA.tex
Updates from Overleaf

@@
 Additionally, we will consider the impact of new trends and technological advancements on MSA and the directions in which the field is likely to evolve.
-Through this examination, we aim to provide an overview of MSA's technical and musical aspects and its challenges~\cite{Nieto2020}~\cite{Chaki2021}.
+Through this examination, we aim to provide an overview of MSA's technical and musical aspects and its challenges.
 
@@
 This subjectivity makes it difficult to objectively analyze the structure of a piece of music, as different annotators may place boundaries between segments differently based on their perception and interpretation of the music.
-It can also have multiple structures, including hierarchical structures ~\cite{hiererchical}, that makes it difficult to untangle the underlying structure.
+It can also have multiple structures, including hierarchical structures, that make it difficult to untangle the underlying structure.
 
@@
 
+The method of computing a novelty curve from a self-similarity matrix is widely used in Music Information Retrieval and audio analysis to assess the deviation from the average similarity of a given time frame in a music signal.
+It is primarily driven by Digital Signal Processing (DSP) and not necessarily motivated by musical considerations, yet it can be valuable in music segmentation, beat tracking, and structural analysis.
+However, the approach may be vulnerable to the choice of self-similarity measure used to calculate the matrix, and it may require further domain-specific knowledge and interpretation to extract practical information.
+Besides, the novelty curve could be limited in its ability to reflect musically meaningful events as it measures the deviation from the average similarity across time frames, rather than following musically motivated criteria.
+Therefore, the analysis and interpretation of the novelty curve may require additional caution to ensure its efficacy in capturing useful information about the music signal.
+
 \section{Musicological approach}
@@
 MSA has a long history, dating back to music theory and composition studies.
-In the 18th and 19th centuries, music theorists such as Rameau~\cite{christensen2004rameau} and Schenker~\cite{schenkerdocumentsonline} developed analytical frameworks for understanding the structure of music in terms of harmony, melody, and form.
+In the 18th and 19th centuries, music theorists such as Rameau and Schenker developed analytical frameworks for understanding the structure of music in terms of harmony, melody, and form.
 
@@
 
-Heinrich Schenker~\cite{schenkerdocumentsonline} was a prominent music theorist who developed \textit{Schenkerian Analysis}, a method for analyzing tonal music.
+Heinrich Schenker was a prominent music theorist who developed \textit{Schenkerian Analysis}, a method for analyzing tonal music.
 This method is based on the concept of "the Ursatz," a fundamental structure of three levels: foreground, middle-ground, and background.
@@
 
-Schenkerian analysis uses specialized musical notation and is either presented in a generative manner, starting from the Ursatz and ending at the score or in a reductive manner, starting from the score and reducing it to its fundamental structure.
+Schenkerian analysis uses specialized musical notation and is either presented in a generative manner, starting from the Ursatz and ending at the score, or in a reductive manner, starting from the score and reducing it to its fundamental structure.
 The Ursatz is presented in an arrhythmic graph, and rhythmic signs display hierarchical relationships between events.
@@
 
-Aural music skills are the capacity to comprehend and analyze musical compositions through listening.
-These skills include identifying musical elements such as rhythm, melody, harmony, timbre, and form, performing music from memory, and transcribing audio recordings into written musical scores.
+The capacity to comprehend and analyze musical compositions through listening requires a range of abilities.
+These include recognizing musical elements such as rhythm, melody, harmony, timbre, and form, performing music from memory, and transcribing audio recordings into written musical scores.
 
-In the context of music, having strong aural skills is crucial for achieving a complete understanding of the art form.
-It enables musicians to make knowledgeable decisions about their playing and interpretation, as well as to evaluate the playing of others critically.
-Additionally, aural skills are an integral part of music education, playing a role in deepening one's appreciation of music and promoting creativity and musical expression.
+Having a keen sense of hearing is crucial for a complete understanding of music.
+It enables musicians to make informed decisions about their playing and interpretation, as well as critically evaluate the playing of others.
+Aural abilities are essential in music education, deepening appreciation of music and promoting creativity and expression.
 
-Aural skills can be honed through various activities, such as listening to music, singing, playing musical instruments, and analyzing music through written or visual means.
-Formal music education teaches aural skills through ear training, dictation, and sight-reading exercises.
+Developing these skills can be achieved through various activities, such as attentive listening, singing, playing instruments, and analyzing music through written or visual means.
+Formal music education includes ear training, dictation, and sight-reading exercises.
 
-Aural music skills are crucial not only for an individual's personal musical growth but also for gaining a deeper understanding of the underlying musical structure of a piece.
-Identifying and analyzing musical elements through listening allows one to comprehend their relationships and how they contribute to the overall musical structure.
-This ability to perceive and understand musical structure is fundamental to making informed decisions and interpretations.
+Strong aural abilities facilitate personal musical growth and understanding of the underlying musical structure of a piece.
+Identifying and analyzing musical elements through listening allows comprehension of their relationships and contribution to the overall musical structure.
+This is fundamental to making informed decisions and interpretations.
 
-In addition, solid aural skills enable musicians to communicate their musical ideas to others effectively, as well as to more fully comprehend the musical ideas of others.
-They provide a common ground for musical discussion and collaboration, allowing musicians to create and perform music at a higher level.
+Solid listening skills enable effective communication and collaboration among musicians. They provide a common ground for musical discussion, creating and performing music at a higher level.
 
-Moreover, aural skills also play an essential role in preserving and continuing musical traditions, as they allow musicians to accurately pass down and preserve the musical heritage of their culture.
-By recognizing and understanding the underlying musical structures of traditional music, musicians can maintain its authenticity and ensure its continuation for future generations.
+The ability to perceive and understand musical structure is also essential for preserving musical traditions by accurately passing down the musical heritage of a culture.
+Recognizing and understanding the underlying musical structures of traditional music maintains its authenticity and ensures its continuation for future generations.
 
-In conclusion, aural music skills are crucial for personal musical growth and a deeper understanding of the musical structure, effective musical communication, collaboration, and preserving musical traditions.
+In conclusion, the ability to comprehend and analyze musical compositions through listening is vital for personal musical growth, understanding the musical structure, effective communication, collaboration, and preserving musical traditions.

### 2023-03-04 music analysis/MSA.tex
Updates from Overleaf

@@
 
-It can be computed by representing the audio signal as a spectrogram (or any other suitable representation) and then calculating the similarity between all pairs of time frames in the spectrogram.
+It can be computed by representing the audio signal as a spectrogram (or any other suitable representation such as CQT or a Mel-spectrogram) and then calculating the similarity between all pairs of time frames in the spectrogram.
 

### 2023-03-09 future work/future work.tex
Updates from Overleaf

chapter{}

hybrid autoencoder architecture + UNet stuff

### 2023-03-10 introduction/Subsections/Introduction.tex
Updates from Overleaf

@@
 
-The purpose of this work is to generalize the fundamental harmonic structure of music to facilitate its application in downstream tasks.
+The purpose of this work is to generalize the fundamental harmonic structure of music to facilitate its application in downstream music information retrieval (MIR) tasks.
 Music, being a complex and fascinating art form, has been extensively studied by scholars and musicians for centuries.

### 2023-03-10 introduction/Subsections/Objectives.tex
Updates from Overleaf

@@
 
-As a professional music transcriber, I aim to understand how deep neural networks (DNNs) filter musical features, listen to the NN layers from a musician's perspective and analyze the resulting data.
+As a professional music transcriber myself, I aim to understand how deep neural networks (DNNs) filter musical features, listen to the NN layers from a musician's perspective and analyze the resulting data.
 I aim to approach the technology from a technical and musical standpoint to understand how DNNs process and extract musical information.

### 2023-03-10 methods/methods.tex
Updates from Overleaf

@@
 \section{Materials}
+\input{methods/subsections/model}
 
 \section{Convolutional Neural Network (CNN)}
-
-A CNN, or Convolutional Neural Network, is a deep-learning neural network. The architecture of a CNN is composed of several layers, including:
-
-\begin{itemize}
-
-\item Convolutional layers: These layers apply a convolution operation to the input data, effectively learning local patterns and features in the image.
-The raw audio data is typically transformed into a spectrogram or a Mel-spectrogram representation, which can be considered an image-like 2D representation of the audio data.
-The convolutional layers are designed to learn local patterns and features in the audio data
-\vspace*{3mm}
-
-\item Pooling layers: These layers downsample the data, reducing the spatial dimensions of the input while retaining important information.
-They can also be used to downsample the data and reduce the temporal dimensions of the input while retaining important information.
-\vspace*{3mm}
-
-\item Fully connected layers: These layers connect every neuron in one layer to every neuron in another layer, allowing the network to learn non-linear combinations of the features learned in the previous layers.
-\vspace*{3mm}
-
-\item Output layer: The output layer produces the final predictions of the network.
-\end{itemize}
-
-Compared to a traditional neural network, CNNs are more computationally efficient and have less number of parameters to train.
-This makes them more feasible for large-scale datasets and real-world problems.
-
-On top of that, one of the main advantages of using CNNs for audio analysis is that they can automatically and adaptively learn temporal hierarchies of features from audio data, which traditional audio processing methods may not be able to do effectively.
-
-\subsection{Neural Network (NN)}
-
-%Single
-\input{Figures/Figures CNN/Single Neuron}
-%NN
-\input{Figures/Figures CNN/Network_graph}
-
-%Backpropagation
-\input{Figures/Figures CNN/Multi-layer_NN}
-
-%CNN
-A high-level illustration of a simple convolutional neural network indicating convolutional layers, pooling layers, and fully-connected layers without details (number of channels or neurons per layer or the input image size) can be seen in XXX.
-\input{Figures/Figures CNN/CNN_diagram}
-
-%Single CNN
-\input{Figures/Figures CNN/Single_CNN}
-
-%Single pooling layer
-\input{Figures/Figures CNN/Single_Pooling_Layer}
-
-%Backpropagation
-\input{Figures/Figures CNN/Back_propagation}
-
+\input{methods/subsections/test}
 \newpage

### 2023-03-10 methods/subsections/model.tex
Updates from Overleaf

The Triplet Loss function is a function that measures the distance between an anchor, a positive sample, and a negative sample in a high-dimensional space. The formula for this function is given:

$$L = \max( ||f(x_{a}) - f(x_{p})||^{2} - ||f(x_{a}) - f(x_{n})||^{2} + \alpha, 0 )$$

where $f$ is a mapping function that transforms the input samples to a high-dimensional space, $x_{a}$ is the anchor sample, $x_{p}$ is the positive sample, $x_{n}$ is the negative sample, $\alpha$ is a margin hyperparameter that specifies the minimum difference between the distance of the anchor-positive pair and the anchor-negative pair, and $||\cdot||^{2}$ denotes the L2 norm squared.

### 2023-03-10 methods/subsections/test.tex
Updates from Overleaf

\chapter{Methods}

We propose the use of a triple siamese network to train a model for music similarity retrieval. Specifically, we aim to minimize the loss function between the anchor, positive, and negative samples by using online triplet mining.

The positive samples are created by transforming and augmenting the original samples while preserving their perceptual underlying musical language. This is achieved by using techniques such as time-stretching, pitch-shifting, and adding noise to the samples. By doing so, we aim to enhance the diversity of the positive samples and improve the model's ability to retrieve similar-sounding samples that share the same underlying musical language.

On the other hand, the negative samples are created by shuffling and scrambling the original samples while maintaining their production texture. This is achieved by using techniques such as random segment selection, time-domain filtering, and frequency-domain masking. The goal is to maintain the production texture of the samples while disrupting their underlying composition.

By using the proposed triple siamese network and online triplet mining, we aim to train a model that can effectively distinguish between similar and dissimilar samples while taking into account both their underlying composition and production texture.

\section{Materials}

\section{Convolutional Neural Network (CNN)}

A Convolutional Neural Network (CNN), is a deep-learning neural network. The architecture of a CNN is composed of several layers, including:

\begin{itemize}

\item Convolutional layers: These layers apply a convolution operation to the input data, effectively learning local patterns and features in the image. The raw audio data is typically transformed into a spectrogram or a Mel-spectrogram representation, which can be considered an image-like 2D representation of the audio data. The convolutional layers are designed to learn local patterns and features in the audio data
\vspace*{3mm}

\item Pooling layers: These layers downsample the data, reducing the spatial dimensions of the input while retaining important information. They can also be used to downsample the data and reduce the temporal dimensions of the input while retaining important information. 
\vspace*{3mm}

\item Fully connected layers: These layers connect every neuron in one layer to every neuron in another layer, allowing the network to learn non-linear combinations of the features learned in the previous layers.
\vspace*{3mm}

\item Output layer: The output layer produces the final predictions of the network.
\end{itemize}

Compared to a traditional neural network, CNNs are more computationally efficient and have less number of parameters to train. This makes them more feasible for large-scale datasets and real-world problems.

On top of that, one of the main advantages of using CNNs for audio analysis is that they can automatically and adaptively learn temporal hierarchies of features from audio data, which traditional audio processing methods may not be able to do effectively.

\subsection{Neural Network (NN)}

%Single
\input{Figures/Figures CNN/Single Neuron}
%NN
\input{Figures/Figures CNN/Network_graph}

%Backpropagation
\input{Figures/Figures CNN/Multi-layer_NN}

%CNN
A high-level illustration of a simple convolutional neural network indicating convolutional layers, pooling layers, and fully-connected layers without details (number of channels or neurons per layer or the input image size) can be seen in XXX.
\input{Figures/Figures CNN/CNN_diagram}

%Single CNN
\input{Figures/Figures CNN/Single_CNN}

%Single pooling layer
\input{Figures/Figures CNN/Single_Pooling_Layer}

%Backpropagation
\input{Figures/Figures CNN/Back_propagation}

\newpage

### 2023-03-10 music analysis/subsections/MSA.tex
Updates from Overleaf

--- 2023-03-04 music analysis/MSA.tex
@@
 MSA considers the interplay between technical and musical aspects, focusing on improving our understanding of music signals and the music itself.
-
-In the following section, we will examine the state of MSA, including its challenges and potential for future advancements.
-Topics such as data representation, computational complexity, and evaluation metrics will be discussed to provide a nuanced summary of the field.
-Additionally, we will consider the impact of new trends and technological advancements on MSA and the directions in which the field is likely to evolve.
-Through this examination, we aim to provide an overview of MSA's technical and musical aspects and its challenges.
 

### 2023-03-12 figures/Figures CNN/Back_propagation.tex
Updates from Overleaf

\begin{SCfigure}[2\sidecaptionrelwidth][h]
	\centering
	\begin{tikzpicture}[shorten >=1pt]
      		\tikzstyle{unit}=[draw,shape=circle,minimum size =1.4cm]

       	\node[unit](i) at (0,1){$y_i^{(l)}$};
        	\node[unit](k1) at (3,2){$y_1^{(l+1)}$};
		\node at (3, 1){$\vdots$};
		\node[unit](km) at (3,-0.25){$y_{m^{(l+1)}}^{(l+1)}$};

		\node at (1.25,2.25){$\delta_1^{(l+1)}$};
		\node at (1.25,-0.5){$\delta_{m^{(l+1)}}^{(l+1)}$};

        	\draw[->] (i) -- (k1);
		\draw[->] (i) -- (km);

		\draw[->,red,line width=0.05cm] (2,-0.25) -- (0.75,0.3);
		\draw[->,red,line width=0.05cm] (2,2) -- (0.75,1.6);
    	\end{tikzpicture}
	\caption[Backpropagation of errors through the network.]{Once evaluated for all output units, the errors $\delta_i^{(L+1)}$ can be propagated backwards.}.
	\label{fig:error-backpropagation}
\end{SCfigure}

### 2023-03-12 figures/Figures CNN/Single_CNN.tex
Updates from Overleaf

--- 2023-01-14 Figures/Figures CNN/Single_CNN.tex
@@
 	\begin{tikzpicture}
-		\node at (1.5,4){\begin{tabular}{c}input image\\or input feature map\end{tabular}};
+		\node at (1.5,4){\begin{tabular}{c}input data\\or input feature map\end{tabular}};
 
@@
 	\caption[Illustration of a convolutional layer.]{Illustration of a single convolutional layer.
-If layer $l$ is a convolutional layer, the input image (if $l = 1$) or a feature map of the previous layer is convolved by different filters to yield the output feature maps of layer $l$.}
+If layer $l$ is a convolutional layer, the input data (if $l = 1$) or a feature map of the previous layer is convolved by different filters to yield the output feature maps of layer $l$.}
 	\label{fig:convolutional-layer}

### 2023-03-12 introduction/Subsections/Introduction.tex
Updates from Overleaf

--- 2023-03-04 introduction/Subsections/Introduction.tex
@@
 
-The purpose of this work is to generalize the fundamental harmonic structure of music to facilitate its application in downstream tasks.
-Music, being a complex and fascinating art form, has been extensively studied by scholars and musicians for centuries.
-Understanding how music is organized and composed is critical, and music theory plays a vital role in this regard.
-Analyzing music structure poses a significant challenge as it comprises several elements, including melody, harmony, rhythm, and form.
+Music is an essential part of human culture, history, and society.
+It has existed in our lives since ancient times and has evolved, reflecting changes in our cultures, traditions, and beliefs.
+Despite its importance, the study of music has always been a challenging and complex task due to its subjective nature and the vast array of musical styles, genres, and cultures that exist worldwide.
 
-In recent years, the utilization of neural networks has made it possible to create low-dimensional musical embeddings that capture crucial musical features and enable the computation of semantic similarity between musical passages.
-By acquiring an embedding function $f(x) \in \mathbb{R}^d$ that maps a given passage $x$ to a vector in the real space $\mathbb{R}^d$, researchers can measure the semantic similarity between two musical passages using the Euclidean distance, as represented by the formula $D_{i,j} = ||f(x_i) - f(x_j)||^2$.
-The effectiveness of such systems depends on the embedding space's ability to interpret music in a way that aligns with human perception.
-Therefore, a suitable embedding space is crucial to ensure that the output aligns with human expectations.
+Humanity has been studying music to understand its underlying structure for millennia.
+From the ancient Greeks, who believed that music had a mathematical and cosmic harmony, to the early works of theorists such as Rameau, Fux, and Schenker, and more recent approaches such as generative theory and corpus studies, music has been a subject of fascination and inquiry.
+This rich music theory and analysis history provides a valuable foundation for guiding and evaluating MIR algorithms and models.
 
-The thesis under discussion explores the various musical elements that constitute music structure analysis, which includes melody, harmony, rhythm, and form.
-Aural skills are required to comprehend musical works through listening, as they involve perceptual and cognitive abilities.
-The underlying musical structure refers to the systematic arrangement of musical elements that results in a coherent and expressive musical work.
+We all humbly seek to unlock the secrets of music's complex and multifaceted nature.
 
-To provide a comprehensive analysis of musical works from diverse styles and genres, the thesis employs computational techniques from MIR and incorporates a musicological perspective to contextualize the findings.
-The objective is to offer fresh insights into these components of musical composition and advance our understanding of their relationships.
+Music Information Retrieval (MIR) is a research area that has emerged in the last decades as an interdisciplinary field combining engineering, musicology, and neuroscience.
+MIR aims to develop algorithms and techniques to automatically analyze, classify, and retrieve musical information from audio signals.
+In my opinion, MIR research has been traditionally focused on technical aspects, such as digital signal processing (DSP), machine learning, and pattern recognition, neglecting other relevant domains, such as perception, cognition, music theory, aural skills, and musicology.
 
-The study investigates the correlation between MSA, aural skills, and the underlying musical structure in musical composition.
-Through this research, the thesis aims to provide a better understanding of musical composition components, their relationships, and their practical applications.
+The reason behind this is non-other but the high implementation complexity for such heuristics and abstract fields of study.
+
+Let's pick a core MSA task as a sample to display such complexity: Music Structure Analysis (MSA) is an interdisciplinary field that aims to understand the structure of music.
+However, due to subjectivity, ambiguity, and data scarcity, audio-based MSA faces challenges such as boundary placement ambiguity and similarity quantification.
+The main principles of MSA were initially defined as homogeneity, novelty, and repetition, with the addition of regularity.
+
+The checkerboard kernel technique is a simple and effective method for Music Structure Analysis (MSA) based on the homogeneity principle.
+The kernel, with a checkerboard-like structure, is convolved over the main diagonal of a Self-Similarity Matrix (SSM) such as $S_{ij}$ is the similarity between time frames $i$ and $j$, $\vec{x}_i$ is the vector representation of time frame $i$, and $\left| \vec{x}_i \right|$ is the Euclidean norm of vector $\vec{x}_i$.
+The dot product of two vectors $\vec{x}_i$ and $\vec{x}_j$ is denoted by $\vec{x}_i \cdot \vec{x}_j$.
+
+\input{introduction/subsections/equations/SSM equation}
+
+This yields a novelty curve that highlights sudden changes in the selected musical features (e.g.
+chroma, MFCCs, beat-synchronous features, onset and offset detection, and harmonic and percussive separation) from which to extract the segment boundaries.
+
+\input{introduction/subsections/equations/Novelty equation}
+
+Mathematical operations are used on predefined principles such as homogeneity and repetition to analyze a musical structure.
+It relies on analyzing features extracted from a musical signal and identifying peaks in a novelty curve to extract segment boundaries.
+In contrast, human aural skills rely on the perception and interpretation of music by human listeners based on cultural and academical background and can capture subtle nuances of musical structure, but those still are subjective and can vary across listeners.
+
+Combining technical tasks, aural skills, and music perception is challenging due to the complexity and subjectivity of musical perception, discrepancies between the features extracted by DSP techniques and the features perceived by humans, and the variability of musical signals and individual differences in musical perception.
+DSP techniques may not always reflect the way humans perceive music, and may not capture the subtle variations in timing or harmonic relationships that are critical to musical perception.
+Variability in musical signals due to instrumentation, genre, and performance style further complicates the development of DSP techniques that can be generalized to different musical contexts.

### 2023-03-12 introduction/Subsections/Objectives.tex
Updates from Overleaf

--- 2023-03-03 introduction/Subsections/Objectives.tex
@@
 
-As a professional music transcriber, I aim to understand how deep neural networks (DNNs) filter musical features, listen to the NN layers from a musician's perspective and analyze the resulting data.
-I aim to approach the technology from a technical and musical standpoint to understand how DNNs process and extract musical information.
-By doing so, I aim to enhance the accuracy and efficiency of the process and contribute to developing AI technology for music analysis.
-By combining my expertise in music with my -not fully developed- knowledge of DNNs, I hope to bring a unique perspective to the field and contribute to the advancement of music analysis.
+The purpose of this work is to generalize the fundamental harmonic structure of music to facilitate its application in downstream music information retrieval (MIR) tasks.
+Music, being a complex and fascinating art form, has been extensively studied by scholars and musicians for centuries.
+Understanding how music is organized and composed is critical, and music theory plays a vital role in this regard.
+Analyzing music structure poses a significant challenge as it comprises several elements, including melody, harmony, rhythm, and form.
+
+In recent years, the utilization of neural networks has made it possible to create low-dimensional musical embeddings that capture crucial musical features and enable the computation of semantic similarity between musical passages.
+By acquiring an embedding function $f(x) \in \mathbb{R}^d$ that maps a given passage $x$ to a vector in the real space $\mathbb{R}^d$, researchers can measure the semantic similarity between two musical passages using the Euclidean distance, as represented by the formula $D_{i,j} = ||f(x_i) - f(x_j)||^2$.
+The effectiveness of such systems depends on the embedding space's ability to interpret music in a way that aligns with human perception.
+Therefore, a suitable embedding space is crucial to ensure that the output aligns with human expectations.
+
+The thesis under discussion explores the various musical elements that constitute music structure analysis, which includes melody, harmony, rhythm, and form.
+Aural skills are required to comprehend musical works through listening, as they involve perceptual and cognitive abilities.
+The underlying musical structure refers to the systematic arrangement of musical elements that results in a coherent and expressive musical work.
+
+To provide a comprehensive analysis of musical works from diverse styles and genres, the thesis employs computational techniques from MIR and incorporates a musicological perspective to contextualize the findings.
+The objective is to offer fresh insights into these components of musical composition and advance our understanding of their relationships.
 
@@
 However, using the latest deep learning techniques, we aim to build a model that achieves good results for a specific task in the domain of music.
+
+We will argue that MIR research should shift from a purely technical-centered approach to a more balanced and comprehensive one that incorporates other relevant domains.
+
+The study investigates the correlation between XXX, aural skills, and the underlying musical structure in musical composition.
+Through this research, the thesis aims to provide a better understanding of musical composition components, their relationships, and their practical applications.

### 2023-03-12 introduction/subsections/equations/Novelty equation.tex
Updates from Overleaf

--- 2023-03-04 music analysis/Equations/Novelty equation.tex
@@
 
-Where:
-\begin{itemize}
-\item $N$ is the number of time frames.
-\item $S_{ij}$ is the similarity between time frames $i$ and $j$.
-\item $S_{ii}$ is the similarity between time frame $i$ and itself.
-\item $n_i$ is the novelty value for time frame $i$.
-\end{itemize}
+Where $N$ is the number of time frames, $S_{ij}$ is the similarity between time frames $i$ and $j$, $S_{ii}$ is the similarity between time frame $i$ and itself, and $n_i$ is the novelty value for time frame $i$.
 
-The numerator of the expression represents the sum of similarities between time frame $i$ and all other time frames, minus the average similarity across all time frames.
+The numerator of the expression represents the sum of similarities between time frame $i$ and all other time frames minus the average similarity across all time frames.
 The denominator of the expression is the standard deviation of the similarities, which is used to normalize the values to ensure that the novelty values are between -1 and 1.

### 2023-03-12 introduction/subsections/underlying language vs waveform.tex
Updates from Overleaf

At a high level, the underlying composition and the master recording represent different aspects of a musical work.

The underlying composition represents the musical and lyrical elements of the song in a fixed and notated form. It includes the melody, rhythm, and harmony of the song as well as the accompanying lyrics. The underlying composition is the intellectual property of the songwriters, composers, musicians, or publishers, who have exclusive rights to reproduce, distribute, and perform the work.

The master recording, on the other hand, is the tangible recording of the sound of the song. It captures the performance, production, and engineering aspects of the work. The master recording is the intellectual property of the performers, producers, or sound engineers, who have exclusive rights to reproduce, distribute, and prepare derivative works of the sound recording.

In essence, the underlying composition is a fixed and notated representation of the song's musical and lyrical elements, while the master recording is a tangible recording of the performance, production, and engineering aspects of the song. The underlying composition is owned by the songwriters, composers, musicians, or publishers, while the master recording is owned by the performers, producers, or sound engineers.

### 2023-03-12 task definition/aural skills.tex
Updates from Overleaf

--- 2023-03-10 music analysis/subsections/MSA.tex
@@
-\chapter{Music Structure Analysis (MSA)}
-
-MSA encompasses various aspects of music analysis, including algorithms, current practices, and trends in technology.
-This field aims to comprehensively understand music structure by applying musicological theories, principles, and signal processing algorithms.
-MSA considers the interplay between technical and musical aspects, focusing on improving our understanding of music signals and the music itself.
-
-\section{Concept definition}
-
-Musical structure and form refer to the organization and arrangement of musical elements in a piece of music. They describe how the music is put together and how it unfolds over time.
-
-Musical structure hierarchically arranges various elements of music, such as melody, harmony, rhythm, timbre, and texture\footnote{Musical texture refers to the arrangement and combination of musical elements, including melody, harmony, rhythm, timbre, and dynamics, in a piece of music.
-Different textures, such as monophonic, homophonic, polyphonic, and heterophonic, can affect a piece's overall character and mood.
-Understanding musical texture is vital for music analysis and appreciation.}.
-This hierarchy can take different forms, such as melody being the most critical element, harmony playing a supportive role, or rhythm being the driving force behind the music.
-The structure of a piece of music is often characterized by its elements' repetition, development, and variation.
-
-Music form, however, refers to the larger-scale organization of musical structure over time.
-It describes how music sections are repeated, varied, and put together to create a complete piece.
-Music form can be thought of as the plan or design that underlies a piece of music.
-Many forms are used in music, such as binary, ternary, rondo, sonata, and theme and variations.
-
-Musicologists and theorists have developed various analytical tools and methods for understanding musical structure and form, including Schenkerian analysis, set theory, and formal function analysis.
-These tools and methods help uncover the underlying musical relationships and patterns in a piece of music and provide a framework for understanding how it is put together and how it develops over time.
-
-\section{The music structure analysis problem}
-
-Audio-based Music Structural Analysis (MSA) identifies adjacent and non-overlapping musical segments in an audio signal and labels them based on similarity.
-Segments can occur at various time scales, from short motives to longer sections.
-Flat MSA focuses on non-hierarchical structures, while hierarchical MSA considers multiple time scales.
-However, MSA faces challenges such as boundary placement ambiguity and similarity quantification.
-Segments must be non-overlapping for a given hierarchical level, although some musicological approaches allow for overlap.
-
-\subsection{Problem definition}
-
-MSA challenges its definition due to subjectivity, ambiguity\footnote{Perception and interpretation of musical structure can vary widely between individuals and depend on factors such as personal background, cultural context, and individual preferences.
-This is due to the complex interplay between individual differences in perception and interpretation and how the auditory system processes sound.
-These factors highlight the importance of considering individual and cultural context in analyzing and interpreting musical structure.}, and data scarcity.
-A flat structural analysis of an audio signal consists of a set of contiguous, non-overlapping, and labeled time intervals that span the entire duration of the audio signal.
-Given a musical recording of T audio samples, a flat segmentation is defined by a set of segment boundaries B, a set of k unique labels Y, and a mapping of segment starting points to labels S.
-This leads to the label assignment L, which assigns a label to each time point.
-The segment boundaries are usually sampled at a rate of 10 Hz to achieve a balance between resolution and computational efficiency.
-
-As an art form, music is open to interpretation and can evoke different emotions and meanings in different listeners.
-This subjectivity makes it difficult to objectively analyze the structure of a piece of music, as different annotators may place boundaries between segments differently based on their perception and interpretation of the music.
-It can also have multiple structures, including hierarchical structures, that make it difficult to untangle the underlying structure.
-
-\subsection{Segmentation principles}
-The main principles of musical structure analysis (MSA) were initially defined as homogeneity, novelty, and repetition, with the addition of regularity later on.
-
-\subsubsection{Homogeneity and novelty}
-Homogeneity assumes that segments are homogeneous in musical attributes, with boundaries between distinct segments being points of novelty.
-
-\subsubsection{Repetition}
-Repetition assumes that segments with the same label are similar sequences, with boundaries defined by repeated sequences' start and endpoints.
-The structure of the music is represented using a self-similarity matrix to make its structure visually apparent.
-Homogeneous blocks may be challenging to subdivide, while repeated sequences appear as paths in the self-similarity matrix.
-MSA approaches focus on identifying these repeated sequences.
-
-\subsubsection{Regularity}
-The regularity principle in music structure analysis aims to exploit the regularities present in musical segments, such as the log-normally distributed length across the track and the tendency for the duration of two equally labeled segments to span an integer ratio of beats.
-
-\section{Common methods}
-
-To analyze the structure of a musical recording, a self-similarity matrix (SSM) is often used to visualize the degree of similarity between audio frames.
-The SSM results in a square matrix with the highest degree of similarity on the diagonal.
-
-It can be computed by representing the audio signal as a spectrogram (or any other suitable representation such as CQT or a Mel-spectrogram) and then calculating the similarity between all pairs of time frames in the spectrogram.
-
-One common approach is to use a dot product, where the similarity between two-time frames is equal to the dot product of their vectors. The dot product of two vectors x and y is given by:
-
-\input{music analysis/Equations/SSM equation}
-
-The resulting matrix will be symmetric, with the diagonal elements representing the similarity between a time frame and itself and the off-diagonal elements representing the similarity between two different time frames.
-
-It's also common to normalize the similarity values by dividing each entry by the Euclidean norm of the compared vectors to ensure that the self-similarity matrix has values between -1 and 1.
-
-Given a self-similarity matrix S, the novelty curve can be computed by taking the row-wise sum of the self-similarity matrix and normalizing the values.
-The novelty curve measures the deviation from the average similarity across time frames.
-
-\input{music analysis/Equations/Novelty equation}
-
-This representation is used for various tasks, such as identifying repeating patterns in the audio, detecting structural changes in the audio, or for music classification.
-
-The method of computing a novelty curve from a self-similarity matrix is widely used in Music Information Retrieval and audio analysis to assess the deviation from the average similarity of a given time frame in a music signal.
-It is primarily driven by Digital Signal Processing (DSP) and not necessarily motivated by musical considerations, yet it can be valuable in music segmentation, beat tracking, and structural analysis.
-However, the approach may be vulnerable to the choice of self-similarity measure used to calculate the matrix, and it may require further domain-specific knowledge and interpretation to extract practical information.
-Besides, the novelty curve could be limited in its ability to reflect musically meaningful events as it measures the deviation from the average similarity across time frames, rather than following musically motivated criteria.
-Therefore, the analysis and interpretation of the novelty curve may require additional caution to ensure its efficacy in capturing useful information about the music signal.
-
-\section{Musicological approach}
-\section{Topic overview}
-
-MSA has a long history, dating back to music theory and composition studies.
-In the 18th and 19th centuries, music theorists such as Rameau and Schenker developed analytical frameworks for understanding the structure of music in terms of harmony, melody, and form.
-
-\subsection{Heinrich Schenker}
-
-Heinrich Schenker was a prominent music theorist who developed \textit{Schenkerian Analysis}, a method for analyzing tonal music.
-This method is based on the concept of "the Ursatz," a fundamental structure of three levels: foreground, middle-ground, and background.
-Schenker's approach emphasizes the horizontal dimension of music, specifically melody, and the relationships between individual notes and the piece's overall structure.
-His ideas have significantly impacted the field of music theory and analysis, and the method is still widely used today.
-While the approach is primarily theoretical and relies on human interpretation, it can also be approached through computer algorithms such as CNNs; the results are not the same as human interpretation.
-
-The fundamental structure, also known as \textit{Ursatz}, represents the underlying structure of a tonal work at the most remote or background level, in the most abstract form.
-It comprises an essential elaboration of the tonic triad, including the entire line and accompanying bass arpeggiation.
-The fundamental structure, like the fundamental line, takes one of three forms, depending on which pitch of the tonic triad serves as the primary tone.
-For example, the key of C major would represent the fundamental structure by the fundamental descending line from scale degree 3.
-
-The \textit{Urlinie}, or fundamental line, unfolds the basic triad and presents tonality on horizontal paths.
-The tonal system also flows into this to bring a sense of purposeful order to chords by selecting harmonic degrees.
-Voice leading serves as the mediator between the horizontal formulation of tonality presented by the Urlinie and the vertical formulation presented by the harmonic degrees.
-
-The upper voice of the fundamental structure, represented by the whole line, utilizes a descending direction.
-In contrast, the lower voice, the bass arpeggiation through the fifth, takes an ascending direction (as shown in figure 1).
-The combination of the fundamental line and bass arpeggiation constitutes a unity, and neither can exist alone; it is only through their unification in a contrapuntal structure that they produce art.
-
-\subsection{Schenkerian analysis}
-
-Schenkerian analysis is a musical analysis method that examines tonal music using the theories of Heinrich Schenker.
-The purpose is to showcase the organic unity of a piece by highlighting the relationship between the foreground (all musical notes in the score) and the deep abstract structure known as the \textit{Ursatz}.
-The Ursatz, roughly the same for all tonal music, is then developed into a unique foreground in each work.
-The concept of tonal space, defined as the intervals between the notes of the tonic triad in the background, is crucial to the analysis.
-The tonal space is filled with passing and neighbor tones, creating new triads and tonal spaces for further elaboration.
-
-Schenkerian analysis uses specialized musical notation and is either presented in a generative manner, starting from the Ursatz and ending at the score, or in a reductive manner, starting from the score and reducing it to its fundamental structure.
-The Ursatz is presented in an arrhythmic graph, and rhythmic signs display hierarchical relationships between events.
-\footnote{In Schenkerian analysis, structural levels refer to the representation of a piece of music at different levels of abstraction.
-These levels typically include the foreground, middle ground, and background.
-Schenker posits that musical form, as represented through these structural levels, can be understood as an energy transformation, specifically the transformation of forces that flow from the background to the foreground through the various levels.}
-
-While complex and challenging, Schenkerian analysis is designed to reveal the internal coherence of a work, which ultimately lies in its tonality.
-The analysis's results may reflect the analyst's perceptions and intuitions.
-
 \subsection{Aural skills}

### 2023-03-12 introduction/Subsections/Motivation.tex
Updates from Overleaf

@@
 
+We argues that MIR research needs to incorporate a more balanced approach that considers the interdisciplinary nature of music and the importance of other domains beyond DSP.
+
 As a music lover, professional musician, and connoisseur, I am interested in gaining a deeper understanding of the fundamental building of musical composition, the various techniques used to create musical works, and capturing underlying relationships among them.
-I am deeply interested in learning how to retrieve embedded information within music.
-The study of music structure analysis provides a means to systematically analyze and understand musical pieces.
+I am deeply interested in learning how to retrieve embedded information within the music.
+The study of music structure analysis provides a means to analyze and understand musical pieces systematically.
 It has traditionally been approached through music theory, formal musical notation, musical analysis techniques, and machine learning, which I plan to blend.
@@
 
-As a professional musician and music transcriber, I am interested in understanding how Deep Neural Networks (DNNs) filter musical features.
-In other words, I am eager to learn how DNNs listen to music.
+As a professional musician and music transcriber, I want to understand how Deep Neural Networks (DNNs) filter musical features. In other words, I am eager to learn how DNNs listen to music.
 

### 2023-03-12 introduction/Subsections/Objectives.tex
Updates from Overleaf

@@
 
-The purpose of this work is to generalize the fundamental harmonic structure of music to facilitate its application in downstream music information retrieval (MIR) tasks.
-Music, being a complex and fascinating art form, has been extensively studied by scholars and musicians for centuries.
+This work aims to generalize the fundamental tonal-working structure of western-tradition music by learning and embedding space used to facilitate its application in downstream MIR tasks.
 Understanding how music is organized and composed is critical, and music theory plays a vital role in this regard.
-Analyzing music structure poses a significant challenge as it comprises several elements, including melody, harmony, rhythm, and form.
 
-In recent years, the utilization of neural networks has made it possible to create low-dimensional musical embeddings that capture crucial musical features and enable the computation of semantic similarity between musical passages.
+In recent years, the utilization of neural networks has made it possible to create low-dimensional musical embeddings that capture crucial musical features and enable the computation of content-based similarity between musical passages.
 By acquiring an embedding function $f(x) \in \mathbb{R}^d$ that maps a given passage $x$ to a vector in the real space $\mathbb{R}^d$, researchers can measure the semantic similarity between two musical passages using the Euclidean distance, as represented by the formula $D_{i,j} = ||f(x_i) - f(x_j)||^2$.

### 2023-03-12 MasterThesis.tex
Updates from Overleaf

@@
 %Title parameters
-\title{Capturing underlying musical structure: an audio-based approach using deep learning}
+\title{%
+  Uncovering underlying musical content in the temporal domain \\
+  \small Leveraging deep learning, inductive bias, and aural skills to learn embedding spaces from raw waveforms with applications to MIR downstream tasks}
+
 \author{\href{oriol.colome.font@epidemicsound.com}{Oriol Colomé Font}}
@@
 
-%\maketitle
 \restoregeometry
@@
 \input{introduction/introduction}
-%Music analysis explanation
-\input{music analysis/MSA}
+%Task definition
+%%\input{task definition}
 %Methods

### 2023-03-12 dedication/dedication.tex
Updates from Overleaf

%\addcontentsline{toc}{chapter}{Acknowledgement}
\begin{dedication}
\pagenumbering{gobble}% Remove page numbers (and reset to 1)
I dedicate this master's thesis to my closest family (Joaquim Colomé, Imma Font, Maria Colomé, and Ariadna Balasch), who has been my constant support and inspiration throughout this journey. Their unwavering love and encouragement have motivated me to pursue my academic goals, and their belief in me has never faltered. I am grateful for their patience, understanding, and sacrifices as I pursued my studies. Their presence in my life has made this journey meaningful, and this thesis is a tribute to their unwavering support. 
\newpage

\end{dedication}

### 2023-03-12 introduction/Subsections/Objectives.tex
Updates from Overleaf

--- 2023-03-10 introduction/Subsections/Objectives.tex
@@
 
-As a professional music transcriber myself, I aim to understand how deep neural networks (DNNs) filter musical features, listen to the NN layers from a musician's perspective and analyze the resulting data.
-I aim to approach the technology from a technical and musical standpoint to understand how DNNs process and extract musical information.
-By doing so, I aim to enhance the accuracy and efficiency of the process and contribute to developing AI technology for music analysis.
-By combining my expertise in music with my -not fully developed- knowledge of DNNs, I hope to bring a unique perspective to the field and contribute to the advancement of music analysis.
+This work aims to generalize the fundamental tonal-working structure of western-tradition music by learning and embedding space used to facilitate its application in downstream MIR tasks.
+Understanding how music is organized and composed is critical, and music theory plays a vital role.
 
-Music is a complex and multi-faceted phenomenon, and implementing a model that mimics human aural music skills is challenging.
-However, using the latest deep learning techniques, we aim to build a model that achieves good results for a specific task in the domain of music.
+In recent years, using neural networks has enabled low-dimensional musical embeddings that capture crucial musical features and allow the computation of content-based similarity between musical passages.
+By acquiring an embedding function $f(x) \in \mathbb{R}^d$ that maps a given course $x$ to a vector in the real space $\mathbb{R}^d$, we can measure the similarity between two musical passages using the Euclidean distance, as represented by the formula $D_{i,j} = ||f(x_i) - f(x_j)||^2$.
+The effectiveness of such systems depends on the embedding space's ability to interpret music in a way that aligns with human perception.
+Therefore, a suitable embedding space is crucial to ensure the output aligns with human expectations.
+
+This study aims to comprehensively analyze musical works from diverse styles and genres by incorporating computational techniques from Music Information Retrieval (MIR) and a musicological perspective to contextualize the findings.
+Aural skills are required to comprehend musical works through listening, as they involve perceptual and cognitive abilities.
+The underlying musical structure refers to the systematic arrangement of elements that produce a coherent and expressive musical work.
+This study aims to offer fresh insights into these components of musical composition and advance our understanding of their relationships.
+
+Music is a complex and multi-faceted phenomenon, and implementing a model mimicking human aural music skills is challenging.
+However, the latest deep learning techniques provide a promising avenue to build a model that achieves good results for a specific task in music.
+Therefore, this study will utilize deep learning techniques to investigate the correlation between aural skills and the underlying tonal-working structure of music.
+
+Furthermore, this study will argue that MIR research should shift from a purely technical-centered approach to a more balanced and comprehensive one incorporating other relevant domains such as musicology and music theory.
+By doing so, we can better understand the interplay between technical and musical aspects of music and improve our understanding of music signals and the music itself.

### 2023-03-15 introduction/Subsections/Introduction.tex
Updates from Overleaf

@@
 Music is an essential part of human culture, history, and society.
-It has existed in our lives since ancient times and has evolved, reflecting changes in our cultures, traditions, and beliefs.
+It has existed since ancient times and evolved, reflecting changes in our cultures, traditions, and beliefs.
 Despite its importance, the study of music has always been a challenging and complex task due to its subjective nature and the vast array of musical styles, genres, and cultures that exist worldwide.
@@
 From the ancient Greeks, who believed that music had a mathematical and cosmic harmony, to the early works of theorists such as Rameau, Fux, and Schenker, and more recent approaches such as generative theory and corpus studies, music has been a subject of fascination and inquiry.
-This rich music theory and analysis history provides a valuable foundation for guiding and evaluating MIR algorithms and models.
+This rich music theory and analysis history provide a valuable foundation for guiding and evaluating MIR algorithms and models.
 
@@
 The reason behind this is non-other but the high implementation complexity for such heuristics and abstract fields of study.
-
-Let's pick a core MSA task as a sample to display such complexity: Music Structure Analysis (MSA) is an interdisciplinary field that aims to understand the structure of music.
-However, due to subjectivity, ambiguity, and data scarcity, audio-based MSA faces challenges such as boundary placement ambiguity and similarity quantification.
-The main principles of MSA were initially defined as homogeneity, novelty, and repetition, with the addition of regularity.
-
-The checkerboard kernel technique is a simple and effective method for Music Structure Analysis (MSA) based on the homogeneity principle.
-The kernel, with a checkerboard-like structure, is convolved over the main diagonal of a Self-Similarity Matrix (SSM) such as $S_{ij}$ is the similarity between time frames $i$ and $j$, $\vec{x}_i$ is the vector representation of time frame $i$, and $\left| \vec{x}_i \right|$ is the Euclidean norm of vector $\vec{x}_i$.
-The dot product of two vectors $\vec{x}_i$ and $\vec{x}_j$ is denoted by $\vec{x}_i \cdot \vec{x}_j$.
-
-\input{introduction/subsections/equations/SSM equation}
-
-This yields a novelty curve that highlights sudden changes in the selected musical features (e.g.
-chroma, MFCCs, beat-synchronous features, onset and offset detection, and harmonic and percussive separation) from which to extract the segment boundaries.
-
-\input{introduction/subsections/equations/Novelty equation}
-
-Mathematical operations are used on predefined principles such as homogeneity and repetition to analyze a musical structure.
-It relies on analyzing features extracted from a musical signal and identifying peaks in a novelty curve to extract segment boundaries.
-In contrast, human aural skills rely on the perception and interpretation of music by human listeners based on cultural and academical background and can capture subtle nuances of musical structure, but those still are subjective and can vary across listeners.
-
-Combining technical tasks, aural skills, and music perception is challenging due to the complexity and subjectivity of musical perception, discrepancies between the features extracted by DSP techniques and the features perceived by humans, and the variability of musical signals and individual differences in musical perception.
-DSP techniques may not always reflect the way humans perceive music, and may not capture the subtle variations in timing or harmonic relationships that are critical to musical perception.
-Variability in musical signals due to instrumentation, genre, and performance style further complicates the development of DSP techniques that can be generalized to different musical contexts.

### 2023-03-15 introduction/Subsections/Motivation.tex
Updates from Overleaf

--- 2023-03-04 introduction/Subsections/Motivation.tex
@@
 
-As a music lover, professional musician, and connoisseur, I am interested in gaining a deeper understanding of the fundamental building of musical composition, the various techniques used to create musical works, and capturing underlying relationships among them.
+We argue that MIR research needs to incorporate a more balanced approach that considers the interdisciplinary nature of music and the importance of other domains beyond DSP.
+
+Let's pick a core MSA task as a sample to display such complexity: Music Structure Analysis (MSA) is an interdisciplinary field that aims to understand the structure of music.
+However, due to subjectivity, ambiguity, and data scarcity, audio-based MSA faces challenges like boundary placement ambiguity and similarity quantification.
+The main principles of MSA were initially defined as homogeneity, novelty, and repetition, with the addition of regularity.
+
+The checkerboard kernel technique is a simple and effective method for Music Structure Analysis (MSA) based on the homogeneity principle.
+The kernel, with a checkerboard-like structure, is convolved over the main diagonal of a Self-Similarity Matrix (SSM) such as $S_{ij}$ is the similarity between time frames $i$ and $j$, $\vec{x}_i$ is the vector representation of time frame $i$, and $\left| \vec{x}_i \right|$ is the Euclidean norm of vector $\vec{x}_i$.
+The dot product of two vectors $\vec{x}_i$ and $\vec{x}_j$ is denoted by $\vec{x}_i \cdot \vec{x}_j$.
+
+\input{introduction/subsections/equations/SSM equation}
+
+This yields a novelty curve that highlights sudden changes in the selected musical features (some examples would be chroma, MFCCs, beat-synchronous features, onset and offset detection, and harmonic and percussive separation) from which to extract the segment boundaries.
+
+\input{introduction/subsections/equations/Novelty equation}
+
+Mathematical operations are used on predefined principles such as homogeneity and repetition to analyze a musical structure.
+It analyzes features extracted from a musical signal and identifies peaks in a novelty curve to extract segment boundaries.
+In contrast, human aural skills rely on the perception and interpretation of music by human listeners based on cultural and academic background.
+They can capture subtle nuances of musical structure, but those still are subjective and can vary across listeners.
+
+Combining technical tasks, aural skills, and music perception is challenging due to the complexity and subjectivity of musical perception, discrepancies between the features extracted by DSP techniques and the features perceived by humans, and the variability of musical signals and individual differences in musical perception.
+DSP techniques may not always reflect how humans perceive music and may not capture the subtle variations in timing or harmonic relationships critical to musical perception.
+Variability in musical signals due to instrumentation, genre, and performance style further complicates the development of DSP techniques that can be generalized to different musical contexts.
+
+As a music lover, professional musician, and connoisseur, I am interested in gaining a deeper understanding of the fundamental building of musical composition, the various techniques used to create musical works, and capturing underlying relationships among them using DN.
+I am eager to learn how DNNs listen to music.
 I am deeply interested in learning how to retrieve embedded information within music.
-The study of music structure analysis provides a means to systematically analyze and understand musical pieces.
-It has traditionally been approached through music theory, formal musical notation, musical analysis techniques, and machine learning, which I plan to blend.
-
-With the advent of Artificial Intelligence (AI) and Machine Learning (ML), Music Information Retrieval (MIR) has expanded to encompass musically motivated neural network architectures.
-These networks are designed to incorporate musical concepts and perceptual approaches and use this knowledge to analyze and understand the structure of musical pieces in a way that goes beyond traditional music analysis techniques.
-
-As a professional musician and music transcriber, I am interested in understanding how Deep Neural Networks (DNNs) filter musical features.
-In other words, I am eager to learn how DNNs listen to music.
-
-By studying music structure analysis using musically motivated neural networks, we will gain an in-depth understanding of the latest advancements in the field and how these techniques are being used to revolutionize our understanding of music.
-Additionally, we will be able to contribute to developing new and innovative methods for musical analysis.

### 2023-03-15 introduction/Subsections/Objectives.tex
Updates from Overleaf

@@
 \section{Objectives}
+
+With the advent of Machine Learning (ML), MIR has expanded to encompass musically motivated neural network architectures.
+These networks are designed to incorporate musical concepts and perceptual approaches and use this knowledge to analyze and understand the structure of musical pieces in a way that goes beyond traditional music analysis techniques.
+
+By studying music structure analysis using musically motivated neural networks, we will gain an in-depth understanding of the latest advancements in the field and how these techniques are being used to revolutionize our understanding of music.
+Additionally, we will be able to contribute to developing new and innovative methods for musical analysis.
 

### 2023-03-15 introduction/subsections/underlying language vs waveform.tex
Updates from Overleaf

@@
 
-The underlying composition represents the musical and lyrical elements of the song in a fixed and notated form.
-It includes the melody, rhythm, and harmony of the song as well as the accompanying lyrics.
-The underlying composition is the intellectual property of the songwriters, composers, musicians, or publishers, who have exclusive rights to reproduce, distribute, and perform the work.
+The underlying composition represents the musical and lyrical elements of the song in a fixed, heuristic, and possibly notated form.
+It includes the melody, rhythm, harmony of the song, and accompanying lyrics, if any.
+In the lawsuit domain, the underlying composition is the intellectual property of the songwriters, composers, musicians, or publishers, who have exclusive rights to reproduce, distribute, and perform the work.
 
-The master recording, on the other hand, is the tangible recording of the sound of the song.
+The master recording, on the other hand, is the tangible recording of the song's sound.
 It captures the performance, production, and engineering aspects of the work.
@@
 
-In essence, the underlying composition is a fixed and notated representation of the song's musical and lyrical elements, while the master recording is a tangible recording of the performance, production, and engineering aspects of the song.
+The underlying composition is a fixed and notated representation of the song's musical and lyrical elements.
+At the same time, the master recording is a tangible recording of the song's performance, production, and engineering aspects.
 The underlying composition is owned by the songwriters, composers, musicians, or publishers, while the master recording is owned by the performers, producers, or sound engineers.

### 2023-03-15 methods/subsections/test.tex
Updates from Overleaf

@@
 %Single
-\input{Figures/Figures CNN/Single Neuron}
+\input{figures/Figures CNN/Single Neuron}
 %NN
-\input{Figures/Figures CNN/Network_graph}
+\input{figures/Figures CNN/Network_graph}
 
 %Backpropagation
-\input{Figures/Figures CNN/Multi-layer_NN}
+\input{figures/Figures CNN/Multi-layer_NN}
 
 %CNN
-A high-level illustration of a simple convolutional neural network indicating convolutional layers, pooling layers, and fully-connected layers without details (number of channels or neurons per layer or the input image size) can be seen in XXX.
-\input{Figures/Figures CNN/CNN_diagram}
+A high-level illustration of a simple convolutional neural network indicating convolutional layers, pooling layers, and fully-connected layers without details on the number of channels or neurons per layer or the input data size can be seen in XXX.
+\input{figures/Figures CNN/CNN_diagram}
 
 %Single CNN
-\input{Figures/Figures CNN/Single_CNN}
+\input{figures/Figures CNN/Single_CNN}
 
 %Single pooling layer
-\input{Figures/Figures CNN/Single_Pooling_Layer}
+\input{figures/Figures CNN/Single_Pooling_Layer}
 
 %Backpropagation
-\input{Figures/Figures CNN/Back_propagation}
+\input{figures/Figures CNN/Back_propagation}
 

### 2023-03-16 methods/subsections/model.tex
Updates from Overleaf

@@
+SSL, or self-supervised learning, is a technique to learn latent representations from large-scale data without relying on human annotations.
+Instead, it solves pretext tasks by creating different views of an object that are highly correlated.
+An SSL model is then trained to generalize objects' representations in a latent high-dimensional space.
+To achieve this, the model contrasts the representations of the same object with other objects (defined as negative samples) during training.
+By doing so, a contrastive SSL model is expected to produce more distinctive representations.
+
 The Triplet Loss function is a function that measures the distance between an anchor, a positive sample, and a negative sample in a high-dimensional space. The formula for this function is given:

### 2023-03-16 introduction/Subsections/Objectives.tex
Updates from Overleaf

@@
 
+Let's denote the single embedding for a music piece as $e(M)$.
+
+Given a music piece $M$, we aim to learn a single embedding, $e(M)$, simultaneously capturing the underlying content (melody, harmony, and critical, holistic elements) and the production aspects.
+The embedding space should be structured so that similar content and production features are clustered together, effectively isolating the two aspects.
+Formally, our objective is to learn the embedding function $e(M)$ such that:
+
+\begin{itemize}
+  \item Similar content features are closer in the embedding space: $\|e(M_1) - e(M_2)\| < \epsilon_c$ for music pieces $M_1$ and $M_2$ with similar content.
+  \item Similar production features are closer in the embedding space: $\|e(M_1) - e(M_3)\| < \epsilon_p$ for music pieces $M_1$ and $M_3$ with similar production.
+  \item Distinct content and production features are further apart in the embedding space.
+\end{itemize}
+
+We describe learning a single embedding $e(M)$ that captures content and production features.
+The embedding space is structured to cluster similar content and production features together, effectively isolating the two aspects.
+
 Music is a complex and multi-faceted phenomenon, and implementing a model mimicking human aural music skills is challenging.

### 2023-03-16 methods/subsections/model.tex
Updates from Overleaf

@@
 
-The Triplet Loss function is a function that measures the distance between an anchor, a positive sample, and a negative sample in a high-dimensional space. The formula for this function is given:
+TRIPLET LOSS
 
-$$L = \max( ||f(x_{a}) - f(x_{p})||^{2} - ||f(x_{a}) - f(x_{n})||^{2} + \alpha, 0 )$$
+ implements the triplet loss function, which is commonly used for learning embeddings in metric learning problems.
+The triplet loss aims to ensure that the distance between an anchor and a positive sample (both from the same class) is smaller than the distance between the anchor and a negative sample (from a different class) by a margin.
 
-where $f$ is a mapping function that transforms the input samples to a high-dimensional space, $x_{a}$ is the anchor sample, $x_{p}$ is the positive sample, $x_{n}$ is the negative sample, $\alpha$ is a margin hyperparameter that specifies the minimum difference between the distance of the anchor-positive pair and the anchor-negative pair, and $||\cdot||^{2}$ denotes the L2 norm squared.
+$\mathcal{L} = \frac{1}{N}\sum_{i=1}^{N} \max \left( d\left(a_i, p_i\right) - d\left(a_i, n_i\right) + m, 0 \right)$
+
+In this equation:
+
+$N$ is the number of triplets in the batch
+$a_i$ is the $i$-th anchor
+$p_i$ is the $i$-th positive sample
+$n_i$ is the $i$-th negative sample
+$d(\cdot, \cdot)$ is the Euclidean distance function
+$m$ is the margin; in this case, it is set to 0.2 by default
+The forward method computes the triplet loss as follows:
+
+Calculate the pairwise Euclidean distance between the anchor and positive samples, denoted as $d(a_i, p_i)$.
+Calculate the pairwise Euclidean distance between the anchor and negative samples, denoted as $d(a_i, n_i)$.
+Compute the loss for each triplet in the batch by subtracting the negative distance from the positive distance and adding the margin: $d(a_i, p_i) - d(a_i, n_i) + m$.
+Apply the ReLU function, which is equivalent to taking the maximum value between the computed value and 0: $\max \left( d(a_i, p_i) - d(a_i, n_i) + m, 0 \right)$.
+Calculate the mean of the losses across all triplets in the batch.

### 2023-03-16 methods/subsections/test.tex
Updates from Overleaf

@@
 
-We propose the use of a triple siamese network to train a model for music similarity retrieval.
+We propose using a triple siamese network to train a model for music similarity retrieval.
 Specifically, we aim to minimize the loss function between the anchor, positive, and negative samples by using online triplet mining.
@@
 The positive samples are created by transforming and augmenting the original samples while preserving their perceptual underlying musical language.
-This is achieved by using techniques such as time-stretching, pitch-shifting, and adding noise to the samples.
+This is achieved using techniques such as time-stretching, pitch-shifting, and adding noise to the samples.
 By doing so, we aim to enhance the diversity of the positive samples and improve the model's ability to retrieve similar-sounding samples that share the same underlying musical language.
@@
 On the other hand, the negative samples are created by shuffling and scrambling the original samples while maintaining their production texture.
-This is achieved by using techniques such as random segment selection, time-domain filtering, and frequency-domain masking.
+This is achieved using techniques such as random segment selection, time-domain filtering, and frequency-domain masking.
 The goal is to maintain the production texture of the samples while disrupting their underlying composition.
 
-By using the proposed triple siamese network and online triplet mining, we aim to train a model that can effectively distinguish between similar and dissimilar samples while taking into account both their underlying composition and production texture.
+Using the proposed triple siamese network and online triplet mining, we aim to train a model that can effectively distinguish between similar and dissimilar samples while considering their underlying composition and production texture.
 
@@
 
-\item Fully connected layers: These layers connect every neuron in one layer to every neuron in another layer, allowing the network to learn non-linear combinations of the features learned in the previous layers.
+\item Fully connected layers: These layers connect every neuron in one layer to every neuron in another, allowing the network to learn non-linear combinations of the features learned in the previous layers.
 \vspace*{3mm}
@@
 
-On top of that, one of the main advantages of using CNNs for audio analysis is that they can automatically and adaptively learn temporal hierarchies of features from audio data, which traditional audio processing methods may not be able to do effectively.
+On top of that, one of the main advantages of using CNNs for audio analysis is that they can automatically and adaptively learn temporal hierarchies of features from audio data, which traditional audio processing methods may not do effectively.
 

### 2023-03-16 introduction/Subsections/Introduction.tex
Updates from Overleaf

@@
 The reason behind this is non-other but the high implementation complexity for such heuristics and abstract fields of study.
+
+%%%%%%%%%%%%%%%%%%
+
+\begin{figure}[!ht]
+\includegraphics[clip,width=\columnwidth]{figures/schenkerian analysis/SchubertOp4no3.png}% 
+\caption{Small excerpt of \textit{Wandrers Nachtlied, Op. 4, D. 224} by Franz Schubert. We can see the passage's original score and the schenkerian unfolding.}
+\label{fig:timeseries}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[clip,width=\columnwidth]{figures/schenkerian analysis/schubert.png}% 
+\caption{\textit{Wandrers Nachtlied, Op. 4, D. 224} by Franz Schubert as performed by Dietrich Fischer-Dieskau and Jörg Demus}
+\label{fig:timeseries}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[clip,width=\columnwidth]{figures/schenkerian analysis/subert redu.png}% 
+\caption{\textit{Wandrers Nachtlied, Op. 4, D. 224} by Franz Schubert (Schenkerian reduction or unfolding)}
+\label{fig:timeseries}
+\end{figure}

### 2023-03-16 methods/subsections/test.tex
Updates from Overleaf

@@
 On the other hand, the negative samples are created by shuffling and scrambling the original samples while maintaining their production texture.
-This is achieved using techniques such as random segment selection, time-domain filtering, and frequency-domain masking.
+This is achieved using random segment selection, time-domain filtering, and frequency-domain masking.
 The goal is to maintain the production texture of the samples while disrupting their underlying composition.
@@
 %Single
-\input{figures/Figures CNN/Single Neuron}
+\input{figures/cnn/Single Neuron}
 %NN
-\input{figures/Figures CNN/Network_graph}
+\input{figures/cnn/Network_graph}
 
 %Backpropagation
-\input{figures/Figures CNN/Multi-layer_NN}
+\input{figures/cnn/Multi-layer_NN}
 
@@
 A high-level illustration of a simple convolutional neural network indicating convolutional layers, pooling layers, and fully-connected layers without details on the number of channels or neurons per layer or the input data size can be seen in XXX.
-\input{figures/Figures CNN/CNN_diagram}
+\input{figures/cnn/CNN_diagram}
 
 %Single CNN
-\input{figures/Figures CNN/Single_CNN}
+\input{figures/cnn/Single_CNN}
 
 %Single pooling layer
-\input{figures/Figures CNN/Single_Pooling_Layer}
+\input{figures/cnn/Single_Pooling_Layer}
 
 %Backpropagation
-\input{figures/Figures CNN/Back_propagation}
+\input{figures/cnn/Back_propagation}
 

### 2023-03-16 results/results.tex
Updates from Overleaf

--- 2023-01-14 results/results.tex
@@
 
-This is an example paragraph. As you can see, the main text uses a font size of 12 pt and a line spacing of 1.5. Neither the paragraphs nor the first lines of paragraphs should be indented.
-
-There is no very strict page limit.
-Your number of pages will be strongly influenced by the size and total number of your figures and tables.
-It is recommended staying within 30-50 pages.
-Do not try to fill as many pages as you can.
-Longer theses are not necessarily of higher quality and of more non-redundant content than shorter theses.
-Certainly, a master thesis of 15 pages is too short, and a master thesis of 100 pages is too long.
+XXXXXXXXXXXXXXXXX
 
@@
 
-This is an example paragraph. As you can see, the main text uses a font size of 12 pt and a line spacing of 1.5. Neither the paragraphs nor the first lines of paragraphs should be indented.
-
-There is no very strict page limit.
-Your number of pages will be strongly influenced by the size and total number of your figures and tables.
-It is recommended staying within 30-50 pages.
-Do not try to fill as many pages as you can.
-Longer theses are not necessarily of higher quality and of more non-redundant content than shorter theses.
-Certainly, a master thesis of 15 pages is too short, and a master thesis of 100 pages is too long.
+XXXXXXXXXXXXXXXXX
 
 \begin{figure}[!ht]
-\includegraphics[clip,width=\columnwidth]{Figures/PlotTimeSeriesResult}% 
+\includegraphics[clip,width=\columnwidth]{figures/PlotTimeSeriesResult}% 
 \caption{This is an example of a figure and its caption.}

### 2023-03-21 acknowledgements/acknowledgements.tex
Updates from Overleaf

@@
 \item Carlos Lordelo, and Carl Thomé for their invaluable guidance and support throughout my thesis.
-Your expertise in MIR helped shape the direction of my research and make it a success.
-Your unwavering support and encouragement helped me overcome any difficulties I encountered during the process.
+Your expertise in MIR, ML, and DSP helped shape the direction of my research and make it a success.
+Your unwavering support and encouragement helped me overcome any difficulties I encountered.
 I also appreciate the time and effort you invested in mentoring me.
 Your dedication to your students is truly inspiring, and I am honored to have had the opportunity to work with you.
+\vspace*{3mm}
+\item Cody Hesse and Sebastian Löf
+\vspace*{3mm}
+\item Epidemic Sound AB (\textit{Aktiebolag})
 \vspace*{3mm}

### 2023-03-21 introduction/Subsections/Objectives.tex
Updates from Overleaf

@@
 By doing so, we can better understand the interplay between technical and musical aspects of music and improve our understanding of music signals and the music itself.
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+%POTENTIAL APPLICATIONS
+%%%%%%%%%%%%%%%%%%%%%%%%%
+
+A self-supervised model that learns an embedding space to retrieve musical content from raw audio signals could have several potential applications and downstream tasks in Music Information Retrieval (MIR).
+Here are some examples:
+
+\begin{enumerate}
+\item Music recommendation: The learned embedding space can retrieve similar musical content and recommend songs or playlists to users based on their listening history or preferences.
+\item Music classification: The embedding space can classify songs based on genre, mood, or other musical characteristics.
+\item Music transcription: The learned embedding space can transcribe audio signals into symbolic music notation, such as MIDI or sheet music.
+\item Music generation: The embedding space can generate new musical content by sampling from the learned distribution of musical features.
+\item Music synchronization: The learned embedding space can synchronize audio and visual content in applications such as music videos or virtual reality experiences.
+\item Music search: The embedding space can search for specific musical content based on high-level perceptual concepts and the relationships they have among them
+\end{enumerate}

### 2023-03-21 introduction/subsections/underlying language vs waveform.tex
Updates from Overleaf

--- 2023-03-12 introduction/subsections/underlying language vs waveform.tex
@@
-At a high level, the underlying composition and the master recording represent different aspects of a musical work.
+The underlying composition and master recording represent distinct and essential aspects of a musical work.
+The underlying composition consists of the musical and lyrical elements of the song, including the melody, harmony, rhythm, and lyrics, which are fixed and notated forms of the musical work.
+The composition represents the intellectual property of the songwriters, composers, musicians, or publishers, who have exclusive rights to reproduce, distribute, and perform the work.
 
-The underlying composition represents the musical and lyrical elements of the song in a fixed and notated form.
-It includes the melody, rhythm, and harmony of the song as well as the accompanying lyrics.
-The underlying composition is the intellectual property of the songwriters, composers, musicians, or publishers, who have exclusive rights to reproduce, distribute, and perform the work.
+The master recording, on the other hand, is a tangible recording that captures the sound of the work's performance, production, and engineering aspects.
+The master recording is owned by the performers, producers, or sound engineers, who have exclusive rights to reproduce, distribute, and prepare derivative works of the sound recording.
 
-The master recording, on the other hand, is the tangible recording of the sound of the song.
-It captures the performance, production, and engineering aspects of the work.
-The master recording is the intellectual property of the performers, producers, or sound engineers, who have exclusive rights to reproduce, distribute, and prepare derivative works of the sound recording.
+In the scientific and technical realm, the underlying composition is considered a fixed, heuristic representation of the musical work, whereas the master recording represents the sound recording of the performance.
+The composition is typically notated, meaning the musical elements are represented by symbols representing specific pitches, rhythms, and chords.
+This notation provides a way to represent the musical work in a standardized form that can be read and interpreted by musicians and musicologists alike.
 
-In essence, the underlying composition is a fixed and notated representation of the song's musical and lyrical elements, while the master recording is a tangible recording of the performance, production, and engineering aspects of the song.
-The underlying composition is owned by the songwriters, composers, musicians, or publishers, while the master recording is owned by the performers, producers, or sound engineers.
+The master recording, on the other hand, is a physical recording that captures the sound of the work's performance, production, and engineering aspects.
+This recording represents a tangible artifact that can be played back and studied in detail to understand the nuances of the performance, such as the tempo, dynamics, and tonal quality.
+In addition, the master recording can be manipulated through various audio production techniques to create derivative works, such as remixes or cover versions of the original song.
+
+Overall, the underlying composition and master recording represent two essential aspects of a musical work, each with unique characteristics, properties, and ownership rights.
+The composition represents the fixed musical and lyrical elements of the work.
+It is owned by songwriters, composers, musicians, or publishers.
+At the same time, the master recording captures the performance and production aspects of the work and is owned by the performers, producers, or sound engineers.

### 2023-03-26 abstract/abstract.tex
Updates from Overleaf

@@
 \bigskip
-Keywords: Music; Music Theory; Music Information Retrieval; Music Structure Analysis; Machine Learning; Neural Networks; Deep Learning
+Keywords: Music; Music Theory; Music Information Retrieval; Music Structure Analysis; Machine Learning; Neural Networks; Deep Learning; Self-Supervised Learning; Music Similarity; Epidemic Sound
 

### 2023-03-26 introduction/Subsections/Introduction.tex
Updates from Overleaf

--- 2023-03-15 introduction/Subsections/Introduction.tex
@@
 Humanity has been studying music to understand its underlying structure for millennia.
-From the ancient Greeks, who believed that music had a mathematical and cosmic harmony, to the early works of theorists such as Rameau, Fux, and Schenker, and more recent approaches such as generative theory and corpus studies, music has been a subject of fascination and inquiry.
-This rich music theory and analysis history provide a valuable foundation for guiding and evaluating MIR algorithms and models.
+From the ancient Greeks to the early days, music has been a subject of fascination and inquiry.
+This rich music theory and analysis history provide a valuable foundation for guiding and evaluating Music Information Retrieval (MIR) algorithms and models.
 
@@
 
-Music Information Retrieval (MIR) is a research area that has emerged in the last decades as an interdisciplinary field combining engineering, musicology, and neuroscience.
-MIR aims to develop algorithms and techniques to automatically analyze, classify, and retrieve musical information from audio signals.
-In my opinion, MIR research has been traditionally focused on technical aspects, such as digital signal processing (DSP), machine learning, and pattern recognition, neglecting other relevant domains, such as perception, cognition, music theory, aural skills, and musicology.
+MIR is a research area that has emerged in the last decades as an interdisciplinary field combining engineering, musicology, and neuroscience.
+MIR aims to develop algorithms and techniques to automatically analyze, classify, and retrieve musical information from mainly audio signals.
+I believe that traditionally, MIR research has primarily concentrated on technical aspects, such as Digital Signal Processing (DSP), or pattern recognition.
+As a result, other relevant domains, including perception, cognition, music theory, aural skills, and musicology, along with its subfields, such as the symbolic domain, orchestration, and automatic transcription, have often been overlooked.
+However, it is worth noting that there has been a significant shift in this tendency recently.
 
-The reason behind this is non-other but the high implementation complexity for such heuristics and abstract fields of study.
+The reason behind this is non-other but the implementation complexity for such heuristics and abstract fields of study.
+
+With the advent of Machine Learning (ML), MIR has expanded to encompass musically motivated neural network architectures\cite{musicmotivCNN}.
+These networks are designed to incorporate musical concepts and perceptual approaches and use this knowledge to analyze and understand the structure of musical pieces in a way that goes beyond traditional music analysis techniques.

### 2023-03-26 introduction/Subsections/Motivation.tex
Updates from Overleaf

@@
 I am deeply interested in learning how to retrieve embedded information within music.
+
+\section{About aural skills and high-level perceptual}
+
+%%%%%%%%%%%%%%%%%%
+
+\begin{figure}[!ht]
+\includegraphics[clip,width=\columnwidth]{figures/schenkerian analysis/SchubertOp4no3.png}% 
+\caption{Small excerpt of \textit{Wandrers Nachtlied, Op.
+4, D.
+224} by Franz Schubert.
+We can see the passage's original score, the schenkerian unfolding of the melody, the chord degrees, and the tonal function.}
+\label{fig:timeseries}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+I have consistently been inspired by researchers who strive to uncover musical ground truth within the existing tonal paradigm, such as Heinrich Schenker\cite{}, or by challenging it, as exemplified by George Russell\cite{LydianRussell}.
+Both approaches aim to identify abstract concepts that reinforce or disrupt the tonal foundation.
+Their ultimate goal is to advance the tonal landscape, providing musicians with a dependable playground for growth and development.
+
+Schenkerian Analysis:
+Schenkerian Analysis, developed by Austrian music theorist Heinrich Schenker, analyzes tonal music focusing on its underlying structure.
+It seeks to reveal the hierarchical relationships between pitches, based on the premise that all tonal music has a fundamental structure known as the "Ursatz" or "basic shape." The Ursatz consists of a stepwise descending line (Urlinie) supported by a bass arpeggiation (Bassbrechung).
+Schenkerian Analysis reduces a musical composition to its essential elements, enabling the analyst to observe how the work's various layers contribute to the overall structure.
+It is worth mentioning that such analysis is done in the symbolic domain.
+
+George Russell's Lydian Chromatic Concept:
+George Russell's Lydian Chromatic Concept of Tonal Organization is an innovative approach to understanding and organizing musical relationships.
+Introduced in the 1950s, the theory asserts that the Lydian mode, rather than the traditional major scale, is the accurate parent scale in Western music.
+The Lydian scale is characterized by a raised fourth degree, giving it a brighter and more consonant sound.
+Russell's concept revolves around "chord modes," derived from a chord's parent Lydian scale.
+This system allows for greater harmonic flexibility and a broader range of tonal colors, influencing the development of jazz and contemporary music.

### 2023-03-26 introduction/Subsections/Objectives.tex
Updates from Overleaf

@@
 
-With the advent of Machine Learning (ML), MIR has expanded to encompass musically motivated neural network architectures.
-These networks are designed to incorporate musical concepts and perceptual approaches and use this knowledge to analyze and understand the structure of musical pieces in a way that goes beyond traditional music analysis techniques.
+This work aims to uncover a generalization of the fundamental tonal-working structure of western-tradition music by learning and embedding space used to facilitate its application in downstream MIR tasks.
 
-By studying music structure analysis using musically motivated neural networks, we will gain an in-depth understanding of the latest advancements in the field and how these techniques are being used to revolutionize our understanding of music.
-Additionally, we will be able to contribute to developing new and innovative methods for musical analysis.
-
-This work aims to generalize the fundamental tonal-working structure of western-tradition music by learning and embedding space used to facilitate its application in downstream MIR tasks.
 Understanding how music is organized and composed is critical, and music theory plays a vital role.

### 2023-03-28 methods/subsections/machine learning.tex
Updates from Overleaf

--- 2023-03-16 methods/subsections/test.tex
@@
-\chapter{Methods}
+Machine Learning (ML), particularly Deep Learning, has significantly advanced the Music Information Retrieval (MIR) field by enabling automatic feature learning, improving classification and analysis tasks, and facilitating novel applications like music generation and source separation.
+Adopting techniques like Convolutional Neural Networks (CNNs), Recurrent Neural Networks (RNNs), and generative models has led to better performance in tasks such as music classification, tagging, recommendation, transcription, synthesis, and analysis.
+As a result, ML has unlocked the potential of MIR, revolutionizing how we interact with, understand, and create music.
 
-We propose using a triple siamese network to train a model for music similarity retrieval.
-Specifically, we aim to minimize the loss function between the anchor, positive, and negative samples by using online triplet mining.
+\section{Artificial Neural Networks (ANNs)}
+A neural network, formally known as an artificial neural network (ANN), is a computational model inspired by the structure and functionality of biological neural networks.
+It is a mathematical framework designed to process information and perform tasks like pattern recognition, classification, and regression by mimicking how biological neurons and synapses operate.
+ANNs comprise interconnected layers of artificial neurons or nodes, each performing a mathematical transformation on the input data to generate an output.
+The connections between these neurons, often called "weights," are adjusted during learning to optimize the network's performance on a given task.
 
-The positive samples are created by transforming and augmenting the original samples while preserving their perceptual underlying musical language.
-This is achieved using techniques such as time-stretching, pitch-shifting, and adding noise to the samples.
-By doing so, we aim to enhance the diversity of the positive samples and improve the model's ability to retrieve similar-sounding samples that share the same underlying musical language.
+\subsection{About ANNs}
+The concept of neural networks can be traced back to the early 20th century, with the pioneering work of Warren McCulloch and Walter Pitts in 1943.
+They proposed a mathematical model of a neuron known as the McCulloch-Pitts neuron, which provided a foundation for future research in artificial intelligence.
+However, Frank Rosenblatt's invention of the perceptron in 1957 marked the beginning of modern neural networks.
+The perceptron is a single-layer neural network capable of learning linearly separable patterns.
 
-On the other hand, the negative samples are created by shuffling and scrambling the original samples while maintaining their production texture.
-This is achieved using random segment selection, time-domain filtering, and frequency-domain masking.
-The goal is to maintain the production texture of the samples while disrupting their underlying composition.
+In a more technical description, an ANN consists of an input layer, one or more hidden layers, and an output layer.
+Each neuron in a layer receives input from the previous layer and computes an output value using an activation function.
+Some standard activation functions include the sigmoid, hyperbolic tangent (tanh), and rectified linear unit (ReLU).
+The output of the last layer represents the prediction or classification result.
 
-Using the proposed triple siamese network and online triplet mining, we aim to train a model that can effectively distinguish between similar and dissimilar samples while considering their underlying composition and production texture.
-
-\section{Materials}
+%Single neuron
+\input{figures/neural networks/Single Neuron}
+%NN
+\input{figures/neural networks/Network_graph}
+%Multi-layer_NN
+\input{figures/neural networks/Multi-layer_NN}
+%Backpropagation
+\input{figures/neural networks/Back_propagation}
 
@@
 
-\subsection{Neural Network (NN)}
-
-%Single
-\input{figures/cnn/Single Neuron}
-%NN
-\input{figures/cnn/Network_graph}
-
-%Backpropagation
-\input{figures/cnn/Multi-layer_NN}
-
 %CNN
 A high-level illustration of a simple convolutional neural network indicating convolutional layers, pooling layers, and fully-connected layers without details on the number of channels or neurons per layer or the input data size can be seen in XXX.
-\input{figures/cnn/CNN_diagram}
+\input{figures/neural networks/CNN_diagram}
 
 %Single CNN
-\input{figures/cnn/Single_CNN}
+\input{figures/neural networks/Single_CNN}
 
 %Single pooling layer
-\input{figures/cnn/Single_Pooling_Layer}
-
-%Backpropagation
-\input{figures/cnn/Back_propagation}
+\input{figures/neural networks/Single_Pooling_Layer}
 

### 2023-03-28 methods/subsections/model architecture and training strategy.tex
Updates from Overleaf

--- 2023-03-16 methods/subsections/model.tex
@@
-SSL, or self-supervised learning, is a technique to learn latent representations from large-scale data without relying on human annotations.
+\section{Model architecture and training strategy}
+Self-Supervised Learning (SSL) is a technique to learn latent representations from large-scale data without relying on human annotations.
 Instead, it solves pretext tasks by creating different views of an object that are highly correlated.
@@
 
-TRIPLET LOSS
+\section{}
 
- implements the triplet loss function, which is commonly used for learning embeddings in metric learning problems.
+We propose using a Triple Siamese Network to train a model for music similarity retrieval.
+Specifically, we aim to minimize the loss function between the anchor, positive, and negative samples by using online triplet mining.
+
+The positive samples are created by transforming and augmenting the original samples while preserving their perceptual underlying musical language.
+This is achieved using techniques such as time-stretching, pitch-shifting, and adding noise to the samples.
+By doing so, we aim to enhance the diversity of the positive samples and improve the model's ability to retrieve similar-sounding samples that share the same underlying musical language.
+
+On the other hand, the negative samples are created by shuffling and scrambling the original samples while maintaining their production texture.
+This is achieved using random segment selection, time-domain filtering, and frequency-domain masking.
+The goal is to maintain the production texture of the samples while disrupting their underlying composition.
+
+Using the proposed triple siamese network and online triplet mining, we aim to train a model that can effectively distinguish between similar and dissimilar samples while considering their underlying composition and production texture.
+
+ Implements the triplet loss function, commonly used for learning embeddings in metric learning problems.
 The triplet loss aims to ensure that the distance between an anchor and a positive sample (both from the same class) is smaller than the distance between the anchor and a negative sample (from a different class) by a margin.

### 2023-03-28 figures/neural networks/Single_CNN.tex
Updates from Overleaf

--- 2023-03-12 figures/Figures CNN/Single_CNN.tex
@@
 	\end{tikzpicture}
-	\caption[Illustration of a convolutional layer.]{Illustration of a single convolutional layer.
-If layer $l$ is a convolutional layer, the input data (if $l = 1$) or a feature map of the previous layer is convolved by different filters to yield the output feature maps of layer $l$.}
+	\caption[Illustration of a 2D convolutional layer.]{Illustration of a 2D single convolutional layer.
+If layer $l$ is a convolutional layer, the input data (if $l = 1$) or a feature map of the previous layer is convolved by different filters (or kernels) to yield the output feature maps of layer $l$.}
 	\label{fig:convolutional-layer}

### 2023-03-28 introduction/Subsections/Introduction.tex
Updates from Overleaf

@@
 The reason behind this is non-other but the implementation complexity for such heuristics and abstract fields of study.
-
-With the advent of Machine Learning (ML), MIR has expanded to encompass musically motivated neural network architectures\cite{musicmotivCNN}.
-These networks are designed to incorporate musical concepts and perceptual approaches and use this knowledge to analyze and understand the structure of musical pieces in a way that goes beyond traditional music analysis techniques.

### 2023-03-28 introduction/Subsections/Motivation.tex
Updates from Overleaf

@@
 
-Let's pick a core MSA task as a sample to display such complexity: Music Structure Analysis (MSA) is an interdisciplinary field that aims to understand the structure of music.
+Let's pick a core MIR task as a sample to display such complexity: Music Structure Analysis (MSA), an interdisciplinary field that aims to understand the structure of music\cite{Nieto2020Audio-BasedApplications}.
 However, due to subjectivity, ambiguity, and data scarcity, audio-based MSA faces challenges like boundary placement ambiguity and similarity quantification.
@@
 We can see the passage's original score, the schenkerian unfolding of the melody, the chord degrees, and the tonal function.}
-\label{fig:timeseries}
+\label{fig:Wandrers Nachtlied, Op. 4, D. 224}
 \end{figure}

### 2023-03-28 introduction/Subsections/Objectives.tex
Updates from Overleaf

@@
 By acquiring an embedding function $f(x) \in \mathbb{R}^d$ that maps a given course $x$ to a vector in the real space $\mathbb{R}^d$, we can measure the similarity between two musical passages using the Euclidean distance, as represented by the formula $D_{i,j} = ||f(x_i) - f(x_j)||^2$.
-The effectiveness of such systems depends on the embedding space's ability to interpret music in a way that aligns with human perception.
+The effectiveness of such systems depends on the level of musical abstraction and the embedding space's ability to interpret music in a way that aligns with human perception.
 Therefore, a suitable embedding space is crucial to ensure the output aligns with human expectations.

### 2023-03-28 methods/subsections/machine learning.tex
Updates from Overleaf

@@
-Machine Learning (ML), particularly Deep Learning, has significantly advanced the Music Information Retrieval (MIR) field by enabling automatic feature learning, improving classification and analysis tasks, and facilitating novel applications like music generation and source separation.
-Adopting techniques like Convolutional Neural Networks (CNNs), Recurrent Neural Networks (RNNs), and generative models has led to better performance in tasks such as music classification, tagging, recommendation, transcription, synthesis, and analysis.
-As a result, ML has unlocked the potential of MIR, revolutionizing how we interact with, understand, and create music.
+\section{Introduction}
+Machine Learning (ML), and particularly Deep Learning, has significantly advanced the MIR field by enabling automatic feature learning, improving classification and analysis tasks, and facilitating novel applications like music generation and source separation.
+Adopting musically motivated neural network architectures \cite{musicmotivCNN} blends together musical concepts and perceptual approaches and use this knowledge to analyze and understand music in a way that goes beyond traditional music analysis techniques.
 
@@
 
+%Single neuron
+\input{figures/neural networks/Single Neuron}
+
 In a more technical description, an ANN consists of an input layer, one or more hidden layers, and an output layer.
@@
 
-%Single neuron
-\input{figures/neural networks/Single Neuron}
 %NN
 \input{figures/neural networks/Network_graph}
+
 %Multi-layer_NN
 \input{figures/neural networks/Multi-layer_NN}
+
+\section{Deep Learning (DL)}
+
 %Backpropagation
@@
 
-\section{Convolutional Neural Network (CNN)}
+\subsection{Convolutional Neural Network (CNN)}
 
@@
 
-\item Convolutional layers: These layers apply a convolution operation to the input data, effectively learning local patterns and features in the image.
-The raw audio data is typically transformed into a spectrogram or a Mel-spectrogram representation, which can be considered an image-like 2D representation of the audio data.
-The convolutional layers are designed to learn local patterns and features in the audio data
+\item \textbf{Convolutional layers:} These layers apply a convolution operation to the input data.
+The raw audio data can be either a 1D signal or transformed into a spectrogram or a Mel-spectrogram representation, which can be considered an image-like 2D representation of the audio data.
+The convolutional layers are designed to effectively learn local patterns and features in the audio data \footnote{For a visual explanation of convolution, see this video: \url{https://youtu.be/KuXjwB4LzSA}}.
+
+\textbf{1D Convolution Example:} Given a 1D input signal $I = [i_1, i_2, ..., i_n]$ and a filter (or kernel) $K = [k_1, k_2, ..., k_m]$, the convolution operation is defined as $(I * K)j = \sum{u=1}^{m} I_{j-u+1} K_u$, where $j$ ranges from $1$ to $n-m+1$, and $I * K$ represents the resulting feature vector after applying the convolution.
+The objective of the 1D convolution operation is to slide the filter over the input signal and compute the element-wise product and sum for each local region, effectively learning and detecting local patterns in the input data.
+
+\item \textbf{Pooling layers:} These layers downsample the data, reducing the spatial or temporal dimensions of the input while retaining important information.
+A common pooling operation is the max-pooling, which can be defined as follows: given an input matrix $I$ and a pooling window of size $m \times n$, the max-pooling operation selects the maximum value within each non-overlapping $m \times n$ region of the input matrix.
+This operation effectively reduces the input's dimensions while retaining the most important information in each region.
 \vspace*{3mm}
 
-\item Pooling layers: These layers downsample the data, reducing the spatial dimensions of the input while retaining important information.
-They can also be used to downsample the data and reduce the temporal dimensions of the input while retaining important information.
+\item \textbf{Fully connected layers:} These layers connect every neuron in one layer to every neuron in another, allowing the network to learn non-linear combinations of the features learned in the previous layers.
+Mathematically, a fully connected layer can be represented as $Y = XW + b$, where $X$ is the input matrix, $W$ is the weight matrix, $b$ is the bias vector, and $Y$ is the output matrix.
+The non-linearity is introduced through the activation function, which is applied element-wise to the output matrix, such as $Y' = f(Y)$, where $f$ represents the activation function and $Y'$ is the transformed output matrix.
 \vspace*{3mm}
 
-\item Fully connected layers: These layers connect every neuron in one layer to every neuron in another, allowing the network to learn non-linear combinations of the features learned in the previous layers.
-\vspace*{3mm}
+\item \textbf{Output layer:} The output layer produces the final predictions of the network.
 
-\item Output layer: The output layer produces the final predictions of the network.
 \end{itemize}
@@
 %CNN
-A high-level illustration of a simple convolutional neural network indicating convolutional layers, pooling layers, and fully-connected layers without details on the number of channels or neurons per layer or the input data size can be seen in XXX.
 \input{figures/neural networks/CNN_diagram}

### 2023-03-28 methods/subsections/model architecture and training strategy.tex
Updates from Overleaf

@@
 \section{Model architecture and training strategy}
-Self-Supervised Learning (SSL) is a technique to learn latent representations from large-scale data without relying on human annotations.
-Instead, it solves pretext tasks by creating different views of an object that are highly correlated.
-An SSL model is then trained to generalize objects' representations in a latent high-dimensional space.
+\section{Self-Supervised Learning (SSL)}
+Self-Supervised Learning (SSL) is a technique that leverages inductive bias to learn latent representations from large-scale data without relying on human annotations.
+By focusing on pretext tasks that create different, highly correlated views of an object, SSL models exploit the underlying structure and known variance in the data.
+
+An SSL model is trained to generalize objects' representations in a latent high-dimensional space.
 To achieve this, the model contrasts the representations of the same object with other objects (defined as negative samples) during training.
-By doing so, a contrastive SSL model is expected to produce more distinctive representations.
+By doing so, a contrastive SSL model is expected to produce more distinctive representations \cite{audioselfsupsurvey}.
+Several MIR fields, such as music genre classification, or music similarity (both in the symbolic \cite{musicviaselfsup} and time domain \cite{epidemic}), have taken advantage of SSL techniques to improve their performance and alleviate the need for large amounts of labeled data \cite{audioselfsupsurvey}.
+
+\subsubsection{Strengths}
+
+\begin{enumerate}
+    \item Reduces dependency on labeled data: SSL capitalizes on inductive bias to learn from large amounts of unlabeled data, which is particularly beneficial when obtaining labeled data is expensive or time-consuming.
+    \item Encourages feature extraction: SSL encourages learning useful features or representations from the data, which can lead to better generalization and improved performance on downstream tasks.
+    \item Transfer learning: SSL models can be fine-tuned for specific tasks with smaller labeled datasets, allowing for more efficient training and potentially better results.
+    \item Robustness: SSL models can learn robust features from noisy or incomplete data, improving their ability to handle real-world scenarios.
+\end{enumerate}
+
+\subsubsection{Flaws}
+
+\begin{enumerate}
+    \item Less interpretable: SSL models tend to be less interpretable than supervised models, as their learning mechanisms are less explicit and rely more on inductive bias.
+    \item Computational complexity: SSL models often require more training iterations and larger batch sizes, which can result in higher computational costs.
+    \item Sensitive to hyperparameters: SSL models can be sensitive to hyperparameters such as learning rate, batch size, and the choice of the contrastive loss function, which may require extensive tuning.
+    \item Limited applicability: SSL may not be suitable for all tasks or domains, as its performance depends on the quality and relevance of the self-supervised pretext tasks and the effectiveness of the inductive bias in capturing the known variance in the data.
+\end{enumerate}
+
+\subsection{Contrastive Learning of Musical Representations (CLMR)}
+
+Contrastive Learning of Musical Representations (CLMR) is a self-supervised learning technique that aims to learn discriminative representations of music by leveraging its structure and content without explicit labels \cite{CLMR2021}\cite{multisourceclmr2023}.
+The learning process involves creating different augmentations or transformations of the same musical piece as positive pairs and using other randomly selected pieces as antagonistic pairs.
+A neural network is then trained to minimize a contrastive loss function, which encourages the model to produce similar representations for positive pairs and dissimilar representations for opposing pairs.
+Once trained, these learned representations can be utilized for various MIR downstream tasks.
 
@@
 
-We propose using a Triple Siamese Network to train a model for music similarity retrieval.
+We propose using a Triple Siamese Network to train a model for music similarity retrieval \cite{contentmusicsimtriplet2020}.
 Specifically, we aim to minimize the loss function between the anchor, positive, and negative samples by using online triplet mining.

### 2023-03-28 preface/preface.tex
5-2-2023 commit
Updates from Overleaf

@@
-%\addcontentsline{toc}{chapter}{Acknowledgement}
+\addcontentsline{toc}{chapter}{Acknowledgement}
 \begin{preface}
 \pagenumbering{gobble}% Remove page numbers (and reset to 1)
-(Optional, if used placed on a right page next to an empty left page)
 
-I would like to dedicate this work to...
+Music and science have always been my two greatest passions.
+When the opportunity to work at Epidemic Sound presented itself, it was as if the universe had conspired to bring my interests together, offering me the chance to explore the fascinating Music Information Retrieval (MIR) field.
+With the support and encouragement of my loved ones, I took a leap of faith and moved to Stockholm to embark on this exciting journey.
+
+This work aims to help untangle the complexities of music and offer a more musically-driven perspective to MIR.
+I aim to contribute to a deeper understanding of the intricate relationships within musical data by bridging the gap between music theory and computational analysis.
+
+I am deeply grateful to the Epidemic Sound team for their guidance, expertise, and camaraderie throughout this project.
+I would also like to extend my heartfelt appreciation to my family for their unwavering support and belief in my abilities.
+
+My motivation for writing this piece stems from a desire to grow as a musician, programmer, professional, and individual.
+I believe that by delving into the world of MIR, I can expand my horizons while making a meaningful contribution to the field.
+
+This work is intended for any curious human being, regardless of their background in music or computer science.
+I hope it will inspire others to explore the captivating intersection of these two disciplines.
+
+The scope of this work encompasses a range of MIR tasks and methodologies, as well as discussions on the challenges and opportunities that arise within the field.
+Despite the ambitious nature of this project, I acknowledge that time and my academic background limitations may have constrained the depth of my analysis.
+Nevertheless, I hope this work will serve as a starting point for further exploration and inspire new ideas in the realm of MIR.
+
 \newpage
-
 \end{preface}

### 2023-03-29 introduction/Subsections/Introduction.tex
Updates from Overleaf

@@
 MIR aims to develop algorithms and techniques to automatically analyze, classify, and retrieve musical information from mainly audio signals.
-I believe that traditionally, MIR research has primarily concentrated on technical aspects, such as Digital Signal Processing (DSP), or pattern recognition.
-As a result, other relevant domains, including perception, cognition, music theory, aural skills, and musicology, along with its subfields, such as the symbolic domain, orchestration, and automatic transcription, have often been overlooked.
-However, it is worth noting that there has been a significant shift in this tendency recently.
+I believe that traditionally, MIR research has primarily concentrated on technical aspects, such as Digital Signal Processing (DSP) or pattern recognition.
+As a result, other relevant domains, including perception, cognition, music theory, aural skills, and musicology, along with its subfields, might have been overlooked.
+
+It is worth mentioning that there has been a significant shift in this tendency on retrieval tasks in the symbolic and musicological domain, such as powerful open-source analysis frameworks \cite{ScottCuthbertChristopherArizaMusic21:Data}, MIDI to proper sheet music syntax \cite{Suzuki2021ScoreRepresentation}, projective orchestration \cite{Crestel2018AOrchestration}, or automatic lead sheet generation \cite{WeilAutomaticSignals} to name a few.
 
 The reason behind this is non-other but the implementation complexity for such heuristics and abstract fields of study.
+Closing the gap between human perception, environmental and cultural factors, and computational solutions to mimic the formers is an already tackled topic \cite{Large1994ResonanceMeter}\cite{Mullensiefen2003MeasuringJudgments}\cite{Sears2014PerceivingCadence}\cite{Thaut2014HumanPatter}, yet remains a vast open challenge.

### 2023-03-29 introduction/Subsections/Motivation.tex
Updates from Overleaf

@@
 \section{Motivation}
+As a music lover, professional musician, and connoisseur, I am interested in gaining a deeper understanding of the fundamental building of musical composition, the various techniques used to create musical works, and capturing underlying relationships among them.
+I am deeply interested in learning how to retrieve useful embedded information within the music.
+
+\subsection{Beyond Digital Signal Processing (DSP)}
 
@@
 Let's pick a core MIR task as a sample to display such complexity: Music Structure Analysis (MSA), an interdisciplinary field that aims to understand the structure of music\cite{Nieto2020Audio-BasedApplications}.
-However, due to subjectivity, ambiguity, and data scarcity, audio-based MSA faces challenges like boundary placement ambiguity and similarity quantification.
+However, due to subjectivity, ambiguity, and data scarcity, audio-based MSA faces challenges like boundary placement ambiguity and similarity quantification \cite{NietoPerceptualMusic}.
 The main principles of MSA were initially defined as homogeneity, novelty, and repetition, with the addition of regularity.
@@
 
-As a music lover, professional musician, and connoisseur, I am interested in gaining a deeper understanding of the fundamental building of musical composition, the various techniques used to create musical works, and capturing underlying relationships among them using DN.
-I am eager to learn how DNNs listen to music.
-I am deeply interested in learning how to retrieve embedded information within music.
-
 \section{About aural skills and high-level perceptual}
@@
 
-\begin{figure}[!ht]
+\begin{figure}[h]
 \includegraphics[clip,width=\columnwidth]{figures/schenkerian analysis/SchubertOp4no3.png}% 
@@
 
+Schenkerian analysis is a method of analyzing tonal music, focusing on hierarchical relationships between musical elements.
+The theory is based on the ideas of Heinrich Schenker, who sought to show that free composition was an elaboration of strict composition, particularly two-voice counterpoint.
+Schenker's theory includes several key concepts:
+
+Prolongational levels: Hierarchically organized levels of elaboration, with each level representing a new freedom with respect to the rules of strict composition.
+Harmony: The basic component is the Stufe (scale degree), and Schenker's theory is monotonal, meaning that the work as a whole projects a single key.
+Counterpoint and voice-leading: Schenker emphasizes the importance of two-voice counterpoint and melodic fluency (stepwise motion) in both strict and free composition.
+Ursatz (fundamental structure): The underlying structure from which a work originates, consisting of a fundamental line (Urlinie) and bass arpeggiation (Bassbrechung).
+Schenkerian analysis is about showing how each work elaborates the background structure in a unique way, determining its identity and meaning.
+While the theory has been criticized for reducing all tonal works to a few background structures, Schenker argues that the focus is on individual elaboration.
+
 George Russell's Lydian Chromatic Concept:

### 2023-03-29 introduction/Subsections/Objectives.tex
Updates from Overleaf

@@
 This work aims to uncover a generalization of the fundamental tonal-working structure of western-tradition music by learning and embedding space used to facilitate its application in downstream MIR tasks.
-
 Understanding how music is organized and composed is critical, and music theory plays a vital role.
 
-In recent years, using neural networks has enabled low-dimensional musical embeddings that capture crucial musical features and allow the computation of content-based similarity between musical passages.
+In recent years, using neural networks has enabled low-dimensional musical embeddings that capture crucial musical features and allow the computation of content-based similarity between musical passages \cite{}.
 By acquiring an embedding function $f(x) \in \mathbb{R}^d$ that maps a given course $x$ to a vector in the real space $\mathbb{R}^d$, we can measure the similarity between two musical passages using the Euclidean distance, as represented by the formula $D_{i,j} = ||f(x_i) - f(x_j)||^2$.

### 2023-03-29 introduction/Subsections/Motivation.tex
Updates from Overleaf

--- 2023-03-28 introduction/Subsections/Motivation.tex
@@
 
-As a music lover, professional musician, and connoisseur, I am interested in gaining a deeper understanding of the fundamental building of musical composition, the various techniques used to create musical works, and capturing underlying relationships among them using DN.
-I am eager to learn how DNNs listen to music.
-I am deeply interested in learning how to retrieve embedded information within music.
+\section{About music aural skills and high-level perception}
 
-\section{About aural skills and high-level perceptual}
+I have consistently been inspired by musicians and researchers who strive to uncover musical ground truth within the existing tonal paradigm, such as Heinrich Schenker \cite{}, or by challenging it, as exemplified by George Russell \cite{LydianRussell}.
+Both approaches aim to identify abstract concepts that reinforce or disrupt the tonal foundation.
+Their ultimate goal is to advance the tonal landscape, providing musicians with a dependable playground for growth and development.
 
@@
 
-I have consistently been inspired by researchers who strive to uncover musical ground truth within the existing tonal paradigm, such as Heinrich Schenker\cite{}, or by challenging it, as exemplified by George Russell\cite{LydianRussell}.
-Both approaches aim to identify abstract concepts that reinforce or disrupt the tonal foundation.
-Their ultimate goal is to advance the tonal landscape, providing musicians with a dependable playground for growth and development.
+Schenkerian Analysis, devised by Austrian music theorist Heinrich Schenker, explores tonal music's underlying structure by concentrating on the hierarchical relationships between pitches.
+Based on the idea that all tonal music shares a fundamental structure called "Ursatz" or "basic shape," the method identifies the stepwise descending line (Urlinie) and bass arpeggiation (Bassbrechung).
+Schenkerian Analysis simplifies a musical piece to its core elements, allowing analysts to examine how different layers contribute to the overall structure.
+Key concepts include prolongational levels, harmony, counterpoint, voice-leading, and Ursatz (fundamental structure).
+Although criticized for reducing all tonal works to a few background structures, Schenker emphasizes the importance of individual elaboration in determining a work's identity and meaning.
 
-Schenkerian Analysis:
-Schenkerian Analysis, developed by Austrian music theorist Heinrich Schenker, analyzes tonal music focusing on its underlying structure.
-It seeks to reveal the hierarchical relationships between pitches, based on the premise that all tonal music has a fundamental structure known as the "Ursatz" or "basic shape." The Ursatz consists of a stepwise descending line (Urlinie) supported by a bass arpeggiation (Bassbrechung).
-Schenkerian Analysis reduces a musical composition to its essential elements, enabling the analyst to observe how the work's various layers contribute to the overall structure.
-It is worth mentioning that such analysis is done in the symbolic domain.
+Anstieg (Initial Ascent): Ascending motion leading to the primary tone of the fundamental line.
+Arpeggiation (Brechung): Elementary elaboration of a harmony.
+Background (Hintergrund): The structural level of the fundamental structure.
+Bass Arpeggiation (Bassbrechung): Bass pattern I-V-I forming the harmonic content of the background of tonal musical pieces.
+Chord of Nature (Klang): The complex sound consisting of the first five notes of the harmonic series, suggesting a model for the major triad.
+Diminution: The process by which an interval formed by notes of longer value is expressed in notes of smaller value.
+Foreground (Vordergrund): The surface level of musical structure in Schenkerian analysis.
+Fundamental Line (Urlinie): The melodic aspect of the fundamental structure, a stepwise descent from one of the triad notes to the tonic.
+Middleground (Mittelgrund): An intermediate structural level between the background and foreground in Schenkerian analysis.
+Prolongation (Auskomponierung): The process in tonal music through which a pitch, interval, or consonant triad is able to govern spans of music when not physically sounding.
+Structural Level (Schicht): Refers to the different levels of musical structure in Schenkerian analysis, including background, middleground, and foreground.
+Tonal Space: A general principle of Schenkerian analysis where intervals between the notes of the tonic triad form a tonal space that is filled with passing and neighbor notes.
+Unfolding (Ausfaltung): The transformation of a single chord into a horizontal succession.
+Voice Leading: The study of the principles that govern the progression of the component voices of a composition both separately and in combination.
+The glossary also includes related articles, references, and external links for further reading and understanding of Schenkerian analysis.
 
@@
 This system allows for greater harmonic flexibility and a broader range of tonal colors, influencing the development of jazz and contemporary music.
+
+\subsection{Assumptions}

### 2023-03-30 methods/subsections/model architecture and training strategy.tex
Updates from Overleaf

--- 2023-03-28 methods/subsections/model architecture and training strategy.tex
@@
 \section{Model architecture and training strategy}
-Self-Supervised Learning (SSL) is a technique to learn latent representations from large-scale data without relying on human annotations.
-Instead, it solves pretext tasks by creating different views of an object that are highly correlated.
-An SSL model is then trained to generalize objects' representations in a latent high-dimensional space.
-To achieve this, the model contrasts the representations of the same object with other objects (defined as negative samples) during training.
-By doing so, a contrastive SSL model is expected to produce more distinctive representations.
+\subsection{Contrastive Self-Supervised Learning for Musical Representations (CSSLMR)}
+
+Contrastive Self-Supervised Learning for Musical Representations (CSSLMR) is an approach that combines the principles of Self-Supervised Learning (SSL) and Contrastive Learning of Musical Representations (CLMR) to learn discriminative and valuable representations of music without relying on explicit labels.
+By leveraging the structure and content of music and contrasting different augmentations or transformations of the same musical piece against randomly (or not) selected pieces, CSSLMR models can effectively capture the underlying structure and known invariance in the data.
+
+The CSSL methodology involves the following steps:
+
+\textbf{Data Augmentation:} Create different augmentations or transformations of the same musical piece as positive pairs and use other randomly selected pieces as negative pairs.
+\textbf{Contrastive Learning:} Train a neural network to minimize a contrastive loss function, which encourages the model to produce similar representations for positive pairs and dissimilar representations for negative pairs.
+\textbf{Latent Representation:} Utilize the learned representations for various MIR downstream tasks, such as music genre classification or music similarity, both in the symbolic and time domains.
+\subsubsection{Strengths}
+
+CSSL inherits the strengths of both SSL and CLMR:
+
+\begin{enumerate}
+\item Reduces dependency on labeled data: By leveraging inductive bias and the structure of musical data, CSSL can learn from large amounts of unlabeled data.
+\item Encourages feature extraction: CSSL promotes learning useful and discriminative features or representations
+\end{enumerate}
 

### 2023-03-30 methods/subsections/model architecture and training strategy.tex
Updates from Overleaf

@@
 
-\textbf{Data Augmentation:} Create different augmentations or transformations of the same musical piece as positive pairs and use other randomly selected pieces as negative pairs.
-\textbf{Contrastive Learning:} Train a neural network to minimize a contrastive loss function, which encourages the model to produce similar representations for positive pairs and dissimilar representations for negative pairs.
-\textbf{Latent Representation:} Utilize the learned representations for various MIR downstream tasks, such as music genre classification or music similarity, both in the symbolic and time domains.
+\begin{enumerate}
+\item \textbf{Data Augmentation:} Create different augmentations or transformations of the same musical piece as positive pairs and use other randomly selected pieces as antagonistic pairs.
+\item \textbf{Contrastive Learning:} Train a neural network to minimize a contrastive loss function, which encourages the model to produce similar representations for positive pairs and dissimilar representations for antagonistic pairs.
+\item\textbf{Latent Representation:} Utilize the learned representations for various MIR downstream tasks, such as music genre classification or music similarity, both in the symbolic and time domains.
+\end{enumerate}
+
 \subsubsection{Strengths}
 
-CSSL inherits the strengths of both SSL and CLMR:
+CSSLMR inherits the strengths of both SSL and CLMR:
 
 \begin{enumerate}
-\item Reduces dependency on labeled data: By leveraging inductive bias and the structure of musical data, CSSL can learn from large amounts of unlabeled data.
-\item Encourages feature extraction: CSSL promotes learning useful and discriminative features or representations
+\item Reduces dependency on labeled data: by leveraging inductive bias (assuming a known invariance across the data samples), CSSL can learn from large amounts of unlabeled data.
+\item Encourages feature extraction: CSSLMR promotes learning useful and discriminative features or representations
 \end{enumerate}
 
-\section{}
+\section{Model architecture}
 
 We propose using a Triple Siamese Network to train a model for music similarity retrieval \cite{contentmusicsimtriplet2020}.
-Specifically, we aim to minimize the loss function between the anchor, positive, and negative samples by using online triplet mining.
+Specifically, we aim to minimize the loss function between the anchor, positive, and negative samples by using online triplet mining \cite{Sikaroudi2020OfflinePatches}.
 

### 2023-04-03 introduction/Subsections/Assumptions.tex
Updates from Overleaf

\section{Assumptions}

This thesis assumes that high-level musical concepts are agnostic and invariant to the unique tonal quality of the waveform, much like how a sheet music composition can be performed in a variety of ways using different instruments and styles while still retaining its musical essence.

We rely on a flexible and adaptable blueprint for musical expression, allowing performers to creatively interpret and express the same musical concepts in different ways.

Different waveforms can express the same musical concepts despite having distinct timbres or production styles, but it is crucial to distinguish between low-level and high-level musical features when analyzing or comparing different musical pieces. High-level features, such as melody, harmony, rhythm, tempo, form, and expression, are more abstract and can be recognized regardless of the specific waveform or production style used.

The thesis relies on the objective and comprehensive perspective on the musical content and meaning of a piece, much like reading sheet music can reveal the underlying musical structure and intention behind a piece of music.

One sheet music composition can be performed and recorded in a limitless variety of ways using different instruments, voices, tempos, and interpretations, resulting in an infinite number of valid waveforms that represent its musical content.

Conversely, the same waveform may have only a limited number of sheet music representations that accurately can capture its musical elements as per the current tradition and conventions. This is because the unique tonal quality of the waveform is strongly influenced by the specific instrument or production technology used to create it, making it difficult to transcribe its sonic properties into a precise sheet music notation. Moreover, this unique tonal quality is represented by high-level natural language concepts belonging to an old and rich cultural and sociological tradition.

### 2023-04-03 methods/subsections/machine learning.tex
Updates from Overleaf

@@
 \section{Introduction}
-Machine Learning (ML), and particularly Deep Learning, has significantly advanced the MIR field by enabling automatic feature learning, improving classification and analysis tasks, and facilitating novel applications like music generation and source separation.
-Adopting musically motivated neural network architectures \cite{musicmotivCNN} blends together musical concepts and perceptual approaches and use this knowledge to analyze and understand music in a way that goes beyond traditional music analysis techniques.
+Machine Learning (ML), particularly Deep Learning, has significantly advanced the MIR field by enabling automatic feature learning, improving classification and analysis tasks, and facilitating novel applications like music generation and source separation.
+Adopting musically motivated neural network architectures \cite{musicmotivCNN} blends musical concepts and perceptual approaches and use this knowledge to analyze and understand music in a way that goes beyond traditional music analysis techniques.
 
@@
 
-A Convolutional Neural Network (CNN), is a deep-learning neural network. The architecture of a CNN is composed of several layers, including:
+A Convolutional Neural Network (CNN) is a deep-learning neural network. The architecture of a CNN is composed of several layers, including:
 
@@
 \item \textbf{Pooling layers:} These layers downsample the data, reducing the spatial or temporal dimensions of the input while retaining important information.
-A common pooling operation is the max-pooling, which can be defined as follows: given an input matrix $I$ and a pooling window of size $m \times n$, the max-pooling operation selects the maximum value within each non-overlapping $m \times n$ region of the input matrix.
-This operation effectively reduces the input's dimensions while retaining the most important information in each region.
+A joint pooling operation is the max-pooling, which can be defined as follows: given an input matrix $I$ and a pooling window of size $m \times n$, the max-pooling operation selects the maximum value within each non-overlapping $m \times n$ region of the input matrix.
+This operation effectively reduces the input's dimensions while retaining the most essential information in each region.
 \vspace*{3mm}
@@
 Mathematically, a fully connected layer can be represented as $Y = XW + b$, where $X$ is the input matrix, $W$ is the weight matrix, $b$ is the bias vector, and $Y$ is the output matrix.
-The non-linearity is introduced through the activation function, which is applied element-wise to the output matrix, such as $Y' = f(Y)$, where $f$ represents the activation function and $Y'$ is the transformed output matrix.
+The nonlinearity is introduced through the activation function, which is applied element-wise to the output matrix, such as $Y' = f(Y)$, where $f$ represents the activation function and $Y'$ is the transformed output matrix.
 \vspace*{3mm}

### 2023-04-03 methods/subsections/model architecture and training strategy.tex
Updates from Overleaf

@@
 \section{Model architecture and training strategy}
+Piaget's theory of cognitive development \cite{Piagets_Theory_of_Cognitive_Development} posits that children acquire knowledge from sensory and motor experiences in their early stages, from birth to around 18 months.
+This period referred to as the 'sensorimotor stage', sees the emergence of early representational thought through basic actions such as sucking, grasping, looking, and listening.
+As children progress through different developmental stages until adolescence and adulthood, their reasoning progressively moves toward abstract ideas and the use of deductive logic.
+Schemas, higher-order cognitive structures hypothesized to underlie many aspects of human knowledge and skill, emerge during this process, which Piaget interprets through an equilibration mechanism that balances new information with old knowledge.
+This mechanism involves \textit{assimilation} and \textit{accommodation}, which entail taking in new information to fit pre-existing schemas and modifying existing schemas resulting from new information.
+In the context of learning, complex structures are based on simpler ones, and transfer of learning occurs when dynamic structures capable of generalization are created.
+\cite{audioselfsupsurvey}
+
+There are similarities between assimilation and accommodation in Piaget's theory of cognitive development and backpropagation in machine learning, both of which involve modifying existing structures based on new information.
+However, it should be noted that these processes' underlying mechanisms and contexts are distinct.
+While assimilation and accommodation involve modifying mental structures to incorporate new information, backpropagation entails adjusting neural network weights to improve output predictions.
+Assimilation and accommodation occur in cognitive development, while backpropagation is specific to machine learning.
+Thus, while there are broad similarities between these processes, they are fundamentally different and cannot be directly compared in detail.
+
 \subsection{Contrastive Self-Supervised Learning for Musical Representations (CSSLMR)}
@@
 
-The CSSL methodology involves the following steps:
+The CSSLMR methodology involves the following steps:
 

### 2023-04-05 introduction/Subsections/Assumptions.tex
Updates from Overleaf

@@
 
-This thesis assumes that high-level musical concepts are agnostic and invariant to the unique tonal quality of the waveform, much like how a sheet music composition can be performed in a variety of ways using different instruments and styles while still retaining its musical essence.
+This thesis assumes that high-level musical concepts are agnostic and invariant to the unique tonal quality of the waveform, much like how a sheet music composition can be performed in infinite ways using different instruments and styles while retaining its musical essence.
 
-We rely on a flexible and adaptable blueprint for musical expression, allowing performers to creatively interpret and express the same musical concepts in different ways.
+We rely on a flexible and adaptable blueprint for musical expression, allowing performers to interpret and express the same musical concepts differently creatively.
 
-Different waveforms can express the same musical concepts despite having distinct timbres or production styles, but it is crucial to distinguish between low-level and high-level musical features when analyzing or comparing different musical pieces.
-High-level features, such as melody, harmony, rhythm, tempo, form, and expression, are more abstract and can be recognized regardless of the specific waveform or production style used.
+Different waveforms can express the same musical concepts despite having distinct timbres or production styles.
+Still, it is crucial to distinguish between low-level and high-level musical features when analyzing or comparing different musical pieces.
+High-level features, such as melody, harmony, rhythm, tempo, form, and expression, are more abstract and can be recognized regardless of the specific waveform or production style.
 
-The thesis relies on the objective and comprehensive perspective on the musical content and meaning of a piece, much like reading sheet music can reveal the underlying musical structure and intention behind a piece of music.
+The thesis relies on the objective and comprehensive perspective on a piece's musical content and meaning, much like reading sheet music can reveal the underlying musical structure and intention behind a piece of music.
 
-One sheet music composition can be performed and recorded in a limitless variety of ways using different instruments, voices, tempos, and interpretations, resulting in an infinite number of valid waveforms that represent its musical content.
+One sheet music composition can be performed and recorded in a limitless variety of ways using different instruments, voices, tempos, and interpretations, resulting in an infinite number of valid waveforms representing its musical content.
 
-Conversely, the same waveform may have only a limited number of sheet music representations that accurately can capture its musical elements as per the current tradition and conventions.
+Conversely, the same waveform may have only a limited number of sheet music representations that can accurately capture its musical elements as per the current tradition and conventions.
 This is because the unique tonal quality of the waveform is strongly influenced by the specific instrument or production technology used to create it, making it difficult to transcribe its sonic properties into a precise sheet music notation.
-Moreover, this unique tonal quality is represented by high-level natural language concepts belonging to an old and rich cultural and sociological tradition.
+Moreover, this unique tonal quality is represented by high-level natural language concepts belonging to a rich old cultural and sociological tradition.

### 2023-04-05 methods/subsections/model architecture and training strategy.tex
Updates from Overleaf

@@
 Piaget's theory of cognitive development \cite{Piagets_Theory_of_Cognitive_Development} posits that children acquire knowledge from sensory and motor experiences in their early stages, from birth to around 18 months.
-This period referred to as the 'sensorimotor stage', sees the emergence of early representational thought through basic actions such as sucking, grasping, looking, and listening.
-As children progress through different developmental stages until adolescence and adulthood, their reasoning progressively moves toward abstract ideas and the use of deductive logic.
+This period, referred to as the \textit{sensorimotor stage}, sees the emergence of early representational thought through basic actions such as sucking, grasping, looking, and listening.
+As children progress through different developmental stages until adolescence and adulthood, their reasoning progressively moves toward abstract ideas and deductive logic.
 Schemas, higher-order cognitive structures hypothesized to underlie many aspects of human knowledge and skill, emerge during this process, which Piaget interprets through an equilibration mechanism that balances new information with old knowledge.
@@
 
-There are similarities between assimilation and accommodation in Piaget's theory of cognitive development and backpropagation in machine learning, both of which involve modifying existing structures based on new information.
+There are similarities between assimilation and accommodation in Piaget's theory of cognitive development and backpropagation in DL, both of which involve modifying existing structures based on new information.
 However, it should be noted that these processes' underlying mechanisms and contexts are distinct.
@@
 Assimilation and accommodation occur in cognitive development, while backpropagation is specific to machine learning.
-Thus, while there are broad similarities between these processes, they are fundamentally different and cannot be directly compared in detail.
+Thus, while these processes have broad similarities, they are fundamentally different and cannot be directly compared in detail.
 

### 2023-04-06 methods/subsections/experiment setup and hyperparameter tuning.tex
Updates from Overleaf

\section{Experiment setup, hyperparameters, and training fine-tuning}

For finetuning and improving the model's behavior, we followed \href{http://karpathy.github.io/2019/04/25/recipe/}{\textit{A Recipe for Training Neural Networks}} \cite{AndrejKarpathyHttp://karpathy.github.io/2019/04/25/recipe/} by \href{https://karpathy.ai/}{Andrej Karpathy} \cite{AndrejKarpathyHttps://karpathy.ai/}. A blog post that discusses a recipe for training neural networks. The author of the blog post tweeted about common mistakes people make when training neural nets and the post aims to expand on those mistakes by explaining how to avoid them through a particular process. Andrej Karpathy notes that there is often a gap between understanding the technical aspects of a neural network and achieving state-of-the-art results.

### 2023-04-06 introduction/Subsections/Introduction.tex
Updates from Overleaf

@@
 The reason behind this is non-other but the implementation complexity for such heuristics and abstract fields of study.
-Closing the gap between human perception, environmental and cultural factors, and computational solutions to mimic the formers is an already tackled topic \cite{Large1994ResonanceMeter}\cite{Mullensiefen2003MeasuringJudgments}\cite{Sears2014PerceivingCadence}\cite{Thaut2014HumanPatter}, yet remains a vast open challenge.
+Closing the gap between human perception, environmental and cultural factors, and computational solutions to mimic the formers is an already tackled topic \cite{Large1994ResonanceMeter}\cite{Mullensiefen2003MeasuringJudgments}\cite{Sears2014PerceivingCadence}\cite{Thaut2014HumanPatter}\cite{, yet remains a vast open challenge.

### 2023-04-06 introduction/Subsections/Motivation.tex
Updates from Overleaf

@@
 
-\section{About music aural skills and high-level perception}
+\section{About music aural skills and high-level perceptual concepts}
 
@@
 
-\begin{figure}[h]
+\begin{figure}[ht]
 \includegraphics[clip,width=\columnwidth]{figures/schenkerian analysis/SchubertOp4no3.png}% 
@@
 Background (Hintergrund): The structural level of the fundamental structure.
-Bass Arpeggiation (Bassbrechung): Bass pattern I-V-I forming the harmonic content of the background of tonal musical pieces.
-Chord of Nature (Klang): The complex sound consisting of the first five notes of the harmonic series, suggesting a model for the major triad.
+Bass Arpeggiation (Bassbrechung): Bass pattern I-V-I forms the harmonic content of the background of tonal musical pieces.
+Chord of Nature (Klang): The complex sound consisting of the first five harmonic series notes suggests a model for the major triad.
 Diminution: The process by which an interval formed by notes of longer value is expressed in notes of smaller value.
@@
 Middleground (Mittelgrund): An intermediate structural level between the background and foreground in Schenkerian analysis.
-Prolongation (Auskomponierung): The process in tonal music through which a pitch, interval, or consonant triad is able to govern spans of music when not physically sounding.
-Structural Level (Schicht): Refers to the different levels of musical structure in Schenkerian analysis, including background, middleground, and foreground.
-Tonal Space: A general principle of Schenkerian analysis where intervals between the notes of the tonic triad form a tonal space that is filled with passing and neighbor notes.
+Prolongation (Auskomponierung): The process in tonal music through which a pitch, interval, or consonant triad can govern music spans when not physically sounding.
+Structural Level (Schicht): Refers to the different levels of musical structure in Schenkerian analysis, including background, middle-ground, and foreground.
+Tonal Space: A general principle of Schenkerian analysis where intervals between the notes of the tonic triad form a tonal space filled with passing and neighbor notes.
 Unfolding (Ausfaltung): The transformation of a single chord into a horizontal succession.
-Voice Leading: The study of the principles that govern the progression of the component voices of a composition both separately and in combination.
-The glossary also includes related articles, references, and external links for further reading and understanding of Schenkerian analysis.
+Voice Leading: The study of the principles that govern the progression of the component voices of the composition both separately and in combination.
+The glossary also includes related articles, references, and external links for further reading and understanding Schenkerian analysis.
 

### 2023-04-07 MasterThesis.tex
Updates from Overleaf

@@
 \usepackage{sidecap}
+
 %---tikz---
+
 \usepackage{tikz}
@@
 \usetikzlibrary{fadings}
+\usetikzlibrary{positioning}
 
@@
   Uncovering underlying musical content in the temporal domain \\
-  \small Leveraging deep learning, inductive bias, and aural skills to learn embedding spaces from raw waveforms with applications to MIR downstream tasks}
+  \small Leveraging deep learning, inductive bias, and music aural skills to learn embedding spaces from raw waveforms with applications to MIR downstream tasks}
 
@@
 \input{discussion/discussion}
+%Future work
+\input{future work/future work}
+\newpage
 
@@
 \bibliographystyle{naturemag}
-\bibliography{bibliography}
+\bibliography{bibliography/references.bib}
 
+\newpage
 \input{appendix/appendix}

### 2023-04-07 introduction/Subsections/Assumptions.tex
Updates from Overleaf

@@
 
-This thesis assumes that high-level musical concepts are agnostic and invariant to the unique tonal quality of the waveform, much like how a sheet music composition can be performed in infinite ways using different instruments and styles while retaining its musical essence.
+This thesis argues that high-level musical concepts are invariant to the unique tonal quality of the waveform, much like a sheet music composition can be performed in countless ways using various instruments and styles while retaining its essence.
 
-We rely on a flexible and adaptable blueprint for musical expression, allowing performers to interpret and express the same musical concepts differently creatively.
+High-level features like melody, harmony, rhythm, tempo, form, and expression are more abstract and can be recognized regardless of waveform or production style.
+This approach provides an objective and comprehensive perspective on a piece's musical content and meaning, similar to how reading sheet music reveals a piece's underlying structure and intention.
 
-Different waveforms can express the same musical concepts despite having distinct timbres or production styles.
-Still, it is crucial to distinguish between low-level and high-level musical features when analyzing or comparing different musical pieces.
-High-level features, such as melody, harmony, rhythm, tempo, form, and expression, are more abstract and can be recognized regardless of the specific waveform or production style.
+While a waveform may have a limited number of sheet music representations that accurately capture its musical elements, one sheet music composition can be performed in infinite ways using different instruments, voices, tempos, and interpretations.
+The unique tonal quality of a waveform is strongly influenced by the specific instrument or production technology used to create it, making it difficult to transcribe its sonic properties into precise sheet music notation.
 
-The thesis relies on the objective and comprehensive perspective on a piece's musical content and meaning, much like reading sheet music can reveal the underlying musical structure and intention behind a piece of music.
-
-One sheet music composition can be performed and recorded in a limitless variety of ways using different instruments, voices, tempos, and interpretations, resulting in an infinite number of valid waveforms representing its musical content.
-
-Conversely, the same waveform may have only a limited number of sheet music representations that can accurately capture its musical elements as per the current tradition and conventions.
-This is because the unique tonal quality of the waveform is strongly influenced by the specific instrument or production technology used to create it, making it difficult to transcribe its sonic properties into a precise sheet music notation.
-Moreover, this unique tonal quality is represented by high-level natural language concepts belonging to a rich old cultural and sociological tradition.
+Additionally, this unique tonal quality is represented by high-level natural language concepts that belong to a rich cultural and sociological tradition.

### 2023-04-07 introduction/Subsections/Introduction.tex
Updates from Overleaf

--- 2023-03-29 introduction/Subsections/Introduction.tex
@@
 The reason behind this is non-other but the implementation complexity for such heuristics and abstract fields of study.
-Closing the gap between human perception, environmental and cultural factors, and computational solutions to mimic the formers is an already tackled topic \cite{Large1994ResonanceMeter}\cite{Mullensiefen2003MeasuringJudgments}\cite{Sears2014PerceivingCadence}\cite{Thaut2014HumanPatter}, yet remains a vast open challenge.
+Closing the gap between human perception, environmental and cultural factors, and computational solutions to mimic the formers is an already tackled topic \cite{Large1994ResonanceMeter}\cite{Mullensiefen2003MeasuringJudgments}\cite{Sears2014PerceivingCadence}\cite{Thaut2014HumanPatter}\cite{Hernandez-Olivan2023SymbolicMethods}, yet remains a vast open challenge.

### 2023-04-07 introduction/Subsections/Motivation.tex
Updates from Overleaf

@@
 
-Let's pick a core MIR task as a sample to display such complexity: Music Structure Analysis (MSA), an interdisciplinary field that aims to understand the structure of music\cite{Nieto2020Audio-BasedApplications}.
+Let's pick a core MIR task as a sample to display such complexity: Music Structure Analysis (MSA), an interdisciplinary field that aims to understand the structure of music \cite{Nieto2020Audio-BasedApplications}.
 However, due to subjectivity, ambiguity, and data scarcity, audio-based MSA faces challenges like boundary placement ambiguity and similarity quantification \cite{NietoPerceptualMusic}.
+
 The main principles of MSA were initially defined as homogeneity, novelty, and repetition, with the addition of regularity.
-
-The checkerboard kernel technique is a simple and effective method for Music Structure Analysis (MSA) based on the homogeneity principle.
+The checkerboard kernel technique is a simple and effective method for MSA based on the homogeneity principle.
 The kernel, with a checkerboard-like structure, is convolved over the main diagonal of a Self-Similarity Matrix (SSM) such as $S_{ij}$ is the similarity between time frames $i$ and $j$, $\vec{x}_i$ is the vector representation of time frame $i$, and $\left| \vec{x}_i \right|$ is the Euclidean norm of vector $\vec{x}_i$.
@@
 
-This yields a novelty curve that highlights sudden changes in the selected musical features (some examples would be chroma, MFCCs, beat-synchronous features, onset and offset detection, and harmonic and percussive separation) from which to extract the segment boundaries.
+This yields a novelty curve highlighting sudden changes in the selected musical features from which to extract the segment boundaries.
 
@@
 Combining technical tasks, aural skills, and music perception is challenging due to the complexity and subjectivity of musical perception, discrepancies between the features extracted by DSP techniques and the features perceived by humans, and the variability of musical signals and individual differences in musical perception.
-DSP techniques may not always reflect how humans perceive music and may not capture the subtle variations in timing or harmonic relationships critical to musical perception.
-Variability in musical signals due to instrumentation, genre, and performance style further complicates the development of DSP techniques that can be generalized to different musical contexts.
+
+Purely mathematical approaches may not always reflect how humans perceive music and may not capture the subtle variations in timing or harmonic relationships critical to musical perception.
+Variability in musical signals due to instrumentation, genre, and performance style further complicates the development of these techniques that can be generalized to different musical contexts.
 
@@
 Both approaches aim to identify abstract concepts that reinforce or disrupt the tonal foundation.
-Their ultimate goal is to advance the tonal landscape, providing musicians with a dependable playground for growth and development.
+Their ultimate goal is to advance the tonal landscape, providing musicians with a dependable playground for growth, development, and further understanding of tonal paradigms.
 
@@
 This system allows for greater harmonic flexibility and a broader range of tonal colors, influencing the development of jazz and contemporary music.
-
-\subsection{Assumptions}

### 2023-04-07 introduction/Subsections/Objectives.tex
Updates from Overleaf

@@
 
-A self-supervised model that learns an embedding space to retrieve musical content from raw audio signals could have several potential applications and downstream tasks in Music Information Retrieval (MIR).
-Here are some examples:
+A self-supervised model that learns an embedding space to retrieve musical content from raw audio signals could have several potential applications and downstream tasks in MIR. Here are some examples:
 

### 2023-04-07 methods/subsections/model architecture and training strategy.tex
Updates from Overleaf

@@
 Piaget's theory of cognitive development \cite{Piagets_Theory_of_Cognitive_Development} posits that children acquire knowledge from sensory and motor experiences in their early stages, from birth to around 18 months.
-This period, referred to as the \textit{sensorimotor stage}, sees the emergence of early representational thought through basic actions such as sucking, grasping, looking, and listening.
+This period referred to as the \textit{sensorimotor stage}, sees the emergence of early representational thought through basic actions such as sucking, grasping, looking, and listening.
 As children progress through different developmental stages until adolescence and adulthood, their reasoning progressively moves toward abstract ideas and deductive logic.

### 2023-04-10 introduction/Subsections/Motivation.tex
Updates from Overleaf

@@
 Both approaches aim to identify abstract concepts that reinforce or disrupt the tonal foundation.
-Their ultimate goal is to advance the tonal landscape, providing musicians with a dependable playground for growth, development, and further understanding of tonal paradigms.
+Their ultimate goal is to advance the tonal landscape, providing musicians with a dependable playground for growth, development, and further understanding tonal paradigms.
 
@@
 Bass Arpeggiation (Bassbrechung): Bass pattern I-V-I forms the harmonic content of the background of tonal musical pieces.
-Chord of Nature (Klang): The complex sound consisting of the first five harmonic series notes suggests a model for the major triad.
+Chord of Nature (Klang): The complex sound of the first five harmonic series notes suggests a model for the major triad.
 Diminution: The process by which an interval formed by notes of longer value is expressed in notes of smaller value.
@@
 
-George Russell's Lydian Chromatic Concept:
-George Russell's Lydian Chromatic Concept of Tonal Organization is an innovative approach to understanding and organizing musical relationships.
-Introduced in the 1950s, the theory asserts that the Lydian mode, rather than the traditional major scale, is the accurate parent scale in Western music.
-The Lydian scale is characterized by a raised fourth degree, giving it a brighter and more consonant sound.
-Russell's concept revolves around "chord modes," derived from a chord's parent Lydian scale.
-This system allows for greater harmonic flexibility and a broader range of tonal colors, influencing the development of jazz and contemporary music.
+%%%%%%%%%%%%%
+%MESOSTRUC
+%%%%%%%%%%%%%
+
+Mesostructures \cite{Mesostructures2023} are intermediate levels of articulation between waveshapes' microstructure and musical forms' macrostructure.
+Examples of mesostructures include melody, arpeggios, syncopation, polyphonic grouping, and textural contrast.
+The article notes that mesostructures have received limited attention in deep learning, as current models only focus on microstructures.
+The article proposes a new approach to mesostructural audio modeling, which involves a differentiable arpeggiator and time-frequency scattering.
+The article also discusses the need for a time-invariant and multiscale differentiable time-frequency model of similarity at the level of both local spectra and spectrotemporal modulations.

### 2023-04-10 methods/subsections/machine learning.tex
Updates from Overleaf

@@
 
-\textbf{1D Convolution Example:} Given a 1D input signal $I = [i_1, i_2, ..., i_n]$ and a filter (or kernel) $K = [k_1, k_2, ..., k_m]$, the convolution operation is defined as $(I * K)j = \sum{u=1}^{m} I_{j-u+1} K_u$, where $j$ ranges from $1$ to $n-m+1$, and $I * K$ represents the resulting feature vector after applying the convolution.
-The objective of the 1D convolution operation is to slide the filter over the input signal and compute the element-wise product and sum for each local region, effectively learning and detecting local patterns in the input data.
+\textbf{Convolution:} It involves sliding a small window, called a filter or kernel, over input data to compute the dot product between the kernel and each local region of the data.
+The result is a new feature map highlighting patterns and essential information.
+
+Given a 2D input data represented as a matrix $I = [i_{ij}]{m \times n}$ and a filter $K = [k{ij}]_{p \times q}$, the convolution operation is defined as:
+
+$$(I * K)_{kl} = \sum_{i=1}^{p} \sum_{j=1}^{q} i_{k+i-1, l+j-1}k_{ij}$$
+
+Here, $k$ ranges from $1$ to $m-p+1$ and $l$ ranges from $1$ to $n-q+1$. The resulting feature map after applying the convolution is denoted by $(I * K)_{kl}$.
+
+The convolution operation slides the kernel $K$ over the input image $I$, performing an element-wise multiplication and sum of the local region centered at pixel $(k,l)$ to compute the value of each element in the output feature map, $(I * K)_{kl}$.
+This process is repeated for each pixel $(k,l)$, resulting in a new feature map that captures local patterns in the input image.
+
+\input{figures/neural networks/convolution}
 

### 2023-04-10 methods/subsections/model architecture and training strategy.tex
Updates from Overleaf

@@
 
-\subsection{Contrastive Self-Supervised Learning for Musical Representations (CSSLMR)}
+\subsection{Contrastive Self-Supervised Learning of Musical Representations (CSSLMR)}
 
-Contrastive Self-Supervised Learning for Musical Representations (CSSLMR) is an approach that combines the principles of Self-Supervised Learning (SSL) and Contrastive Learning of Musical Representations (CLMR) to learn discriminative and valuable representations of music without relying on explicit labels.
+Contrastive Self-Supervised Learning of Musical Representations (CSSLMR) is an approach that combines the principles of Self-Supervised Learning (SSL) and Contrastive Learning of Musical Representations (CLMR) to learn discriminative and valuable representations of music without relying on explicit labels.
 By leveraging the structure and content of music and contrasting different augmentations or transformations of the same musical piece against randomly (or not) selected pieces, CSSLMR models can effectively capture the underlying structure and known invariance in the data.

### 2023-04-11 MasterThesis.tex
Updates from Overleaf

@@
 \usetikzlibrary{fadings}
-\usetikzlibrary{positioning}
+\usetikzlibrary{matrix, positioning}
+
+%---NN tikz diagrams---
+
+\usepackage{amsmath} % for aligned
+%\usepackage{amssymb} % for \mathbb
+\usepackage{tikz}
+%\usepackage{etoolbox} % for \ifthen
+\usepackage{listofitems} % for \readlist to create arrays
+\usetikzlibrary{arrows.meta} % for arrow size
+\usepackage[outline]{contour} % glow around text
+\contourlength{1.4pt}
+
+\tikzset{>=latex} % for LaTeX arrow head
+\usepackage{xcolor}
+\colorlet{myred}{red!80!black}
+\colorlet{myblue}{blue!80!black}
+\colorlet{mygreen}{green!60!black}
+\colorlet{myorange}{orange!70!red!60!black}
+\colorlet{mydarkred}{red!30!black}
+\colorlet{mydarkblue}{blue!40!black}
+\colorlet{mydarkgreen}{green!30!black}
+\tikzstyle{node}=[thick,circle,draw=myblue,minimum size=22,inner sep=0.5,outer sep=0.6]
+\tikzstyle{node in}=[node,green!20!black,draw=mygreen!30!black,fill=mygreen!25]
+\tikzstyle{node hidden}=[node,blue!20!black,draw=myblue!30!black,fill=myblue!20]
+\tikzstyle{node convol}=[node,orange!20!black,draw=myorange!30!black,fill=myorange!20]
+\tikzstyle{node out}=[node,red!20!black,draw=myred!30!black,fill=myred!20]
+\tikzstyle{connect}=[thick,mydarkblue] %,line cap=round
+\tikzstyle{connect arrow}=[-{Latex[length=4,width=3.5]},thick,mydarkblue,shorten <=0.5,shorten >=1]
+\tikzset{ % node styles, numbered for easy mapping with \nstyle
+  node 1/.style={node in},
+  node 2/.style={node hidden},
+  node 3/.style={node out},
+}
+\def\nstyle{int(\lay<\Nnodlen?min(2,\lay):3)} % map layer number onto 1, 2, or 3
+
+%------------------------
 

### 2023-04-11 figures/neural networks/activation.tex
Updates from Overleaf

% NEURAL NETWORK activation
% https://www.youtube.com/watch?v=aircAruvnKk&list=PLZHQObOWTQDNU6R1_67000Dx_ZCJB-3pi&index=1
\begin{tikzpicture}[x=2.7cm,y=1.6cm]
  \message{^^JNeural network activation}
  \def\NI{5} % number of nodes in input layers
  \def\NO{4} % number of nodes in output layers
  \def\yshift{0.4} % shift last node for dots

  % INPUT LAYER
  \foreach \i [evaluate={\c=int(\i==\NI); \y=\NI/2-\i-\c*\yshift; \index=(\i<\NI?int(\i):"n");}]
              in {1,...,\NI}{ % loop over nodes
    \node[node in,outer sep=0.6] (NI-\i) at (0,\y) {$a_{\index}^{(0)}$};
  }

  % OUTPUT LAYER
  \foreach \i [evaluate={\c=int(\i==\NO); \y=\NO/2-\i-\c*\yshift; \index=(\i<\NO?int(\i):"m");}]
    in {\NO,...,1}{ % loop over nodes
    \ifnum\i=1 % high-lighted node
      \node[node hidden]
        (NO-\i) at (1,\y) {$a_{\index}^{(1)}$};
      \foreach \j [evaluate={\index=(\j<\NI?int(\j):"n");}] in {1,...,\NI}{ % loop over nodes in previous layer
        \draw[connect,white,line width=1.2] (NI-\j) -- (NO-\i);
        \draw[connect] (NI-\j) -- (NO-\i)
          node[pos=0.50] {\contour{white}{$w_{1,\index}$}};
      }
    \else % other light-colored nodes
      \node[node,blue!20!black!80,draw=myblue!20,fill=myblue!5]
        (NO-\i) at (1,\y) {$a_{\index}^{(1)}$};
      \foreach \j in {1,...,\NI}{ % loop over nodes in previous layer
        %\draw[connect,white,line width=1.2] (NI-\j) -- (NO-\i);
        \draw[connect,myblue!20] (NI-\j) -- (NO-\i);
      }
    \fi
  }

  % DOTS
  \path (NI-\NI) --++ (0,1+\yshift) node[midway,scale=1.2] {$\vdots$};
  \path (NO-\NO) --++ (0,1+\yshift) node[midway,scale=1.2] {$\vdots$};

  % EQUATIONS
  \def\agr#1{{\color{mydarkgreen}a_{#1}^{(0)}}}
  \node[below=17,right=11,mydarkblue,scale=0.95] at (NO-1)
    {$\begin{aligned} %\underset{\text{bias}}{b_1}
       &= \color{mydarkred}\sigma\left( \color{black}
            w_{1,0}\agr{0} + w_{1,1}\agr{1} + \ldots + w_{1,n}\agr{n} + b_1^{(0)}
          \color{mydarkred}\right)\\
       &= \color{mydarkred}\sigma\left( \color{black}
            \sum_{i=1}^{n} w_{1,i}\agr{i} + b_1^{(0)}
           \color{mydarkred}\right)
     \end{aligned}$};
  \node[right,scale=0.9] at (1.3,-1.3)
    {$\begin{aligned}
      {\color{mydarkblue}
      \begin{pmatrix}
        a_{1}^{(1)} \\[0.3em]
        a_{2}^{(1)} \\
        \vdots \\
        a_{m}^{(1)}
      \end{pmatrix}}
      &=
      \color{mydarkred}\sigma\left[ \color{black}
      \begin{pmatrix}
        w_{1,0} & w_{1,1} & \ldots & w_{1,n} \\
        w_{2,0} & w_{2,1} & \ldots & w_{2,n} \\
        \vdots  & \vdots  & \ddots & \vdots  \\
        w_{m,0} & w_{m,1} & \ldots & w_{m,n}
      \end{pmatrix}
      {\color{mydarkgreen}
      \begin{pmatrix}
        a_{1}^{(0)} \\[0.3em]
        a_{2}^{(0)} \\
        \vdots \\
        a_{n}^{(0)}
      \end{pmatrix}}
      +
      \begin{pmatrix}
        b_{1}^{(0)} \\[0.3em]
        b_{2}^{(0)} \\
        \vdots \\
        b_{m}^{(0)}
      \end{pmatrix}
      \color{mydarkred}\right]\\[0.5em]
      {\color{mydarkblue}a^{(1)}}
      &= \color{mydarkred}\sigma\left( \color{black}
           \mathbf{W}^{(0)} {\color{mydarkgreen}a^{(0)}}+\mathbf{b}^{(0)}
         \color{mydarkred}\right)
         %\color{black},\quad \mathbf{W}^{(0)} \in \mathbb{R}^{m\times n}
    \end{aligned}$};

\end{tikzpicture}

### 2023-04-11 figures/neural networks/convolution.tex
Updates from Overleaf

\begin{center}
\begin{tikzpicture}[
    2d-arr/.style={matrix of nodes, row sep=-\pgflinewidth, column sep=-\pgflinewidth, nodes={draw}}
  ]
  % TikZ code here

  \matrix (mtr) [2d-arr] {
  0 & 1 & 1 & |[fill=orange!30]| 1 & |[fill=orange!30]| 0 & |[fill=orange!30]| 0 & 0\\
  0 & 0 & 1 & |[fill=orange!30]| 1 & |[fill=orange!30]| 1 & |[fill=orange!30]| 0 & 0\\
  0 & 0 & 0 & |[fill=orange!30]| 1 & |[fill=orange!30]| 1 & |[fill=orange!30]| 1 & 0\\
  0 & 0 & 0 & 1 & 1 & 0 & 0\\
  0 & 0 & 1 & 1 & 0 & 0 & 0\\
  0 & 1 & 1 & 0 & 0 & 0 & 0\\
  1 & 1 & 0 & 0 & 0 & 0 & 0\\
  };

  \node[below=of mtr-5-4] {$\mathbf I$};

  \node[right=0.2em of mtr] (str) {$*$};

  \matrix (K) [2d-arr, right=0.2em of str, nodes={draw, fill=teal!30}] {
    1 & 0 & 1 \\
    0 & 1 & 0 \\
    1 & 0 & 1 \\
  };
  \node[below=of K-3-2] {$\mathbf K$};

  \node[right=0.2em of K] (eq) {$=$};

  \matrix (ret) [2d-arr, right=0.2em of eq] {
  1 & 4 & 3 & |[fill=blue!80!black!30]| 4 & 1\\
  1 & 2 & 4 & 3 & 3\\
  1 & 2 & 3 & 4 & 1\\
  1 & 3 & 3 & 1 & 1\\
  3 & 3 & 1 & 1 & 0\\
  };
  \node[below=of ret-4-3] {$\mathbf{I * K}$};

  \draw[dashed, teal] (mtr-1-6.north east) -- (K-1-1.north west);
  \draw[dashed, teal] (mtr-3-6.south east) -- (K-3-1.south west);

  \draw[dashed, blue!80!black] (K-1-3.north east) -- (ret-1-4.north west);
  \draw[dashed, blue!80!black] (K-3-3.south east) -- (ret-1-4.south west);

  \foreach \i in {1,2,3} {
      \foreach \j in {4,5,6} {
          \node[font=\tiny, scale=0.6, shift={(-1.2ex,-2ex)}] at (mtr-\i-\j) {$\times \pgfmathparse{int(mod(\i+\j,2))}\pgfmathresult$};
        }
    }
\end{tikzpicture}
\end{center}

### 2023-04-11 introduction/Subsections/Objectives.tex
Updates from Overleaf

@@
 \item Music generation: The embedding space can generate new musical content by sampling from the learned distribution of musical features.
-\item Music synchronization: The learned embedding space can synchronize audio and visual content in applications such as music videos or virtual reality experiences.
+\item Music synchronization: The discovered embedding space can synchronize audio and visual content in applications such as music videos or virtual reality experiences.
 \item Music search: The embedding space can search for specific musical content based on high-level perceptual concepts and the relationships they have among them

### 2023-04-11 methods/subsections/machine learning.tex
Updates from Overleaf

@@
 
+%Activation equation
+\input{figures/neural networks/activation}
+
 %NN
@@
 \item \textbf{Convolutional layers:} These layers apply a convolution operation to the input data.
-The raw audio data can be either a 1D signal or transformed into a spectrogram or a Mel-spectrogram representation, which can be considered an image-like 2D representation of the audio data.
 The convolutional layers are designed to effectively learn local patterns and features in the audio data \footnote{For a visual explanation of convolution, see this video: \url{https://youtu.be/KuXjwB4LzSA}}.
 
-\textbf{Convolution:} It involves sliding a small window, called a filter or kernel, over input data to compute the dot product between the kernel and each local region of the data.
+A convolution operation involves sliding a small window, called a filter or kernel, over input data to compute the dot product between the kernel and each local region of the data.
 The result is a new feature map highlighting patterns and essential information.

### 2023-04-13 figures/neural networks/Back_propagation.tex
Updates from Overleaf

--- 2023-03-12 figures/Figures CNN/Back_propagation.tex
@@
     	\end{tikzpicture}
-	\caption[Backpropagation of errors through the network.]{Once evaluated for all output units, the errors $\delta_i^{(L+1)}$ can be propagated backwards.}.
+	\caption[Backpropagation of errors through the network.]{\small{Once evaluated for all output units, the errors $\delta_i^{(L+1)}$ can be propagated backwards.}}.
 	\label{fig:error-backpropagation}

### 2023-04-13 figures/neural networks/NN with coefficients, shifted.tex
Updates from Overleaf

% NEURAL NETWORK with coefficients, shifted
\begin{tikzpicture}[x=2.2cm,y=1.4cm]
  \message{^^JNeural network, shifted}
  \readlist\Nnod{4,5,5,5,3} % array of number of nodes per layer
  \readlist\Nstr{n,m,m,m,k} % array of string number of nodes per layer
  \readlist\Cstr{\strut x,a^{(\prev)},a^{(\prev)},a^{(\prev)},y} % array of coefficient symbol per layer
  \def\yshift{0.5} % shift last node for dots

  \message{^^J  Layer}
  \foreachitem \N \in \Nnod{ % loop over layers
    \def\lay{\Ncnt} % alias of index of current layer
    \pgfmathsetmacro\prev{int(\Ncnt-1)} % number of previous layer
    \message{\lay,}
    \foreach \i [evaluate={\c=int(\i==\N); \y=\N/2-\i-\c*\yshift;
                 \index=(\i<\N?int(\i):"\Nstr[\lay]");
                 \x=\lay; \n=\nstyle;}] in {1,...,\N}{ % loop over nodes
      % NODES
      \node[node \n] (N\lay-\i) at (\x,\y) {$\Cstr[\lay]_{\index}$};

      % CONNECTIONS
      \ifnum\lay>1 % connect to previous layer
        \foreach \j in {1,...,\Nnod[\prev]}{ % loop over nodes in previous layer
          \draw[connect,white,line width=1.2] (N\prev-\j) -- (N\lay-\i);
          \draw[connect] (N\prev-\j) -- (N\lay-\i);
          %\draw[connect] (N\prev-\j.0) -- (N\lay-\i.180); % connect to left
        }
      \fi % else: nothing to connect first layer

    }
    \path (N\lay-\N) --++ (0,1+\yshift) node[midway,scale=1.5] {$\vdots$};
  }

  % LABELS
  \node[above=5,align=center,mygreen!60!black] at (N1-1.90) {input\\[-0.2em]layer};
  \node[above=2,align=center,myblue!60!black] at (N3-1.90) {hidden layers};
  \node[above=10,align=center,myred!60!black] at (N\Nnodlen-1.90) {output\\[-0.2em]layer};

\end{tikzpicture}

### 2023-04-13 figures/neural networks/Network_graph.tex
Updates from Overleaf

--- 2023-01-14 Figures/Figures CNN/Network_graph.tex
@@
-\begin{SCfigure}[12][h]
+\begin{SCfigure}[12][ht]
 	\centering
@@
     \end{tikzpicture}
-    \caption[Network graph of a perceptron with $D$ input units and $C$ output units.]{The perceptron consists of $D$ input units and $C$ output units.
+    \caption[Network graph of a perceptron with $D$ input units and $C$ output units.]{\small{The perceptron consists of $D$ input units and $C$ output units.
 All units are labeled according to their output: $y_i = f(z_i)$ in the case of output units; $x_i$ in the case of input units.
 The input values $x_i$ are propagated to each output unit using the weighted sum propagation rule.
-The additional input value $x_0 := 1$ is used to include the biases as weights.}
+The additional input value $x_0 := 1$ is used to include the biases as weights.}}
     \label{fig:perceptron}

### 2023-04-13 figures/neural networks/Single Neuron.tex
Updates from Overleaf

--- 2023-01-14 Figures/Figures CNN/Single Neuron.tex
@@
 		\draw (0,0) node[xshift=-10]{$x_D$} -- (p);
-		\draw (p) -- (3,1) node[xshift=30]{$y := f(z)$};
+		\draw (p) -- (3,1) node[xshift=30]{$y := a(z)$};
 	\end{tikzpicture}
-	\caption[Single processing units and its components.]{Single processing unit and its components.
-The activation function is denoted by $f$ and applied to the actual input $z$ of the unit to form its output $y = f(z)$.
+	\caption[Single processing units and its components.]{\small{Single processing unit and its components.
+The activation function is denoted by $a$ and applied to the actual input $z$ of the unit to form its output $y = a(z)$.
 $x_1, \ldots, x_D$ represent input from other units within the network; $w_0$ is called bias and represents an external input to the unit.
-All inputs are mapped onto the actual input $z$ using the propagation rule.}
+The propagation rule maps all inputs onto the actual input $z$.}}
 	\label{fig:processing-unit}

### 2023-04-13 figures/neural networks/Single_CNN.tex
Updates from Overleaf

--- 2023-03-12 figures/Figures CNN/Single_CNN.tex
@@
 	\centering
+        \scalebox{0.8}{
 	\begin{tikzpicture}
@@
 	\end{tikzpicture}
-	\caption[Illustration of a convolutional layer.]{Illustration of a single convolutional layer.
-If layer $l$ is a convolutional layer, the input data (if $l = 1$) or a feature map of the previous layer is convolved by different filters to yield the output feature maps of layer $l$.}
-	\label{fig:convolutional-layer}
+        }
+	\caption[Illustration of a 2D convolutional layer.]{\small{Illustration of a 2D single convolutional layer.
+If layer $l$ is a convolutional layer, the input data (if $l = 1$) or a feature map of the previous layer is convolved by different filters (or kernels) to yield the output feature maps of layer $l$.}}
+	\label{fig: convolutional layer}
 \end{SCfigure}

### 2023-04-13 figures/neural networks/colour CNN.tex
Updates from Overleaf

\begin{figure}[ht]
    \centering
% DEEP CONVOLUTIONAL NEURAL NETWORK
\begin{tikzpicture}[x=1.6cm,y=1.1cm]
  \large
  \message{^^JDeep convolution neural network}
  \readlist\Nnod{5,5,4,3,2,4,4,3} % array of number of nodes per layer
  \def\NC{6} % number of convolutional layers
  \def\nstyle{int(\lay<\Nnodlen?(\lay<\NC?min(2,\lay):3):4)} % map layer number on 1, 2, or 3
  \tikzset{ % node styles, numbered for easy mapping with \nstyle
    node 1/.style={node in},
    node 2/.style={node convol},
    node 3/.style={node hidden},
    node 4/.style={node out},
  }

  % TRAPEZIA
  \draw[myorange!40,fill=myorange,fill opacity=0.02,rounded corners=2]
    %(1.6,-2.5) rectangle (4.4,2.5);
    (1.6,-2.7) --++ (0,5.4) --++ (3.8,-1.9) --++ (0,-1.6) -- cycle;
  \draw[myblue!40,fill=myblue,fill opacity=0.02,rounded corners=2]
    (5.6,-2.0) rectangle++ (1.8,4.0);
  \node[right=19,above=1,align=center,myorange!60!black] at (3.1,1.8) {convolutional\\[-0.2em]layers};
  \node[above=1,align=center,myblue!60!black] at (6.5,1.9) {fully-connected\\[-0.2em]hidden layers};

  \message{^^J  Layer}
  \foreachitem \N \in \Nnod{ % loop over layers
    \def\lay{\Ncnt} % alias of index of current layer
    \pgfmathsetmacro\prev{int(\Ncnt-1)} % number of previous layer
    %\pgfmathsetmacro\Nprev{\Nnod[\prev]} % array of number of nodes in previous layer
    \message{\lay,}
    \foreach \i [evaluate={\y=\N/2-\i+0.5; \x=\lay; \n=\nstyle;}] in {1,...,\N}{ % loop over nodes
      %\message{^^J  Layer \lay, node \i}

      % NODES
      \node[node \n,outer sep=0.6] (N\lay-\i) at (\x,\y) {};

      % CONNECTIONS
      \ifnum\lay>1 % connect to previous layer
        \ifnum\lay<\NC % convolutional layers
          \foreach \j [evaluate={\jprev=int(\i-\j); \cconv=int(\Nnod[\prev]>\N); \ctwo=(\cconv&&\j>0);
                       \c=int((\jprev<1||\jprev>\Nnod[\prev]||\ctwo)?0:1);}]
                       in {-1,0,1}{
            \ifnum\c=1
              \ifnum\cconv=0
                \draw[connect,white,line width=1.2] (N\prev-\jprev) -- (N\lay-\i);
              \fi
              \draw[connect] (N\prev-\jprev) -- (N\lay-\i);
            \fi
          }

        \else % fully connected layers
          \foreach \j in {1,...,\Nnod[\prev]}{ % loop over nodes in previous layer
            \draw[connect,white,line width=1.2] (N\prev-\j) -- (N\lay-\i);
            \draw[connect] (N\prev-\j) -- (N\lay-\i);
          }
        \fi
      \fi % else: nothing to connect first layer

    }
  }

  % LABELS
  \node[above=0.5,align=center,mygreen!60!black] at (N1-1.90) {input\\[-0.2em]layer};
  \node[above=1.5,align=center,myred!60!black] at (N\Nnodlen-1.90) {output\\[-0.2em]layer};

\end{tikzpicture}
    \caption{High-level illustration of a CNN}
    \label{fig: CNN colour diagram}
\end{figure}

### 2023-04-13 introduction/Subsections/Assumptions.tex
Updates from Overleaf

@@
 
-This thesis argues that high-level musical concepts are invariant to the unique tonal quality of the waveform, much like a sheet music composition can be performed in countless ways using various instruments and styles while retaining its essence.
+This thesis posits that high-level musical concepts manifest over time and remain invariant to specific attributes such as tonal quality, tempo, key, orchestration, signal noise, and others.
+This is akin to a sheet music composition being performed in myriad ways using diverse instruments and styles while preserving its core essence.
 
-High-level features like melody, harmony, rhythm, tempo, form, and expression are more abstract and can be recognized regardless of waveform or production style.
-This approach provides an objective and comprehensive perspective on a piece's musical content and meaning, similar to how reading sheet music reveals a piece's underlying structure and intention.
+Abstract features, such as melody, harmony, rhythm, tempo, form, and expression, can be identified irrespective of waveform or production style.
+This approach offers an objective and comprehensive insight into a piece's musical content and meaning, analogous to how analyzing sheet music unveils a composition's underlying structure and intent.
 
-While a waveform may have a limited number of sheet music representations that accurately capture its musical elements, one sheet music composition can be performed in infinite ways using different instruments, voices, tempos, and interpretations.
-The unique tonal quality of a waveform is strongly influenced by the specific instrument or production technology used to create it, making it difficult to transcribe its sonic properties into precise sheet music notation.
+Although a waveform might have a limited number of sheet music representations that accurately encapsulate its musical components, a single sheet music composition can be performed infinitely using various instruments, voices, tempos, and interpretations.
+The distinct tonal quality of a waveform is significantly influenced by the specific instrument or production technology employed in its creation, complicating the transcription of its sonic properties into precise sheet music notation.
 
-Additionally, this unique tonal quality is represented by high-level natural language concepts that belong to a rich cultural and sociological tradition.
+Moreover, this distinct tonal quality is represented by high-level natural language concepts embedded within a rich cultural and sociological tradition.

### 2023-04-13 introduction/Subsections/Introduction.tex
Updates from Overleaf

--- 2023-03-29 introduction/Subsections/Introduction.tex
@@
 
-It is worth mentioning that there has been a significant shift in this tendency on retrieval tasks in the symbolic and musicological domain, such as powerful open-source analysis frameworks \cite{ScottCuthbertChristopherArizaMusic21:Data}, MIDI to proper sheet music syntax \cite{Suzuki2021ScoreRepresentation}, projective orchestration \cite{Crestel2018AOrchestration}, or automatic lead sheet generation \cite{WeilAutomaticSignals} to name a few.
+\subsubsection{Bridging the gap}
+
+It is worth mentioning that there has been a significant shift in this tendency on retrieval tasks in the symbolic and musicological domain, such as powerful open-source analysis frameworks for the symbolic domain \cite{ScottCuthbertChristopherArizaMusic21:Data}, MIDI to good sheet music "human" syntax \cite{Suzuki2021ScoreRepresentation}, projective orchestration \cite{Crestel2018AOrchestration}, or automatic lead sheet generation \cite{WeilAutomaticSignals} to name a few.
 
 The reason behind this is non-other but the implementation complexity for such heuristics and abstract fields of study.
-Closing the gap between human perception, environmental and cultural factors, and computational solutions to mimic the formers is an already tackled topic \cite{Large1994ResonanceMeter}\cite{Mullensiefen2003MeasuringJudgments}\cite{Sears2014PerceivingCadence}\cite{Thaut2014HumanPatter}, yet remains a vast open challenge.
+Bridging the gap between human perception \cite{Large1994ResonanceMeter}\cite{Thaut2014HumanPatter}, environmental and cultural factors \cite{Sears2014PerceivingCadence}, and computational solutions to mimic the formers \cite{Mullensiefen2003MeasuringJudgments} is an already tackled topic \cite{Hernandez-Olivan2023SymbolicMethods}, yet remains a vast open challenge.

### 2023-04-13 introduction/Subsections/Motivation.tex
Updates from Overleaf

@@
 I am deeply interested in learning how to retrieve useful embedded information within the music.
-
-\subsection{Beyond Digital Signal Processing (DSP)}
-
-We argue that MIR research needs to incorporate a more balanced approach that considers the interdisciplinary nature of music and the importance of other domains beyond DSP.
-
-Let's pick a core MIR task as a sample to display such complexity: Music Structure Analysis (MSA), an interdisciplinary field that aims to understand the structure of music \cite{Nieto2020Audio-BasedApplications}.
-However, due to subjectivity, ambiguity, and data scarcity, audio-based MSA faces challenges like boundary placement ambiguity and similarity quantification \cite{NietoPerceptualMusic}.
-
-The main principles of MSA were initially defined as homogeneity, novelty, and repetition, with the addition of regularity.
-The checkerboard kernel technique is a simple and effective method for MSA based on the homogeneity principle.
-The kernel, with a checkerboard-like structure, is convolved over the main diagonal of a Self-Similarity Matrix (SSM) such as $S_{ij}$ is the similarity between time frames $i$ and $j$, $\vec{x}_i$ is the vector representation of time frame $i$, and $\left| \vec{x}_i \right|$ is the Euclidean norm of vector $\vec{x}_i$.
-The dot product of two vectors $\vec{x}_i$ and $\vec{x}_j$ is denoted by $\vec{x}_i \cdot \vec{x}_j$.
-
-\input{introduction/subsections/equations/SSM equation}
-
-This yields a novelty curve highlighting sudden changes in the selected musical features from which to extract the segment boundaries.
-
-\input{introduction/subsections/equations/Novelty equation}
-
-Mathematical operations are used on predefined principles such as homogeneity and repetition to analyze a musical structure.
-It analyzes features extracted from a musical signal and identifies peaks in a novelty curve to extract segment boundaries.
-In contrast, human aural skills rely on the perception and interpretation of music by human listeners based on cultural and academic background.
-They can capture subtle nuances of musical structure, but those still are subjective and can vary across listeners.
-
-Combining technical tasks, aural skills, and music perception is challenging due to the complexity and subjectivity of musical perception, discrepancies between the features extracted by DSP techniques and the features perceived by humans, and the variability of musical signals and individual differences in musical perception.
-
-Purely mathematical approaches may not always reflect how humans perceive music and may not capture the subtle variations in timing or harmonic relationships critical to musical perception.
-Variability in musical signals due to instrumentation, genre, and performance style further complicates the development of these techniques that can be generalized to different musical contexts.
 
@@
 The article proposes a new approach to mesostructural audio modeling, which involves a differentiable arpeggiator and time-frequency scattering.
-The article also discusses the need for a time-invariant and multiscale differentiable time-frequency model of similarity at the level of both local spectra and spectrotemporal modulations.
+The report also discusses the need for a time-invariant and multiscale differentiable time-frequency model of similarity at the level of both local spectra and spectrotemporal modulations.
+
+\subsection{Beyond Digital Signal Processing (DSP)}
+
+We argue that MIR research needs to incorporate a more balanced approach that considers the interdisciplinary nature of music and the importance of other domains beyond DSP.
+
+\subsection{Sample MIR task}
+
+Let's pick a core MIR task as a sample to display such complexity: Music Structure Analysis (MSA), an interdisciplinary field that aims to understand the structure of music \cite{Nieto2020Audio-BasedApplications}.
+However, due to subjectivity, ambiguity, and data scarcity, audio-based MSA faces challenges like boundary placement ambiguity and similarity quantification \cite{NietoPerceptualMusic}.
+
+The main principles of MSA were initially defined as homogeneity, novelty, and repetition, with the addition of regularity.
+The checkerboard kernel technique is a simple and effective method for MSA based on the homogeneity principle.
+The kernel, with a checkerboard-like structure, is convolved over the main diagonal of a Self-Similarity Matrix (SSM) such as $S_{ij}$ is the similarity between time frames $i$ and $j$, $\vec{x}_i$ is the vector representation of time frame $i$, and $\left| \vec{x}_i \right|$ is the Euclidean norm of vector $\vec{x}_i$.
+The dot product of two vectors $\vec{x}_i$ and $\vec{x}_j$ is denoted by $\vec{x}_i \cdot \vec{x}_j$.
+
+\input{introduction/subsections/equations/SSM equation}
+
+This yields a novelty curve highlighting sudden changes in the selected musical features from which to extract the segment boundaries.
+
+\input{introduction/subsections/equations/Novelty equation}
+
+Mathematical operations are used on predefined principles such as homogeneity and repetition to analyze a musical structure.
+It explores features extracted from a musical signal and identifies peaks in a novelty curve to extract segment boundaries.
+In contrast, human aural skills rely on the perception and interpretation of music by human listeners based on cultural and academic background.
+They can capture subtle nuances of musical structure, but those still are subjective and can vary across listeners.
+
+Combining technical tasks, aural skills, and music perception is challenging due to the complexity and subjectivity of musical perception, discrepancies between the features extracted by DSP techniques and the features perceived by humans, and the variability of musical signals and individual differences in musical perception.
+
+Purely mathematical approaches may not always reflect how humans perceive music and may not capture the subtle variations in timing or harmonic relationships critical to musical perception.
+Variability in musical signals due to instrumentation, genre, and performance style further complicates the development of these techniques that can be generalized to different musical contexts.

### 2023-04-13 introduction/Subsections/Objectives.tex
Updates from Overleaf

@@
 This work aims to uncover a generalization of the fundamental tonal-working structure of western-tradition music by learning and embedding space used to facilitate its application in downstream MIR tasks.
-Understanding how music is organized and composed is critical, and music theory plays a vital role.
 
@@
 
-Given a music piece $M$, we aim to learn a single embedding, $e(M)$, simultaneously capturing the underlying content (melody, harmony, and critical, holistic elements) and the production aspects.
-The embedding space should be structured so that similar content and production features are clustered together, effectively isolating the two aspects.
+Given a music piece $M$, we aim to learn a single embedding, $e(M)$, simultaneously capturing the underlying content (melody, harmony, critical, holistic elements) and the production aspects.
+The embedding space should be structured so that similar content and production features are clustered together, effectively isolating the two elements.
 Formally, our objective is to learn the embedding function $e(M)$ such that:
@@
 
+\subsection{Applications}
 %%%%%%%%%%%%%%%%%%%%%%%%

### 2023-04-13 methods/subsections/experiment setup and hyperparameter tuning.tex
Updates from Overleaf

@@
 A blog post that discusses a recipe for training neural networks.
-The author of the blog post tweeted about common mistakes people make when training neural nets and the post aims to expand on those mistakes by explaining how to avoid them through a particular process.
+The author of the blog aims to expand on common mistakes people make when training neural nets by explaining how to avoid them through a particular process.
 Andrej Karpathy notes that there is often a gap between understanding the technical aspects of a neural network and achieving state-of-the-art results.
+
+\input{figures/neural networks/dropout}

### 2023-04-13 methods/subsections/machine learning.tex
Updates from Overleaf

@@
 
+%NN
+\input{figures/neural networks/Network_graph}
+
 In a more technical description, an ANN consists of an input layer, one or more hidden layers, and an output layer.
@@
 
-%NN
-\input{figures/neural networks/Network_graph}
-
 %Multi-layer_NN
@@
 \section{Deep Learning (DL)}
+
+Deep learning is a machine learning subfield that utilizes deep neural networks to learn hierarchical data representations automatically.
+These networks handle complex, high-dimensional data across domains such as computer vision and natural language processing.
+Their effectiveness stems from their nonlinear modeling capabilities and scalability with large datasets.
+
+A core algorithm in deep learning is backpropagation which efficiently computes gradients of the loss function concerning the network's parameters.
+It involves a two-step process: (1) forward pass, where input data propagates through the network to generate predictions, and (2) backward pass, where the error between predictions and ground truth is calculated and propagated back through the network.
+This process updates the network's parameters using gradient descent, which minimizes the loss function and improves the model's performance.
 
@@
 \input{figures/neural networks/convolution}
+%Single CNN
+\input{figures/neural networks/Single_CNN}
 
@@
 A joint pooling operation is the max-pooling, which can be defined as follows: given an input matrix $I$ and a pooling window of size $m \times n$, the max-pooling operation selects the maximum value within each non-overlapping $m \times n$ region of the input matrix.
-This operation effectively reduces the input's dimensions while retaining the most essential information in each region.
+This operation effectively reduces the input's dimensions while retaining the essential information in each area.
 \vspace*{3mm}
 
-\item \textbf{Fully connected layers:} These layers connect every neuron in one layer to every neuron in another, allowing the network to learn non-linear combinations of the features learned in the previous layers.
+%Single pooling layer
+\input{figures/neural networks/Single_Pooling_Layer}
+
+\item \textbf{Fully connected layers:} These layers connect every neuron in one layer to every neuron in another, allowing the network to learn non-linear combinations of the features discovered in the previous layers.
 Mathematically, a fully connected layer can be represented as $Y = XW + b$, where $X$ is the input matrix, $W$ is the weight matrix, $b$ is the bias vector, and $Y$ is the output matrix.
@@
 
-%CNN
-\input{figures/neural networks/CNN_diagram}
-
-%Single CNN
-\input{figures/neural networks/Single_CNN}
-
-%Single pooling layer
-\input{figures/neural networks/Single_Pooling_Layer}
+%Colour CNN
+\input{figures/neural networks/colour CNN}
 

### 2023-04-13 methods/subsections/model architecture and training strategy.tex
Updates from Overleaf

@@
 Piaget's theory of cognitive development \cite{Piagets_Theory_of_Cognitive_Development} posits that children acquire knowledge from sensory and motor experiences in their early stages, from birth to around 18 months.
-This period referred to as the \textit{sensorimotor stage}, sees the emergence of early representational thought through basic actions such as sucking, grasping, looking, and listening.
+This period, called the \textit{sensorimotor stage}, sees the emergence of early representational thought through basic actions such as sucking, grasping, looking, and listening.
 As children progress through different developmental stages until adolescence and adulthood, their reasoning progressively moves toward abstract ideas and deductive logic.
 Schemas, higher-order cognitive structures hypothesized to underlie many aspects of human knowledge and skill, emerge during this process, which Piaget interprets through an equilibration mechanism that balances new information with old knowledge.
-This mechanism involves \textit{assimilation} and \textit{accommodation}, which entail taking in new information to fit pre-existing schemas and modifying existing schemas resulting from new information.
-In the context of learning, complex structures are based on simpler ones, and transfer of learning occurs when dynamic structures capable of generalization are created.
+This mechanism involves \textit{assimilation} and \textit{accommodation}, which entail taking in further information to fit pre-existing schemas and modifying existing schemas resulting from the latest news.
+In the context of learning, complex structures are based on simpler ones, and knowledge transfer occurs when dynamic systems capable of generalization are created.
 \cite{audioselfsupsurvey}
@@
 
-Contrastive Self-Supervised Learning of Musical Representations (CSSLMR) is an approach that combines the principles of Self-Supervised Learning (SSL) and Contrastive Learning of Musical Representations (CLMR) to learn discriminative and valuable representations of music without relying on explicit labels.
+Contrastive Self-Supervised Learning of Musical Representations (CSSLMR) is an approach that combines the principles of Self-Supervised Learning (SSL) \cite{audioselfsupsurvey} and Contrastive Learning of Musical Representations (CLMR) \cite{CLMR2021} to learn discriminative and valuable representations of music without relying on explicit labels.
 By leveraging the structure and content of music and contrasting different augmentations or transformations of the same musical piece against randomly (or not) selected pieces, CSSLMR models can effectively capture the underlying structure and known invariance in the data.
@@
 \item \textbf{Data Augmentation:} Create different augmentations or transformations of the same musical piece as positive pairs and use other randomly selected pieces as antagonistic pairs.
-\item \textbf{Contrastive Learning:} Train a neural network to minimize a contrastive loss function, which encourages the model to produce similar representations for positive pairs and dissimilar representations for antagonistic pairs.
-\item\textbf{Latent Representation:} Utilize the learned representations for various MIR downstream tasks, such as music genre classification or music similarity, both in the symbolic and time domains.
+\item \textbf{Contrastive Learning:} Train a neural network to minimize a contrastive loss function, encouraging the model to produce similar representations for positive and dissimilar representations for antagonistic pairs.
+\item\textbf{Latent Representation:} Utilize the learned representations for various MIR downstream tasks, such as music genre classification or similarity, both in the symbolic and time domains.
 \end{enumerate}
@@
 \begin{enumerate}
-\item Reduces dependency on labeled data: by leveraging inductive bias (assuming a known invariance across the data samples), CSSL can learn from large amounts of unlabeled data.
-\item Encourages feature extraction: CSSLMR promotes learning useful and discriminative features or representations
+\item Reduces dependency on labeled data: by leveraging inductive bias (assuming a general invariance across the data samples), CSSL can learn from large amounts of unlabeled data.
+\item Encourages feature extraction: CSSLMR promotes learning practical and discriminative representations.
 \end{enumerate}
@@
 We propose using a Triple Siamese Network to train a model for music similarity retrieval \cite{contentmusicsimtriplet2020}.
-Specifically, we aim to minimize the loss function between the anchor, positive, and negative samples by using online triplet mining \cite{Sikaroudi2020OfflinePatches}.
+Specifically, we aim to minimize the loss function between an anchor, a positive, and a negative sample by using online triplet mining \cite{Sikaroudi2020OfflinePatches}.
 
+Using the proposed triple siamese network and online triplet mining, we aim to train a model that can effectively distinguish between similar and dissimilar samples while considering their underlying composition and production texture.
+
+\subsection{Encoder}
+
+\subsection{Data augmentation and transformation pipeline}
 The positive samples are created by transforming and augmenting the original samples while preserving their perceptual underlying musical language.
@@
 This is achieved using random segment selection, time-domain filtering, and frequency-domain masking.
-The goal is to maintain the production texture of the samples while disrupting their underlying composition.
+The goal is to retain the texture production of the samples while disrupting their underlying composition.
 
-Using the proposed triple siamese network and online triplet mining, we aim to train a model that can effectively distinguish between similar and dissimilar samples while considering their underlying composition and production texture.
+\subsection{Loss function}
 

### 2023-04-13 preface/preface.tex
Updates from Overleaf

@@
-\addcontentsline{toc}{chapter}{Acknowledgement}
+%\addcontentsline{toc}{chapter}{Acknowledgement}
 \begin{preface}
@@
 Music and science have always been my two greatest passions.
-When the opportunity to work at Epidemic Sound presented itself, it was as if the universe had conspired to bring my interests together, offering me the chance to explore the fascinating Music Information Retrieval (MIR) field.
+When the opportunity to work at Epidemic Sound presented itself, it was as if the universe had conspired to bring my interests together, offering me the chance to explore the fascinating field of MIR from an industrial perspective.
 With the support and encouragement of my loved ones, I took a leap of faith and moved to Stockholm to embark on this exciting journey.

### 2023-04-16 figures/my model/SampleCNN.tex
Updates from Overleaf

\begin{tikzpicture}[
  node distance=0.5cm,
  block/.style={draw, rectangle, fill=blue!20, text width=1.5cm, align=center, minimum height=1cm},
  arrow/.style={->, >=stealth, line width=0.5mm}
]

% Input
\node (input) [block] {Input};

% Conv 1
\node (conv1) [block, right=of input] {Conv1D\\128};
\draw[arrow] (input) -- (conv1);

% BatchNorm 1 and ReLU 1
\node (bn1) [block, right=of conv1] {BatchNorm\\ReLU};
\draw[arrow] (conv1) -- (bn1);

% Hidden Layers
\node (hidden1) [block, right=of bn1] {Hidden Layer 1};
\draw[arrow] (bn1) -- (hidden1);

\node (hidden2) [block, right=of hidden1] {Hidden Layer 2};
\draw[arrow] (hidden1) -- (hidden2);

\node (hidden3) [block, right=of hidden2] {Hidden Layer 3};
\draw[arrow] (hidden2) -- (hidden3);

\node (dots) [right=of hidden3] {$\cdots$};
\draw[arrow] (hidden3) -- (dots);

% Conv N
\node (convN) [block, right=of dots] {Conv1D\\512};
\draw[arrow] (dots) -- (convN);

% BatchNorm N and ReLU N
\node (bnN) [block, right=of convN] {BatchNorm\\ReLU};
\draw[arrow] (convN) -- (bnN);

% Average Pooling
\node (avgpool) [block, right=of bnN] {Avg Pool};
\draw[arrow] (bnN) -- (avgpool);

% Dropout (optional)
\node (dropout) [block, right=of avgpool, dashed] {Dropout (optional)};
\draw[arrow, dashed] (avgpool) -- (dropout);

% Fully Connected
\node (fc) [block, right=of dropout] {Linear\\Out\_dim};
\draw[arrow] (dropout) -- (fc);

\end{tikzpicture}

### 2023-04-16 figures/neural networks/colour CNN.tex
Updates from Overleaf

@@
     (5.6,-2.0) rectangle++ (1.8,4.0);
-  \node[right=19,above=1,align=center,myorange!60!black] at (3.1,1.8) {convolutional\\[-0.2em]layers};
-  \node[above=1,align=center,myblue!60!black] at (6.5,1.9) {fully-connected\\[-0.2em]hidden layers};
+  \node[right=19,above=1,align=center,myorange!60!black] at (3.4,1.9) {convolutional\\[-0.2em]layers};
+  \node[above=1,align=center,myblue!60!black] at (6.3,1.9) {fully-connected\\[-0.2em]hidden layers};
 

### 2023-04-16 methods/subsections/model architecture and training strategy.tex
Updates from Overleaf

@@
 \subsection{Encoder}
+\subsubsection{SampleCNN}
 
-\subsection{Data augmentation and transformation pipeline}
+The SampleCNN model takes in 1D input data with a single channel.
+The first layer is a 1D convolutional layer with a kernel size of 3, stride of 3, and 128 output channels.
+It is followed by batch normalization and ReLU activation.
+
+After the initial layer, there are 9 hidden layers with varying kernel sizes, strides, and channels according to the values specified in self.strides and self.hidden. Each hidden layer consists of:
+
+A 1D convolutional layer with the specified number of input and output channels, kernel size, stride of 1, and padding of 1.
+Batch normalization.
+ReLU activation.
+Max pooling with kernel size and stride equal to the stride value of the current layer.
+After the hidden layers, there's another 1D convolutional layer with 512 input channels, 512 output channels, kernel size of 3, stride of 1, and padding of 1.
+This is followed by batch normalization and ReLU activation.
+
+The output of the final convolutional layer is passed through an average pooling operation across the temporal dimension (dim=2).
+
+If the model is in supervised mode, dropout with a rate of 0.5 is applied.
+
+Finally, a linear layer with 512 input features and 128 output dimension features is applied to generate the embeddings.
+
+\input{figures/my model/SampleCNN}
+
+Layer 1:
+
+Input channels: 1
+Output channels: 128
+Layer 2:
+
+Input channels: 128
+Output channels: 128
+Layer 3:
+
+Input channels: 128
+Output channels: 128
+Layer 4:
+
+Input channels: 128
+Output channels: 128
+Layer 5:
+
+Input channels: 128
+Output channels: 256
+Layer 6:
+
+Input channels: 256
+Output channels: 256
+Layer 7:
+
+Input channels: 256
+Output channels: 256
+Layer 8:
+
+Input channels: 256
+Output channels: 256
+Layer 9:
+
+Input channels: 256
+Output channels: 256
+Layer 10:
+
+Input channels: 256
+Output channels: 256
+Layer 11:
+
+Input channels: 256
+Output channels: 256
+Layer 12:
+
+Input channels: 256
+Output channels: 512
+Layer 13:
+
+Input channels: 512
+Output channels: 512
+Layer 14:
+
+Input channels: 512
+Output channels: 128
+
+\subsection{Audio augmentation and transformation pipeline}
 The positive samples are created by transforming and augmenting the original samples while preserving their perceptual underlying musical language.
@@
 $d(\cdot, \cdot)$ is the Euclidean distance function
-$m$ is the margin; in this case, it is set to 0.2 by default
+$m$ is the margin; commonly set to 0.2 by default
 The forward method computes the triplet loss as follows:

### 2023-04-16 MasterThesis.tex
Updates from Overleaf

@@
 
+\usepackage{amsfonts}
+\usepackage{graphicx}
+
 \usepackage[utf8]{inputenc}
@@
 \usetikzlibrary{matrix, positioning}
+\usetikzlibrary{shapes,arrows,positioning}
 
@@
   Uncovering underlying musical content in the temporal domain \\
-  \small Leveraging deep learning, inductive bias, and music aural skills to learn embedding spaces from raw waveforms with applications to MIR downstream tasks}
+  \small Leveraging deep learning, inductive bias, and aural music skills to learn embedding spaces from raw waveforms with applications to MIR downstream tasks}
 

### 2023-04-16 introduction/Subsections/Motivation.tex
Updates from Overleaf

@@
 As a music lover, professional musician, and connoisseur, I am interested in gaining a deeper understanding of the fundamental building of musical composition, the various techniques used to create musical works, and capturing underlying relationships among them.
-I am deeply interested in learning how to retrieve useful embedded information within the music.
+I am deeply interested in learning how to retrieve useful embedded information within music.
 
@@
 
-I have consistently been inspired by musicians and researchers who strive to uncover musical ground truth within the existing tonal paradigm, such as Heinrich Schenker \cite{}, or by challenging it, as exemplified by George Russell \cite{LydianRussell}.
+I have consistently been inspired by musicians and researchers who strive to uncover musical ground truth within the existing tonal paradigm, such as Heinrich Schenker, or by challenging it, as exemplified by George Russell \cite{LydianRussell}.
 Both approaches aim to identify abstract concepts that reinforce or disrupt the tonal foundation.

### 2023-04-16 methods/subsections/machine learning.tex
Updates from Overleaf

@@
 \item \textbf{Convolutional layers:} These layers apply a convolution operation to the input data.
-The convolutional layers are designed to effectively learn local patterns and features in the audio data \footnote{For a visual explanation of convolution, see this video: \url{https://youtu.be/KuXjwB4LzSA}}.
+The convolutional layers are designed to effectively learn local patterns and features in the audio data \footnote{For a visual explanation and further understanding of the operation convolution, see this video: \url{https://youtu.be/KuXjwB4LzSA}}.
 
@@
 Mathematically, a fully connected layer can be represented as $Y = XW + b$, where $X$ is the input matrix, $W$ is the weight matrix, $b$ is the bias vector, and $Y$ is the output matrix.
-The nonlinearity is introduced through the activation function, which is applied element-wise to the output matrix, such as $Y' = f(Y)$, where $f$ represents the activation function and $Y'$ is the transformed output matrix.
 \vspace*{3mm}

### 2023-04-16 methods/subsections/model architecture and training strategy.tex
Updates from Overleaf

@@
 \section{Model architecture and training strategy}
-Piaget's theory of cognitive development \cite{Piagets_Theory_of_Cognitive_Development} posits that children acquire knowledge from sensory and motor experiences in their early stages, from birth to around 18 months.
-This period, called the \textit{sensorimotor stage}, sees the emergence of early representational thought through basic actions such as sucking, grasping, looking, and listening.
+Piaget's theory of cognitive development \cite{Huitt2003PiagetsDevelopment} posits that children acquire knowledge from sensory and motor experiences in their early stages, from birth to around 18 months.
+This period called the \textit{sensorimotor stage}, sees the emergence of early representational thought through basic actions such as sucking, grasping, looking, and listening.
 As children progress through different developmental stages until adolescence and adulthood, their reasoning progressively moves toward abstract ideas and deductive logic.

### 2023-04-19 discussion/discussion.tex
Updates from Overleaf

--- 2023-01-14 results/results.tex
@@
-\chapter{Results}
+\chapter{Discussion}
 
-This is an example paragraph. As you can see, the main text uses a font size of 12 pt and a line spacing of 1.5. Neither the paragraphs nor the first lines of paragraphs should be indented.
+XXXXXXXXXXX
 
-There is no very strict page limit.
-Your number of pages will be strongly influenced by the size and total number of your figures and tables.
-It is recommended staying within 30-50 pages.
-Do not try to fill as many pages as you can.
-Longer theses are not necessarily of higher quality and of more non-redundant content than shorter theses.
-Certainly, a master thesis of 15 pages is too short, and a master thesis of 100 pages is too long.
+\section{Discussion}
 
-\section{Tables and graphics}
+XXXXXXXXXXX
 
-This is an example paragraph. As you can see, the main text uses a font size of 12 pt and a line spacing of 1.5. Neither the paragraphs nor the first lines of paragraphs should be indented.
+\section{Conclusions}
 
-There is no very strict page limit.
-Your number of pages will be strongly influenced by the size and total number of your figures and tables.
-It is recommended staying within 30-50 pages.
-Do not try to fill as many pages as you can.
-Longer theses are not necessarily of higher quality and of more non-redundant content than shorter theses.
-Certainly, a master thesis of 15 pages is too short, and a master thesis of 100 pages is too long.
-
-\begin{figure}[!ht]
-\includegraphics[clip,width=\columnwidth]{Figures/PlotTimeSeriesResult}% 
-\caption{This is an example of a figure and its caption.}
-\label{fig:timeseries}
-\end{figure}
-
-\begin{table}[!ht]
-\renewcommand{\arraystretch}{1.50}
-\caption{This is an example of a table and its caption.}
-\label{tablePCA}
-\centering
-\begin{tabular}{| c | c |}
-\hline
-\bfseries PCA & \bfseries Residual mean (in absolute values) \\
-\hline\hline
-Original PCA & 0.1267  \\
-\hline
-PCA on Centroid 1 & 0.1249\\
-\hline
-PCA on Centroid 2 & 0.1214  \\
-\hline
-\end{tabular}
-\end{table}
+XXXXXXXXXXX
 

### 2023-04-19 introduction/Subsections/Motivation.tex
Updates from Overleaf

@@
 
-\section{About music aural skills and high-level perceptual concepts}
+\subsection{About music aural skills and high-level perceptual concepts}
 
@@
 
-Schenkerian Analysis, devised by Austrian music theorist Heinrich Schenker, explores tonal music's underlying structure by concentrating on the hierarchical relationships between pitches.
-Based on the idea that all tonal music shares a fundamental structure called "Ursatz" or "basic shape," the method identifies the stepwise descending line (Urlinie) and bass arpeggiation (Bassbrechung).
-Schenkerian Analysis simplifies a musical piece to its core elements, allowing analysts to examine how different layers contribute to the overall structure.
-Key concepts include prolongational levels, harmony, counterpoint, voice-leading, and Ursatz (fundamental structure).
-Although criticized for reducing all tonal works to a few background structures, Schenker emphasizes the importance of individual elaboration in determining a work's identity and meaning.
+Schenkerian Analysis, developed by Austrian music theorist Heinrich Schenker, investigates the underlying structure of tonal music by focusing on the hierarchical relationships between pitches.
+This analytical approach is founded on the premise that all tonal music shares a fundamental structure known as "Ursatz" or "basic shape." The method identifies a piece's stepwise descending line (Urlinie) and bass arpeggiation (Bassbrechung), simplifying it to its essential elements and examining how different layers contribute to the overall structure.
+Central concepts in Schenkerian Analysis include prolongation levels, harmony, counterpoint, voice-leading, and Ursatz (fundamental structure).
+Despite criticism for reducing all tonal works to a limited number of background structures, Schenker highlights the significance of individual elaboration in determining a piece's identity and meaning.
 
-Anstieg (Initial Ascent): Ascending motion leading to the primary tone of the fundamental line.
-Arpeggiation (Brechung): Elementary elaboration of a harmony.
-Background (Hintergrund): The structural level of the fundamental structure.
-Bass Arpeggiation (Bassbrechung): Bass pattern I-V-I forms the harmonic content of the background of tonal musical pieces.
-Chord of Nature (Klang): The complex sound of the first five harmonic series notes suggests a model for the major triad.
-Diminution: The process by which an interval formed by notes of longer value is expressed in notes of smaller value.
-Foreground (Vordergrund): The surface level of musical structure in Schenkerian analysis.
-Fundamental Line (Urlinie): The melodic aspect of the fundamental structure, a stepwise descent from one of the triad notes to the tonic.
-Middleground (Mittelgrund): An intermediate structural level between the background and foreground in Schenkerian analysis.
-Prolongation (Auskomponierung): The process in tonal music through which a pitch, interval, or consonant triad can govern music spans when not physically sounding.
-Structural Level (Schicht): Refers to the different levels of musical structure in Schenkerian analysis, including background, middle-ground, and foreground.
-Tonal Space: A general principle of Schenkerian analysis where intervals between the notes of the tonic triad form a tonal space filled with passing and neighbor notes.
-Unfolding (Ausfaltung): The transformation of a single chord into a horizontal succession.
-Voice Leading: The study of the principles that govern the progression of the component voices of the composition both separately and in combination.
-The glossary also includes related articles, references, and external links for further reading and understanding Schenkerian analysis.
+While such analysis is designed for the symbolic domain, we argue that musical abstraction is also feasible in the audio time domain.
+In this section, we explore the application of Schenkerian Analysis principles to the Music Information Retrieval (MIR) domain by examining the foreground, middle-ground, and background levels of musical structure as follows:
 
-%%%%%%%%%%%%%
-%MESOSTRUC
-%%%%%%%%%%%%%
+\begin{itemize}
+\item \textbf{Foreground}: The surface level of a musical composition, consisting of the notes, rhythms, and articulations directly perceived by the listener, representing the most detailed level of the musical structure.
 
-Mesostructures \cite{Mesostructures2023} are intermediate levels of articulation between waveshapes' microstructure and musical forms' macrostructure.
+\item \textbf{Middle-ground and mesostructures}: An intermediate level of analysis focusing on essential structural elements such as harmonic progressions, thematic materials, and voice-leading reductions that contribute to the overall composition.
+In the MIR domain, this level can also be understood as mesostructure.
+Mesostructures are intermediate levels of articulation between waveshapes' microstructure and musical forms' macrostructure.
 Examples of mesostructures include melody, arpeggios, syncopation, polyphonic grouping, and textural contrast.
-The article notes that mesostructures have received limited attention in deep learning, as current models only focus on microstructures.
-The article proposes a new approach to mesostructural audio modeling, which involves a differentiable arpeggiator and time-frequency scattering.
-The report also discusses the need for a time-invariant and multiscale differentiable time-frequency model of similarity at the level of both local spectra and spectrotemporal modulations.
+Mesostructures might have received limited attention in deep learning, as current models only focus on microstructures \cite{Mesostructures2023}.
+
+\item \textbf{Background}: The most abstract level of musical structure, representing the fundamental core consisting of the \textit{Urlinie} and \textit{Bassbrechung}, which serves as the foundation for the entire composition.
+\end{itemize}
+
+By understanding and applying Schenkerian Analysis principles to the MIR domain, we can better understand the complex relationships between different levels of musical structure in the audio time domain, allowing for a more comprehensive analysis of tonal music.
 
@@
 
-\subsection{Sample MIR task}
+\subsubsection{Sample MIR task}
 

### 2023-04-19 introduction/Subsections/Objectives.tex
Updates from Overleaf

@@
 
-In recent years, using neural networks has enabled low-dimensional musical embeddings that capture crucial musical features and allow the computation of content-based similarity between musical passages \cite{}.
+In recent years, using neural networks has enabled low-dimensional musical embeddings that capture crucial musical features and allow the computation of content-based similarity between musical passages \cite{Chen2020LearningRecommendation}\cite{KimLEARNINGLOSS}\cite{Hung2022Feature-informedClassification}\cite{WonEmotionStories}.
 By acquiring an embedding function $f(x) \in \mathbb{R}^d$ that maps a given course $x$ to a vector in the real space $\mathbb{R}^d$, we can measure the similarity between two musical passages using the Euclidean distance, as represented by the formula $D_{i,j} = ||f(x_i) - f(x_j)||^2$.
@@
 A self-supervised model that learns an embedding space to retrieve musical content from raw audio signals could have several potential applications and downstream tasks in MIR. Here are some examples:
-
-\begin{enumerate}
-\item Music recommendation: The learned embedding space can retrieve similar musical content and recommend songs or playlists to users based on their listening history or preferences.
-\item Music classification: The embedding space can classify songs based on genre, mood, or other musical characteristics.
-\item Music transcription: The learned embedding space can transcribe audio signals into symbolic music notation, such as MIDI or sheet music.
-\item Music generation: The embedding space can generate new musical content by sampling from the learned distribution of musical features.
-\item Music synchronization: The discovered embedding space can synchronize audio and visual content in applications such as music videos or virtual reality experiences.
-\item Music search: The embedding space can search for specific musical content based on high-level perceptual concepts and the relationships they have among them
-\end{enumerate}

### 2023-04-19 methods/subsections/experiment setup and hyperparameter tuning.tex
Updates from Overleaf

@@
 
-For finetuning and improving the model's behavior, we followed \href{http://karpathy.github.io/2019/04/25/recipe/}{\textit{A Recipe for Training Neural Networks}} \cite{AndrejKarpathyHttp://karpathy.github.io/2019/04/25/recipe/} by \href{https://karpathy.ai/}{Andrej Karpathy} \cite{AndrejKarpathyHttps://karpathy.ai/}.
+Musically motivated NN \cite{musicmotivCNN}.
+
+For finetuning and improving the model's behavior, we followed \href{http://karpathy.github.io/2019/04/25/recipe/}{\textit{A Recipe for Training Neural Networks}} \cite{AndrejKarpathyHttp://karpathy.github.io/2019/04/25/recipe/} by Andrej Karpathy.
 A blog post that discusses a recipe for training neural networks.
@@
 Andrej Karpathy notes that there is often a gap between understanding the technical aspects of a neural network and achieving state-of-the-art results.
-
-\input{figures/neural networks/dropout}

### 2023-04-19 methods/subsections/machine learning.tex
Updates from Overleaf

@@
 \section{Introduction}
-Machine Learning (ML), particularly Deep Learning, has significantly advanced the MIR field by enabling automatic feature learning, improving classification and analysis tasks, and facilitating novel applications like music generation and source separation.
-Adopting musically motivated neural network architectures \cite{musicmotivCNN} blends musical concepts and perceptual approaches and use this knowledge to analyze and understand music in a way that goes beyond traditional music analysis techniques.
+
+In this chapter, we present the methodology employed in this study.
+
+We provide an overview of the Machine Learning (ML) and Deep Learning techniques that have played a pivotal role in advancing the MIR field.
+We then discuss the importance of feature extraction and selection in MIR and how automatic feature learning has facilitated the development of more robust models.
+
+Subsequently, we delve into the concept of musically motivated neural network architectures, which incorporate domain-specific knowledge and musical ideas into the design of neural networks.
+We explore techniques proposed in the literature for blending musical concepts and perceptual approaches.
+
+We then outline the specific MIR tasks that our study focuses on and discuss the evaluation metrics used to assess the performance of the proposed models.
+Finally, we present the experimental setup, including the datasets used for training and validation, the preprocessing steps, and the training parameters.
+
+Throughout this chapter, we aim to provide a comprehensive understanding of the methodology employed in our research, laying the foundation for the presentation and discussion of the results in the following chapters.
 

### 2023-04-19 methods/subsections/model architecture and training strategy.tex
Updates from Overleaf

@@
 The SampleCNN model takes in 1D input data with a single channel.
-The first layer is a 1D convolutional layer with a kernel size of 3, stride of 3, and 128 output channels.
+The first layer is a 1D convolutional layer with a kernel size of 3, a stride of 3, and 128 output channels.
 It is followed by batch normalization and ReLU activation.
 
-After the initial layer, there are 9 hidden layers with varying kernel sizes, strides, and channels according to the values specified in self.strides and self.hidden. Each hidden layer consists of:
+After the initial layer, there are nine hidden layers with varying kernel sizes, strides, and channels. Each hidden layer consists of:
 
-A 1D convolutional layer with the specified number of input and output channels, kernel size, stride of 1, and padding of 1.
-Batch normalization.
-ReLU activation.
-Max pooling with kernel size and stride equal to the stride value of the current layer.
-After the hidden layers, there's another 1D convolutional layer with 512 input channels, 512 output channels, kernel size of 3, stride of 1, and padding of 1.
+\begin{itemize}
+    \item A 1D convolutional layer with the specified number of input and output channels, kernel size, a stride of 1, and padding of 1.
+    \item Batch normalization.
+    \item ReLU activation.
+    \item Max pooling with kernel size and stride equal to the stride value of the current layer.
+\end{itemize}
+
+\begin{tabular}{|c|c|c|}
+\hline
+\textbf{Layer} & \textbf{Input Channels} & \textbf{Output Channels} \\
+\hline
+1 & 128 & 128 \\
+\hline
+2 & 128 & 128 \\
+\hline
+3 & 128 & 256 \\
+\hline
+4 & 256 & 256 \\
+\hline
+5 & 256 & 256 \\
+\hline
+6 & 256 & 256 \\
+\hline
+7 & 256 & 256 \\
+\hline
+8 & 256 & 256 \\
+\hline
+9 & 256 & 512 \\
+\hline
+\end{tabular}
+
+After the hidden layers, there's another 1D convolutional layer with 512 input channels, 512 output channels, a kernel size of 3, a stride of 1, and padding of 1.
 This is followed by batch normalization and ReLU activation.
@@
 
-If the model is in supervised mode, dropout with a rate of 0.5 is applied.
+If the model is "supervised", dropout with a rate of 0.5 is applied.
+
+\input{figures/neural networks/dropout}
 
@@
 
-Layer 1:
+\subsection{Audio augmentation and transformation pipeline}
+\subsubsection{Positive sample generation}
+Let $W$ be the input waveform and $W_p$ be the generated positive waveform.
+The pipeline applies a series of audio effects and adds noise with a random SNR.
+Define the following random variables for the effects:
 
-Input channels: 1
-Output channels: 128
-Layer 2:
+\begin{alignat*}{2}
+&gain \sim \text{Uniform}(-12, 0), \quad
+&pitch \sim \text{Uniform}(-1200, 1200), \\
+&reverb\_params \sim \text{Uniform}(0, 100)^3, \quad
+&chorus\_params = \begin{cases}
+\text{Uniform}(0.1, 1.0), & i=1,2, \\
+\text{Uniform}(20, 55), & i=3, \\
+\text{Uniform}(0.1, 0.9), & i=4, \\
+\text{Uniform}(0.1, 2.0), & i=5, \\
+\text{Uniform}(2, 5), & i=6, \\
+\text{Categorical}(\{-s, -t\}), & i=7,
+\end{cases}, \\
+&drive \sim \text{Uniform}(0, 30), \quad
+&stretch \sim \text{Uniform}(0.9, 1.1), \\
+&speed \sim \text{Uniform}(0.9, 1.1), \quad
+&tremolo\_speed \sim \text{Uniform}(0.1, 100), \\
+&tremolo\_depth \sim \text{Uniform}(1, 101), \quad
+&snr\_range \sim \text{Uniform}(12, 100).
+\end{alignat*}
 
-Input channels: 128
-Output channels: 128
-Layer 3:
+For white noise, let $N$ be the noise matrix with dimensions (channels, samples) as $W$. Calculate signal power $P_s$ and noise power $P_n$:
 
-Input channels: 128
-Output channels: 128
-Layer 4:
+\begin{align*}
+&P_s = \sum (W_{ij})^2, \
+&P_n = \sum (N_{ij})^2.
+\end{align*}
 
-Input channels: 128
-Output channels: 128
-Layer 5:
+Calculate the scaling factor $\alpha$ for noise based on the desired SNR:
 
-Input channels: 128
-Output channels: 256
-Layer 6:
+\[
+\alpha = \sqrt{\frac{P_s}{P_n \times 10^{\frac{snr\_range}{10}}}}
+\]
 
-Input channels: 256
-Output channels: 256
-Layer 7:
+Compute the scaled noise matrix $N_s$ and the noisy waveform matrix $W_n$:
 
-Input channels: 256
-Output channels: 256
-Layer 8:
+\begin{align*}
+&N_s = \alpha \times N, \
+&W_n = W + N_s.
+\end{align*}
 
-Input channels: 256
-Output channels: 256
-Layer 9:
+The final positive waveform $W_p$ is obtained with noise added according to the chosen SNR.
+This pipeline enhances the diversity of the positive samples and aims to improve the model's ability to retrieve similar-sounding samples sharing the same underlying musical language.
 
-Input channels: 256
-Output channels: 256
-Layer 10:
+\subsubsection{Negative sample generation}
 
-Input channels: 256
-Output channels: 256
-Layer 11:
+Let $a$ be the original anchor clip and $n$ be the negative clip to be generated. The steps for generating the negative clip $n$ are as follows:
 
-Input channels: 256
-Output channels: 256
-Layer 12:
+\begin{enumerate}
+\item Calculate the length $L_a$ and duration $T_a$ of the anchor clip $a$:
 
-Input channels: 256
-Output channels: 512
-Layer 13:
+$L_a = \text{shape}(a)$, $\quad T_a = \frac{L_a}{f_s}$,
 
-Input channels: 512
-Output channels: 512
-Layer 14:
+where $\text{shape}(a)$ returns the shape of the audio clip, and $f_s$ is the sample rate of the audio.
 
-Input channels: 512
-Output channels: 128
+\item Determine the number of chunks $n_c$ to split the anchor clip into based on a minimum chunk duration $T_c$:
+$$
+n_c = \left\lfloor\frac{T_a}{T_c}\right\rfloor.
+$$
 
-\subsection{Audio augmentation and transformation pipeline}
-The positive samples are created by transforming and augmenting the original samples while preserving their perceptual underlying musical language.
-This is achieved using techniques such as time-stretching, pitch-shifting, and adding noise to the samples.
-By doing so, we aim to enhance the diversity of the positive samples and improve the model's ability to retrieve similar-sounding samples that share the same underlying musical language.
+\item Calculate the minimum and maximum chunk lengths in samples:
+$$
+L_{c,\text{min}} = T_c \times f_s, \quad L_{c,\text{max}} = T_{\text{max}} \times f_s,
+$$
+where $T_{\text{max}}$ is the maximum chunk duration specified in seconds.
 
-On the other hand, the negative samples are created by shuffling and scrambling the original samples while maintaining their production texture.
-This is achieved using random segment selection, time-domain filtering, and frequency-domain masking.
-The goal is to retain the texture production of the samples while disrupting their underlying composition.
+\item Generate $n_c$ chunk lengths $L_{c,1},\ldots,L_{c,n_c}$ as follows:
+$$
+L_{c,i} = \begin{cases}
+L_{c,\text{min}}, & i=1, \\
+\text{randint}(L_{c,\text{min}}, L_{c,\text{max}}), & 1<i<n_c, \\
+L_a - \sum_{j=1}^{i-1} L_{c,j}, & i=n_c.
+\end{cases}
+$$
+
+\item Split the anchor clip into chunks $c_1,\ldots,c_{n_c}$ based on the lengths $L_{c,1},\ldots,L_{c,n_c}$:
+$$
+c_i = a[..., s_i : s_i + L_{c,i}], \quad S_c = \text{cumsum}([0] + [L_{c,1},\ldots,L_{c,n_c-1}]), \quad s_i = S_c[i], \quad i=1,\ldots,n_c.
+$$
+
+\item Shuffle the resulting list of chunks randomly to obtain the reordered chunks $c'_1,\ldots,c'_{n_c}$:
+$$
+c' = \text{shuffle}([c_1,\ldots,c_{n_c}]).
+$$
+
+\item Concatenate the shuffled chunks $c'_1,\ldots,c'_{n_c}$ to create the negative clip $n$:
+$$
+n = \text{concatenate}(c').
+$$
+
+\end{enumerate}
 
@@
 
-Implements the triplet loss function, commonly used for learning embeddings in metric learning problems.
 The triplet loss aims to ensure that the distance between an anchor and a positive sample (both from the same class) is smaller than the distance between the anchor and a negative sample (from a different class) by a margin.

### 2023-04-19 introduction/Subsections/Assumptions.tex
Updates from Overleaf

@@
 
-This thesis posits that high-level musical concepts manifest over time and remain invariant to specific attributes such as tonal quality, tempo, key, orchestration, signal noise, and others.
-This is akin to a sheet music composition being performed in myriad ways using diverse instruments and styles while preserving its core essence.
+This thesis posits that high-level musical concepts manifest over time and remain invariant to specific attributes such as tonal quality, tempo, key, orchestration, signal noise, etc.
+This is akin to a sheet music composition performed in myriad ways using diverse instruments and styles while preserving its essence.
 
 Abstract features, such as melody, harmony, rhythm, tempo, form, and expression, can be identified irrespective of waveform or production style.
-This approach offers an objective and comprehensive insight into a piece's musical content and meaning, analogous to how analyzing sheet music unveils a composition's underlying structure and intent.
+This approach offers objective and comprehensive insight into a piece's musical content and meaning, analogous to how analyzing sheet music unveils a composition's underlying structure and intent.
 
-Although a waveform might have a limited number of sheet music representations that accurately encapsulate its musical components, a single sheet music composition can be performed infinitely using various instruments, voices, tempos, and interpretations.
+Although a waveform might have limited sheet music representations that accurately encapsulate its musical components, a single sheet music composition can be performed infinitely using various instruments, voices, tempos, and interpretations.
 The distinct tonal quality of a waveform is significantly influenced by the specific instrument or production technology employed in its creation, complicating the transcription of its sonic properties into precise sheet music notation.
@@
 Moreover, this distinct tonal quality is represented by high-level natural language concepts embedded within a rich cultural and sociological tradition.
+
+\begin{figure}[h]
+\includegraphics[clip,width=\columnwidth]{figures/images/sheet1.png}% 
+\caption{\small{XXXX}}
+\label{fig: Sheet music aug 1}
+\end{figure}
+
+\begin{figure}[h]
+\includegraphics[clip,width=\columnwidth]{figures/images/sheet2.png}% 
+\caption{\small{XXXX}}
+\label{fig: Sheet music aug 2}
+\end{figure}
+
+\begin{figure}[h]
+\includegraphics[clip,width=\columnwidth]{figures/images/sheet3.png}% 
+\caption{\small{XXXX}}
+\label{fig: Sheet music aug 3}
+\end{figure}
+
+\begin{figure}[h]
+\includegraphics[clip,width=\columnwidth]{figures/images/sheet4.png}% 
+\caption{\small{XXXX}}
+\label{fig: Sheet music aug 4}
+\end{figure}

### 2023-04-19 introduction/Subsections/Assumptions.tex
Updates from Overleaf

@@
 Although a waveform might have limited sheet music representations that accurately encapsulate its musical components, a single sheet music composition can be performed infinitely using various instruments, voices, tempos, and interpretations.
-The distinct tonal quality of a waveform is significantly influenced by the specific instrument or production technology employed in its creation, complicating the transcription of its sonic properties into precise sheet music notation.
+The distinct tonal quality of a waveform is significantly influenced by the specific instrument timbre or production technology employed in its creation, complicating the transcription of its sonic properties into precise sheet music notation.
 
 Moreover, this distinct tonal quality is represented by high-level natural language concepts embedded within a rich cultural and sociological tradition.
-
-\begin{figure}[h]
-\includegraphics[clip,width=\columnwidth]{figures/images/sheet1.png}% 
-\caption{\small{XXXX}}
-\label{fig: Sheet music aug 1}
-\end{figure}
-
-\begin{figure}[h]
-\includegraphics[clip,width=\columnwidth]{figures/images/sheet2.png}% 
-\caption{\small{XXXX}}
-\label{fig: Sheet music aug 2}
-\end{figure}
-
-\begin{figure}[h]
-\includegraphics[clip,width=\columnwidth]{figures/images/sheet3.png}% 
-\caption{\small{XXXX}}
-\label{fig: Sheet music aug 3}
-\end{figure}
-
-\begin{figure}[h]
-\includegraphics[clip,width=\columnwidth]{figures/images/sheet4.png}% 
-\caption{\small{XXXX}}
-\label{fig: Sheet music aug 4}
-\end{figure}

### 2023-04-19 introduction/Subsections/Introduction.tex
Updates from Overleaf

--- 2023-04-06 introduction/Subsections/Introduction.tex
@@
 
-Music is an essential part of human culture, history, and society.
-It has existed since ancient times and evolved, reflecting changes in our cultures, traditions, and beliefs.
-Despite its importance, the study of music has always been a challenging and complex task due to its subjective nature and the vast array of musical styles, genres, and cultures that exist worldwide.
+Music, an essential component of human culture, history, and society, has existed since ancient times.
+It reflects the changes in our cultures, traditions, and beliefs as it evolves.
+Studying music, however, has always been a challenging and complex task due to its subjective nature and the sheer variety of musical styles, genres, and cultures that exist worldwide.
 
-Humanity has been studying music to understand its underlying structure for millennia.
-From the ancient Greeks to the early days, music has been a subject of fascination and inquiry.
-This rich music theory and analysis history provide a valuable foundation for guiding and evaluating Music Information Retrieval (MIR) algorithms and models.
+For millennia, people have sought to understand the underlying structure of music.
+Music has captivated and intrigued us from the ancient Greeks to the present day.
+This rich music theory and analysis history form a valuable foundation for guiding and evaluating Music Information Retrieval (MIR) algorithms and models.
 
-We all humbly seek to unlock the secrets of music's complex and multifaceted nature.
+Music Information Retrieval (MIR) has emerged over the last few decades as an interdisciplinary field that combines engineering, musicology, and neuroscience.
+It aims to develop algorithms and techniques for automatically analyzing, classifying, and retrieving musical information, primarily from audio signals.
+While MIR research has traditionally focused on technical aspects such as Digital Signal Processing (DSP) and pattern recognition, it may have overlooked other relevant domains, including perception, cognition, music theory, aural skills, and musicology, along with their subfields.
 
-MIR is a research area that has emerged in the last decades as an interdisciplinary field combining engineering, musicology, and neuroscience.
-MIR aims to develop algorithms and techniques to automatically analyze, classify, and retrieve musical information from mainly audio signals.
-I believe that traditionally, MIR research has primarily concentrated on technical aspects, such as Digital Signal Processing (DSP) or pattern recognition.
-As a result, other relevant domains, including perception, cognition, music theory, aural skills, and musicology, along with its subfields, might have been overlooked.
+\subsubsection{Bridging the gap}
 
-It is worth mentioning that there has been a significant shift in this tendency on retrieval tasks in the symbolic and musicological domain, such as powerful open-source analysis frameworks \cite{ScottCuthbertChristopherArizaMusic21:Data}, MIDI to proper sheet music syntax \cite{Suzuki2021ScoreRepresentation}, projective orchestration \cite{Crestel2018AOrchestration}, or automatic lead sheet generation \cite{WeilAutomaticSignals} to name a few.
+There has been a noticeable shift in this tendency in recent years, with a growing emphasis on retrieval tasks in the symbolic and musicological domain.
+Several powerful open-source analysis frameworks have emerged for the symbolic domain \cite{ScottCuthbertChristopherArizaMusic21:Data}, as well as advancements in MIDI to human-readable sheet music syntax \cite{Suzuki2021ScoreRepresentation}, projective orchestration \cite{Crestel2018AOrchestration}, and automatic lead sheet generation \cite{WeilAutomaticSignals}, among others.
 
-The reason behind this is non-other but the implementation complexity for such heuristics and abstract fields of study.
-Closing the gap between human perception, environmental and cultural factors, and computational solutions to mimic the formers is an already tackled topic \cite{Large1994ResonanceMeter}\cite{Mullensiefen2003MeasuringJudgments}\cite{Sears2014PerceivingCadence}\cite{Thaut2014HumanPatter}\cite{, yet remains a vast open challenge.
+The driving force behind this shift might be the recognition of the complexity of implementing heuristics and abstract fields of study.
+Bridging the gap between human perception \cite{Large1994ResonanceMeter}\cite{Thaut2014HumanPatter}, environmental and cultural factors \cite{Sears2014PerceivingCadence}, and computational solutions that mimic these aspects \cite{Mullensiefen2003MeasuringJudgments} is a topic that has been previously explored \cite{Hernandez-Olivan2023SymbolicMethods}.
+
+Still, it remains a vast and open challenge.

### 2023-04-19 introduction/Subsections/Motivation.tex
Updates from Overleaf

@@
 \section{Motivation}
-As a music lover, professional musician, and connoisseur, I am interested in gaining a deeper understanding of the fundamental building of musical composition, the various techniques used to create musical works, and capturing underlying relationships among them.
-I am deeply interested in learning how to retrieve useful embedded information within music.
+In the context of this thesis, the research was conducted in collaboration with Epidemic Sound \cite{EpidemicSite}, a renowned organization in the music technology sector.
+Acquiring an in-depth understanding of music and its fundamental structures serves not only to satisfy intellectual curiosity but also to generate potential advancements and benefits for the technical products and services offered by the company.
+
+As a music enthusiast, professional musician, and scholar, I am fervently dedicated to examining the foundational elements of musical composition, investigating the diverse techniques employed in crafting musical pieces, and discerning the intricate relationships among them.
+
+This passion motivates my pursuit of knowledge on extracting valuable information embedded within music, which can contribute to developing more sophisticated and effective music-related technologies and solutions in the industrial landscape.
+
+By championing exposure as the primary method of learning music, I underscore the importance of immersing oneself in many musical experiences to foster a holistic understanding of music as an art form.
+Individuals can cultivate well-rounded musical expertise by engaging with various styles, genres, techniques, and learning approaches, ultimately promoting creativity and experimentation in both personal and professional domains.
 
@@
 
-I have consistently been inspired by musicians and researchers who strive to uncover musical ground truth within the existing tonal paradigm, such as Heinrich Schenker, or by challenging it, as exemplified by George Russell \cite{LydianRussell}.
+I have consistently been inspired by musicians and researchers who strive to uncover musical ground truth within the existing tonal paradigm, such as Heinrich Schenker, or by challenging it, exemplified by George Russell \cite{LydianRussell}.
 Both approaches aim to identify abstract concepts that reinforce or disrupt the tonal foundation.
@@
 224} by Franz Schubert.
-We can see the passage's original score, the schenkerian unfolding of the melody, the chord degrees, and the tonal function.}
+We can see the passage's original score, the schenkerian unfolding of the melody, the chord degrees analysis, as well as the the tonal function.}
 \label{fig:Wandrers Nachtlied, Op. 4, D. 224}

### 2023-04-20 figures/equations/ReLU.tex
Updates from Overleaf

The Rectified Linear Unit (ReLU) activation function is a simple yet highly effective non-linear function used in neural networks. It helps introduce non-linearity to the model and accelerates training due to its computational efficiency. Here's a brief LaTeX explanation of the ReLU function:

ReLU is a piecewise linear function that outputs the input value if it's positive and zero otherwise. Mathematically, it can be represented as:

\begin{equation}
  f(x) =
  \begin{cases}
    x & \text{if } x > 0 \\
    0 & \text{otherwise}
  \end{cases}
\end{equation}

Derivative: The derivative of the ReLU function is used during backpropagation to update the weights in the neural network. It is given by:

\begin{equation}
  f'(x) =
  \begin{cases}
    1 & \text{if } x > 0 \\
    0 & \text{otherwise}
  \end{cases}
\end{equation}

Advantages: ReLU offers several advantages over other activation functions, such as sigmoid or hyperbolic tangent (tanh). These include faster training due to reduced computational complexity and mitigating the vanishing gradient problem.

Drawbacks: Despite its benefits, ReLU has some drawbacks, such as the "dying ReLU" issue, where neurons can become inactive during training and never fire again. This problem can be addressed using variants like Leaky ReLU or Parametric ReLU.

### 2023-04-20 introduction/Subsections/Objectives.tex
Updates from Overleaf

@@
 
-In recent years, using neural networks has enabled low-dimensional musical embeddings that capture crucial musical features and allow the computation of content-based similarity between musical passages \cite{Chen2020LearningRecommendation}\cite{KimLEARNINGLOSS}\cite{Hung2022Feature-informedClassification}\cite{WonEmotionStories}.
+In recent years, using neural networks has enabled low-dimensional musical embeddings that capture crucial musical features and allow the computation of content-based similarity between musical passages \cite{KimLEARNINGLOSS}\cite{Hung2022Feature-informedClassification}.
 By acquiring an embedding function $f(x) \in \mathbb{R}^d$ that maps a given course $x$ to a vector in the real space $\mathbb{R}^d$, we can measure the similarity between two musical passages using the Euclidean distance, as represented by the formula $D_{i,j} = ||f(x_i) - f(x_j)||^2$.
@@
 Given a music piece $M$, we aim to learn a single embedding, $e(M)$, simultaneously capturing the underlying content (melody, harmony, critical, holistic elements) and the production aspects.
-The embedding space should be structured so that similar content and production features are clustered together, effectively isolating the two elements.
+The embedding space should be structured so that similar content and production features are clustered together, effectively isolating the two aspects.
 Formally, our objective is to learn the embedding function $e(M)$ such that:
@@
 
-\subsection{Applications}
-%%%%%%%%%%%%%%%%%%%%%%%%
-%POTENTIAL APPLICATIONS
-%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Academic research and industrial applications}
 
-A self-supervised model that learns an embedding space to retrieve musical content from raw audio signals could have several potential applications and downstream tasks in MIR. Here are some examples:
+The advent of self-supervised models that learn embedding spaces for retrieving musical content from audio signals has opened up novel avenues in academic research and industrial applications.
+By capturing high-level semantic information from raw audio data in an unsupervised manner, these models can potentially revolutionize various aspects of the music industry.
+Their applications span music information retrieval, sharing learned latent representations for MIR \cite{HamelTransferSimilarity}, recommendation systems, digital rights management, and audio signal processing, fostering interdisciplinary research and innovation in musicology, computer science, and artificial intelligence.
+
+The embedding spaces generated by these models can be utilized to create personalized and intelligent music recommendation systems \cite{Chen2020LearningRecommendation}\cite{epidemic}, facilitate effective enforcement of intellectual property rights, and contribute to developing more sophisticated audio editing-production tools, and technical products in general, \cite{WonEmotionStories}, ultimately enhancing our interaction with music in the digital age.

### 2023-04-20 methods/subsections/model architecture and training strategy.tex
Updates from Overleaf

@@
 
-Contrastive Self-Supervised Learning of Musical Representations (CSSLMR) is an approach that combines the principles of Self-Supervised Learning (SSL) \cite{audioselfsupsurvey} and Contrastive Learning of Musical Representations (CLMR) \cite{CLMR2021} to learn discriminative and valuable representations of music without relying on explicit labels.
+Contrastive Self-Supervised Learning of Musical Representations (CoSSLeMuR) is an approach that combines the principles of Self-Supervised Learning (SSL) \cite{audioselfsupsurvey} and Contrastive Learning of Musical Representations (CLMR) \cite{CLMR2021} to learn discriminative and valuable representations of music without relying on explicit labels.
 By leveraging the structure and content of music and contrasting different augmentations or transformations of the same musical piece against randomly (or not) selected pieces, CSSLMR models can effectively capture the underlying structure and known invariance in the data.
@@
 \item \textbf{Data Augmentation:} Create different augmentations or transformations of the same musical piece as positive pairs and use other randomly selected pieces as antagonistic pairs.
-\item \textbf{Contrastive Learning:} Train a neural network to minimize a contrastive loss function, encouraging the model to produce similar representations for positive and dissimilar representations for antagonistic pairs.
+\item \textbf{Contrastive Learning:} Train a neural network to minimize a contrastive loss function, encouraging the model to produce similar positive and dissimilar representations for antagonistic pairs.
 \item\textbf{Latent Representation:} Utilize the learned representations for various MIR downstream tasks, such as music genre classification or similarity, both in the symbolic and time domains.
@@
 
-The SampleCNN model takes in 1D input data with a single channel.
+The SampleCNN model \cite{CLMR2021} takes in 1D input data with a single channel.
 The first layer is a 1D convolutional layer with a kernel size of 3, a stride of 3, and 128 output channels.
@@
 
-After the initial layer, there are nine hidden layers with varying kernel sizes, strides, and channels. Each hidden layer consists of:
+After the initial layer, there are nine hidden layers with varying kernel sizes, strides, and channels. Each hidden layer consists of the following:
 
@@
     \item A 1D convolutional layer with the specified number of input and output channels, kernel size, a stride of 1, and padding of 1.
+
+    \begin{equation}
+y_{c_o}(n) = \sum_{c_i=1}^{C_{\text{in}}} \sum_{k=-\lfloor K/2 \rfloor}^{\lfloor K/2 \rfloor} x_{c_i}(n - k) \cdot w_{c_o, c_i}(k)
+\end{equation}
+
+where:
+
+$y_{c_o}(n)$ is the output for the $c_o$-th output channel at position $n$
+$C_{\text{in}}$ is the number of input channels
+$x_{c_i}(n)$ is the input for the $c_i$-th input channel at position $n$
+$w_{c_o, c_i}(k)$ is the kernel weight for the $c_o$-th output channel and $c_i$-th input channel at position $k$
+$K$ is the kernel size
+The stride is set to 1 and padding is set to 1 (equal padding $\lfloor K/2 \rfloor$ on both sides)
+s
     \item Batch normalization.
-    \item ReLU activation.
+We process a batch of data containing anchor, positive, and negative samples.
+It pads the waveforms to the same length, performs online triplet mining to find the hardest negatives, and returns the padded anchors, positives, and hardest negatives.
+
+    Let $A$, $P$, and $N$ represent the anchor, positive, and negative samples, respectively. The maximum length in the batch is given by:
+
+    \begin{equation}
+L_{\text{max}} = \max_{\text{item} \in \text{batch}}(\max(\text{length}(A_{\text{item}}), \text{length}(P_{\text{item}}), \text{length}(N_{\text{item}})))
+\end{equation}
+
+    The anchor-positive distance and the anchor-negative distance are computed as the Euclidean distance between the corresponding samples:
+
+    \begin{equation}
+D_{\text{AP}} = \sqrt{\sum_{i} (A_i - P_i)^2}
+\end{equation}
+
+    The hardest negative index for each anchor-positive pair is determined by maximizing the difference between the anchor-negative and anchor-positive distances:
+
+    \begin{equation}
+D_{\text{AN}} = \sqrt{\sum_{i} (A_i - N_i)^2}
+\end{equation}
+
+    \item ReLU activation. \input{figures/equations/ReLU}
+
     \item Max pooling with kernel size and stride equal to the stride value of the current layer.
@@
 
+We have changed and adapted the original architecture for our experiments to our purpose and needs—the weights initialization and the final average pooling step.
+
 \subsection{Audio augmentation and transformation pipeline}
 \subsubsection{Positive sample generation}
-Let $W$ be the input waveform and $W_p$ be the generated positive waveform.
-The pipeline applies a series of audio effects and adds noise with a random SNR.
-Define the following random variables for the effects:
+Let $W$ be the input waveform and $W_p$ be the generated positive waveform. The pipeline applies audio effects and adds noise with a random SNR. Define the following random variables for the effects:
 
-\begin{alignat*}{2}
-&gain \sim \text{Uniform}(-12, 0), \quad
-&pitch \sim \text{Uniform}(-1200, 1200), \\
-&reverb\_params \sim \text{Uniform}(0, 100)^3, \quad
-&chorus\_params = \begin{cases}
+\begin{equation}
+gain \sim \text{Uniform}(-12, 0)
+\end{equation}
+\begin{equation}
+pitch \sim \text{Uniform}(-1200, 1200)
+\end{equation}
+\begin{equation}
+reverb\_params \sim \text{Uniform}(0, 100)^3
+\end{equation}
+\begin{equation}
+chorus\_params = \begin{cases}
 \text{Uniform}(0.1, 1.0), & i=1,2, \\
@@
 \text{Categorical}(\{-s, -t\}), & i=7,
-\end{cases}, \\
-&drive \sim \text{Uniform}(0, 30), \quad
-&stretch \sim \text{Uniform}(0.9, 1.1), \\
-&speed \sim \text{Uniform}(0.9, 1.1), \quad
-&tremolo\_speed \sim \text{Uniform}(0.1, 100), \\
-&tremolo\_depth \sim \text{Uniform}(1, 101), \quad
-&snr\_range \sim \text{Uniform}(12, 100).
-\end{alignat*}
+\end{cases}
+\end{equation}
+\begin{equation}
+drive \sim \text{Uniform}(0, 30)
+\end{equation}
+\begin{equation}
+stretch \sim \text{Uniform}(0.9, 1.1)
+\end{equation}
+\begin{equation}
+speed \sim \text{Uniform}(0.9, 1.1)
+\end{equation}
+\begin{equation}
+tremolo\_speed \sim \text{Uniform}(0.1, 100)
+\end{equation}
+\begin{equation}
+tremolo\_depth \sim \text{Uniform}(1, 101)
+\end{equation}
+\begin{equation}
+snr\_range \sim \text{Uniform}(12, 100)
+\end{equation}
 
-For white noise, let $N$ be the noise matrix with dimensions (channels, samples) as $W$. Calculate signal power $P_s$ and noise power $P_n$:
+Let $N$ be the noise matrix with dimensions [channels, time domain samples] as $W$ for white noise. Calculate signal power $P_s$ and noise power $P_n$:
 
-\begin{align*}
-&P_s = \sum (W_{ij})^2, \
-&P_n = \sum (N_{ij})^2.
-\end{align*}
+\begin{equation}
+P_s = \sum (W_{ij})^2
+\end{equation}
+\begin{equation}
+P_n = \sum (N_{ij})^2
+\end{equation}
 
-Calculate the scaling factor $\alpha$ for noise based on the desired SNR:
+Calculate the scaling factor $\alpha$ for noise based on the desired signal-to-noise ratio (SNR):
 
-\[
+\begin{equation}
 \alpha = \sqrt{\frac{P_s}{P_n \times 10^{\frac{snr\_range}{10}}}}
-\]
+\end{equation}
 
@@
 
-\begin{align*}
-&N_s = \alpha \times N, \
-&W_n = W + N_s.
-\end{align*}
+\begin{equation}
+N_s = \alpha \times N
+\end{equation}
+\begin{equation}
+W_n = W + N_s
+\end{equation}
 
@@
 
-Let $a$ be the original anchor clip and $n$ be the negative clip to be generated. The steps for generating the negative clip $n$ are as follows:
+Let $a$ be the original anchor clip and $n$ be the negative clip generated. The steps for generating the negative clip $n$ are as follows:
 
@@
 
-$L_a = \text{shape}(a)$, $\quad T_a = \frac{L_a}{f_s}$,
+\begin{equation}
+L_a = \text{shape}(a)
+\end{equation}
+\begin{equation}
+T_a = \frac{L_a}{f_s}
+\end{equation}
 
@@
 \item Determine the number of chunks $n_c$ to split the anchor clip into based on a minimum chunk duration $T_c$:
-$$
-n_c = \left\lfloor\frac{T_a}{T_c}\right\rfloor.
-$$
+
+\begin{equation}
+n_c = \left\lfloor\frac{T_a}{T_c}\right\rfloor
+\end{equation}
 
 \item Calculate the minimum and maximum chunk lengths in samples:
-$$
-L_{c,\text{min}} = T_c \times f_s, \quad L_{c,\text{max}} = T_{\text{max}} \times f_s,
-$$
+
+\begin{equation}
+L_{c,\text{min}} = T_c \times f_s
+\end{equation}
+\begin{equation}
+L_{c,\text{max}} = T_{\text{max}} \times f_s
+\end{equation}
+
 where $T_{\text{max}}$ is the maximum chunk duration specified in seconds.
@@
 \item Generate $n_c$ chunk lengths $L_{c,1},\ldots,L_{c,n_c}$ as follows:
-$$
+
+\begin{equation}
 L_{c,i} = \begin{cases}
@@
 \end{cases}
-$$
+\end{equation}
 
 \item Split the anchor clip into chunks $c_1,\ldots,c_{n_c}$ based on the lengths $L_{c,1},\ldots,L_{c,n_c}$:
-$$
-c_i = a[..., s_i : s_i + L_{c,i}], \quad S_c = \text{cumsum}([0] + [L_{c,1},\ldots,L_{c,n_c-1}]), \quad s_i = S_c[i], \quad i=1,\ldots,n_c.
-$$
+
+\begin{equation}
+c_i = a[..., s_i : s_i + L_{c,i}]
+\end{equation}
+\begin{equation}
+S_c = \text{cumsum}([0] + [L_{c,1},\ldots,L_{c,n_c-1}])
+\end{equation}
+\begin{equation}
+s_i = S_c[i]
+\end{equation}
+\begin{equation}
+i=1,\ldots,n_c
+\end{equation}
 
 \item Shuffle the resulting list of chunks randomly to obtain the reordered chunks $c'_1,\ldots,c'_{n_c}$:
-$$
-c' = \text{shuffle}([c_1,\ldots,c_{n_c}]).
-$$
+
+\begin{equation}
+c' = \text{shuffle}([c_1,\ldots,c_{n_c}])
+\end{equation}
 
 \item Concatenate the shuffled chunks $c'_1,\ldots,c'_{n_c}$ to create the negative clip $n$:
-$$
-n = \text{concatenate}(c').
-$$
+
+\begin{equation}
+n = \text{concatenate}(c')
+\end{equation}
 

### 2023-04-26 figures/equations/ReLU.tex
Updates from Overleaf

@@
 It helps introduce non-linearity to the model and accelerates training due to its computational efficiency.
-Here's a brief LaTeX explanation of the ReLU function:
 
-ReLU is a piecewise linear function that outputs the input value if it's positive and zero otherwise. Mathematically, it can be represented as:
+ReLU is a piecewise linear function that outputs the input value if positive and zero otherwise. Mathematically, it can be represented as:
 
@@
 
-Drawbacks: Despite its benefits, ReLU has some drawbacks, such as the "dying ReLU" issue, where neurons can become inactive during training and never fire again.
-This problem can be addressed using variants like Leaky ReLU or Parametric ReLU.
+Drawbacks: Despite its benefits, ReLU has some flaws, such as the "dying ReLU" issue, where neurons can become inactive during training and never fire again.

### 2023-04-26 introduction/Subsections/Motivation.tex
Updates from Overleaf

--- 2023-04-19 introduction/Subsections/Motivation.tex
@@
 \section{Motivation}
-As a music lover, professional musician, and connoisseur, I am interested in gaining a deeper understanding of the fundamental building of musical composition, the various techniques used to create musical works, and capturing underlying relationships among them.
-I am deeply interested in learning how to retrieve useful embedded information within music.
+
+This thesis is driven by personal, academic, and industrial motivations and is conducted in collaboration with Epidemic Sound \cite{EpidemicSite}, a prominent organization in the music technology sector.
+A deeper understanding of music and its fundamental structures fulfills intellectual curiosity and generates potential advancements and benefits for the company's technical products and services.
+
+\subsubsection{Personal motivation}
+
+As a music enthusiast, professional musician, and scholar, I am passionately committed to exploring the foundational elements of musical composition, investigating the diverse techniques employed in creating musical works, and deciphering the intricate relationships among them.
+This passion fuels my quest for knowledge on extracting valuable information embedded within music, contributing to developing more sophisticated and effective music-related technologies and solutions in the industrial landscape.
+
+I advocate for exposure as the primary method of learning music, emphasizing the importance of immersing oneself in various musical experiences to foster a holistic understanding of music as an art form.
+Individuals can cultivate well-rounded musical expertise by engaging with different styles, genres, techniques, and learning approaches, ultimately promoting creativity and experimentation in both personal and professional domains.
+
+\subsubsection{Academic motivation}
+
+The emergence of self-supervised models that learn embedding spaces for retrieving musical content from audio signals has unveiled new opportunities in academic research.
+By capturing high-level semantic information from raw audio data in an unsupervised manner, these models can potentially revolutionize various aspects of the music industry.
+Their applications encompass music information retrieval, sharing learned latent representations for MIR \cite{HamelTransferSimilarity}, and fostering interdisciplinary research and innovation in musicology, computer science, and artificial intelligence.
+
+\subsubsection{Industrial and corporate motivation}
+
+In the industrial and corporate realm, the embedding spaces generated by these models can be utilized to create personalized and intelligent music recommendation systems \cite{Chen2020LearningRecommendation}\cite{epidemic}, facilitate effective enforcement of intellectual property rights, and contribute to the development of more sophisticated audio editing-production tools and technical products \cite{WonEmotionStories}.
+These advancements ultimately enhance our interaction with music in the digital age, promoting innovation and collaboration across the music industry.
 
@@
 
-I have consistently been inspired by musicians and researchers who strive to uncover musical ground truth within the existing tonal paradigm, such as Heinrich Schenker, or by challenging it, as exemplified by George Russell \cite{LydianRussell}.
+I have consistently been inspired by musicians and researchers who strive to uncover musical ground truth within the existing tonal paradigm, such as Heinrich Schenker, or by challenging it, exemplified by George Russell \cite{LydianRussell}.
 Both approaches aim to identify abstract concepts that reinforce or disrupt the tonal foundation.
-Their ultimate goal is to advance the tonal landscape, providing musicians with a dependable playground for growth, development, and further understanding tonal paradigms.
+Their ultimate goal is to advance the tonal landscape, providing musicians with a dependable playground for growth, development, and further understanding of tonal paradigms.
 
@@
 224} by Franz Schubert.
-We can see the passage's original score, the schenkerian unfolding of the melody, the chord degrees, and the tonal function.}
+We can see the passage's original score, the schenkerian unfolding of the melody, the chord degrees analysis, and the tonal function.}
 \label{fig:Wandrers Nachtlied, Op. 4, D. 224}

### 2023-04-26 introduction/Subsections/Objectives.tex
Updates from Overleaf

--- 2023-04-19 introduction/Subsections/Objectives.tex
@@
 
-This work aims to uncover a generalization of the fundamental tonal-working structure of western-tradition music by learning and embedding space used to facilitate its application in downstream MIR tasks.
+This study seeks to discover a generalization of the fundamental tonal structure in Western music by creating and examining an embedding space that can be applied to downstream Music Information Retrieval (MIR) tasks.
 
-In recent years, using neural networks has enabled low-dimensional musical embeddings that capture crucial musical features and allow the computation of content-based similarity between musical passages \cite{Chen2020LearningRecommendation}\cite{KimLEARNINGLOSS}\cite{Hung2022Feature-informedClassification}\cite{WonEmotionStories}.
-By acquiring an embedding function $f(x) \in \mathbb{R}^d$ that maps a given course $x$ to a vector in the real space $\mathbb{R}^d$, we can measure the similarity between two musical passages using the Euclidean distance, as represented by the formula $D_{i,j} = ||f(x_i) - f(x_j)||^2$.
-The effectiveness of such systems depends on the level of musical abstraction and the embedding space's ability to interpret music in a way that aligns with human perception.
-Therefore, a suitable embedding space is crucial to ensure the output aligns with human expectations.
+Neural networks have recently facilitated the development of low-dimensional musical embeddings that capture essential musical features, enabling the computation of content-based similarity between musical passages \cite{KimLEARNINGLOSS}\cite{Hung2022Feature-informedClassification}.
+An embedding function $f(x) \in \mathbb{R}^d$ maps a given course $x$ to a vector in the real space $\mathbb{R}^d$, allowing the measurement of similarity between two musical passages using Euclidean distance, as denoted by the formula $D_{i,j} = ||f(x_i) - f(x_j)||^2$.
+The success of such systems hinges on the level of musical abstraction and the embedding space's capacity to interpret music in a manner consistent with human perception.
+As a result, a suitable embedding space is vital for producing output that aligns with human expectations.
 
-This study aims to comprehensively analyze musical works from diverse styles and genres by incorporating computational techniques from Music Information Retrieval (MIR) and a musicological perspective to contextualize the findings.
-Aural skills are required to comprehend musical works through listening, as they involve perceptual and cognitive abilities.
-The underlying musical structure refers to the systematic arrangement of elements that produce a coherent and expressive musical work.
-This study aims to offer fresh insights into these components of musical composition and advance our understanding of their relationships.
+This research aims to thoroughly analyze musical works from various styles and genres, employing computational techniques from Music Information Retrieval (MIR) and a musicological perspective to contextualize the findings.
+Aural skills, encompassing perceptual and cognitive abilities, are necessary for understanding musical works through listening.
+The underlying musical structure consists of a systematic arrangement of elements that generate a coherent and expressive musical work.
+This study seeks to provide new insights into these components of musical composition and further our comprehension of their interrelationships.
 
-Let's denote the single embedding for a music piece as $e(M)$.
+We denote a single embedding for a music piece as $e(M)$.
 
-Given a music piece $M$, we aim to learn a single embedding, $e(M)$, simultaneously capturing the underlying content (melody, harmony, critical, holistic elements) and the production aspects.
-The embedding space should be structured so that similar content and production features are clustered together, effectively isolating the two elements.
+For a given music piece $M$, we aim to learn a single embedding, $e(M)$, that captures both the underlying content (melody, harmony, critical, holistic elements) and production aspects.
+The embedding space should be structured to cluster similar content and production features together, effectively separating the two aspects.
 Formally, our objective is to learn the embedding function $e(M)$ such that:
@@
 \begin{itemize}
-  \item Similar content features are closer in the embedding space: $\|e(M_1) - e(M_2)\| < \epsilon_c$ for music pieces $M_1$ and $M_2$ with similar content.
-  \item Similar production features are closer in the embedding space: $\|e(M_1) - e(M_3)\| < \epsilon_p$ for music pieces $M_1$ and $M_3$ with similar production.
+\item Similar content features are closer in the embedding space: $|e(M_1) - e(M_2)| < \epsilon_c$ for music pieces $M_1$ and $M_2$ with similar content.
+\item Similar production features are closer in the embedding space: $|e(M_1) - e(M_3)| < \epsilon_p$ for music pieces $M_1$ and $M_3$ with similar production.
 \item Distinct content and production features are further apart in the embedding space.
@@
 
-We describe learning a single embedding $e(M)$ that captures content and production features.
-The embedding space is structured to cluster similar content and production features together, effectively isolating the two aspects.
+We propose learning a single embedding $e(M)$ that captures content and production features, with the embedding space structured to cluster similar aspects together, effectively distinguishing between the two.
 
-Music is a complex and multi-faceted phenomenon, and implementing a model mimicking human aural music skills is challenging.
-However, the latest deep learning techniques provide a promising avenue to build a model that achieves good results for a specific task in music.
-Therefore, this study will utilize deep learning techniques to investigate the correlation between aural skills and the underlying tonal-working structure of music.
+Music is a complex and multi-dimensional phenomenon, and developing a model that emulates human aural skills is challenging.
+Nonetheless, recent advancements in deep learning offer promising avenues for creating a model that achieves satisfactory results in specific music-related tasks.
+This study will employ deep learning techniques to explore the correlation between aural skills and the underlying tonal structure of music.
 
-Furthermore, this study will argue that MIR research should shift from a purely technical-centered approach to a more balanced and comprehensive one incorporating other relevant domains such as musicology and music theory.
-By doing so, we can better understand the interplay between technical and musical aspects of music and improve our understanding of music signals and the music itself.
-
-\subsection{Applications}
-%%%%%%%%%%%%%%%%%%%%%%%%
-%POTENTIAL APPLICATIONS
-%%%%%%%%%%%%%%%%%%%%%%%%%
-
-A self-supervised model that learns an embedding space to retrieve musical content from raw audio signals could have several potential applications and downstream tasks in MIR. Here are some examples:
+Additionally, this research contends that MIR studies should transition from a solely technical-centered approach to a more balanced and comprehensive method that integrates other pertinent domains such as musicology and music theory.
+This shift will enable a better understanding of the interplay between technical and musical aspects of music, enhancing our comprehension of music signals and music itself.

### 2023-04-26 methods/subsections/model architecture and training strategy.tex
Updates from Overleaf

@@
 \section{Model architecture and training strategy}
-Piaget's theory of cognitive development \cite{Huitt2003PiagetsDevelopment} posits that children acquire knowledge from sensory and motor experiences in their early stages, from birth to around 18 months.
-This period called the \textit{sensorimotor stage}, sees the emergence of early representational thought through basic actions such as sucking, grasping, looking, and listening.
+Piaget's theory of cognitive development \cite{Huitt2003PiagetsDevelopment} posits that children acquire knowledge from sensory and motor experiences in their early stages, from birth to around 18 months, during the \textit{sensorimotor stage}.
+This stage sees the emergence of early representational thought through basic actions such as sucking, grasping, looking, and listening.
 As children progress through different developmental stages until adolescence and adulthood, their reasoning progressively moves toward abstract ideas and deductive logic.
 Schemas, higher-order cognitive structures hypothesized to underlie many aspects of human knowledge and skill, emerge during this process, which Piaget interprets through an equilibration mechanism that balances new information with old knowledge.
-This mechanism involves \textit{assimilation} and \textit{accommodation}, which entail taking in further information to fit pre-existing schemas and modifying existing schemas resulting from the latest news.
+This mechanism involves \textit{assimilation} and \textit{accommodation}, which entail taking in further information to fit pre-existing schemas and modifying existing schemas resulting from the latest information.
 In the context of learning, complex structures are based on simpler ones, and knowledge transfer occurs when dynamic systems capable of generalization are created.
@@
 
-Contrastive Self-Supervised Learning of Musical Representations (CoSSLeMuR) is an approach that combines the principles of Self-Supervised Learning (SSL) \cite{audioselfsupsurvey} and Contrastive Learning of Musical Representations (CLMR) \cite{CLMR2021} to learn discriminative and valuable representations of music without relying on explicit labels.
+Contrastive Self-Supervised Learning of Musical Representations (CSSLMR) is an approach that combines the principles of Self-Supervised Learning (SSL) \cite{audioselfsupsurvey} and Contrastive Learning of Musical Representations (CLMR) \cite{CLMR2021} to learn discriminative and valuable representations of music without relying on explicit labels.
 By leveraging the structure and content of music and contrasting different augmentations or transformations of the same musical piece against randomly (or not) selected pieces, CSSLMR models can effectively capture the underlying structure and known invariance in the data.
@@
 
-where:
+Where:
 
@@
 
-    Let $A$, $P$, and $N$ represent the anchor, positive, and negative samples, respectively. The maximum length in the batch is given by:
+    Let $A$, $P$, and $N$ represent the anchor, positive, and negative samples. The maximum length in the batch is given by:
 
@@
 
-    The hardest negative index for each anchor-positive pair is determined by maximizing the difference between the anchor-negative and anchor-positive distances:
+    The "hardest" negative index for each anchor-positive pair is determined by maximizing the difference between the anchor-negative and anchor-positive distances:
 
@@
 
-If the model is "supervised", dropout with a rate of 0.5 is applied.
+If the model is "supervised", dropout with a rate of 0.5 is applied; a regularization technique randomly drops out neurons during training to prevent overfitting, with a 0.5 rate meaning half of the neurons are dropped out.
 
@@
 
-We have changed and adapted the original architecture for our experiments to our purpose and needs—the weights initialization and the final average pooling step.
+We have adapted the original architecture for our experiments to our purpose and needs—the weights initialization and the final average pooling step.
 
@@
 The final positive waveform $W_p$ is obtained with noise added according to the chosen SNR.
-This pipeline enhances the diversity of the positive samples and aims to improve the model's ability to retrieve similar-sounding samples sharing the same underlying musical language.
+This pipeline enhances the diversity of the positive samples and aims to improve the model's ability to retrieve content-based similar-sounding samples sharing the same underlying musical language.
 
@@
 \begin{equation}
-L_a = \text{shape}(a)
+L_a = \text{len}(a)
 \end{equation}
+
 \begin{equation}
@@
 
-where $\text{shape}(a)$ returns the shape of the audio clip, and $f_s$ is the sample rate of the audio.
+where $\text{len}(a)$ returns the shape of the audio clip, and $f_s$ is the sample rate of the audio.
 
@@
 \begin{equation}
-S_c = \text{cumsum}([0] + [L_{c,1},\ldots,L_{c,n_c-1}])
+S_c = [0] + [L_{c,1},...,L_{c,n_c-1}]
+S_c = \sum_{i=0}^{n_c-1} S_{c,i}
 \end{equation}
@@
 
-\item Shuffle the resulting list of chunks randomly to obtain the reordered chunks $c'_1,\ldots,c'_{n_c}$:
+\item Shuffle the resulting list of chunks randomly to obtain the reordered chips $c'_1,\ldots,c'_{n_c}$:
 
+Let $p$ be a random permutation of the indices $1$ to $n_c$. Then, the shuffled array $c'$ is given by:
 \begin{equation}
-c' = \text{shuffle}([c_1,\ldots,c_{n_c}])
+c' = [c_{p(1)}, c_{p(2)}, \dots, c_{p(n_c)}]
 \end{equation}
 
-\item Concatenate the shuffled chunks $c'_1,\ldots,c'_{n_c}$ to create the negative clip $n$:
-
+\item Let $c'_1, \dots, c'_{n_c}$ be the shuffled chunks. Then, the negative clip $n$ is obtained by concatenating the shuffled chunks:
 \begin{equation}
-n = \text{concatenate}(c')
+n = [c'_1, \dots, c'_{n_c}]
 \end{equation}
@@
 
-The triplet loss aims to ensure that the distance between an anchor and a positive sample (both from the same class) is smaller than the distance between the anchor and a negative sample (from a different class) by a margin.
+The mathematical expression for the triplet loss function with a variable margin can be written as follows:
 
-$\mathcal{L} = \frac{1}{N}\sum_{i=1}^{N} \max \left( d\left(a_i, p_i\right) - d\left(a_i, n_i\right) + m, 0 \right)$
+\begin{equation}
+L(\mathbf{a}, \mathbf{p}, \mathbf{n}) = \frac{1}{N} \sum_{i=1}^{N} \max \left(0, m + \left| \mathbf{a}_i - \mathbf{p}_i \right|_2^2 - \left| \mathbf{a}_i - \mathbf{n}_i \right|_2^2 \right)
+\end{equation}
 
-In this equation:
+In the triplet loss function, $d(\mathbf{a}, \mathbf{p})$ and $d(\mathbf{a}, \mathbf{n})$ denote the Euclidean distance (L2-norm) between the anchor $\mathbf{a}$ and the positive sample $\mathbf{p}$ and the negative sample $\mathbf{n}$, respectively.
+The margin $m$ is a positive constant determining the minimum distance between the anchor-positive and anchor-negative pairs.
 
-$N$ is the number of triplets in the batch
-$a_i$ is the $i$-th anchor
-$p_i$ is the $i$-th positive sample
-$n_i$ is the $i$-th negative sample
-$d(\cdot, \cdot)$ is the Euclidean distance function
-$m$ is the margin; commonly set to 0.2 by default
-The forward method computes the triplet loss as follows:
+The $\max(0, ...)$ function computes the maximum of the expression within the parentheses and 0.
+This function aims to ensure that the loss is only calculated for triplets that violate the margin constraint, where the negative sample is closer to the anchor than the positive sample by at least the margin.
+When the distance between the positive and negative samples is greater than the margin, the loss is zero.
+Otherwise, the loss is proportional to the extent to which the constraint is violated.
 
-Calculate the pairwise Euclidean distance between the anchor and positive samples, denoted as $d(a_i, p_i)$.
-Calculate the pairwise Euclidean distance between the anchor and negative samples, denoted as $d(a_i, n_i)$.
-Compute the loss for each triplet in the batch by subtracting the negative distance from the positive distance and adding the margin: $d(a_i, p_i) - d(a_i, n_i) + m$.
-Apply the ReLU function, which is equivalent to taking the maximum value between the computed value and 0: $\max \left( d(a_i, p_i) - d(a_i, n_i) + m, 0 \right)$.
-Calculate the mean of the losses across all triplets in the batch.
+The final form of the loss function is obtained by averaging the loss over a mini-batch of triplets.
+
+\begin{equation}
+L = \frac{1}{N} \sum_{i=1}^{N} L(anchor_i, positive_i, negative_i)
+\end{equation}
+
+Here, $N$ is the number of triplets in the mini-batch, and $L(anchor_i, positive_i, negative_i)$ represents the loss function computed for the i-th triplet in the batch.

### 2023-04-28 introduction/Subsections/Introduction.tex
Updates from Overleaf

@@
 
-There has been a noticeable shift in this tendency in recent years, with a growing emphasis on retrieval tasks in the symbolic and musicological domain.
-Several powerful open-source analysis frameworks have emerged for the symbolic domain \cite{ScottCuthbertChristopherArizaMusic21:Data}, as well as advancements in MIDI to human-readable sheet music syntax \cite{Suzuki2021ScoreRepresentation}, projective orchestration \cite{Crestel2018AOrchestration}, and automatic lead sheet generation \cite{WeilAutomaticSignals}, among others.
+Music similarity is a critical factor in query-by-example retrieval systems.
+However, similarity calculation and definition can differ depending on user needs and retrieval scenarios.
+While acoustic properties like voice, genre, melody, tempo, instrumentation, and rhythm contribute to similarity, personal preferences, and cultural context also play a significant role.
+For instance, a user may avoid a particular artist's music despite its similarity to their favorite artists due to the album cover.
+Moreover, the user's context, such as driving or running, can also influence their preference and perception of similarity.
 
-The driving force behind this shift might be the recognition of the complexity of implementing heuristics and abstract fields of study.
-Bridging the gap between human perception \cite{Large1994ResonanceMeter}\cite{Thaut2014HumanPatter}, environmental and cultural factors \cite{Sears2014PerceivingCadence}, and computational solutions that mimic these aspects \cite{Mullensiefen2003MeasuringJudgments} is a topic that has been previously explored \cite{Hernandez-Olivan2023SymbolicMethods}.
-
-Still, it remains a vast and open challenge.
+Metadata is the traditional approach to electronic music searches, but it can be impractical and unintuitive for users who are unfamiliar with most tracks.
+Retrieval systems often overlook the cultural, personal, and musical aspects of music information needs, rendering them less useful for non-expert users.
+Many people search for music based on emotions or usage context rather than bibliographic information.

### 2023-04-28 introduction/Subsections/Motivation.tex
Updates from Overleaf

@@
 
-This thesis is driven by personal, academic, and industrial motivations and is conducted in collaboration with Epidemic Sound \cite{EpidemicSite}, a prominent organization in the music technology sector.
-A deeper understanding of music and its fundamental structures fulfills intellectual curiosity and generates potential advancements and benefits for the company's technical products and services.
+This thesis is driven by personal, academic, and industrial motivations and is conducted in collaboration with \textit{Epidemic Sound AB (ES)} \cite{EpidemicSite}, a prominent Swedish company that provides a global library of over 40,000+ royalty-free soundtrack music and 90,000+ sound effects, and the \textit{Music Technology Group (MTG)} at Universitat Pompeu Fabra in Barcelona, Spain.
+
+The MTG specializes in developing new technologies related to sound and music, including music information retrieval, digital signal processing, computational models of music perception and cognition, and interactive music systems.
+
+The collaboration with Epidemic Sound and the MTG aims to deepen our understanding of music and its fundamental structures, which could potentially lead to advancements and benefits for the company's technical products and services as well as academic research.
 

### 2023-04-29 introduction/Subsections/Motivation.tex
Updates from Overleaf

--- 2023-04-26 introduction/Subsections/Motivation.tex
@@
 
-This thesis is driven by personal, academic, and industrial motivations and is conducted in collaboration with Epidemic Sound \cite{EpidemicSite}, a prominent organization in the music technology sector.
-A deeper understanding of music and its fundamental structures fulfills intellectual curiosity and generates potential advancements and benefits for the company's technical products and services.
+Personal, academic, and industrial motivations drive this thesis.
+It is conducted in collaboration with \textit{Epidemic Sound AB (ES)} \cite{EpidemicSite}, a prominent Swedish company that provides a global library of over 40,000+ royalty-free soundtrack music and 90,000+ sound effects, and the \textit{Music Technology Group (MTG)} at Universitat Pompeu Fabra in Barcelona, Spain.
+
+The MTG specializes in developing new technologies related to sound and music, including music information retrieval, digital signal processing, computational models of music perception and cognition, and interactive music systems.
+
+The collaboration with Epidemic Sound and the MTG aims to deepen our understanding of music and its fundamental structures, potentially leading to advancements and benefits for the company's technical products, services, and MIR academic research.
 
@@
 As a music enthusiast, professional musician, and scholar, I am passionately committed to exploring the foundational elements of musical composition, investigating the diverse techniques employed in creating musical works, and deciphering the intricate relationships among them.
-This passion fuels my quest for knowledge on extracting valuable information embedded within music, contributing to developing more sophisticated and effective music-related technologies and solutions in the industrial landscape.
+This passion fuels my quest for knowledge on extracting valuable information embedded within music in any domain, contributing to developing more sophisticated and effective music-related technologies and solutions in the industrial landscape.
 
@@
 
+While it is true that the theoretical foundations of machine learning can be traced back to the pioneering work of figures such as Alan Turing and Claude Shannon in the mid-twentieth century, we are currently experiencing a period of significant breakthroughs in AI research \cite{Vaswani2017AttentionNeed}.
+These breakthroughs have facilitated the implementation of AI in widely used products \cite{OpenAI2023GPT-4Report}.
+Many researchers and corporations are keen to stay abreast of these developments and contribute to this exciting and rapidly evolving field.
+
 \subsection{About music aural skills and high-level perceptual concepts}
 
-I have consistently been inspired by musicians and researchers who strive to uncover musical ground truth within the existing tonal paradigm, such as Heinrich Schenker, or by challenging it, exemplified by George Russell \cite{LydianRussell}.
-Both approaches aim to identify abstract concepts that reinforce or disrupt the tonal foundation.
+I have consistently been inspired by musicians and researchers who strive to uncover musical ground truth within an existing tonal paradigm, such as Heinrich Schenker and his school of thought, or by challenging it, exemplified by Arnold Schoenberg or George Russell \cite{LydianRussell}.
+These approaches aim to identify abstract concepts that reinforce or disrupt the tonal foundation.
 Their ultimate goal is to advance the tonal landscape, providing musicians with a dependable playground for growth, development, and further understanding of tonal paradigms.

### 2023-05-02 introduction/Subsections/Motivation.tex
Updates from Overleaf

@@
 Personal, academic, and industrial motivations drive this thesis.
-It is conducted in collaboration with \textit{Epidemic Sound AB (ES)} \cite{EpidemicSite}, a prominent Swedish company that provides a global library of over 40,000+ royalty-free soundtrack music and 90,000+ sound effects, and the \textit{Music Technology Group (MTG)} at Universitat Pompeu Fabra in Barcelona, Spain.
+
+This research is conducted in collaboration with \textit{Epidemic Sound AB (ES)} \cite{EpidemicSite}, a prominent Swedish company that provides a global library of over 40,000+ royalty-free soundtrack music and 90,000+ sound effects, and the \textit{Music Technology Group (MTG)} at Universitat Pompeu Fabra in Barcelona, Spain.
 
@@
 As a music enthusiast, professional musician, and scholar, I am passionately committed to exploring the foundational elements of musical composition, investigating the diverse techniques employed in creating musical works, and deciphering the intricate relationships among them.
-This passion fuels my quest for knowledge on extracting valuable information embedded within music in any domain, contributing to developing more sophisticated and effective music-related technologies and solutions in the industrial landscape.
+This passion fuels my quest for knowledge on extracting valuable information embedded within music in any domain, being my main interest in the audio and symbolic domain, contributing to developing more sophisticated and effective music-related technologies and solutions in the industrial landscape.
 
 I advocate for exposure as the primary method of learning music, emphasizing the importance of immersing oneself in various musical experiences to foster a holistic understanding of music as an art form.
-Individuals can cultivate well-rounded musical expertise by engaging with different styles, genres, techniques, and learning approaches, ultimately promoting creativity and experimentation in both personal and professional domains.
+Individuals can cultivate well-rounded musical expertise by engaging with different styles, genres, techniques, and learning approaches, ultimately promoting creativity and experimentation.
 
@@
 \includegraphics[clip,width=\columnwidth]{figures/schenkerian analysis/SchubertOp4no3.png}% 
-\caption{Small excerpt of \textit{Wandrers Nachtlied, Op.
+\caption{\small{Small excerpt of \textit{Wandrers Nachtlied, Op.
 4, D.
 224} by Franz Schubert.
-We can see the passage's original score, the schenkerian unfolding of the melody, the chord degrees analysis, and the tonal function.}
+We can see the passage's original score, the schenkerian unfolding of the melody, the chord degrees analysis, and the tonal function.}}
 \label{fig:Wandrers Nachtlied, Op. 4, D. 224}

### 2023-05-02 introduction/Subsections/Objectives.tex
Updates from Overleaf

@@
 This study seeks to discover a generalization of the fundamental tonal structure in Western music by creating and examining an embedding space that can be applied to downstream Music Information Retrieval (MIR) tasks.
-
-Neural networks have recently facilitated the development of low-dimensional musical embeddings that capture essential musical features, enabling the computation of content-based similarity between musical passages \cite{KimLEARNINGLOSS}\cite{Hung2022Feature-informedClassification}.
-An embedding function $f(x) \in \mathbb{R}^d$ maps a given course $x$ to a vector in the real space $\mathbb{R}^d$, allowing the measurement of similarity between two musical passages using Euclidean distance, as denoted by the formula $D_{i,j} = ||f(x_i) - f(x_j)||^2$.
-The success of such systems hinges on the level of musical abstraction and the embedding space's capacity to interpret music in a manner consistent with human perception.
-As a result, a suitable embedding space is vital for producing output that aligns with human expectations.
 
@@
 
+Neural networks have recently facilitated the development of low-dimensional musical embeddings that capture essential musical features, enabling the computation of content-based similarity between musical passages \cite{Kim2021LearningLoss}\cite{Hung2022Feature-informedClassification}.
+An embedding function $f(x) \in \mathbb{R}^d$ maps a given course $x$ to a vector in the real space $\mathbb{R}^d$, allowing the measurement of similarity between two musical passages using Euclidean distance, as denoted by the formula $D_{i,j} = ||f(x_i) - f(x_j)||^2$.
+The success of such systems hinges on the level of musical abstraction and the embedding space's capacity to interpret music in a manner consistent with human perception.
+As a result, a suitable embedding space is vital for producing output that aligns with human expectations.
+
 We denote a single embedding for a music piece as $e(M)$.
 
-For a given music piece $M$, we aim to learn a single embedding, $e(M)$, that captures both the underlying content (melody, harmony, critical, holistic elements) and production aspects.
-The embedding space should be structured to cluster similar content and production features together, effectively separating the two aspects.
+For a given music piece $M$, we aim to learn a single embedding, $e(M)$, that captures the underlying content (melody, harmony, critical, holistic elements) and production aspects.
+The embedding space should be structured to cluster similar content and production features, effectively separating the two elements.
 Formally, our objective is to learn the embedding function $e(M)$ such that:
@@
 
-We propose learning a single embedding $e(M)$ that captures content and production features, with the embedding space structured to cluster similar aspects together, effectively distinguishing between the two.
+We propose learning a single embedding $e(M)$ that captures musical high-level content while keeping agnostic to production features.
+The embedding space is structured to cluster similar aspects together, effectively distinguishing between the two.
 
@@
 
-Additionally, this research contends that MIR studies should transition from a solely technical-centered approach to a more balanced and comprehensive method that integrates other pertinent domains such as musicology and music theory.
-This shift will enable a better understanding of the interplay between technical and musical aspects of music, enhancing our comprehension of music signals and music itself.
+Additionally, this research contends that MIR studies should transition from a solely technical-centered approach to a more balanced and comprehensive method that integrates other pertinent domains, such as musicology and music theory.
+This shift will enable a better understanding of the interplay between technical and musical aspects of music, enhancing our comprehension of music signals and the music itself.

### 2023-05-02 methods/subsections/machine learning.tex
Updates from Overleaf

@@
 \section{Artificial Neural Networks (ANNs)}
-A neural network, formally known as an artificial neural network (ANN), is a computational model inspired by the structure and functionality of biological neural networks.
+A neural network, formally known as an Artificial Neural Network (ANN), is a computational model inspired by the structure and functionality of biological neural networks.
 It is a mathematical framework designed to process information and perform tasks like pattern recognition, classification, and regression by mimicking how biological neurons and synapses operate.
@@
 \item \textbf{Convolutional layers:} These layers apply a convolution operation to the input data.
-The convolutional layers are designed to effectively learn local patterns and features in the audio data \footnote{For a visual explanation and further understanding of the operation convolution, see this video: \url{https://youtu.be/KuXjwB4LzSA}}.
+The convolutional layers are designed to effectively learn local patterns and features in the audio data \footnote{For a visual explanation and further understanding of the convolution operation, please refer to this video: \url{https://youtu.be/KuXjwB4LzSA}}.
 
@@
 
-$$(I * K)_{kl} = \sum_{i=1}^{p} \sum_{j=1}^{q} i_{k+i-1, l+j-1}k_{ij}$$
+\begin{equation}
+    (I * K)_{kl} = \sum_{i=1}^{p} \sum_{j=1}^{q} i_{k+i-1, l+j-1}k_{ij}
+\end{equation}
 

### 2023-05-03 evaluation/evaluation.tex
Updates from Overleaf

\chapter{Evaluation}

\input{evaluation/subsections/beyond dsp}

\newpage

### 2023-05-03 evaluation/subsections/beyond dsp.tex
Updates from Overleaf

--- 2023-04-28 introduction/Subsections/Motivation.tex
@@
-\section{Motivation}
-
-This thesis is driven by personal, academic, and industrial motivations and is conducted in collaboration with \textit{Epidemic Sound AB (ES)} \cite{EpidemicSite}, a prominent Swedish company that provides a global library of over 40,000+ royalty-free soundtrack music and 90,000+ sound effects, and the \textit{Music Technology Group (MTG)} at Universitat Pompeu Fabra in Barcelona, Spain.
-
-The MTG specializes in developing new technologies related to sound and music, including music information retrieval, digital signal processing, computational models of music perception and cognition, and interactive music systems.
-
-The collaboration with Epidemic Sound and the MTG aims to deepen our understanding of music and its fundamental structures, which could potentially lead to advancements and benefits for the company's technical products and services as well as academic research.
-
-\subsubsection{Personal motivation}
-
-As a music enthusiast, professional musician, and scholar, I am passionately committed to exploring the foundational elements of musical composition, investigating the diverse techniques employed in creating musical works, and deciphering the intricate relationships among them.
-This passion fuels my quest for knowledge on extracting valuable information embedded within music, contributing to developing more sophisticated and effective music-related technologies and solutions in the industrial landscape.
-
-I advocate for exposure as the primary method of learning music, emphasizing the importance of immersing oneself in various musical experiences to foster a holistic understanding of music as an art form.
-Individuals can cultivate well-rounded musical expertise by engaging with different styles, genres, techniques, and learning approaches, ultimately promoting creativity and experimentation in both personal and professional domains.
-
-\subsubsection{Academic motivation}
-
-The emergence of self-supervised models that learn embedding spaces for retrieving musical content from audio signals has unveiled new opportunities in academic research.
-By capturing high-level semantic information from raw audio data in an unsupervised manner, these models can potentially revolutionize various aspects of the music industry.
-Their applications encompass music information retrieval, sharing learned latent representations for MIR \cite{HamelTransferSimilarity}, and fostering interdisciplinary research and innovation in musicology, computer science, and artificial intelligence.
-
-\subsubsection{Industrial and corporate motivation}
-
-In the industrial and corporate realm, the embedding spaces generated by these models can be utilized to create personalized and intelligent music recommendation systems \cite{Chen2020LearningRecommendation}\cite{epidemic}, facilitate effective enforcement of intellectual property rights, and contribute to the development of more sophisticated audio editing-production tools and technical products \cite{WonEmotionStories}.
-These advancements ultimately enhance our interaction with music in the digital age, promoting innovation and collaboration across the music industry.
-
-\subsection{About music aural skills and high-level perceptual concepts}
-
-I have consistently been inspired by musicians and researchers who strive to uncover musical ground truth within the existing tonal paradigm, such as Heinrich Schenker, or by challenging it, exemplified by George Russell \cite{LydianRussell}.
-Both approaches aim to identify abstract concepts that reinforce or disrupt the tonal foundation.
-Their ultimate goal is to advance the tonal landscape, providing musicians with a dependable playground for growth, development, and further understanding of tonal paradigms.
-
-%%%%%%%%%%%%%%%%%%
-
-\begin{figure}[ht]
-\includegraphics[clip,width=\columnwidth]{figures/schenkerian analysis/SchubertOp4no3.png}% 
-\caption{Small excerpt of \textit{Wandrers Nachtlied, Op.
-4, D.
-224} by Franz Schubert.
-We can see the passage's original score, the schenkerian unfolding of the melody, the chord degrees analysis, and the tonal function.}
-\label{fig:Wandrers Nachtlied, Op. 4, D. 224}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Schenkerian Analysis, developed by Austrian music theorist Heinrich Schenker, investigates the underlying structure of tonal music by focusing on the hierarchical relationships between pitches.
-This analytical approach is founded on the premise that all tonal music shares a fundamental structure known as "Ursatz" or "basic shape." The method identifies a piece's stepwise descending line (Urlinie) and bass arpeggiation (Bassbrechung), simplifying it to its essential elements and examining how different layers contribute to the overall structure.
-Central concepts in Schenkerian Analysis include prolongation levels, harmony, counterpoint, voice-leading, and Ursatz (fundamental structure).
-Despite criticism for reducing all tonal works to a limited number of background structures, Schenker highlights the significance of individual elaboration in determining a piece's identity and meaning.
-
-While such analysis is designed for the symbolic domain, we argue that musical abstraction is also feasible in the audio time domain.
-In this section, we explore the application of Schenkerian Analysis principles to the Music Information Retrieval (MIR) domain by examining the foreground, middle-ground, and background levels of musical structure as follows:
-
-\begin{itemize}
-\item \textbf{Foreground}: The surface level of a musical composition, consisting of the notes, rhythms, and articulations directly perceived by the listener, representing the most detailed level of the musical structure.
-
-\item \textbf{Middle-ground and mesostructures}: An intermediate level of analysis focusing on essential structural elements such as harmonic progressions, thematic materials, and voice-leading reductions that contribute to the overall composition.
-In the MIR domain, this level can also be understood as mesostructure.
-Mesostructures are intermediate levels of articulation between waveshapes' microstructure and musical forms' macrostructure.
-Examples of mesostructures include melody, arpeggios, syncopation, polyphonic grouping, and textural contrast.
-Mesostructures might have received limited attention in deep learning, as current models only focus on microstructures \cite{Mesostructures2023}.
-
-\item \textbf{Background}: The most abstract level of musical structure, representing the fundamental core consisting of the \textit{Urlinie} and \textit{Bassbrechung}, which serves as the foundation for the entire composition.
-\end{itemize}
-
-By understanding and applying Schenkerian Analysis principles to the MIR domain, we can better understand the complex relationships between different levels of musical structure in the audio time domain, allowing for a more comprehensive analysis of tonal music.
-
-\subsection{Beyond Digital Signal Processing (DSP)}
+\section{Beyond Digital Signal Processing (DSP)}
 
@@
 
-\subsubsection{Sample MIR task}
+\subsection{Sample MIR task}
 

### 2023-05-03 introduction/Subsections/Introduction.tex
Updates from Overleaf

@@
 
-Music, an essential component of human culture, history, and society, has existed since ancient times.
+Music \footnote{In this thesis, "music" refers to the Western tradition, characterized by conventions, practices, and aesthetics that have developed primarily in Europe and North America.
+This usage is not intended to deny the diversity and richness of other musical traditions worldwide but instead reflects the present study's focus on a specific cultural context.}, an essential component of human culture, history, and society, has existed since ancient times.
 It reflects the changes in our cultures, traditions, and beliefs as it evolves.
@@
 For instance, a user may avoid a particular artist's music despite its similarity to their favorite artists due to the album cover.
-Moreover, the user's context, such as driving or running, can also influence their preference and perception of similarity.
+Moreover, the user's context, such as driving or running, can influence their preference and perception of similarity.
 
-Metadata is the traditional approach to electronic music searches, but it can be impractical and unintuitive for users who are unfamiliar with most tracks.
+Metadata is the traditional approach to electronic music searches, but it can be impractical and unintuitive for users unfamiliar with most tracks.
 Retrieval systems often overlook the cultural, personal, and musical aspects of music information needs, rendering them less useful for non-expert users.
-Many people search for music based on emotions or usage context rather than bibliographic information.
+Many searches for music are based on emotions or usage context rather than bibliographic information.

### 2023-05-03 introduction/Subsections/Motivation.tex
Updates from Overleaf

@@
 By understanding and applying Schenkerian Analysis principles to the MIR domain, we can better understand the complex relationships between different levels of musical structure in the audio time domain, allowing for a more comprehensive analysis of tonal music.
-
-\subsection{Beyond Digital Signal Processing (DSP)}
-
-We argue that MIR research needs to incorporate a more balanced approach that considers the interdisciplinary nature of music and the importance of other domains beyond DSP.
-
-\subsubsection{Sample MIR task}
-
-Let's pick a core MIR task as a sample to display such complexity: Music Structure Analysis (MSA), an interdisciplinary field that aims to understand the structure of music \cite{Nieto2020Audio-BasedApplications}.
-However, due to subjectivity, ambiguity, and data scarcity, audio-based MSA faces challenges like boundary placement ambiguity and similarity quantification \cite{NietoPerceptualMusic}.
-
-The main principles of MSA were initially defined as homogeneity, novelty, and repetition, with the addition of regularity.
-The checkerboard kernel technique is a simple and effective method for MSA based on the homogeneity principle.
-The kernel, with a checkerboard-like structure, is convolved over the main diagonal of a Self-Similarity Matrix (SSM) such as $S_{ij}$ is the similarity between time frames $i$ and $j$, $\vec{x}_i$ is the vector representation of time frame $i$, and $\left| \vec{x}_i \right|$ is the Euclidean norm of vector $\vec{x}_i$.
-The dot product of two vectors $\vec{x}_i$ and $\vec{x}_j$ is denoted by $\vec{x}_i \cdot \vec{x}_j$.
-
-\input{introduction/subsections/equations/SSM equation}
-
-This yields a novelty curve highlighting sudden changes in the selected musical features from which to extract the segment boundaries.
-
-\input{introduction/subsections/equations/Novelty equation}
-
-Mathematical operations are used on predefined principles such as homogeneity and repetition to analyze a musical structure.
-It explores features extracted from a musical signal and identifies peaks in a novelty curve to extract segment boundaries.
-In contrast, human aural skills rely on the perception and interpretation of music by human listeners based on cultural and academic background.
-They can capture subtle nuances of musical structure, but those still are subjective and can vary across listeners.
-
-Combining technical tasks, aural skills, and music perception is challenging due to the complexity and subjectivity of musical perception, discrepancies between the features extracted by DSP techniques and the features perceived by humans, and the variability of musical signals and individual differences in musical perception.
-
-Purely mathematical approaches may not always reflect how humans perceive music and may not capture the subtle variations in timing or harmonic relationships critical to musical perception.
-Variability in musical signals due to instrumentation, genre, and performance style further complicates the development of these techniques that can be generalized to different musical contexts.

### 2023-05-03 methods/subsections/machine learning.tex
Updates from Overleaf

@@
 \subsection{About ANNs}
-The concept of neural networks can be traced back to the early 20th century, with the pioneering work of Warren McCulloch and Walter Pitts in 1943.
+The concept of neural networks can be traced back to the mid-20th century, with the pioneering work of Warren McCulloch and Walter Pitts in 1943.
 They proposed a mathematical model of a neuron known as the McCulloch-Pitts neuron, which provided a foundation for future research in artificial intelligence.
@@
 Each neuron in a layer receives input from the previous layer and computes an output value using an activation function.
-Some standard activation functions include the sigmoid, hyperbolic tangent (tanh), and rectified linear unit (ReLU).
 The output of the last layer represents the prediction or classification result.
@@
 
-Deep learning is a machine learning subfield that utilizes deep neural networks to learn hierarchical data representations automatically.
-These networks handle complex, high-dimensional data across domains such as computer vision and natural language processing.
+Deep learning is a machine learning subfield that utilizes deep neural networks to learn hierarchical data representations.
+These networks handle complex, high-dimensional data across several domains.
 Their effectiveness stems from their nonlinear modeling capabilities and scalability with large datasets.

### 2023-05-03 methods/subsections/model architecture and training strategy.tex
Updates from Overleaf

@@
 Thus, while these processes have broad similarities, they are fundamentally different and cannot be directly compared in detail.
+
+We propose using a Triple Siamese Network to train a model for music similarity retrieval \cite{contentmusicsimtriplet2020}.
+Specifically, we aim to minimize the loss function between an anchor, a positive, and a negative sample by using online triplet mining \cite{Sikaroudi2020OfflinePatches}.
+
+Using the proposed triple siamese network and online triplet mining, we aim to train a model that can effectively distinguish between similar and dissimilar samples while considering their underlying composition and production texture.
 
@@
 
-\section{Model architecture}
-
-We propose using a Triple Siamese Network to train a model for music similarity retrieval \cite{contentmusicsimtriplet2020}.
-Specifically, we aim to minimize the loss function between an anchor, a positive, and a negative sample by using online triplet mining \cite{Sikaroudi2020OfflinePatches}.
-
-Using the proposed triple siamese network and online triplet mining, we aim to train a model that can effectively distinguish between similar and dissimilar samples while considering their underlying composition and production texture.
-
 \subsection{Encoder}
@@
 
-Where:
+where:
 
@@
 We process a batch of data containing anchor, positive, and negative samples.
-It pads the waveforms to the same length, performs online triplet mining to find the hardest negatives, and returns the padded anchors, positives, and hardest negatives.
+We pad the waveforms to the same  maximum length among batch, performs online triplet mining to find the hardest negatives, and returns the padded anchors, positives, and hardest negatives.
 
-    Let $A$, $P$, and $N$ represent the anchor, positive, and negative samples. The maximum length in the batch is given by:
+    Let $A$, $P$, and $N$ represent the anchor, positive, and negative samples. The maximum array length in the batch is given by:
 
@@
 
-We have adapted the original architecture for our experiments to our purpose and needs—the weights initialization and the final average pooling step.
+We have adapted the original architecture for our experiments to our purpose, which consists of the final average pooling step.
+
+\begin{equation}
+y_i = \frac{1}{N} \sum_{j=1}^{N} x_{ij}
+\end{equation}
+
+\begin{itemize}
+  \item \(y_i\) represents the output tensor after the average pooling operation,
+  \item \(x_{ij}\) represents the elements in the 2D input tensor,
+  \item \(N\) is the number of elements along the second dimension of the input tensor,
+  \item \(i\) iterates over the first dimension of the tensors, and
+  \item \(j\) iterates over the second dimension of the input tensor.
+\end{itemize}
 

### 2023-05-05 introduction/Subsections/Motivation.tex
Updates from Overleaf

@@
 By understanding and applying Schenkerian Analysis principles to the MIR domain, we can better understand the complex relationships between different levels of musical structure in the audio time domain, allowing for a more comprehensive analysis of tonal music.
+
+%%%%%%%% PERCEPTION %%%%%%%%%%%%%
+
+Kurt Koffka (1886-1941) was a German psychologist and a founding member of the Gestalt school of psychology, along with Max Wertheimer and Wolfgang Köhler.
+Gestalt psychology emerged as a reaction against the structuralist approach to psychology, emphasizing analyzing mental processes into their most basic elements.
+Instead, Gestalt psychologists sought to understand the principles underlying the organization and perception of complex forms and wholes.
+
+Koffka's most significant contribution to the field was the development of the principles of Gestalt psychology and their application to perception.
+His 1935 book, ``Principles of Gestalt Psychology,'' remains a seminal work in the field \cite{Koffka2013PrinciplesPsychology}.
+In it, Koffka systematically describes the foundational concepts of Gestalt psychology and presents empirical evidence to support these ideas.
+
+Applying the principles of Gestalt psychology to music can provide valuable insights into the cognitive processes underlying musical perception, organization, and interpretation.
+In music, just as in visual perception, the human mind seeks to identify patterns and structures to make sense of the auditory input.
+Several Gestalt principles can be applied to understanding musical perception, such as the law of Prägnanz, grouping principles, and holistic processing.
+
+As with visual perception, the mind organizes musical information into the most straightforward and stable patterns.
+This principle can be observed in listeners' perceptions of harmony, melody, and rhythm.
+For example, Western tonal music is built upon hierarchical structures that allow the listener to make sense of complex musical information by organizing it coherently \cite{Lerdahl1985AMusic}.
+
+In conclusion, applying the principles of Gestalt psychology to the study of music has led to a deeper understanding of the cognitive processes underlying musical perception and organization.
+This approach has influenced various areas of music research, including music theory, music cognition, and music therapy.

### 2023-05-05 evaluation/subsections/beyond dsp.tex
Updates from Overleaf

@@
 Variability in musical signals due to instrumentation, genre, and performance style further complicates the development of these techniques that can be generalized to different musical contexts.
+
+%%%%%%%% SIMILARITY %%%%%%%%%
+
+\subsubsection{Bridging the gap}
+
+Music similarity is a critical factor in query-by-example retrieval systems.
+However, similarity calculation and definition can differ depending on user needs and retrieval scenarios.
+While acoustic properties like voice, genre, melody, tempo, instrumentation, and rhythm contribute to similarity, personal preferences, and cultural context also play a significant role.
+For instance, a user may avoid a particular artist's music despite its similarity to their favorite artists due to the album cover.
+Moreover, the user's context, such as driving or running, can influence their preference and perception of similarity.
+
+Metadata is the traditional approach to electronic music searches, but it can be impractical and unintuitive for users unfamiliar with most tracks.
+Retrieval systems often overlook the cultural, personal, and musical aspects of music information needs, rendering them less useful for non-expert users.
+Many searches for music are based on emotions or usage context rather than bibliographic information.

### 2023-05-05 figures/neural networks/Single_CNN.tex
Updates from Overleaf

@@
-\begin{SCfigure}[2\sidecaptionrelwidth][h]
+\begin{SCfigure}[2\sidecaptionrelwidth][ht]
 	\centering
@@
 	\begin{tikzpicture}
-		\node at (1.5,4){\begin{tabular}{c}input data\\or input feature map\end{tabular}};
+		\node at (1.5,4){\begin{tabular}{c}input data or \\ feature map\end{tabular}};
 
@@
 	\caption[Illustration of a 2D convolutional layer.]{\small{Illustration of a 2D single convolutional layer.
-If layer $l$ is a convolutional layer, the input data (if $l = 1$) or a feature map of the previous layer is convolved by different filters (or kernels) to yield the output feature maps of layer $l$.}}
+If layer $l$ is a convolutional layer, the input data or a feature map of the previous layer is convolved by different kernels to yield the output feature maps of layer $l$.}}
 	\label{fig: convolutional layer}

### 2023-05-05 figures/neural networks/convolution.tex
Updates from Overleaf

@@
-\begin{center}
+\begin{figure}[ht]
+    \centering
     \begin{tikzpicture}[
@@
 \end{tikzpicture}
-\end{center}
+
+    \caption{\small{Illustration of the 2D convolution operation on a binary input matrix $\mathbf I$ with a kernel matrix $\mathbf K$.
+The orange-highlighted region in $\mathbf I$ represents the portion convolved with the kernel, resulting in the blue-highlighted element in the output matrix $\mathbf{I * K}$.}}
+    \label{fig: Convolution}
+\end{figure}

### 2023-05-05 introduction/Subsections/Introduction.tex
Updates from Overleaf

@@
 
-Music \footnote{In this thesis, "music" refers to the Western tradition, characterized by conventions, practices, and aesthetics that have developed primarily in Europe and North America.
+Music\footnote{In this thesis, "music" refers to the Western tradition, characterized by conventions, practices, and aesthetics that have developed primarily in Europe and North America.
 This usage is not intended to deny the diversity and richness of other musical traditions worldwide but instead reflects the present study's focus on a specific cultural context.}, an essential component of human culture, history, and society, has existed since ancient times.
 It reflects the changes in our cultures, traditions, and beliefs as it evolves.
-Studying music, however, has always been a challenging and complex task due to its subjective nature and the sheer variety of musical styles, genres, and cultures that exist worldwide.
+Studying music, however, has always been a challenging and complex task due to its subjective nature, relative and mutable ground truth, and the sheer variety of musical styles, genres, and worldwide cultures.
 
@@
 While MIR research has traditionally focused on technical aspects such as Digital Signal Processing (DSP) and pattern recognition, it may have overlooked other relevant domains, including perception, cognition, music theory, aural skills, and musicology, along with their subfields.
-
-\subsubsection{Bridging the gap}
-
-Music similarity is a critical factor in query-by-example retrieval systems.
-However, similarity calculation and definition can differ depending on user needs and retrieval scenarios.
-While acoustic properties like voice, genre, melody, tempo, instrumentation, and rhythm contribute to similarity, personal preferences, and cultural context also play a significant role.
-For instance, a user may avoid a particular artist's music despite its similarity to their favorite artists due to the album cover.
-Moreover, the user's context, such as driving or running, can influence their preference and perception of similarity.
-
-Metadata is the traditional approach to electronic music searches, but it can be impractical and unintuitive for users unfamiliar with most tracks.
-Retrieval systems often overlook the cultural, personal, and musical aspects of music information needs, rendering them less useful for non-expert users.
-Many searches for music are based on emotions or usage context rather than bibliographic information.

### 2023-05-05 introduction/Subsections/Motivation.tex
Updates from Overleaf

@@
 This approach has influenced various areas of music research, including music theory, music cognition, and music therapy.
+
+%%%%%%%%%%
+
+Piaget's theory of cognitive development posits that children acquire knowledge from sensory and motor experiences in their early stages, from birth to around 18 months, during the \textit{sensorimotor stage} \cite{Huitt2003PiagetsDevelopment}.
+This stage sees the emergence of early representational thought through basic actions such as sucking, grasping, looking, and listening.
+As children progress through different developmental stages until adolescence and adulthood, their reasoning progressively moves toward abstract ideas and deductive logic.
+Schemas, higher-order cognitive structures hypothesized to underlie many aspects of human knowledge and skill, emerge during this process, which Piaget interprets through an equilibration mechanism that balances new information with old knowledge.
+This mechanism involves \textit{assimilation} and \textit{accommodation}, which entail taking in further information to fit pre-existing schemas and modifying existing schemas resulting from the latest information.
+In the context of learning, complex structures are based on simpler ones, and knowledge transfer occurs when dynamic systems capable of generalization are created.
+\cite{audioselfsupsurvey}
+
+There are similarities between assimilation and accommodation in Piaget's theory of cognitive development and backpropagation in DL, both of which involve modifying existing structures based on new information.
+However, it should be noted that these processes' underlying mechanisms and contexts are entirely distinct.
+While assimilation and accommodation involve modifying mental structures to incorporate new information, backpropagation entails adjusting neural network weights to improve output predictions.
+
+%%%%%%%%%%

### 2023-05-05 methods/subsections/machine learning.tex
Updates from Overleaf

@@
 \item \textbf{Convolutional layers:} These layers apply a convolution operation to the input data.
-The convolutional layers are designed to effectively learn local patterns and features in the audio data \footnote{For a visual explanation and further understanding of the convolution operation, please refer to this video: \url{https://youtu.be/KuXjwB4LzSA}}.
+The convolutional layers are designed to effectively learn local patterns and features in the audio data \footnote{For a visual explanation and further understanding of the convolution operation, please refer to this URL: \url{https://youtu.be/KuXjwB4LzSA}}.
 

### 2023-05-05 methods/subsections/model architecture and training strategy.tex
Updates from Overleaf

@@
-\section{Model architecture and training strategy}
-Piaget's theory of cognitive development \cite{Huitt2003PiagetsDevelopment} posits that children acquire knowledge from sensory and motor experiences in their early stages, from birth to around 18 months, during the \textit{sensorimotor stage}.
-This stage sees the emergence of early representational thought through basic actions such as sucking, grasping, looking, and listening.
-As children progress through different developmental stages until adolescence and adulthood, their reasoning progressively moves toward abstract ideas and deductive logic.
-Schemas, higher-order cognitive structures hypothesized to underlie many aspects of human knowledge and skill, emerge during this process, which Piaget interprets through an equilibration mechanism that balances new information with old knowledge.
-This mechanism involves \textit{assimilation} and \textit{accommodation}, which entail taking in further information to fit pre-existing schemas and modifying existing schemas resulting from the latest information.
-In the context of learning, complex structures are based on simpler ones, and knowledge transfer occurs when dynamic systems capable of generalization are created.
-\cite{audioselfsupsurvey}
+\section{Machine Learning Modeling}
 
-There are similarities between assimilation and accommodation in Piaget's theory of cognitive development and backpropagation in DL, both of which involve modifying existing structures based on new information.
-However, it should be noted that these processes' underlying mechanisms and contexts are distinct.
-While assimilation and accommodation involve modifying mental structures to incorporate new information, backpropagation entails adjusting neural network weights to improve output predictions.
-Assimilation and accommodation occur in cognitive development, while backpropagation is specific to machine learning.
-Thus, while these processes have broad similarities, they are fundamentally different and cannot be directly compared in detail.
+This section delves into the systematic process of developing, training and evaluating algorithms, which empower data-driven learning, predictions, and decisions.
+This process encompasses selecting an appropriate algorithm, designing the model architecture, preprocessing and transforming data, and extracting relevant features.
+By iteratively adjusting the model's parameters, we aim to minimize the prediction error.
+The choice of techniques, such as supervised, unsupervised, or reinforcement learning, is dictated by the specific problem and data structure.
+Model evaluation, fine-tuning, and deployment are essential to ensure the model generalizes well to new data and performs effectively in real-world applications.
 
-We propose using a Triple Siamese Network to train a model for music similarity retrieval \cite{contentmusicsimtriplet2020}.
+\subsection{Model architecture and training strategy}
+
+Given the nature of our task, we propose using a Triple Siamese Network.
+This model architecture has been proven efficient for music similarity retrieval tasks \cite{contentmusicsimtriplet2020}.
 Specifically, we aim to minimize the loss function between an anchor, a positive, and a negative sample by using online triplet mining \cite{Sikaroudi2020OfflinePatches}.
@@
 
-\subsection{Contrastive Self-Supervised Learning of Musical Representations (CSSLMR)}
+\subsection{Problem to solve}
 
-Contrastive Self-Supervised Learning of Musical Representations (CSSLMR) is an approach that combines the principles of Self-Supervised Learning (SSL) \cite{audioselfsupsurvey} and Contrastive Learning of Musical Representations (CLMR) \cite{CLMR2021} to learn discriminative and valuable representations of music without relying on explicit labels.
+\subsection{Self-Supervised Learning (SSL)}
+
+Self-supervised learning is a subfield of machine learning where models learn to generate representations of data by finding patterns and structures within the data without relying on external labels or annotations.
+In other words, the model learns by creating its supervision signal from the raw, unlabeled data.\cite{audioselfsupsurvey}
+
+This approach to learning is inspired by the way humans and animals learn from their environment, where a great deal of knowledge is acquired through observation and interaction without explicit instruction.
+Self-supervised learning algorithms often involve tasks where the model learns to predict or reconstruct parts of the input data, such as predicting the next word in a sentence or completing an image with missing pixels.
+
+Some of the main advantages of self-supervised learning include:
+
+\begin{enumerate}
+\item Reduces dependency on labeled data, which can be expensive and time-consuming to collect and annotate.
+\item Encourages more generalizable and robust representations of the data since they capture the inherent structure and properties of the data rather than relying on human-provided labels.
+\end{enumerate}
+
+\subsubsection{Known and unknown invariance}
+
+In machine learning and pattern recognition, invariance refers to the property of a model or algorithm being robust to certain transformations or changes in the input data.
+In other words, an invariant model should produce the same or similar output for different instances of the same object, even if they have undergone some changes.
+
+Known invariance: Known invariances are transformations or changes that the model or algorithm is explicitly designed to be robust against.
+This can include the input data's rotations, translations, scaling, or other known perturbations.
+By incorporating these invariances into the model's design, the algorithm is better equipped to generalize and recognize patterns in the presence of these transformations.
+
+Unknown invariance: Unknown invariances are transformations or change the model has not been explicitly designed to handle.
+However, it still manages to be robust due to its learning capabilities.
+These invariances can emerge from the data and may not be known a priori.
+For example, a deep learning model might automatically learn to be invariant to certain lighting conditions or other factors not explicitly specified in its design.
+
+In summary, known invariances are explicitly incorporated into the design of a model or algorithm to improve its robustness and generalization.
+In contrast, the model learns unknown invariances from the data without explicit instruction.
+
+\begin{equation}
+\forall x \in X, \forall y \in Y, \forall \rho \in \mathcal{T}, f(x) = f(y) \implies f(\rho(x)) = f(\rho(y))
+\end{equation}
+
+In this expression, $X$ and $Y$ represent sets of input data, $\rho$ represents a transformation function, and $f$ represents a machine learning model.
+The expression states that for all inputs $x$ and $y$ in $X$ and $Y$, if $f(x) = f(y)$, then $f(\rho(x)) = f(\rho(y))$.
+
+The expression specifies that a model is invariant to a particular transformation function $\rho$ if it produces the same output for both the original and transformed input.
+
+\subsection{Contrastive Learning of Musical Representations (CLMR)}
+
+Contrastive Learning of Musical Representations (CLMR) is an approach that combines the principles of Self-Supervised Learning (SSL) and Contrastive Learning of Musical Representations (CLMR) \cite{CLMR2021} to learn discriminative and valuable representations of music without relying on explicit labels.
 By leveraging the structure and content of music and contrasting different augmentations or transformations of the same musical piece against randomly (or not) selected pieces, CSSLMR models can effectively capture the underlying structure and known invariance in the data.
 
-The CSSLMR methodology involves the following steps:
+The CLMR methodology involves the following steps:
 
@@
 \item \textbf{Data Augmentation:} Create different augmentations or transformations of the same musical piece as positive pairs and use other randomly selected pieces as antagonistic pairs.
-\item \textbf{Contrastive Learning:} Train a neural network to minimize a contrastive loss function, encouraging the model to produce similar positive and dissimilar representations for antagonistic pairs.
+\item \textbf{Contrastive Learning:} Train by minimizing a contrastive loss function, encouraging the model to produce similar positive and dissimilar representations for antagonistic pairs.
 \item\textbf{Latent Representation:} Utilize the learned representations for various MIR downstream tasks, such as music genre classification or similarity, both in the symbolic and time domains.
@@
 
-\subsubsection{Strengths}
-
-CSSLMR inherits the strengths of both SSL and CLMR:
-
-\begin{enumerate}
-\item Reduces dependency on labeled data: by leveraging inductive bias (assuming a general invariance across the data samples), CSSL can learn from large amounts of unlabeled data.
-\item Encourages feature extraction: CSSLMR promotes learning practical and discriminative representations.
-\end{enumerate}
+\subsection{Siamese Networks}
+\subsection{Triplet Siamese Networks}
+\subsection{XXX}
+\subsection{XXX}
 
@@
 
+Triplet loss was initially proposed and used by Google to learn face recognition of the same person at different poses and angles. \cite{Schroff2015FaceNet:Clustering}
+
 The mathematical expression for the triplet loss function with a variable margin can be written as follows:
@@
 The $\max(0, ...)$ function computes the maximum of the expression within the parentheses and 0.
-This function aims to ensure that the loss is only calculated for triplets that violate the margin constraint, where the negative sample is closer to the anchor than the positive sample by at least the margin.
-When the distance between the positive and negative samples is greater than the margin, the loss is zero.
+This function ensures that the loss is only calculated for triplets that violate the margin constraint, where the negative sample is closer to the anchor than the positive sample by at least the margin.
+The loss is zero when the distance between the positive and negative samples is greater than the margin.
 Otherwise, the loss is proportional to the extent to which the constraint is violated.

### 2023-05-06 figures/neural networks/activation.tex
Updates from Overleaf

@@
+\begin{figure}
+    \centering
+    \scalebox{0.8}{
 % NEURAL NETWORK activation
@@
 \begin{tikzpicture}[x=2.7cm,y=1.6cm]
+\centering
   \message{^^JNeural network activation}
@@
 \end{tikzpicture}
+}
+    \caption[Activation function]{\small{The input layer has "n" nodes, represented as $a_i^{(0)}$, where $i$ ranges from 1 to n.
+The output layer has "m" nodes, represented as $a_j^{(1)}$, where $j$ ranges from 1 to m.
+The connections between the input and output layers are defined by the weight matrix $\mathbf{W}^{(0)} \in \mathbb{R}^{m\times n}$, with each element represented as $w_{j,i}$, and the bias vector $\mathbf{b}^{(0)} \in \mathbb{R}^{m}$, with each element represented as $b_j^{(0)}$.The activation function, \\sigma, is applied element-wise to the product of the weight matrix and the input vector plus the bias vector}}
+
+    \label{fig:activation_function}
+
+\end{figure}

### 2023-05-06 figures/neural networks/colour CNN.tex
Updates from Overleaf

@@
 \end{tikzpicture}
-    \caption{High-level illustration of a CNN}
+    \caption[High-level CNN diagram.]{\small{High-level illustration of a CNN.
+It consists of an input layer that takes in raw data, followed by a downsampling process using convolution and pooling layers to extract features.
+Finally, fully-connected hidden layers are added for learning the global structure, and an output layer produces the desired predictions.}}
     \label{fig: CNN colour diagram}

### 2023-05-06 figures/neural networks/convolution.tex
Updates from Overleaf

@@
 
-    \caption{\small{Illustration of the 2D convolution operation on a binary input matrix $\mathbf I$ with a kernel matrix $\mathbf K$.
+    \caption[Illustration of the 2D convolution operation.]{\small{Illustration of the 2D convolution operation on a binary input matrix $\mathbf I$ with a kernel matrix $\mathbf K$.
 The orange-highlighted region in $\mathbf I$ represents the portion convolved with the kernel, resulting in the blue-highlighted element in the output matrix $\mathbf{I * K}$.}}

### 2023-05-06 introduction/Subsections/Assumptions.tex
Updates from Overleaf

@@
 Abstract features, such as melody, harmony, rhythm, tempo, form, and expression, can be identified irrespective of waveform or production style.
-This approach offers objective and comprehensive insight into a piece's musical content and meaning, analogous to how analyzing sheet music unveils a composition's underlying structure and intent.
+This approach offers an objective and comprehensive insight into a piece's musical content and meaning, analogous to how analyzing sheet music unveils a composition's underlying structure and intent.
 
@@
 Moreover, this distinct tonal quality is represented by high-level natural language concepts embedded within a rich cultural and sociological tradition.
+
+\subsection{Beyond Digital Signal Processing (DSP)}
+
+We argue that MIR research needs to incorporate a more balanced approach that considers the interdisciplinary nature of music and the importance of other domains beyond DSP.

### 2023-05-06 introduction/Subsections/Introduction.tex
Updates from Overleaf

@@
 
-Music\footnote{In this thesis, "music" refers to the Western tradition, characterized by conventions, practices, and aesthetics that have developed primarily in Europe and North America.
+Music \footnote{In this thesis, "music" refers to the Western tradition, characterized by conventions, practices, and aesthetics that have developed primarily in Europe and North America.
 This usage is not intended to deny the diversity and richness of other musical traditions worldwide but instead reflects the present study's focus on a specific cultural context.}, an essential component of human culture, history, and society, has existed since ancient times.

### 2023-05-06 introduction/Subsections/Motivation.tex
Updates from Overleaf

@@
 \includegraphics[clip,width=\columnwidth]{figures/schenkerian analysis/SchubertOp4no3.png}% 
-\caption{\small{Small excerpt of \textit{Wandrers Nachtlied, Op.
+\caption[Small excerpt of \textit{Wandrers Nachtlied, Op.
+4, D.
+224} by Franz Schubert.]{\small{Small excerpt of \textit{Wandrers Nachtlied, Op.
 4, D.
 224} by Franz Schubert.
-We can see the passage's original score, the schenkerian unfolding of the melody, the chord degrees analysis, and the tonal function.}}
+Passage's original score, the schenkerian unfolding of the melody, the chord degrees analysis, and their tonal function.}}
 \label{fig:Wandrers Nachtlied, Op. 4, D. 224}

### 2023-05-06 methods/subsections/model architecture and training strategy.tex
Updates from Overleaf

@@
 
-In machine learning and pattern recognition, invariance refers to the property of a model or algorithm being robust to certain transformations or changes in the input data.
+In pattern recognition, invariance refers to the property of a model or algorithm being robust to certain transformations or changes in the input data.
 In other words, an invariant model should produce the same or similar output for different instances of the same object, even if they have undergone some changes.
@@
 
-In summary, known invariances are explicitly incorporated into the design of a model or algorithm to improve its robustness and generalization.
-In contrast, the model learns unknown invariances from the data without explicit instruction.
-
 \begin{equation}
+\label{eq:invariance_to_particular_transformation_function}
 \forall x \in X, \forall y \in Y, \forall \rho \in \mathcal{T}, f(x) = f(y) \implies f(\rho(x)) = f(\rho(y))
@@
 
-In this expression, $X$ and $Y$ represent sets of input data, $\rho$ represents a transformation function, and $f$ represents a machine learning model.
+In this expression \ref{eq:invariance_to_particular_transformation_function}, $X$ and $Y$ represent sets of input data, $\rho$ represents a transformation function, and $f$ represents a machine learning model.
 The expression states that for all inputs $x$ and $y$ in $X$ and $Y$, if $f(x) = f(y)$, then $f(\rho(x)) = f(\rho(y))$.
@@
 
-Contrastive Learning of Musical Representations (CLMR) is an approach that combines the principles of Self-Supervised Learning (SSL) and Contrastive Learning of Musical Representations (CLMR) \cite{CLMR2021} to learn discriminative and valuable representations of music without relying on explicit labels.
-By leveraging the structure and content of music and contrasting different augmentations or transformations of the same musical piece against randomly (or not) selected pieces, CSSLMR models can effectively capture the underlying structure and known invariance in the data.
+Contrastive Learning of Musical Representations (CLMR) \cite{CLMR2021} aims to learn discriminative and valuable representations of music without relying on explicit labels.
+By leveraging the structure and content of music and contrasting different augmentations or transformations of the same musical piece against randomly generated pieces, CLMR models can effectively capture the underlying known invariances that are explicitly incorporated into the design of a model to improve its robustness and generalization.
+
+In contrast, the model learns unknown invariances from the data without explicit instruction.
 
@@
 $K$ is the kernel size
-The stride is set to 1 and padding is set to 1 (equal padding $\lfloor K/2 \rfloor$ on both sides)
+The stride is set to 1, and padding is set to 1 (equal padding $\lfloor K/2 \rfloor$ on both sides)
 s
@@
 We process a batch of data containing anchor, positive, and negative samples.
-We pad the waveforms to the same  maximum length among batch, performs online triplet mining to find the hardest negatives, and returns the padded anchors, positives, and hardest negatives.
+We pad the waveforms to the same  maximum length among the collection, perform online triplet mining to find the hardest negatives and return the padded anchors, positives, and hardest negatives.
 
@@
 This function ensures that the loss is only calculated for triplets that violate the margin constraint, where the negative sample is closer to the anchor than the positive sample by at least the margin.
-The loss is zero when the distance between the positive and negative samples is greater than the margin.
+The loss is zero when the distance between the positive and negative samples exceeds the margin.
 Otherwise, the loss is proportional to the extent to which the constraint is violated.

### 2023-05-06 introduction/subsections/equations/Novelty equation.tex
Updates from Overleaf

@@
 \begin{equation}
+\label{eq:novelty_curve}
 n_i = \frac{\sum\limits_{j=1}^{N} S_{ij} - N\cdot S_{ii}}{\sqrt{\sum\limits_{j=1}^{N} (S_{ij} - S_{ii})^2}}
@@
 
-The numerator of the expression represents the sum of similarities between time frame $i$ and all other time frames minus the average similarity across all time frames.
+The numerator of the expression \ref{eq:novelty_curve} represents the sum of similarities between time frame $i$ and all other time frames minus the average similarity across all time frames.
 The denominator of the expression is the standard deviation of the similarities, which is used to normalize the values to ensure that the novelty values are between -1 and 1.

### 2023-05-06 methods/subsections/machine learning.tex
Updates from Overleaf

@@
 
-Deep learning is a machine learning subfield that utilizes deep neural networks to learn hierarchical data representations.
-These networks handle complex, high-dimensional data across several domains.
-Their effectiveness stems from their nonlinear modeling capabilities and scalability with large datasets.
+Deep learning is a subfield of machine learning that employs deep neural networks to learn hierarchical data representations, enabling computational models with multiple processing layers to learn data abstractions across numerous levels.
+These methods have dramatically advanced the state-of-the-art in various domains, including speech recognition, visual object recognition, object detection, drug discovery, genomics, and more \cite{LeCun2015DeepLearning}.
+The effectiveness of deep learning arises from its nonlinear modeling capabilities and scalability with large datasets.
 
-A core algorithm in deep learning is backpropagation which efficiently computes gradients of the loss function concerning the network's parameters.
-It involves a two-step process: (1) forward pass, where input data propagates through the network to generate predictions, and (2) backward pass, where the error between predictions and ground truth is calculated and propagated back through the network.
-This process updates the network's parameters using gradient descent, which minimizes the loss function and improves the model's performance.
+A central algorithm in deep learning is backpropagation, which uses the forward and backward pass process to efficiently compute gradients of the loss function concerning the network's parameters.
+The forward pass involves propagating input data through the network to generate predictions.
+In contrast, the backward pass calculates the error between predictions and ground truth and subsequently returns it through the network.
+This procedure updates the network's parameters using gradient descent, minimizing the loss function and enhancing the model's performance.
+
+Deep learning has led to breakthroughs in processing complex, high-dimensional data, including images, video, speech, and audio, primarily due to deep convolutional nets.
+Simultaneously, recurrent nets have illuminated sequential data analysis such as text and speech.
+Deep learning discovers intricate structures in large datasets, improving our understanding and processing capabilities across various applications.
 

### 2023-05-06 methods/subsections/model architecture and training strategy.tex
Updates from Overleaf

@@
 
-In this expression \ref{eq:invariance_to_particular_transformation_function}, $X$ and $Y$ represent sets of input data, $\rho$ represents a transformation function, and $f$ represents a machine learning model.
+In expression \ref{eq:invariance_to_particular_transformation_function}, $X$ and $Y$ represent sets of input data, $\rho$ represents a transformation function, and $f$ represents a machine learning model.
 The expression states that for all inputs $x$ and $y$ in $X$ and $Y$, if $f(x) = f(y)$, then $f(\rho(x)) = f(\rho(y))$.
@@
 \subsection{Siamese Networks}
+
+A Siamese Network is a class of deep learning architecture specifically designed to address tasks involving similarity or comparison between two input instances.
+Bromley and LeCun first introduced it in the early 1990s to solve signature verification tasks to assess the similarity between two input images.
+The name "Siamese" comes from the network's structure, which involves two or more identical subnetworks connected in parallel and joined at their output layer.
+
+Architecture: A Siamese Network consists of two or more identical subnetworks (also known as "sister networks" or "twin networks") that share the same architecture, weights, and hyperparameters.
+Each subnetwork processes an input independently, and the outputs from these subnetworks are then combined and processed further to produce a single similarity score.
+
+Shared Weights: The critical feature of Siamese Networks is that the subnetworks share the same weights during training.
+This weight-sharing mechanism enables the model to learn an invariant representation for the input instances, making it more efficient in comparing and contrasting them.
+
+Loss Function: Siamese Networks use a specialized loss function, often called contrastive or triplet loss, to guide the training process.
+These loss functions are designed to minimize the distance between similar input pairs and maximize the distance between dissimilar input pairs, thus encouraging the network to learn a meaningful similarity metric.
+
+Applications: Siamese Networks are particularly well-suited for tasks such as one-shot learning, where a model needs to generalize from very few examples and functions that require a comparison or matching between instances, such as image recognition, face recognition, signature verification, and anomaly detection.
+
+Advantages: Siamese Networks have several advantages over traditional deep learning architectures.
+They are more efficient regarding memory usage and computational complexity due to the shared weights.
+They are also more effective in learning from limited or imbalanced datasets, as the network focuses on learning the similarity metric rather than the specific features of individual classes.
+
+In summary, a Siamese Network is a deep learning architecture designed for similarity-based tasks, consisting of two or more identical subnetworks sharing weights and connected at the output layer.
+It employs specialized loss functions to learn a meaningful similarity metric and is particularly well-suited for tasks involving one-shot learning or comparison between instances.
+
 \subsection{Triplet Siamese Networks}
+
+A Triplet Siamese Network is a variation of the Siamese Network architecture that extends the concept of similarity comparison to three input instances instead of two.
+The primary goal of a Triplet Siamese Network is to learn an adequate embedding space where the distance between similar instances is minimized.
+In contrast, the distance between dissimilar instances is maximized.
+
+In a Triplet Siamese Network, the input consists of three instances: an anchor, a positive, and a negative.
+The anchor and the positive instances belong to the same class, while the negative instance belongs to a different class.
+Each instance is processed by an identical subnetwork with the same architecture, weights, and hyperparameters.
+
+The Triplet Siamese Network uses a specialized loss function called the triplet loss to guide the learning process.
+The triplet loss function encourages the network to minimize the distance between the anchor and the positive instances (similar instances) and to maximize the distance between the anchor and the negative instances (dissimilar instances).
+A margin parameter is introduced in the loss function to ensure a minimum separation between the positive and negative instances in the embedding space.
+
 \subsection{XXX}

### 2023-05-09 figures/neural networks/manifold.tex
Updates from Overleaf

\begin{figure}[ht]
    \centering
    \scalebox{1.2}{

\begin{tikzpicture}
\centering
\draw[->] (0, 0) -- ++(0, 2);
\draw[->] (0, 0) -- ++(2.5, 0.6);
\draw[->] (0, 0) -- ++(3, 0) node[midway, below, yshift=-0.5em]
    {Original space ${\cal X}$};

\draw[fill=green!50, draw=none, shift={(0.2, 0.7)},scale=0.5]
  (0, 0) to[out=20, in=140] (1.5, -0.2) to [out=60, in=160]
  (5, 0.5) to[out=130, in=60]
  cycle;

\shade[thin, left color=green!10, right color=green!50, draw=none,
  shift={(0.2, 0.7)},scale=0.5]
  (0, 0) to[out=10, in=140] (3.3, -0.8) to [out=60, in=190] (5, 0.5)
    to[out=130, in=60] cycle;

  \draw[->] (4.8, 0.8) -- ++(0, 2);
  \draw[->] (4.8, 0.8) -- ++(2, 0) node[midway, below, yshift=-0.5em]
      {Latent space ${\cal F}$};

  \draw[thin, fill=green!30, draw=none, shift={(5.4, 1.1)}, rotate=20]
    (0, 0) -- (1, 0) -- (1, 1) -- (0, 1) -- cycle;

  \draw[thick,->,red]
    (1.5, 1.3) to [out=55, in=150] node[midway, above, xshift=6pt, yshift=2pt]
    {$f$} (5.7, 2);

  \draw[thick,->,blue] (1.5, 1.3) ++(4.03, 0.3) to [out=150, in=55]
    node[midway, below, xshift=2pt, yshift=-2pt] {$g$} ++(-3.6, -0.5);

\end{tikzpicture}}

    \caption[High-level diagram of dimensionality reduction and latent space representation.]{Dimensionality reduction and latent space representation: Mapping between the original high-dimensional space ${\cal X}$ and the lower-dimensional latent space ${\cal F}$ using functions $f$ and $g$.}
    \label{fig:my_label}
\end{figure}

### 2023-05-09 figures/neural networks/pipeline.tex
Updates from Overleaf

\def\circRad{4em}

\begin{tikzpicture}[
    line cap=round, thick,
    stage/.style={shape=circle, draw, font=\bfseries, minimum width=2*\circRad},
    challenge/.style={draw, very thin, inner sep=2, rounded corners=2},
    every node/.style={align=center},
  ]
\centering
\scalebox{0.7}{
  \begin{scope}[local bounding box=challenges]
    % Data
    \node [stage, fill=orange!40] (data) {Data\\Challenges};
    \foreach \itm [count=\i, evaluate={\a=\i*15+120;}] in
      {volume, velocity, variety, veracity, visualization, long-term storage, standardization} {
        \node[challenge] at (\a:\circRad + 2mm) [rotate=\a+180, anchor=east] {\itm};
        \draw (\a:\circRad + 2mm) -- (\a:\circRad);
      }

    % Descriptor
    \begin{scope}[xshift=6cm]
      \node [stage, fill=yellow!40] (descriptor) {Descriptor\\Challenges};
      \foreach \itm [count=\i, evaluate={\a=\i*15+140;}] in
        {symmetry invariance, translation, rotation, permutation} {
          \node[challenge] at (\a:\circRad + 2mm) [rotate=\a+180, anchor=east] {\itm};
          \draw (\a:\circRad + 2mm) -- (\a:\circRad);
        }
      \foreach \itm [count=\i, evaluate={\a=30-\i*15;}] in
        {efficiency, speed, compactness} {
          \node[challenge] at (\a:\circRad + 2mm) [rotate=\a, anchor=west] {\itm};
          \draw (\a:\circRad + 2mm) -- (\a:\circRad);
        }
    \end{scope}

    % Model
    \begin{scope}[xshift=12cm]
      \node [stage, fill=blue!20] (model) {Model\\Challenges};
      \foreach \itm [count=\i, evaluate={\a=70-\i*16;}] in
        {reproducibility, benchmarking, transfer learning, extrapolation, {sharing model+results}, computational cost, incorporate physics} {
          \node[challenge] at (\a:\circRad + 2mm) [rotate=\a, anchor=west] {\itm};
          \draw (\a:\circRad + 2mm) -- (\a:\circRad);
        }
    \end{scope}
  \end{scope}

  \draw[ultra thick,->] (data.-70) to [bend right] (descriptor.-110);
  \draw[ultra thick,->] (descriptor.70) to [bend left] (model.110);
    }
\end{tikzpicture}

### 2023-05-09 methods/subsections/experiment setup and hyperparameter tuning.tex
Updates from Overleaf

@@
 
-For finetuning and improving the model's behavior, we followed \href{http://karpathy.github.io/2019/04/25/recipe/}{\textit{A Recipe for Training Neural Networks}} \cite{AndrejKarpathyHttp://karpathy.github.io/2019/04/25/recipe/} by Andrej Karpathy.
+For finetuning and improving the model's behavior, we followed \textit{A Recipe for Training Neural Networks} \cite{AndrejKarpathyHttp://karpathy.github.io/2019/04/25/recipe/} by Andrej Karpathy.
 A blog post that discusses a recipe for training neural networks.
-The author of the blog aims to expand on common mistakes people make when training neural nets by explaining how to avoid them through a particular process.
+The blog aims to expand on common mistakes people make when training neural nets by explaining how to avoid them through a particular process.
 Andrej Karpathy notes that there is often a gap between understanding the technical aspects of a neural network and achieving state-of-the-art results.

### 2023-05-09 methods/subsections/model architecture and training strategy.tex
Updates from Overleaf

--- 2023-05-06 methods/subsections/model architecture and training strategy.tex
@@
 
-Self-supervised learning is a subfield of machine learning where models learn to generate representations of data by finding patterns and structures within the data without relying on external labels or annotations.
+Self-supervised learning (SSL) is a subfield of machine learning where models learn to generate representations of data by finding patterns and structures within the data without relying on external labels or annotations.
 In other words, the model learns by creating its supervision signal from the raw, unlabeled data.\cite{audioselfsupsurvey}
@@
 This approach to learning is inspired by the way humans and animals learn from their environment, where a great deal of knowledge is acquired through observation and interaction without explicit instruction.
-Self-supervised learning algorithms often involve tasks where the model learns to predict or reconstruct parts of the input data, such as predicting the next word in a sentence or completing an image with missing pixels.
+SSL algorithms often involve tasks where the model learns to predict or reconstruct parts of the input data, such as predicting the next word in a sentence or completing an image with missing pixels.
 
-Some of the main advantages of self-supervised learning include:
+Some of the main advantages of SSL include:
 
@@
 
-In pattern recognition, invariance refers to the property of a model or algorithm being robust to certain transformations or changes in the input data.
+In this section, we discuss the concepts of known and unknown invariance in pattern recognition.
+Invariance refers to the property of a model or algorithm being robust to certain transformations or changes in the input data.
 In other words, an invariant model should produce the same or similar output for different instances of the same object, even if they have undergone some changes.
@@
 
-Unknown invariance: Unknown invariances are transformations or change the model has not been explicitly designed to handle.
+Unknown invariance: Unknown invariances are transformations or changes the model has not been explicitly designed to handle.
 However, it still manages to be robust due to its learning capabilities.
@@
 \item \textbf{Data Augmentation:} Create different augmentations or transformations of the same musical piece as positive pairs and use other randomly selected pieces as antagonistic pairs.
-\item \textbf{Contrastive Learning:} Train by minimizing a contrastive loss function, encouraging the model to produce similar positive and dissimilar representations for antagonistic pairs.
-\item\textbf{Latent Representation:} Utilize the learned representations for various MIR downstream tasks, such as music genre classification or similarity, both in the symbolic and time domains.
+\item \textbf{Contrastive Learning:} Train by minimizing a contrastive loss function, encouraging the model to produce similar representations for positive pairs and dissimilar representations for antagonistic pairs.
+\item\textbf{Latent Representation:} Utilize the learned representations for various Music Information Retrieval (MIR) downstream tasks, such as music genre classification or similarity, both in the symbolic and time domains.
 \end{enumerate}
 
+By following these steps, CLMR models can learn meaningful and robust representations of music, potentially enhancing their performance in various MIR tasks and reducing the need for labeled data.
+
 \subsection{Siamese Networks}
+
+A Siamese Network, a deep learning architecture introduced by Bromley and LeCun in the early 1990s \cite{Bromley1993SignatureNetwork}, is designed explicitly for tasks involving similarity or comparison between two input instances, such as signature verification.
+Its name derives from the structure, which consists of two or more identical subnetworks connected in parallel and joined at the output layer.
+These subnetworks share the same architecture, weights, and hyperparameters, allowing for more efficient memory usage and computational complexity.
+This design is particularly effective for learning from limited or imbalanced datasets, as it focuses on learning the similarity metric rather than specific features of individual classes.
+
+Each subnetwork processes an input independently, and its outputs are combined and further processed to yield a single similarity score.
+The shared weights during training enable the model to learn an invariant representation for the input instances, improving its efficiency in comparing and contrasting them.
+Siamese Networks employ specialized loss functions, such as contrastive or triplet loss, which minimize the distance between similar input pairs and maximize the distance between dissimilar ones.
+This approach encourages the network to learn a meaningful similarity metric.
+
 \subsection{Triplet Siamese Networks}
+
+Triplet Siamese Networks, an extension of the Siamese Network architecture, involve comparing three input instances instead of two, aiming to learn an embedding space where similar instances are close and dissimilar instances are distant.
+The input consists of an anchor, a positive instance (same class as the anchor), and a negative instance (different class).
+Each instance is processed by an identical subnetwork with shared architecture, weights, and hyperparameters.
+
+The triplet loss function guides learning, minimizing the distance between the anchor and positive instances while maximizing the distance between the anchor and negative instances.
+A margin parameter in the loss function ensures a minimum separation between positive and negative instances in the embedding space.
+
+Triplet Siamese Networks offer several advantages, including learning fine-grained similarity metrics, being well-suited for one-shot learning tasks, and offering efficient memory usage and computational complexity due to shared weights.
+These networks have been applied to various tasks and domains, such as image recognition, face recognition, speaker recognition, text similarity, and medical imaging for diagnosis or treatment purposes.
+
 \subsection{XXX}
@@
 \subsection{Audio augmentation and transformation pipeline}
+
+%\input{figures/neural networks/pipeline}
+
 \subsubsection{Positive sample generation}
-Let $W$ be the input waveform and $W_p$ be the generated positive waveform. The pipeline applies audio effects and adds noise with a random SNR. Define the following random variables for the effects:
+Given an anchor audio signal $A[n]$, we generate a positive signal $P[n]$ by applying a series of audio effects and adding noise.
+Let $g \in [-12, 0]$ represent the gain, $\Delta p \in [-1200, 1200]$ the pitch shift, $h_R[n]$ the impulse response of the reverb with parameters in $[0, 100]$, $h_C[n]$ the impulse response of the chorus with parameters determined by the specified ranges, $d \in [0, 30]$ the overdrive parameter, $\alpha \in [0.9, 1.1]$ the speed change factor, $\beta \in [0.9, 1.1]$ the stretch factor, $f_m \in [0.1, 100]$ the modulation frequency of the tremolo, and $d_m \in [1, 101]$ the depth of the tremolo.
 
-\begin{equation}
-gain \sim \text{Uniform}(-12, 0)
-\end{equation}
-\begin{equation}
-pitch \sim \text{Uniform}(-1200, 1200)
-\end{equation}
-\begin{equation}
-reverb\_params \sim \text{Uniform}(0, 100)^3
-\end{equation}
-\begin{equation}
-chorus\_params = \begin{cases}
-\text{Uniform}(0.1, 1.0), & i=1,2, \\
-\text{Uniform}(20, 55), & i=3, \\
-\text{Uniform}(0.1, 0.9), & i=4, \\
-\text{Uniform}(0.1, 2.0), & i=5, \\
-\text{Uniform}(2, 5), & i=6, \\
-\text{Categorical}(\{-s, -t\}), & i=7,
-\end{cases}
-\end{equation}
-\begin{equation}
-drive \sim \text{Uniform}(0, 30)
-\end{equation}
-\begin{equation}
-stretch \sim \text{Uniform}(0.9, 1.1)
-\end{equation}
-\begin{equation}
-speed \sim \text{Uniform}(0.9, 1.1)
-\end{equation}
-\begin{equation}
-tremolo\_speed \sim \text{Uniform}(0.1, 100)
-\end{equation}
-\begin{equation}
-tremolo\_depth \sim \text{Uniform}(1, 101)
-\end{equation}
-\begin{equation}
-snr\_range \sim \text{Uniform}(12, 100)
+The positive signal $P[n]$ is generated as follows:
+
+\begin{equation}\label{eq:positive_signal}
+P[n] = A[n] \ast h_{G}[n] \ast h_{C}[n] \ast h_{D}[n] \ast h_{P_t}[n] \ast h_{R}[n] \ast h_{S}[n] \ast h_{T}[n] \ast h_{T_m}[n] + N[n]
 \end{equation}
 
-Let $N$ be the noise matrix with dimensions [channels, time domain samples] as $W$ for white noise. Calculate signal power $P_s$ and noise power $P_n$:
+where $\ast$ denotes convolution, $h_{G}[n] = g \delta[n]$, $h_{D}[n]$ is the impulse response of the overdrive effect, $h_{P_t}[n]$ is the impulse response of the pitch shift effect, $h_{S}[n]$ represents the impulse response of the speed change effect, $h_{T}[n]$ is the impulse response of the stretch effect, and $h_{T_m}[n] = (1 - d_m \cos(2 \pi f_m n))\delta[n]$ is the impulse response of the tremolo effect.
+The noise signal $N[n]$ is added with a specific signal-to-noise ratio (SNR) in the range $[12, 100]$ in decibels.
 
-\begin{equation}
-P_s = \sum (W_{ij})^2
-\end{equation}
-\begin{equation}
-P_n = \sum (N_{ij})^2
-\end{equation}
+These effect selections behave and affect the signal in several domains, adding aggressive transformations while preserving high-level musical content.
 
-Calculate the scaling factor $\alpha$ for noise based on the desired signal-to-noise ratio (SNR):
+\begin{itemize}
+\item \textbf{Amplitude effects:} Amplitude or gain modification.
+\begin{itemize}
+    \item Gain: Adjusts the overall amplitude of the signal by a constant factor $g \in [-12, 0]$ dB.
+\end{itemize}
 
-\begin{equation}
-\alpha = \sqrt{\frac{P_s}{P_n \times 10^{\frac{snr\_range}{10}}}}
-\end{equation}
+\item \textbf{Time-domain effects:} Time-domain manipulation alters the signal's timing or duration.
+\begin{itemize}
+    \item Speed change: Alters the playback speed of the signal by a factor $\alpha \in [0.9, 1.1]$.
+    \item Stretch: Changes the signal duration without affecting its pitch by a factor $\beta \in [0.9, 1.1]$.
+\end{itemize}
 
-Compute the scaled noise matrix $N_s$ and the noisy waveform matrix $W_n$:
+\item \textbf{Frequency-domain effects:} Frequency domain manipulation alters the frequency content or pitch of the signal.
+\begin{itemize}
+    \item Pitch shift: Changes the signal's pitch by $\Delta p \in [-1200, 1200]$ cents.
+\end{itemize}
 
-\begin{equation}
-N_s = \alpha \times N
-\end{equation}
-\begin{equation}
-W_n = W + N_s
-\end{equation}
+\item \textbf{Nonlinear effects:} Nonlinear transformations to the audio signal, resulting in harmonic distortion or other complex changes.
+\begin{itemize}
+    \item Overdrive: Adds harmonic distortion to the signal based on the parameter $d \in [0, 30]$.
+\end{itemize}
 
-The final positive waveform $W_p$ is obtained with noise added according to the chosen SNR.
-This pipeline enhances the diversity of the positive samples and aims to improve the model's ability to retrieve content-based similar-sounding samples sharing the same underlying musical language.
+\item \textbf{Modulation effects:} Audio signal modulation using a low-frequency oscillator or control signal.
+\begin{itemize}
+    \item Chorus: Applies a varying time delay to the signal, resulting in a richer, thicker sound. The specified ranges determine the chorus parameters.
+    \item Tremolo: Modulates the signal's amplitude at a modulation frequency $f_m \in [0.1, 100]$ Hz and depth $d_m \in [1, 101]$.
+\end{itemize}
+
+\item \textbf{Reverberation effects:} Acoustic reflections simulation and reverberations of physical space.
+\begin{itemize}
+    \item Reverb: Applies an impulse response $h_R[n]$ that simulates the reverberation of space with parameters in the range $[0, 100]$.
+\end{itemize}
+
+\item \textbf{Noise effects:} These effects add noise or other random elements to the audio signal.
+\begin{itemize}
+    \item Additive noise: Adds a noise signal $N[n]$ with a specific signal-to-noise ratio (SNR) in the range $[12, 100]$.
+\end{itemize}
+\end{itemize}
 
@@
 
-Let $a$ be the original anchor clip and $n$ be the negative clip generated. The steps for generating the negative clip $n$ are as follows:
+\begin{enumerate}
+\item Calculate the minimum and maximum chunk lengths in samples:
+2\begin{equation}
+l_{min} = t_{min} \times S
+\end{equation}
+\begin{equation}
+l_{max} = t_{max} \times S
+\end{equation}
+\item Generate random chunk lengths $l_1, l_2, \ldots, l_{n-1}$ from the uniform distribution on the interval $[l_{min}, l_{max}]$. Calculate the final chunk length as:
+\begin{equation}
+l_n = L_A - \sum_{i=1}^{n-1} l_i
+\end{equation}
+where $L_A$ is the length of the anchor signal in samples.
+\item Split the anchor signal $A$ into chunks $C_1, C_2, \ldots, C_n$ according to the calculated chunk lengths.
+\item Shuffle the chunks randomly to get the permuted chunks $C_{\sigma(1)}, C_{\sigma(2)}, \ldots, C_{\sigma(n)}$, where $\sigma$ is a random permutation of indices from $1$ to $n$.
+\item Concatenate the shuffled chunks to generate the negative signal:
+\begin{equation}\label{eq:negative_signal}
+N = C_{\sigma(1)} \oplus C_{\sigma(2)} \oplus \ldots \oplus C_{\sigma(n)}
+\end{equation}
+\end{enumerate}
 
-\begin{enumerate}
-\item Calculate the length $L_a$ and duration $T_a$ of the anchor clip $a$:
+Ensure that the length of the anchor and negative signals are the same, i.e.,
 
 \begin{equation}
-L_a = \text{len}(a)
+L_A = L_N,
 \end{equation}
 
-\begin{equation}
-T_a = \frac{L_a}{f_s}
-\end{equation}
-
-where $\text{len}(a)$ returns the shape of the audio clip, and $f_s$ is the sample rate of the audio.
-
-\item Determine the number of chunks $n_c$ to split the anchor clip into based on a minimum chunk duration $T_c$:
-
-\begin{equation}
-n_c = \left\lfloor\frac{T_a}{T_c}\right\rfloor
-\end{equation}
-
-\item Calculate the minimum and maximum chunk lengths in samples:
-
-\begin{equation}
-L_{c,\text{min}} = T_c \times f_s
-\end{equation}
-\begin{equation}
-L_{c,\text{max}} = T_{\text{max}} \times f_s
-\end{equation}
-
-where $T_{\text{max}}$ is the maximum chunk duration specified in seconds.
-
-\item Generate $n_c$ chunk lengths $L_{c,1},\ldots,L_{c,n_c}$ as follows:
-
-\begin{equation}
-L_{c,i} = \begin{cases}
-L_{c,\text{min}}, & i=1, \\
-\text{randint}(L_{c,\text{min}}, L_{c,\text{max}}), & 1<i<n_c, \\
-L_a - \sum_{j=1}^{i-1} L_{c,j}, & i=n_c.
-\end{cases}
-\end{equation}
-
-\item Split the anchor clip into chunks $c_1,\ldots,c_{n_c}$ based on the lengths $L_{c,1},\ldots,L_{c,n_c}$:
-
-\begin{equation}
-c_i = a[..., s_i : s_i + L_{c,i}]
-\end{equation}
-\begin{equation}
-S_c = [0] + [L_{c,1},...,L_{c,n_c-1}]
-S_c = \sum_{i=0}^{n_c-1} S_{c,i}
-\end{equation}
-\begin{equation}
-s_i = S_c[i]
-\end{equation}
-\begin{equation}
-i=1,\ldots,n_c
-\end{equation}
-
-\item Shuffle the resulting list of chunks randomly to obtain the reordered chips $c'_1,\ldots,c'_{n_c}$:
-
-Let $p$ be a random permutation of the indices $1$ to $n_c$. Then, the shuffled array $c'$ is given by:
-\begin{equation}
-c' = [c_{p(1)}, c_{p(2)}, \dots, c_{p(n_c)}]
-\end{equation}
-
-\item Let $c'_1, \dots, c'_{n_c}$ be the shuffled chunks. Then, the negative clip $n$ is obtained by concatenating the shuffled chunks:
-\begin{equation}
-n = [c'_1, \dots, c'_{n_c}]
-\end{equation}
-
-\end{enumerate}
+where $L_N$ is the length of the negative signal in samples.
 
@@
 
-Triplet loss was initially proposed and used by Google to learn face recognition of the same person at different poses and angles. \cite{Schroff2015FaceNet:Clustering}
+Schroff, F., Kalenichenko, D.
+and Philbin, J.
+at Google initially proposed and used triplet loss to learn face recognition of the same person at different poses and angles.
+\cite{Schroff2015FaceNet:Clustering}
 
-The mathematical expression for the triplet loss function with a variable margin can be written as follows:
+A triplet loss function with a variable margin can be written as follows:
 
 \begin{equation}
-L(\mathbf{a}, \mathbf{p}, \mathbf{n}) = \frac{1}{N} \sum_{i=1}^{N} \max \left(0, m + \left| \mathbf{a}_i - \mathbf{p}_i \right|_2^2 - \left| \mathbf{a}_i - \mathbf{n}_i \right|_2^2 \right)
+\mathcal{L}(\mathbf{a}, \mathbf{p}, \mathbf{n}) = \sum_{i=1}^{N} \max \left(0, \left| \mathbf{a}_i - \mathbf{p}_i \right|_2^2 - \left| \mathbf{a}_i - \mathbf{n}_i \right|_2^2 + m \right)
 \end{equation}
 
-In the triplet loss function, $d(\mathbf{a}, \mathbf{p})$ and $d(\mathbf{a}, \mathbf{n})$ denote the Euclidean distance (L2-norm) between the anchor $\mathbf{a}$ and the positive sample $\mathbf{p}$ and the negative sample $\mathbf{n}$, respectively.
-The margin $m$ is a positive constant determining the minimum distance between the anchor-positive and anchor-negative pairs.
+In this equation:
 
-The $\max(0, ...)$ function computes the maximum of the expression within the parentheses and 0.
-This function ensures that the loss is only calculated for triplets that violate the margin constraint, where the negative sample is closer to the anchor than the positive sample by at least the margin.
-The loss is zero when the distance between the positive and negative samples exceeds the margin.
-Otherwise, the loss is proportional to the extent to which the constraint is violated.
+$\mathcal{L}$ is the triplet loss function.
+$\mathbf{a}_i$, $\mathbf{p}_i$, and $\mathbf{n}_i$ are the anchor, positive, and negative embedding vectors, respectively, for the $i$-th sample.
+$\left| \cdot \right|_2^2$ denotes the squared Euclidean distance between two points.
+$m$ is the margin, a hyperparameter that helps ensure that the anchor-positive distance is smaller than the anchor-negative distance by at least a margin.
+The summation $\sum_{i=1}^{N}$ is over all $N$ triplets in the dataset.
+The goal of the triplet loss is to minimize the distance between the anchor and the positive sample while maximizing the distance between the anchor and the negative sample.
+This encourages the model to learn embeddings that are similar for the same class and dissimilar for different classes.
 
@@
 \begin{equation}
-L = \frac{1}{N} \sum_{i=1}^{N} L(anchor_i, positive_i, negative_i)
+\mathcal{L} = \frac{1}{N} \sum_{i=1}^{N} L(anchor_i, positive_i, negative_i)
 \end{equation}

### 2023-05-09 introduction/Subsections/Assumptions.tex
Updates from Overleaf

@@
 
+\begin{figure}
+    \scalebox{0.9}{
+    \centering
+    \includegraphics[width=\textwidth]{figures/images/Mahler 9 Giant Steps score.png}
+        }
+    \caption[]{\small{A small yet evocative excerpt from Mahler's 9th Symphony, 2nd movement: The melodic contour weaves and leaps while the harmony propels through non-diatonic major thirds, painting a vivid and almost atonal canvas.}}
+    \label{fig:mahler}
+\end{figure}
+
+\begin{figure}
+    \scalebox{0.9}{
+    \centering
+    \includegraphics[width=\textwidth]{figures/images/giant steps score.png}
+        }
+    \caption[]{\small{John Coltrane's Giant Steps head: A testament to harmonic exploration, featuring rapid chord changes in thirds, pushing the boundaries of jazz improvisation and technique.}}
+    \label{fig:giant_steps}
+\end{figure}
+
+\begin{figure}
+    \scalebox{0.9}{
+    \centering
+    \includegraphics[width=\textwidth]{figures/images/train interlude score.png}
+        }
+    \caption[]{\small{Pat Metheny's Last Train Home interlude: A masterful fusion of intricate guitar work, showcasing rhythmic precision and melodic nuance, that transports listeners through a tapestry of sonic landscapes.}}
+    \label{fig:last_train}
+\end{figure}
+
 \subsection{Beyond Digital Signal Processing (DSP)}

### 2023-05-10 figures/neural networks/manifold.tex
Updates from Overleaf

@@
 
-    \caption[High-level diagram of dimensionality reduction and latent space representation.]{Dimensionality reduction and latent space representation: Mapping between the original high-dimensional space ${\cal X}$ and the lower-dimensional latent space ${\cal F}$ using functions $f$ and $g$.}
+    \caption[High-level diagram of dimensionality reduction and latent space representation.]{\small{Dimensionality reduction and latent space representation: Mapping between the original high-dimensional space ${\cal X}$ and the lower-dimensional latent space ${\cal F}$ using functions $f$ and $g$.}}
     \label{fig:my_label}

### 2023-05-10 figures/neural networks/pipeline.tex
Updates from Overleaf

@@
 
+\begin{figure}
+    \centering
     \begin{tikzpicture}[
@@
     \foreach \itm [count=\i, evaluate={\a=\i*15+120;}] in
-      {volume, velocity, variety, veracity, visualization, long-term storage, standardization} {
+      {volume, variety, integrity, accessibility, reproduciability} {
         \node[challenge] at (\a:\circRad + 2mm) [rotate=\a+180, anchor=east] {\itm};
@@
 
-    % Descriptor
+    % Transformations
     \begin{scope}[xshift=6cm]
-      \node [stage, fill=yellow!40] (descriptor) {Descriptor\\Challenges};
+      \node [stage, fill=yellow!40] (descriptor) {Augmentation\\Challenges};
       \foreach \itm [count=\i, evaluate={\a=\i*15+140;}] in
-        {symmetry invariance, translation, rotation, permutation} {
+        {meaningful, useful, not harmful,} {
           \node[challenge] at (\a:\circRad + 2mm) [rotate=\a+180, anchor=east] {\itm};
@@
       \foreach \itm [count=\i, evaluate={\a=30-\i*15;}] in
-        {efficiency, speed, compactness} {
+        {efficiency, speed, compactness, computational cost} {
           \node[challenge] at (\a:\circRad + 2mm) [rotate=\a, anchor=west] {\itm};
@@
       \foreach \itm [count=\i, evaluate={\a=70-\i*16;}] in
-        {reproducibility, benchmarking, transfer learning, extrapolation, {sharing model+results}, computational cost, incorporate physics} {
+        {transfer learning, computational cost, performance, evaluation} {
           \node[challenge] at (\a:\circRad + 2mm) [rotate=\a, anchor=west] {\itm};
@@
 \end{tikzpicture}
+    \caption[Challenges in Data, Augmentation, and Model Stages]{\small{A visual representation of the challenges in three main stages of a machine learning pipeline: Data, Augmentation, and Model.
+The Data stage includes challenges such as volume, variety, integrity, accessibility, and reproducibility.
+The Augmentation stage covers challenges related to creating meaningful, useful, and not harmful augmentations while considering efficiency, speed, compactness, and computational cost.
+The Model stage addresses challenges in transfer learning, computational cost, performance, and evaluation.
+Arrows indicate the flow of progression from one stage to another.}}
+
+    \label{fig:my_label}
+\end{figure}

### 2023-05-10 figures/neural networks/r128 sphere.tex
Updates from Overleaf

% A Bloch sphere of radius |a| = 1 contains all possible states of a two-state quantum system (qubit).
% Each Bloch vector fully determines a spin-1/2 density matrix.
% Used in Exercise Sheet 10 of Statistical Physics by Manfred Salmhofer (2016), available at https://janosh.dev/physics/statistical-physics.

%\usetikzlibrary{angles, quotes}

\begin{figure}
    \centering
    \scalebox{1.0}{
    \begin{tikzpicture}

  % Define radius
  \def\r{3}

  % Bloch vector
  \draw (0, 0) node[circle, fill, inner sep=1] (orig) {} -- (\r/3, \r/2) node[circle, fill, inner sep=0.7, label=above:$\vec{a}$] (a) {};
  \draw[dashed] (orig) -- (\r/3, -\r/5) node (phi) {} -- (a);

  % Sphere
  \draw (orig) circle (\r);
  \draw[dashed] (orig) ellipse (\r{} and \r/3);

  % Axes
  \draw[->] (orig) -- ++(-\r/5, -\r/3) node[below] (x1) {$x_1$};
  \draw[->] (orig) -- ++(\r, 0) node[right] (x2) {$x_n \in \mathbb{R}$ $2 \leq n \leq 127$};
  \draw[->] (orig) -- ++(0, \r) node[above] (x3) {$x_128$};

\end{tikzpicture}}
    \caption[128-dimensional hypersphere]{\small{A representation of a 128-dimensional hypersphere in the Euclidean space $\mathbb{R}^{128}$. Due to the limitations of visualizing high-dimensional objects in two or three dimensions, this figure offers a simplified and abstract depiction of the hypersphere.}}
    \label{fig:my_label}
\end{figure}

### 2023-05-10 introduction/Subsections/Assumptions.tex
Updates from Overleaf

--- 2023-05-06 introduction/Subsections/Assumptions.tex
@@
 
+\begin{figure}
+    \centering
+    \scalebox{0.9}{
+    \includegraphics[width=\textwidth]{figures/images/Mahler 9 Giant Steps score.png}
+        }
+    \caption[Mahler's 9th Symphony, 2nd movement]{\small{A small excerpt from Mahler's 9th Symphony, 2nd movement: The melodic and harmonic contour propels through non-diatonic major thirds.}}
+    \label{fig:mahler}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \scalebox{0.9}{
+    \includegraphics[width=\textwidth]{figures/images/giant steps score.png}
+        }
+    \caption[Giant Steps]{\small{John Coltrane's Giant Steps head: A testament to harmonic exploration, featuring rapid chord changes in non-diatonic major thirds.}}
+    \label{fig:giant_steps}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \scalebox{0.9}{
+    \includegraphics[width=\textwidth]{figures/images/train interlude score.png}
+        }
+    \caption[Last Train Home]{\small{Pat Metheny's Last Train Home interlude.}}
+    \label{fig:last_train}
+\end{figure}
+
 \subsection{Beyond Digital Signal Processing (DSP)}

### 2023-05-10 introduction/Subsections/Assumptions.tex
Updates from Overleaf

@@
 
-Abstract features, such as melody, harmony, rhythm, tempo, form, and expression, can be identified irrespective of waveform or production style.
-This approach offers an objective and comprehensive insight into a piece's musical content and meaning, analogous to how analyzing sheet music unveils a composition's underlying structure and intent.
+Abstract high-level features, such as melody, harmony, rhythm, tempo, form, and expression, can be identified irrespective of waveform or production style.
+This approach offers objective and comprehensive insight into a piece's musical content and meaning, analogous to how analyzing sheet music unveils a composition's underlying structure and intent.
 

### 2023-05-12 MasterThesis.tex
Updates from Overleaf

@@
 \usepackage{tikz}
-\usetikzlibrary{decorations.pathreplacing}
-\usetikzlibrary{fadings}
-\usetikzlibrary{matrix, positioning}
-\usetikzlibrary{shapes,arrows,positioning}
+\usetikzlibrary{decorations.pathreplacing,fadings,matrix, positioning,shapes,arrows,angles,quotes}
 
@@
 \title{%
-  Uncovering underlying musical content in the temporal domain \\
-  \small Leveraging deep learning, inductive bias, and aural music skills to learn embedding spaces from raw waveforms with applications to MIR downstream tasks}
+  Uncovering underlying high-level musical content in the temporal domain \\
+  \small Leveraging self-supervised deep neural networks, inductive bias, and aural music skills to learn music embeddings with applications to MIR downstream tasks}
 
@@
 \input{methods/methods}
+%Evaluation
+\input{evaluation/evaluation}
 %Results

### 2023-05-12 evaluation/subsections/beyond dsp.tex
Updates from Overleaf

--- 2023-05-03 evaluation/subsections/beyond dsp.tex
@@
-\section{Beyond Digital Signal Processing (DSP)}
-
-We argue that MIR research needs to incorporate a more balanced approach that considers the interdisciplinary nature of music and the importance of other domains beyond DSP.
-
-\subsection{Sample MIR task}
+\section{Music Structure Analysis as downstream task}
 
@@
 Variability in musical signals due to instrumentation, genre, and performance style further complicates the development of these techniques that can be generalized to different musical contexts.
+
+\input{figures/neural networks/r128 sphere}
+
+\section{SALAMI dataset}
+\subsection{Overview}
+
+SALAMI (Structural Analysis of Large Amounts of Music Information) \cite{Smith2011DESIGNANNOTATIONS} aims to conduct massive structural analyses of different types of music.
+The project covers diverse music, from Western pop to Indian classical and from live to studio recordings.
+
+\subsubsection{Formal Analysis Definition}
+Formal analysis, in this context, doesn't refer to classifying the piece into a formal type (e.g., sonata, song, or canon) or reducing it into its Ursatz as in Schenkerian analysis.
+Instead, it means organizing and dividing the piece into specific sections and understanding how they relate.
+
+%%%%%%%%%%
+
+\subsubsection{Approaches to Music Analysis}
+
+The method proposed combines aspects of the following three approaches, separating the organization of instrumentation, musical material, and formal function.
+This allows for the analysis of a wide variety of music pieces in a consistent way using a constrained vocabulary.
+It's important to note that music structure is often hierarchical, and the appropriate timescale for analysis can be hard to determine.
+The proposed method includes a few markers to partly address this issue.
+
+Perceptual Approach: This involves listening for prominent harmonic or rhythmic boundaries in the piece to segment and apply labels to sections based on their similarity.
+However, this approach might not reflect the different structural roles of similar-sounding sections.
+
+Functional Approach: This involves dividing the song into its functional parts, like verses, choruses, intros, outros, etc.
+This might result in the same music being labeled differently based on its function or different musical ideas having the same functional label.
+
+Transcription Approach: This involves recording musical parameters like chord patterns and instrumentation directly.
+While this method may be less subjective, it may not provide a comprehensive view of the piece's structure.
+
+%%%%%%%
+
+\subsubsection{SALAMI Annotation Labels}
+
+The structural analysis of each piece involves partitioning it into sections and labeling these sections.
+There are three independent layers of labels: musical similarity, function, and instrumentation.
+
+Musical Similarity: Labels (A, B, C, D, E, ...) represent large-scale musical phrases, ideas, or subjects differentiated based on rhythmic, melodic, or harmonic material.
+Each unique musical idea gets its label.
+Although the guide recommends limiting to five labels, more can be used.
+Every moment in the piece must be labeled.
+
+'Z' is a particular label for sections that strongly differ from the rest of the piece or shouldn't be considered part of it (e.g., applause or spoken dialogue).
+
+A prime symbol (') indicates a section similar to a previous one but has significant changes (e.g., transposition or mode change).
+
+Given the hierarchical nature of music, annotators should mark musical similarity on at least two scales.
+The large-scale sections (A, B, C, ...) should be divided into subsections using lowercase letters (a, b, c, ...).
+All boundaries marked by an uppercase letter should also be marked by a lowercase letter.
+Lowercase letters have significance across large-scale sections, indicating the same musical idea even if used in both sections "A" and "B".
+
+Musical Function: It's crucial to correctly identify different sections of the song and label them accordingly.
+These labels include verse, chorus (or refrain), bridge, intro, outro, and solo.
+Each of these has a specific role and characteristic:
+
+Verse: This is where the lyrics often change but the melody remains the same.
+Chorus (Refrain): This part contrasts with the verse and is repeated more strictly.
+Bridge: This section contrasts with the verse and chorus and often serves as a transition.
+Intro: This part leads into the rest of the piece.
+Outro: This part signals the end of the piece.
+Solo: This is when a single instrument or voice is highlighted.
+If the song doesn't strictly follow traditional pop song structure (verse, chorus, etc.), you might use labels like main theme and secondary theme.
+
+Leading Instrumentation: In polyphonic music, you must identify and label the instrument or voice that carries the main melody in each segment.
+If there's no clear lead, that's fine; if two instruments seem to share the lead, you can label both.
+For instance, in a rock song, you might label segments with the lead vocal as "vocal" and segments where the guitar carries the melody as "guitar" or "electric guitar".
+
+Remember, your analysis should aim to represent the structure and prominent features of the song accurately.
+The more detail you can provide, the better.
+Be consistent in labeling and descriptions, and use a standard music analysis vocabulary to ensure others understand your work.

### 2023-05-12 introduction/Subsections/Motivation.tex
Updates from Overleaf

@@
 
+On top of that, I argue that MIR research needs to incorporate a more balanced approach that considers the interdisciplinary nature of music and the importance of other domains beyond DSP.
+
 \subsubsection{Academic motivation}
@@
 
-I have consistently been inspired by musicians and researchers who strive to uncover musical ground truth within an existing tonal paradigm, such as Heinrich Schenker and his school of thought, or by challenging it, exemplified by Arnold Schoenberg or George Russell \cite{LydianRussell}.
+I have consistently been inspired by musicians and researchers who strive to uncover musical ground truth within an existing tonal paradigm, such as Heinrich Schenker and his school of thought \cite{Komar1959SchenkersStructure}, particularly by challenging it, exemplified by Arnold Schoenberg \cite{Samson1974SchoenbergsMusic}, George Russell \cite{LydianRussell} or Ernst Levy \cite{LevyAHarmony}.
 These approaches aim to identify abstract concepts that reinforce or disrupt the tonal foundation.
-Their ultimate goal is to advance the tonal landscape, providing musicians with a dependable playground for growth, development, and further understanding of tonal paradigms.
+Their ultimate goal is to advance the tonal landscape, providing musicians with a dependable playground for growth, development, and further understanding tonal and atonal paradigms.
 

### 2023-05-12 methods/subsections/model architecture and training strategy.tex
Updates from Overleaf

@@
 Model evaluation, fine-tuning, and deployment are essential to ensure the model generalizes well to new data and performs effectively in real-world applications.
+
+\input{figures/neural networks/pipeline}
 
@@
 
-In this section, we discuss the concepts of known and unknown invariance in pattern recognition.
-Invariance refers to the property of a model or algorithm being robust to certain transformations or changes in the input data.
+In pattern recognition, \textit{invariance} refers to the property of a model to be robust to certain transformations or changes in the input data.
 In other words, an invariant model should produce the same or similar output for different instances of the same object, even if they have undergone some changes.
 
-Known invariance: Known invariances are transformations or changes that the model or algorithm is explicitly designed to be robust against.
+\begin{definition}[Known invariance]
+Known invariances are transformations or changes that the model or algorithm is explicitly designed to be robust against.
 This can include the input data's rotations, translations, scaling, or other known perturbations.
 By incorporating these invariances into the model's design, the algorithm is better equipped to generalize and recognize patterns in the presence of these transformations.
+\end{definition}
+
+\begin{definition}[Unknown invariance]
 
@@
 For example, a deep learning model might automatically learn to be invariant to certain lighting conditions or other factors not explicitly specified in its design.
+\end{definition}
 
@@
 
-The SampleCNN model \cite{CLMR2021} takes in 1D input data with a single channel.
+The SampleCNN model \cite{Lee2018SampleCNN:Classification} takes in 1D input data with a single channel.
 The first layer is a 1D convolutional layer with a kernel size of 3, a stride of 3, and 128 output channels.
@@
 \subsection{Audio augmentation and transformation pipeline}
-
-%\input{figures/neural networks/pipeline}
 

### 2023-05-13 abstract/abstract.tex
Updates from Overleaf

--- 2023-02-09 abstract/abstract.tex
@@
 
-The abstract should have at least 200 but not more than 600 words. Placed on the right page next to a blank left page.
+Music, an integral part of human culture, offers a diverse yet complex field of study due to its intricate styles, mutable ground truth, and subjective nature.
+This research, conducted in collaboration with Epidemic Sound AB and the Music Technology Group at Universitat Pompeu Fabra, employs self-supervised learning and contrastive learning of musical representation to uncover the fundamental tonal structure of Western music.
+
+Embracing a subtle novel approach, this process is facilitated through the application of Siamese networks with a triplet loss, mimicking human aural skills in interpreting music to discern musical elements, irrespective of the sonic qualities.
+The study replaces traditional acoustical features with deep audio embeddings, to compute high-level, sound-agnostic, and content-sensitive music identification.
+
+Results XXXXXX
+
+We strongly believe that this approach to learning music-informed embeddings can benefit almost every MIR downstream task.
+The potential implications of this research include advancements in intelligent music recommendation systems and efficient intellectual property rights enforcement, ultimately promoting innovation across the music industry.
 
 \bigskip
-Keywords: Music; Music Theory; Music Information Retrieval; Music Structure Analysis; Machine Learning; Neural Networks; Deep Learning
+Keywords: Music; Music Theory; Music Information Retrieval; Music Structure Analysis; Machine Learning; Deep Learning; Self-Supervised Learning;
 

### 2023-05-13 discussion/discussion.tex
Updates from Overleaf

@@
 
-XXXXXXXXXXX
+XXXXXX
 
@@
 
-XXXXXXXXXXX
+In this work, we introduced a XXXX that leverages deep audio embeddings learned via self-supervised methods.
+Building on top of an existing algorithm based on XXX and framed within MSAF, we replaced traditional features with deep embeddings trained via XXXX for computing high-level music content identification.
 

### 2023-05-13 evaluation/subsections/beyond dsp.tex
Updates from Overleaf

--- 2023-05-03 evaluation/subsections/beyond dsp.tex
@@
 Variability in musical signals due to instrumentation, genre, and performance style further complicates the development of these techniques that can be generalized to different musical contexts.
+
+\input{figures/neural networks/r128 sphere}
+
+\section{SALAMI dataset}
+\subsection{Overview}
+
+SALAMI (Structural Analysis of Large Amounts of Music Information) \cite{Smith2011DESIGNANNOTATIONS} aims to conduct massive structural analyses of different types of music.
+The project covers diverse music, from Western pop to Indian classical and from live to studio recordings.
+
+\subsubsection{Formal Analysis Definition}
+Formal analysis, in this context, doesn't refer to classifying the piece into a formal type (e.g., sonata, song, or canon) or reducing it into its Ursatz as in Schenkerian analysis.
+Instead, it means organizing and dividing the piece into specific sections and understanding how they relate.
+
+%%%%%%%%%%
+
+\subsubsection{Approaches to Music Analysis}
+
+The method proposed combines aspects of the following three approaches, separating the organization of instrumentation, musical material, and formal function.
+This allows for the analysis of a wide variety of music pieces in a consistent way using a constrained vocabulary.
+It's important to note that music structure is often hierarchical, and the appropriate timescale for analysis can be hard to determine.
+The proposed method includes a few markers to partly address this issue.
+
+Perceptual Approach: This involves listening for prominent harmonic or rhythmic boundaries in the piece to segment and apply labels to sections based on their similarity.
+However, this approach might not reflect the different structural roles of similar-sounding sections.
+
+Functional Approach: This involves dividing the song into its functional parts, like verses, choruses, intros, outros, etc.
+This might result in the same music being labeled differently based on its function or different musical ideas having the same functional label.
+
+Transcription Approach: This involves recording musical parameters like chord patterns and instrumentation directly.
+While this method may be less subjective, it may not provide a comprehensive view of the piece's structure.

### 2023-05-13 introduction/Subsections/Assumptions.tex
Updates from Overleaf

--- 2023-05-10 introduction/Subsections/Assumptions.tex
@@
 
-This thesis posits that high-level musical concepts manifest over time and remain invariant to specific attributes such as tonal quality, tempo, key, orchestration, signal noise, etc.
-This is akin to a sheet music composition performed in myriad ways using diverse instruments and styles while preserving its essence.
+This thesis posits the existence of high-level musical concepts invariant to specific attributes such as tonal quality, tempo, key, orchestration, and signal noise that evolve and unfolds through time.
+This idea parallels the nature of sheet music, which maintains its essence despite being interpreted through diverse performances using various instruments and styles.
 
-Abstract features, such as melody, harmony, rhythm, tempo, form, and expression, can be identified irrespective of waveform or production style.
-This approach offers an objective and comprehensive insight into a piece's musical content and meaning, analogous to how analyzing sheet music unveils a composition's underlying structure and intent.
+Abstract high-level features like melody, harmony, rhythm, tempo, form, and expression can be discerned regardless of waveform or production style.
+This approach provides an objective, comprehensive insight into a composition's musical content and meaning, much like analyzing sheet music uncovers its structural and intentional foundation.
 
-Although a waveform might have limited sheet music representations that accurately encapsulate its musical components, a single sheet music composition can be performed infinitely using various instruments, voices, tempos, and interpretations.
-The distinct tonal quality of a waveform is significantly influenced by the specific instrument timbre or production technology employed in its creation, complicating the transcription of its sonic properties into precise sheet music notation.
+It's worth noting that while a single waveform might have a limited number of sheet music representations that adequately capture its musical components, a single piece of sheet music can be interpreted in infinite ways through different instruments, voices, tempos, and interpretations.
+The distinct tonal quality of a waveform, heavily influenced by the specific timbre of the instrument or production technology, adds complexity to the transcription of its sonic properties into accurate sheet music notation.
 
-Moreover, this distinct tonal quality is represented by high-level natural language concepts embedded within a rich cultural and sociological tradition.
+Despite the differences in cultural contexts, stylistic elements, time signatures, key signatures, and sonic properties, we propose that figures \ref{fig:mahler} and \ref{fig:giant_steps} share a similarity.
+Both pieces carry the same musicological fingerprint, derived from the propulsion of their melodic and harmonic contours through non-diatonic major thirds.
 
-\begin{figure}
+This concept finds grounding in the theories of Kurt Koffka, a founder of the Gestalt school of psychology, who proposed a holistic approach to understanding complex forms, contrary to the structuralist practice of reducing mental processes into basic elements.
+His work, primarily embodied in the book, "Principles of Gestalt Psychology," established the foundation for Gestalt psychology and its applications to perception \cite{Koffka2013PrinciplesPsychology}.
+
+When applied to music, the principles of Gestalt psychology offer insights into how we perceive, organize, and interpret musical patterns.
+They suggest that our minds perceive auditory input much like visual input, seeking patterns and structures.
+This understanding significantly contributes to the comprehension of cognitive processes in musical perception and organization, influencing music theory, cognition, and therapy \cite{Lerdahl1985AMusic}.
+
+\begin{figure}[ht]
     \centering
@@
 
-\begin{figure}
+\begin{figure}[ht]
     \centering
@@
 \end{figure}
-
-\subsection{Beyond Digital Signal Processing (DSP)}
-
-We argue that MIR research needs to incorporate a more balanced approach that considers the interdisciplinary nature of music and the importance of other domains beyond DSP.

### 2023-05-13 introduction/Subsections/Motivation.tex
Updates from Overleaf

@@
 \end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Schenkerian Analysis, developed by Austrian music theorist Heinrich Schenker, investigates the underlying structure of tonal music by focusing on the hierarchical relationships between pitches.
-This analytical approach is founded on the premise that all tonal music shares a fundamental structure known as "Ursatz" or "basic shape." The method identifies a piece's stepwise descending line (Urlinie) and bass arpeggiation (Bassbrechung), simplifying it to its essential elements and examining how different layers contribute to the overall structure.
-Central concepts in Schenkerian Analysis include prolongation levels, harmony, counterpoint, voice-leading, and Ursatz (fundamental structure).
-Despite criticism for reducing all tonal works to a limited number of background structures, Schenker highlights the significance of individual elaboration in determining a piece's identity and meaning.
-
-While such analysis is designed for the symbolic domain, we argue that musical abstraction is also feasible in the audio time domain.
-In this section, we explore the application of Schenkerian Analysis principles to the Music Information Retrieval (MIR) domain by examining the foreground, middle-ground, and background levels of musical structure as follows:
-
-\begin{itemize}
-\item \textbf{Foreground}: The surface level of a musical composition, consisting of the notes, rhythms, and articulations directly perceived by the listener, representing the most detailed level of the musical structure.
-
-\item \textbf{Middle-ground and mesostructures}: An intermediate level of analysis focusing on essential structural elements such as harmonic progressions, thematic materials, and voice-leading reductions that contribute to the overall composition.
-In the MIR domain, this level can also be understood as mesostructure.
-Mesostructures are intermediate levels of articulation between waveshapes' microstructure and musical forms' macrostructure.
-Examples of mesostructures include melody, arpeggios, syncopation, polyphonic grouping, and textural contrast.
-Mesostructures might have received limited attention in deep learning, as current models only focus on microstructures \cite{Mesostructures2023}.
-
-\item \textbf{Background}: The most abstract level of musical structure, representing the fundamental core consisting of the \textit{Urlinie} and \textit{Bassbrechung}, which serves as the foundation for the entire composition.
-\end{itemize}
-
-By understanding and applying Schenkerian Analysis principles to the MIR domain, we can better understand the complex relationships between different levels of musical structure in the audio time domain, allowing for a more comprehensive analysis of tonal music.
-
-%%%%%%%% PERCEPTION %%%%%%%%%%%%%
-
-Kurt Koffka (1886-1941) was a German psychologist and a founding member of the Gestalt school of psychology, along with Max Wertheimer and Wolfgang Köhler.
-Gestalt psychology emerged as a reaction against the structuralist approach to psychology, emphasizing analyzing mental processes into their most basic elements.
-Instead, Gestalt psychologists sought to understand the principles underlying the organization and perception of complex forms and wholes.
-
-Koffka's most significant contribution to the field was the development of the principles of Gestalt psychology and their application to perception.
-His 1935 book, ``Principles of Gestalt Psychology,'' remains a seminal work in the field \cite{Koffka2013PrinciplesPsychology}.
-In it, Koffka systematically describes the foundational concepts of Gestalt psychology and presents empirical evidence to support these ideas.
-
-Applying the principles of Gestalt psychology to music can provide valuable insights into the cognitive processes underlying musical perception, organization, and interpretation.
-In music, just as in visual perception, the human mind seeks to identify patterns and structures to make sense of the auditory input.
-Several Gestalt principles can be applied to understanding musical perception, such as the law of Prägnanz, grouping principles, and holistic processing.
-
-As with visual perception, the mind organizes musical information into the most straightforward and stable patterns.
-This principle can be observed in listeners' perceptions of harmony, melody, and rhythm.
-For example, Western tonal music is built upon hierarchical structures that allow the listener to make sense of complex musical information by organizing it coherently \cite{Lerdahl1985AMusic}.
-
-In conclusion, applying the principles of Gestalt psychology to the study of music has led to a deeper understanding of the cognitive processes underlying musical perception and organization.
-This approach has influenced various areas of music research, including music theory, music cognition, and music therapy.
-
-%%%%%%%%%%
-
-Piaget's theory of cognitive development posits that children acquire knowledge from sensory and motor experiences in their early stages, from birth to around 18 months, during the \textit{sensorimotor stage} \cite{Huitt2003PiagetsDevelopment}.
-This stage sees the emergence of early representational thought through basic actions such as sucking, grasping, looking, and listening.
-As children progress through different developmental stages until adolescence and adulthood, their reasoning progressively moves toward abstract ideas and deductive logic.
-Schemas, higher-order cognitive structures hypothesized to underlie many aspects of human knowledge and skill, emerge during this process, which Piaget interprets through an equilibration mechanism that balances new information with old knowledge.
-This mechanism involves \textit{assimilation} and \textit{accommodation}, which entail taking in further information to fit pre-existing schemas and modifying existing schemas resulting from the latest information.
-In the context of learning, complex structures are based on simpler ones, and knowledge transfer occurs when dynamic systems capable of generalization are created.
-\cite{audioselfsupsurvey}
-
-There are similarities between assimilation and accommodation in Piaget's theory of cognitive development and backpropagation in DL, both of which involve modifying existing structures based on new information.
-However, it should be noted that these processes' underlying mechanisms and contexts are entirely distinct.
-While assimilation and accommodation involve modifying mental structures to incorporate new information, backpropagation entails adjusting neural network weights to improve output predictions.
-
-%%%%%%%%%%

### 2023-05-13 introduction/Subsections/Previous work.tex
Updates from Overleaf

\section{Previous work}

Learning deep audio embeddings can somehow be considered as breaking down the essence of tonal music to its fundamental and most empirical elements. Dissecting musical structures from the most ethereal and spiritual foreground  to the foundational numerical nuances.

It also delves into middle-ground elements and mesostructures \cite{Mesostructures2023}, bridging micro and macro structures with harmonic progressions, thematic materials, and voice-leading reductions.

\subsection{}

### 2023-05-13 methods/subsections/model architecture and training strategy.tex
Updates from Overleaf

@@
 
-\subsection{Problem to solve}
-
-\subsection{Self-Supervised Learning (SSL)}
+\subsubsection{Self-Supervised Learning (SSL)}
 
@@
 This approach to learning is inspired by the way humans and animals learn from their environment, where a great deal of knowledge is acquired through observation and interaction without explicit instruction.
-SSL algorithms often involve tasks where the model learns to predict or reconstruct parts of the input data, such as predicting the next word in a sentence or completing an image with missing pixels.
 
@@
 \end{enumerate}
+
+Further understanding of the cognitive processes in music can be obtained through Jean Piaget's theory of cognitive development.
+Piaget suggests that children acquire knowledge through sensory and motor experiences in their early stages, with reasoning gradually evolving toward abstract ideas and deductive logic through the development of schemas—cognitive structures that underlie human knowledge and skill \cite{Huitt2003PiagetsDevelopment}.
+These schemas evolve through an equilibration mechanism that incorporates new information with pre-existing knowledge, involving processes of assimilation and accommodation \cite{audioselfsupsurvey}.
+
+Although there are resemblances between assimilation and accommodation in Piaget's theory and backpropagation in Deep Learning (DL), these processes occur in distinct mechanisms and contexts.
+Assimilation and accommodation modify mental structures to incorporate new information, while backpropagation adjusts neural network weights to enhance output predictions.
 
@@
 
-Unknown invariance: Unknown invariances are transformations or changes the model has not been explicitly designed to handle.
+Unknown invariance: Unknown invariances are transformations the model has not been explicitly designed to handle.
 However, it still manages to be robust due to its learning capabilities.
@@
 
-\subsection{Contrastive Learning of Musical Representations (CLMR)}
+\subsubsection{Contrastive Learning of Musical Representations (CLMR)}
 
@@
 
-\subsection{Triplet Siamese Networks}
+\subsubsection{Triplet Siamese Networks}
 
@@
 
-$y_{c_o}(n)$ is the output for the $c_o$-th output channel at position $n$
-$C_{\text{in}}$ is the number of input channels
-$x_{c_i}(n)$ is the input for the $c_i$-th input channel at position $n$
-$w_{c_o, c_i}(k)$ is the kernel weight for the $c_o$-th output channel and $c_i$-th input channel at position $k$
-$K$ is the kernel size
-The stride is set to 1, and padding is set to 1 (equal padding $\lfloor K/2 \rfloor$ on both sides)
-s
+$y_{c_o}(n)$ is the output for the $c_o$-th output channel at position $n$, $C_{\text{in}}$ is the number of input channels, $x_{c_i}(n)$ is the input for the $c_i$-th input channel at position $n$, $w_{c_o, c_i}(k)$ is the kernel weight for the $c_o$-th output channel and $c_i$-th input, channel at position $k$, and $K$ is the kernel size.
+The stride is set to 1 and padding to 1 (equal padding $\lfloor K/2 \rfloor$ on both sides).
+
 \item Batch normalization.
@@
 We pad the waveforms to the same  maximum length among the collection, perform online triplet mining to find the hardest negatives and return the padded anchors, positives, and hardest negatives.
+
+We have intentionally chosen to use zero padding instead of array truncating in our experiment.
+This decision was based on our belief that preserving the integrity of the music data was more critical, despite the potential trade-off with computational efficiency during the normalization process.
 
@@
 
-We have adapted the original architecture for our experiments to our purpose, which consists of the final average pooling step.
+We have adapted the original architecture to our purpose, which consists of the final average pooling step.
 
@@
 
-\begin{itemize}
-  \item \(y_i\) represents the output tensor after the average pooling operation,
-  \item \(x_{ij}\) represents the elements in the 2D input tensor,
-  \item \(N\) is the number of elements along the second dimension of the input tensor,
-  \item \(i\) iterates over the first dimension of the tensors, and
-  \item \(j\) iterates over the second dimension of the input tensor.
-\end{itemize}
+$y_i$ represents the output tensor after the average pooling operation, $x_{ij}$ represents the elements in the 2D input tensor, $N$ is the number of elements along the second dimension of the input tensor, $i$ iterates over the first dimension of the tensors, and $j$ iterates over the second dimension of the input tensor.
 
@@
 \subsubsection{Positive sample generation}
-Given an anchor audio signal $A[n]$, we generate a positive signal $P[n]$ by applying a series of audio effects and adding noise.
+Given an anchor audio signal $A[n]$, we generate a positive signal $P[n]$ by applying a series of amplitude, time-domain, frequency-domain, modulation, reverberation, and nonlinear effects with additive noise on top.
+
 Let $g \in [-12, 0]$ represent the gain, $\Delta p \in [-1200, 1200]$ the pitch shift, $h_R[n]$ the impulse response of the reverb with parameters in $[0, 100]$, $h_C[n]$ the impulse response of the chorus with parameters determined by the specified ranges, $d \in [0, 30]$ the overdrive parameter, $\alpha \in [0.9, 1.1]$ the speed change factor, $\beta \in [0.9, 1.1]$ the stretch factor, $f_m \in [0.1, 100]$ the modulation frequency of the tremolo, and $d_m \in [1, 101]$ the depth of the tremolo.

### 2023-05-14 abstract/abstract.tex
Updates from Overleaf

--- 2023-02-09 abstract/abstract.tex
@@
 
-The abstract should have at least 200 but not more than 600 words. Placed on the right page next to a blank left page.
+Music, an integral part of human culture, offers a diverse yet complex field of study due to its intricate styles, mutable ground truth, and subjective nature.
+This research, conducted in collaboration with Epidemic Sound AB and the Music Technology Group (MTG) at Universitat Pompeu Fabra (UPF), employs self-supervised contrastive learning of musical representation to uncover the fundamental structure of Western tonal music.
+
+Embracing a subtle novel approach, this process is facilitated by applying Siamese networks with a triplet loss, mimicking human aural skills in interpreting music to discern abstract and semantic musical elements, irrespective of the sonic qualities.
+The study replaces traditional acoustical features with deep audio embeddings to compute high-level, sound-agnostic, and content-sensitive music identification.
+
+Results XXXXXX
+
+The preliminary results suggest that our approach to learning music-informed embeddings holds significant potential for nearly all MIR downstream tasks.
+Music-motivated embeddings represent a promising technique, adaptable potentially to other tasks hindered by data scarcity.
+This method could significantly influence advancements in intelligent music recommendation systems and the efficient enforcement of intellectual property rights.
 
 \bigskip
-Keywords: Music; Music Theory; Music Information Retrieval; Music Structure Analysis; Machine Learning; Neural Networks; Deep Learning
+Keywords: Music Information Retrieval; Music Structure Analysis; Deep Audio Embeddings, Aural Skills
 

### 2023-05-14 evaluation/subsections/beyond dsp.tex
Updates from Overleaf

@@
 While this method may be less subjective, it may not provide a comprehensive view of the piece's structure.
+
+\section{\textit{Embeddiogram} custom feature}
+
+Features extracted from audio files play a vital role in characterizing and differentiating sound and music.
+One such feature, known as the \textit{Embeddiogram}, offers a unique and powerful representation of an audio signal.
+The Embeddiogram is derived by applying a pre-trained neural network model to windowed segments of an audio signal, generating a sequence of embedding vectors.
+These embedding vectors collectively form a high-dimensional description of the audio signal's structure and content.
+
+Below is a detailed explanation of computing the Embeddiogram from a given audio signal.
+This process comprises five key steps, including loading the audio data, slicing the audio data into windowed segments, processing each window using a pre-trained model to produce an embedding, collecting these embeddings, and finally normalizing the Embeddiogram.
+
+\begin{enumerate}
+\item \textbf{Load the audio data}: The audio data is loaded into memory as a one-dimensional array, denoted as $\text{input\_audio}$, of length $N$.
+
+\item \textbf{Slice the audio data}: The audio data is segmented into overlapping windows.
+Each window contains $w$ samples, and consecutive windows are separated by $h$.
+This gives a total of $H$ windows, defined as:
+\begin{equation}
+H = 1 + \left\lfloor \frac{N - w}{h} \right\rfloor
+\end{equation}
+In the case where $\left( N - w \right) \mod h > 0$, we have $H += 1$ to account for the final, potentially smaller, window.
+
+\item \textbf{Process each window}: Each window of audio data is processed independently, passed through the pre-trained neural network model and transformed into an embedding vector.
+Formally, for each window $w_i$ of audio data, we have:
+\begin{equation}
+\text{embedding}_i = \text{model}(w_i)
+\end{equation}
+
+\item \textbf{Collect the embeddings}: The embedding vectors are collected and stacked together.
+Each row represents a feature vector for a given time frame to form the \textit{Embeddiogram}, denoted as $\text{embeddiogram}$:
+\begin{equation}
+\text{embeddiogram} = \begin{bmatrix} \text{embedding}_1 \\ \text{embedding}_2 \\ \vdots \\ \text{embedding}_H \end{bmatrix}
+\end{equation}
+
+\item \textbf{Normalize the Embeddiogram}: The Embeddiogram is normalized to have a minimum value of 0 and a maximum value of 1. The normalization process is given by:
+\begin{equation}
+E'_{ij} = \frac{e_{ij} - \min(E)}{\max(E) - \min(E)}
+\end{equation}
+\end{enumerate}

### 2023-05-14 introduction/Subsections/Assumptions.tex
Updates from Overleaf

@@
 This thesis posits the existence of high-level musical concepts invariant to specific attributes such as tonal quality, tempo, key, orchestration, and signal noise that evolve and unfolds through time.
-This idea parallels the nature of sheet music, which maintains its essence despite being interpreted through diverse performances using various instruments and styles.
-
-Abstract high-level features like melody, harmony, rhythm, tempo, form, and expression can be discerned regardless of waveform or production style.
-This approach provides an objective, comprehensive insight into a composition's musical content and meaning, much like analyzing sheet music uncovers its structural and intentional foundation.
-
-It's worth noting that while a single waveform might have a limited number of sheet music representations that adequately capture its musical components, a single piece of sheet music can be interpreted in infinite ways through different instruments, voices, tempos, and interpretations.
+This idea parallels the nature of the symbolic domain (sheet music), which maintains its essence despite being interpreted through diverse performances using various instruments and styles.
+While a single waveform might have a limited number of sheet music representations that adequately capture its musical components, a single piece can be interpreted in infinite ways through different instruments, voices, tempos, and interpretations.
 The distinct tonal quality of a waveform, heavily influenced by the specific timbre of the instrument or production technology, adds complexity to the transcription of its sonic properties into accurate sheet music notation.
 
-Despite the differences in cultural contexts, stylistic elements, time signatures, key signatures, and sonic properties, we propose that figures \ref{fig:mahler} and \ref{fig:giant_steps} share a similarity.
-Both pieces carry the same musicological fingerprint, derived from the propulsion of their melodic and harmonic contours through non-diatonic major thirds.
+Abstract high-level features can be discerned regardless of waveform or production style.
+This approach provides an objective, comprehensive insight into a composition's musical content and meaning, much like analyzing sheet music uncovers its intentional foundation.
 
-This concept finds grounding in the theories of Kurt Koffka, a founder of the Gestalt school of psychology, who proposed a holistic approach to understanding complex forms, contrary to the structuralist practice of reducing mental processes into basic elements.
-His work, primarily embodied in the book, "Principles of Gestalt Psychology," established the foundation for Gestalt psychology and its applications to perception \cite{Koffka2013PrinciplesPsychology}.
+For example, despite the differences in cultural contexts, stylistic elements, time signatures, key signatures, and sonic properties, we propose that figures \ref{fig:mahler} and \ref{fig:giant_steps} share a similarity.
+Both pieces carry the same musicological fingerprint so to say, derived from the propulsion of their melodic and harmonic contours through non-diatonic major thirds.
+
+This concept finds grounding in the theories of Kurt Koffka, a founder of the Gestalt school of psychology, who proposed a holistic approach to understanding complex forms, contrary to the structuralist practice of reducing mental processes into essential elements \cite{Koffka2013PrinciplesPsychology}.
 

### 2023-05-14 introduction/Subsections/Objectives.tex
Updates from Overleaf

--- 2023-04-26 introduction/Subsections/Objectives.tex
@@
 
-This study seeks to discover a generalization of the fundamental tonal structure in Western music by creating and examining an embedding space that can be applied to downstream Music Information Retrieval (MIR) tasks.
+This study aims to explore the core tonal structure of Western music by constructing and analyzing an embedding space applicable to subsequent Music Information Retrieval (MIR) tasks.
 
-Neural networks have recently facilitated the development of low-dimensional musical embeddings that capture essential musical features, enabling the computation of content-based similarity between musical passages \cite{KimLEARNINGLOSS}\cite{Hung2022Feature-informedClassification}.
-An embedding function $f(x) \in \mathbb{R}^d$ maps a given course $x$ to a vector in the real space $\mathbb{R}^d$, allowing the measurement of similarity between two musical passages using Euclidean distance, as denoted by the formula $D_{i,j} = ||f(x_i) - f(x_j)||^2$.
-The success of such systems hinges on the level of musical abstraction and the embedding space's capacity to interpret music in a manner consistent with human perception.
-As a result, a suitable embedding space is vital for producing output that aligns with human expectations.
+By employing a blend of MIR computational techniques and a musicological approach, it intends to examine a wide spectrum of musical works across diverse styles and genres.
+Crucial to this is the understanding of aural skills – perceptual and cognitive abilities essential for interpreting musical works through listening.
 
-This research aims to thoroughly analyze musical works from various styles and genres, employing computational techniques from Music Information Retrieval (MIR) and a musicological perspective to contextualize the findings.
-Aural skills, encompassing perceptual and cognitive abilities, are necessary for understanding musical works through listening.
-The underlying musical structure consists of a systematic arrangement of elements that generate a coherent and expressive musical work.
-This study seeks to provide new insights into these components of musical composition and further our comprehension of their interrelationships.
+The research focuses on the learning of a single embedding, $e(M)$, for a music piece $M$ which encapsulates the underlying high-level content such as melody contour, harmony inter-relationships, and other holistic elements.
+The structuring of the embedding space will prioritize the clustering of similar content and sonic quality features while maintaining a clear distinction between them.
 
-We denote a single embedding for a music piece as $e(M)$.
-
-For a given music piece $M$, we aim to learn a single embedding, $e(M)$, that captures both the underlying content (melody, harmony, critical, holistic elements) and production aspects.
-The embedding space should be structured to cluster similar content and production features together, effectively separating the two aspects.
-Formally, our objective is to learn the embedding function $e(M)$ such that:
-
-\begin{itemize}
-\item Similar content features are closer in the embedding space: $|e(M_1) - e(M_2)| < \epsilon_c$ for music pieces $M_1$ and $M_2$ with similar content.
-\item Similar production features are closer in the embedding space: $|e(M_1) - e(M_3)| < \epsilon_p$ for music pieces $M_1$ and $M_3$ with similar production.
-\item Distinct content and production features are further apart in the embedding space.
-\end{itemize}
-
-We propose learning a single embedding $e(M)$ that captures content and production features, with the embedding space structured to cluster similar aspects together, effectively distinguishing between the two.
-
-Music is a complex and multi-dimensional phenomenon, and developing a model that emulates human aural skills is challenging.
-Nonetheless, recent advancements in deep learning offer promising avenues for creating a model that achieves satisfactory results in specific music-related tasks.
-This study will employ deep learning techniques to explore the correlation between aural skills and the underlying tonal structure of music.
-
-Additionally, this research contends that MIR studies should transition from a solely technical-centered approach to a more balanced and comprehensive method that integrates other pertinent domains such as musicology and music theory.
-This shift will enable a better understanding of the interplay between technical and musical aspects of music, enhancing our comprehension of music signals and music itself.
+The goal is to create an embedding $e(M)$ that captures high-level musical content and remains agnostic to production features.

### 2023-05-14 introduction/Subsections/Previous work.tex
Updates from Overleaf

@@
-\section{Previous work}
+\section{Related work}
 
@@
 
-\subsection{}
+\subsection{XXXX}
+
+Neural networks have recently facilitated the development of low-dimensional musical embeddings that capture essential musical features, enabling the computation of content-based similarity between musical passages \cite{Kim2021LearningLoss}\cite{Hung2022Feature-informedClassification}.
+An embedding function $f(x) \in \mathbb{R}^d$ maps a given course $x$ to a vector in the real space $\mathbb{R}^d$, allowing the measurement of similarity between two musical passages using Euclidean distance, as denoted by the formula $D_{i,j} = ||f(x_i) - f(x_j)||^2$.
+The success of such systems hinges on the level of musical abstraction and the embedding space's capacity to interpret music in a manner consistent with human perception.
+As a result, a suitable embedding space is vital for producing output that aligns with human expectations.

### 2023-05-14 introduction/Subsections/Previous work.tex
Updates from Overleaf

--- 2023-05-13 introduction/Subsections/Previous work.tex
@@
-\section{Previous work}
+\section{Related work}
 
-Learning deep audio embeddings can somehow be considered as breaking down the essence of tonal music to its fundamental and most empirical elements.
-Dissecting musical structures from the most ethereal and spiritual foreground  to the foundational numerical nuances.
+Neural networks have recently facilitated the development of low-dimensional embeddings that capture essential musical features, enabling the computation of various task-specific aspects.
+These aspects include:
 
-It also delves into middle-ground elements and mesostructures \cite{Mesostructures2023}, bridging micro and macro structures with harmonic progressions, thematic materials, and voice-leading reductions.
+\begin{itemize}
 
-\subsection{}
+\item The utilization of multi-level music segmentation through deep audio embeddings has replaced manually engineered features and demonstrated significant performance improvement over existing approaches \cite{SalamonDeepSegmentation}.
+
+\item The enhancement of environmental sound classification, suggesting the potential for further improvements through class-specific augmentations \cite{Kim2020OneStrategies}.
+
+\item The improvement of vocal-centric music tasks using cross-domain audio embedding \cite{Kim2021LearningLoss}.
+
+\item The enhancement of audio classification through a combination of task-specific and pre-trained features \cite{Hung2022Feature-informedClassification}.
+
+\item The creation of a music similarity search engine specifically for video producers \cite{epidemic}.
+
+\item The improved performance in Music Emotion Recognition (MER) tasks, eliminating the necessity for expert human engineering \cite{KohComparisonRecognition}.
+
+\item The resolution of the cross-modal text-to-music retrieval problem, enabling content creators to find music that matches the emotion conveyed in their text-based stories \cite{WonEmotionStories}.
+\end{itemize}
+
+Moreover, deep audio embeddings offer the advantage of transferability.
+Once trained, these embeddings can be utilized as a starting point for various other tasks, thus saving computational resources and time compared to training a model from scratch.
+
+Given their demonstrated success in the literature and their potential for transfer learning, exploring deep audio embeddings for MIR downstream tasks seems worthwhile.
+
+Returning to musicological influences, the concept of the middle ground can be compared to the mesostructure in music.
+The middle ground, analogous to the mesostructure, represents the intermediate-level musical patterns that bridge the micro and macro structures.
+This element is often overlooked when applying deep learning to music.
+As emphasized by \cite{Mesostructures2023}, models that address this mesostructure level could significantly enrich tasks such as music analysis, composition, and retrieval, providing a more holistic understanding of music similar to the insights gained from analyzing the middle-ground in Schenkerian analysis.
+\cite{Introduction_to_Schenkerian_Analysis}

### 2023-05-14 MasterThesis.tex
Updates from Overleaf

@@
   Uncovering underlying high-level musical content in the temporal domain \\
-  \small Leveraging self-supervised deep neural networks, inductive bias, and aural music skills to learn music embeddings with applications to MIR downstream tasks}
+  \small Leveraging self-supervised deep neural networks, inductive bias, and aural skills to learn music embeddings with applications to MIR downstream tasks}
 

### 2023-05-14 methods/subsections/model architecture and training strategy.tex
Updates from Overleaf

@@
 
-A Siamese Network, a deep learning architecture introduced by Bromley and LeCun in the early 1990s \cite{Bromley1993SignatureNetwork}, is designed explicitly for tasks involving similarity or comparison between two input instances, such as signature verification.
+A Siamese Network, a deep learning architecture introduced by Bromley and LeCun in the early 1990s \cite{Bromley1993SignatureNetwork}, is designed explicitly for tasks involving similarity or comparison between two input instances.
 Its name derives from the structure, which consists of two or more identical subnetworks connected in parallel and joined at the output layer.
 These subnetworks share the same architecture, weights, and hyperparameters, allowing for more efficient memory usage and computational complexity.
+
 This design is particularly effective for learning from limited or imbalanced datasets, as it focuses on learning the similarity metric rather than specific features of individual classes.

### 2023-05-15 evaluation/subsections/beyond dsp.tex
Updates from Overleaf

@@
 
-Let's pick a core MIR task as a sample to display such complexity: Music Structure Analysis (MSA), an interdisciplinary field that aims to understand the structure of music \cite{Nieto2020Audio-BasedApplications}.
+While the usefulness of deep audio embeddings can be evaluated in several tasks, we have chosen a core MIR task for its popularity and complexity: Music Structure Analysis (MSA).
+This interdisciplinary field aims to understand the structure of music \cite{Nieto2020Audio-BasedApplications}.
 However, due to subjectivity, ambiguity, and data scarcity, audio-based MSA faces challenges like boundary placement ambiguity and similarity quantification \cite{NietoPerceptualMusic}.
@@
 The main principles of MSA were initially defined as homogeneity, novelty, and repetition, with the addition of regularity.
-The checkerboard kernel technique is a simple and effective method for MSA based on the homogeneity principle.
-The kernel, with a checkerboard-like structure, is convolved over the main diagonal of a Self-Similarity Matrix (SSM) such as $S_{ij}$ is the similarity between time frames $i$ and $j$, $\vec{x}_i$ is the vector representation of time frame $i$, and $\left| \vec{x}_i \right|$ is the Euclidean norm of vector $\vec{x}_i$.
-The dot product of two vectors $\vec{x}_i$ and $\vec{x}_j$ is denoted by $\vec{x}_i \cdot \vec{x}_j$.
-
-\input{introduction/subsections/equations/SSM equation}
-
-This yields a novelty curve highlighting sudden changes in the selected musical features from which to extract the segment boundaries.
-
-\input{introduction/subsections/equations/Novelty equation}
-
-Mathematical operations are used on predefined principles such as homogeneity and repetition to analyze a musical structure.
-It explores features extracted from a musical signal and identifies peaks in a novelty curve to extract segment boundaries.
-In contrast, human aural skills rely on the perception and interpretation of music by human listeners based on cultural and academic background.
-They can capture subtle nuances of musical structure, but those still are subjective and can vary across listeners.
-
-Combining technical tasks, aural skills, and music perception is challenging due to the complexity and subjectivity of musical perception, discrepancies between the features extracted by DSP techniques and the features perceived by humans, and the variability of musical signals and individual differences in musical perception.
-
-Purely mathematical approaches may not always reflect how humans perceive music and may not capture the subtle variations in timing or harmonic relationships critical to musical perception.
-Variability in musical signals due to instrumentation, genre, and performance style further complicates the development of these techniques that can be generalized to different musical contexts.
 
@@
 Features extracted from audio files play a vital role in characterizing and differentiating sound and music.
-One such feature, known as the \textit{Embeddiogram}, offers a unique and powerful representation of an audio signal.
+One such feature, the \textit{Embeddiogram}, offers a unique and powerful representation of an audio signal.
 The Embeddiogram is derived by applying a pre-trained neural network model to windowed segments of an audio signal, generating a sequence of embedding vectors.
@@
 \end{enumerate}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/images/embeddiogram_SALAMI_track_2.png}
+    \caption[Embeddiogram]{Caption}
+    \label{fig:embeddiogram}
+\end{figure}

### 2023-05-15 figures/equations/ReLU.tex
Updates from Overleaf

@@
 It helps introduce non-linearity to the model and accelerates training due to its computational efficiency.
-
-ReLU is a piecewise linear function that outputs the input value if positive and zero otherwise. Mathematically, it can be represented as:
-
-\begin{equation}
-  f(x) =
-  \begin{cases}
-    x & \text{if } x > 0 \\
-    0 & \text{otherwise}
-  \end{cases}
-\end{equation}
-
-Derivative: The derivative of the ReLU function is used during backpropagation to update the weights in the neural network. It is given by:
-
-\begin{equation}
-  f'(x) =
-  \begin{cases}
-    1 & \text{if } x > 0 \\
-    0 & \text{otherwise}
-  \end{cases}
-\end{equation}
-
-Advantages: ReLU offers several advantages over other activation functions, such as sigmoid or hyperbolic tangent (tanh).
-These include faster training due to reduced computational complexity and mitigating the vanishing gradient problem.
-
-Drawbacks: Despite its benefits, ReLU has some flaws, such as the "dying ReLU" issue, where neurons can become inactive during training and never fire again.

### 2023-05-15 introduction/Subsections/Assumptions.tex
Updates from Overleaf

@@
 
-This thesis posits the existence of high-level musical concepts invariant to specific attributes such as tonal quality, tempo, key, orchestration, and signal noise that evolve and unfolds through time.
+This thesis posits the existence of high-level musical concepts invariant to specific attributes such as sound quality, tempo, key, orchestration, and signal noise that evolve and unfolds through time.
 This idea parallels the nature of the symbolic domain (sheet music), which maintains its essence despite being interpreted through diverse performances using various instruments and styles.

### 2023-05-15 introduction/Subsections/Motivation.tex
Updates from Overleaf

@@
 This passion fuels my quest for knowledge on extracting valuable information embedded within music in any domain, being my main interest in the audio and symbolic domain, contributing to developing more sophisticated and effective music-related technologies and solutions in the industrial landscape.
-
-I advocate for exposure as the primary method of learning music, emphasizing the importance of immersing oneself in various musical experiences to foster a holistic understanding of music as an art form.
-Individuals can cultivate well-rounded musical expertise by engaging with different styles, genres, techniques, and learning approaches, ultimately promoting creativity and experimentation.
 
@@
 
+Purely mathematical approaches may not always reflect how humans perceive music and may not capture the subtle variations in timing or harmonic relationships critical to musical perception.
+
 I have consistently been inspired by musicians and researchers who strive to uncover musical ground truth within an existing tonal paradigm, such as Heinrich Schenker and his school of thought \cite{Komar1959SchenkersStructure}, particularly by challenging it, exemplified by Arnold Schoenberg \cite{Samson1974SchoenbergsMusic}, George Russell \cite{LydianRussell} or Ernst Levy \cite{LevyAHarmony}.
@@
 \includegraphics[clip,width=\columnwidth]{figures/schenkerian analysis/SchubertOp4no3.png}% 
-\caption[Small excerpt of \textit{Wandrers Nachtlied, Op.
+\caption[Excerpt of \textit{Wandrers Nachtlied, Op.
 4, D.

### 2023-05-15 introduction/Subsections/Previous work.tex
Updates from Overleaf

@@
 
-\item The utilization of multi-level music segmentation through deep audio embeddings has replaced manually engineered features and demonstrated significant performance improvement over existing approaches \cite{SalamonDeepSegmentation}.
+\item The utilization of multi-level music segmentation through deep audio embeddings to replace manually engineered features \cite{SalamonDeepSegmentation}.
 
-\item The enhancement of environmental sound classification, suggesting the potential for further improvements through class-specific augmentations \cite{Kim2020OneStrategies}.
+\item The enhancement of environmental sound classification \cite{Kim2020OneStrategies}.
 
@@
 
-Returning to musicological influences, the concept of the middle ground can be compared to the mesostructure in music.
-The middle ground, analogous to the mesostructure, represents the intermediate-level musical patterns that bridge the micro and macro structures.
+On top of that and returning to musicological influences, the middle ground in Schenkerian analysis can be compared to the mesostructure in music.
+Analogous to the mesostructure, it represents the intermediate-level musical patterns that bridge the micro and macro structures.
 This element is often overlooked when applying deep learning to music.

### 2023-05-15 methods/subsections/machine learning.tex
Updates from Overleaf

@@
 
-\subsection{Convolutional Neural Network (CNN)}
-
-A Convolutional Neural Network (CNN) is a deep-learning neural network. The architecture of a CNN is composed of several layers, including:
-
-\begin{itemize}
-
-\item \textbf{Convolutional layers:} These layers apply a convolution operation to the input data.
-The convolutional layers are designed to effectively learn local patterns and features in the audio data \footnote{For a visual explanation and further understanding of the convolution operation, please refer to this URL: \url{https://youtu.be/KuXjwB4LzSA}}.
-
-A convolution operation involves sliding a small window, called a filter or kernel, over input data to compute the dot product between the kernel and each local region of the data.
-The result is a new feature map highlighting patterns and essential information.
-
-Given a 2D input data represented as a matrix $I = [i_{ij}]{m \times n}$ and a filter $K = [k{ij}]_{p \times q}$, the convolution operation is defined as:
-
-\begin{equation}
-    (I * K)_{kl} = \sum_{i=1}^{p} \sum_{j=1}^{q} i_{k+i-1, l+j-1}k_{ij}
-\end{equation}
-
-Here, $k$ ranges from $1$ to $m-p+1$ and $l$ ranges from $1$ to $n-q+1$. The resulting feature map after applying the convolution is denoted by $(I * K)_{kl}$.
-
-The convolution operation slides the kernel $K$ over the input image $I$, performing an element-wise multiplication and sum of the local region centered at pixel $(k,l)$ to compute the value of each element in the output feature map, $(I * K)_{kl}$.
-This process is repeated for each pixel $(k,l)$, resulting in a new feature map that captures local patterns in the input image.
-
-\input{figures/neural networks/convolution}
-%Single CNN
-\input{figures/neural networks/Single_CNN}
-
-\item \textbf{Pooling layers:} These layers downsample the data, reducing the spatial or temporal dimensions of the input while retaining important information.
-A joint pooling operation is the max-pooling, which can be defined as follows: given an input matrix $I$ and a pooling window of size $m \times n$, the max-pooling operation selects the maximum value within each non-overlapping $m \times n$ region of the input matrix.
-This operation effectively reduces the input's dimensions while retaining the essential information in each area.
-\vspace*{3mm}
-
-%Single pooling layer
-\input{figures/neural networks/Single_Pooling_Layer}
-
-\item \textbf{Fully connected layers:} These layers connect every neuron in one layer to every neuron in another, allowing the network to learn non-linear combinations of the features discovered in the previous layers.
-Mathematically, a fully connected layer can be represented as $Y = XW + b$, where $X$ is the input matrix, $W$ is the weight matrix, $b$ is the bias vector, and $Y$ is the output matrix.
-\vspace*{3mm}
-
-\item \textbf{Output layer:} The output layer produces the final predictions of the network.
-
-\end{itemize}
-
-Compared to a traditional neural network, CNNs are more computationally efficient and have less number of parameters to train.
-This makes them more feasible for large-scale datasets and real-world problems.
-
-On top of that, one of the main advantages of using CNNs for audio analysis is that they can automatically and adaptively learn temporal hierarchies of features from audio data, which traditional audio processing methods may not do effectively.
-
-%Colour CNN
-\input{figures/neural networks/colour CNN}
-
 \newpage

### 2023-05-15 methods/subsections/model architecture and training strategy.tex
Updates from Overleaf

@@
 
+I advocate for exposure as the primary method of learning music, emphasizing the importance of immersing oneself in various musical experiences to foster a holistic understanding of music as an art form.
+Individuals can cultivate well-rounded musical expertise by engaging with different styles, genres, techniques, and learning approaches, ultimately promoting creativity and experimentation.
+
 Given the nature of our task, we propose using a Triple Siamese Network.
@@
 
-\subsubsection{Self-Supervised Learning (SSL)}
+\subsection{Self-Supervised Learning (SSL)}
 
@@
 
-\subsubsection{Contrastive Learning of Musical Representations (CLMR)}
+\subsection{Contrastive Learning of Musical Representations (CLMR)}
 
@@
 The input consists of an anchor, a positive instance (same class as the anchor), and a negative instance (different class).
-Each instance is processed by an identical subnetwork with shared architecture, weights, and hyperparameters.
+An identical subnetwork with shared architecture, weights, and hyperparameters processes each instance.
 
@@
 
-\subsection{XXX}
-\subsection{XXX}
+\subsection{Convolutional Neural Network (CNN)}
 
-\subsection{Encoder}
-\subsubsection{SampleCNN}
+A Convolutional Neural Network (CNN) is a deep-learning neural network. The architecture of a CNN is composed of several layers, including:
+
+\begin{itemize}
+
+\item \textbf{Convolutional layers:} These layers apply a convolution operation to the input data.
+The convolutional layers are designed to effectively learn local patterns and features in the audio data \footnote{For a visual explanation and further understanding of the convolution operation, please refer to this URL: \url{https://youtu.be/KuXjwB4LzSA}}.
+
+Let's consider a 1D input sequence or signal represented as a vector $I = [i_{i}]{n}$ and a filter $K = [k_{j}]_{p}$, where $n$ is the length of the input sequence and $p$ is the length of the filter.
+The convolution operation is defined as:
+
+\begin{equation}
+(I * K){k} = \sum{j=1}^{p} i_{k+j-1}k_{j}
+\end{equation}
+
+Here, $k$ ranges from $1$ to $n-p+1$. The resulting feature vector after applying the convolution is denoted by $(I * K)_{k}$.
+
+The convolution operation slides the kernel $K$ over the input sequence $I$, performing an element-wise multiplication and sum of the local region centered at element $k$ to compute the value of each element in the output feature vector, $(I * K)_{k}$.
+This process is repeated for each component $k$, resulting in a new feature vector that captures local patterns in the input sequence.
+
+In simple terms, the filter or kernel is slid across the 1D input data.
+For each position, we perform an element-wise multiplication of the filter with the portion of the input it currently covers and sums the results.
+This value becomes the corresponding entry in the output.
+The process is repeated for each position the filter can occupy.
+
+\item \textbf{Pooling layers:} These layers downsample the data, reducing the input dimensions while retaining important information.
+A joint pooling operation is the max-pooling, which can be defined as follows: given an input matrix $I$ and a pooling window of size $m \times n$, the max-pooling operation selects the maximum value within each non-overlapping $m \times n$ region of the input matrix.
+This operation effectively reduces the input's dimensions while retaining the essential information in each area.
+\vspace*{3mm}
+
+\item \textbf{Fully connected layers:} These layers connect every neuron in one layer to every neuron in another, allowing the network to learn non-linear combinations of the features discovered in the previous layers.
+Mathematically, a fully connected layer can be represented as $Y = XW + b$, where $X$ is the input matrix, $W$ is the weight matrix, $b$ is the bias vector, and $Y$ is the output matrix.
+\vspace*{3mm}
+
+\item \textbf{Output layer:} The output layer produces the final predictions of the network.
+
+\end{itemize}
+
+Compared to a traditional neural network, CNNs are more computationally efficient and have less number of parameters to train.
+This makes them more feasible for large-scale datasets and real-world problems.
+On top of that, one of the main advantages of using CNNs for audio analysis is that they can automatically and adaptively learn temporal hierarchies of features from audio data, which traditional audio processing methods may not do effectively.
+
+%Colour CNN
+\input{figures/neural networks/colour CNN}
+
+\subsection{Encoder: SampleCNN}
 
@@
 
-\item ReLU activation. \input{figures/equations/ReLU}
+\item ReLU activation.
+The Rectified Linear Unit (ReLU) activation function is a simple yet highly effective non-linear function used in neural networks.
+It helps introduce non-linearity to the model and accelerates training due to its computational efficiency.
 
@@
 
-\begin{tabular}{|c|c|c|}
-\hline
-\textbf{Layer} & \textbf{Input Channels} & \textbf{Output Channels} \\
-\hline
-1 & 128 & 128 \\
-\hline
-2 & 128 & 128 \\
-\hline
-3 & 128 & 256 \\
-\hline
-4 & 256 & 256 \\
-\hline
-5 & 256 & 256 \\
-\hline
-6 & 256 & 256 \\
-\hline
-7 & 256 & 256 \\
-\hline
-8 & 256 & 256 \\
-\hline
-9 & 256 & 512 \\
-\hline
-\end{tabular}
-
 After the hidden layers, there's another 1D convolutional layer with 512 input channels, 512 output channels, a kernel size of 3, a stride of 1, and padding of 1.
@@
 
-The output of the final convolutional layer is passed through an average pooling operation across the temporal dimension (dim=2).
+The original model has been modified slightly to serve our specific needs: the output from the final convolutional layer is now subjected to an average pooling operation across the temporal dimension.
+
+This adaptation of the original architecture incorporates an average pooling step at the end.
+
+\begin{figure}[ht]
+\centering
+\begin{equation}
+y_i = \frac{1}{N} \sum_{j=1}^{N} x_{ij}
+\end{equation}
+\caption{\small{Representation of the Average Pooling operation.
+Here, $y_i$ is the output tensor after the average pooling process.
+Each element $x_{ij}$ is part of the 2D input tensor.
+$N$ is the count of elements in the second dimension of the input tensor, while $i$ and $j$ are used to iterate over the first and second dimensions of the tensors, respectively.}}
+\end{figure}
 
@@
 \input{figures/my model/SampleCNN}
-
-We have adapted the original architecture to our purpose, which consists of the final average pooling step.
-
-\begin{equation}
-y_i = \frac{1}{N} \sum_{j=1}^{N} x_{ij}
-\end{equation}
-
-$y_i$ represents the output tensor after the average pooling operation, $x_{ij}$ represents the elements in the 2D input tensor, $N$ is the number of elements along the second dimension of the input tensor, $i$ iterates over the first dimension of the tensors, and $j$ iterates over the second dimension of the input tensor.
 

### 2023-05-15 abstract/abstract.tex
Updates from Overleaf

@@
 
-Music, an integral part of human culture, offers a diverse yet complex field of study due to its intricate styles, mutable ground truth, and subjective nature.
+This thesis posits the existence of high-level musical concepts invariant to sonic qualities that evolve and unfolds through time.
+This idea parallels the nature of the symbolic domain, which maintains its essence despite being interpreted through diverse performances using various instruments and styles.
+
 This research, conducted in collaboration with Epidemic Sound AB and the Music Technology Group (MTG) at Universitat Pompeu Fabra (UPF), employs self-supervised contrastive learning of musical representation to uncover the fundamental structure of Western tonal music.
@@
 
-Results XXXXXX
+Results XXXXXX TBC
 

### 2023-05-15 evaluation/subsections/beyond dsp.tex
Updates from Overleaf

@@
-\section{Music Structure Analysis as downstream task}
+\section{Music Structure Analysis (MSA) as downstream task}
 
@@
 The main principles of MSA were initially defined as homogeneity, novelty, and repetition, with the addition of regularity.
-
-\input{figures/neural networks/r128 sphere}
 
@@
 \begin{enumerate}
-\item \textbf{Load the audio data}: The audio data is loaded into memory as a one-dimensional array, denoted as $\text{input\_audio}$, of length $N$.
+\item \textbf{Load the audio data}: The audio data is loaded into memory as a one-dimensional array of length $N$.
 

### 2023-05-15 introduction/Subsections/Assumptions.tex
Updates from Overleaf

@@
 
-This thesis posits the existence of high-level musical concepts invariant to specific attributes such as sound quality, tempo, key, orchestration, and signal noise that evolve and unfolds through time.
+This thesis posits the existence of high-level musical concepts invariant to sonic qualities that evolve and unfolds through time such as melody, harmony, rhythm, form, motif, counterpoint, etc.
 This idea parallels the nature of the symbolic domain (sheet music), which maintains its essence despite being interpreted through diverse performances using various instruments and styles.
 While a single waveform might have a limited number of sheet music representations that adequately capture its musical components, a single piece can be interpreted in infinite ways through different instruments, voices, tempos, and interpretations.
-The distinct tonal quality of a waveform, heavily influenced by the specific timbre of the instrument or production technology, adds complexity to the transcription of its sonic properties into accurate sheet music notation.
 
@@
 For example, despite the differences in cultural contexts, stylistic elements, time signatures, key signatures, and sonic properties, we propose that figures \ref{fig:mahler} and \ref{fig:giant_steps} share a similarity.
-Both pieces carry the same musicological fingerprint so to say, derived from the propulsion of their melodic and harmonic contours through non-diatonic major thirds.
+Both pieces carry the same musicological fingerprint, so to say, derived from the propulsion of their melodic and harmonic contours through non-diatonic major thirds.
 

### 2023-05-15 introduction/Subsections/Motivation.tex
Updates from Overleaf

@@
 As a music enthusiast, professional musician, and scholar, I am passionately committed to exploring the foundational elements of musical composition, investigating the diverse techniques employed in creating musical works, and deciphering the intricate relationships among them.
-This passion fuels my quest for knowledge on extracting valuable information embedded within music in any domain, being my main interest in the audio and symbolic domain, contributing to developing more sophisticated and effective music-related technologies and solutions in the industrial landscape.
 
-On top of that, I argue that MIR research needs to incorporate a more balanced approach that considers the interdisciplinary nature of music and the importance of other domains beyond DSP.
+This passion fuels my quest for knowledge on extracting valuable information embedded within music in any domain, being my main interest in the audio and symbolic domains, contributing to developing more sophisticated and effective music-related technologies and solutions in the industrial landscape.
 
-\subsubsection{Academic motivation}
-
-The emergence of self-supervised models that learn embedding spaces for retrieving musical content from audio signals has unveiled new opportunities in academic research.
-By capturing high-level semantic information from raw audio data in an unsupervised manner, these models can potentially revolutionize various aspects of the music industry.
-Their applications encompass music information retrieval, sharing learned latent representations for MIR \cite{HamelTransferSimilarity}, and fostering interdisciplinary research and innovation in musicology, computer science, and artificial intelligence.
-
-\subsubsection{Industrial and corporate motivation}
-
-In the industrial and corporate realm, the embedding spaces generated by these models can be utilized to create personalized and intelligent music recommendation systems \cite{Chen2020LearningRecommendation}\cite{epidemic}, facilitate effective enforcement of intellectual property rights, and contribute to the development of more sophisticated audio editing-production tools and technical products \cite{WonEmotionStories}.
-These advancements ultimately enhance our interaction with music in the digital age, promoting innovation and collaboration across the music industry.
+\subsubsection{Academic and industrial motivation}
 
@@
 
+The emergence of self-supervised models that learn embedding spaces for retrieving musical content from audio signals has unveiled new opportunities in academic research.
+By capturing high-level semantic information from raw audio data in an unsupervised manner, these models can potentially revolutionize various aspects of the music industry.
+
+In the industrial and corporate realm, the embedding spaces generated by these models can be utilized to create all sorts of valuable products and user experiences for content creators.
+These advancements ultimately enhance our interaction with music in the digital age, promoting innovation and collaboration across the music industry.
+
 \subsection{About music aural skills and high-level perceptual concepts}
@@
 Purely mathematical approaches may not always reflect how humans perceive music and may not capture the subtle variations in timing or harmonic relationships critical to musical perception.
+We argue that MIR research needs to incorporate a more balanced approach that considers the interdisciplinary nature of music and the importance of other domains beyond digital signal processing.
 
-I have consistently been inspired by musicians and researchers who strive to uncover musical ground truth within an existing tonal paradigm, such as Heinrich Schenker and his school of thought \cite{Komar1959SchenkersStructure}, particularly by challenging it, exemplified by Arnold Schoenberg \cite{Samson1974SchoenbergsMusic}, George Russell \cite{LydianRussell} or Ernst Levy \cite{LevyAHarmony}.
+I have consistently been inspired by musicians and researchers who strive to uncover musical ground truth within an existing tonal paradigm, such as Heinrich Schenker and his school of thought \cite{Komar1959SchenkersStructure}, and particularly by challenging it, exemplified by Arnold Schoenberg \cite{Samson1974SchoenbergsMusic}, George Russell \cite{LydianRussell} or Ernst Levy \cite{LevyAHarmony}.
 These approaches aim to identify abstract concepts that reinforce or disrupt the tonal foundation.

### 2023-05-15 introduction/Subsections/Objectives.tex
Updates from Overleaf

@@
 
-This study aims to explore the core tonal structure of Western music by constructing and analyzing an embedding space applicable to subsequent Music Information Retrieval (MIR) tasks.
+This study explores music's core tonal structure by constructing and analyzing an embedding space applicable to subsequent MIR tasks.
 
-By employing a blend of MIR computational techniques and a musicological approach, it intends to examine a wide spectrum of musical works across diverse styles and genres.
-Crucial to this is the understanding of aural skills – perceptual and cognitive abilities essential for interpreting musical works through listening.
+By blending MIR computational techniques and a musicological approach, we intend to examine a broad spectrum of musical works across diverse styles and genres to mimic human aural skills in interpreting music to discern abstract and semantic musical elements, irrespective of the sonic qualities.
 
-The research focuses on the learning of a single embedding, $e(M)$, for a music piece $M$ which encapsulates the underlying high-level content such as melody contour, harmony inter-relationships, and other holistic elements.
-The structuring of the embedding space will prioritize the clustering of similar content and sonic quality features while maintaining a clear distinction between them.
-
-The goal is to create an embedding $e(M)$ that captures high-level musical content and remains agnostic to production features.
+The research focuses on learning a single embedding, $e(M)$, for a music piece $M$ which encapsulates the underlying high-level content such as melody contour, harmony inter-relationships, and other holistic elements.
+The structuring of the embedding space will prioritize the clustering of high-level musical content while maintaining agnostic to sonic quality features.

### 2023-05-15 methods/subsections/model architecture and training strategy.tex
Updates from Overleaf

@@
 Model evaluation, fine-tuning, and deployment are essential to ensure the model generalizes well to new data and performs effectively in real-world applications.
-
-\input{figures/neural networks/pipeline}
 
@@
 \end{equation}
-\caption{\small{Representation of the Average Pooling operation.
+\caption[Average Pooling operation]{\small{Representation of the Average Pooling operation.
 Here, $y_i$ is the output tensor after the average pooling process.
@@
 \subsubsection{Positive sample generation}
-Given an anchor audio signal $A[n]$, we generate a positive signal $P[n]$ by applying a series of amplitude, time-domain, frequency-domain, modulation, reverberation, and nonlinear effects with additive noise on top.
+Given an anchor audio signal $A[n]$, we generate a positive signal $P[n]$ by applying a series of amplitude, time-domain, frequency-domain, modulation, reverberation, and nonlinear effects with additive noise on top of the chain.
 
@@
 \begin{itemize}
-    \item Pitch shift: Changes the signal's pitch by $\Delta p \in [-1200, 1200]$ cents.
+    \item Pitch shift: Changes the signal's pitch by $\Delta p \in [-1200, 1200]$ cents. Two-octave range, one octave higher to one octave lower.
 \end{itemize}
@@
 \begin{enumerate}
-\item Calculate the minimum and maximum chunk lengths in samples:
+\item Calculate the minimum and maximum audio chunk lengths in samples:
 2\begin{equation}
@@
 \end{equation}
-\item Generate random chunk lengths $l_1, l_2, \ldots, l_{n-1}$ from the uniform distribution on the interval $[l_{min}, l_{max}]$. Calculate the final chunk length as:
+\item Generate random audio chunk lengths $l_1, l_2, \ldots, l_{n-1}$ from the uniform distribution on the interval $[l_{min}, l_{max}]$. Calculate the final audio chunk length as:
 \begin{equation}
@@
 where $L_A$ is the length of the anchor signal in samples.
-\item Split the anchor signal $A$ into chunks $C_1, C_2, \ldots, C_n$ according to the calculated chunk lengths.
-\item Shuffle the chunks randomly to get the permuted chunks $C_{\sigma(1)}, C_{\sigma(2)}, \ldots, C_{\sigma(n)}$, where $\sigma$ is a random permutation of indices from $1$ to $n$.
-\item Concatenate the shuffled chunks to generate the negative signal:
+\item Split the anchor signal $A$ into audio chunks $C_1, C_2, \ldots, C_n$ according to the calculated audio chunk lengths.
+\item Shuffle the audio chunks randomly to get the permuted slices $C_{\sigma(1)}, C_{\sigma(2)}, \ldots, C_{\sigma(n)}$, where $\sigma$ is a random permutation of indices from $1$ to $n$.
+\item Concatenate the shuffled audio chunks to generate the negative signal:
 \begin{equation}\label{eq:negative_signal}
@@
 
-Ensure that the length of the anchor and negative signals are the same, i.e.,
-
-\begin{equation}
-L_A = L_N,
-\end{equation}
-
-where $L_N$ is the length of the negative signal in samples.
-
 \subsection{Loss function}
 
-Schroff, F., Kalenichenko, D.
-and Philbin, J.
+Schroff, F., Kalenichenko, D., and Philbin, J.
 at Google initially proposed and used triplet loss to learn face recognition of the same person at different poses and angles.
 \cite{Schroff2015FaceNet:Clustering}
-
-A triplet loss function with a variable margin can be written as follows:
 
@@
 
-In this equation:
+In this equation, triplet loss function with a variable margin:
 

### 2023-05-16 abstract/abstract.tex
Updates from Overleaf

@@
 
-Embracing a subtle novel approach, this process is facilitated by applying Siamese networks with a triplet loss, mimicking human aural skills in interpreting music to discern abstract and semantic musical elements, irrespective of the sonic qualities.
+Embracing a subtle novel approach, this process is facilitated by using deep neural networks with a triplet loss, somewhat mimicking human aural skills in interpreting music to discern abstract and semantic musical elements, irrespective of the sonic qualities.
 The study replaces traditional acoustical features with deep audio embeddings to compute high-level, sound-agnostic, and content-sensitive music identification.
@@
 
-The preliminary results suggest that our approach to learning music-informed embeddings holds significant potential for nearly all MIR downstream tasks.
+The preliminary results suggest that our approach to learning musically-informed embeddings holds significant potential for nearly all MIR downstream tasks.
 Music-motivated embeddings represent a promising technique, adaptable potentially to other tasks hindered by data scarcity.

### 2023-05-16 figures/neural networks/Back_propagation.tex
Updates from Overleaf

--- 2023-03-12 figures/Figures CNN/Back_propagation.tex
@@
     	\end{tikzpicture}
-	\caption[Backpropagation of errors through the network.]{Once evaluated for all output units, the errors $\delta_i^{(L+1)}$ can be propagated backwards.}.
+	\caption[Backpropagation.]{\small{Backpropagation of errors through the network: once evaluated for all output units, the errors $\delta_i^{(L+1)}$ can be propagated backward.}}
 	\label{fig:error-backpropagation}

### 2023-05-16 introduction/Subsections/Assumptions.tex
Updates from Overleaf

@@
 
-This thesis posits the existence of high-level musical concepts invariant to sonic qualities that evolve and unfolds through time such as melody, harmony, rhythm, form, motif, counterpoint, etc.
+This thesis posits the existence of high-level musical concepts invariant to sonic qualities that evolve and unfolds through time, such as melody, harmony, rhythm, form, motif, counterpoint, etc.
 This idea parallels the nature of the symbolic domain (sheet music), which maintains its essence despite being interpreted through diverse performances using various instruments and styles.
@@
 Abstract high-level features can be discerned regardless of waveform or production style.
-This approach provides an objective, comprehensive insight into a composition's musical content and meaning, much like analyzing sheet music uncovers its intentional foundation.
+This approach provides an objective, comprehensive insight into a composition's musical content, much like analyzing sheet music uncovers its behavioral foundation.
 
 For example, despite the differences in cultural contexts, stylistic elements, time signatures, key signatures, and sonic properties, we propose that figures \ref{fig:mahler} and \ref{fig:giant_steps} share a similarity.
-Both pieces carry the same musicological fingerprint, so to say, derived from the propulsion of their melodic and harmonic contours through non-diatonic major thirds.
+Both pieces carry the same musicological fingerprint, so to say, derived from the envelope of their melodic and harmonic contours through non-diatonic major thirds.
 
 This concept finds grounding in the theories of Kurt Koffka, a founder of the Gestalt school of psychology, who proposed a holistic approach to understanding complex forms, contrary to the structuralist practice of reducing mental processes into essential elements \cite{Koffka2013PrinciplesPsychology}.
-
 When applied to music, the principles of Gestalt psychology offer insights into how we perceive, organize, and interpret musical patterns.

### 2023-05-16 introduction/Subsections/Introduction.tex
Updates from Overleaf

@@
 Music \footnote{In this thesis, "music" refers to the Western tradition, characterized by conventions, practices, and aesthetics that have developed primarily in Europe and North America.
-This usage is not intended to deny the diversity and richness of other musical traditions worldwide but instead reflects the present study's focus on a specific cultural context.}, an essential component of human culture, history, and society, has existed since ancient times.
+This usage is not intended to deny the diversity and richness of other musical traditions worldwide but instead reflects the present study's focus on a specific cultural context.}, an essential component of human culture, history, and society; it has existed since ancient times.
 It reflects the changes in our cultures, traditions, and beliefs as it evolves.
-Studying music, however, has always been a challenging and complex task due to its subjective nature, relative and mutable ground truth, and the sheer variety of musical styles, genres, and worldwide cultures.
+Studying music, therefore, has always been a challenging and complex task due to its subjective nature, relative and mutable ground truth, and the sheer variety of musical styles, genres, and worldwide cultures.
 
@@
 
-Music Information Retrieval (MIR) has emerged over the last few decades as an interdisciplinary field that combines engineering, musicology, and neuroscience.
+MIR has emerged over the last few decades as an interdisciplinary field that combines engineering, musicology, and neuroscience.
 It aims to develop algorithms and techniques for automatically analyzing, classifying, and retrieving musical information, primarily from audio signals.
-While MIR research has traditionally focused on technical aspects such as Digital Signal Processing (DSP) and pattern recognition, it may have overlooked other relevant domains, including perception, cognition, music theory, aural skills, and musicology, along with their subfields.
+While MIR research has traditionally focused on technical aspects such as Digital Signal Processing (DSP) and pattern recognition, it may have overlooked other relevant domains, including perception, cognition, music theory, aural skills, musicology, and their subfields.

### 2023-05-16 introduction/Subsections/Motivation.tex
Updates from Overleaf

@@
 
-This research is conducted in collaboration with \textit{Epidemic Sound AB (ES)} \cite{EpidemicSite}, a prominent Swedish company that provides a global library of over 40,000+ royalty-free soundtrack music and 90,000+ sound effects, and the \textit{Music Technology Group (MTG)} at Universitat Pompeu Fabra in Barcelona, Spain.
+This research is conducted in collaboration with \textit{Epidemic Sound AB (ES)} \cite{EpidemicSite}, and the \textit{Music Technology Group (MTG)} at Universitat Pompeu Fabra.
 
-The MTG specializes in developing new technologies related to sound and music, including music information retrieval, digital signal processing, computational models of music perception and cognition, and interactive music systems.
+ES is a prominent Swedish company that provides a global library of over 40,000+ royalty-free soundtrack music and 90,000+ sound effects.
 
-The collaboration with Epidemic Sound and the MTG aims to deepen our understanding of music and its fundamental structures, potentially leading to advancements and benefits for the company's technical products, services, and MIR academic research.
+The MTG, based in Barcelona (Spain), specializes in developing new technologies related to sound and music, including music information retrieval, digital signal processing, computational models of music perception and cognition, and interactive music systems.
+
+The collaboration with ES and the MTG aims to deepen our understanding of music and its fundamental structures, potentially leading to advancements and benefits for the company's technical products, services, and MIR academic research.
 

### 2023-05-16 introduction/Subsections/Objectives.tex
Updates from Overleaf

@@
 
-This study explores music's core tonal structure by constructing and analyzing an embedding space applicable to subsequent MIR tasks.
+This study explores music's high-level tonal structure by leveraging self-supervised deep neural networks, inductive bias, and aural skills to learn and analyze music embeddings applicable to subsequent MIR tasks.
 
-By blending MIR computational techniques and a musicological approach, we intend to examine a broad spectrum of musical works across diverse styles and genres to mimic human aural skills in interpreting music to discern abstract and semantic musical elements, irrespective of the sonic qualities.
+The study aims to develop a unified embedding, $e(M)$, for a music piece $M$ that integrates high-level elements like melody contour, harmony relationships, and other comprehensive components, arranging the embedding space to emphasize clustering of these sophisticated musical content without any consideration for sonic quality attributes.
+Utilizing a blend of Music Information Retrieval (MIR) computational methodologies and musicological perspectives, the research will explore musical compositions from various styles and genres.
 
-The research focuses on learning a single embedding, $e(M)$, for a music piece $M$ which encapsulates the underlying high-level content such as melody contour, harmony inter-relationships, and other holistic elements.
-The structuring of the embedding space will prioritize the clustering of high-level musical content while maintaining agnostic to sonic quality features.
+This approach seeks to replicate human auditory capabilities in understanding and identifying abstract and semantic musical elements independent of their sonic qualities.

### 2023-05-16 introduction/Subsections/Previous work.tex
Updates from Overleaf

@@
 \item The resolution of the cross-modal text-to-music retrieval problem, enabling content creators to find music that matches the emotion conveyed in their text-based stories \cite{WonEmotionStories}.
+
+\item Music rearrangement is traditionally undertaken by expert music engineers or more classical MIR approaches \cite{Stoller2018IntuitiveTransitions}.
+This innovative approach presents a promising avenue for automated music rearrangement, enhancing the process's efficiency and quality.
+\cite{Plachouras2023MusicSegmentation}
+
 \end{itemize}
@@
 Moreover, deep audio embeddings offer the advantage of transferability.
-Once trained, these embeddings can be utilized as a starting point for various other tasks, thus saving computational resources and time compared to training a model from scratch.
-
-Given their demonstrated success in the literature and their potential for transfer learning, exploring deep audio embeddings for MIR downstream tasks seems worthwhile.
+Once trained, these latent representations can be utilized as a starting point for various other tasks, thus saving computational resources and time compared to training a model from scratch \cite{HamelTransferSimilarity}.
 
@@
 \cite{Introduction_to_Schenkerian_Analysis}
+
+Given their demonstrated success in the literature and their potential for transfer learning, exploring deep audio embeddings for MIR downstream tasks seems worthwhile.

### 2023-05-16 methods/subsections/model architecture and training strategy.tex
Updates from Overleaf

@@
 This approach to learning is inspired by the way humans and animals learn from their environment, where a great deal of knowledge is acquired through observation and interaction without explicit instruction.
+Self-supervised learning is a machine learning process where the model trains itself to learn one part of the input from another part of the input.
+In this process, the unsupervised problem is transformed into a supervised problem by auto-generating the labels.
 
@@
 
-Although there are resemblances between assimilation and accommodation in Piaget's theory and backpropagation in Deep Learning (DL), these processes occur in distinct mechanisms and contexts.
-Assimilation and accommodation modify mental structures to incorporate new information, while backpropagation adjusts neural network weights to enhance output predictions.
-
 \subsubsection{Known and unknown invariance}
@@
 Known invariances are transformations or changes that the model or algorithm is explicitly designed to be robust against.
-This can include the input data's rotations, translations, scaling, or other known perturbations.
 By incorporating these invariances into the model's design, the algorithm is better equipped to generalize and recognize patterns in the presence of these transformations.
@@
 
-Unknown invariance: Unknown invariances are transformations the model has not been explicitly designed to handle.
+Unknown invariances are transformations the model has not been explicitly designed to handle.
 However, it still manages to be robust due to its learning capabilities.
 These invariances can emerge from the data and may not be known a priori.
-For example, a deep learning model might automatically learn to be invariant to certain lighting conditions or other factors not explicitly specified in its design.
 \end{definition}
-
-\begin{equation}
-\label{eq:invariance_to_particular_transformation_function}
-\forall x \in X, \forall y \in Y, \forall \rho \in \mathcal{T}, f(x) = f(y) \implies f(\rho(x)) = f(\rho(y))
-\end{equation}
-
-In expression \ref{eq:invariance_to_particular_transformation_function}, $X$ and $Y$ represent sets of input data, $\rho$ represents a transformation function, and $f$ represents a machine learning model.
-The expression states that for all inputs $x$ and $y$ in $X$ and $Y$, if $f(x) = f(y)$, then $f(\rho(x)) = f(\rho(y))$.
-
-The expression specifies that a model is invariant to a particular transformation function $\rho$ if it produces the same output for both the original and transformed input.
 
@@
 
-\item \textbf{Time-domain effects:} Time-domain manipulation alters the signal's timing or duration.
+\item \textbf{Time-domain effects:} Alters the signal's timing or duration.
 \begin{itemize}
@@
 
-\item \textbf{Frequency-domain effects:} Frequency domain manipulation alters the frequency content or pitch of the signal.
+\item \textbf{Frequency-domain effects:} Alters the frequency content or pitch of the signal.
 \begin{itemize}
@@
 
-\item \textbf{Nonlinear effects:} Nonlinear transformations to the audio signal, resulting in harmonic distortion or other complex changes.
+\item \textbf{Nonlinear effects:} Harmonic distortion or other complex changes.
 \begin{itemize}
@@
 
-\item \textbf{Modulation effects:} Audio signal modulation using a low-frequency oscillator or control signal.
+\item \textbf{Modulation effects:} Modulation using a low-frequency oscillator or control signal.
 \begin{itemize}
@@
 
-\item \textbf{Noise effects:} These effects add noise or other random elements to the audio signal.
+\item \textbf{Noise effects:}
 \begin{itemize}

### 2023-05-16 results/results.tex
Updates from Overleaf

@@
 XXXXXXXXXXXXXXXXX
+
+\input{figures/neural networks/manifold}
 
@@
 \includegraphics[clip,width=\columnwidth]{figures/PlotTimeSeriesResult}% 
-\caption{This is an example of a figure and its caption.}
+\caption[Graph.]{This is an example of a figure and its caption.}
 \label{fig:timeseries}
@@
 \renewcommand{\arraystretch}{1.50}
-\caption{This is an example of a table and its caption.}
+\caption[Table]{This is an example of a table and its caption.}
 \label{tablePCA}
 \centering
-\begin{tabular}{| c | c |}
+\begin{tabular}{| c | c | c | c | c |}
 \hline
-\bfseries PCA & \bfseries Residual mean (in absolute values) \\
+\bfseries PCA & \bfseries Residual mean & \bfseries XXX & \bfseries XXX & \bfseries XXX \\
 \hline\hline
-Original PCA & 0.1267  \\
+Original PCA & 0.1267 & XXX & XXX & XXX  \\
 \hline
-PCA on Centroid 1 & 0.1249\\
+PCA on Centroid 1 & 0.1249 & XXX & XXX  & XXX\\
 \hline
-PCA on Centroid 2 & 0.1214  \\
+PCA on Centroid 2 & 0.1214  & XXX & XXX  & XXX\\
 \hline

### 2023-05-17 introduction/Subsections/Previous work.tex
Updates from Overleaf

@@
 This element is often overlooked when applying deep learning to music.
-As emphasized by \cite{Mesostructures2023}, models that address this mesostructure level could significantly enrich tasks such as music analysis, composition, and retrieval, providing a more holistic understanding of music similar to the insights gained from analyzing the middle-ground in Schenkerian analysis.
+As emphasized by \cite{Mesostructures2023}, models that address this mesostructure level could significantly enrich tasks such as music analysis, composition, and retrieval, providing a more holistic understanding of music, similar to the insights gained from analyzing the middle-ground in Schenkerian analysis.
 \cite{Introduction_to_Schenkerian_Analysis}

### 2023-05-17 methods/subsections/machine learning.tex
Updates from Overleaf

@@
 \section{Introduction}
-
-In this chapter, we present the methodology employed in this study.
-
-We provide an overview of the Machine Learning (ML) and Deep Learning techniques that have played a pivotal role in advancing the MIR field.
-We then discuss the importance of feature extraction and selection in MIR and how automatic feature learning has facilitated the development of more robust models.
-
-Subsequently, we delve into the concept of musically motivated neural network architectures, which incorporate domain-specific knowledge and musical ideas into the design of neural networks.
-We explore techniques proposed in the literature for blending musical concepts and perceptual approaches.
-
-We then outline the specific MIR tasks that our study focuses on and discuss the evaluation metrics used to assess the performance of the proposed models.
-Finally, we present the experimental setup, including the datasets used for training and validation, the preprocessing steps, and the training parameters.
 
@@
 \section{Artificial Neural Networks (ANNs)}
-A neural network, formally known as an Artificial Neural Network (ANN), is a computational model inspired by the structure and functionality of biological neural networks.
-It is a mathematical framework designed to process information and perform tasks like pattern recognition, classification, and regression by mimicking how biological neurons and synapses operate.
-ANNs comprise interconnected layers of artificial neurons or nodes, each performing a mathematical transformation on the input data to generate an output.
-The connections between these neurons, often called "weights," are adjusted during learning to optimize the network's performance on a given task.
-
-\subsection{About ANNs}
-The concept of neural networks can be traced back to the mid-20th century, with the pioneering work of Warren McCulloch and Walter Pitts in 1943.
-They proposed a mathematical model of a neuron known as the McCulloch-Pitts neuron, which provided a foundation for future research in artificial intelligence.
-However, Frank Rosenblatt's invention of the perceptron in 1957 marked the beginning of modern neural networks.
-The perceptron is a single-layer neural network capable of learning linearly separable patterns.
+Artificial Neural Networks (ANNs) are computational models inspired by biological neural systems.
+They use interconnected layers of artificial neurons to process information and perform tasks like pattern recognition, classification, and regression.
+ANNs adjust the connections, or "weights," between neurons during learning to improve performance.
+The concept of neural networks emerged in the mid-20th century with the work of Warren McCulloch and Walter Pitts.
+Still, modern neural networks began with Frank Rosenblatt's perceptron in 1957, a single-layer network able to learn linearly separable patterns.
 
@@
 
-In a more technical description, an ANN consists of an input layer, one or more hidden layers, and an output layer.
+It consists of an input layer, one or more hidden layers, and an output layer.
 Each neuron in a layer receives input from the previous layer and computes an output value using an activation function.

### 2023-05-17 methods/subsections/model architecture and training strategy.tex
Updates from Overleaf

@@
 
-Some of the main advantages of SSL include:
-
-\begin{enumerate}
-\item Reduces dependency on labeled data, which can be expensive and time-consuming to collect and annotate.
-\item Encourages more generalizable and robust representations of the data since they capture the inherent structure and properties of the data rather than relying on human-provided labels.
-\end{enumerate}
+SSL's main advantages include reducing dependency on labeled data, which can be expensive and time-consuming to collect and annotate.
+Also, encourages more generalizable and robust representations of the data since they capture the inherent structure and properties of the data rather than relying on human-provided labels.
 

### 2023-05-18 acknowledgements/acknowledgements.tex
Updates from Overleaf

@@
 
-I want to express my sincerest gratitude to...
+I want to extend my deepest gratitude to...
 
 \begin{itemize}
-\item Carlos Lordelo, and Carl Thomé for their invaluable guidance and support throughout my thesis.
-Your expertise in MIR, ML, and DSP helped shape the direction of my research and make it a success.
-Your unwavering support and encouragement helped me overcome any difficulties I encountered.
-I also appreciate the time and effort you invested in mentoring me.
-Your dedication to your students is truly inspiring, and I am honored to have had the opportunity to work with you.
+\item Carlos Lordelo and Carl Thomé for their invaluable guidance and support throughout my thesis.
+Their MIR, ML, and DSP expertise has been instrumental in shaping my research and driving it toward success.
+I am truly grateful for their unwavering support and encouragement, which helped me surmount any difficulties I encountered during this journey.
+Their time, effort, and dedication in mentoring me have not gone unnoticed.
+They inspire me with their commitment to their students, and I feel honored to have had the opportunity to work with them.
+
+Words fall short of my profound gratitude for their consistent, knowledgeable, and steadfast support. I am beyond grateful that their dedication has left an indelible mark on my academic journey.
+
 \vspace*{3mm}
@@
 \vspace*{3mm}
-\item My family
-\vspace*{3mm}
-\item My girlfriend
-\vspace*{3mm}
 \end{itemize}

### 2023-05-18 dedication/dedication.tex
Updates from Overleaf

@@
 \pagenumbering{gobble}% Remove page numbers (and reset to 1)
-I dedicate this master's thesis to my closest family (Joaquim Colomé, Imma Font, Maria Colomé, and Ariadna Balasch), who has been my constant support and inspiration throughout this journey.
+I dedicate this master's thesis to my closest family and friends, who have supported and inspired me throughout this journey.
 Their unwavering love and encouragement have motivated me to pursue my academic goals, and their belief in me has never faltered.
 I am grateful for their patience, understanding, and sacrifices as I pursued my studies.
-Their presence in my life has made this journey meaningful, and this thesis is a tribute to their unwavering support.
+
+Their presence in my life has made this journey meaningful, and this thesis is a tribute to their support.
+
 \newpage

### 2023-05-18 discussion/discussion.tex
Updates from Overleaf

--- 2023-04-19 discussion/discussion.tex
@@
 
-XXXXXXXXXXX
+In this work, we introduced a method to uncover underlying high-level musical
+content in the temporal domain by leveraging self-supervised deep neural networks, inductive bias, and aural skills to learn music latent representations with applications to MIR downstream tasks.
+Building on top of existing approaches and architectures and wrapped within MSAF \cite{NietoMSAF:FRAMEWORK}, we replaced traditional features with deep embeddings trained to represent high-level musical content information.
 

### 2023-05-18 evaluation/subsections/beyond dsp.tex
Updates from Overleaf

@@
 
-\section{SALAMI dataset}
-\subsection{Overview}
+\subsection{SALAMI dataset}
 
@@
 
-\subsubsection{Formal Analysis Definition}
+\subsubsection{Formal analysis definition and approaches}
 Formal analysis, in this context, doesn't refer to classifying the piece into a formal type (e.g., sonata, song, or canon) or reducing it into its Ursatz as in Schenkerian analysis.
@@
 
-%%%%%%%%%%
+The proposed method integrates aspects of three approaches: perceptual, functional, and transcription, enabling a comprehensive analysis of a wide range of music pieces using a limited vocabulary.
 
-\subsubsection{Approaches to Music Analysis}
+It considers the hierarchical nature of music structure and employs markers to partially address the challenge of determining the appropriate timescale for analysis.
 
-The method proposed combines aspects of the following three approaches, separating the organization of instrumentation, musical material, and formal function.
-This allows for the analysis of a wide variety of music pieces in a consistent way using a constrained vocabulary.
-It's important to note that music structure is often hierarchical, and the appropriate timescale for analysis can be hard to determine.
-The proposed method includes a few markers to partly address this issue.
+The perceptual approach involves segmenting and labeling sections based on harmonic or rhythmic boundaries, although it may not accurately reflect the structural roles of similar-sounding sections.
 
-Perceptual Approach: This involves listening for prominent harmonic or rhythmic boundaries in the piece to segment and apply labels to sections based on their similarity.
-However, this approach might not reflect the different structural roles of similar-sounding sections.
+The functional approach categorizes the song into components like verses and choruses, potentially leading to varied labels for identical music or identical labels for different musical ideas based on their function.
 
-Functional Approach: This involves dividing the song into its functional parts, like verses, choruses, intros, outros, etc.
-This might result in the same music being labeled differently based on its function or different musical ideas having the same functional label.
+The transcription approach records musical parameters directly, such as chord patterns and instrumentation, providing a less subjective method, but it might not capture the complete structure of the piece.
 
-Transcription Approach: This involves recording musical parameters like chord patterns and instrumentation directly.
-While this method may be less subjective, it may not provide a comprehensive view of the piece's structure.
+\section{\textit{Embeddiogram} feature}
 
-\section{\textit{Embeddiogram} custom feature}
-
-Features extracted from audio files play a vital role in characterizing and differentiating sound and music.
-One such feature, the \textit{Embeddiogram}, offers a unique and powerful representation of an audio signal.
 The Embeddiogram is derived by applying a pre-trained neural network model to windowed segments of an audio signal, generating a sequence of embedding vectors.
@@
     \includegraphics[width=\textwidth]{figures/images/embeddiogram_SALAMI_track_2.png}
-    \caption[Embeddiogram]{Caption}
+    \caption[Embeddiogram]{Embeddiogram computed from...}
     \label{fig:embeddiogram}
 \end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/images/noveltypeaks_SALAMI_track_2.png}
+    \caption[Novelty curve]{Caption}
+    \label{fig:embeddiogram}
+\end{figure}
+
+\begin{figure}[ht]
+    \centering
+    \begin{minipage}{0.45\textwidth}
+        \centering
+        \includegraphics[width=0.9\textwidth]{figures/images/Rec_matrix_SALAMI_track_2.png} % first figure itself
+        \caption{first figure}
+    \end{minipage}\hfill
+    \begin{minipage}{0.45\textwidth}
+        \centering
+        \includegraphics[width=0.9\textwidth]{figures/images/Rec_matrix_smooth_SALAMI_track_2.png} % second figure itself
+        \caption{second figure}
+    \end{minipage}
+\end{figure}

### 2023-05-18 methods/subsections/model architecture and training strategy.tex
Updates from Overleaf

@@
 
-This section delves into the systematic process of developing, training and evaluating algorithms, which empower data-driven learning, predictions, and decisions.
-This process encompasses selecting an appropriate algorithm, designing the model architecture, preprocessing and transforming data, and extracting relevant features.
-By iteratively adjusting the model's parameters, we aim to minimize the prediction error.
-The choice of techniques, such as supervised, unsupervised, or reinforcement learning, is dictated by the specific problem and data structure.
-Model evaluation, fine-tuning, and deployment are essential to ensure the model generalizes well to new data and performs effectively in real-world applications.
+This section outlines the methodical procedure of creating, training and assessing algorithms that enable data-driven learning and decision-making.
+The process involves algorithm selection, model architecture design, data preprocessing and transformation, and feature extraction.
+The objective is to minimize prediction error by iteratively fine-tuning the model's parameters.
+The selection between supervised, unsupervised, or reinforcement learning techniques depends on the problem's specifics and data structure.
+Evaluating, refining, and deploying the model to ensure its effective performance with new data in real-world applications is crucial.
 
-\subsection{Model architecture and training strategy}
+I advocate for exposure as the primary method of learning music, highlighting the importance of various musical experiences for a comprehensive understanding of the art form.
+Engagement with diverse musical styles, genres, techniques, and learning methods fosters well-rounded musical proficiency, encouraging creativity and experimentation.
 
-I advocate for exposure as the primary method of learning music, emphasizing the importance of immersing oneself in various musical experiences to foster a holistic understanding of music as an art form.
-Individuals can cultivate well-rounded musical expertise by engaging with different styles, genres, techniques, and learning approaches, ultimately promoting creativity and experimentation.
+Considering the task at hand, we suggest using a Triple Siamese Network, an architecture proven efficient for music similarity retrieval tasks \cite{contentmusicsimtriplet2020}.
+The goal is to minimize the loss function between an anchor, positive, and negative sample, achieved through online triplet mining \cite{Sikaroudi2020OfflinePatches}.
 
-Given the nature of our task, we propose using a Triple Siamese Network.
-This model architecture has been proven efficient for music similarity retrieval tasks \cite{contentmusicsimtriplet2020}.
-Specifically, we aim to minimize the loss function between an anchor, a positive, and a negative sample by using online triplet mining \cite{Sikaroudi2020OfflinePatches}.
+Using the proposed triple siamese network, and online triplet mining in a self-supervised setting, we aim to train a model that can effectively distinguish between similar and dissimilar samples while considering their underlying composition and production texture.
 
-Using the proposed triple siamese network and online triplet mining, we aim to train a model that can effectively distinguish between similar and dissimilar samples while considering their underlying composition and production texture.
+\subsection{Contrastive Learning of Musical Representations (CLMR)}
 
-\subsection{Self-Supervised Learning (SSL)}
+Contrastive Learning of Musical Representations (CLMR) \cite{CLMR2021} aims to learn discriminative and valuable representations of music without relying on explicit labels.
+By leveraging the structure and content of music and contrasting different augmentations or transformations of the same musical piece against randomly generated pieces, CLMR models can effectively capture the underlying known invariances that are explicitly incorporated into the design of a model to improve its robustness and generalization.
+
+In contrast, the model learns unknown invariances from the data without explicit instruction.
+
+The CLMR methodology involves the following steps:
+
+\begin{enumerate}
+\item \textbf{Data Augmentation:} Create different augmentations or transformations of the same musical piece as positive pairs and use other randomly selected pieces as antagonistic pairs.
+\item \textbf{Contrastive Learning:} Train by minimizing a contrastive loss function, encouraging the model to produce similar representations for positive pairs and dissimilar representations for antagonistic pairs.
+\item\textbf{Latent Representation:} Utilize the learned representations for various Music Information Retrieval (MIR) downstream tasks, such as music genre classification or similarity, both in the symbolic and time domains.
+\end{enumerate}
+
+By following these steps, CLMR models can learn meaningful and robust representations of music, potentially enhancing their performance in various MIR tasks and reducing the need for labeled data.
+
+\subsection{Encoder: SampleCNN}
+
+The SampleCNN model \cite{Lee2018SampleCNN:Classification} takes 1D input data with a single channel.
+The first layer is a 1D convolutional layer with a kernel size of 3, a stride of 3, and 128 output channels.
+It is followed by batch normalization and ReLU activation.
+
+The original model has been modified slightly to serve our specific needs: the output from the final convolutional layer is now subjected to an average pooling operation across the temporal dimension.
+
+%%%%%BATCH NORM%%%%%%%%%%
+
+The maximum array length in the batch is given by:
+
+\begin{equation}
+L_{\text{max}} = \max_{\text{item} \in \text{batch}}(\max(\text{length}(A_{\text{item}}), \text{length}(P_{\text{item}}), \text{length}(N_{\text{item}})))
+\end{equation}
+
+This adaptation of the original architecture incorporates an average pooling step at the end.
+
+\begin{figure}[ht]
+\centering
+\begin{equation}
+y_i = \frac{1}{N} \sum_{j=1}^{N} x_{ij}
+\end{equation}
+\caption[Average Pooling operation]{\small{Representation of the Average Pooling operation.
+Here, $y_i$ is the output tensor after the average pooling process.
+Each element $x_{ij}$ is part of the 2D input tensor.
+$N$ is the count of elements in the second dimension of the input tensor, while $i$ and $j$ are used to iterate over the first and second dimensions of the tensors, respectively.}}
+\end{figure}
+
+\input{figures/neural networks/dropout}
+
+\input{figures/my model/SampleCNN}
+
+%Colour CNN
+\input{figures/neural networks/colour CNN}
+
+\subsection{Siamese Networks}
+
+A Siamese Network, a deep learning architecture introduced by Bromley and LeCun in the early 1990s \cite{Bromley1993SignatureNetwork}, is designed explicitly for tasks involving similarity or comparison between two input instances.
+Its name derives from the structure, which consists of two or more identical subnetworks connected in parallel and joined at the output layer.
+These subnetworks share the same architecture, weights, and hyperparameters, allowing for more efficient memory usage and computational complexity.
+
+This design is particularly effective for learning from limited or imbalanced datasets, as it focuses on learning the similarity metric rather than specific features of individual classes.
+
+Each subnetwork processes an input independently, and its outputs are combined and further processed to yield a single similarity score.
+The shared weights during training enable the model to learn an invariant representation for the input instances, improving its efficiency in comparing and contrasting them.
+Siamese Networks employ specialized loss functions, such as contrastive or triplet loss, which minimize the distance between similar input pairs and maximize the distance between dissimilar ones.
+This approach encourages the network to learn a meaningful similarity metric.
+
+\subsubsection{Triplet Siamese Networks}
+
+Triplet Siamese Networks, an extension of the Siamese Network architecture, involve comparing three input instances instead of two, aiming to learn an embedding space where similar instances are close and dissimilar instances are distant.
+The input consists of an anchor, a positive instance (same class as the anchor), and a negative instance (different class).
+An identical subnetwork with shared architecture, weights, and hyperparameters processes each instance.
+
+The triplet loss function guides learning, minimizing the distance between the anchor and positive instances while maximizing the distance between the anchor and negative instances.
+A margin parameter in the loss function ensures a minimum separation between positive and negative instances in the embedding space.
+
+Due to shared weights, Triplet Siamese Networks offer efficient memory usage and computational complexity.
+
+\subsubsection{Self-Supervised Learning (SSL)}
 
@@
 
-\subsection{Contrastive Learning of Musical Representations (CLMR)}
-
-Contrastive Learning of Musical Representations (CLMR) \cite{CLMR2021} aims to learn discriminative and valuable representations of music without relying on explicit labels.
-By leveraging the structure and content of music and contrasting different augmentations or transformations of the same musical piece against randomly generated pieces, CLMR models can effectively capture the underlying known invariances that are explicitly incorporated into the design of a model to improve its robustness and generalization.
-
-In contrast, the model learns unknown invariances from the data without explicit instruction.
-
-The CLMR methodology involves the following steps:
-
-\begin{enumerate}
-\item \textbf{Data Augmentation:} Create different augmentations or transformations of the same musical piece as positive pairs and use other randomly selected pieces as antagonistic pairs.
-\item \textbf{Contrastive Learning:} Train by minimizing a contrastive loss function, encouraging the model to produce similar representations for positive pairs and dissimilar representations for antagonistic pairs.
-\item\textbf{Latent Representation:} Utilize the learned representations for various Music Information Retrieval (MIR) downstream tasks, such as music genre classification or similarity, both in the symbolic and time domains.
-\end{enumerate}
-
-By following these steps, CLMR models can learn meaningful and robust representations of music, potentially enhancing their performance in various MIR tasks and reducing the need for labeled data.
-
-\subsection{Siamese Networks}
-
-A Siamese Network, a deep learning architecture introduced by Bromley and LeCun in the early 1990s \cite{Bromley1993SignatureNetwork}, is designed explicitly for tasks involving similarity or comparison between two input instances.
-Its name derives from the structure, which consists of two or more identical subnetworks connected in parallel and joined at the output layer.
-These subnetworks share the same architecture, weights, and hyperparameters, allowing for more efficient memory usage and computational complexity.
-
-This design is particularly effective for learning from limited or imbalanced datasets, as it focuses on learning the similarity metric rather than specific features of individual classes.
-
-Each subnetwork processes an input independently, and its outputs are combined and further processed to yield a single similarity score.
-The shared weights during training enable the model to learn an invariant representation for the input instances, improving its efficiency in comparing and contrasting them.
-Siamese Networks employ specialized loss functions, such as contrastive or triplet loss, which minimize the distance between similar input pairs and maximize the distance between dissimilar ones.
-This approach encourages the network to learn a meaningful similarity metric.
-
-\subsubsection{Triplet Siamese Networks}
-
-Triplet Siamese Networks, an extension of the Siamese Network architecture, involve comparing three input instances instead of two, aiming to learn an embedding space where similar instances are close and dissimilar instances are distant.
-The input consists of an anchor, a positive instance (same class as the anchor), and a negative instance (different class).
-An identical subnetwork with shared architecture, weights, and hyperparameters processes each instance.
-
-The triplet loss function guides learning, minimizing the distance between the anchor and positive instances while maximizing the distance between the anchor and negative instances.
-A margin parameter in the loss function ensures a minimum separation between positive and negative instances in the embedding space.
-
-Triplet Siamese Networks offer several advantages, including learning fine-grained similarity metrics, being well-suited for one-shot learning tasks, and offering efficient memory usage and computational complexity due to shared weights.
-These networks have been applied to various tasks and domains, such as image recognition, face recognition, speaker recognition, text similarity, and medical imaging for diagnosis or treatment purposes.
-
-\subsection{Convolutional Neural Network (CNN)}
-
-A Convolutional Neural Network (CNN) is a deep-learning neural network. The architecture of a CNN is composed of several layers, including:
-
-\begin{itemize}
-
-\item \textbf{Convolutional layers:} These layers apply a convolution operation to the input data.
-The convolutional layers are designed to effectively learn local patterns and features in the audio data \footnote{For a visual explanation and further understanding of the convolution operation, please refer to this URL: \url{https://youtu.be/KuXjwB4LzSA}}.
-
-Let's consider a 1D input sequence or signal represented as a vector $I = [i_{i}]{n}$ and a filter $K = [k_{j}]_{p}$, where $n$ is the length of the input sequence and $p$ is the length of the filter.
-The convolution operation is defined as:
-
-\begin{equation}
-(I * K){k} = \sum{j=1}^{p} i_{k+j-1}k_{j}
-\end{equation}
-
-Here, $k$ ranges from $1$ to $n-p+1$. The resulting feature vector after applying the convolution is denoted by $(I * K)_{k}$.
-
-The convolution operation slides the kernel $K$ over the input sequence $I$, performing an element-wise multiplication and sum of the local region centered at element $k$ to compute the value of each element in the output feature vector, $(I * K)_{k}$.
-This process is repeated for each component $k$, resulting in a new feature vector that captures local patterns in the input sequence.
-
-In simple terms, the filter or kernel is slid across the 1D input data.
-For each position, we perform an element-wise multiplication of the filter with the portion of the input it currently covers and sums the results.
-This value becomes the corresponding entry in the output.
-The process is repeated for each position the filter can occupy.
-
-\item \textbf{Pooling layers:} These layers downsample the data, reducing the input dimensions while retaining important information.
-A joint pooling operation is the max-pooling, which can be defined as follows: given an input matrix $I$ and a pooling window of size $m \times n$, the max-pooling operation selects the maximum value within each non-overlapping $m \times n$ region of the input matrix.
-This operation effectively reduces the input's dimensions while retaining the essential information in each area.
-\vspace*{3mm}
-
-\item \textbf{Fully connected layers:} These layers connect every neuron in one layer to every neuron in another, allowing the network to learn non-linear combinations of the features discovered in the previous layers.
-Mathematically, a fully connected layer can be represented as $Y = XW + b$, where $X$ is the input matrix, $W$ is the weight matrix, $b$ is the bias vector, and $Y$ is the output matrix.
-\vspace*{3mm}
-
-\item \textbf{Output layer:} The output layer produces the final predictions of the network.
-
-\end{itemize}
-
-Compared to a traditional neural network, CNNs are more computationally efficient and have less number of parameters to train.
-This makes them more feasible for large-scale datasets and real-world problems.
-On top of that, one of the main advantages of using CNNs for audio analysis is that they can automatically and adaptively learn temporal hierarchies of features from audio data, which traditional audio processing methods may not do effectively.
-
-%Colour CNN
-\input{figures/neural networks/colour CNN}
-
-\subsection{Encoder: SampleCNN}
-
-The SampleCNN model \cite{Lee2018SampleCNN:Classification} takes in 1D input data with a single channel.
-The first layer is a 1D convolutional layer with a kernel size of 3, a stride of 3, and 128 output channels.
-It is followed by batch normalization and ReLU activation.
-
-After the initial layer, there are nine hidden layers with varying kernel sizes, strides, and channels. Each hidden layer consists of the following:
-
-\begin{itemize}
-    \item A 1D convolutional layer with the specified number of input and output channels, kernel size, a stride of 1, and padding of 1.
-
-    \begin{equation}
-y_{c_o}(n) = \sum_{c_i=1}^{C_{\text{in}}} \sum_{k=-\lfloor K/2 \rfloor}^{\lfloor K/2 \rfloor} x_{c_i}(n - k) \cdot w_{c_o, c_i}(k)
-\end{equation}
-
-Where:
-
-$y_{c_o}(n)$ is the output for the $c_o$-th output channel at position $n$, $C_{\text{in}}$ is the number of input channels, $x_{c_i}(n)$ is the input for the $c_i$-th input channel at position $n$, $w_{c_o, c_i}(k)$ is the kernel weight for the $c_o$-th output channel and $c_i$-th input, channel at position $k$, and $K$ is the kernel size.
-The stride is set to 1 and padding to 1 (equal padding $\lfloor K/2 \rfloor$ on both sides).
-
-\item Batch normalization.
-We process a batch of data containing anchor, positive, and negative samples.
-We pad the waveforms to the same  maximum length among the collection, perform online triplet mining to find the hardest negatives and return the padded anchors, positives, and hardest negatives.
-
-We have intentionally chosen to use zero padding instead of array truncating in our experiment.
-This decision was based on our belief that preserving the integrity of the music data was more critical, despite the potential trade-off with computational efficiency during the normalization process.
-
-Let $A$, $P$, and $N$ represent the anchor, positive, and negative samples. The maximum array length in the batch is given by:
-
-\begin{equation}
-L_{\text{max}} = \max_{\text{item} \in \text{batch}}(\max(\text{length}(A_{\text{item}}), \text{length}(P_{\text{item}}), \text{length}(N_{\text{item}})))
-\end{equation}
-
-The anchor-positive distance and the anchor-negative distance are computed as the Euclidean distance between the corresponding samples:
-
-\begin{equation}
-D_{\text{AP}} = \sqrt{\sum_{i} (A_i - P_i)^2}
-\end{equation}
-
-The "hardest" negative index for each anchor-positive pair is determined by maximizing the difference between the anchor-negative and anchor-positive distances:
-
-\begin{equation}
-D_{\text{AN}} = \sqrt{\sum_{i} (A_i - N_i)^2}
-\end{equation}
-
-\item ReLU activation.
-The Rectified Linear Unit (ReLU) activation function is a simple yet highly effective non-linear function used in neural networks.
-It helps introduce non-linearity to the model and accelerates training due to its computational efficiency.
-
-\item Max pooling with kernel size and stride equal to the stride value of the current layer.
-\end{itemize}
-
-After the hidden layers, there's another 1D convolutional layer with 512 input channels, 512 output channels, a kernel size of 3, a stride of 1, and padding of 1.
-This is followed by batch normalization and ReLU activation.
-
-The original model has been modified slightly to serve our specific needs: the output from the final convolutional layer is now subjected to an average pooling operation across the temporal dimension.
-
-This adaptation of the original architecture incorporates an average pooling step at the end.
-
-\begin{figure}[ht]
-\centering
-\begin{equation}
-y_i = \frac{1}{N} \sum_{j=1}^{N} x_{ij}
-\end{equation}
-\caption[Average Pooling operation]{\small{Representation of the Average Pooling operation.
-Here, $y_i$ is the output tensor after the average pooling process.
-Each element $x_{ij}$ is part of the 2D input tensor.
-$N$ is the count of elements in the second dimension of the input tensor, while $i$ and $j$ are used to iterate over the first and second dimensions of the tensors, respectively.}}
-\end{figure}
-
-If the model is "supervised", dropout with a rate of 0.5 is applied; a regularization technique randomly drops out neurons during training to prevent overfitting, with a 0.5 rate meaning half of the neurons are dropped out.
-
-\input{figures/neural networks/dropout}
-
-Finally, a linear layer with 512 input features and 128 output dimension features is applied to generate the embeddings.
-
-\input{figures/my model/SampleCNN}
-
 \subsection{Audio augmentation and transformation pipeline}
@@
 \subsubsection{Positive sample generation}
+
+While useful audio transformations tools \cite{Spijkervet2021Spijkervet/torchaudio-augmentations:V1.0}
+
 Given an anchor audio signal $A[n]$, we generate a positive signal $P[n]$ by applying a series of amplitude, time-domain, frequency-domain, modulation, reverberation, and nonlinear effects with additive noise on top of the chain.
@@
 Here, $N$ is the number of triplets in the mini-batch, and $L(anchor_i, positive_i, negative_i)$ represents the loss function computed for the i-th triplet in the batch.
+
+\subsubsection{Triplet mining}
+
+The anchor-positive distance and the anchor-negative distance are computed as the Euclidean distance between the corresponding samples:
+
+\begin{equation}
+D_{\text{AP}} = \sqrt{\sum_{i} (A_i - P_i)^2}
+\end{equation}
+
+The "hardest" negative index for each anchor-positive pair is determined by maximizing the difference between the anchor-negative and anchor-positive distances:
+
+\begin{equation}
+D_{\text{AN}} = \sqrt{\sum_{i} (A_i - N_i)^2}
+\end{equation}

### 2023-05-22 methods/subsections/machine learning.tex
Updates from Overleaf

@@
 
-\section{Artificial Neural Networks (ANNs)}
+\section{Machine Learning Modeling}
+
+This section outlines the methodical procedure of creating, training and assessing algorithms that enable data-driven learning and decision-making.
+The process involves algorithm selection, model architecture design, data preprocessing and transformation, and feature extraction.
+The objective is to minimize prediction error by iteratively fine-tuning the model's parameters.
+The selection between supervised, unsupervised, or reinforcement learning techniques depends on the problem's specifics and data structure.
+It is crucial to evaluate, refine, and deploy the model to ensure its effective performance with new data in real-world applications.
+
+I advocate for exposure as the primary method of learning music, highlighting the importance of various musical experiences for a comprehensive understanding of the art form.
+Engagement with diverse musical styles, genres, techniques, and learning methods fosters well-rounded musical proficiency, encouraging creativity and experimentation.
+
+Considering the task at hand, we suggest using a Triple Siamese Network, an architecture proven efficient for music similarity retrieval tasks \cite{contentmusicsimtriplet2020}.
+The goal is to minimize the loss function between an anchor, positive, and negative sample, achieved through online triplet mining \cite{Sikaroudi2020OfflinePatches}.
+
+Using the proposed triple siamese network and online triplet mining in a self-supervised setting, we aim to train a model that can effectively distinguish between similar and dissimilar samples while considering their underlying composition and production texture.
+
+At a superficial level, our approach could be described as cognitive modeling, given that it seeks to approximate human problem-solving and mental processing through a computerized model.
+
+\section{Deep Learning (DL)}
+
+Deep learning is a subfield of machine learning that employs deep neural networks to learn hierarchical data representations, enabling computational models with multiple processing layers to learn data abstractions across numerous levels.
+These methods have dramatically advanced the state-of-the-art in various domains, including speech recognition, visual object recognition, object detection, drug discovery, genomics, and more \cite{LeCun2015DeepLearning}.
+The effectiveness of deep learning arises from its nonlinear modeling capabilities and scalability with large datasets.
+
+A central algorithm in deep learning is backpropagation, which uses the forward and backward pass process to efficiently compute gradients of the loss function concerning the network's parameters.
+The forward pass involves propagating input data through the network to generate predictions.
+In contrast, the backward pass calculates the error between predictions and ground truth and subsequently returns it through the network.
+This procedure updates the network's parameters using gradient descent, minimizing the loss function and enhancing the model's performance.
+
+Deep learning has led to breakthroughs in processing complex, high-dimensional data, including images, video, speech, and audio, primarily due to deep convolutional nets.
+Simultaneously, recurrent nets have illuminated sequential data analysis such as text and speech.
+Deep learning discovers intricate structures in large datasets, improving our understanding and processing capabilities across various applications.
+
+%Backpropagation
+\input{figures/neural networks/Back_propagation}
+
+\subsection{Artificial Neural Networks (ANNs)}
 Artificial Neural Networks (ANNs) are computational models inspired by biological neural systems.
@@
 
-\section{Deep Learning (DL)}
-
-Deep learning is a subfield of machine learning that employs deep neural networks to learn hierarchical data representations, enabling computational models with multiple processing layers to learn data abstractions across numerous levels.
-These methods have dramatically advanced the state-of-the-art in various domains, including speech recognition, visual object recognition, object detection, drug discovery, genomics, and more \cite{LeCun2015DeepLearning}.
-The effectiveness of deep learning arises from its nonlinear modeling capabilities and scalability with large datasets.
-
-A central algorithm in deep learning is backpropagation, which uses the forward and backward pass process to efficiently compute gradients of the loss function concerning the network's parameters.
-The forward pass involves propagating input data through the network to generate predictions.
-In contrast, the backward pass calculates the error between predictions and ground truth and subsequently returns it through the network.
-This procedure updates the network's parameters using gradient descent, minimizing the loss function and enhancing the model's performance.
-
-Deep learning has led to breakthroughs in processing complex, high-dimensional data, including images, video, speech, and audio, primarily due to deep convolutional nets.
-Simultaneously, recurrent nets have illuminated sequential data analysis such as text and speech.
-Deep learning discovers intricate structures in large datasets, improving our understanding and processing capabilities across various applications.
-
-%Backpropagation
-\input{figures/neural networks/Back_propagation}
-
 \newpage

### 2023-05-22 methods/subsections/model architecture and training strategy.tex
Updates from Overleaf

@@
-\section{Machine Learning Modeling}
-
-This section outlines the methodical procedure of creating, training and assessing algorithms that enable data-driven learning and decision-making.
-The process involves algorithm selection, model architecture design, data preprocessing and transformation, and feature extraction.
-The objective is to minimize prediction error by iteratively fine-tuning the model's parameters.
-The selection between supervised, unsupervised, or reinforcement learning techniques depends on the problem's specifics and data structure.
-Evaluating, refining, and deploying the model to ensure its effective performance with new data in real-world applications is crucial.
-
-I advocate for exposure as the primary method of learning music, highlighting the importance of various musical experiences for a comprehensive understanding of the art form.
-Engagement with diverse musical styles, genres, techniques, and learning methods fosters well-rounded musical proficiency, encouraging creativity and experimentation.
-
-Considering the task at hand, we suggest using a Triple Siamese Network, an architecture proven efficient for music similarity retrieval tasks \cite{contentmusicsimtriplet2020}.
-The goal is to minimize the loss function between an anchor, positive, and negative sample, achieved through online triplet mining \cite{Sikaroudi2020OfflinePatches}.
-
-Using the proposed triple siamese network, and online triplet mining in a self-supervised setting, we aim to train a model that can effectively distinguish between similar and dissimilar samples while considering their underlying composition and production texture.
-
 \subsection{Contrastive Learning of Musical Representations (CLMR)}
@@
 
-\subsection{Siamese Networks}
+\subsection{Siamese and Triplet Siamese Networks}
 
-A Siamese Network, a deep learning architecture introduced by Bromley and LeCun in the early 1990s \cite{Bromley1993SignatureNetwork}, is designed explicitly for tasks involving similarity or comparison between two input instances.
-Its name derives from the structure, which consists of two or more identical subnetworks connected in parallel and joined at the output layer.
-These subnetworks share the same architecture, weights, and hyperparameters, allowing for more efficient memory usage and computational complexity.
+A Siamese Network is a deep learning architecture introduced by Bromley and LeCun in the early 1990s \cite{Bromley1993SignatureNetwork}.
+This architecture is explicitly designed for tasks requiring comparing or assessing similarity between two input instances.
+Its name is derived from the network structure, which consists of two or more identical subnetworks connected in parallel and joined at the output layer.
+These subnetworks share the same architecture, weights, and hyperparameters, allowing more efficient memory usage and computational complexity.
 
-This design is particularly effective for learning from limited or imbalanced datasets, as it focuses on learning the similarity metric rather than specific features of individual classes.
+Siamese Networks are especially effective for learning from limited or imbalanced datasets, as they focus on learning a similarity metric rather than the specific features of individual classes.
+Each subnetwork processes an input independently, and its outputs are then combined and further processed to yield a single similarity score.
+The shared weights during training enable the model to learn an invariant representation for the input instances, thereby enhancing its efficiency in comparing and contrasting them.
+To achieve this, Siamese Networks employ specialized loss functions, such as contrastive or triplet loss, which aim to minimize the distance between similar input pairs and maximize the distance between dissimilar ones.
 
-Each subnetwork processes an input independently, and its outputs are combined and further processed to yield a single similarity score.
-The shared weights during training enable the model to learn an invariant representation for the input instances, improving its efficiency in comparing and contrasting them.
-Siamese Networks employ specialized loss functions, such as contrastive or triplet loss, which minimize the distance between similar input pairs and maximize the distance between dissimilar ones.
-This approach encourages the network to learn a meaningful similarity metric.
+An extension of this architecture is the Triplet Siamese Network, which involves comparing three input instances instead of two.
+This network aims to learn an embedding space in which similar instances are close to each other and dissimilar instances are distant.
+The input to this network consists of an anchor, a positive instance (from the same class as the anchor), and a negative instance (from a different class).
+Each instance is processed by an identical subnetwork that shares its architecture, weights, and hyperparameters with the others.
 
-\subsubsection{Triplet Siamese Networks}
-
-Triplet Siamese Networks, an extension of the Siamese Network architecture, involve comparing three input instances instead of two, aiming to learn an embedding space where similar instances are close and dissimilar instances are distant.
-The input consists of an anchor, a positive instance (same class as the anchor), and a negative instance (different class).
-An identical subnetwork with shared architecture, weights, and hyperparameters processes each instance.
-
-The triplet loss function guides learning, minimizing the distance between the anchor and positive instances while maximizing the distance between the anchor and negative instances.
-A margin parameter in the loss function ensures a minimum separation between positive and negative instances in the embedding space.
-
-Due to shared weights, Triplet Siamese Networks offer efficient memory usage and computational complexity.
+The triplet loss function used in this network guides the learning process.
+It seeks to minimize the distance between the anchor and positive instances while maximizing the distance between the anchor and the negative instances.
+A margin parameter is included in the loss function to ensure a minimum separation between positive and negative instances in the embedding space.
+Due to the shared weights among the subnetworks, Triplet Siamese Networks also offer efficient memory usage and computational complexity.
 
@@
 
-In this equation, triplet loss function with a variable margin:
+In this equation, the triplet loss function with a variable margin:
 

### 2023-05-24 evaluation/subsections/beyond dsp.tex
Updates from Overleaf

@@
-\section{Music Structure Analysis (MSA) as downstream task}
+\section{Music Structure Analysis as downstream task}
 
-While the usefulness of deep audio embeddings can be evaluated in several tasks, we have chosen a core MIR task for its popularity and complexity: Music Structure Analysis (MSA).
+While the usefulness of deep audio embeddings can be evaluated in several scenarios, we have chosen a core MIR task for its popularity and complexity: Music Structure Analysis (MSA).
 This interdisciplinary field aims to understand the structure of music \cite{Nieto2020Audio-BasedApplications}.

### 2023-05-24 future work/future work.tex
Updates from Overleaf

@@
-chapter{}
+\chapter{Future Work}
 
 hybrid autoencoder architecture + UNet stuff
+transforms
+stems
+different takes
+
+Utilize the dB-scale Mel-spectrum magnitude of audio as input data; are a popular choice for input representation in music-related tasks when applying CNNs, as has been demonstrated in various studies.
+In addition to their wide usage, it's been recently reported that their frequency-domain summarization, grounded in psycho-acoustics, is efficient and challenging to replicate through solely data-driven methods.
+\cite{Kim2020OneStrategies}

### 2023-05-24 methods/subsections/machine learning.tex
Updates from Overleaf

--- 2023-05-17 methods/subsections/machine learning.tex
@@
 
-Throughout this chapter, we aim to provide a comprehensive understanding of the methodology employed in our research, laying the foundation for the presentation and discussion of the results in the following chapters.
+Throughout this chapter, we furnish an exhaustive understanding of the methodical process employed in our research, thereby setting the stage for the presentation and discussion of the results in subsequent chapters.
 
-\section{Artificial Neural Networks (ANNs)}
+Our approach could be broadly categorized as cognitive modeling, as it strives to mimic human cognitive processes and problem-solving through a computerized model.
+We champion exposure-based learning in music and active engagement with an array of musical styles, genres, techniques, and learning methods to foster well-rounded musical proficiency and efficient performance with novel data in practical applications.
+
+\section{Deep Learning Modeling}
+
+Deep learning (DL) is a subfield of machine learning that employs deep neural networks to learn hierarchical data representations, enabling computational models with multiple processing layers to learn data abstractions across numerous levels.
+These methods have dramatically advanced the state-of-the-art in various domains, including speech recognition, visual object recognition, object detection, drug discovery, genomics, and more \cite{LeCun2015DeepLearning}.
+The effectiveness of deep learning arises from its nonlinear modeling capabilities and scalability with large datasets.
+
+A central algorithm in deep learning is backpropagation, which uses the forward and backward pass process to compute gradients of the loss function concerning the network's parameters.
+The forward pass involves propagating input data through the network to generate predictions.
+In contrast, the backward pass calculates the error between predictions and ground truth and returns it through the network.
+This procedure updates the network's parameters minimizing the loss function and enhancing the model's performance.
+
+%Backpropagation
+\input{figures/neural networks/Back_propagation}
+
+\subsection{Artificial Neural Networks (ANNs)}
 Artificial Neural Networks (ANNs) are computational models inspired by biological neural systems.
 They use interconnected layers of artificial neurons to process information and perform tasks like pattern recognition, classification, and regression.
-ANNs adjust the connections, or "weights," between neurons during learning to improve performance.
+ANNs adjust the connections or weights between neurons during learning to improve performance.
 The concept of neural networks emerged in the mid-20th century with the work of Warren McCulloch and Walter Pitts.

### 2023-05-24 methods/subsections/model architecture and training strategy.tex
Updates from Overleaf

@@
 
-Contrastive Learning of Musical Representations (CLMR) \cite{CLMR2021} aims to learn discriminative and valuable representations of music without relying on explicit labels.
-By leveraging the structure and content of music and contrasting different augmentations or transformations of the same musical piece against randomly generated pieces, CLMR models can effectively capture the underlying known invariances that are explicitly incorporated into the design of a model to improve its robustness and generalization.
+Piaget's theory of cognitive development suggests children acquire knowledge through sensory experiences, gradually developing abstract reasoning and schemas—basic cognitive structures \cite{Huitt2003PiagetsDevelopment}.
+These schemas evolve by integrating new information through assimilation and accommodation \cite{audioselfsupsurvey}.
 
-In contrast, the model learns unknown invariances from the data without explicit instruction.
+In pattern recognition, models are designed to be robust against known invariances—input data transformations—allowing consistent output.
+Conversely, unknown invariances not considered in the model's design can still be handled due to its learning capacity.
+
+Contrastive Learning of Musical Representations (CLMR) learns valuable, discriminative music representations without explicit labels by contrasting positive augmentations of a musical piece against negative ones \cite{CLMR2021}.
+CLMR works under a machine learning subset called Self-Supervised Learning (SSL), where models self-learn from unlabeled data, creating their supervisory signal \cite{audioselfsupsurvey}.
+This mimics human learning from observations and interactions, transforming unsupervised problems into supervised ones by auto-generating labels.
+The benefits of SSL include reduced reliance on labeled data, making data representation more robust and generalizable.
 
@@
 \item \textbf{Contrastive Learning:} Train by minimizing a contrastive loss function, encouraging the model to produce similar representations for positive pairs and dissimilar representations for antagonistic pairs.
-\item\textbf{Latent Representation:} Utilize the learned representations for various Music Information Retrieval (MIR) downstream tasks, such as music genre classification or similarity, both in the symbolic and time domains.
 \end{enumerate}
 
-By following these steps, CLMR models can learn meaningful and robust representations of music, potentially enhancing their performance in various MIR tasks and reducing the need for labeled data.
+\subsection{Siamese and Triplet Siamese Networks}
 
-\subsection{Encoder: SampleCNN}
+For this task, a Triple Siamese Network is suggested, a model architecture proved efficient for music similarity retrieval tasks \cite{contentmusicsimtriplet2020}, intending to minimize the loss function between an anchor, positive, and negative sample, achieved through online triplet mining \cite{Sikaroudi2020OfflinePatches}.
+The overarching aim is to train a model in a self-supervised setting, which can effectively distinguish between similar and dissimilar samples while considering their underlying composition and production texture.
+
+A Siamese Network is a deep learning architecture introduced by Bromley and LeCun in the early 1990s \cite{Bromley1993SignatureNetwork}.
+This architecture is explicitly designed for tasks requiring comparing or assessing similarity between two input instances.
+It comprises two or more identical subnetworks connected in parallel and joined at the output layer.
+These subnetworks share the same architecture, weights, and hyperparameters, allowing more efficient memory usage and computational complexity.
+
+Siamese Networks are especially effective for learning from limited or imbalanced datasets, as they focus on learning a similarity metric rather than the specific features of individual classes.
+Each subnetwork processes an input independently, and its outputs are then combined and further processed to yield a single similarity score.
+The shared weights during training enable the model to learn an invariant representation for the input instances, thereby enhancing its efficiency in comparing and contrasting them.
+To achieve this, Siamese Networks employ specialized loss functions, such as contrastive or triplet loss, which aim to minimize the distance between similar input pairs and maximize the distance between dissimilar ones.
+
+An extension of this architecture is the Triplet Siamese Network, which involves comparing three input instances instead of two.
+This network aims to learn an embedding space in which similar instances are close to each other and dissimilar instances are distant.
+The input to this network consists of an anchor, a positive instance (from the same class as the anchor), and a negative instance (from a different class).
+Each instance is processed by an identical subnetwork that shares its architecture, weights, and hyperparameters with the others.
+
+The triplet loss function used in this network guides the learning process.
+It seeks to minimize the distance between the anchor and positive instances while maximizing the distance between the anchor and the negative instances.
+A margin parameter is included in the loss function to ensure a minimum separation between positive and negative instances in the embedding space.
+Due to the shared weights among the subnetworks, Triplet Siamese Networks also offer efficient memory usage and computational complexity.
+
+\subsubsection{Encoder: SampleCNN}
 
@@
 
-\begin{figure}[ht]
-\centering
 \begin{equation}
@@
 \end{equation}
-\caption[Average Pooling operation]{\small{Representation of the Average Pooling operation.
+
+Representation of the Average Pooling operation.
 Here, $y_i$ is the output tensor after the average pooling process.
 Each element $x_{ij}$ is part of the 2D input tensor.
-$N$ is the count of elements in the second dimension of the input tensor, while $i$ and $j$ are used to iterate over the first and second dimensions of the tensors, respectively.}}
-\end{figure}
+$N$ is the count of elements in the second dimension of the input tensor, while $i$ and $j$ are used to iterate over the first and second dimensions of the tensors, respectively.
 
@@
 
-\subsection{Siamese and Triplet Siamese Networks}
-
-A Siamese Network is a deep learning architecture introduced by Bromley and LeCun in the early 1990s \cite{Bromley1993SignatureNetwork}.
-This architecture is explicitly designed for tasks requiring comparing or assessing similarity between two input instances.
-Its name is derived from the network structure, which consists of two or more identical subnetworks connected in parallel and joined at the output layer.
-These subnetworks share the same architecture, weights, and hyperparameters, allowing more efficient memory usage and computational complexity.
-
-Siamese Networks are especially effective for learning from limited or imbalanced datasets, as they focus on learning a similarity metric rather than the specific features of individual classes.
-Each subnetwork processes an input independently, and its outputs are then combined and further processed to yield a single similarity score.
-The shared weights during training enable the model to learn an invariant representation for the input instances, thereby enhancing its efficiency in comparing and contrasting them.
-To achieve this, Siamese Networks employ specialized loss functions, such as contrastive or triplet loss, which aim to minimize the distance between similar input pairs and maximize the distance between dissimilar ones.
-
-An extension of this architecture is the Triplet Siamese Network, which involves comparing three input instances instead of two.
-This network aims to learn an embedding space in which similar instances are close to each other and dissimilar instances are distant.
-The input to this network consists of an anchor, a positive instance (from the same class as the anchor), and a negative instance (from a different class).
-Each instance is processed by an identical subnetwork that shares its architecture, weights, and hyperparameters with the others.
-
-The triplet loss function used in this network guides the learning process.
-It seeks to minimize the distance between the anchor and positive instances while maximizing the distance between the anchor and the negative instances.
-A margin parameter is included in the loss function to ensure a minimum separation between positive and negative instances in the embedding space.
-Due to the shared weights among the subnetworks, Triplet Siamese Networks also offer efficient memory usage and computational complexity.
-
-\subsubsection{Self-Supervised Learning (SSL)}
-
-Self-supervised learning (SSL) is a subfield of machine learning where models learn to generate representations of data by finding patterns and structures within the data without relying on external labels or annotations.
-In other words, the model learns by creating its supervision signal from the raw, unlabeled data.\cite{audioselfsupsurvey}
-
-This approach to learning is inspired by the way humans and animals learn from their environment, where a great deal of knowledge is acquired through observation and interaction without explicit instruction.
-Self-supervised learning is a machine learning process where the model trains itself to learn one part of the input from another part of the input.
-In this process, the unsupervised problem is transformed into a supervised problem by auto-generating the labels.
-
-SSL's main advantages include reducing dependency on labeled data, which can be expensive and time-consuming to collect and annotate.
-Also, encourages more generalizable and robust representations of the data since they capture the inherent structure and properties of the data rather than relying on human-provided labels.
-
-Further understanding of the cognitive processes in music can be obtained through Jean Piaget's theory of cognitive development.
-Piaget suggests that children acquire knowledge through sensory and motor experiences in their early stages, with reasoning gradually evolving toward abstract ideas and deductive logic through the development of schemas—cognitive structures that underlie human knowledge and skill \cite{Huitt2003PiagetsDevelopment}.
-These schemas evolve through an equilibration mechanism that incorporates new information with pre-existing knowledge, involving processes of assimilation and accommodation \cite{audioselfsupsurvey}.
-
-\subsubsection{Known and unknown invariance}
-
-In pattern recognition, \textit{invariance} refers to the property of a model to be robust to certain transformations or changes in the input data.
-In other words, an invariant model should produce the same or similar output for different instances of the same object, even if they have undergone some changes.
-
-\begin{definition}[Known invariance]
-Known invariances are transformations or changes that the model or algorithm is explicitly designed to be robust against.
-By incorporating these invariances into the model's design, the algorithm is better equipped to generalize and recognize patterns in the presence of these transformations.
-\end{definition}
-
-\begin{definition}[Unknown invariance]
-
-Unknown invariances are transformations the model has not been explicitly designed to handle.
-However, it still manages to be robust due to its learning capabilities.
-These invariances can emerge from the data and may not be known a priori.
-\end{definition}
-
 \subsection{Audio augmentation and transformation pipeline}
 
-\subsubsection{Positive sample generation}
+\subsubsection{Positive sample generation chain}
 
-While useful audio transformations tools \cite{Spijkervet2021Spijkervet/torchaudio-augmentations:V1.0}
+The positive image in our study should preserve its intelligible content when subjected to temporal transformations, regardless of alterations in sonic qualities.
+Maintaining the temporal structure and meaningfulness of the content allows it to present musical elements identical or strikingly similar to the original track.
 
-Given an anchor audio signal $A[n]$, we generate a positive signal $P[n]$ by applying a series of amplitude, time-domain, frequency-domain, modulation, reverberation, and nonlinear effects with additive noise on top of the chain.
+While the MIR community has access to helpful audio transformation tools \cite{Spijkervet2021Spijkervet/torchaudio-augmentations:V1.0}, the specific requirements of our experiments necessitated the development of our transformation chain: given an anchor audio signal $A[n]$, we generate a positive signal $P[n]$ by applying a series of amplitude, time-domain, frequency-domain, modulation, reverberation, and nonlinear effects with additive noise on top of it.
 
 Let $g \in [-12, 0]$ represent the gain, $\Delta p \in [-1200, 1200]$ the pitch shift, $h_R[n]$ the impulse response of the reverb with parameters in $[0, 100]$, $h_C[n]$ the impulse response of the chorus with parameters determined by the specified ranges, $d \in [0, 30]$ the overdrive parameter, $\alpha \in [0.9, 1.1]$ the speed change factor, $\beta \in [0.9, 1.1]$ the stretch factor, $f_m \in [0.1, 100]$ the modulation frequency of the tremolo, and $d_m \in [1, 101]$ the depth of the tremolo.
-
-The positive signal $P[n]$ is generated as follows:
-
-\begin{equation}\label{eq:positive_signal}
-P[n] = A[n] \ast h_{G}[n] \ast h_{C}[n] \ast h_{D}[n] \ast h_{P_t}[n] \ast h_{R}[n] \ast h_{S}[n] \ast h_{T}[n] \ast h_{T_m}[n] + N[n]
-\end{equation}
-
-where $\ast$ denotes convolution, $h_{G}[n] = g \delta[n]$, $h_{D}[n]$ is the impulse response of the overdrive effect, $h_{P_t}[n]$ is the impulse response of the pitch shift effect, $h_{S}[n]$ represents the impulse response of the speed change effect, $h_{T}[n]$ is the impulse response of the stretch effect, and $h_{T_m}[n] = (1 - d_m \cos(2 \pi f_m n))\delta[n]$ is the impulse response of the tremolo effect.
-The noise signal $N[n]$ is added with a specific signal-to-noise ratio (SNR) in the range $[12, 100]$ in decibels.
 
@@
 
+The positive signal $P[n]$ is generated as follows:
+
+\begin{equation}\label{eq:positive_signal}
+P[n] = A[n] \ast h_{G}[n] \ast h_{C}[n] \ast h_{D}[n] \ast h_{P_t}[n] \ast h_{R}[n] \ast h_{S}[n] \ast h_{T}[n] \ast h_{T_m}[n] + N[n]
+\end{equation}
+
+where $\ast$ denotes convolution, $h_{G}[n] = g \delta[n]$, $h_{D}[n]$ is the impulse response of the overdrive effect, $h_{P_t}[n]$ is the impulse response of the pitch shift effect, $h_{S}[n]$ represents the impulse response of the speed change effect, $h_{T}[n]$ is the impulse response of the stretch effect, and $h_{T_m}[n] = (1 - d_m \cos(2 \pi f_m n))\delta[n]$ is the impulse response of the tremolo effect.
+The noise signal $N[n]$ is added with a specific signal-to-noise ratio (SNR) in the range $[12, 100]$ in decibels.
+
 \subsubsection{Negative sample generation}
+
+We posit that high-level musical content unfolds over time; therefore, we argue that the temporal structure of the negative images related to our anchor should be disrupted.
+While maintaining similar sonic qualities, the content should be rendered unintelligible.
 
@@
 \item Calculate the minimum and maximum audio chunk lengths in samples:
-2\begin{equation}
+\begin{equation}
 l_{min} = t_{min} \times S
@@
 
-The anchor-positive distance and the anchor-negative distance are computed as the Euclidean distance between the corresponding samples:
+The anchor-positive and anchor-negative distances are computed as the Euclidean distances between the corresponding samples.
 
@@
 
-The "hardest" negative index for each anchor-positive pair is determined by maximizing the difference between the anchor-negative and anchor-positive distances:
+The "hardest" negative index for each anchor-positive pair is determined by maximizing the difference between the anchor-negative and anchor-positive distances \cite{XuanImprovedMining}.
 

### 2023-05-25 abstract/abstract.tex
Updates from Overleaf

--- 2023-05-14 abstract/abstract.tex
@@
 
-Music, an integral part of human culture, offers a diverse yet complex field of study due to its intricate styles, mutable ground truth, and subjective nature.
-This research, conducted in collaboration with Epidemic Sound AB and the Music Technology Group (MTG) at Universitat Pompeu Fabra (UPF), employs self-supervised contrastive learning of musical representation to uncover the fundamental structure of Western tonal music.
+This thesis asserts the existence of high-level musical concepts that, while evolving and unfolding over time, remain invariant to changes in sonic qualities.
+This notion echoes the symbolic domain's characteristics, wherein the essence persists regardless of varied interpretations through diverse performances, instruments, and styles.
 
-Embracing a subtle novel approach, this process is facilitated by applying Siamese networks with a triplet loss, mimicking human aural skills in interpreting music to discern abstract and semantic musical elements, irrespective of the sonic qualities.
-The study replaces traditional acoustical features with deep audio embeddings to compute high-level, sound-agnostic, and content-sensitive music identification.
+In collaboration with Epidemic Sound AB and the Music Technology Group (MTG) at Universitat Pompeu Fabra (UPF), we employed self-supervised contrastive learning of musical representation to decipher the underlying structure of Western tonal music.
 
-Results XXXXXX
+Taking a subtle yet novel approach, we utilized deep neural networks with a triplet loss function to facilitate this process.
+This strategy mirrors human aural skills in music interpretation, discerning abstract and semantic musical elements irrespective of their sonic qualities.
+This research supplants traditional acoustical features with deep audio embeddings, enabling high-level, sound-agnostic, and content-sensitive music identification.
 
-The preliminary results suggest that our approach to learning music-informed embeddings holds significant potential for nearly all MIR downstream tasks.
-Music-motivated embeddings represent a promising technique, adaptable potentially to other tasks hindered by data scarcity.
-This method could significantly influence advancements in intelligent music recommendation systems and the efficient enforcement of intellectual property rights.
+Our method of learning embeddings is significant, emphasizing the use of full-resolution data to maintain the integrity of high-level musical information.
+Leveraging our expertise in the music domain, we construct aggressive transformations to embed heuristic musical concepts.
+With these innovative strides, we strive to bridge the gap between music and machine learning, improving the efficacy of machine listening models.
+
+Preliminary results indicate that our musically-informed approach to learning embeddings carries the substantial potential for boundary detection tasks and, as our intuition suggests, possibly for nearly all Music Information Retrieval (MIR) downstream tasks.
+Music-motivated embeddings emerge as a promising technique, potentially adaptable to other tasks challenged by data scarcity.
 

### 2023-05-25 figures/neural networks/Multi-layer_NN.tex
Updates from Overleaf

--- 2023-01-14 Figures/Figures CNN/Multi-layer_NN.tex
@@
-\begin{figure}[h]
+\begin{figure}[ht]
 	\centering
-	\begin{tikzpicture}[shorten >=1pt]
-		\tikzstyle{unit}=[draw,shape=circle,minimum size=1.15cm]
-		%\tikzstyle{hidden}=[draw,shape=circle,fill=black!25,minimum size=1.15cm]
-		\tikzstyle{hidden}=[draw,shape=circle,minimum size=1.15cm]
+	% NEURAL NETWORK with coefficients, shifted
+\begin{tikzpicture}[x=2.2cm,y=1.4cm]
+  \message{^^JNeural network, shifted}
+  \readlist\Nnod{4,5,5,5,3} % array of number of nodes per layer
+  \readlist\Nstr{n,m,m,m,k} % array of string number of nodes per layer
+  \readlist\Cstr{\strut x,a^{(\prev)},a^{(\prev)},a^{(\prev)},y} % array of coefficient symbol per layer
+  \def\yshift{0.5} % shift last node for dots
 
-		\node[unit](x0) at (0,3.5){$x_0$};
-		\node[unit](x1) at (0,2){$x_1$};
-		\node at (0,1){\vdots};
-		\node[unit](xd) at (0,0){$x_D$};
+  \message{^^J  Layer}
+  \foreachitem \N \in \Nnod{ % loop over layers
+    \def\lay{\Ncnt} % alias of index of current layer
+    \pgfmathsetmacro\prev{int(\Ncnt-1)} % number of previous layer
+    \message{\lay,}
+    \foreach \i [evaluate={\c=int(\i==\N); \y=\N/2-\i-\c*\yshift;
+                 \index=(\i<\N?int(\i):"\Nstr[\lay]");
+                 \x=\lay; \n=\nstyle;}] in {1,...,\N}{ % loop over nodes
+      % NODES
+      \node[node \n] (N\lay-\i) at (\x,\y) {$\Cstr[\lay]_{\index}$};
 
-		\node[hidden](h10) at (3,4){$y_0^{(1)}$};
-		\node[hidden](h11) at (3,2.5){$y_1^{(1)}$};
-		\node at (3,1.5){\vdots};
-		\node[hidden](h1m) at (3,-0.5){$y_{m^{(1)}}^{(1)}$};
+      % CONNECTIONS
+      \ifnum\lay>1 % connect to previous layer
+        \foreach \j in {1,...,\Nnod[\prev]}{ % loop over nodes in previous layer
+          \draw[connect,white,line width=1.2] (N\prev-\j) -- (N\lay-\i);
+          \draw[connect] (N\prev-\j) -- (N\lay-\i);
+          %\draw[connect] (N\prev-\j.0) -- (N\lay-\i.180); % connect to left
+        }
+      \fi % else: nothing to connect first layer
 
-		\node(h22) at (5,0){};
-		\node(h21) at (5,2){};
-		\node(h20) at (5,4){};
+    }
+    \path (N\lay-\N) --++ (0,1+\yshift) node[midway,scale=1.5] {$\vdots$};
+  }
 
-		\node(d3) at (6,0){$\ldots$};
-		\node(d2) at (6,2){$\ldots$};
-		\node(d1) at (6,4){$\ldots$};
+  % LABELS
+  \node[above=0.8,align=center,mygreen!60!black] at (N1-1.90) {input\\[-0.2em]layer};
+  \node[above=0.5,align=center,myblue!60!black] at (N3-1.90) {hidden layers};
+  \node[above=1.3,align=center,myred!60!black] at (N\Nnodlen-1.90) {output\\[-0.2em]layer};
 
-		\node(hL12) at (7,0){};
-		\node(hL11) at (7,2){};
-		\node(hL10) at (7,4){};
-
-		\node[hidden](hL0) at (9,4){$y_0^{(L)}$};
-		\node[hidden](hL1) at (9,2.5){$y_1^{(L)}$};
-		\node at (9,1.5){\vdots};
-		\node[hidden](hLm) at (9,-0.5){$y_{m^{(L)}}^{(L)}$};
-
-		\node[unit](y1) at (12,3.5){$y_1^{(L+1)}$};
-		\node[unit](y2) at (12,2){$y_2^{(L+1)}$};
-		\node at (12,1){\vdots};	
-		\node[unit](yc) at (12,0){$y_C^{(L+1)}$};
-
-		\draw[->] (x0) -- (h11);
-		\draw[->] (x0) -- (h1m);
-
-		\draw[->] (x1) -- (h11);
-		\draw[->] (x1) -- (h1m);
-
-		\draw[->] (xd) -- (h11);
-		\draw[->] (xd) -- (h1m);
-
-		\draw[->] (hL0) -- (y1);
-		\draw[->] (hL0) -- (yc);
-		\draw[->] (hL0) -- (y2);
-
-		\draw[->] (hL1) -- (y1);
-		\draw[->] (hL1) -- (yc);
-		\draw[->] (hL1) -- (y2);
-
-		\draw[->] (hLm) -- (y1);
-		\draw[->] (hLm) -- (y2);
-		\draw[->] (hLm) -- (yc);
-
-		\draw[->,path fading=east] (h10) -- (h21);
-		\draw[->,path fading=east] (h10) -- (h22);
-
-		\draw[->,path fading=east] (h11) -- (h21);
-		\draw[->,path fading=east] (h11) -- (h22);
-
-		\draw[->,path fading=east] (h1m) -- (h21);
-		\draw[->,path fading=east] (h1m) -- (h22);
-
-		\draw[->,path fading=west] (hL10) -- (hL1);
-		\draw[->,path fading=west] (hL11) -- (hL1);
-		\draw[->,path fading=west] (hL12) -- (hL1);
-
-		\draw[->,path fading=west] (hL10) -- (hLm);
-		\draw[->,path fading=west] (hL11) -- (hLm);
-		\draw[->,path fading=west] (hL12) -- (hLm);
-
-		\draw [decorate,decoration={brace,amplitude=10pt},xshift=-4pt,yshift=0pt] (-0.5,4) -- (0.75,4) node [black,midway,yshift=+0.6cm]{input layer};
-		\draw [decorate,decoration={brace,amplitude=10pt},xshift=-4pt,yshift=0pt] (2.5,4.5) -- (3.75,4.5) node [black,midway,yshift=+0.6cm]{$1^{\text{st}}$ hidden layer};
-		\draw [decorate,decoration={brace,amplitude=10pt},xshift=-4pt,yshift=0pt] (8.5,4.5) -- (9.75,4.5) node [black,midway,yshift=+0.6cm]{$L^{\text{th}}$ hidden layer};
-		\draw [decorate,decoration={brace,amplitude=10pt},xshift=-4pt,yshift=0pt] (11.5,4) -- (12.75,4) node [black,midway,yshift=+0.6cm]{output layer};
 \end{tikzpicture}
-	\caption[Network graph for a $(L+1)$-layer perceptron.]{Network graph of a $(L+1)$-layer perceptron with $D$ input units and $C$ output units.
-The $l^{\text{th}}$ hidden layer contains $m^{(l)}$ hidden units.}
-	\label{fig:multilayer-perceptron}
+	\caption[Network graph for perceptron.]{\small{Network graph of a perceptron with $D$ input units and $C$ output units.
+The $l^{\text{th}}$ hidden layer contains $m^{(l)}$ hidden units.
+Each neuron in a layer receives input from the previous layer and computes an output value using an activation function.
+The output of the last layer represents the prediction or classification result.
+}}
+	\label{fig: multilayer color perceptron}
 \end{figure}

### 2023-05-25 figures/neural networks/activation.tex
Updates from Overleaf

--- 2023-04-11 figures/neural networks/activation.tex
@@
+\begin{figure}
+    \centering
+    \scalebox{0.9}{
 % NEURAL NETWORK activation
@@
 \end{tikzpicture}
+}
+\caption[Activation function.]{\small{The input layer with \textit{n} nodes is denoted as $a_i^{(0)}$ for $i \in \{1, \ldots, n\}$.
+The output layer with \textit{m} nodes is $a_j^{(1)}$ for $j \in \{1, \ldots, m\}$.
+Connections between these layers are governed by the weight matrix $\mathbf{W}^{(0)} \in \mathbb{R}^{m\times n}$ and bias vector $\mathbf{b}^{(0)} \in \mathbb{R}^{m}$, with elements $w_{j,i}$ and $b_j^{(0)}$ respectively.
+The activation function, denoted as $\sigma$, operates element-wise on the sum of the product of the weight matrix, input vector, and bias vector.}}
+
+    \label{fig:activation_function}
+
+\end{figure}

### 2023-05-25 methods/subsections/machine learning.tex
Updates from Overleaf

@@
 
-Deep learning (DL) is a subfield of machine learning that employs deep neural networks to learn hierarchical data representations, enabling computational models with multiple processing layers to learn data abstractions across numerous levels.
-These methods have dramatically advanced the state-of-the-art in various domains, including speech recognition, visual object recognition, object detection, drug discovery, genomics, and more \cite{LeCun2015DeepLearning}.
-The effectiveness of deep learning arises from its nonlinear modeling capabilities and scalability with large datasets.
+Deep learning (DL), a subset of machine learning, employs deep neural networks to decipher hierarchical data representations, allowing models with multiple processing layers to abstract data across numerous levels \cite{LeCun2015DeepLearning}.
+DL models have significantly improved various domains due to their nonlinear modeling capabilities and scalability with large datasets.
 
-A central algorithm in deep learning is backpropagation, which uses the forward and backward pass process to compute gradients of the loss function concerning the network's parameters.
-The forward pass involves propagating input data through the network to generate predictions.
-In contrast, the backward pass calculates the error between predictions and ground truth and returns it through the network.
-This procedure updates the network's parameters minimizing the loss function and enhancing the model's performance.
+They leverage the central algorithm, backpropagation, which calculates gradients of the loss function related to network parameters through forward and backward pass processes, thereby optimizing model performance.
 
@@
 
-\subsection{Artificial Neural Networks (ANNs)}
-Artificial Neural Networks (ANNs) are computational models inspired by biological neural systems.
-They use interconnected layers of artificial neurons to process information and perform tasks like pattern recognition, classification, and regression.
-ANNs adjust the connections or weights between neurons during learning to improve performance.
-The concept of neural networks emerged in the mid-20th century with the work of Warren McCulloch and Walter Pitts.
-Still, modern neural networks began with Frank Rosenblatt's perceptron in 1957, a single-layer network able to learn linearly separable patterns.
+Deep Neural Networks (DNNs), computational models rooted in biological neural systems, utilize layers of artificial neurons for tasks such as pattern recognition, classification, and regression.
+DNNs evolve by adjusting connections between neurons during learning, a concept initiated in the mid-20th century but modernized with Frank Rosenblatt's single-layer perceptron in 1957, capable of learning linearly separable patterns.
 
-%Single neuron
-\input{figures/neural networks/Single Neuron}
+%Multi-layer_NN
+\input{figures/neural networks/Multi-layer_NN}
 
-%NN
-\input{figures/neural networks/Network_graph}
-
-It consists of an input layer, one or more hidden layers, and an output layer.
-Each neuron in a layer receives input from the previous layer and computes an output value using an activation function.
-The output of the last layer represents the prediction or classification result.
+Another crucial component in the operation of DNNs is the activation function.
+This function is applied to a neuron's inputs, transforming the input's summed product and weights into an output passed onto the next layer.
+It introduces non-linearity into the network, enabling it to learn complex patterns and relationships from the data.
 
@@
 
-%Multi-layer_NN
-\input{figures/neural networks/Multi-layer_NN}
+%Colour CNN
+\input{figures/neural networks/colour CNN}
 

### 2023-05-25 methods/subsections/model architecture and training strategy.tex
Updates from Overleaf

@@
 
-The original model has been modified slightly to serve our specific needs: the output from the final convolutional layer is now subjected to an average pooling operation across the temporal dimension.
-
-%%%%%BATCH NORM%%%%%%%%%%
-
-The maximum array length in the batch is given by:
-
-\begin{equation}
-L_{\text{max}} = \max_{\text{item} \in \text{batch}}(\max(\text{length}(A_{\text{item}}), \text{length}(P_{\text{item}}), \text{length}(N_{\text{item}})))
-\end{equation}
-
-This adaptation of the original architecture incorporates an average pooling step at the end.
+The original model has been modified slightly to serve our specific needs: the output from the final convolutional layer is now subjected to an average pooling operation at the end.
 
@@
 
-Representation of the Average Pooling operation.
 Here, $y_i$ is the output tensor after the average pooling process.
-Each element $x_{ij}$ is part of the 2D input tensor.
+Each element $x_{ij}$ is part of the input tensor.
 $N$ is the count of elements in the second dimension of the input tensor, while $i$ and $j$ are used to iterate over the first and second dimensions of the tensors, respectively.
 
-\input{figures/neural networks/dropout}
+%%%%%BATCH NORM%%%%%%%%%%
 
-\input{figures/my model/SampleCNN}
+In implementing batch normalization, it is necessary to standardize the audio lengths across all elements in the minibatch.
+We opted to zero-pad all clips to the length of the longest clip, valuing data integrity and completeness over potential performance trade-offs.
+Thus, the length of the longest array in the batch, which sets the standard for all others, is as follows:
 
-%Colour CNN
-\input{figures/neural networks/colour CNN}
+\begin{equation}
+L_{\text{max}} = \max_{\text{item} \in \text{batch}}(\max(\text{length}(A_{\text{item}}), \text{length}(P_{\text{item}}), \text{length}(N_{\text{item}})))
+\end{equation}
 
@@
 \end{equation}
+
+\begin{figure}
+    \centering
+    \includegraphics[clip,width=\columnwidth]{figures/images/Triplet Network.jpeg}
+    \caption[]{Caption}
+    \label{fig:my_label}
+\end{figure}

### 2023-05-25 methods/subsections/deep learning.tex
Updates from Overleaf

--- 2023-05-25 methods/subsections/machine learning.tex
@@
-\section{Introduction}
-
-Throughout this chapter, we furnish an exhaustive understanding of the methodical process employed in our research, thereby setting the stage for the presentation and discussion of the results in subsequent chapters.
-
-Our approach could be broadly categorized as cognitive modeling, as it strives to mimic human cognitive processes and problem-solving through a computerized model.
-We champion exposure-based learning in music and active engagement with an array of musical styles, genres, techniques, and learning methods to foster well-rounded musical proficiency and efficient performance with novel data in practical applications.
-
 \section{Deep Learning Modeling}

### 2023-05-25 methods/subsections/intro.tex
Updates from Overleaf

--- 2023-05-25 methods/subsections/machine learning.tex
@@
 We champion exposure-based learning in music and active engagement with an array of musical styles, genres, techniques, and learning methods to foster well-rounded musical proficiency and efficient performance with novel data in practical applications.
-
-\section{Deep Learning Modeling}
-
-Deep learning (DL), a subset of machine learning, employs deep neural networks to decipher hierarchical data representations, allowing models with multiple processing layers to abstract data across numerous levels \cite{LeCun2015DeepLearning}.
-DL models have significantly improved various domains due to their nonlinear modeling capabilities and scalability with large datasets.
-
-They leverage the central algorithm, backpropagation, which calculates gradients of the loss function related to network parameters through forward and backward pass processes, thereby optimizing model performance.
-
-%Backpropagation
-\input{figures/neural networks/Back_propagation}
-
-Deep Neural Networks (DNNs), computational models rooted in biological neural systems, utilize layers of artificial neurons for tasks such as pattern recognition, classification, and regression.
-DNNs evolve by adjusting connections between neurons during learning, a concept initiated in the mid-20th century but modernized with Frank Rosenblatt's single-layer perceptron in 1957, capable of learning linearly separable patterns.
-
-%Multi-layer_NN
-\input{figures/neural networks/Multi-layer_NN}
-
-Another crucial component in the operation of DNNs is the activation function.
-This function is applied to a neuron's inputs, transforming the input's summed product and weights into an output passed onto the next layer.
-It introduces non-linearity into the network, enabling it to learn complex patterns and relationships from the data.
-
-%Activation equation
-\input{figures/neural networks/activation}
-
-%Colour CNN
-\input{figures/neural networks/colour CNN}
-
-\newpage

### 2023-05-25 evaluation/subsections/beyond dsp.tex
Updates from Overleaf

@@
     \centering
-    \includegraphics[width=\textwidth]{figures/images/embeddiogram_SALAMI_track_2.png}
+    \includegraphics[width=\textwidth]{figures/images/embeddiogram SALAMI 3.png}
     \caption[Embeddiogram]{Embeddiogram computed from...}
@@
         \centering
-        \includegraphics[width=0.9\textwidth]{figures/images/Rec_matrix_SALAMI_track_2.png} % first figure itself
+        \includegraphics[width=0.9\textwidth]{figures/images/recurrence plot SALAMI 3.png} % first figure itself
         \caption{first figure}

### 2023-05-26 methods/subsections/implementation.tex
Updates from Overleaf

--- 2023-05-25 methods/subsections/model architecture and training strategy.tex
@@
+\section{Implementation details}
 \subsection{Contrastive Learning of Musical Representations (CLMR)}
@@
 
-The SampleCNN model \cite{Lee2018SampleCNN:Classification} takes 1D input data with a single channel.
-The first layer is a 1D convolutional layer with a kernel size of 3, a stride of 3, and 128 output channels.
-It is followed by batch normalization and ReLU activation.
+The SampleCNN model \cite{Lee2018SampleCNN:Classification} takes 1D input data with a single channel and follows the next architecture:
+
+\begin{tabular}{|p{4.5cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}|}
+\hline
+\textbf{Layer Type} & \textbf{In Channels} & \textbf{Out Channels} & \textbf{Kernel Size} & \textbf{Stride} \\
+\hline
+Conv1d + BatchNorm1d + ReLU & 1 & 128 & 3 & 3 \\
+\hline
+\multicolumn{5}{|c|}{The following layers are repeated depending on the strides and hidden parameters} \\
+\hline
+Conv1d + BatchNorm1d + ReLU + MaxPool1d & 128 & 128 & `<stride>` & `<stride>` \\
+Conv1d + BatchNorm1d + ReLU + MaxPool1d & 128 & 128 & `<stride>` & `<stride>` \\
+Conv1d + BatchNorm1d + ReLU + MaxPool1d & 128 & 256 & `<stride>` & `<stride>` \\
+Conv1d + BatchNorm1d + ReLU + MaxPool1d & 256 & 256 & `<stride>` & `<stride>` \\
+Conv1d + BatchNorm1d + ReLU + MaxPool1d & 256 & 256 & `<stride>` & `<stride>` \\
+Conv1d + BatchNorm1d + ReLU + MaxPool1d & 256 & 256 & `<stride>` & `<stride>` \\
+Conv1d + BatchNorm1d + ReLU + MaxPool1d & 256 & 256 & `<stride>` & `<stride>` \\
+Conv1d + BatchNorm1d + ReLU + MaxPool1d & 256 & 256 & `<stride>` & `<stride>` \\
+Conv1d + BatchNorm1d + ReLU + MaxPool1d & 256 & 512 & `<stride>` & `<stride>` \\
+\hline
+Conv1d + BatchNorm1d + ReLU & 512 & 512 & 3 & 1 \\
+\hline
+Dropout (optional) & - & - & - & - \\
+\hline
+Linear (Fully Connected) & 512 & 128 & - & - \\
+\hline
+\end{tabular}
 
@@
 
-%%%%%BATCH NORM%%%%%%%%%%
-
-In implementing batch normalization, it is necessary to standardize the audio lengths across all elements in the minibatch.
-We opted to zero-pad all clips to the length of the longest clip, valuing data integrity and completeness over potential performance trade-offs.
-Thus, the length of the longest array in the batch, which sets the standard for all others, is as follows:
-
-\begin{equation}
-L_{\text{max}} = \max_{\text{item} \in \text{batch}}(\max(\text{length}(A_{\text{item}}), \text{length}(P_{\text{item}}), \text{length}(N_{\text{item}})))
-\end{equation}
+\subsubsection{Optimizer}
 
@@
 \end{figure}
+
+%%%%%BATCH NORM%%%%%%%%%%
+
+In implementing batch normalization, it is necessary to standardize the audio lengths across all elements in the minibatch.
+We opted to zero-pad all clips to the length of the longest clip, valuing data integrity and completeness over potential performance trade-offs.
+Thus, the length of the longest array in the batch, which sets the standard for all others, is as follows:
+
+\begin{equation}
+L_{\text{max}} = \max_{\text{item} \in \text{batch}}(\max(\text{length}(A_{\text{item}}), \text{length}(P_{\text{item}}), \text{length}(N_{\text{item}})))
+\end{equation}
+\newpage

### 2023-05-26 figures/neural networks/Back_propagation.tex
Updates from Overleaf

@@
     	\end{tikzpicture}
-	\caption[Backpropagation.]{\small{Backpropagation of errors through the network: once evaluated for all output units, the errors $\delta_i^{(L+1)}$ can be propagated backward.}}
+	\caption[Backpropagation.]{\small{Backpropagation of errors through the network; once evaluated for all output units, the errors $\delta_i^{(L+1)}$ can be propagated backward.}}
 	\label{fig:error-backpropagation}

### 2023-05-26 introduction/Subsections/Previous work.tex
Updates from Overleaf

@@
 Neural networks have recently facilitated the development of low-dimensional embeddings that capture essential musical features, enabling the computation of various task-specific aspects.
-These aspects include:
 
-\begin{itemize}
-
-\item The utilization of multi-level music segmentation through deep audio embeddings to replace manually engineered features \cite{SalamonDeepSegmentation}.
-
-\item The enhancement of environmental sound classification \cite{Kim2020OneStrategies}.
-
-\item The improvement of vocal-centric music tasks using cross-domain audio embedding \cite{Kim2021LearningLoss}.
-
-\item The enhancement of audio classification through a combination of task-specific and pre-trained features \cite{Hung2022Feature-informedClassification}.
-
-\item The creation of a music similarity search engine specifically for video producers \cite{epidemic}.
-
-\item The improved performance in Music Emotion Recognition (MER) tasks, eliminating the necessity for expert human engineering \cite{KohComparisonRecognition}.
-
-\item The resolution of the cross-modal text-to-music retrieval problem, enabling content creators to find music that matches the emotion conveyed in their text-based stories \cite{WonEmotionStories}.
-
-\item Music rearrangement is traditionally undertaken by expert music engineers or more classical MIR approaches \cite{Stoller2018IntuitiveTransitions}.
-This innovative approach presents a promising avenue for automated music rearrangement, enhancing the process's efficiency and quality.
-\cite{Plachouras2023MusicSegmentation}
-
-\end{itemize}
+These aspects include the utilization of multi-level music segmentation through deep audio embeddings to replace manually engineered features \cite{SalamonDeepSegmentation}, the enhancement of environmental sound classification \cite{Kim2020OneStrategies}, the improvement of vocal-centric music tasks using cross-domain audio embedding \cite{Kim2021LearningLoss}, the enhancement of audio classification through a combination of task-specific and pre-trained features \cite{Hung2022Feature-informedClassification}, the creation of a music similarity search engine specifically for video producers \cite{epidemic}, the improved performance in Music Emotion Recognition (MER) tasks \cite{KohComparisonRecognition}, embedding songs for similarity comparison based on artist identification \cite{contentmusicsimtriplet2020}, the resolution of the cross-modal text-to-music retrieval problem \cite{WonEmotionStories}, and music rearrangement \cite{Stoller2018IntuitiveTransitions}.
+This last innovative approach presents a promising avenue for automated music rearrangement, enhancing the process's efficiency and quality \cite{Plachouras2023MusicSegmentation}.
 

### 2023-05-26 methods/subsections/implementation.tex
Updates from Overleaf

--- 2023-05-25 methods/subsections/model architecture and training strategy.tex
@@
 
-The SampleCNN model \cite{Lee2018SampleCNN:Classification} takes 1D input data with a single channel.
-The first layer is a 1D convolutional layer with a kernel size of 3, a stride of 3, and 128 output channels.
-It is followed by batch normalization and ReLU activation.
+The SampleCNN model \cite{Lee2018SampleCNN:Classification} takes 1D input data with a single channel and follows the next architecture:
+
+\begin{table}[h]
+\centering
+\small
+\begin{tabularx}{\textwidth}{|>{\hsize=1.6\hsize}X|>{\hsize=0.6\hsize}X|>{\hsize=0.6\hsize}X|}
+\hline
+\textbf{Layer Type} & \textbf{In Channels} & \textbf{Out Channels} \\
+\hline
+Conv1d + BatchNorm1d + ReLU & 1 & 128 \\
+\hline
+\multicolumn{3}{|c|}{The following layers are repeated depending on the strides and hidden parameters} \\
+\hline
+Conv1d + BatchNorm1d + ReLU + MaxPool1d & 128 & 128 \\
+Conv1d + BatchNorm1d + ReLU + MaxPool1d & 128 & 128 \\
+Conv1d + BatchNorm1d + ReLU + MaxPool1d & 128 & 256 \\
+Conv1d + BatchNorm1d + ReLU + MaxPool1d & 256 & 256 \\
+Conv1d + BatchNorm1d + ReLU + MaxPool1d & 256 & 256 \\
+Conv1d + BatchNorm1d + ReLU + MaxPool1d & 256 & 256 \\
+Conv1d + BatchNorm1d + ReLU + MaxPool1d & 256 & 256 \\
+Conv1d + BatchNorm1d + ReLU + MaxPool1d & 256 & 256 \\
+Conv1d + BatchNorm1d + ReLU + MaxPool1d & 256 & 512 \\
+\hline
+Conv1d + BatchNorm1d + ReLU & 512 & 512 \\
+\hline
+Fully connected representation layer & 512 & 128 \\
+\hline
+\end{tabularx}
+\caption{Layer specifications for SampleCNN model}
+\label{tab:samplecnn}
+\end{table}
 
@@
 
-In this equation, the triplet loss function with a variable margin:
-
 $\mathcal{L}$ is the triplet loss function.
@@
 
-The "hardest" negative index for each anchor-positive pair is determined by maximizing the difference between the anchor-negative and anchor-positive distances \cite{XuanImprovedMining}.
+The "hardest" negative index for each anchor-positive pair is determined by maximizing the difference between the anchor-negative and anchor-positive distances \cite{Sikaroudi2020OfflinePatches}\cite{XuanImprovedMining}.
 
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[clip,width=\columnwidth]{figures/images/Triplet Network.jpeg}
-    \caption[]{Caption}
-    \label{fig:my_label}
-\end{figure}
+%%%%%BATCH NORM%%%%%%%%%%
+
+In implementing batch normalization, it is necessary to standardize the audio lengths across all elements in the minibatch.
+We opted to zero-pad all clips to the length of the longest clip, valuing data integrity and completeness over potential performance trade-offs.
+Thus, the length of the longest array in the batch, which sets the standard for all others, is as follows:
+
+\begin{equation}
+L_{\text{max}} = \max_{\text{item} \in \text{batch}}(\max(\text{length}(A_{\text{item}}), \text{length}(P_{\text{item}}), \text{length}(N_{\text{item}})))
+\end{equation}
+\newpage

### 2023-05-29 evaluation/subsections/beyond dsp.tex
Updates from Overleaf

@@
 
-While the usefulness of deep audio embeddings can be evaluated in several scenarios, we have chosen a core MIR task for its popularity and complexity: Music Structure Analysis (MSA).
+While the usefulness of deep audio embeddings can be evaluated in countless downstream tasks, we have chosen Music Structure Analysis (MSA) for its popularity, complexity, and product-compelling nature.
 This interdisciplinary field aims to understand the structure of music \cite{Nieto2020Audio-BasedApplications}.
-However, due to subjectivity, ambiguity, and data scarcity, audio-based MSA faces challenges like boundary placement ambiguity and similarity quantification \cite{NietoPerceptualMusic}.
+Due to subjectivity, ambiguity, and data scarcity, audio-based MSA faces challenges like boundary placement ambiguity and similarity quantification \cite{NietoPerceptualMusic}.
 
@@
 
-SALAMI (Structural Analysis of Large Amounts of Music Information) \cite{Smith2011DESIGNANNOTATIONS} aims to conduct massive structural analyses of different types of music.
+SALAMI (Structural Analysis of Large Amounts of Music Information) aims to conduct massive structural analyses of different types of music \cite{Smith2011DESIGNANNOTATIONS}.
 The project covers diverse music, from Western pop to Indian classical and from live to studio recordings.
 
-\subsubsection{Formal analysis definition and approaches}
-Formal analysis, in this context, doesn't refer to classifying the piece into a formal type (e.g., sonata, song, or canon) or reducing it into its Ursatz as in Schenkerian analysis.
-Instead, it means organizing and dividing the piece into specific sections and understanding how they relate.
-
-The proposed method integrates aspects of three approaches: perceptual, functional, and transcription, enabling a comprehensive analysis of a wide range of music pieces using a limited vocabulary.
-
-It considers the hierarchical nature of music structure and employs markers to partially address the challenge of determining the appropriate timescale for analysis.
-
-The perceptual approach involves segmenting and labeling sections based on harmonic or rhythmic boundaries, although it may not accurately reflect the structural roles of similar-sounding sections.
-
-The functional approach categorizes the song into components like verses and choruses, potentially leading to varied labels for identical music or identical labels for different musical ideas based on their function.
-
-The transcription approach records musical parameters directly, such as chord patterns and instrumentation, providing a less subjective method, but it might not capture the complete structure of the piece.
+The authors propose a unique music analysis approach that segments pieces into sections rather than traditional forms.
+Their method combines perceptual, functional, and transcription analyses, considers music's hierarchical nature, and uses markers to determine analysis timescales.
+While providing a comprehensive investigation, each analysis approach has limitations in accurately reflecting musical structure, labeling identical or different music sections, and capturing the complete structural framework.
+This innovative approach aims for a more nuanced, holistic music analysis.
 
@@
 
-The Embeddiogram is derived by applying a pre-trained neural network model to windowed segments of an audio signal, generating a sequence of embedding vectors.
-These embedding vectors collectively form a high-dimensional description of the audio signal's structure and content.
+The \textit{embeddiogram} is derived by applying our pre-trained neural network model to sliding windowed segments across the audio signal, generating a sequence of embedding vectors.
+These relatively high-dimensional embedding vectors collectively form a two-dimensional description of the audio signal's musical content.
 
-Below is a detailed explanation of computing the Embeddiogram from a given audio signal.
+Below is a detailed explanation of how we compute the \textit{embeddiogram} from a given audio signal.
 This process comprises five key steps, including loading the audio data, slicing the audio data into windowed segments, processing each window using a pre-trained model to produce an embedding, collecting these embeddings, and finally normalizing the Embeddiogram.
@@
 \item \textbf{Collect the embeddings}: The embedding vectors are collected and stacked together.
-Each row represents a feature vector for a given time frame to form the \textit{Embeddiogram}, denoted as $\text{embeddiogram}$:
+Each row represents a feature vector for a given time frame to form the \textit{embeddiogram}, denoted as $\text{e}$:
 \begin{equation}
-\text{embeddiogram} = \begin{bmatrix} \text{embedding}_1 \\ \text{embedding}_2 \\ \vdots \\ \text{embedding}_H \end{bmatrix}
+\text{e} = \begin{bmatrix} \text{embedding}_1 \\ \text{embedding}_2 \\ \vdots \\ \text{embedding}_H \end{bmatrix}
 \end{equation}
 
-\item \textbf{Normalize the Embeddiogram}: The Embeddiogram is normalized to have a minimum value of 0 and a maximum value of 1. The normalization process is given by:
+\item \textbf{Normalize the \textit{embeddiogram}}: The \textit{embeddiogram} is normalized to have a minimum value of 0 and a maximum value of 1. The normalization process is given by:
 \begin{equation}
@@
 
-\begin{figure}
+\begin{figure}[ht]
   \centering
-    \includegraphics[width=\textwidth]{figures/images/embeddiogram SALAMI 3.png}
-    \caption[Embeddiogram]{Embeddiogram computed from...}
-    \label{fig:embeddiogram}
-\end{figure}
+  \begin{minipage}[b]{.8\linewidth}
+    \centering
+    \includegraphics[width=\linewidth]{figures/images/salami_391_embeddiogram.png}
+    \caption[]{Caption for image1}
+    \label{fig:image1}
+  \end{minipage}
 
-\begin{figure}
+  \begin{minipage}[b]{.8\linewidth}
     \centering
-    \includegraphics[width=\textwidth]{figures/images/noveltypeaks_SALAMI_track_2.png}
-    \caption[Novelty curve]{Caption}
-    \label{fig:embeddiogram}
+    \includegraphics[width=\linewidth]{figures/images/samali_391_novelty_curve_peaks.png}
+    \caption[]{Caption for image2}
+    \label{fig:image2}
+  \end{minipage}
 \end{figure}
@@
         \centering
-        \includegraphics[width=0.9\textwidth]{figures/images/recurrence plot SALAMI 3.png} % first figure itself
-        \caption{first figure}
+        \includegraphics[width=0.9\textwidth]{figures/images/salami_391_R matrix after Gaussian smoothing.png} % first figure itself
+        \caption[]{first figure}
     \end{minipage}\hfill
@@
         \centering
-        \includegraphics[width=0.9\textwidth]{figures/images/Rec_matrix_smooth_SALAMI_track_2.png} % second figure itself
-        \caption{second figure}
+        \includegraphics[width=0.9\textwidth]{figures/images/salami_391_Lag matrix after Gaussian smoothing.png} % second figure itself
+        \caption[]{second figure}
+    \end{minipage}
+    \vfill
+    \begin{minipage}{0.45\textwidth}
+        \centering
+        \includegraphics[width=0.9\textwidth]{figures/images/salami_391_Q_matrix.png} % third figure itself
+        \caption[]{third figure}
+    \end{minipage}\hfill
+    \begin{minipage}{0.45\textwidth}
+        \centering
+        \includegraphics[width=0.9\textwidth]{figures/images/salami_391_binary transitive matrix.png} % fourth figure itself
+        \caption[]{fourth figure}
     \end{minipage}

### 2023-05-29 future work/future work.tex
Updates from Overleaf

@@
 different takes
+k-fold cross validation
 
-Utilize the dB-scale Mel-spectrum magnitude of audio as input data; are a popular choice for input representation in music-related tasks when applying CNNs, as has been demonstrated in various studies.
+Utilize the dB-scale Mel-spectrum magnitude of audio as input data; it is a popular choice for input representation in music-related tasks when applying CNNs, as has been demonstrated in various studies \cite{Kim2020OneStrategies}.
 In addition to their wide usage, it's been recently reported that their frequency-domain summarization, grounded in psycho-acoustics, is efficient and challenging to replicate through solely data-driven methods.
 \cite{Kim2020OneStrategies}
+
+\newpage

### 2023-05-29 methods/subsections/implementation.tex
Updates from Overleaf

--- 2023-05-25 methods/subsections/model architecture and training strategy.tex
@@
-\subsection{Contrastive Learning of Musical Representations (CLMR)}
+\section{Implementation details}
+\subsection{Contrastive Learning of Musical Representations}
 
@@
 
-The CLMR methodology involves the following steps:
+The CLMR methodology involves creating different augmentations of the same musical piece as positive pairs and using others as antagonistic pairs.
+Then, training by minimizing a contrastive loss function encourages the model to produce similar representations for positive pairs and dissimilar representations for antagonistic pairs.
 
-\begin{enumerate}
-\item \textbf{Data Augmentation:} Create different augmentations or transformations of the same musical piece as positive pairs and use other randomly selected pieces as antagonistic pairs.
-\item \textbf{Contrastive Learning:} Train by minimizing a contrastive loss function, encouraging the model to produce similar representations for positive pairs and dissimilar representations for antagonistic pairs.
-\end{enumerate}
-
-\subsection{Siamese and Triplet Siamese Networks}
+\subsection{Triplet Siamese Networks}
 
@@
 
-The triplet loss function used in this network guides the learning process.
-It seeks to minimize the distance between the anchor and positive instances while maximizing the distance between the anchor and the negative instances.
-A margin parameter is included in the loss function to ensure a minimum separation between positive and negative instances in the embedding space.
-Due to the shared weights among the subnetworks, Triplet Siamese Networks also offer efficient memory usage and computational complexity.
-
 \subsubsection{Encoder: SampleCNN}
 
-The SampleCNN model \cite{Lee2018SampleCNN:Classification} takes 1D input data with a single channel.
-The first layer is a 1D convolutional layer with a kernel size of 3, a stride of 3, and 128 output channels.
-It is followed by batch normalization and ReLU activation.
+The SampleCNN model \cite{Lee2018SampleCNN:Classification} takes 1D input data with a single channel and follows the next architecture:
+
+\begin{table}[h]
+\centering
+\small
+\begin{tabularx}{\textwidth}{>{\hsize=1.6\hsize}X>{\hsize=0.6\hsize}X>{\hsize=0.6\hsize}X}
+\toprule
+\thead{\textbf{Layer Type}} & \thead{\textbf{In Channels}} & \thead{\textbf{Out Channels}} \\
+\midrule
+Conv + ReLU & 1 & 128 \\
+\addlinespace
+\multicolumn{3}{c}{The following layers are repeated depending on the strides and hidden parameters:} \\
+\addlinespace
+Conv + BatchNorm + ReLU + MaxPool & 128 & 128 \\
+\addlinespace
+Conv + BatchNorm + ReLU + MaxPool & 128 & 128 \\
+\addlinespace
+Conv + BatchNorm + ReLU + MaxPool & 128 & 256 \\
+\addlinespace
+Conv + BatchNorm + ReLU + MaxPool & 256 & 256 \\
+\addlinespace
+Conv + BatchNorm + ReLU + MaxPool & 256 & 256 \\
+\addlinespace
+Conv + BatchNorm + ReLU + MaxPool & 256 & 256 \\
+\addlinespace
+Conv + BatchNorm + ReLU + MaxPool & 256 & 256 \\
+\addlinespace
+Conv + BatchNorm + ReLU + MaxPool & 256 & 256 \\
+\addlinespace
+Conv + BatchNorm + ReLU + MaxPool & 256 & 512 \\
+\addlinespace
+Conv + BatchNorm + ReLU + AvgPool & 512 & 512 \\
+\addlinespace
+Fully connected (representation layer) & 512 & 128 \\
+\bottomrule
+\end{tabularx}
+\caption{Layer specifications for SampleCNN model}
+\label{tab:samplecnn}
+\end{table}
 
@@
 
+We believe our experiments can benefit from time-domain processing because it allows more natural handling of temporal patterns and sequences in the data while avoiding windowing artifacts.
+
+Mel-spectrogram-based approaches have proved useful in numerous audio-related machine-learning tasks using CNN, as their frequency-domain summarization is efficient and not easily learnable through data-driven approaches \cite{Kim2020OneStrategies}.
+That being said,  they exhibit limitations concerning their representation of perceptual similarity: the spectrogram of an audio signal, denoted as $\phi(x)$ for audio signal $x$ and $\phi(y)$ for audio signal $y$, captures the distribution of frequencies as they vary over time.
+A small difference between $\phi(x)$ and $\phi(y)$ generally signifies high perceptual similarity from a human listener's perspective.
+In other words, if two audio signals have similar spectrograms, they are likely to sound alike when heard.
+
+However, the inverse is not consistently true.
+There exist instances where two audio signals can have significantly different spectrograms, i.e., a high spectrogram distance between $\phi(x)$ and $\phi(y)$, but are still perceived as musically similar by human listeners.
+This discrepancy is due to the complexity of human auditory perception that goes beyond just the distribution of frequencies over time \cite{Mesostructures2023}.
+
+Our perception of sound involves several other factors, including temporal patterns, phase relationships between frequencies, and even higher-level musical structures.
+Therefore, even if two sounds have very different spectrograms, they might still be perceived as similar if they share these other characteristics.
+This underlines the inherent limitation of using only spectrogram distance to measure high-level music similarity, as it may not always produce results consistent with human perceptual judgments.
+
 \subsubsection{Positive sample generation chain}
 
-The positive image in our study should preserve its intelligible content when subjected to temporal transformations, regardless of alterations in sonic qualities.
+The positive image in our study must preserve its intelligible content when subjected to temporal (or any) transformations, regardless of alterations in sonic qualities.
 Maintaining the temporal structure and meaningfulness of the content allows it to present musical elements identical or strikingly similar to the original track.
 
-While the MIR community has access to helpful audio transformation tools \cite{Spijkervet2021Spijkervet/torchaudio-augmentations:V1.0}, the specific requirements of our experiments necessitated the development of our transformation chain: given an anchor audio signal $A[n]$, we generate a positive signal $P[n]$ by applying a series of amplitude, time-domain, frequency-domain, modulation, reverberation, and nonlinear effects with additive noise on top of it.
+While we have experimented with helpful audio augmentation tools such as \cite{Spijkervet2021Spijkervet/torchaudio-augmentations:V1.0} and \cite{Kharitonov2020DataDomain}, the specific requirements of our experiments necessitated the development of our transformation chain using \textit{torchaudio} \cite{Yang2021TorchAudio:Processing}: given an anchor audio signal $A[n]$, we generate a positive signal $P[n]$ by applying a series of amplitude, time-domain, frequency-domain, modulation, reverberation, and nonlinear effects with additive noise on top of it.
 
@@
 
+The triplet loss function used in Siamese networks guides the learning process.
+It seeks to minimize the distance between the anchor and positive instances while maximizing the distance between the anchor and the negative instances.
+A margin parameter is included in the loss function to ensure a minimum separation between positive and negative instances in the embedding space.
+
+The triplet loss function $\mathcal{L}(\mathbf{a}, \mathbf{p}, \mathbf{n})$ aims to ensure that an anchor vector $\mathbf{a}_i$ is closer in the embedding space to a positive vector $\mathbf{p}_i$ (representing an example of the same class) than to a negative vector $\mathbf{n}_i$ (representing an example of a different class) by at least a margin $m$.
+It is calculated by summing the losses overall $N$ triplets in the dataset, where the equation gives the loss for each triplet:
+
 \begin{equation}
@@
 
-In this equation, the triplet loss function with a variable margin:
-
-$\mathcal{L}$ is the triplet loss function.
-$\mathbf{a}_i$, $\mathbf{p}_i$, and $\mathbf{n}_i$ are the anchor, positive, and negative embedding vectors, respectively, for the $i$-th sample.
-$\left| \cdot \right|_2^2$ denotes the squared Euclidean distance between two points.
-$m$ is the margin, a hyperparameter that helps ensure that the anchor-positive distance is smaller than the anchor-negative distance by at least a margin.
-The summation $\sum_{i=1}^{N}$ is over all $N$ triplets in the dataset.
-The goal of the triplet loss is to minimize the distance between the anchor and the positive sample while maximizing the distance between the anchor and the negative sample.
-This encourages the model to learn embeddings that are similar for the same class and dissimilar for different classes.
-
-The final form of the loss function is obtained by averaging the loss over a mini-batch of triplets.
+The final loss used for model training is then the average loss over a mini-batch of $N$ triplets:
 
 \begin{equation}
-\mathcal{L} = \frac{1}{N} \sum_{i=1}^{N} L(anchor_i, positive_i, negative_i)
+\mathcal{L} = \frac{1}{N} \sum_{i=1}^{N} \mathcal{L}(\mathbf{a}_i, \mathbf{p}_i, \mathbf{n}_i)
 \end{equation}
 
-Here, $N$ is the number of triplets in the mini-batch, and $L(anchor_i, positive_i, negative_i)$ represents the loss function computed for the i-th triplet in the batch.
+The goal of minimizing this loss function is to learn discriminative embeddings, where similar examples are grouped closely together and dissimilar examples are placed farther apart in the embedding space.
 
-\subsubsection{Triplet mining}
+\subsection{Online triplet mining and batch normalization}
 
-The anchor-positive and anchor-negative distances are computed as the Euclidean distances between the corresponding samples.
+Online triplet mining is beneficial for managing large datasets by dynamically selecting the most informative triplets during training, focusing on each mini-batch.
+This strategy makes the process memory-efficient by negating the need to store all possible triplet combinations.
+Still, it also enhances model performance through quicker convergence by focusing on challenging examples based on the current model state.
+
+This hard triplet mining selects triplets $(a, p, n)$ to maximize the Euclidean distance between the anchor and positive samples and the anchor and negative samples.
+These distances, $D_{\text{AP}}$ and $D_{\text{AN}}$, are computed respectively as:
+
+\begin{align}
+D_{\text{AP}} &= \sqrt{\sum_{i} (A_i - P_i)^2} & D_{\text{AN}} &= \sqrt{\sum_{i} (A_i - N_i)^2}
+\end{align}
+
+\subsubsection{Batch normalization}
+
+In implementing the batch normalization step, it is necessary to standardize the audio lengths across all elements in the minibatch.
+We opted to zero-pad all clips to the length of the longest clip, valuing data integrity and completeness over potential performance trade-offs.
+Thus, the length of the longest array in the batch, which sets the standard for all others, is as follows:
 
 \begin{equation}
-D_{\text{AP}} = \sqrt{\sum_{i} (A_i - P_i)^2}
+L_{\text{max}} = \max_{i \in I} \left( \max \left( |A_i|, |P_i|, |N_i| \right) \right)
 \end{equation}
 
-The "hardest" negative index for each anchor-positive pair is determined by maximizing the difference between the anchor-negative and anchor-positive distances \cite{XuanImprovedMining}.
+\begin{itemize}
+    \item $I$ represents the set of all items in the batch.
+    \item $|A_i|$, $|P_i|$, and $|N_i|$ denote the lengths of the anchor, positive, and negative embedding vectors for the $i$-th item, respectively.
+    \item The $\max$ function is applied to find the longest of these three lengths for each item, and then the maximum of these maximum lengths is taken over all items in the batch.
+This gives the maximum length, $L_{\text{max}}$, of any vector in the batch.
+    \end{itemize}
 
-\begin{equation}
-D_{\text{AN}} = \sqrt{\sum_{i} (A_i - N_i)^2}
-\end{equation}
-
-\begin{figure}
-    \centering
-    \includegraphics[clip,width=\columnwidth]{figures/images/Triplet Network.jpeg}
-    \caption[]{Caption}
-    \label{fig:my_label}
-\end{figure}
+\newpage

### 2023-05-29 results/results.tex
Updates from Overleaf

@@
 XXXXXXXXXXXXXXXXX
+
+Extend table by \cite{Hernandez-Olivan2021MusicFeatures}
+
+\begin{table}[h]
+\centering
+\footnotesize
+\begin{tabularx}{\textwidth}{|X|X|X|X|X|X|X|X|}
+\hline
+Year & Authors & Ref. & Algorithm & Input & Method & Supervised? & F-measure SALAMI \\
+\hline
+2009 & Paulus \& Klapuri & [24] & PK & MFCCs, chromas & Fitness function & No & - \\
+2010 & Mauch et al. & [25] & MND1 & MFCCs, Discrete Cepstrum & HMM & No & - \\
+2011 & Sargent et al. & [26] & SB-VRS1 & Chords estimation & Viterbi & No & - \\
+2012 & Kaiser et al. & [27] & KSP2 & SSM & Novelty measure & No & 0.286 \\
+2013 & McFee \& Ellis & [20] & MP2 & MLS & Fisher’s Linear Discriminant & No & 0.317 \\
+2014 & Nieto \& Bello & [28] & NB1 & MFCCs + chromas & Checkerboard-like kernel & No & 0.299 \\
+2015 & Cannam et al. & [29] & CC1 & Timbre-type histograms & HMM & No & 0.213 \\
+2016 & Nieto & [30] & ON2 & Constant-Q Transform Spectrogram & Linear Discriminant Analysis & No & 0.299 \\
+2017 & Cannam et al. & [29] & CC1 & Timbre-type histograms & HMM & No & 0.212 \\
+2014 & Schlüter et al. & [31] & SUG1 & MLS & CNN & Yes & 0.529 \\
+2015 & Grill \& Schlüter & [32] & GS1 & MLS + SSLMs & CNN & Yes & 0.541 \\
+2007 & Turnbull et al. & [19] & - & MFCCs, chromas, spectrogram & Boosted Decision Stump & No & 0.378 \\
+2011 & Sargent et al. & [34] & - & MFCCs, chromas & Viterbi & No & 0.356 \\
+2014 & Ullrich et. al & [22] & - & MLS & CNN & No & 0.465 \\
+2015 & Grill \& Schlüter & [4] & - & MLS + SSLMs & CNN & No & 0.523 \\
+2015 & Grill \& Schlüter & [5] & - & MLS + PCPs + SSLMs & CNN & No & 0.508 \\
+2017 & Hadria \& Peeters & [35] & - & MLS + SSLMs & CNN & No & 0.291 \\
+\hline
+\end{tabularx}
+\caption{Your Caption}
+\label{tab:my_label}
+\end{table}
 

### 2023-05-30 discussion/discussion.tex
Updates from Overleaf

@@
 content in the temporal domain by leveraging self-supervised deep neural networks, inductive bias, and aural skills to learn music latent representations with applications to MIR downstream tasks.
-Building on top of existing approaches and architectures and wrapped within MSAF \cite{NietoMSAF:FRAMEWORK}, we replaced traditional features with deep embeddings trained to represent high-level musical content information.
+Building on existing approaches and architectures, we replaced traditional features with deep embeddings trained to represent high-level musical content information.
 

### 2023-05-30 evaluation/evaluation.tex
Updates from Overleaf

@@
 
-\input{evaluation/subsections/beyond dsp}
+\section{Music Structure Analysis as downstream task}
+
+While the usefulness of deep audio embeddings can be evaluated in countless downstream tasks, we have chosen Music Structure Analysis (MSA) for its popularity, complexity, and product-compelling nature.
+This interdisciplinary field aims to understand the structure of music \cite{Nieto2020Audio-BasedApplications}.
+Due to subjectivity, ambiguity, and data scarcity, audio-based MSA faces challenges like boundary placement ambiguity and similarity quantification \cite{NietoPerceptualMusic}.
+
+All the evaluation experiments have been wrapped around MSAF \cite{NietoMSAF:FRAMEWORK}, a popular framework for Music Structure Analysis.
+
+All the evaluation metrics have been computed using the mir-eval package \cite{RaffelMir_eval:METRICS}.
+
+\subsection{SALAMI dataset}
+
+SALAMI (Structural Analysis of Large Amounts of Music Information) aims to conduct massive structural analyses of different types of music \cite{Smith2011DESIGNANNOTATIONS}.
+The project covers diverse music, from Western pop to Indian classical and from live to studio recordings.
+
+The authors propose a unique music analysis approach that segments pieces into sections rather than traditional forms.
+Their method combines perceptual, functional, and transcription analyses, considers music's hierarchical nature, and uses markers to determine analysis timescales.
+While providing a comprehensive investigation, each analysis approach has limitations in accurately reflecting musical structure, labeling identical or different music sections, and capturing the complete structural framework.
+This innovative approach aims for a more nuanced, holistic music analysis.
+
+\section{\textit{Embeddiogram} feature}
+
+The \textit{embeddiogram} is derived by applying our pre-trained neural network model to sliding windowed segments across the audio signal, generating a sequence of embedding vectors.
+These relatively high-dimensional embedding vectors collectively form a two-dimensional description of the audio signal's musical content.
+
+Below is a detailed explanation of how we compute the \textit{embeddiogram} from a given audio signal.
+This process comprises five key steps, including loading the audio data, slicing the audio data into windowed segments, processing each window using a pre-trained model to produce an embedding, collecting these embeddings, and finally normalizing the Embeddiogram.
+
+\begin{enumerate}
+\item \textbf{Load the audio data}: The audio data is loaded into memory as a one-dimensional array of length $N$.
+
+\item \textbf{Slice the audio data}: The audio data is segmented into overlapping windows.
+Each window contains $w$ samples, and consecutive windows are separated by $h$.
+This gives a total of $H$ windows, defined as:
+\begin{equation}
+H = 1 + \left\lfloor \frac{N - w}{h} \right\rfloor
+\end{equation}
+In the case where $\left( N - w \right) \mod h > 0$, we have $H += 1$ to account for the final, potentially smaller, window.
+
+\item \textbf{Process each window}: Each window of audio data is processed independently, passed through the pre-trained neural network model and transformed into an embedding vector.
+Formally, for each window $w_i$ of audio data, we have:
+\begin{equation}
+\text{embedding}_i = \text{model}(w_i)
+\end{equation}
+
+\item \textbf{Collect the embeddings}: The embedding vectors are collected and stacked together.
+Each row represents a feature vector for a given time frame to form the \textit{embeddiogram}, denoted as $\text{e}$:
+\begin{equation}
+\text{e} = \begin{bmatrix} \text{embedding}_1 \\ \text{embedding}_2 \\ \vdots \\ \text{embedding}_H \end{bmatrix}
+\end{equation}
+
+\item \textbf{Normalize the \textit{embeddiogram}}: The \textit{embeddiogram} is normalized to have a minimum value of 0 and a maximum value of 1. The normalization process is given by:
+\begin{equation}
+E'_{ij} = \frac{e_{ij} - \min(E)}{\max(E) - \min(E)}
+\end{equation}
+\end{enumerate}
+
+\begin{figure}[ht]
+  \centering
+  \begin{minipage}[b]{.8\linewidth}
+    \centering
+    \includegraphics[width=\linewidth]{figures/images/salami_391_embeddiogram.png}
+    \caption[]{Caption for image1}
+    \label{fig:image1}
+  \end{minipage}
+
+  \begin{minipage}[b]{.8\linewidth}
+    \centering
+    \includegraphics[width=\linewidth]{figures/images/samali_391_novelty_curve_peaks.png}
+    \caption[]{Caption for image2}
+    \label{fig:image2}
+  \end{minipage}
+\end{figure}
+
+\begin{figure}[ht]
+    \centering
+    \begin{minipage}{0.45\textwidth}
+        \centering
+        \includegraphics[width=0.9\textwidth]{figures/images/salami_391_R matrix after Gaussian smoothing.png} % first figure itself
+        \caption[]{first figure}
+    \end{minipage}\hfill
+    \begin{minipage}{0.45\textwidth}
+        \centering
+        \includegraphics[width=0.9\textwidth]{figures/images/salami_391_Lag matrix after Gaussian smoothing.png} % second figure itself
+        \caption[]{second figure}
+    \end{minipage}
+    \vfill
+    \begin{minipage}{0.45\textwidth}
+        \centering
+        \includegraphics[width=0.9\textwidth]{figures/images/salami_391_Q_matrix.png} % third figure itself
+        \caption[]{third figure}
+    \end{minipage}\hfill
+    \begin{minipage}{0.45\textwidth}
+        \centering
+        \includegraphics[width=0.9\textwidth]{figures/images/salami_391_binary transitive matrix.png} % fourth figure itself
+        \caption[]{fourth figure}
+    \end{minipage}
+\end{figure}
 

### 2023-05-30 introduction/Subsections/Assumptions.tex
Updates from Overleaf

@@
 
-This thesis posits the existence of high-level musical concepts invariant to sonic qualities that evolve and unfolds through time, such as melody, harmony, rhythm, form, motif, counterpoint, etc.
+This thesis proposes the existence of high-level musical concepts such as melody, harmony, rhythm, form, motif, and counterpoint.
+These concepts are invariant to sonic qualities, demonstrating their independence and endurance over time.
+Furthermore, we argue these elements interact and evolve with each other.
 This idea parallels the nature of the symbolic domain (sheet music), which maintains its essence despite being interpreted through diverse performances using various instruments and styles.
@@
 This concept finds grounding in the theories of Kurt Koffka, a founder of the Gestalt school of psychology, who proposed a holistic approach to understanding complex forms, contrary to the structuralist practice of reducing mental processes into essential elements \cite{Koffka2013PrinciplesPsychology}.
-When applied to music, the principles of Gestalt psychology offer insights into how we perceive, organize, and interpret musical patterns.
-They suggest that our minds perceive auditory input much like visual input, seeking patterns and structures.
+When applied to music, the principles of Gestalt psychology suggest that our minds perceive auditory input much like visual input, seeking patterns and structures.
 This understanding significantly contributes to the comprehension of cognitive processes in musical perception and organization, influencing music theory, cognition, and therapy \cite{Lerdahl1985AMusic}.

### 2023-05-30 methods/subsections/implementation.tex
Updates from Overleaf

@@
 
+%Colour CNN
+\input{figures/neural networks/colour CNN}
+
 \subsubsection{Optimizer}
@@
 
-While we have experimented with helpful audio augmentation tools such as \cite{Spijkervet2021Spijkervet/torchaudio-augmentations:V1.0} and \cite{Kharitonov2020DataDomain}, the specific requirements of our experiments necessitated the development of our transformation chain using \textit{torchaudio} \cite{Yang2021TorchAudio:Processing}: given an anchor audio signal $A[n]$, we generate a positive signal $P[n]$ by applying a series of amplitude, time-domain, frequency-domain, modulation, reverberation, and nonlinear effects with additive noise on top of it.
+While we have experimented with helpful audio augmentation tools such as \cite{Spijkervet2021Spijkervet/torchaudio-augmentations:V1.0} and \cite{Kharitonov2020DataDomain}, the specific requirements of our experiments necessitated the development of our transformation chain using \textit{torchaudio's} \cite{Yang2021TorchAudio:Processing} implementation of \textit{SoX} \cite{sox}: given an anchor audio signal $A[n]$, we generate a positive signal $P[n]$ by applying a series of amplitude, time-domain, frequency-domain, modulation, reverberation, and nonlinear effects with additive noise on top of it.
 

### 2023-05-30 results/results.tex
Updates from Overleaf

--- 2023-05-16 results/results.tex
@@
 XXXXXXXXXXXXXXXXX
-
-\input{figures/neural networks/manifold}
 
@@
 
-\begin{figure}[!ht]
-\includegraphics[clip,width=\columnwidth]{figures/PlotTimeSeriesResult}% 
-\caption[Graph.]{This is an example of a figure and its caption.}
-\label{fig:timeseries}
-\end{figure}
+Extend table by Hernandez-Olivan, C., Beltran, J. R. \& Diaz-Guerra, D. 
+\cite{Hernandez-Olivan2021MusicFeatures}
+
+\begin{table}[h]
+\centering
+\small
+\begin{tabularx}{\textwidth}{>{\raggedright\arraybackslash}p{5cm}XXXXX}
+\toprule
+\thead{\textbf{Year, Authors, Ref}} & \thead{\textbf{Algorithm}} & \thead{\textbf{Input}} & \thead{\textbf{Method}} & \thead{\textbf{F-measure SALAMI}} \\
+\midrule
+\addlinespace
+2009, Paulus \& Klapuri, [24] & PK & MFCCs, chromas & Fitness function  & - \\
+\addlinespace
+2010, Mauch et al., [25] & MND1 & MFCCs, Discrete Cepstrum & HMM  & - \\
+\addlinespace
+2011, Sargent et al., [26]& SB-VRS1 & Chords estimation & Viterbi  & - \\
+\addlinespace
+2012, Kaiser et al., [27]& KSP2 & SSM & Novelty measure  & 0.286 \\
+\addlinespace
+2013, McFee \& Ellis, [20] & MP2 & MLS & Fisher’s Linear Discriminant  & 0.317 \\
+\addlinespace
+2014, Nieto \& Bello, [28] & NB1 & MFCCs + chromas & Checkerboard-like kernel  & 0.299 \\
+\addlinespace
+2015, Cannam et al., [29] & CC1 & Timbre-type histograms & HMM  & 0.213 \\
+\addlinespace
+2016, Nieto, [30] & ON2 & Constant-Q Transform Spectrogram & Linear Discriminant Analysis  & 0.299 \\
+\addlinespace
+2017, Cannam et al., [29] & CC1 & Timbre-type histograms & HMM  & 0.212 \\
+\addlinespace
+2007, Turnbull et al., [19] & - & MFCCs, chromas, spectrogram & Boosted Decision Stump  & 0.378 \\
+\addlinespace
+2011, Sargent et al., [34] & - & MFCCs, chromas & Viterbi  & 0.356 \\
+\addlinespace
+2014, Ullrich et. al, [22] & - & MLS & CNN  & 0.465 \\
+\addlinespace
+2015, Grill \& Schlüter, [4] & - & MLS + SSLMs & CNN  & 0.523 \\
+\addlinespace
+2015, Grill \& Schlüter, [5] & - & MLS + PCPs + SSLMs & CNN  & 0.508 \\
+\addlinespace
+2017, Hadria \& Peeters, [35] & - & MLS + SSLMs & CNN  & 0.291 \\
+\bottomrule
+\end{tabularx}
+\caption{Your Caption}
+\label{tab:my_label}
+\end{table}
 

### 2023-05-31 evaluation/evaluation.tex
Updates from Overleaf

@@
         \includegraphics[width=0.9\textwidth]{figures/images/salami_391_R matrix after Gaussian smoothing.png} % first figure itself
-        \caption[]{first figure}
+        \caption[self-similarity matrix]{Self-similarity matrix visualizes the similarity of different parts of the audio feature to each other.
+It illustrates how each point in the feature space correlates with every other point, providing insights into structural patterns or repetitions in the audio.}
     \end{minipage}\hfill
@@
         \includegraphics[width=0.9\textwidth]{figures/images/salami_391_Lag matrix after Gaussian smoothing.png} % second figure itself
-        \caption[]{second figure}
+        \caption[Self-similarity lag matrix]{A self-similarity lag matrix represents how similar each point in the feature space is with its 'lagged' or time-shifted versions.
+This provides insights into periodicity and temporal patterns within the audio data.}
     \end{minipage}
@@
         \includegraphics[width=0.9\textwidth]{figures/images/salami_391_Q_matrix.png} % third figure itself
-        \caption[]{third figure}
+        \caption[Q-matrix]{The cumulative matrix uses a recursive process that maximizes previous values and adds the current value from the recurrence plot.
+The Q-matrix acts as a global similarity measure by considering all aligned sample matches throughout the time series without penalizing local disruptions or mismatches.}
     \end{minipage}\hfill
@@
         \includegraphics[width=0.9\textwidth]{figures/images/salami_391_binary transitive matrix.png} % fourth figure itself
-        \caption[]{fourth figure}
+        \caption[Transitive Binary Similarity Matrix]{Transitive Binary Similarity Matrix identifies similarity relationships between different segments or points in the feature.
+This matrix aids in discovering recurrent patterns or structures within the audio feature.}
     \end{minipage}

### 2023-05-31 results/results.tex
Updates from Overleaf

--- 2023-05-16 results/results.tex
@@
 
-XXXXXXXXXXXXXXXXX
+\input{results/subsections/tables}
 
-\input{figures/neural networks/manifold}
-
-\section{Tables and graphics}
-
-XXXXXXXXXXXXXXXXX
-
-\begin{figure}[!ht]
-\includegraphics[clip,width=\columnwidth]{figures/PlotTimeSeriesResult}% 
-\caption[Graph.]{This is an example of a figure and its caption.}
-\label{fig:timeseries}
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/images/first results.png}
+    \caption{Caption}
+    \label{fig:boxplotmetrics}
 \end{figure}
 
-\begin{table}[!ht]
-\renewcommand{\arraystretch}{1.50}
-\caption[Table]{This is an example of a table and its caption.}
-\label{tablePCA}
+\begin{figure}
     \centering
-\begin{tabular}{| c | c | c | c | c |}
-\hline
-\bfseries PCA & \bfseries Residual mean & \bfseries XXX & \bfseries XXX & \bfseries XXX \\
-\hline\hline
-Original PCA & 0.1267 & XXX & XXX & XXX  \\
-\hline
-PCA on Centroid 1 & 0.1249 & XXX & XXX  & XXX\\
-\hline
-PCA on Centroid 2 & 0.1214  & XXX & XXX  & XXX\\
-\hline
-\end{tabular}
-\end{table}
+    \includegraphics[width=\textwidth]{figures/images/f-measure.png}
+    \caption{Caption}
+    \label{fig:boxplotfmeasure}
+\end{figure}
+
+The F-measure is a widely used boundary detection metric computed by comparing the predicted and ground truth boundaries.
+This metric, ranging from 0 to 1, represents the harmonic mean of precision and recall, providing a balanced view of under-segmentation and over-segmentation.
+Precision calculates the percentage of correctly detected boundaries, whereas recall assesses the percentage of actual boundaries detected correctly.
+Given the potential inaccuracies in human annotations and prediction errors, the F-measure tolerates minor discrepancies between predicted and ground truth boundaries.
+This tolerance level can be adjusted, enabling the metric to consider a predicted boundary as correct if it's within the set tolerance window of a ground truth boundary \cite{Turnbull2007ABOOSTING}.
 

### 2023-05-31 results/subsections/tables.tex
Updates from Overleaf

Extend table by Hernandez-Olivan, C., Beltran, J. R. \& Diaz-Guerra, D. 
\cite{Hernandez-Olivan2021MusicFeatures}

\begin{table}[h]
\centering
\small
\begin{tabularx}{\textwidth}{>{\raggedright\arraybackslash}p{5cm}XXXXX}
\toprule
\thead{\textbf{Year, Authors, Ref}} & \thead{\textbf{Algorithm}} & \thead{\textbf{Input}} & \thead{\textbf{Method}} & \thead{\textbf{F-measure}} \\
\midrule
\addlinespace
2012, Kaiser et al., [27]& KSP2 & SSM & Novelty measure  & 0.286 \\
\addlinespace
2013, McFee \& Ellis, [20] & MP2 & MLS & Fisher’s Linear Discriminant  & 0.317 \\
\addlinespace
2014, Nieto \& Bello, [28] & NB1 & MFCCs + chromas & Checkerboard-like kernel  & 0.299 \\
\addlinespace
2015, Cannam et al., [29] & CC1 & Timbre-type histograms & HMM  & 0.213 \\
\addlinespace
2016, Nieto, [30] & ON2 & Constant-Q Transform Spectrogram & Linear Discriminant Analysis  & 0.299 \\
\addlinespace
2017, Cannam et al., [29] & CC1 & Timbre-type histograms & HMM  & 0.212 \\
\addlinespace
2007, Turnbull et al., [19] & - & MFCCs, chromas, spectrogram & Boosted Decision Stump  & 0.378 \\
\addlinespace
2011, Sargent et al., [34] & - & MFCCs, chromas & Viterbi  & 0.356 \\
\addlinespace
2014, Ullrich et. al, [22] & - & MLS & CNN  & 0.465 \\
\addlinespace
2015, Grill \& Schlüter, [4] & - & MLS + SSLMs & CNN  & 0.523 \\
\addlinespace
2015, Grill \& Schlüter, [5] & - & MLS + PCPs + SSLMs & CNN  & 0.508 \\
\addlinespace
2017, Hadria \& Peeters, [35] & - & MLS + SSLMs & CNN  & 0.291 \\
\bottomrule
\end{tabularx}
\caption{Your Caption}
\label{tab:my_label}
\end{table}

### 2023-05-31 MasterThesis.tex
Updates from Overleaf

@@
 \usepackage{float}
+\usepackage{booktabs}
+\usepackage{makecell}
 
@@
 \usepackage{sidecap}
+\usepackage{tabularx}
 
@@
 \title{%
-  Uncovering underlying high-level musical content in the temporal domain \\
-  \small Leveraging self-supervised deep neural networks, inductive bias, and aural skills to learn music embeddings with applications to MIR downstream tasks}
+  Uncovering underlying high-level musical content in the time domain \\
+  \small Leveraging self-supervised deep neural networks, inductive bias, and aural skills to learn deep audio embeddings with applications to MIR downstream tasks}
 
@@
 \input{appendix/appendix}
+\newpage
 

### 2023-05-31 abstract/abstract.tex
Updates from Overleaf

--- 2023-05-15 abstract/abstract.tex
@@
 
-This thesis posits the existence of high-level musical concepts invariant to sonic qualities that evolve and unfolds through time.
-This idea parallels the nature of the symbolic domain, which maintains its essence despite being interpreted through diverse performances using various instruments and styles.
+This thesis posits the existence of invariant high-level musical concepts that persist through changes in sonic qualities, akin to the symbolic domain where essence endures despite varying interpretations through different performances, instruments, and styles, among many other variables.
 
-This research, conducted in collaboration with Epidemic Sound AB and the Music Technology Group (MTG) at Universitat Pompeu Fabra (UPF), employs self-supervised contrastive learning of musical representation to uncover the fundamental structure of Western tonal music.
+In collaboration with Epidemic Sound AB and the Music Technology Group (MTG) at Universitat Pompeu Fabra (UPF), we used self-supervised contrastive learning to uncover the underlying structure of Western tonal music.
+We applied deep convolutional neural networks and a triplet loss function, identifying abstract and semantic musical elements without relying on their sonic qualities.
+This way, we replaced traditional acoustic features with deep audio embeddings, paving the way for high-level, sound-agnostic, and content-sensitive music identification.
 
-Embracing a subtle novel approach, this process is facilitated by applying Siamese networks with a triplet loss, mimicking human aural skills in interpreting music to discern abstract and semantic musical elements, irrespective of the sonic qualities.
-The study replaces traditional acoustical features with deep audio embeddings to compute high-level, sound-agnostic, and content-sensitive music identification.
-
-Results XXXXXX TBC
-
-The preliminary results suggest that our approach to learning music-informed embeddings holds significant potential for nearly all MIR downstream tasks.
-Music-motivated embeddings represent a promising technique, adaptable potentially to other tasks hindered by data scarcity.
-This method could significantly influence advancements in intelligent music recommendation systems and the efficient enforcement of intellectual property rights.
+Our cognitively-based approach for learning embeddings focuses on using full resolution data and preserving high-level musical information.
+Drawing upon our domain expertise, we developed robust transformations to encode heuristic musical concepts that should remain constant.
+This novel approach aims to reconcile music and machine learning, enhancing machine listening models' efficacy.
+Preliminary results suggest that our musically-informed technique has significant potential for boundary detection tasks and possibly nearly all MIR downstream tasks that are not purely sonic-based.
+Consequently, music-motivated embeddings appear promising and potentially adaptable to other tasks constrained by data scarcity.
 

### 2023-05-31 figures/neural networks/manifold.tex
Updates from Overleaf

--- 2023-05-09 figures/neural networks/manifold.tex
@@
 
-    \caption[High-level diagram of dimensionality reduction and latent space representation.]{Dimensionality reduction and latent space representation: Mapping between the original high-dimensional space ${\cal X}$ and the lower-dimensional latent space ${\cal F}$ using functions $f$ and $g$.}
-    \label{fig:my_label}
+    \caption[High-level diagram of dimensionality reduction and latent space representation \cite{tikz}.]{\small{Dimensionality reduction and latent space representation: Mapping between the original high-dimensional space ${\cal X}$ and the lower-dimensional latent space ${\cal F}$ using functions $f$ and $g$.}}
+    \label{fig:manifold}
 \end{figure}

### 2023-05-31 introduction/Subsections/Assumptions.tex
Updates from Overleaf

--- 2023-05-16 introduction/Subsections/Assumptions.tex
@@
 
-This thesis posits the existence of high-level musical concepts invariant to sonic qualities that evolve and unfolds through time, such as melody, harmony, rhythm, form, motif, counterpoint, etc.
-This idea parallels the nature of the symbolic domain (sheet music), which maintains its essence despite being interpreted through diverse performances using various instruments and styles.
-While a single waveform might have a limited number of sheet music representations that adequately capture its musical components, a single piece can be interpreted in infinite ways through different instruments, voices, tempos, and interpretations.
+This thesis proposes the existence of high-level musical concepts, including melody, harmony, rhythm, form, motif, and counterpoint.
+These concepts, despite changes in sonic qualities, demonstrate enduring independence.
+Additionally, these elements are interactive, continually evolving within the musical context.
+This echoes the nature of the symbolic domain, such as sheet music, which retains its essence despite varied interpretations across diverse performances, instruments, and styles.
+While a single waveform might correspond to a finite set of sheet music representations encapsulating its musical components, one piece of music can be interpreted infinitely, varying by instruments, voices, tempos, and performance styles.
 
-Abstract high-level features can be discerned regardless of waveform or production style.
-This approach provides an objective, comprehensive insight into a composition's musical content, much like analyzing sheet music uncovers its behavioral foundation.
+Abstract high-level features can be discerned irrespective of the waveform or production style, providing an objective, comprehensive insight into the musical content of a composition.
+This approach is akin to analyzing sheet music to uncover its foundational behaviors.
 
-For example, despite the differences in cultural contexts, stylistic elements, time signatures, key signatures, and sonic properties, we propose that figures \ref{fig:mahler} and \ref{fig:giant_steps} share a similarity.
-Both pieces carry the same musicological fingerprint, so to say, derived from the envelope of their melodic and harmonic contours through non-diatonic major thirds.
+These features enable listeners to identify and recreate musical structures by ear, fostering deeper engagement with music.
+Heuristics, mental shortcuts, or rules of thumb facilitate rapid comprehension of complex musical concepts, bringing underlying patterns and structures into focus.
 
-This concept finds grounding in the theories of Kurt Koffka, a founder of the Gestalt school of psychology, who proposed a holistic approach to understanding complex forms, contrary to the structuralist practice of reducing mental processes into essential elements \cite{Koffka2013PrinciplesPsychology}.
-When applied to music, the principles of Gestalt psychology offer insights into how we perceive, organize, and interpret musical patterns.
-They suggest that our minds perceive auditory input much like visual input, seeking patterns and structures.
-This understanding significantly contributes to the comprehension of cognitive processes in musical perception and organization, influencing music theory, cognition, and therapy \cite{Lerdahl1985AMusic}.
+For example, despite differences in cultural contexts, stylistic elements, time signatures, key signatures, and sonic properties, we propose a similarity between figures \ref{fig:mahler} and \ref{fig:giant_steps}.
+Both pieces exhibit the same musicological fingerprint, so to speak, derived from the envelope of their melodic and harmonic contours through non-diatonic major thirds.
+
+This concept aligns with the theories of Kurt Koffka, a founding member of the Gestalt school of psychology, who advocated for a holistic approach to understanding complex forms, as opposed to the structuralist practice of dissecting mental processes into their elemental components \cite{Koffka2013PrinciplesPsychology}.
+In the context of music, Gestalt psychology principles suggest our minds process auditory input similarly to visual input, by seeking patterns and structures.
+This understanding significantly enhances the comprehension of cognitive processes in musical perception and organization, influencing music theory, cognition, and therapy \cite{Lerdahl1985AMusic}.
 
@@
 \end{figure}
-
-\begin{figure}
-    \centering
-    \scalebox{0.9}{
-    \includegraphics[width=\textwidth]{figures/images/train interlude score.png}
-        }
-    \caption[Last Train Home]{\small{Pat Metheny's Last Train Home interlude.}}
-    \label{fig:last_train}
-\end{figure}

### 2023-05-31 introduction/Subsections/Introduction.tex
Updates from Overleaf

@@
 
-Music \footnote{In this thesis, "music" refers to the Western tradition, characterized by conventions, practices, and aesthetics that have developed primarily in Europe and North America.
-This usage is not intended to deny the diversity and richness of other musical traditions worldwide but instead reflects the present study's focus on a specific cultural context.}, an essential component of human culture, history, and society; it has existed since ancient times.
-It reflects the changes in our cultures, traditions, and beliefs as it evolves.
+Music is essential to human culture, history, and society; it has existed since ancient times.
+It reflects the changes in our cultures, traditions, and beliefs as they evolve \footnote{In this thesis, "music" refers to the Western tradition, characterized by conventions, practices, and aesthetics that have developed primarily in Europe and North America.
+This usage does not deny the diversity and richness of other musical traditions worldwide but reflects the present study's focus on a specific cultural context.}.
 Studying music, therefore, has always been a challenging and complex task due to its subjective nature, relative and mutable ground truth, and the sheer variety of musical styles, genres, and worldwide cultures.
@@
 Music has captivated and intrigued us from the ancient Greeks to the present day.
-This rich music theory and analysis history form a valuable foundation for guiding and evaluating Music Information Retrieval (MIR) algorithms and models.
+This rich music theory and analysis history form a valuable foundation for guiding and evaluating MIR algorithms and models.
 
@@
 It aims to develop algorithms and techniques for automatically analyzing, classifying, and retrieving musical information, primarily from audio signals.
-While MIR research has traditionally focused on technical aspects such as Digital Signal Processing (DSP) and pattern recognition, it may have overlooked other relevant domains, including perception, cognition, music theory, aural skills, musicology, and their subfields.

### 2023-05-31 introduction/Subsections/Motivation.tex
Updates from Overleaf

@@
 
-As a music enthusiast, professional musician, and scholar, I am passionately committed to exploring the foundational elements of musical composition, investigating the diverse techniques employed in creating musical works, and deciphering the intricate relationships among them.
+As a music enthusiast, musician, and scholar, I am passionately committed to exploring the foundational elements of musical composition, investigating the diverse techniques employed in creating musical works, and deciphering the intricate relationships among them.
 
-This passion fuels my quest for knowledge on extracting valuable information embedded within music in any domain, being my main interest in the audio and symbolic domains, contributing to developing more sophisticated and effective music-related technologies and solutions in the industrial landscape.
+This passion fuels my quest for knowledge on extracting valuable information embedded within music in any domain, being my main interest in the audio and symbolic domains \cite{Crestel2018AOrchestration}\cite{WeilAutomaticSignals}, contributing to developing more sophisticated and effective music-related technologies and solutions in the industrial landscape.
 
-\subsubsection{Academic and industrial motivation}
+\subsubsection{Industrial motivation}
 
@@
 
-The emergence of self-supervised models that learn embedding spaces for retrieving musical content from audio signals has unveiled new opportunities in academic research.
+The emergence of self-supervised models that learn embedding spaces for retrieving musical content from audio signals has unveiled new opportunities.
 By capturing high-level semantic information from raw audio data in an unsupervised manner, these models can potentially revolutionize various aspects of the music industry.
@@
 
+While MIR research has traditionally focused on technical aspects, it may have overlooked other relevant domains, including perception, cognition, music theory, aural skills, musicology, and their subfields.
 Purely mathematical approaches may not always reflect how humans perceive music and may not capture the subtle variations in timing or harmonic relationships critical to musical perception.
-We argue that MIR research needs to incorporate a more balanced approach that considers the interdisciplinary nature of music and the importance of other domains beyond digital signal processing.
+We argue that MIR research needs to incorporate a more balanced approach that considers the interdisciplinary nature of music and the importance of other domains beyond DSP.
 
-I have consistently been inspired by musicians and researchers who strive to uncover musical ground truth within an existing tonal paradigm, such as Heinrich Schenker and his school of thought \cite{Komar1959SchenkersStructure}, and particularly by challenging it, exemplified by Arnold Schoenberg \cite{Samson1974SchoenbergsMusic}, George Russell \cite{LydianRussell} or Ernst Levy \cite{LevyAHarmony}.
+I have consistently been inspired by musicians and researchers who strive to bridge the gap and uncover musical ground truth within an existing tonal paradigm, such as Heinrich Schenker and his school of thought \cite{Komar1959SchenkersStructure}, and particularly by challenging it, exemplified by Arnold Schoenberg \cite{Samson1974SchoenbergsMusic}, George Russell \cite{LydianRussell} or Ernst Levy \cite{LevyAHarmony}.
 These approaches aim to identify abstract concepts that reinforce or disrupt the tonal foundation.
-Their ultimate goal is to advance the tonal landscape, providing musicians with a dependable playground for growth, development, and further understanding tonal and atonal paradigms.
+Their ultimate goal is to advance the tonal landscape, providing musicians with a dependable playground for growth, development, and further understanding of tonal and atonal paradigms.
 

### 2023-05-31 introduction/Subsections/Previous work.tex
Updates from Overleaf

@@
 
-These aspects include the utilization of multi-level music segmentation through deep audio embeddings to replace manually engineered features \cite{SalamonDeepSegmentation}, the enhancement of environmental sound classification \cite{Kim2020OneStrategies}, the improvement of vocal-centric music tasks using cross-domain audio embedding \cite{Kim2021LearningLoss}, the enhancement of audio classification through a combination of task-specific and pre-trained features \cite{Hung2022Feature-informedClassification}, the creation of a music similarity search engine specifically for video producers \cite{epidemic}, the improved performance in Music Emotion Recognition (MER) tasks \cite{KohComparisonRecognition}, embedding songs for similarity comparison based on artist identification \cite{contentmusicsimtriplet2020}, the resolution of the cross-modal text-to-music retrieval problem \cite{WonEmotionStories}, and music rearrangement \cite{Stoller2018IntuitiveTransitions}.
-This last innovative approach presents a promising avenue for automated music rearrangement, enhancing the process's efficiency and quality \cite{Plachouras2023MusicSegmentation}.
-
-Moreover, deep audio embeddings offer the advantage of transferability.
-Once trained, these latent representations can be utilized as a starting point for various other tasks, thus saving computational resources and time compared to training a model from scratch \cite{HamelTransferSimilarity}.
+These aspects include the utilization of multi-level music segmentation through deep audio embeddings to replace manually engineered features \cite{SalamonDeepSegmentation}, the enhancement of environmental sound classification \cite{Kim2020OneStrategies}, the improvement of vocal-centric music tasks using cross-domain audio embedding \cite{Kim2021LearningLoss}, the enhancement of audio classification through a combination of task-specific and pre-trained features \cite{Hung2022Feature-informedClassification}, the creation of a music similarity search engine specifically for video producers \cite{epidemic}, the improved performance in Music Emotion Recognition (MER) tasks \cite{KohComparisonRecognition}, embedding songs for similarity comparison based on artist identification \cite{contentmusicsimtriplet2020}, the resolution of the cross-modal text-to-music retrieval problem \cite{WonEmotionStories}, and automated music rearrangement \cite{Stoller2018IntuitiveTransitions}\cite{Plachouras2023MusicSegmentation}.
 
@@
 
+Moreover, deep audio embeddings offer the advantage of transferability.
+Once trained, these latent representations can be utilized as a starting point for various other tasks, thus saving computational resources and time compared to training a model from scratch \cite{HamelTransferSimilarity}.
+
 Given their demonstrated success in the literature and their potential for transfer learning, exploring deep audio embeddings for MIR downstream tasks seems worthwhile.

### 2023-05-31 methods/subsections/deep learning.tex
Updates from Overleaf

@@
 
-They leverage the central algorithm, backpropagation, which calculates gradients of the loss function related to network parameters through forward and backward pass processes, thereby optimizing model performance.
+They leverage the central algorithm, backpropagation, which calculates gradients of the loss function related to network parameters through forward and backward pass processes, thereby optimizing model performance \cite{Rumelhart1986LearningInternal}.
 
@@
 Deep Neural Networks (DNNs), computational models rooted in biological neural systems, utilize layers of artificial neurons for tasks such as pattern recognition, classification, and regression.
-DNNs evolve by adjusting connections between neurons during learning, a concept initiated in the mid-20th century but modernized with Frank Rosenblatt's single-layer perceptron in 1957, capable of learning linearly separable patterns.
+DNNs evolve by adjusting connections between neurons during learning, a concept initiated in the mid-20th century but modernized with Frank Rosenblatt's single-layer perceptron in 1957, capable of learning linearly separable patterns \cite{Rosenblatt1958ThePerceptron}.
 
@@
 This function is applied to a neuron's inputs, transforming the input's summed product and weights into an output passed onto the next layer.
-It introduces non-linearity into the network, enabling it to learn complex patterns and relationships from the data.
+It introduces non-linearity into the network, enabling it to learn complex patterns and relationships from the data \cite{Goodfellow2016DeepLearning}.
 
@@
 
-%Colour CNN
-\input{figures/neural networks/colour CNN}
-
 \newpage

### 2023-05-31 methods/subsections/implementation.tex
Updates from Overleaf

@@
 \section{Implementation details}
+
+Our approach could be broadly categorized as cognitive modeling, as it strives to mimic human cognitive processes and problem-solving through a computerized model.
+We champion exposure-based learning in music and active engagement with an array of musical styles, genres, techniques, and learning methods to foster well-rounded musical proficiency and efficient performance with novel data in practical applications.
+
 \subsection{Contrastive Learning of Musical Representations}
@@
 For this task, a Triple Siamese Network is suggested, a model architecture proved efficient for music similarity retrieval tasks \cite{contentmusicsimtriplet2020}, intending to minimize the loss function between an anchor, positive, and negative sample, achieved through online triplet mining \cite{Sikaroudi2020OfflinePatches}.
-The overarching aim is to train a model in a self-supervised setting, which can effectively distinguish between similar and dissimilar samples while considering their underlying composition and production texture.
+The overarching aim is to train a model in a self-supervised setting, which can effectively distinguish between similar and dissimilar samples.
 
@@
 
-The SampleCNN model \cite{Lee2018SampleCNN:Classification} takes 1D input data with a single channel and follows the next architecture:
+The SampleCNN model \cite{Lee2018SampleCNN:Classification} is a CNN designed for raw waveform audio data, treating each audio sample as an independent channel and applying 1-dimensional convolution along the temporal axis.
+Its implementation is an adaptation of \cite{CLMR2021} using PyTorch \cite{Paszke2019PyTorch:Library} and PyTorch Lightning \cite{PyTorchDocumentation}.
+
+This fully convolutional model reduces computational requirements and learns features at different scales through its multi-resolution architecture \ref{tab:samplecnn}.
 
@@
 
-\begin{equation}
-y_i = \frac{1}{N} \sum_{j=1}^{N} x_{ij}
-\end{equation}
-
-Here, $y_i$ is the output tensor after the average pooling process.
-Each element $x_{ij}$ is part of the input tensor.
-$N$ is the count of elements in the second dimension of the input tensor, while $i$ and $j$ are used to iterate over the first and second dimensions of the tensors, respectively.
-
 %Colour CNN
@@
 
-\subsubsection{Optimizer}
+\subsection{Optimizer and learning rate}
+
+In our research, we've employed the AdamW optimizer \cite{Loshchilov2017DecoupledRegularization}, an optimized variant of the widely-used Adam optimizer for training neural networks.
+AdamW adeptly balances the learning rate across network weights, providing an efficient strategy for weight decay management by isolating it from gradient updates.
+
+\subsubsection{Learning rate}
+
+The learning rate, set at 0.003, is a pivotal parameter dictating the step size at each iteration towards loss function minimization.
+It's a delicate balancing act— a high rate promises swift convergence with a risk of minimum overshoot, while a lower rate provides careful convergence but necessitates more iterations.
 
@@
 
-We believe our experiments can benefit from time-domain processing because it allows more natural handling of temporal patterns and sequences in the data while avoiding windowing artifacts.
-
-Mel-spectrogram-based approaches have proved useful in numerous audio-related machine-learning tasks using CNN, as their frequency-domain summarization is efficient and not easily learnable through data-driven approaches \cite{Kim2020OneStrategies}.
-That being said,  they exhibit limitations concerning their representation of perceptual similarity: the spectrogram of an audio signal, denoted as $\phi(x)$ for audio signal $x$ and $\phi(y)$ for audio signal $y$, captures the distribution of frequencies as they vary over time.
-A small difference between $\phi(x)$ and $\phi(y)$ generally signifies high perceptual similarity from a human listener's perspective.
-In other words, if two audio signals have similar spectrograms, they are likely to sound alike when heard.
-
-However, the inverse is not consistently true.
-There exist instances where two audio signals can have significantly different spectrograms, i.e., a high spectrogram distance between $\phi(x)$ and $\phi(y)$, but are still perceived as musically similar by human listeners.
-This discrepancy is due to the complexity of human auditory perception that goes beyond just the distribution of frequencies over time \cite{Mesostructures2023}.
-
-Our perception of sound involves several other factors, including temporal patterns, phase relationships between frequencies, and even higher-level musical structures.
-Therefore, even if two sounds have very different spectrograms, they might still be perceived as similar if they share these other characteristics.
-This underlines the inherent limitation of using only spectrogram distance to measure high-level music similarity, as it may not always produce results consistent with human perceptual judgments.
+Our experiments can benefit from incorporating time-domain processing, which allows for more natural handling of temporal patterns and sequences in the data while avoiding windowing artifacts.
+While mel-spectrogram-based approaches have proven useful in various audio-related machine-learning tasks, their limitations lie in their representation of perceptual similarity.
+Spectrograms capture the distribution of frequencies over time, and small differences in spectrograms generally indicate high perceptual similarity from a human listener's perspective.
+However, there are cases where two audio signals can have significantly different spectrograms but still be perceived as musically similar.
+This discrepancy is due to the complexity of human auditory perception, which encompasses temporal patterns, phase relationships between frequencies, and higher-level musical structures.
+Therefore, relying solely on spectrogram distance to measure high-level music similarity may not consistently align with human perceptual judgments \cite{Kim2020OneStrategies}\cite{Mesostructures2023}.
 
@@
 
-Let $g \in [-12, 0]$ represent the gain, $\Delta p \in [-1200, 1200]$ the pitch shift, $h_R[n]$ the impulse response of the reverb with parameters in $[0, 100]$, $h_C[n]$ the impulse response of the chorus with parameters determined by the specified ranges, $d \in [0, 30]$ the overdrive parameter, $\alpha \in [0.9, 1.1]$ the speed change factor, $\beta \in [0.9, 1.1]$ the stretch factor, $f_m \in [0.1, 100]$ the modulation frequency of the tremolo, and $d_m \in [1, 101]$ the depth of the tremolo.
+In this analysis, various parameters represent different effects on the signal.
+We use $g \in [-12, 0]$ for gain, $\Delta p \in [-1200, 1200]$ for pitch shift, $h_R[n]$ for the reverb impulse response, $h_C[n]$ for the chorus impulse response, $d \in [0, 30]$ for overdrive, $\alpha \in [0.9, 1.1]$ for speed change, $\beta \in [0.9, 1.1]$ for stretch factor, $f_m \in [0.1, 100]$ for tremolo's modulation frequency, and $d_m \in [1, 101]$ for tremolo's depth.
+Each effect is applied aggressively but does not disrupt the high-level musical content.
 
-These effect selections behave and affect the signal in several domains, adding aggressive transformations while preserving high-level musical content.
+\textbf{Amplitude effects}, like gain, modify the signal's overall amplitude with a constant factor $g$.
 
-\begin{itemize}
-\item \textbf{Amplitude effects:} Amplitude or gain modification.
-\begin{itemize}
-    \item Gain: Adjusts the overall amplitude of the signal by a constant factor $g \in [-12, 0]$ dB.
-\end{itemize}
+\textbf{Time-domain effects} such as speed change and stretch alter the signal's playback speed and duration without changing its pitch, respectively.
+The speed and stretch factors are $\alpha$ and $\beta$.
 
-\item \textbf{Time-domain effects:} Alters the signal's timing or duration.
-\begin{itemize}
-    \item Speed change: Alters the playback speed of the signal by a factor $\alpha \in [0.9, 1.1]$.
-    \item Stretch: Changes the signal duration without affecting its pitch by a factor $\beta \in [0.9, 1.1]$.
-\end{itemize}
+\textbf{Frequency-domain effects} adjust the frequency content or pitch of the signal, as in pitch shifting, which alters the pitch by $\Delta p$.
 
-\item \textbf{Frequency-domain effects:} Alters the frequency content or pitch of the signal.
-\begin{itemize}
-    \item Pitch shift: Changes the signal's pitch by $\Delta p \in [-1200, 1200]$ cents. Two-octave range, one octave higher to one octave lower.
-\end{itemize}
+\textbf{Nonlinear effects} such as overdrive add harmonic distortion using the parameter $d$.
 
-\item \textbf{Nonlinear effects:} Harmonic distortion or other complex changes.
-\begin{itemize}
-    \item Overdrive: Adds harmonic distortion to the signal based on the parameter $d \in [0, 30]$.
-\end{itemize}
+\textbf{Modulation effects}, including chorus and tremolo, use a control signal or low-frequency oscillator.
+The specified ranges determine the chorus parameters, and the tremolo's amplitude modulation frequency and depth are $f_m$ and $d_m$.
 
-\item \textbf{Modulation effects:} Modulation using a low-frequency oscillator or control signal.
-\begin{itemize}
-    \item Chorus: Applies a varying time delay to the signal, resulting in a richer, thicker sound. The specified ranges determine the chorus parameters.
-    \item Tremolo: Modulates the signal's amplitude at a modulation frequency $f_m \in [0.1, 100]$ Hz and depth $d_m \in [1, 101]$.
-\end{itemize}
+\textbf{Reverberation effects} simulate physical space's acoustic reflections and reverberations, like reverb that applies an impulse response $h_R[n]$.
+Finally, \textbf{Noise effects} add a noise signal $N[n]$ with a signal-to-noise ratio (SNR) in the range $[12, 100]$.
 
-\item \textbf{Reverberation effects:} Acoustic reflections simulation and reverberations of physical space.
-\begin{itemize}
-    \item Reverb: Applies an impulse response $h_R[n]$ that simulates the reverberation of space with parameters in the range $[0, 100]$.
-\end{itemize}
-
-\item \textbf{Noise effects:}
-\begin{itemize}
-    \item Additive noise: Adds a noise signal $N[n]$ with a specific signal-to-noise ratio (SNR) in the range $[12, 100]$.
-\end{itemize}
-\end{itemize}
-
-The positive signal $P[n]$ is generated as follows:
+The positive signal $P[n]$ is generated according to the equation given below, where the symbols denote specific effects as indicated:
 
@@
 
-where $\ast$ denotes convolution, $h_{G}[n] = g \delta[n]$, $h_{D}[n]$ is the impulse response of the overdrive effect, $h_{P_t}[n]$ is the impulse response of the pitch shift effect, $h_{S}[n]$ represents the impulse response of the speed change effect, $h_{T}[n]$ is the impulse response of the stretch effect, and $h_{T_m}[n] = (1 - d_m \cos(2 \pi f_m n))\delta[n]$ is the impulse response of the tremolo effect.
-The noise signal $N[n]$ is added with a specific signal-to-noise ratio (SNR) in the range $[12, 100]$ in decibels.
+The $\ast$ symbol represents convolution, and the various $h$ symbols indicate the impulse responses of specific effects. The noise signal $N[n]$ is included with a specific SNR.
 
@@
 
-The triplet loss function used in Siamese networks guides the learning process.
+The triplet loss function used in Siamese-like networks guides the learning process.
 It seeks to minimize the distance between the anchor and positive instances while maximizing the distance between the anchor and the negative instances.
@@
 
-The goal of minimizing this loss function is to learn discriminative embeddings, where similar examples are grouped closely together and dissimilar examples are placed farther apart in the embedding space.
+As previously stated, the goal of minimizing this loss function is to learn discriminative embeddings, where similar examples are grouped closely together while dissimilar examples are placed farther apart in the embedding space.
 

### 2023-05-31 preface/preface.tex
Updates from Overleaf

--- 2023-01-14 preface/preface.tex
@@
 \pagenumbering{gobble}% Remove page numbers (and reset to 1)
-(Optional, if used placed on a right page next to an empty left page)
 
-I would like to dedicate this work to...
+Music and science have always been my two greatest passions.
+
+When the opportunity to work at Epidemic Sound presented itself, it was as if the universe had conspired to bring my interests together, offering me the chance to explore the fascinating field of Music Information Retrieval (MIR) from an industrial perspective.
+
+With the support and encouragement of my loved ones, I took a leap of faith and moved from Barcelona to Stockholm to embark on this exciting journey.
+
+This work humbly aims to help untangle the complexities of music and offer a more musically-driven perspective to MIR.
+We aim to contribute to a deeper understanding of the intricate relationships within musical data by bridging the gap between music theory and computational analysis.
+
+I am deeply grateful to the Epidemic Sound team for their guidance, expertise, and camaraderie throughout this project.
+I would also like to extend my heartfelt appreciation to my family for their unwavering support and belief in my abilities.
+
+My motivation for writing this piece stems from a desire to grow as a musician, developer, and individual.
+I believe that by delving into the world of MIR, I can expand my horizons while making a meaningful contribution to the field.
+
+This work is intended for any curious human being, regardless of their background in music or computer science.
+I hope it will inspire others to explore the fascinating intersection of these two disciplines.
+
+The scope of this work encompasses a range of MIR tasks and methodologies, as well as discussions on the challenges and opportunities that arise within the field.
+We hope this work will serve as a starting point for further exploration and inspire new ideas in the realm of MIR.
+
 \newpage
-
 \end{preface}

### 2023-05-31 results/results.tex
Updates from Overleaf

@@
 
-The F-measure is a widely used boundary detection metric computed by comparing the predicted and ground truth boundaries.
-This metric, ranging from 0 to 1, represents the harmonic mean of precision and recall, providing a balanced view of under-segmentation and over-segmentation.
-Precision calculates the percentage of correctly detected boundaries, whereas recall assesses the percentage of actual boundaries detected correctly.
-Given the potential inaccuracies in human annotations and prediction errors, the F-measure tolerates minor discrepancies between predicted and ground truth boundaries.
-This tolerance level can be adjusted, enabling the metric to consider a predicted boundary as correct if it's within the set tolerance window of a ground truth boundary \cite{Turnbull2007ABOOSTING}.
-
 \newpage

### 2023-05-31 results/subsections/tables.tex
Updates from Overleaf

@@
 \small
-\begin{tabularx}{\textwidth}{>{\raggedright\arraybackslash}p{5cm}XXXXX}
+\begin{tabularx}{\textwidth}{>{\raggedright\arraybackslash}p{4.5cm}XXXXX}
 \toprule
-\thead{\textbf{Year, Authors, Ref}} & \thead{\textbf{Algorithm}} & \thead{\textbf{Input}} & \thead{\textbf{Method}} & \thead{\textbf{F-measure}} \\
+\thead{\centering\textbf{Year, Authors, Ref}} & \thead{\centering\textbf{Algorithm}} & \thead{\centering\textbf{Input}} & \thead{\centering\textbf{Method}} & \thead{\centering\textbf{F-measure \footnote{The F-measure is a widely used boundary detection metric computed by comparing the predicted and ground truth boundaries.
+This metric, ranging from 0 to 1, represents the harmonic mean of precision and recall, providing a balanced view of under-segmentation and over-segmentation.
+Precision calculates the percentage of correctly detected boundaries, whereas recall assesses the percentage of actual boundaries detected correctly.
+Given the potential inaccuracies in human annotations and prediction errors, the F-measure tolerates minor discrepancies between predicted and ground truth boundaries.
+This tolerance level can be adjusted, enabling the metric to consider a predicted boundary as correct if it's within the set tolerance window of a ground truth boundary \cite{Turnbull2007ABOOSTING}.}}} \\
 \midrule
@@
 \addlinespace
-2014, Nieto \& Bello, [28] & NB1 & MFCCs + chromas & Checkerboard-like kernel  & 0.299 \\
+2014, Nieto \& Bello, [28] & NB1 & MFCCs, chromas & Checkerboard-like kernel  & 0.299 \\
 \addlinespace
@@
 \addlinespace
-2015, Grill \& Schlüter, [4] & - & MLS + SSLMs & CNN  & 0.523 \\
+2015, Grill \& Schlüter, [4] & - & MLS, SSLMs & CNN  & 0.523 \\
 \addlinespace
-2015, Grill \& Schlüter, [5] & - & MLS + PCPs + SSLMs & CNN  & 0.508 \\
+2015, Grill \& Schlüter, [5] & - & MLS, PCPs, SSLMs & CNN  & 0.508 \\
 \addlinespace
-2017, Hadria \& Peeters, [35] & - & MLS + SSLMs & CNN  & 0.291 \\
+2017, Hadria \& Peeters, [35] & - & MLS, SSLMs & CNN  & 0.291 \\
 \bottomrule

### 2023-06-03 abstract/abstract.tex
Updates from Overleaf

@@
 
-Our cognitively-based approach for learning embeddings focuses on using full resolution data and preserving high-level musical information.
+Our cognitively-based approach for learning embeddings focuses on using full-resolution data and preserving high-level musical information.
 Drawing upon our domain expertise, we developed robust transformations to encode heuristic musical concepts that should remain constant.
@@
 \bigskip
-Keywords: Music Information Retrieval; Music Structure Analysis; Deep Audio Embeddings, Aural Skills
+Keywords: MIR; Music Structure Analysis; deep audio embeddings; audio representations; representation learning; embeddings; transfer learning; multi-task learning; multi-modal learning; aural Skills
 

### 2023-06-03 introduction/Subsections/Motivation.tex
Updates from Overleaf

@@
 
-Personal, academic, and industrial motivations drive this thesis.
+Driven by personal, academic, and industrial motivations, this thesis is a product of a collaboration between \href{https://www.epidemicsound.com/}{Epidemic Sound} (ES) and the \href{https://www.upf.edu/web/mtg}{Music Technology Group} (MTG) at Universitat Pompeu Fabra.
+ES, a leading Swedish company, holds and curates an expansive global library of 40,000+ royalty-free music tracks and 90,000+ sound effects.
+MTG, based in Barcelona, Spain, excels in developing innovative technologies related to sound and music, such as music information retrieval, digital signal processing, interactive music systems, and computational musicology.
 
-This research is conducted in collaboration with \textit{Epidemic Sound AB (ES)} \cite{EpidemicSite}, and the \textit{Music Technology Group (MTG)} at Universitat Pompeu Fabra.
+This partnership seeks to enhance our understanding of music's fundamental structures, potentially improving ES's technical products, services, and advancements in Music Information Retrieval (MIR) research.
 
-ES is a prominent Swedish company that provides a global library of over 40,000+ royalty-free soundtrack music and 90,000+ sound effects.
+As a music enthusiast, musician, and scholar, I am deeply committed to exploring the foundational elements of musical composition, investigating various creation techniques, and deciphering their intricate relationships.
+This passion drives my endeavor to extract valuable information embedded within music across any domain, particularly in audio and symbolic domains.
 
-The MTG, based in Barcelona (Spain), specializes in developing new technologies related to sound and music, including music information retrieval, digital signal processing, computational models of music perception and cognition, and interactive music systems.
-
-The collaboration with ES and the MTG aims to deepen our understanding of music and its fundamental structures, potentially leading to advancements and benefits for the company's technical products, services, and MIR academic research.
-
-\subsubsection{Personal motivation}
-
-As a music enthusiast, musician, and scholar, I am passionately committed to exploring the foundational elements of musical composition, investigating the diverse techniques employed in creating musical works, and deciphering the intricate relationships among them.
-
-This passion fuels my quest for knowledge on extracting valuable information embedded within music in any domain, being my main interest in the audio and symbolic domains \cite{Crestel2018AOrchestration}\cite{WeilAutomaticSignals}, contributing to developing more sophisticated and effective music-related technologies and solutions in the industrial landscape.
-
-\subsubsection{Industrial motivation}
-
-While it is true that the theoretical foundations of machine learning can be traced back to the pioneering work of figures such as Alan Turing and Claude Shannon in the mid-twentieth century, we are currently experiencing a period of significant breakthroughs in AI research \cite{Vaswani2017AttentionNeed}.
-These breakthroughs have facilitated the implementation of AI in widely used products \cite{OpenAI2023GPT-4Report}.
-Many researchers and corporations are keen to stay abreast of these developments and contribute to this exciting and rapidly evolving field.
-
-The emergence of self-supervised models that learn embedding spaces for retrieving musical content from audio signals has unveiled new opportunities.
-By capturing high-level semantic information from raw audio data in an unsupervised manner, these models can potentially revolutionize various aspects of the music industry.
-
-In the industrial and corporate realm, the embedding spaces generated by these models can be utilized to create all sorts of valuable products and user experiences for content creators.
-These advancements ultimately enhance our interaction with music in the digital age, promoting innovation and collaboration across the music industry.
+We are witnessing significant breakthroughs in AI research \cite{Vaswani2017AttentionNeed}, building on the theoretical foundations of pioneers such as Alan Turing and Claude Shannon.
+These advancements have resulted in the widespread application of AI in popular products \cite{OpenAI2023GPT-4Report}, prompting researchers and corporations to stay informed and contribute to this rapidly evolving field.
+The advent of self-supervised models that learn embedding spaces for retrieving musical content from audio signals presents fresh opportunities.
+By autonomously extracting high-level semantic information from raw audio data, these models could transform various facets of the music industry.
+In the industrial realm, these embedding spaces can be harnessed to devise valuable products and enrich user experiences for content creators, thereby fostering innovation and collaboration across the music industry.
 

### 2023-06-03 introduction/Subsections/Objectives.tex
Updates from Overleaf

@@
 
-The study aims to develop a unified embedding, $e(M)$, for a music piece $M$ that integrates high-level elements like melody contour, harmony relationships, and other comprehensive components, arranging the embedding space to emphasize clustering of these sophisticated musical content without any consideration for sonic quality attributes.
-Utilizing a blend of Music Information Retrieval (MIR) computational methodologies and musicological perspectives, the research will explore musical compositions from various styles and genres.
+The study aims to develop a unified numerical understanding (or embedding \footnote{A learned representation or embedding is a numerical output -usually a fixed-size vector- produced by a machine-learning model from a low-level input.
+Good representations should be versatile across various tasks and require limited supervision \cite{Turian2022HEAR:Representations}.}) for a music piece that integrates high-level elements like melody contour, harmony relationships, and other comprehensive components such as the relationships between elements unfolding through time, arranging the embedding space to emphasize the clustering of these sophisticated musical content without considering sonic qualities or attributes.
+
+The research will utilize MIR computational methodologies and musicological perspectives to explore musical compositions from various styles and genres.
 

### 2023-06-03 introduction/Subsections/Previous work.tex
Updates from Overleaf

@@
 
-Neural networks have recently facilitated the development of low-dimensional embeddings that capture essential musical features, enabling the computation of various task-specific aspects.
+Recent advancements in neural networks have enabled the development of low-dimensional embeddings which encapsulate critical musical attributes, thus facilitating the computation of diverse task-specific elements.
 
-These aspects include the utilization of multi-level music segmentation through deep audio embeddings to replace manually engineered features \cite{SalamonDeepSegmentation}, the enhancement of environmental sound classification \cite{Kim2020OneStrategies}, the improvement of vocal-centric music tasks using cross-domain audio embedding \cite{Kim2021LearningLoss}, the enhancement of audio classification through a combination of task-specific and pre-trained features \cite{Hung2022Feature-informedClassification}, the creation of a music similarity search engine specifically for video producers \cite{epidemic}, the improved performance in Music Emotion Recognition (MER) tasks \cite{KohComparisonRecognition}, embedding songs for similarity comparison based on artist identification \cite{contentmusicsimtriplet2020}, the resolution of the cross-modal text-to-music retrieval problem \cite{WonEmotionStories}, and automated music rearrangement \cite{Stoller2018IntuitiveTransitions}\cite{Plachouras2023MusicSegmentation}.
+Such tasks encompass developing an audio embedding method that excels across a wide array of applications without fine-tuning \cite{Turian2022HEAR:Representations}, deploying deep audio embeddings for multi-level music segmentation \cite{SalamonDeepSegmentation}, improving environmental sound classification \cite{Kim2020OneStrategies}, enhancing vocal-centric music tasks via cross-domain audio embedding \cite{Kim2021LearningLoss}, combining task-specific and pre-trained features for improved audio classification \cite{Hung2022Feature-informedClassification}, creating a music similarity search engine tailored for video producers \cite{epidemic}, enhancing Music Emotion Recognition (MER) performance \cite{KohComparisonRecognition}, investigating the efficacy of speaker recognition pre-trained model embeddings \cite{lightweight}, embedding songs for similarity comparison via artist identification \cite{contentmusicsimtriplet2020}, solving the cross-modal text-to-music retrieval issue \cite{WonEmotionStories}, and facilitating automated music rearrangement \cite{Stoller2018IntuitiveTransitions, Plachouras2023MusicSegmentation}.
 
-On top of that and returning to musicological influences, the middle ground in Schenkerian analysis can be compared to the mesostructure in music.
-Analogous to the mesostructure, it represents the intermediate-level musical patterns that bridge the micro and macro structures.
-This element is often overlooked when applying deep learning to music.
-As emphasized by \cite{Mesostructures2023}, models that address this mesostructure level could significantly enrich tasks such as music analysis, composition, and retrieval, providing a more holistic understanding of music, similar to the insights gained from analyzing the middle-ground in Schenkerian analysis.
-\cite{Introduction_to_Schenkerian_Analysis}
+Furthermore, deep learning applications in music often overlook the intermediate-level musical patterns, analogous to the 'mesostructure' in music and the middle ground in Schenkerian analysis.
+As highlighted by \cite{Mesostructures2023}, addressing this mesostructure could significantly improve tasks like music analysis, composition, and retrieval by providing a more holistic understanding of music, comparable to insights from Schenkerian analysis \cite{Introduction_to_Schenkerian_Analysis}.
 
-Moreover, deep audio embeddings offer the advantage of transferability.
-Once trained, these latent representations can be utilized as a starting point for various other tasks, thus saving computational resources and time compared to training a model from scratch \cite{HamelTransferSimilarity}.
+Additionally, deep audio embeddings offer the benefit of transferability, acting as a starting point for various tasks, thus saving computational resources and time as opposed to training a model from scratch \cite{HamelTransferSimilarity}.
 
-Given their demonstrated success in the literature and their potential for transfer learning, exploring deep audio embeddings for MIR downstream tasks seems worthwhile.
+However, it is still an open question whether a general-purpose audio representation can effectively mimic human hearing \cite{Turian2022HEAR:Representations}.
+
+Considering their proven efficacy in existing literature and their potential for transfer learning, it appears promising to further investigate deep audio embeddings for Music Information Retrieval (MIR) downstream tasks.

### 2023-06-03 methods/subsections/implementation.tex
Updates from Overleaf

@@
 Our approach could be broadly categorized as cognitive modeling, as it strives to mimic human cognitive processes and problem-solving through a computerized model.
-We champion exposure-based learning in music and active engagement with an array of musical styles, genres, techniques, and learning methods to foster well-rounded musical proficiency and efficient performance with novel data in practical applications.
+We champion exposure-based learning in music and active engagement with musical styles, genres, techniques, and learning methods to foster well-rounded musical proficiency and efficient performance with novel data in practical applications.
 
@@
 
-Our experiments can benefit from incorporating time-domain processing, which allows for more natural handling of temporal patterns and sequences in the data while avoiding windowing artifacts.
-While mel-spectrogram-based approaches have proven useful in various audio-related machine-learning tasks, their limitations lie in their representation of perceptual similarity.
-Spectrograms capture the distribution of frequencies over time, and small differences in spectrograms generally indicate high perceptual similarity from a human listener's perspective.
-However, there are cases where two audio signals can have significantly different spectrograms but still be perceived as musically similar.
-This discrepancy is due to the complexity of human auditory perception, which encompasses temporal patterns, phase relationships between frequencies, and higher-level musical structures.
-Therefore, relying solely on spectrogram distance to measure high-level music similarity may not consistently align with human perceptual judgments \cite{Kim2020OneStrategies}\cite{Mesostructures2023}.
+Conventional transformations, such as log-scaled Mel spectrograms or Mel Frequency Cepstral Coefficients, capture key features but may obscure some information inherent in raw audio data.
+
+Raw audio data offers unique advantages.
+Primarily, it ensures the retention of the original signal, which could reveal novel findings, and facilitates the direct extraction of features through advanced deep learning models \cite{learning}.
+However, it is not without challenges: high sample rates result in high dimensionality, demanding substantial computational resources.
+Additionally, raw audio is noise-sensitive, complicating the extraction process.
+Features derived from raw audio also often lack the interpretability of traditional ones \cite{Schindler2020DeepTutorial}.
+Hence, the choice of input data depends on the specific task, available computational resources, and the balance between data preservation and computational efficiency.
+
+Time-domain processing, a feature of our experiments, naturally handles temporal patterns and sequences in data, thereby avoiding windowing artifacts.
+Although Mel-spectrogram-based methods are effective for various audio-related machine learning tasks, their limitations lie in representing perceptual similarity.
+Spectrograms capture frequency distribution over time.
+Yet, the complexity of human auditory perception—encompassing temporal patterns, phase relationships between frequencies, and higher-level musical structures—means that musically similar sounds can have distinct spectrograms.
+This discrepancy implies that using spectrogram distance alone for measuring high-level music similarity may not always align with human perceptions \cite{Kim2020OneStrategies}\cite{Mesostructures2023}.
 
@@
 
-We posit that high-level musical content unfolds over time; therefore, we argue that the temporal structure of the negative images related to our anchor should be disrupted.
+Circling back to our premises and assumptions, we posit that high-level musical content unfolds over time; therefore, we argue that the temporal structure of the negative images, in contrast to our anchor, should be disrupted.
 While maintaining similar sonic qualities, the content should be rendered unintelligible.
@@
 \end{equation}
+
+The minimum duration $t_{min}$ is set to 0.05 seconds, and the maximum duration $t_{max}$ is set to 1 second.
+This range is chosen thoughtfully to strike a balance between the two factors.
+On the one hand, it is above the just noticeable difference (JND) threshold, the smallest change in a stimulus that can be perceived.
+On the other hand, it is short enough to maintain a reasonably-sized window to avoid discernible musical content \cite{Fastl2007Just-NoticeableChanges}.
+
 \item Generate random audio chunk lengths $l_1, l_2, \ldots, l_{n-1}$ from the uniform distribution on the interval $[l_{min}, l_{max}]$. Calculate the final audio chunk length as:
@@
 
-As previously stated, the goal of minimizing this loss function is to learn discriminative embeddings, where similar examples are grouped closely together while dissimilar examples are placed farther apart in the embedding space.
+As previously stated, the goal of minimizing this loss function is to learn discriminative embeddings, where similar examples are grouped closely together.
+In contrast, dissimilar examples are placed farther apart in the embedding space.
+
+While some packages can be found in the MIR literature \cite{auraloss}, we wrote our own PyTorch \cite{Paszke2019PyTorch:Library} implementation for the sake of our experiments.
 

### 2023-06-03 results/subsections/tables.tex
Updates from Overleaf

@@
+METRICS
+
+\begin{itemize}
+    \item \textbf{Precision}: Precision measures the proportion of correctly detected boundaries out of the total estimated boundaries.
+It quantifies the accuracy of the boundary detection algorithm.
+It is calculated as:
+
+    \[
+    \text{Precision} = \frac{\text{True Positives}}{\text{True Positives} + \text{False Positives}}
+    \]
+
+    High precision indicates a low rate of false positives, meaning the algorithm correctly identifies boundaries without many incorrect detections.
+
+    \item \textbf{Recall}: Recall measures the proportion of correctly detected boundaries out of the total reference boundaries.
+It quantifies the completeness or sensitivity of the boundary detection algorithm.
+It is calculated as:
+
+    \[
+    \text{Recall} = \frac{\text{True Positives}}{\text{True Positives} + \text{False Negatives}}
+    \]
+
+    High recall indicates a low rate of false negatives, meaning that the algorithm successfully detects most of the true boundaries without missing many.
+
+    \item \textbf{F-measure}: The F-measure is a widely used boundary detection metric computed by comparing the predicted and ground truth boundaries.
+This metric, ranging from 0 to 1, represents the harmonic mean of precision and recall, providing a balanced view of under-segmentation and over-segmentation.
+Precision calculates the percentage of correctly detected boundaries, whereas recall assesses the percentage of actual boundaries detected correctly \cite{Turnbull2007ABOOSTING}.
+The F-measure is calculated as follows:
+
+    \[
+    \text{F-measure} = \frac{2 \times \text{Precision} \times \text{Recall}}{\text{Precision} + \text{Recall}}
+    \]
+\end{itemize}
+
 Extend table by Hernandez-Olivan, C., Beltran, J. R. \& Diaz-Guerra, D. 
@@
 \toprule
-\thead{\centering\textbf{Year, Authors, Ref}} & \thead{\centering\textbf{Algorithm}} & \thead{\centering\textbf{Input}} & \thead{\centering\textbf{Method}} & \thead{\centering\textbf{F-measure \footnote{The F-measure is a widely used boundary detection metric computed by comparing the predicted and ground truth boundaries.
-This metric, ranging from 0 to 1, represents the harmonic mean of precision and recall, providing a balanced view of under-segmentation and over-segmentation.
-Precision calculates the percentage of correctly detected boundaries, whereas recall assesses the percentage of actual boundaries detected correctly.
-Given the potential inaccuracies in human annotations and prediction errors, the F-measure tolerates minor discrepancies between predicted and ground truth boundaries.
-This tolerance level can be adjusted, enabling the metric to consider a predicted boundary as correct if it's within the set tolerance window of a ground truth boundary \cite{Turnbull2007ABOOSTING}.}}} \\
+\thead{\centering\textbf{Year, Authors, Ref}} & \thead{\centering\textbf{Algorithm}} & \thead{\centering\textbf{Input}} & \thead{\centering\textbf{Method}} & \thead{\centering\textbf{F-measure}} \\
 \midrule
@@
 \end{tabularx}
-\caption{Your Caption}
+\caption[Baseline.
+State of the art table.]{Your Caption.
+Given the potential inaccuracies in human annotations and prediction errors, the F-measure tolerates minor discrepancies between predicted and ground truth boundaries.
+This tolerance level can be adjusted, enabling the metric to consider a predicted boundary as correct if it's within the set tolerance window of a ground truth boundary.}
 \label{tab:my_label}

### 2023-06-04 methods/subsections/implementation.tex
Updates from Overleaf

@@
 
-The positive image in our study must preserve its intelligible content when subjected to temporal (or any) transformations, regardless of alterations in sonic qualities.
+The positive image in our study must preserve its intelligible content when subjected to transformations, regardless of alterations in sonic qualities.
 Maintaining the temporal structure and meaningfulness of the content allows it to present musical elements identical or strikingly similar to the original track.
 
-While we have experimented with helpful audio augmentation tools such as \cite{Spijkervet2021Spijkervet/torchaudio-augmentations:V1.0} and \cite{Kharitonov2020DataDomain}, the specific requirements of our experiments necessitated the development of our transformation chain using \textit{torchaudio's} \cite{Yang2021TorchAudio:Processing} implementation of \textit{SoX} \cite{sox}: given an anchor audio signal $A[n]$, we generate a positive signal $P[n]$ by applying a series of amplitude, time-domain, frequency-domain, modulation, reverberation, and nonlinear effects with additive noise on top of it.
+While we have experimented with helpful audio augmentation tools such as \cite{Spijkervet2021Spijkervet/torchaudio-augmentations:V1.0} and \cite{Kharitonov2020DataDomain}, the specific requirements of our experiments necessitated the development of our own transformation chain using \textit{torchaudio's} \cite{Yang2021TorchAudio:Processing} implementation of \textit{SoX} \cite{sox}: given an anchor audio signal $A[n]$, we generate a positive signal $P[n]$ by applying a series of amplitude, time-domain, frequency-domain, modulation, reverberation, and nonlinear effects with additive noise on top of it.
 
@@
 
+The computation goes as follows:
+
 \begin{enumerate}
-\item Calculate the minimum and maximum audio chunk lengths in samples:
+\item We first calculate the minimum and maximum audio chunk lengths in samples:
 \begin{equation}
@@
 
-\item Generate random audio chunk lengths $l_1, l_2, \ldots, l_{n-1}$ from the uniform distribution on the interval $[l_{min}, l_{max}]$. Calculate the final audio chunk length as:
+\item We then generate random audio chunk lengths $l_1, l_2, \ldots, l_{n-1}$ from the uniform distribution on the interval $[l_{min}, l_{max}]$. Calculate the final audio chunk length as:
 \begin{equation}
@@
 where $L_A$ is the length of the anchor signal in samples.
-\item Split the anchor signal $A$ into audio chunks $C_1, C_2, \ldots, C_n$ according to the calculated audio chunk lengths.
+
+\item The third step is to split the anchor signal $A$ into audio chunks $C_1, C_2, \ldots, C_n$ according to the calculated audio chunk lengths in the previous step.
+
 \item Shuffle the audio chunks randomly to get the permuted slices $C_{\sigma(1)}, C_{\sigma(2)}, \ldots, C_{\sigma(n)}$, where $\sigma$ is a random permutation of indices from $1$ to $n$.
+
 \item Concatenate the shuffled audio chunks to generate the negative signal:
@@
 \end{enumerate}
+
+Again, the whole purpose of it is to disturb the time domain.
 

### 2023-06-08 abstract/abstract.tex
Updates from Overleaf

@@
 
-This thesis posits the existence of invariant high-level musical concepts that persist through changes in sonic qualities, akin to the symbolic domain where essence endures despite varying interpretations through different performances, instruments, and styles, among many other variables.
+This thesis posits the existence of invariant high-level musical concepts that persist regardless of changes in sonic qualities, akin to the symbolic domain where essence endures despite varying interpretations through different performances, instruments, and styles, among many other, almost countless variables.
 
@@
 We applied deep convolutional neural networks and a triplet loss function, identifying abstract and semantic musical elements without relying on their sonic qualities.
-This way, we replaced traditional acoustic features with deep audio embeddings, paving the way for high-level, sound-agnostic, and content-sensitive music identification.
+This way, we replaced traditional acoustic features with deep audio embeddings, paving the way for high-level, sound-agnostic, and content-sensitive music representation.
 
@@
 Preliminary results suggest that our musically-informed technique has significant potential for boundary detection tasks and possibly nearly all MIR downstream tasks that are not purely sonic-based.
-Consequently, music-motivated embeddings appear promising and potentially adaptable to other tasks constrained by data scarcity.
+While it didn't outperform state-of-the-art results, it showed very competitive results and room for improvement.
+Consequently, music-motivated audio embeddings appear promising and potentially adaptable to other tasks constrained by data scarcity.
 

### 2023-06-08 acknowledgements/acknowledgements.tex
Updates from Overleaf

--- 2023-01-14 acknowledgements/acknowledgements.tex
@@
 
-I want to express my sincerest gratitude to...
+I want to extend my deepest gratitude to...
 
 \begin{itemize}
-\item Carlos Lordelo, and Carl Thomé for their invaluable guidance and support throughout my thesis.
-Your expertise in MIR helped shape the direction of my research and make it a success.
-Your unwavering support and encouragement helped me overcome any difficulties I encountered during the process.
-I also appreciate the time and effort you invested in mentoring me.
-Your dedication to your students is truly inspiring, and I am honored to have had the opportunity to work with you.
+\item Carl Thomé and Carlos Lordeloª, whose expertise in MIR, ML, and DSP has been pivotal to the progress and success of my thesis.
+Their invaluable guidance and unwavering encouragement have empowered me to overcome the challenges encountered throughout this journey.
+Their dedication and commitment to mentorship are truly inspiring, and their influence has left an indelible mark on my academic path.
+The opportunity to work under their mentorship has been a privilege and an honor.
+Their profound impact is beyond what words can encapsulate.
+
 \vspace*{3mm}
-\item My co-supervisor
+\item Cody Hesse and Sebastian Löf
+
 \vspace*{3mm}
-\item The Music Technology Group (MTG)
+\item Epidemic Sound
+
+\vspace*{3mm}
+\item The Music Technology Group (MTG) and Universitat Pompeu Fabra (UPF).
+My profound thanks go to Xavier Serra for his faith in accepting a non-traditional profile to the master's program.
+Additionally, I appreciate Pedro Ramoneda and Genís Plaja for their patient assistance throughout my journey.
+
 \vspace*{3mm}
@@
 His understanding and willingness to accommodate my academic commitments effectively allowed me to balance my work and research responsibilities.
-His guidance and advice on professional matters have been instrumental in my growth as a professional.
-I am genuinely grateful for his unwavering support and encouragement and for being a great mentor.
+
 \vspace*{3mm}
@@
 I sincerely appreciate everything you have done for me and will always cherish the knowledge and experience I have gained under your guidance.
-\vspace*{3mm}
-\item My family
-\vspace*{3mm}
-\item My girlfriend
+
 \vspace*{3mm}

### 2023-06-08 evaluation/evaluation.tex
Updates from Overleaf

--- 2023-05-30 evaluation/evaluation.tex
@@
 
-\section{\textit{Embeddiogram} feature}
+\section{The \textit{embeddiogram}, an audio feature embedding representation}
 
 The \textit{embeddiogram} is derived by applying our pre-trained neural network model to sliding windowed segments across the audio signal, generating a sequence of embedding vectors.
-These relatively high-dimensional embedding vectors collectively form a two-dimensional description of the audio signal's musical content.
+These relatively low-dimensional embedding vectors collectively form a two-dimensional description of the audio signal's musical content.
 
-Below is a detailed explanation of how we compute the \textit{embeddiogram} from a given audio signal.
-This process comprises five key steps, including loading the audio data, slicing the audio data into windowed segments, processing each window using a pre-trained model to produce an embedding, collecting these embeddings, and finally normalizing the Embeddiogram.
+Below is a detailed explanation of how we compute the \textit{embeddiogram} from a given audio signal of length $N$.
+This process comprises loading the audio data, slicing the audio data into windowed segments, processing each window using a pre-trained model to produce an embedding, collecting and stacking these embeddings, and finally normalizing the \textit{embeddiogram}.
 
@@
   \centering
-  \begin{minipage}[b]{.8\linewidth}
+  \begin{minipage}[b]{1.0\linewidth}
     \centering
     \includegraphics[width=\linewidth]{figures/images/salami_391_embeddiogram.png}
-    \caption[]{Caption for image1}
+    \caption[Embeddiogram. Track 391 (SALAMI dataset).]{Embeddiogram. Track 391 (SALAMI dataset).}
     \label{fig:image1}
@@
 
-  \begin{minipage}[b]{.8\linewidth}
+  \begin{minipage}[b]{1.0\linewidth}
     \centering
     \includegraphics[width=\linewidth]{figures/images/samali_391_novelty_curve_peaks.png}
-    \caption[]{Caption for image2}
+    \caption[Novelty curve + peaks. Track 391 (SALAMI dataset).]{Novelty curve + peaks. Track 391 (SALAMI dataset).}
     \label{fig:image2}
@@
         \includegraphics[width=0.9\textwidth]{figures/images/salami_391_R matrix after Gaussian smoothing.png} % first figure itself
-        \caption[]{first figure}
+        \caption[Track 391 (SALAMI dataset) Self-similarity matrix]{Self-similarity matrix. Track 391 (SALAMI dataset).}
     \end{minipage}\hfill
@@
         \includegraphics[width=0.9\textwidth]{figures/images/salami_391_Lag matrix after Gaussian smoothing.png} % second figure itself
-        \caption[]{second figure}
+        \caption[Track 391 (SALAMI dataset) Self-similarity lag matrix]{Self-similarity lag matrix. Track 391 (SALAMI dataset).}
     \end{minipage}
@@
         \includegraphics[width=0.9\textwidth]{figures/images/salami_391_Q_matrix.png} % third figure itself
-        \caption[]{third figure}
+        \caption[Track 391 (SALAMI dataset). Q-matrix]{Cumulative matrix. Track 391 (SALAMI dataset).}
     \end{minipage}\hfill
@@
         \includegraphics[width=0.9\textwidth]{figures/images/salami_391_binary transitive matrix.png} % fourth figure itself
-        \caption[]{fourth figure}
+        \caption[Track 391 (SALAMI dataset). Transitive Binary Similarity Matrix]{Transitive Binary Matrix. Track 391 (SALAMI dataset).}
     \end{minipage}

### 2023-06-08 future work/future work.tex
Updates from Overleaf

@@
 
-hybrid autoencoder architecture + UNet stuff
+The question as per \cite{Turian2022HEAR:Representations} or \cite{Li2023MERT:Training} remains if such general-purpose audio representation can mimic human hearing.
+
 transforms
@@
 k-fold cross validation
+hyper-params: kernel size 0.005 times the sample rate
 
@@
 
+Listening evaluation
+2D or 3D latent space visualization as per \ref{fig:manifold}
+
+\input{figures/neural networks/manifold}
+
 \newpage

### 2023-06-08 introduction/Subsections/Motivation.tex
Updates from Overleaf

@@
 
+The MIR community appears to slowly converge and bridge the gap in musicology, theory, perception, and technical complexities by addressing.
+For example, by studing intermediate-level musical patterns, or \textit{mesostructures}.
+Deep learning applications in music often fail to consider these mesostructures, akin to Schenkerian analysis' middle ground.
+As noted by \cite{Mesostructures2023}, attending to these patterns could greatly enhance tasks like music analysis, composition, and retrieval by offering a more comprehensive understanding of music, echoing insights from Schenkerian analysis \cite{Introduction_to_Schenkerian_Analysis}.
+
 %%%%%%%%%%%%%%%%%%

### 2023-06-08 introduction/Subsections/Objectives.tex
Updates from Overleaf

@@
 
-The study aims to develop a unified numerical understanding (or embedding \footnote{A learned representation or embedding is a numerical output -usually a fixed-size vector- produced by a machine-learning model from a low-level input.
+The study aims to develop a unified numerical understanding (or embedding \footnote{A learned representation or embedding is a numerical output -usually a fixed-size vector- produced by a machine-learning model.
 Good representations should be versatile across various tasks and require limited supervision \cite{Turian2022HEAR:Representations}.}) for a music piece that integrates high-level elements like melody contour, harmony relationships, and other comprehensive components such as the relationships between elements unfolding through time, arranging the embedding space to emphasize the clustering of these sophisticated musical content without considering sonic qualities or attributes.

### 2023-06-08 introduction/Subsections/Previous work.tex
Updates from Overleaf

@@
 
-Recent advancements in neural networks have enabled the development of low-dimensional embeddings which encapsulate critical musical attributes, thus facilitating the computation of diverse task-specific elements.
+Prior research has underlined the importance of choosing audio features for effectively identifying and labeling distinct music segments in music segmentation.
+However, acquiring music segment annotation data for learning feature transformations has been a limiting factor due to its time-consuming and costly nature.
+To overcome this, studies have employed unsupervised deep learning, using abundantly available music audio.
+Combining spectrograms with self-similarity lag matrices has captured a broader spectrum of structural information.
+This approach has significantly improved the performance of segmentation algorithms, achieving state-of-the-art results.
+Additionally, strategies considering the hierarchical nature of the structural organization, utilizing two-level annotations of main and secondary boundaries, have further enhanced boundary recognition performance \cite{unsupervisedlearndeepfeat, GrillMUSICANNOTATIONS, Hernandez-Olivan2021MusicFeatures, SalamonDeepSegmentation}.
 
-Such tasks encompass developing an audio embedding method that excels across a wide array of applications without fine-tuning \cite{Turian2022HEAR:Representations}, deploying deep audio embeddings for multi-level music segmentation \cite{SalamonDeepSegmentation}, improving environmental sound classification \cite{Kim2020OneStrategies}, enhancing vocal-centric music tasks via cross-domain audio embedding \cite{Kim2021LearningLoss}, combining task-specific and pre-trained features for improved audio classification \cite{Hung2022Feature-informedClassification}, creating a music similarity search engine tailored for video producers \cite{epidemic}, enhancing Music Emotion Recognition (MER) performance \cite{KohComparisonRecognition}, investigating the efficacy of speaker recognition pre-trained model embeddings \cite{lightweight}, embedding songs for similarity comparison via artist identification \cite{contentmusicsimtriplet2020}, solving the cross-modal text-to-music retrieval issue \cite{WonEmotionStories}, and facilitating automated music rearrangement \cite{Stoller2018IntuitiveTransitions, Plachouras2023MusicSegmentation}.
-
-Furthermore, deep learning applications in music often overlook the intermediate-level musical patterns, analogous to the 'mesostructure' in music and the middle ground in Schenkerian analysis.
-As highlighted by \cite{Mesostructures2023}, addressing this mesostructure could significantly improve tasks like music analysis, composition, and retrieval by providing a more holistic understanding of music, comparable to insights from Schenkerian analysis \cite{Introduction_to_Schenkerian_Analysis}.
+Aside from the music structure applications, recent advancements in neural networks have enabled the development of low-dimensional embeddings which encapsulate critical musical attributes, thus facilitating the computation of diverse task-specific elements.
+Such tasks encompass developing an audio embedding method that excels across a wide array of applications without fine-tuning \cite{Turian2022HEAR:Representations}, improving environmental \cite{Kim2020OneStrategies} sound classification \cite{CramerLOOKEMBEDDINGS}, enhancing vocal-centric music tasks via cross-domain audio embedding \cite{Kim2021LearningLoss}, combining task-specific and pre-trained features for improved audio classification \cite{Hung2022Feature-informedClassification}, creating a music similarity search engine tailored for video producers \cite{epidemic}, enhancing Music Emotion Recognition (MER) performance \cite{KohComparisonRecognition}, investigating the efficacy of speaker recognition pre-trained model embeddings \cite{lightweight}, embedding songs for similarity comparison via artist identification \cite{contentmusicsimtriplet2020}, solving the cross-modal text-to-music retrieval issue \cite{WonEmotionStories}, and facilitating automated music rearrangement \cite{Stoller2018IntuitiveTransitions, Plachouras2023MusicSegmentation}.
 
@@
 
-However, it is still an open question whether a general-purpose audio representation can effectively mimic human hearing \cite{Turian2022HEAR:Representations}.
-
-Considering their proven efficacy in existing literature and their potential for transfer learning, it appears promising to further investigate deep audio embeddings for Music Information Retrieval (MIR) downstream tasks.
+Considering their proven promising efficacy in the existing literature and their potential for transfer learning, it appears appealing to investigate further deep audio embeddings for MIR downstream tasks.
+Especially as it is still an open question whether a general-purpose audio representation can effectively mimic human hearing \cite{Turian2022HEAR:Representations} even though some approaches achieved to generalize up to fourteen music understanding tasks \cite{Li2023MERT:Training}.

### 2023-06-08 methods/subsections/deep learning.tex
Updates from Overleaf

--- 2023-05-25 methods/subsections/deep learning.tex
@@
-\section{Deep Learning Modeling}
+\section{Deep Learning modeling}
 

### 2023-06-08 methods/subsections/implementation.tex
Updates from Overleaf

@@
 Contrastive Learning of Musical Representations (CLMR) learns valuable, discriminative music representations without explicit labels by contrasting positive augmentations of a musical piece against negative ones \cite{CLMR2021}.
-CLMR works under a machine learning subset called Self-Supervised Learning (SSL), where models self-learn from unlabeled data, creating their supervisory signal \cite{audioselfsupsurvey}.
+CLMR works under a machine learning subset called self-supervised learning (SSL), where models self-learn from unlabeled data, creating their supervisory signal \cite{audioselfsupsurvey}.
 This mimics human learning from observations and interactions, transforming unsupervised problems into supervised ones by auto-generating labels.
@@
 Then, training by minimizing a contrastive loss function encourages the model to produce similar representations for positive pairs and dissimilar representations for antagonistic pairs.
+
+Although SSL has been proven effective in speech and audio, its
+application to music audio has yet to be thoroughly explored. This is primarily due
+to the distinctive challenges associated with modeling musical knowledge, particularly tonal and pitched characteristics of music \cite{Li2023MERT:Training}.
 
@@
 AdamW adeptly balances the learning rate across network weights, providing an efficient strategy for weight decay management by isolating it from gradient updates.
-
-\subsubsection{Learning rate}
 
@@
 
-\subsubsection{Batch normalization}
-
 In implementing the batch normalization step, it is necessary to standardize the audio lengths across all elements in the minibatch.

### 2023-06-08 results/subsections/tables.tex
Updates from Overleaf

@@
 This metric, ranging from 0 to 1, represents the harmonic mean of precision and recall, providing a balanced view of under-segmentation and over-segmentation.
-Precision calculates the percentage of correctly detected boundaries, whereas recall assesses the percentage of actual boundaries detected correctly \cite{Turnbull2007ABOOSTING}.
+Given the potential inaccuracies in human annotations and prediction errors, the F-measure tolerates minor discrepancies between predicted and ground truth boundaries.
+This tolerance level can be adjusted, enabling the metric to consider a predicted boundary as correct if it's within the set tolerance window of a ground truth boundary \cite{Turnbull2007ABOOSTING}.
 The F-measure is calculated as follows:
@@
 \end{tabularx}
-\caption[Baseline.
-State of the art table.]{Your Caption.
-Given the potential inaccuracies in human annotations and prediction errors, the F-measure tolerates minor discrepancies between predicted and ground truth boundaries.
-This tolerance level can be adjusted, enabling the metric to consider a predicted boundary as correct if it's within the set tolerance window of a ground truth boundary.}
+\caption[Baseline. State of the art table.]{Your Caption.}
 \label{tab:my_label}

### 2023-06-08 abstract/abstract.tex
Updates from Overleaf

@@
 
-In collaboration with Epidemic Sound AB and the Music Technology Group (MTG) at Universitat Pompeu Fabra (UPF), we used self-supervised contrastive learning to uncover the underlying structure of Western tonal music.
-We applied deep convolutional neural networks and a triplet loss function, identifying abstract and semantic musical elements without relying on their sonic qualities.
-This way, we replaced traditional acoustic features with deep audio embeddings, paving the way for high-level, sound-agnostic, and content-sensitive music representation.
+In collaboration with Epidemic Sound AB and the Music Technology Group (MTG) at Universitat Pompeu Fabra (UPF), we used self-supervised contrastive learning to uncover the underlying structure of Western tonal music by learning deep audio features to improve unsupervised music boundary detection.
+We applied deep convolutional neural networks and a triplet loss function to identify abstract and semantic musical elements without relying on their sonic qualities.
+This way, we replaced traditional acoustic features with deep audio embeddings, paving the way for high-level, sound-agnostic, and content-sensitive music representation for boundary detection.
 
@@
 This novel approach aims to reconcile music and machine learning, enhancing machine listening models' efficacy.
+
 Preliminary results suggest that our musically-informed technique has significant potential for boundary detection tasks and possibly nearly all MIR downstream tasks that are not purely sonic-based.

### 2023-06-08 future work/future work.tex
Updates from Overleaf

@@
 
-Listening evaluation
-2D or 3D latent space visualization as per \ref{fig:manifold}
+Visual and listening evaluation: 2D or 3D latent space visualization as per \ref{fig:manifold}.
+Arranging the embedding space in a visual display to evaluate the clustering of this sophisticated musical content to see to what extent they consider sonic attributes.
 

### 2023-06-08 introduction/Subsections/Objectives.tex
Updates from Overleaf

--- 2023-05-16 introduction/Subsections/Objectives.tex
@@
 
-This study explores music's high-level tonal structure by leveraging self-supervised deep neural networks, inductive bias, and aural skills to learn and analyze music embeddings applicable to subsequent MIR tasks.
+Can we learn deep audio embeddings from reordering and scrambling sequences of musical information and adding audio effects to improve unsupervised music boundary detection?
 
-The study aims to develop a unified embedding, $e(M)$, for a music piece $M$ that integrates high-level elements like melody contour, harmony relationships, and other comprehensive components, arranging the embedding space to emphasize clustering of these sophisticated musical content without any consideration for sonic quality attributes.
-Utilizing a blend of Music Information Retrieval (MIR) computational methodologies and musicological perspectives, the research will explore musical compositions from various styles and genres.
+This study explores music's high-level tonal structure by leveraging self-supervised deep neural networks, inductive bias, and aural skills to learn and analyze music embeddings applicable to subsequent MIR tasks, in our particular case, music boundary detection.
+
+The study aims to develop and learn a unified numerical understanding (or embedding \footnote{A learned representation or embedding is a numerical output -usually a fixed-size vector- produced by a machine-learning model.
+Good representations should be versatile across various tasks and require limited supervision \cite{Turian2022HEAR:Representations}.}) for a music piece that integrates high-level elements like melody contour, harmony relationships, and other comprehensive components such as the relationships between elements unfolding through time.
+
+The research will utilize MIR computational methodologies and musicological perspectives to explore musical compositions from various styles and genres.
 

### 2023-06-08 methods/subsections/implementation.tex
Updates from Overleaf

@@
 
-Conventional transformations, such as log-scaled Mel spectrograms or Mel Frequency Cepstral Coefficients, capture key features but may obscure some information inherent in raw audio data.
+Features derived from raw audio often lack the interpretability of traditional ones \cite{Schindler2020DeepTutorial}.
+Hence, the choice of input data depends on the specific task, available computational resources, and the balance between data preservation and computational efficiency.
 
-Raw audio data offers unique advantages.
-Primarily, it ensures the retention of the original signal, which could reveal novel findings, and facilitates the direct extraction of features through advanced deep learning models \cite{learning}.
+While previous studies have used CNNs and various features as input like Mel-Scaled Log-magnitude Spectograms (MLS), Self-Similarity Matrices (SSM), and Self-Similarity Lag Matrices (SSLM) as inputs \cite{Hernandez-Olivan2021MusicFeatures}, raw audio data offers unique advantages: it ensures the retention of the original signal, which could reveal novel findings, and facilitates the direct extraction of features through advanced deep learning models \cite{learning}.
 However, it is not without challenges: high sample rates result in high dimensionality, demanding substantial computational resources.
 Additionally, raw audio is noise-sensitive, complicating the extraction process.
-Features derived from raw audio also often lack the interpretability of traditional ones \cite{Schindler2020DeepTutorial}.
-Hence, the choice of input data depends on the specific task, available computational resources, and the balance between data preservation and computational efficiency.
 
-Time-domain processing, a feature of our experiments, naturally handles temporal patterns and sequences in data, thereby avoiding windowing artifacts.
+Time-domain processing naturally handles temporal patterns and sequences in data, thereby avoiding windowing artifacts.
 Although Mel-spectrogram-based methods are effective for various audio-related machine learning tasks, their limitations lie in representing perceptual similarity.
@@
 Yet, the complexity of human auditory perception—encompassing temporal patterns, phase relationships between frequencies, and higher-level musical structures—means that musically similar sounds can have distinct spectrograms.
-This discrepancy implies that using spectrogram distance alone for measuring high-level music similarity may not always align with human perceptions \cite{Kim2020OneStrategies}\cite{Mesostructures2023}.
+This discrepancy implies that using spectrogram distance alone for measuring high-level music similarity may not always align with human perceptions \cite{Kim2020OneStrategies, Mesostructures2023}.
 
@@
 
-The positive image in our study must preserve its intelligible content when subjected to transformations, regardless of alterations in sonic qualities.
+The positive image in every triplet of input data must preserve its intelligible content when subjected to transformations, regardless of alterations in sonic qualities.
 Maintaining the temporal structure and meaningfulness of the content allows it to present musical elements identical or strikingly similar to the original track.
 
-While we have experimented with helpful audio augmentation tools such as \cite{Spijkervet2021Spijkervet/torchaudio-augmentations:V1.0} and \cite{Kharitonov2020DataDomain}, the specific requirements of our experiments necessitated the development of our own transformation chain using \textit{torchaudio's} \cite{Yang2021TorchAudio:Processing} implementation of \textit{SoX} \cite{sox}: given an anchor audio signal $A[n]$, we generate a positive signal $P[n]$ by applying a series of amplitude, time-domain, frequency-domain, modulation, reverberation, and nonlinear effects with additive noise on top of it.
+While we have experimented with helpful audio augmentation tools \cite{Spijkervet2021Spijkervet/torchaudio-augmentations:V1.0, Kharitonov2020DataDomain}, the specific requirements of our experiments necessitated the development of our transformation chain using \textit{torchaudio}'s \cite{Yang2021TorchAudio:Processing} implementation of \textit{SoX} \cite{sox}: given an anchor audio signal $A[n]$, we generate a positive signal $P[n]$ by applying a series of amplitude, time-domain, frequency-domain, modulation, reverberation, and nonlinear effects with additive noise on top of it.
 
-In this analysis, various parameters represent different effects on the signal.
-We use $g \in [-12, 0]$ for gain, $\Delta p \in [-1200, 1200]$ for pitch shift, $h_R[n]$ for the reverb impulse response, $h_C[n]$ for the chorus impulse response, $d \in [0, 30]$ for overdrive, $\alpha \in [0.9, 1.1]$ for speed change, $\beta \in [0.9, 1.1]$ for stretch factor, $f_m \in [0.1, 100]$ for tremolo's modulation frequency, and $d_m \in [1, 101]$ for tremolo's depth.
-Each effect is applied aggressively but does not disrupt the high-level musical content.
-
-\textbf{Amplitude effects}, like gain, modify the signal's overall amplitude with a constant factor $g$.
+\textbf{Amplitude effects}, like gain, modify the signal's amplitude with a constant factor $g$. We use $g \in [-12, 0]$.
 
 \textbf{Time-domain effects} such as speed change and stretch alter the signal's playback speed and duration without changing its pitch, respectively.
-The speed and stretch factors are $\alpha$ and $\beta$.
+The speed and stretch factors are $\alpha \in [0.9, 1.1]$ for speed change and $\beta \in [0.9, 1.1]$ for the stretch factor.
 
-\textbf{Frequency-domain effects} adjust the frequency content or pitch of the signal, as in pitch shifting, which alters the pitch by $\Delta p$.
+\textbf{Frequency-domain effects} adjust the frequency content or pitch of the signal, as in pitch shifting, which alters the pitch by $\Delta p \in [-1200, 1200]$.
 
-\textbf{Nonlinear effects} such as overdrive add harmonic distortion using the parameter $d$.
+\textbf{Nonlinear effects} such as overdrive add harmonic distortion using the parameter $d \in [0, 30]$ for overdrive
 
 \textbf{Modulation effects}, including chorus and tremolo, use a control signal or low-frequency oscillator.
-The specified ranges determine the chorus parameters, and the tremolo's amplitude modulation frequency and depth are $f_m$ and $d_m$.
+The specified ranges determine the chorus parameters and the tremolo's amplitude modulation frequency and depth $f_m \in [0.1, 100]$ for the tremolo's modulation frequency and $d_m \in [1, 101]$ for the tremolo's depth
 
 \textbf{Reverberation effects} simulate physical space's acoustic reflections and reverberations, like reverb that applies an impulse response $h_R[n]$.
+
 Finally, \textbf{Noise effects} add a noise signal $N[n]$ with a signal-to-noise ratio (SNR) in the range $[12, 100]$.
@@
 The minimum duration $t_{min}$ is set to 0.05 seconds, and the maximum duration $t_{max}$ is set to 1 second.
-This range is chosen thoughtfully to strike a balance between the two factors.
-On the one hand, it is above the just noticeable difference (JND) threshold, the smallest change in a stimulus that can be perceived.
+This range is chosen thoughtfully to strike a balance between two factors: on the one hand, it is above the just noticeable difference (JND) threshold, the smallest change in a stimulus that can be perceived.
 On the other hand, it is short enough to maintain a reasonably-sized window to avoid discernible musical content \cite{Fastl2007Just-NoticeableChanges}.
@@
 
-\item Concatenate the shuffled audio chunks to generate the negative signal:
+\item We finally concatenate the shuffled audio chunks to generate the negative signal:
 \begin{equation}\label{eq:negative_signal}

### 2023-06-08 results/subsections/tables.tex
Updates from Overleaf

@@
 \toprule
-\thead{\centering\textbf{Year, Authors, Ref}} & \thead{\centering\textbf{Algorithm}} & \thead{\centering\textbf{Input}} & \thead{\centering\textbf{Method}} & \thead{\centering\textbf{F-measure}} \\
+\thead{\centering\textbf{Authors [Ref], Year}} & \thead{\centering\textbf{Input}} & \thead{\centering\textbf{Method}} & \thead{\centering\textbf{F-measure}} \\
 \midrule
 \addlinespace
-2012, Kaiser et al., [27]& KSP2 & SSM & Novelty measure  & 0.286 \\
+Kaiser et al. \cite{27}, 2012 & SSM & Novelty measure  & 0.286 \\
 \addlinespace
-2013, McFee \& Ellis, [20] & MP2 & MLS & Fisher’s Linear Discriminant  & 0.317 \\
+McFee \& Ellis \cite{20}, 2013 & MLS & Fisher’s Linear Discriminant  & 0.317 \\
 \addlinespace
-2014, Nieto \& Bello, [28] & NB1 & MFCCs, chromas & Checkerboard-like kernel  & 0.299 \\
+Nieto \& Bello \cite{28}, 2014 & MFCCs, chromas & Checkerboard-like kernel  & 0.299 \\
 \addlinespace
-2015, Cannam et al., [29] & CC1 & Timbre-type histograms & HMM  & 0.213 \\
+Cannam et al. \cite{29}, 2015 & Timbre-type histograms & HMM  & 0.213 \\
 \addlinespace
-2016, Nieto, [30] & ON2 & Constant-Q Transform Spectrogram & Linear Discriminant Analysis  & 0.299 \\
+Nieto \cite{30}, 2016 & Constant-Q Transform Spectrogram & Linear Discriminant Analysis  & 0.299 \\
 \addlinespace
-2017, Cannam et al., [29] & CC1 & Timbre-type histograms & HMM  & 0.212 \\
+Cannam et al. \cite{29}, 2017 & Timbre-type histograms & HMM  & 0.212 \\
 \addlinespace
-2007, Turnbull et al., [19] & - & MFCCs, chromas, spectrogram & Boosted Decision Stump  & 0.378 \\
+Turnbull et al. \cite{Turnbull2007ABOOSTING}, 2007 & MFCCs, chromas, spectrogram & Boosted Decision Stump  & 0.378 \\
 \addlinespace
-2011, Sargent et al., [34] & - & MFCCs, chromas & Viterbi  & 0.356 \\
+Sargent et al. \cite{34}, 2011 & MFCCs, chromas & Viterbi  & 0.356 \\
 \addlinespace
-2014, Ullrich et. al, [22] & - & MLS & CNN  & 0.465 \\
+Ullrich et. al \cite{22}, 2014 & MLS & CNN  & 0.465 \\
 \addlinespace
-2015, Grill \& Schlüter, [4] & - & MLS, SSLMs & CNN  & 0.523 \\
+Grill \& Schlüter \cite{4}, 2015 & MLS, SSLMs & CNN  & 0.523 \\
 \addlinespace
-2015, Grill \& Schlüter, [5] & - & MLS, PCPs, SSLMs & CNN  & 0.508 \\
+Grill \& Schlüter \cite{GrillMUSICANNOTATIONS}, 2015 & MLS, PCPs, SSLMs & CNN  & 0.508 \\
 \addlinespace
-2017, Hadria \& Peeters, [35] & - & MLS, SSLMs & CNN  & 0.291 \\
+Hadria \& Peeterss \cite{35}, 2017 & MLS, SSLMs & CNN  & 0.291 \\
 \bottomrule

### 2023-06-09 abstract/abstract.tex
Updates from Overleaf

@@
 While it didn't outperform state-of-the-art results, it showed very competitive results and room for improvement.
-Consequently, music-motivated audio embeddings appear promising and potentially adaptable to other tasks constrained by data scarcity.
+
+While music-motivated audio embeddings appear promising and potentially adaptable to other tasks constrained by data scarcity, the question remains if such general-purpose audio representation
+can mimic human hearing.
 

### 2023-06-09 discussion/discussion.tex
Updates from Overleaf

@@
 In this work, we introduced a method to uncover underlying high-level musical
-content in the temporal domain by leveraging self-supervised deep neural networks, inductive bias, and aural skills to learn music latent representations with applications to MIR downstream tasks.
+content in the temporal domain by leveraging self-supervised deep neural networks, inductive bias, and aural skills to learn music latent representations with applications to music boundary detection.
 Building on existing approaches and architectures, we replaced traditional features with deep embeddings trained to represent high-level musical content information.

### 2023-06-09 evaluation/evaluation.tex
Updates from Overleaf

@@
 
-\section{Music Structure Analysis as downstream task}
+\section{Music boundary detection as downstream task}
 
-While the usefulness of deep audio embeddings can be evaluated in countless downstream tasks, we have chosen Music Structure Analysis (MSA) for its popularity, complexity, and product-compelling nature.
+While the usefulness of deep audio embeddings can be evaluated in countless downstream tasks \cite{Li2023MERT:Training, Kim2020OneStrategies}, we have chosen music boundary detection, a subset of Music Structure Analysis (MSA) for its popularity, complexity, and product-compelling nature.
 This interdisciplinary field aims to understand the structure of music \cite{Nieto2020Audio-BasedApplications}.
@@
 
-\section{The \textit{embeddiogram}, an audio feature embedding representation}
+\section{The \textit{embeddiogram}, a deep audio feature representation}
 
@@
 
-\item \textbf{Process each window}: Each window of audio data is processed independently, passed through the pre-trained neural network model and transformed into an embedding vector.
+\item \textbf{Process each window}: Each window of audio data is processed independently, passed through the pre-trained neural network model, and transformed into an embedding vector.
 Formally, for each window $w_i$ of audio data, we have:
@@
 
-\item \textbf{Normalize the \textit{embeddiogram}}: The \textit{embeddiogram} is normalized to have a minimum value of 0 and a maximum value of 1. The normalization process is given by:
+\item \textbf{Normalize the \textit{embeddiogram}}: The \textit{embeddiogram} is normalized to have a minimum value of 0 and a maximum value of 1 per dimension. The normalization process is given by:
 \begin{equation}

### 2023-06-09 introduction/Subsections/Assumptions.tex
Updates from Overleaf

@@
 
-This thesis proposes the existence of high-level musical concepts, including melody, harmony, rhythm, form, motif, and counterpoint.
-These concepts, despite changes in sonic qualities, demonstrate enduring independence.
-Additionally, these elements are interactive, continually evolving within the musical context.
-This echoes the nature of the symbolic domain, such as sheet music, which retains its essence despite varied interpretations across diverse performances, instruments, and styles.
-While a single waveform might correspond to a finite set of sheet music representations encapsulating its musical components, one piece of music can be interpreted infinitely, varying by instruments, voices, tempos, and performance styles.
+This thesis posits that enduring, high-level musical elements persist regardless of sonic changes and constantly evolve within their context, mirroring the nature of sheet music's symbolic domain.
+A single waveform can correspond to a finite set of representations, but one music piece can yield infinite interpretations, varying by factors such as instruments and performance styles.
 
-Abstract high-level features can be discerned irrespective of the waveform or production style, providing an objective, comprehensive insight into the musical content of a composition.
-This approach is akin to analyzing sheet music to uncover its foundational behaviors.
+The premise of our work is that regardless of the waveform or production style, abstract high-level features can be discerned, offering objective and thorough insight into a composition's musical content, analogous to analyzing sheet music for its basic behaviors.
 
-These features enable listeners to identify and recreate musical structures by ear, fostering deeper engagement with music.
-Heuristics, mental shortcuts, or rules of thumb facilitate rapid comprehension of complex musical concepts, bringing underlying patterns and structures into focus.
+These characteristics aid listeners in recognizing and recreating musical structures, promoting deeper interaction with music.
+Mental shortcuts or heuristics enable a swift understanding of complex musical notions, revealing underlying patterns.
 
-For example, despite differences in cultural contexts, stylistic elements, time signatures, key signatures, and sonic properties, we propose a similarity between figures \ref{fig:mahler} and \ref{fig:giant_steps}.
-Both pieces exhibit the same musicological fingerprint, so to speak, derived from the envelope of their melodic and harmonic contours through non-diatonic major thirds.
+Despite differing cultural contexts, styles, time and key signatures, and sonic properties, we suggest a commonality between figures \ref{fig:mahler} and \ref{fig:giant_steps}.
+Both pieces display the same 'musicological fingerprint,' derived from their melodic and harmonic contour envelopes through non-diatonic major thirds.
 
 This concept aligns with the theories of Kurt Koffka, a founding member of the Gestalt school of psychology, who advocated for a holistic approach to understanding complex forms, as opposed to the structuralist practice of dissecting mental processes into their elemental components \cite{Koffka2013PrinciplesPsychology}.
-In the context of music, Gestalt psychology principles suggest our minds process auditory input similarly to visual input, by seeking patterns and structures.
+In the context of music, Gestalt psychology principles suggest our minds process auditory input similarly to visual input by seeking patterns and structures.
 This understanding significantly enhances the comprehension of cognitive processes in musical perception and organization, influencing music theory, cognition, and therapy \cite{Lerdahl1985AMusic}.

### 2023-06-09 methods/subsections/implementation.tex
Updates from Overleaf

@@
 
-\item We finally concatenate the shuffled audio chunks to generate the negative signal:
+\item We finally concatenate the shuffled audio chunks to generate the negative signal that will have similar production while the content is completely ruined:
 \begin{equation}\label{eq:negative_signal}
@@
 
-Again, the whole purpose of it is to disturb the time domain.
+The whole purpose of this process is to disturb the content unfolding in the time domain.
 

### 2023-06-09 introduction/Subsections/Previous work.tex
Updates from Overleaf

--- 2023-05-31 introduction/Subsections/Previous work.tex
@@
 
-Neural networks have recently facilitated the development of low-dimensional embeddings that capture essential musical features, enabling the computation of various task-specific aspects.
+Previous studies have highlighted the significance of selecting suitable audio features to distinguish and label unique music segments in music segmentation tasks.
+However, acquiring music segment annotation data for learning feature transformations presents a challenge due to its labor-intensive and expensive nature.
+Research has leveraged unsupervised deep learning to mitigate this, using readily available music audio.
+This methodology has significantly enhanced the efficacy of segmentation algorithms, yielding state-of-the-art results.
+Furthermore, strategies that recognize the hierarchical nature of the structural organization employing two-level annotations of primary and secondary boundaries have further augmented boundary detection performance \cite{unsupervisedlearndeepfeat, GrillMUSICANNOTATIONS, Hernandez-Olivan2021MusicFeatures, SalamonDeepSegmentation}.
 
-These aspects include the utilization of multi-level music segmentation through deep audio embeddings to replace manually engineered features \cite{SalamonDeepSegmentation}, the enhancement of environmental sound classification \cite{Kim2020OneStrategies}, the improvement of vocal-centric music tasks using cross-domain audio embedding \cite{Kim2021LearningLoss}, the enhancement of audio classification through a combination of task-specific and pre-trained features \cite{Hung2022Feature-informedClassification}, the creation of a music similarity search engine specifically for video producers \cite{epidemic}, the improved performance in Music Emotion Recognition (MER) tasks \cite{KohComparisonRecognition}, embedding songs for similarity comparison based on artist identification \cite{contentmusicsimtriplet2020}, the resolution of the cross-modal text-to-music retrieval problem \cite{WonEmotionStories}, and automated music rearrangement \cite{Stoller2018IntuitiveTransitions}\cite{Plachouras2023MusicSegmentation}.
+Apart from music structure applications, recent advances in neural networks have facilitated the generation of low-dimensional numerical representations that encapsulate key musical attributes.
+This development simplifies the computation of various task-specific elements.
+Such tasks encompass:
 
-On top of that and returning to musicological influences, the middle ground in Schenkerian analysis can be compared to the mesostructure in music.
-Analogous to the mesostructure, it represents the intermediate-level musical patterns that bridge the micro and macro structures.
-This element is often overlooked when applying deep learning to music.
-As emphasized by \cite{Mesostructures2023}, models that address this mesostructure level could significantly enrich tasks such as music analysis, composition, and retrieval, providing a more holistic understanding of music, similar to the insights gained from analyzing the middle-ground in Schenkerian analysis.
-\cite{Introduction_to_Schenkerian_Analysis}
+\begin{itemize}
+\item Developing an audio embedding method that excels across numerous applications without the need for fine-tuning \cite{Turian2022HEAR:Representations}
+\item Enhancing environmental sound classification \cite{Kim2020OneStrategies, CramerLOOKEMBEDDINGS}
+\item Improving vocal-centric music tasks via cross-domain audio embeddings \cite{Kim2021LearningLoss}
+\item Merging task-specific and pre-trained features to improve audio classification \cite{Hung2022Feature-informedClassification}
+\item Designing a music similarity search engine for video producers \cite{epidemic}
+\item Augmenting Music Emotion Recognition (MER) performance \cite{KohComparisonRecognition}
+\item Investigating the efficacy of speaker recognition pre-trained model embeddings \cite{lightweight}
+\item Embedding songs for similarity comparison via artist identification \cite{contentmusicsimtriplet2020}
+\item Addressing the cross-modal text-to-music retrieval issue \cite{WonEmotionStories}
+\item Facilitating automated music rearrangement \cite{Stoller2018IntuitiveTransitions, Plachouras2023MusicSegmentation}
+\end{itemize}
 
-Moreover, deep audio embeddings offer the advantage of transferability.
-Once trained, these latent representations can be utilized as a starting point for various other tasks, thus saving computational resources and time compared to training a model from scratch \cite{HamelTransferSimilarity}.
+Moreover, deep audio embeddings provide the advantage of transferability, serving as a basis for multiple tasks.
+This approach conserves computational resources and time compared to training a model from scratch \cite{HamelTransferSimilarity}.
 
-Given their demonstrated success in the literature and their potential for transfer learning, exploring deep audio embeddings for MIR downstream tasks seems worthwhile.
+Given their demonstrated effectiveness in existing literature and their potential for transfer learning, deep audio embeddings hold substantial promise for MIR downstream tasks, specifically boundary detection.
+Nevertheless, it remains uncertain whether a general-purpose audio representation can effectively replicate human hearing \cite{Turian2022HEAR:Representations}, even though some techniques have managed to generalize across up to fourteen music understanding tasks \cite{Li2023MERT:Training}.

### 2023-06-09 methods/subsections/implementation.tex
Updates from Overleaf

@@
 
-Our approach could be broadly categorized as cognitive modeling, as it strives to mimic human cognitive processes and problem-solving through a computerized model.
-We champion exposure-based learning in music and active engagement with musical styles, genres, techniques, and learning methods to foster well-rounded musical proficiency and efficient performance with novel data in practical applications.
+Our approach falls broadly under cognitive modeling, which seeks to simulate human cognitive processes and problem-solving through a computerized model.
+We advocate for exposure-based learning in music, encouraging active engagement with various musical styles, genres, techniques, and learning methods.
+This approach promotes comprehensive musical proficiency and efficient performance when encountering novel data in practical applications.
 
-\subsection{Contrastive Learning of Musical Representations}
+According to Piaget's theory of cognitive development, children gain knowledge through sensory experiences and gradually develop abstract reasoning and schemas—basic cognitive structures \cite{Huitt2003PiagetsDevelopment}.
+These schemas evolve by incorporating new information through processes of assimilation and accommodation \cite{audioselfsupsurvey}.
 
-Piaget's theory of cognitive development suggests children acquire knowledge through sensory experiences, gradually developing abstract reasoning and schemas—basic cognitive structures \cite{Huitt2003PiagetsDevelopment}.
-These schemas evolve by integrating new information through assimilation and accommodation \cite{audioselfsupsurvey}.
+In pattern recognition, models are designed to exhibit robustness against known invariances—transformations of input data—thereby ensuring consistent output.
+Interestingly, even unknown invariances not explicitly considered in the model's design can be accommodated due to the model's inherent learning capacity.
 
-In pattern recognition, models are designed to be robust against known invariances—input data transformations—allowing consistent output.
-Conversely, unknown invariances not considered in the model's design can still be handled due to its learning capacity.
+Contrastive Learning of Musical Representations (CLMR) is a method that learns valuable, discriminative music representations without explicit labels by contrasting positive augmentations of a musical piece against negative ones \cite{CLMR2021}.
+CLMR falls under a subset of machine learning called self-supervised learning (SSL) \cite{Balestriero2023ALearning}, where models learn independently from unlabeled data to create their supervisory signals \cite{audioselfsupsurvey}.
+This method resembles how humans learn from observations and interactions, turning unsupervised problems into supervised ones by auto-generating labels.
+Benefits of SSL include reduced dependence on labeled data, which contributes to more robust and generalizable data representations.
 
-Contrastive Learning of Musical Representations (CLMR) learns valuable, discriminative music representations without explicit labels by contrasting positive augmentations of a musical piece against negative ones \cite{CLMR2021}.
-CLMR works under a machine learning subset called self-supervised learning (SSL), where models self-learn from unlabeled data, creating their supervisory signal \cite{audioselfsupsurvey}.
-This mimics human learning from observations and interactions, transforming unsupervised problems into supervised ones by auto-generating labels.
-The benefits of SSL include reduced reliance on labeled data, making data representation more robust and generalizable.
+The methodology of CLMR involves generating different augmentations of the same musical piece to serve as positive pairs while using other pieces as antagonistic pairs.
+The training process, which minimizes a contrastive loss function, encourages the model to produce similar representations for positive and dissimilar ones for antagonistic pairs.
 
-The CLMR methodology involves creating different augmentations of the same musical piece as positive pairs and using others as antagonistic pairs.
-Then, training by minimizing a contrastive loss function encourages the model to produce similar representations for positive pairs and dissimilar representations for antagonistic pairs.
-
-Although SSL has been proven effective in speech and audio, its
-application to music audio has yet to be thoroughly explored. This is primarily due
-to the distinctive challenges associated with modeling musical knowledge, particularly tonal and pitched characteristics of music \cite{Li2023MERT:Training}.
+Although SSL has proven effective in speech and audio, its application to music audio remains relatively unexplored.
+This is primarily due to the unique challenges associated with modeling musical knowledge, especially when it comes to music's tonal and pitched characteristics \cite{Li2023MERT:Training}.
 
@@
 
-\textbf{Amplitude effects}, like gain, modify the signal's amplitude with a constant factor $g$. We use $g \in [-12, 0]$.
+\textbf{Amplitude effects}, we use gain to modify the signal's amplitude with a constant factor $g \in [-12, 0]$.
 

### 2023-06-09 evaluation/evaluation.tex
Updates from Overleaf

@@
 All the evaluation metrics have been computed using the mir-eval package \cite{RaffelMir_eval:METRICS}.
-
-\subsection{SALAMI dataset}
-
-SALAMI (Structural Analysis of Large Amounts of Music Information) aims to conduct massive structural analyses of different types of music \cite{Smith2011DESIGNANNOTATIONS}.
-The project covers diverse music, from Western pop to Indian classical and from live to studio recordings.
-
-The authors propose a unique music analysis approach that segments pieces into sections rather than traditional forms.
-Their method combines perceptual, functional, and transcription analyses, considers music's hierarchical nature, and uses markers to determine analysis timescales.
-While providing a comprehensive investigation, each analysis approach has limitations in accurately reflecting musical structure, labeling identical or different music sections, and capturing the complete structural framework.
-This innovative approach aims for a more nuanced, holistic music analysis.
 

### 2023-06-09 results/subsections/tables.tex
Updates from Overleaf

@@
+SALAMI (Structural Analysis of Large Amounts of Music Information) is a project aiming to carry out extensive structural analyses on a wide variety of music, from Western pop to Indian classical, and from live to studio recordings \cite{Smith2011DESIGNANNOTATIONS}.
+Instead of traditional forms, the authors segment pieces into sections, combining perceptual, functional, and transcription analyses.
+Despite limitations, this approach offers a holistic and nuanced perspective on music structure.
+
 METRICS
@@
 \end{tabularx}
-\caption[Baseline. State of the art table.]{Your Caption.}
+\caption[Baseline. State of the art table.]{Your Caption.
+
+SALAMI dataset
+
+}
 \label{tab:my_label}

### 2023-06-10 evaluation/evaluation.tex
Updates from Overleaf

@@
 
-The \textit{embeddiogram} is derived by applying our pre-trained neural network model to sliding windowed segments across the audio signal, generating a sequence of embedding vectors.
+The \textit{embeddiogram}, a deep audio feature representation, is derived by applying our pre-trained neural network to sliding windowed segments across the audio signal, generating a sequence of embedding vectors.
 These relatively low-dimensional embedding vectors collectively form a two-dimensional description of the audio signal's musical content.
@@
 Below is a detailed explanation of how we compute the \textit{embeddiogram} from a given audio signal of length $N$.
-This process comprises loading the audio data, slicing the audio data into windowed segments, processing each window using a pre-trained model to produce an embedding, collecting and stacking these embeddings, and finally normalizing the \textit{embeddiogram}.
+This process comprises loading the audio data, slicing the audio data into windowed segments, processing each window using a pre-trained model to produce an embedding per window/time-frame, collecting and stacking these embeddings, and finally normalizing the resulting matrix or as we like to call it, \textit{embeddiogram}.
 

### 2023-06-10 introduction/Subsections/Motivation.tex
Updates from Overleaf

--- 2023-06-03 introduction/Subsections/Motivation.tex
@@
 
-Driven by personal, academic, and industrial motivations, this thesis is a product of a collaboration between \href{https://www.epidemicsound.com/}{Epidemic Sound} (ES) and the \href{https://www.upf.edu/web/mtg}{Music Technology Group} (MTG) at Universitat Pompeu Fabra.
-ES, a leading Swedish company, holds and curates an expansive global library of 40,000+ royalty-free music tracks and 90,000+ sound effects.
-MTG, based in Barcelona, Spain, excels in developing innovative technologies related to sound and music, such as music information retrieval, digital signal processing, interactive music systems, and computational musicology.
+This thesis, a collaboration between \href{https://www.epidemicsound.com/}{Epidemic Sound} (ES) and the \href{https://www.upf.edu/web/mtg}{Music Technology Group} (MTG) at Universitat Pompeu Fabra (UPF), has been driven by personal, academic, and industrial motivations.
+ES, a Swedish company, curates a vast global library of over 40,000 royalty-free music tracks and 90,000+ sound effects.
+Based in Barcelona, MTG specializes in innovative sound and music technologies, such as information retrieval, digital signal processing, interactive music systems, and computational musicology.
 
-This partnership seeks to enhance our understanding of music's fundamental structures, potentially improving ES's technical products, services, and advancements in Music Information Retrieval (MIR) research.
+The collaboration aims to deepen our understanding of music's fundamental structures, which could enhance ES's technical offerings and further advancements in music information retrieval (MIR) research.
 
-As a music enthusiast, musician, and scholar, I am deeply committed to exploring the foundational elements of musical composition, investigating various creation techniques, and deciphering their intricate relationships.
-This passion drives my endeavor to extract valuable information embedded within music across any domain, particularly in audio and symbolic domains.
+As a musician, enthusiast, and scholar, my passion for music has driven me to investigate the foundational elements of musical composition, various creation techniques, and their intricate relationships.
+I am dedicated to extracting valuable information embedded within music across all domains, with a particular focus on audio and symbolic.
+Musicians who endeavor to bridge the gap and uncover musical truths within the tonal paradigm, such as Heinrich Schenker \cite{Komar1959SchenkersStructure}, or those who challenge it, like Arnold Schoenberg \cite{Samson1974SchoenbergsMusic}, George Russell \cite{LydianRussell}, and Ernst Levy \cite{LevyAHarmony}, have been a continual source of inspiration.
+They aim to identify abstract concepts that reinforce or disrupt the tonal foundation, advancing the tonal landscape and providing a solid base for musicians' growth, development, and understanding of tonal and atonal paradigms.
 
-We are witnessing significant breakthroughs in AI research \cite{Vaswani2017AttentionNeed}, building on the theoretical foundations of pioneers such as Alan Turing and Claude Shannon.
-These advancements have resulted in the widespread application of AI in popular products \cite{OpenAI2023GPT-4Report}, prompting researchers and corporations to stay informed and contribute to this rapidly evolving field.
-The advent of self-supervised models that learn embedding spaces for retrieving musical content from audio signals presents fresh opportunities.
-By autonomously extracting high-level semantic information from raw audio data, these models could transform various facets of the music industry.
-In the industrial realm, these embedding spaces can be harnessed to devise valuable products and enrich user experiences for content creators, thereby fostering innovation and collaboration across the music industry.
+Advancements in AI research, building on the theoretical groundwork laid by pioneers such as Alan Turing and Claude Shannon, have led to significant breakthroughs \cite{Vaswani2017AttentionNeed}.
+With AI being applied broadly in popular products \cite{OpenAI2023GPT-4Report}, researchers and corporations alike must stay abreast of this rapidly evolving field.
+The emergence of self-supervised models capable of learning embedding spaces to retrieve musical content from audio signals presents new opportunities.
+These models, which autonomously extract high-level semantic information from raw audio data, can potentially transform multiple aspects of the music industry.
+Industrially, these embedding spaces can be used to devise innovative products, enhance user experiences for content creators, and stimulate innovation and collaboration across the industry.
 
-\subsection{About music aural skills and high-level perceptual concepts}
-
-While MIR research has traditionally focused on technical aspects, it may have overlooked other relevant domains, including perception, cognition, music theory, aural skills, musicology, and their subfields.
-Purely mathematical approaches may not always reflect how humans perceive music and may not capture the subtle variations in timing or harmonic relationships critical to musical perception.
-We argue that MIR research needs to incorporate a more balanced approach that considers the interdisciplinary nature of music and the importance of other domains beyond DSP.
-
-I have consistently been inspired by musicians and researchers who strive to bridge the gap and uncover musical ground truth within an existing tonal paradigm, such as Heinrich Schenker and his school of thought \cite{Komar1959SchenkersStructure}, and particularly by challenging it, exemplified by Arnold Schoenberg \cite{Samson1974SchoenbergsMusic}, George Russell \cite{LydianRussell} or Ernst Levy \cite{LevyAHarmony}.
-These approaches aim to identify abstract concepts that reinforce or disrupt the tonal foundation.
-Their ultimate goal is to advance the tonal landscape, providing musicians with a dependable playground for growth, development, and further understanding of tonal and atonal paradigms.
+Traditionally, MIR research has focused primarily on technical aspects, perhaps overlooking relevant areas such as perception, cognition, music theory, musicology, aural skills, and high-level perceptual concepts.
+Purely mathematical approaches may not accurately represent human music perception and could miss subtle variations in timing or harmonic relationships essential to the musical experience.
+Therefore, MIR research should strive for a balanced approach, recognizing the interdisciplinary nature of music and the importance of areas beyond digital signal processing.
 

### 2023-06-10 methods/subsections/implementation.tex
Updates from Overleaf

@@
 Contrastive Learning of Musical Representations (CLMR) is a method that learns valuable, discriminative music representations without explicit labels by contrasting positive augmentations of a musical piece against negative ones \cite{CLMR2021}.
-CLMR falls under a subset of machine learning called self-supervised learning (SSL) \cite{Balestriero2023ALearning}, where models learn independently from unlabeled data to create their supervisory signals \cite{audioselfsupsurvey}.
+CLMR falls under a subset of ML called self-supervised learning (SSL) \cite{Balestriero2023ALearning}, where models learn independently from unlabeled data to create their supervisory signals \cite{audioselfsupsurvey}.
 This method resembles how humans learn from observations and interactions, turning unsupervised problems into supervised ones by auto-generating labels.
@@
 Although SSL has proven effective in speech and audio, its application to music audio remains relatively unexplored.
-This is primarily due to the unique challenges associated with modeling musical knowledge, especially when it comes to music's tonal and pitched characteristics \cite{Li2023MERT:Training}.
+This is primarily due to the unique challenges of modeling musical knowledge, especially regarding music's tonal and pitched characteristics \cite{Li2023MERT:Training}.
 
@@
 
-For this task, a Triple Siamese Network is suggested, a model architecture proved efficient for music similarity retrieval tasks \cite{contentmusicsimtriplet2020}, intending to minimize the loss function between an anchor, positive, and negative sample, achieved through online triplet mining \cite{Sikaroudi2020OfflinePatches}.
-The overarching aim is to train a model in a self-supervised setting, which can effectively distinguish between similar and dissimilar samples.
+This work suggests employing a Triple Siamese Network, a model architecture known for its efficacy in music similarity retrieval tasks \cite{contentmusicsimtriplet2020}.
+The aim is to minimize the loss function between a triplet of anchor, positive, and negative samples, utilizing online triplet mining for optimizing memory resources \cite{Sikaroudi2020OfflinePatches}.
+This self-supervised learning (SSL) model aims to distinguish between similar and dissimilar samples effectively.
 
-A Siamese Network is a deep learning architecture introduced by Bromley and LeCun in the early 1990s \cite{Bromley1993SignatureNetwork}.
-This architecture is explicitly designed for tasks requiring comparing or assessing similarity between two input instances.
-It comprises two or more identical subnetworks connected in parallel and joined at the output layer.
-These subnetworks share the same architecture, weights, and hyperparameters, allowing more efficient memory usage and computational complexity.
+Introduced by Bromley and LeCun \cite{Bromley1993SignatureNetwork}, Siamese Networks are deep learning architectures designed for tasks requiring comparison or similarity assessment between instances.
+The architecture comprises identical subnetworks that share the same parameters, improving memory usage and computational efficiency.
+Rather than learning specific features of individual classes, they focus on a similarity metric, making them ideal for limited or imbalanced datasets.
+Each subnetwork processes an input independently, combining the outputs to yield a similarity score.
+Training with shared weights enables the model to learn invariant input representation, improving comparison efficiency.
+This is accomplished through specialized loss functions such as contrastive or triplet loss, aiming to minimize the distance between similar inputs and maximize it for dissimilar ones.
 
-Siamese Networks are especially effective for learning from limited or imbalanced datasets, as they focus on learning a similarity metric rather than the specific features of individual classes.
-Each subnetwork processes an input independently, and its outputs are then combined and further processed to yield a single similarity score.
-The shared weights during training enable the model to learn an invariant representation for the input instances, thereby enhancing its efficiency in comparing and contrasting them.
-To achieve this, Siamese Networks employ specialized loss functions, such as contrastive or triplet loss, which aim to minimize the distance between similar input pairs and maximize the distance between dissimilar ones.
+The Triple Siamese Network extends this architecture, comparing three input instances instead of two.
+It aims to learn an embedding space wherein similar instances are closer and dissimilar ones are distant.
+The inputs, consisting of an anchor, a positive instance (similar to the anchor), and a negative instance (dissimilar to the anchor), are processed by identical subnetworks sharing the same parameters.
 
-An extension of this architecture is the Triplet Siamese Network, which involves comparing three input instances instead of two.
-This network aims to learn an embedding space in which similar instances are close to each other and dissimilar instances are distant.
-The input to this network consists of an anchor, a positive instance (from the same class as the anchor), and a negative instance (from a different class).
-Each instance is processed by an identical subnetwork that shares its architecture, weights, and hyperparameters with the others.
-
-\subsubsection{Encoder: SampleCNN}
+\subsubsection{Encoder architecture: SampleCNN}
 
 The SampleCNN model \cite{Lee2018SampleCNN:Classification} is a CNN designed for raw waveform audio data, treating each audio sample as an independent channel and applying 1-dimensional convolution along the temporal axis.
-Its implementation is an adaptation of \cite{CLMR2021} using PyTorch \cite{Paszke2019PyTorch:Library} and PyTorch Lightning \cite{PyTorchDocumentation}.
+Its implementation is an adaptation of \cite{CLMR2021} using \textit{PyTorch} \cite{Paszke2019PyTorch:Library} and \textit{PyTorch Lightning} \cite{PyTorchDocumentation}.
 
@@
 \addlinespace
-Fully connected (representation layer) & 512 & 128 \\
+Fully connected or representation layer & 512 & 128 \\
 \bottomrule
@@
 
-The original model has been modified slightly to serve our specific needs: the output from the final convolutional layer is now subjected to an average pooling operation at the end.
+The original model has been modified slightly to serve our specific needs: the output from the final convolutional layer is now subjected to an average pooling operation.
 
@@
 
-In our research, we've employed the AdamW optimizer \cite{Loshchilov2017DecoupledRegularization}, an optimized variant of the widely-used Adam optimizer for training neural networks.
+We've employed the AdamW optimizer \cite{Loshchilov2017DecoupledRegularization}, an optimized variant of the widely-used Adam optimizer for training neural networks.
 AdamW adeptly balances the learning rate across network weights, providing an efficient strategy for weight decay management by isolating it from gradient updates.
@@
 It's a delicate balancing act— a high rate promises swift convergence with a risk of minimum overshoot, while a lower rate provides careful convergence but necessitates more iterations.
+Given that delicacy, we set it to a standard number broadly used in the literature.
 
@@
 
-Features derived from raw audio often lack the interpretability of traditional ones \cite{Schindler2020DeepTutorial}.
-Hence, the choice of input data depends on the specific task, available computational resources, and the balance between data preservation and computational efficiency.
+The choice of input data is guided by the task, computational resources, and the need to balance data retention with computational efficiency.
 
-While previous studies have used CNNs and various features as input like Mel-Scaled Log-magnitude Spectograms (MLS), Self-Similarity Matrices (SSM), and Self-Similarity Lag Matrices (SSLM) as inputs \cite{Hernandez-Olivan2021MusicFeatures}, raw audio data offers unique advantages: it ensures the retention of the original signal, which could reveal novel findings, and facilitates the direct extraction of features through advanced deep learning models \cite{learning}.
-However, it is not without challenges: high sample rates result in high dimensionality, demanding substantial computational resources.
-Additionally, raw audio is noise-sensitive, complicating the extraction process.
+Previous research has utilized Convolutional Neural Networks (CNNs) with various features such as Mel-Scaled Log-magnitude Spectograms (MLS), Self-Similarity Matrices (SSM), and Self-Similarity Lag Matrices (SSLM) as inputs \cite{Hernandez-Olivan2021MusicFeatures}.
+However, features derived from raw audio may lack interpretability in some scenarios \cite{Schindler2020DeepTutorial}, and raw audio presents unique advantages despite being computationally demanding.
+It ensures the preservation of the original signal, potentially unearthing novel insights, and allows for direct feature extraction via advanced deep learning models \cite{learning}.
+Nevertheless, it comes with challenges such as high dimensionality due to high sample rates, requiring substantial computational resources.
+Moreover, it is sensitive to noise, adding complexity to the extraction process.
 
@@
 Yet, the complexity of human auditory perception—encompassing temporal patterns, phase relationships between frequencies, and higher-level musical structures—means that musically similar sounds can have distinct spectrograms.
-This discrepancy implies that using spectrogram distance alone for measuring high-level music similarity may not always align with human perceptions \cite{Kim2020OneStrategies, Mesostructures2023}.
+This discrepancy implies that using spectrogram distance alone for measuring high-level music content may not always align with human perceptions \cite{Kim2020OneStrategies, Mesostructures2023}.
 
@@
 
-The positive image in every triplet of input data must preserve its intelligible content when subjected to transformations, regardless of alterations in sonic qualities.
-Maintaining the temporal structure and meaningfulness of the content allows it to present musical elements identical or strikingly similar to the original track.
+The positive image in every triplet of input data must preserve its intelligible content when subjected to transformations, regardless of alterations in sonic qualities and artifacts.
+Maintaining the temporal structure and meaningfulness of the content allows it to present musical elements identical or remarkably close to the original track.
 
@@
 
-\begin{itemize}
-    \item $I$ represents the set of all items in the batch.
-    \item $|A_i|$, $|P_i|$, and $|N_i|$ denote the lengths of the anchor, positive, and negative embedding vectors for the $i$-th item, respectively.
-    \item The $\max$ function is applied to find the longest of these three lengths for each item, and then the maximum of these maximum lengths is taken over all items in the batch.
+$I$ represents the set of all items in the batch, $|A_i|$, $|P_i|$, and $|N_i|$ denote the lengths of the anchor, positive, and negative embedding vectors for the $i$-th item, respectively.
+The $\max$ function is applied to find the longest of these three lengths for each item, and then the maximum of these maximum lengths is taken over all items in the batch.
 This gives the maximum length, $L_{\text{max}}$, of any vector in the batch.
-    \end{itemize}
 

### 2023-06-10 results/subsections/tables.tex
Updates from Overleaf

@@
 \begin{itemize}
-    \item \textbf{Precision}: Precision measures the proportion of correctly detected boundaries out of the total estimated boundaries.
-It quantifies the accuracy of the boundary detection algorithm.
-It is calculated as:
+    \item \textbf{Precision}: Precision measures the proportion of correctly detected boundaries out of the total estimated boundaries. It quantifies the accuracy of the boundary detection algorithm.
 
@@
 It quantifies the completeness or sensitivity of the boundary detection algorithm.
-It is calculated as:
 
@@
 This tolerance level can be adjusted, enabling the metric to consider a predicted boundary as correct if it's within the set tolerance window of a ground truth boundary \cite{Turnbull2007ABOOSTING}.
-The F-measure is calculated as follows:
 
@@
 
-Extend table by Hernandez-Olivan, C., Beltran, J. R. \& Diaz-Guerra, D. 
-\cite{Hernandez-Olivan2021MusicFeatures}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{table}[h]
+\centering
+\begin{tabularx}{\textwidth}{|X|X|X|X|X|}
+\hline
+\textbf{Technique} & \textbf{Training Dataset} & \textbf{Precision} & \textbf{Recall} & \textbf{F-measure} \\
+\hline
+MFCC & -- & -- & -- & -- \\
+\hline
+Embeddiogram & GTZAN Dataset & -- & -- & -- \\
+\hline
+Embeddiogram & MSD Dataset & -- & -- & -- \\
+\hline
+PCP & -- & -- & -- & -- \\
+\hline
+Tonnetx & -- & -- & -- & -- \\
+\hline
+CQT & -- & -- & -- & -- \\
+\hline
+\end{tabularx}
+\caption{Comparison of precision, recall, and f-measure for different techniques using the SALAMI dataset and the training dataset used for each technique.}
+\label{tab:comparison}
+\end{table}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \end{tabularx}
-\caption[Baseline. State of the art table.]{Your Caption.
-
-SALAMI dataset
-
-}
+\caption[Baseline.
+State-of-the-art table.]{\small{Modified table presented by Hernandez-Olivan, C., Beltran, J.
+R.
+\& Diaz-Guerra, D.
+in \cite{Hernandez-Olivan2021MusicFeatures}.
+Previous studies' boundary detection f-measure results using unsupervised methods for a 0.5s time-window tolerance.
+Only the top-performing algorithm for each year on the SALAMI dataset is displayed.}}
 \label{tab:my_label}

### 2023-06-11 evaluation/evaluation.tex
Updates from Overleaf

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Evaluation dataset and metrics}
+
+The developed model has been evaluated on the SALAMI dataset \cite{Smith2011DESIGNANNOTATIONS}.
+The "Structural Analysis of Large Amounts of Music Information" project aims to execute comprehensive structural analyses on a diverse spectrum of music.
+In contrast to traditional methods, SALAMI segments musical pieces into distinct sections, integrating perceptual, functional, and transcription analyses.
+Despite certain limitations, this novel approach offers a comprehensive and nuanced understanding of musical structure.
+
+Three primary metrics have been utilized to assess the model performance: Precision, Recall, and F-measure.
+Precision quantifies the proportion of accurately identified boundaries relative to all estimated boundaries to indicate the algorithm's accuracy in boundary detection.
+
+\begin{equation}
+\text{Precision} = \frac{\text{True Positives}}{\text{True Positives} + \text{False Positives}}
+\end{equation}
+
+On the other hand, Recall measures the proportion of accurately detected boundaries against all reference boundaries, indicating the completeness or sensitivity of the algorithm.
+
+\begin{equation}
+\text{Recall} = \frac{\text{True Positives}}{\text{True Positives} + \text{False Negatives}}
+\end{equation}
+
+Lastly, the F-measure offers a harmonized view of precision and recall.
+A widely adopted boundary detection metric, it compares predicted and ground truth boundaries, outputting a score between 0 and 1.
+This score is calculated as the harmonic mean of Precision and Recall, effectively considering both under-segmentation and over-segmentation.
+Given the potential inaccuracies inherent in human annotations and prediction errors, the F-measure permits minor deviations between predicted and actual boundaries.
+Its tolerance threshold can be adjusted, allowing a predicted boundary to be deemed correct if it is within a predefined window of a ground truth boundary \cite{Turnbull2007ABOOSTING, NietoPerceptualMusicb}.
+
+\begin{equation}
+\text{F-measure} = \frac{2 \times \text{Precision} \times \text{Recall}}{\text{Precision} + \text{Recall}}
+\end{equation}
+
 \newpage

### 2023-06-11 figures/neural networks/colour CNN.tex
Updates from Overleaf

--- 2023-04-16 figures/neural networks/colour CNN.tex
@@
 % DEEP CONVOLUTIONAL NEURAL NETWORK
-\begin{tikzpicture}[x=1.6cm,y=1.1cm]
+\begin{tikzpicture}[x=1.5cm,y=1.0cm]
   \large
@@
 \end{tikzpicture}
-    \caption{High-level illustration of a CNN}
+    \caption[High-level CNN diagram \cite{tikz}.]{\small{High-level illustration of a CNN.
+It consists of an input layer that takes in numerical data, followed by a downsampling process using convolution and pooling layers to extract features.
+Finally, fully-connected hidden layers are added for learning the global structure, and an output layer produces the desired predictions.}}
     \label{fig: CNN colour diagram}

### 2023-06-11 future work/future work.tex
Updates from Overleaf

@@
 The question as per \cite{Turian2022HEAR:Representations} or \cite{Li2023MERT:Training} remains if such general-purpose audio representation can mimic human hearing.
+That is a "thorn in our side" that we will pursue.
 
@@
 hyper-params: kernel size 0.005 times the sample rate
+larger representation layer
+Loss function margin.
+A margin of 0.2 can be a starting point, but it might not be the best value for every task.
+It's recommended to experiment with different values and choose the one that provides the best performance on your validation set.
 
 Utilize the dB-scale Mel-spectrum magnitude of audio as input data; it is a popular choice for input representation in music-related tasks when applying CNNs, as has been demonstrated in various studies \cite{Kim2020OneStrategies}.
-In addition to their wide usage, it's been recently reported that their frequency-domain summarization, grounded in psycho-acoustics, is efficient and challenging to replicate through solely data-driven methods.
-\cite{Kim2020OneStrategies}
+While raw audio is the most meaningful audio representation, it's been reported that dB-scale Mel-spectrum frequency-domain summarization, grounded in psycho-acoustics, is computationally efficient and challenging to replicate solely through data-driven methods \cite{Kim2020OneStrategies}; therefore, a trade-off that looks worthy of being explored.
 

### 2023-06-11 introduction/Subsections/Previous work.tex
Updates from Overleaf

@@
 
-Given their demonstrated effectiveness in existing literature and their potential for transfer learning, deep audio embeddings hold substantial promise for MIR downstream tasks, specifically boundary detection.
+Given their demonstrated effectiveness in the existing literature and their potential for transfer learning, deep audio embeddings hold substantial promise for MIR downstream tasks, and boundary detection is no exception.
 Nevertheless, it remains uncertain whether a general-purpose audio representation can effectively replicate human hearing \cite{Turian2022HEAR:Representations}, even though some techniques have managed to generalize across up to fourteen music understanding tasks \cite{Li2023MERT:Training}.

### 2023-06-11 methods/subsections/deep learning.tex
Updates from Overleaf

--- 2023-05-25 methods/subsections/deep learning.tex
@@
 
-Deep Neural Networks (DNNs), computational models rooted in biological neural systems, utilize layers of artificial neurons for tasks such as pattern recognition, classification, and regression.
-DNNs evolve by adjusting connections between neurons during learning, a concept initiated in the mid-20th century but modernized with Frank Rosenblatt's single-layer perceptron in 1957, capable of learning linearly separable patterns.
+Deep Neural Networks (DNNs), computational models somewhat rooted in biological neural systems, utilize layers of artificial neurons for tasks such as pattern recognition, classification, and regression.
+DNNs evolve by adjusting connections between neurons during learning, a concept initiated in the mid-20th century but modernized with Frank Rosenblatt's single-layer perceptron in 1957, capable of learning linearly separable patterns \cite{perceptron}.
 

### 2023-06-11 methods/subsections/implementation.tex
Updates from Overleaf

@@
 
-\subsection{Triplet Siamese Networks}
+\subsection{Deep Neural Network Architecture}
 
@@
 The aim is to minimize the loss function between a triplet of anchor, positive, and negative samples, utilizing online triplet mining for optimizing memory resources \cite{Sikaroudi2020OfflinePatches}.
-This self-supervised learning (SSL) model aims to distinguish between similar and dissimilar samples effectively.
+This SSL model aims to distinguish between similar and dissimilar samples effectively.
 
@@
 
+There are several loss functions used in tasks like feature learning, similarity learning, and dimensionality reduction.
+
+Functions such Mean Squared Error (MSE) Loss \cite{Hodson2021MeanDeconstructed}, Cross-Entropy Loss \cite{Zhang2018GeneralizedLabels}, Contrastive Loss \cite{supercontrast} or Triplet Loss are used when training models to understand the difference between various classes or categories.
+
 Schroff, F., Kalenichenko, D., and Philbin, J.
@@
 
-The triplet loss function used in Siamese-like networks guides the learning process.
+The triplet loss function guides the learning process.
 It seeks to minimize the distance between the anchor and positive instances while maximizing the distance between the anchor and the negative instances.
@@
 
-The triplet loss function $\mathcal{L}(\mathbf{a}, \mathbf{p}, \mathbf{n})$ aims to ensure that an anchor vector $\mathbf{a}_i$ is closer in the embedding space to a positive vector $\mathbf{p}_i$ (representing an example of the same class) than to a negative vector $\mathbf{n}_i$ (representing an example of a different class) by at least a margin $m$.
+The triplet loss function $\mathcal{L}(\mathbf{a}, \mathbf{p}, \mathbf{n})$ aims to ensure that an anchor vector $\mathbf{a}_i$ is closer in the embedding space to a positive vector $\mathbf{p}_i$ (representing an example of the same class) than to a negative vector $\mathbf{n}_i$ (representing an example of a different class) by at least a margin $\alpha$.
 It is calculated by summing the losses overall $N$ triplets in the dataset, where the equation gives the loss for each triplet:
@@
 \begin{equation}
-\mathcal{L}(\mathbf{a}, \mathbf{p}, \mathbf{n}) = \sum_{i=1}^{N} \max \left(0, \left| \mathbf{a}_i - \mathbf{p}_i \right|_2^2 - \left| \mathbf{a}_i - \mathbf{n}_i \right|_2^2 + m \right)
+\mathcal{L}(\mathbf{a}, \mathbf{p}, \mathbf{n}) = \sum_{i=1}^{N} \max \left(0, \left| \mathbf{a}_i - \mathbf{p}_i \right|_2^2 - \left| \mathbf{a}_i - \mathbf{n}_i \right|_2^2 + \alpha \right)
 \end{equation}
 
-The final loss used for model training is then the average loss over a mini-batch of $N$ triplets:
+The $\max(0, x)$ operation ensures zero loss when the distances satisfy this condition. The final loss used for model training is then the average loss over a mini-batch of $N$ triplets:
 
@@
 
+The margin is a task-dependent optimal value determined empirically based on model performance.
+If it's too small, the model might not differentiate classes effectively; if it's too large, it might focus on outliers.
+
+While some packages can be found in the MIR literature \cite{auraloss}, we wrote our own PyTorch \cite{Paszke2019PyTorch:Library} implementation for the sake of our experiments.
+
 As previously stated, the goal of minimizing this loss function is to learn discriminative embeddings, where similar examples are grouped closely together.
 In contrast, dissimilar examples are placed farther apart in the embedding space.
-
-While some packages can be found in the MIR literature \cite{auraloss}, we wrote our own PyTorch \cite{Paszke2019PyTorch:Library} implementation for the sake of our experiments.
 
@@
 
-$I$ represents the set of all items in the batch, $|A_i|$, $|P_i|$, and $|N_i|$ denote the lengths of the anchor, positive, and negative embedding vectors for the $i$-th item, respectively.
+$I$ represents the set of all items in the batch, $|A_i|$, $|P_i|$, and $|N_i|$ denote the lengths of the anchor, positive, and negative vectors for the $i$-th item, respectively.
 The $\max$ function is applied to find the longest of these three lengths for each item, and then the maximum of these maximum lengths is taken over all items in the batch.
@@
 
+\subsubsection{Training strategy}
+
+To tackle the computational demands of training models on extensive raw audio data, we incorporated a couple of strategies to optimize efficiency and performance.
+
+First, we utilized 16-mixed precision training.
+This approach leverages the improved performance of modern GPUs for 16-bit computations, enabling the model to run faster and use less memory without sacrificing model performance \cite{Das2018MixedOperations}.
+
+Secondly, to capitalize on the computational capabilities of multiple GPUs and hasten training times, we employed the Distributed Data-Parallel (DDP) strategy \cite{Li2020PyTorchTraining}.
+DDP operates on distinct mini-batches of data across GPUs and synchronizes the gradients after each backward pass, providing a more efficient scaling than other parallel strategies.
+
+These strategies collectively enhance the computational efficiency while maintaining the robustness of the model training on lengthy raw audio data.
+
 \newpage

### 2023-06-11 results/subsections/tables.tex
Updates from Overleaf

@@
-SALAMI (Structural Analysis of Large Amounts of Music Information) is a project aiming to carry out extensive structural analyses on a wide variety of music, from Western pop to Indian classical, and from live to studio recordings \cite{Smith2011DESIGNANNOTATIONS}.
+SALAMI (Structural Analysis of Large Amounts of Music Information) is a project aiming to carry out extensive structural analyses on a wide variety of music \cite{Smith2011DESIGNANNOTATIONS}.
 Instead of traditional forms, the authors segment pieces into sections, combining perceptual, functional, and transcription analyses.
@@
 \hline
-Tonnetx & -- & -- & -- & -- \\
+Tonnetz & -- & -- & -- & -- \\
 \hline
@@
 \caption[Baseline.
-State-of-the-art table.]{\small{Modified table presented by Hernandez-Olivan, C., Beltran, J.
-R.
-\& Diaz-Guerra, D.
-in \cite{Hernandez-Olivan2021MusicFeatures}.
-Previous studies' boundary detection f-measure results using unsupervised methods for a 0.5s time-window tolerance.
-Only the top-performing algorithm for each year on the SALAMI dataset is displayed.}}
+State-of-the-art table.]{\small{Previous studies' boundary detection f-measure results using unsupervised methods for a 0.5s time-window tolerance.
+Only the top-performing algorithm for each year on the SALAMI dataset is displayed.
+Original source \cite{Hernandez-Olivan2021MusicFeatures}}}
 \label{tab:my_label}

### 2023-06-13 evaluation/evaluation.tex
Updates from Overleaf

@@
 
-While the usefulness of deep audio embeddings can be evaluated in countless downstream tasks \cite{Li2023MERT:Training, Kim2020OneStrategies}, we have chosen music boundary detection, a subset of Music Structure Analysis (MSA) for its popularity, complexity, and product-compelling nature.
+While the usefulness of deep audio embeddings can be evaluated in countless downstream tasks \cite{Li2023MERT:Training, Kim2020OneStrategies}, we have chosen music boundary detection, a subset of Music Structure Analysis (MSA) for its popularity \cite{Smith2013ATask}, complexity, and product-compelling nature.
 This interdisciplinary field aims to understand the structure of music \cite{Nieto2020Audio-BasedApplications}.
@@
 All the evaluation experiments have been wrapped around MSAF \cite{NietoMSAF:FRAMEWORK}, a popular framework for Music Structure Analysis.
-
-All the evaluation metrics have been computed using the mir-eval package \cite{RaffelMir_eval:METRICS}.
 

### 2023-06-13 figures/neural networks/activation.tex
Updates from Overleaf

@@
     \centering
-    \scalebox{0.9}{
+    \scalebox{0.8}{
 % NEURAL NETWORK activation
@@
 }
-\caption[Activation function.]{\small{The input layer with \textit{n} nodes is denoted as $a_i^{(0)}$ for $i \in \{1, \ldots, n\}$.
+\caption[Activation function \cite{tikz}.]{\small{The input layer with \textit{n} nodes is denoted as $a_i^{(0)}$ for $i \in \{1, \ldots, n\}$.
 The output layer with \textit{m} nodes is $a_j^{(1)}$ for $j \in \{1, \ldots, m\}$.
 Connections between these layers are governed by the weight matrix $\mathbf{W}^{(0)} \in \mathbb{R}^{m\times n}$ and bias vector $\mathbf{b}^{(0)} \in \mathbb{R}^{m}$, with elements $w_{j,i}$ and $b_j^{(0)}$ respectively.
-The activation function, denoted as $\sigma$, operates element-wise on the sum of the product of the weight matrix, input vector, and bias vector.}}
+The activation function $\sigma$ operates element-wise on the sum of the product of the weight matrix, input vector, and bias vector.}}
 

### 2023-06-13 introduction/Subsections/Previous work.tex
Updates from Overleaf

@@
 
-Previous studies have highlighted the significance of selecting suitable audio features to distinguish and label unique music segments in music segmentation tasks.
-However, acquiring music segment annotation data for learning feature transformations presents a challenge due to its labor-intensive and expensive nature.
-Research has leveraged unsupervised deep learning to mitigate this, using readily available music audio.
-This methodology has significantly enhanced the efficacy of segmentation algorithms, yielding state-of-the-art results.
-Furthermore, strategies that recognize the hierarchical nature of the structural organization employing two-level annotations of primary and secondary boundaries have further augmented boundary detection performance \cite{unsupervisedlearndeepfeat, GrillMUSICANNOTATIONS, Hernandez-Olivan2021MusicFeatures, SalamonDeepSegmentation}.
+Prior research underscores the importance of choosing appropriate audio features to differentiate and label distinct music segments for music segmentation tasks.
+The hurdle lies in procuring annotated data for learning these feature transformations, which can be laborious and costly.
+To overcome this, scholars have turned to unsupervised deep learning, utilizing accessible music audio \cite{unsupervisedlearndeepfeat, GrillMUSICANNOTATIONS}.
+This approach has markedly enhanced the generalization ability of machine-listening models in downstream applications, with segmentation algorithms reaping benefits in the form of state-of-the-art outcomes \cite{Hernandez-Olivan2021MusicFeatures, SalamonDeepSegmentation, teacher, Li2023MERT:Training}.
 
-Apart from music structure applications, recent advances in neural networks have facilitated the generation of low-dimensional numerical representations that encapsulate key musical attributes.
-This development simplifies the computation of various task-specific elements.
-Such tasks encompass:
+Beyond music structure applications, modern advancements in neural networks have facilitated the creation of condensed numerical representations that capture critical musical characteristics.
+This progress has streamlined the calculation process for various task-specific elements.
+Such tasks include:
 

### 2023-06-13 methods/subsections/implementation.tex
Updates from Overleaf

@@
 
-Contrastive Learning of Musical Representations (CLMR) is a method that learns valuable, discriminative music representations without explicit labels by contrasting positive augmentations of a musical piece against negative ones \cite{CLMR2021}.
+Our implementation is a slight tweak to the \textit{contrastive learning of lusical representations} (CLMR), a method that learns valuable, discriminative music representations without explicit labels by contrasting positive augmentations of a musical piece against negative ones \cite{CLMR2021}.
 CLMR falls under a subset of ML called self-supervised learning (SSL) \cite{Balestriero2023ALearning}, where models learn independently from unlabeled data to create their supervisory signals \cite{audioselfsupsurvey}.
@@
 
-The methodology of CLMR involves generating different augmentations of the same musical piece to serve as positive pairs while using other pieces as antagonistic pairs.
-The training process, which minimizes a contrastive loss function, encourages the model to produce similar representations for positive and dissimilar ones for antagonistic pairs.
+As stated above, the methodology of CLMR involves generating different augmentations of the same musical piece to serve as positive pairs while using other pieces as antagonistic pairs.
+The training process, which minimizes a triplet loss function, encourages the model to produce similar representations for positive and dissimilar ones for antagonistic pairs.
 
@@
 
-There are several loss functions used in tasks like feature learning, similarity learning, and dimensionality reduction.
-
-Functions such Mean Squared Error (MSE) Loss \cite{Hodson2021MeanDeconstructed}, Cross-Entropy Loss \cite{Zhang2018GeneralizedLabels}, Contrastive Loss \cite{supercontrast} or Triplet Loss are used when training models to understand the difference between various classes or categories.
+Contrastive loss and triplet loss are two prominent loss functions employed in the fields of feature learning, similarity learning, and dimensionality reduction.
 
 Schroff, F., Kalenichenko, D., and Philbin, J.
-at Google initially proposed and used triplet loss to learn face recognition of the same person at different poses and angles.
-\cite{Schroff2015FaceNet:Clustering}
+from Google first proposed and applied triplet loss for the learning of facial recognition, catering to varied poses and angles of the same individual \cite{Schroff2015FaceNet:Clustering}.
 
-The triplet loss function guides the learning process.
-It seeks to minimize the distance between the anchor and positive instances while maximizing the distance between the anchor and the negative instances.
-A margin parameter is included in the loss function to ensure a minimum separation between positive and negative instances in the embedding space.
+Triplet loss function directs the learning process by endeavoring to minimize the distance between the anchor and positive instances and maximize the distance between the anchor and negative instances.
+Contrastive loss, on the other hand, works on pairs of instances \cite{supercontrast}.
+The inclusion of a margin parameter in the loss function guarantees a minimum separation between positive and negative instances in the embedding space.
+Given the nature of our training needs, we propose to train by using the former.
 

### 2023-06-13 results/subsections/tables.tex
Updates from Overleaf

@@
-SALAMI (Structural Analysis of Large Amounts of Music Information) is a project aiming to carry out extensive structural analyses on a wide variety of music \cite{Smith2011DESIGNANNOTATIONS}.
-Instead of traditional forms, the authors segment pieces into sections, combining perceptual, functional, and transcription analyses.
-Despite limitations, this approach offers a holistic and nuanced perspective on music structure.
-
-METRICS
-
-\begin{itemize}
-    \item \textbf{Precision}: Precision measures the proportion of correctly detected boundaries out of the total estimated boundaries. It quantifies the accuracy of the boundary detection algorithm.
-
-    \[
-    \text{Precision} = \frac{\text{True Positives}}{\text{True Positives} + \text{False Positives}}
-    \]
-
-    High precision indicates a low rate of false positives, meaning the algorithm correctly identifies boundaries without many incorrect detections.
-
-    \item \textbf{Recall}: Recall measures the proportion of correctly detected boundaries out of the total reference boundaries.
-It quantifies the completeness or sensitivity of the boundary detection algorithm.
-
-    \[
-    \text{Recall} = \frac{\text{True Positives}}{\text{True Positives} + \text{False Negatives}}
-    \]
-
-    High recall indicates a low rate of false negatives, meaning that the algorithm successfully detects most of the true boundaries without missing many.
-
-    \item \textbf{F-measure}: The F-measure is a widely used boundary detection metric computed by comparing the predicted and ground truth boundaries.
-This metric, ranging from 0 to 1, represents the harmonic mean of precision and recall, providing a balanced view of under-segmentation and over-segmentation.
-Given the potential inaccuracies in human annotations and prediction errors, the F-measure tolerates minor discrepancies between predicted and ground truth boundaries.
-This tolerance level can be adjusted, enabling the metric to consider a predicted boundary as correct if it's within the set tolerance window of a ground truth boundary \cite{Turnbull2007ABOOSTING}.
-
-    \[
-    \text{F-measure} = \frac{2 \times \text{Precision} \times \text{Recall}}{\text{Precision} + \text{Recall}}
-    \]
-\end{itemize}
+The evaluation results have been obtained using the standard and most commonly used MIR's tools and frameworks such as MSAF \cite{NietoMSAF:FRAMEWORK} for the segmentation algorithms, the SALAMI dataset \cite{Smith2011DESIGNANNOTATIONS} as evaluation ground truth and $mir_eval$ \cite{RaffelMir_eval:METRICS} for metric computation.
 
@@
 Original source \cite{Hernandez-Olivan2021MusicFeatures}}}
-\label{tab:my_label}
+\label{tab:comparison_table}
 \end{table}

### 2023-06-13 evaluation/evaluation.tex
Updates from Overleaf

@@
     \centering
-    \includegraphics[width=\linewidth]{figures/images/salami_391_embeddiogram.png}
-    \caption[Embeddiogram. Track 391 (SALAMI dataset).]{Embeddiogram. Track 391 (SALAMI dataset).}
+    \includegraphics[width=\linewidth]{figures/images/355embeddiogramnormalized.png}
+    \caption[Embeddiogram. Track 355 (SALAMI dataset).]{Embeddiogram. Track 391 (SALAMI dataset).}
     \label{fig:image1}
@@
     \centering
-    \includegraphics[width=\linewidth]{figures/images/samali_391_novelty_curve_peaks.png}
-    \caption[Novelty curve + peaks. Track 391 (SALAMI dataset).]{Novelty curve + peaks. Track 391 (SALAMI dataset).}
+    \includegraphics[width=\linewidth]{figures/images/355novelty.png}
+    \caption[Novelty curve + peaks. Track 391 (SALAMI dataset).]{Novelty curve + peaks. Track 355 (SALAMI dataset).}
     \label{fig:image2}
@@
         \centering
-        \includegraphics[width=0.9\textwidth]{figures/images/salami_391_R matrix after Gaussian smoothing.png} % first figure itself
-        \caption[Track 391 (SALAMI dataset) Self-similarity matrix]{Self-similarity matrix. Track 391 (SALAMI dataset).}
+        \includegraphics[width=0.9\textwidth]{figures/images/355recurrencematrix.png} % first figure itself
+        \caption[Track 355 (SALAMI dataset) Self-similarity matrix]{Self-similarity matrix. Track 355 (SALAMI dataset).}
     \end{minipage}\hfill
@@
         \centering
-        \includegraphics[width=0.9\textwidth]{figures/images/salami_391_Lag matrix after Gaussian smoothing.png} % second figure itself
-        \caption[Track 391 (SALAMI dataset) Self-similarity lag matrix]{Self-similarity lag matrix. Track 391 (SALAMI dataset).}
+        \includegraphics[width=0.9\textwidth]{figures/images/355lagmatrixgaussiansmoothing.png} % second figure itself
+        \caption[Track 355 (SALAMI dataset) Self-similarity lag matrix]{Self-similarity lag matrix. Track 355 (SALAMI dataset).}
     \end{minipage}
@@
         \centering
-        \includegraphics[width=0.9\textwidth]{figures/images/salami_391_Q_matrix.png} % third figure itself
-        \caption[Track 391 (SALAMI dataset). Q-matrix]{Cumulative matrix. Track 391 (SALAMI dataset).}
+        \includegraphics[width=0.9\textwidth]{figures/images/355cumulativematrix.png} % third figure itself
+        \caption[Track 355 (SALAMI dataset). Q-matrix]{Cumulative matrix. Track 355 (SALAMI dataset).}
     \end{minipage}\hfill
@@
         \centering
-        \includegraphics[width=0.9\textwidth]{figures/images/salami_391_binary transitive matrix.png} % fourth figure itself
-        \caption[Track 391 (SALAMI dataset). Transitive Binary Similarity Matrix]{Transitive Binary Matrix. Track 391 (SALAMI dataset).}
+        \includegraphics[width=0.9\textwidth]{figures/images/355transitivebinarysimilaritymatrix.png} % fourth figure itself
+        \caption[Track 355 (SALAMI dataset). Transitive Binary Similarity Matrix]{Transitive Binary Matrix. Track 355 (SALAMI dataset).}
     \end{minipage}

### 2023-06-13 introduction/Subsections/Introduction.tex
Updates from Overleaf

--- 2023-05-16 introduction/Subsections/Introduction.tex
@@
 Music \footnote{In this thesis, "music" refers to the Western tradition, characterized by conventions, practices, and aesthetics that have developed primarily in Europe and North America.
-This usage is not intended to deny the diversity and richness of other musical traditions worldwide but instead reflects the present study's focus on a specific cultural context.}, an essential component of human culture, history, and society; it has existed since ancient times.
-It reflects the changes in our cultures, traditions, and beliefs as it evolves.
-Studying music, therefore, has always been a challenging and complex task due to its subjective nature, relative and mutable ground truth, and the sheer variety of musical styles, genres, and worldwide cultures.
+This usage does not deny the diversity and richness of other musical traditions worldwide but reflects the present study's focus on a specific cultural context.}, integral to human culture and history, has evolved alongside our societies since ancient times.
+Its study is complex due to its subjectivity, mutable ground truth, and various styles and cultural contexts.
 
-For millennia, people have sought to understand the underlying structure of music.
-Music has captivated and intrigued us from the ancient Greeks to the present day.
-This rich music theory and analysis history form a valuable foundation for guiding and evaluating Music Information Retrieval (MIR) algorithms and models.
-
-MIR has emerged over the last few decades as an interdisciplinary field that combines engineering, musicology, and neuroscience.
-It aims to develop algorithms and techniques for automatically analyzing, classifying, and retrieving musical information, primarily from audio signals.
-While MIR research has traditionally focused on technical aspects such as Digital Signal Processing (DSP) and pattern recognition, it may have overlooked other relevant domains, including perception, cognition, music theory, aural skills, musicology, and their subfields.
+XXXXXXX

### 2023-06-13 results/subsections/tables.tex
Updates from Overleaf

@@
 \hline
-MFCC & -- & -- & -- & -- \\
+MFCC & -- & 0.173 & 0.185 & 0.172 \\
 \hline
-Embeddiogram & GTZAN Dataset & -- & -- & -- \\
+Embeddiogram & GTZAN Dataset & 0.228 & 0.171 & 0.185 \\
 \hline
-Embeddiogram & MSD Dataset & -- & -- & -- \\
+Embeddiogram & MSD Dataset & \textbf{0.335} & 0.276 & 0.288 \\
 \hline
-PCP & -- & -- & -- & -- \\
+PCP & -- & 0.311 & 0.324 & 0.305 \\
 \hline
-Tonnetz & -- & -- & -- & -- \\
+Tonnetz & -- & 0.312 & 0.312 & 0.300 \\
 \hline
-CQT & -- & -- & -- & -- \\
+CQT & -- & 0.311 & \textbf{0.339} & \textbf{0.312} \\
 \hline
 \end{tabularx}
-\caption{Comparison of precision, recall, and f-measure for different techniques using the SALAMI dataset and the training dataset used for each technique.}
+\caption[Comparison of precision, recall, and f-measure for different audio features]{Comparison of precision, recall, and f-measure for different features using the SALAMI dataset.
+Sliding windowed segments across the audio signal input signal is 4 seconds}
 \label{tab:comparison}
@@
 \addlinespace
-Grill \& Schlüter \cite{4}, 2015 & MLS, SSLMs & CNN  & 0.523 \\
+Grill \& Schlüter \cite{4}, 2015 & MLS, SSLMs & CNN  & \textbf{0.523} \\
 \addlinespace

### 2023-06-15 abstract/abstract.tex
Updates from Overleaf

--- 2023-06-08 abstract/abstract.tex
@@
 In collaboration with Epidemic Sound AB and the Music Technology Group (MTG) at Universitat Pompeu Fabra (UPF), we used self-supervised contrastive learning to uncover the underlying structure of Western tonal music by learning deep audio features to improve unsupervised music boundary detection.
-We applied deep convolutional neural networks and a triplet loss function to identify abstract and semantic musical elements without relying on their sonic qualities.
-This way, we replaced traditional acoustic features with deep audio embeddings, paving the way for high-level, sound-agnostic, and content-sensitive music representation for boundary detection.
+We applied deep convolutional neural networks and a triplet loss function to identify abstract and semantic high-level musical elements without relying on their sonic qualities.
+This way, we replaced traditional acoustic features with deep audio embeddings, paving the way for sound-agnostic and content-sensitive music representation for boundary detection.
 
-Our cognitively-based approach for learning embeddings focuses on using full-resolution data and preserving high-level musical information.
+Our cognitively-based approach for learning embeddings focuses on using full-resolution data and preserving high-level musical information which unfolds in the time domain.
+A key component in our methodology is the use of triplet networks, which provide an effective way of understanding and preserving the relative distances between different pieces of music.
+This model structure is integral to our work, allowing us to identify and maintain the nuanced relationships within our musical data.
 Drawing upon our domain expertise, we developed robust transformations to encode heuristic musical concepts that should remain constant.
-This novel approach aims to reconcile music and machine learning, enhancing machine listening models' efficacy.
+This novel approach aims to reconcile music and machine learning, enhancing machine listening models' efficacy through deep learning and triplet networks.
 
-Preliminary results suggest that our musically-informed technique has significant potential for boundary detection tasks and possibly nearly all MIR downstream tasks that are not purely sonic-based.
-While it didn't outperform state-of-the-art results, it showed very competitive results and room for improvement.
-Consequently, music-motivated audio embeddings appear promising and potentially adaptable to other tasks constrained by data scarcity.
+Preliminary results suggest that, while not outperforming state-of-the-art results, our musically-informed technique has significant potential for boundary detection tasks and, most likely, nearly all MIR downstream tasks that are not purely sonic-based.
+
+While music-motivated audio embeddings appear promising, delivering competitive results with room for improvement and potentially adaptable to other tasks constrained by data scarcity, the question remains if such general-purpose audio representation can mimic human hearing.
 

### 2023-06-15 discussion/discussion.tex
Updates from Overleaf

--- 2023-05-30 discussion/discussion.tex
@@
 
+Too little representation layer?
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/images/Mean group aggregation.png}
+    \caption{Caption}
+    \label{fig:enter-label}
+\end{figure}
+
 \section{Conclusions}
@@
 In this work, we introduced a method to uncover underlying high-level musical
-content in the temporal domain by leveraging self-supervised deep neural networks, inductive bias, and aural skills to learn music latent representations with applications to MIR downstream tasks.
+content in the temporal domain by leveraging self-supervised deep neural networks to learn low-dimensional music latent representations with applications to music boundary detection.
 Building on existing approaches and architectures, we replaced traditional features with deep embeddings trained to represent high-level musical content information.

### 2023-06-15 evaluation/evaluation.tex
Updates from Overleaf

@@
 \chapter{Evaluation}
-
-\section{Music boundary detection as downstream task}
-
-While the usefulness of deep audio embeddings can be evaluated in countless downstream tasks \cite{Li2023MERT:Training, Kim2020OneStrategies}, we have chosen music boundary detection, a subset of Music Structure Analysis (MSA) for its popularity \cite{Smith2013ATask}, complexity, and product-compelling nature.
-This interdisciplinary field aims to understand the structure of music \cite{Nieto2020Audio-BasedApplications}.
-Due to subjectivity, ambiguity, and data scarcity, audio-based MSA faces challenges like boundary placement ambiguity and similarity quantification \cite{NietoPerceptualMusic}.
-
-All the evaluation experiments have been wrapped around MSAF \cite{NietoMSAF:FRAMEWORK}, a popular framework for Music Structure Analysis.
 
@@
 
+\section{Music boundary detection as downstream task}
+
+While the usefulness of deep audio embeddings can be evaluated in countless downstream tasks \cite{Li2023MERT:Training, Kim2020OneStrategies}, we have chosen music boundary detection, a subset of Music Structure Analysis (MSA) for its popularity \cite{Smith2013ATask}, complexity, and product-compelling nature.
+This interdisciplinary field aims to understand the structure of music \cite{Nieto2020Audio-BasedApplications}.
+Due to subjectivity, ambiguity, and data scarcity, audio-based MSA faces challenges like boundary placement ambiguity and similarity quantification \cite{NietoPerceptualMusic}.
+
+All the evaluation experiments have been wrapped around MSAF \cite{NietoMSAF:FRAMEWORK}, a popular framework for Music Structure Analysis.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Evaluation dataset and metrics}
@@
 The developed model has been evaluated on the SALAMI dataset \cite{Smith2011DESIGNANNOTATIONS}.
-The "Structural Analysis of Large Amounts of Music Information" project aims to execute comprehensive structural analyses on a diverse spectrum of music.
+The \textit{Structural Analysis of Large Amounts of Music Information} project aims to execute comprehensive structural analyses on a diverse spectrum of music.
 In contrast to traditional methods, SALAMI segments musical pieces into distinct sections, integrating perceptual, functional, and transcription analyses.

### 2023-06-15 figures/neural networks/activation.tex
Updates from Overleaf

@@
+\begin{center}
+\end{center}
 \begin{figure}
     \centering
-    \scalebox{0.8}{
+    \scalebox{1.0}{
 % NEURAL NETWORK activation
-% https://www.youtube.com/watch?v=aircAruvnKk&list=PLZHQObOWTQDNU6R1_67000Dx_ZCJB-3pi&index=1
 \begin{tikzpicture}[x=2.7cm,y=1.6cm]
@@
 }
-\caption[Activation function \cite{tikz}.]{\small{The input layer with \textit{n} nodes is denoted as $a_i^{(0)}$ for $i \in \{1, \ldots, n\}$.
-The output layer with \textit{m} nodes is $a_j^{(1)}$ for $j \in \{1, \ldots, m\}$.
-Connections between these layers are governed by the weight matrix $\mathbf{W}^{(0)} \in \mathbb{R}^{m\times n}$ and bias vector $\mathbf{b}^{(0)} \in \mathbb{R}^{m}$, with elements $w_{j,i}$ and $b_j^{(0)}$ respectively.
-The activation function $\sigma$ operates element-wise on the sum of the product of the weight matrix, input vector, and bias vector.}}
+\caption[Activation function \cite{tikz}.]{\small{Input $a_i^{(0)}$ and output $a_j^{(1)}$ layers are connected by weight matrix $\mathbf{W}^{(0)}$ and bias vector $\mathbf{b}^{(0)}$, processed by activation function $\sigma$.}}
 

### 2023-06-15 future work/future work.tex
Updates from Overleaf

@@
 
-transforms
-stems
-different takes
-k-fold cross validation
-hyper-params: kernel size 0.005 times the sample rate
-larger representation layer
+\begin{itemize}
+  \item Transforms
+  \item Stems
+  \item Different takes
+  \item k-fold cross validation
+  \item Hyper-params: kernel size $0.005$ times the sample rate
+  \item Larger representation layer
+  \item Easy triplet mining \cite{XuanImprovedMining}
+  \item Different boundary detection algorithms \cite{sf} was used because it was the default in MSAF \cite{MSAF}
+\end{itemize}
+
 Loss function margin.

### 2023-06-15 introduction/Subsections/Introduction.tex
Updates from Overleaf

@@
 
-Music \footnote{In this thesis, "music" refers to the Western tradition, characterized by conventions, practices, and aesthetics that have developed primarily in Europe and North America.
-This usage does not deny the diversity and richness of other musical traditions worldwide but reflects the present study's focus on a specific cultural context.}, integral to human culture and history, has evolved alongside our societies since ancient times.
-Its study is complex due to its subjectivity, mutable ground truth, and various styles and cultural contexts.
+Music \footnote{Throughout this thesis, "music" refers to the Western tradition, defined by the conventions, practices, and aesthetics that primarily evolved in Europe and North America.
+This term's usage does not negate the diversity and richness of other musical traditions worldwide.
+Instead, it specifies this study's concentration on a particular cultural context.}, a cornerstone of human culture and history, has developed hand in hand with our societies since ancient times.
+However, the study of music is complex due to its inherent subjectivity, ever-changing ground truth, and the array of styles and cultural contexts it encompasses.
 
-XXXXXXX
+Prior research emphasizes the necessity of selecting suitable audio features to distinguish and label unique music segments for music segmentation tasks.
+The challenge lies in acquiring annotated data for these feature transformations, which can be time-consuming and expensive.
+In response, scholars have turned to unsupervised deep learning using readily available music audio \cite{unsupervisedlearndeepfeat, GrillMUSICANNOTATIONS}.
+This method has substantially improved the generalization capacity of machine-listening models in downstream applications.
+Among others, segmentation algorithms have seen significant enhancements and delivered state-of-the-art results \cite{Hernandez-Olivan2021MusicFeatures, Li2023MERT:Training}.
+
+Beyond applications in music structure, the evolution of neural networks has empowered the creation of condensed numerical representations encapsulating crucial musical traits.
+This evolution has simplified the computational process for various task-specific elements, including but not limited to:
+
+\begin{itemize}
+\item Creating an audio embedding method that excels across numerous applications without the necessity for fine-tuning \cite{Turian2022HEAR:Representations}
+\item Boosting the classification of environmental sounds \cite{Kim2020OneStrategies, CramerLOOKEMBEDDINGS}
+\item Enhancing vocal-centric music tasks through cross-domain audio embeddings \cite{Kim2021LearningLoss}
+\item Integrating task-specific and pre-trained features to optimize audio classification \cite{Hung2022Feature-informedClassification}
+\item Developing a music similarity search engine for video production \cite{epidemic}
+\item Improving Music Emotion Recognition (MER) performance \cite{KohComparisonRecognition}
+\item Evaluating the effectiveness of speaker recognition via pre-trained model embeddings \cite{lightweight}
+\item Embedding songs for artist identification to facilitate similarity comparisons \cite{contentmusicsimtriplet2020}
+\item Addressing cross-modal text-to-music retrieval issues \cite{WonEmotionStories}
+\item Enabling automated music rearrangement \cite{Stoller2018IntuitiveTransitions, Plachouras2023MusicSegmentation}
+\end{itemize}
+
+Furthermore, deep audio embeddings offer the benefit of transferability, establishing a foundation for multiple tasks.
+Compared to training a model from scratch, this approach saves computational resources and time \cite{}.
+
+Given the proven effectiveness of deep audio embeddings in existing research and their potential for transfer learning, they hold considerable promise for Music Information Retrieval (MIR) downstream tasks, including boundary detection.
+However, it is yet to be determined whether a general-purpose audio representation can successfully emulate human hearing \cite{Turian2022HEAR:Representations}, even though some techniques have demonstrated generalizability across as many as fourteen music-understanding tasks \cite{Li2023MERT:Training}.

### 2023-06-15 introduction/Subsections/Objectives.tex
Updates from Overleaf

--- 2023-06-08 introduction/Subsections/Objectives.tex
@@
 
-This study explores music's high-level tonal structure by leveraging self-supervised deep neural networks, inductive bias, and aural skills to learn and analyze music embeddings applicable to subsequent MIR tasks.
+Can deep audio embeddings be learned from reordering and scrambling sequences of musical information, and can audio effects be added to improve unsupervised music boundary detection?
 
-The study aims to develop a unified numerical understanding (or embedding \footnote{A learned representation or embedding is a numerical output -usually a fixed-size vector- produced by a machine-learning model.
-Good representations should be versatile across various tasks and require limited supervision \cite{Turian2022HEAR:Representations}.}) for a music piece that integrates high-level elements like melody contour, harmony relationships, and other comprehensive components such as the relationships between elements unfolding through time, arranging the embedding space to emphasize the clustering of these sophisticated musical content without considering sonic qualities or attributes.
+This study explores the high-level tonal structure of music by leveraging self-supervised deep neural networks, inductive bias, and aural skills to learn and analyze music embeddings that can be applied to subsequent MIR tasks, with a particular focus on music boundary detection.
 
-The research will utilize MIR computational methodologies and musicological perspectives to explore musical compositions from various styles and genres.
+This study aims to develop and learn a unified numerical understanding (or embedding \footnote{A learned representation or embedding is a numerical output - usually a fixed-size vector - produced by a machine-learning model.
+Good representations should be versatile across various tasks and require limited supervision \cite{Turian2022HEAR:Representations}.}) for a piece of music that integrates the high-level relationships between musical elements as they unfold over time.
 
-This approach seeks to replicate human auditory capabilities in understanding and identifying abstract and semantic musical elements independent of their sonic qualities.
+The research will employ MIR computational methodologies and musicological perspectives to explore musical compositions across various styles and genres.
+
+This approach seeks to replicate human auditory capabilities by understanding and identifying abstract and semantic musical elements independent of their sonic qualities.

### 2023-06-15 introduction/Subsections/Previous work.tex
Updates from Overleaf

@@
 
-Prior research underscores the importance of choosing appropriate audio features to differentiate and label distinct music segments for music segmentation tasks.
-The hurdle lies in procuring annotated data for learning these feature transformations, which can be laborious and costly.
-To overcome this, scholars have turned to unsupervised deep learning, utilizing accessible music audio \cite{unsupervisedlearndeepfeat, GrillMUSICANNOTATIONS}.
-This approach has markedly enhanced the generalization ability of machine-listening models in downstream applications, with segmentation algorithms reaping benefits in the form of state-of-the-art outcomes \cite{Hernandez-Olivan2021MusicFeatures, SalamonDeepSegmentation, teacher, Li2023MERT:Training}.
+Related research such as \cite{SalamonDeepSegmentation} and \cite{deepfeaturesegment} explore how the use of audio embeddings learned via unsupervised methods can enhance the performance of music segmentation algorithms leveraging the power of deep learning and data-driven feature learning to improve upon traditional, manually-engineered methods of music segmentation.
 
-Beyond music structure applications, modern advancements in neural networks have facilitated the creation of condensed numerical representations that capture critical musical characteristics.
-This progress has streamlined the calculation process for various task-specific elements.
-Such tasks include:
-
-\begin{itemize}
-\item Developing an audio embedding method that excels across numerous applications without the need for fine-tuning \cite{Turian2022HEAR:Representations}
-\item Enhancing environmental sound classification \cite{Kim2020OneStrategies, CramerLOOKEMBEDDINGS}
-\item Improving vocal-centric music tasks via cross-domain audio embeddings \cite{Kim2021LearningLoss}
-\item Merging task-specific and pre-trained features to improve audio classification \cite{Hung2022Feature-informedClassification}
-\item Designing a music similarity search engine for video producers \cite{epidemic}
-\item Augmenting Music Emotion Recognition (MER) performance \cite{KohComparisonRecognition}
-\item Investigating the efficacy of speaker recognition pre-trained model embeddings \cite{lightweight}
-\item Embedding songs for similarity comparison via artist identification \cite{contentmusicsimtriplet2020}
-\item Addressing the cross-modal text-to-music retrieval issue \cite{WonEmotionStories}
-\item Facilitating automated music rearrangement \cite{Stoller2018IntuitiveTransitions, Plachouras2023MusicSegmentation}
-\end{itemize}
-
-Moreover, deep audio embeddings provide the advantage of transferability, serving as a basis for multiple tasks.
-This approach conserves computational resources and time compared to training a model from scratch \cite{HamelTransferSimilarity}.
-
-Given their demonstrated effectiveness in the existing literature and their potential for transfer learning, deep audio embeddings hold substantial promise for MIR downstream tasks, and boundary detection is no exception.
-Nevertheless, it remains uncertain whether a general-purpose audio representation can effectively replicate human hearing \cite{Turian2022HEAR:Representations}, even though some techniques have managed to generalize across up to fourteen music understanding tasks \cite{Li2023MERT:Training}.
+Both studies conclude that using deep learning techniques to derive audio embeddings improves the performance of music segmentation algorithms, thus providing a better alternative to traditional manual feature engineering methods.

### 2023-06-15 methods/subsections/deep learning.tex
Updates from Overleaf

@@
 
-Deep learning (DL), a subset of machine learning, employs deep neural networks to decipher hierarchical data representations, allowing models with multiple processing layers to abstract data across numerous levels \cite{LeCun2015DeepLearning}.
+Deep learning (DL), a subset of machine learning, employs deep neural networks (DNNs) to decipher hierarchical data representations, allowing models with multiple processing layers to abstract data across numerous levels \cite{LeCun2015DeepLearning}.
 DL models have significantly improved various domains due to their nonlinear modeling capabilities and scalability with large datasets.
@@
 
-Deep Neural Networks (DNNs), computational models somewhat rooted in biological neural systems, utilize layers of artificial neurons for tasks such as pattern recognition, classification, and regression.
-DNNs evolve by adjusting connections between neurons during learning, a concept initiated in the mid-20th century but modernized with Frank Rosenblatt's single-layer perceptron in 1957, capable of learning linearly separable patterns \cite{perceptron}.
+DNNs, computational models somewhat rooted in biological neural systems, utilize layers of artificial neurons for tasks such as pattern recognition, classification, and regression.
+They evolve by adjusting connections between neurons during learning, a concept initiated in the mid-20th century but modernized with Frank Rosenblatt's single-layer perceptron in 1957, capable of learning linearly separable patterns \cite{perceptron}.
 

### 2023-06-15 methods/subsections/implementation.tex
Updates from Overleaf

@@
 In pattern recognition, models are designed to exhibit robustness against known invariances—transformations of input data—thereby ensuring consistent output.
-Interestingly, even unknown invariances not explicitly considered in the model's design can be accommodated due to the model's inherent learning capacity.
+Even unknown invariances not explicitly considered in the model's design can be accommodated due to the model's inherent learning capacity.
 
-Our implementation is a slight tweak to the \textit{contrastive learning of lusical representations} (CLMR), a method that learns valuable, discriminative music representations without explicit labels by contrasting positive augmentations of a musical piece against negative ones \cite{CLMR2021}.
+Our implementation is a slight tweak to the \textit{contrastive learning of musical representations} (CLMR), a method that learns valuable, discriminative music representations without explicit labels by contrasting positive augmentations of a musical piece against negative ones \cite{CLMR2021}.
 CLMR falls under a subset of ML called self-supervised learning (SSL) \cite{Balestriero2023ALearning}, where models learn independently from unlabeled data to create their supervisory signals \cite{audioselfsupsurvey}.
@@
 As stated above, the methodology of CLMR involves generating different augmentations of the same musical piece to serve as positive pairs while using other pieces as antagonistic pairs.
-The training process, which minimizes a triplet loss function, encourages the model to produce similar representations for positive and dissimilar ones for antagonistic pairs.
+The training process encourages the model to produce similar representations for positive and dissimilar ones for antagonistic pairs.
 
@@
 
-\subsection{Deep Neural Network Architecture}
+\subsection{Deep architecture design}
 
@@
 The architecture comprises identical subnetworks that share the same parameters, improving memory usage and computational efficiency.
-Rather than learning specific features of individual classes, they focus on a similarity metric, making them ideal for limited or imbalanced datasets.
+Rather than learning specific features of individual classes, they focus on a similarity metric, making them ideal for imbalanced datasets.
 Each subnetwork processes an input independently, combining the outputs to yield a similarity score.
@@
 
-The Triple Siamese Network extends this architecture, comparing three input instances instead of two.
+The Triple Siamese Network extends a binary contrastive architecture by comparing three input instances instead of two.
 It aims to learn an embedding space wherein similar instances are closer and dissimilar ones are distant.
@@
 
-This fully convolutional model reduces computational requirements and learns features at different scales through its multi-resolution architecture \ref{tab:samplecnn}.
+With 2.4 million trainable parameters, this fully convolutional model reduces computational requirements and learns features at different scales through its multi-resolution architecture \ref{tab:samplecnntable}.
 
@@
 \caption{Layer specifications for SampleCNN model}
-\label{tab:samplecnn}
+\label{tab:samplecnntable}
 \end{table}
@@
 
-Previous research has utilized Convolutional Neural Networks (CNNs) with various features such as Mel-Scaled Log-magnitude Spectograms (MLS), Self-Similarity Matrices (SSM), and Self-Similarity Lag Matrices (SSLM) as inputs \cite{Hernandez-Olivan2021MusicFeatures}.
+Previous research has utilized CNNs with various features such as Mel-Scaled Log-magnitude Spectograms (MLS), Self-Similarity Matrices (SSM), and Self-Similarity Lag Matrices (SSLM) as inputs \cite{Hernandez-Olivan2021MusicFeatures}.
 However, features derived from raw audio may lack interpretability in some scenarios \cite{Schindler2020DeepTutorial}, and raw audio presents unique advantages despite being computationally demanding.
-It ensures the preservation of the original signal, potentially unearthing novel insights, and allows for direct feature extraction via advanced deep learning models \cite{learning}.
-Nevertheless, it comes with challenges such as high dimensionality due to high sample rates, requiring substantial computational resources.
+It ensures the preservation of the original signal, potentially uncovering novel insights, and allows for direct feature extraction via advanced DL models \cite{learning}.
+Nevertheless, it comes with challenges, such as high dimensionality requiring substantial computational resources.
 Moreover, it is sensitive to noise, adding complexity to the extraction process.
@@
 Time-domain processing naturally handles temporal patterns and sequences in data, thereby avoiding windowing artifacts.
-Although Mel-spectrogram-based methods are effective for various audio-related machine learning tasks, their limitations lie in representing perceptual similarity.
-Spectrograms capture frequency distribution over time.
+Although audio feature-based methods are effective for various audio-related machine learning tasks, their limitations lie in representing perceptual similarity.
+Mel-Scaled Log-magnitude Spectograms, for example, capture frequency distribution over time.
 Yet, the complexity of human auditory perception—encompassing temporal patterns, phase relationships between frequencies, and higher-level musical structures—means that musically similar sounds can have distinct spectrograms.
@@
 
-The positive image in every triplet of input data must preserve its intelligible content when subjected to transformations, regardless of alterations in sonic qualities and artifacts.
-Maintaining the temporal structure and meaningfulness of the content allows it to present musical elements identical or remarkably close to the original track.
+The positive image in every triplet of input data must preserve its intelligible content when subjected to transformations, regardless of alterations in sonic qualities and processing artifacts.
+Maintaining the temporal structure and meaningfulness of the content allows it to present musical elements remarkably close to the original track.
 
-While we have experimented with helpful audio augmentation tools \cite{Spijkervet2021Spijkervet/torchaudio-augmentations:V1.0, Kharitonov2020DataDomain}, the specific requirements of our experiments necessitated the development of our transformation chain using \textit{torchaudio}'s \cite{Yang2021TorchAudio:Processing} implementation of \textit{SoX} \cite{sox}: given an anchor audio signal $A[n]$, we generate a positive signal $P[n]$ by applying a series of amplitude, time-domain, frequency-domain, modulation, reverberation, and nonlinear effects with additive noise on top of it.
+While we have experimented with helpful audio augmentation tools \cite{Spijkervet2021Spijkervet/torchaudio-augmentations:V1.0, Kharitonov2020DataDomain}, the specific requirements of our experiments required the development of our transformation chain using \textit{torchaudio}'s \cite{Yang2021TorchAudio:Processing} implementation of \textit{SoX} \cite{sox}: given an anchor audio signal $A[n]$, we generate a positive signal $P[n]$ by applying a series of amplitude, time-domain, frequency-domain, modulation, reverberation, and nonlinear effects with additive noise on top of it.
 
-\textbf{Amplitude effects}, we use gain to modify the signal's amplitude with a constant factor $g \in [-12, 0]$.
+\textbf{Amplitude effects}: The signal's amplitude is modified by a constant factor using gain $g \in [-12, 0]$.
 
-\textbf{Time-domain effects} such as speed change and stretch alter the signal's playback speed and duration without changing its pitch, respectively.
-The speed and stretch factors are $\alpha \in [0.9, 1.1]$ for speed change and $\beta \in [0.9, 1.1]$ for the stretch factor.
+\textbf{Time-domain effects}: The signal's playback speed and duration are altered through speed change and stretching, preserving the perceptual musical relationships.
+The respective factors are $\alpha \in [0.9, 1.1]$ for speed change and $\beta \in [0.9, 1.1]$ for stretch.
 
-\textbf{Frequency-domain effects} adjust the frequency content or pitch of the signal, as in pitch shifting, which alters the pitch by $\Delta p \in [-1200, 1200]$.
+\textbf{Frequency-domain effects}: The frequency content is adjusted through pitch-shifting, modifying the pitch by $\Delta p \in [-1200, 1200]$ cents.
 
-\textbf{Nonlinear effects} such as overdrive add harmonic distortion using the parameter $d \in [0, 30]$ for overdrive
+\textbf{Nonlinear effects}: Nonlinear distortion is introduced via overdrive with a parameter $d \in [0, 30]$.
 
-\textbf{Modulation effects}, including chorus and tremolo, use a control signal or low-frequency oscillator.
-The specified ranges determine the chorus parameters and the tremolo's amplitude modulation frequency and depth $f_m \in [0.1, 100]$ for the tremolo's modulation frequency and $d_m \in [1, 101]$ for the tremolo's depth
+\textbf{Modulation effects}: Effects such as chorus and tremolo employ a control signal or low-frequency oscillator.
+The specified ranges determine the chorus parameters, while the tremolo's amplitude modulation frequency and depth are controlled by $f_m \in [0.1, 100]$ and $d_m \in [1, 101]$, respectively.
 
-\textbf{Reverberation effects} simulate physical space's acoustic reflections and reverberations, like reverb that applies an impulse response $h_R[n]$.
+\textbf{Reverberation effects}: These effects simulate a physical space's acoustic reflections and reverberations by applying an impulse response $h_R[n]$.
 
-Finally, \textbf{Noise effects} add a noise signal $N[n]$ with a signal-to-noise ratio (SNR) in the range $[12, 100]$.
+\textbf{Noise effects}: A noise signal $Noise[n]$ is added with a signal-to-noise ratio (SNR) in the range $[12, 100]$.
 
-The positive signal $P[n]$ is generated according to the equation given below, where the symbols denote specific effects as indicated:
+The positive signal $P[n]$ is generated according to the expression given below, where the symbols denote specific effects as indicated:
 
 \begin{equation}\label{eq:positive_signal}
-P[n] = A[n] \ast h_{G}[n] \ast h_{C}[n] \ast h_{D}[n] \ast h_{P_t}[n] \ast h_{R}[n] \ast h_{S}[n] \ast h_{T}[n] \ast h_{T_m}[n] + N[n]
+P[n] = A[n] \ast h_{G}[n] \ast h_{C}[n] \ast h_{D}[n] \ast h_{P_t}[n] \ast h_{R}[n] \ast h_{S}[n] \ast h_{T}[n] \ast h_{T_m}[n] + Noise[n]
 \end{equation}
@@
 The $\ast$ symbol represents convolution, and the various $h$ symbols indicate the impulse responses of specific effects. The noise signal $N[n]$ is included with a specific SNR.
+
+Random parameter updates within hardcoded ranges generate unique audio $P[n]$ out of $A[n]$ for each run-through.
+Adding random white noise and varying SNR creates countless noisy waveform variations.
+Although possible combinations can be estimated by multiplying discrete parameter values, the presence of continuous parameters and randomness in noise generation effectively results in infinite unique audio versions.
 
@@
 
-The computation goes as follows:
+The computation for the negative signal $N[n]$ per every $A[n]$ goes as follows:
 
@@
 \begin{equation}\label{eq:negative_signal}
-N = C_{\sigma(1)} \oplus C_{\sigma(2)} \oplus \ldots \oplus C_{\sigma(n)}
+N[n] = C_{\sigma(1)} \oplus C_{\sigma(2)} \oplus \ldots \oplus C_{\sigma(n)}
 \end{equation}
@@
 
-Contrastive loss and triplet loss are two prominent loss functions employed in the fields of feature learning, similarity learning, and dimensionality reduction.
-
 Schroff, F., Kalenichenko, D., and Philbin, J.
@@
 
-Triplet loss function directs the learning process by endeavoring to minimize the distance between the anchor and positive instances and maximize the distance between the anchor and negative instances.
-Contrastive loss, on the other hand, works on pairs of instances \cite{supercontrast}.
-The inclusion of a margin parameter in the loss function guarantees a minimum separation between positive and negative instances in the embedding space.
-Given the nature of our training needs, we propose to train by using the former.
+On the contrary of the also popular contrastive loss \cite{supercontrast}, the triplet loss function directs the learning process by minimizing the distance between the anchor and positive instances \textbf{and} maximizing the distance between the anchor and negative instances.
+Including a margin parameter in the loss function guarantees a minimum separation between positive and negative instances in the embedding space.
 
@@
 
-\subsubsection{Training strategy}
+\subsubsection{Hardware and training strategy}
+
+The deep learning models were trained on a high-performance cloud computing setup hosted on \href{https://cloud.google.com/}{Google Cloud Platform}.
+The machine was of type \texttt{n1-standard-32}, equipped with an Intel Skylake processor and four NVIDIA Tesla T4 GPUs.
+The multiple GPUs allowed for efficient parallel processing, significantly reducing the training time for the deep learning models.
 

### 2023-06-15 results/subsections/tables.tex
Updates from Overleaf

@@
-The evaluation results have been obtained using the standard and most commonly used MIR's tools and frameworks such as MSAF \cite{NietoMSAF:FRAMEWORK} for the segmentation algorithms, the SALAMI dataset \cite{Smith2011DESIGNANNOTATIONS} as evaluation ground truth and $mir_eval$ \cite{RaffelMir_eval:METRICS} for metric computation.
+The evaluation results have been obtained using the standard and most commonly used MIR's tools and frameworks such as default values of MSAF \cite{MSAF} for the segmentation algorithms \cite{sf}, the SALAMI dataset \cite{Smith2011DESIGNANNOTATIONS} as evaluation ground truth and $mir_eval$ \cite{RaffelMir_eval:METRICS} for metric computation.
 
@@
 \end{tabularx}
-\caption[Comparison of precision, recall, and f-measure for different audio features]{Comparison of precision, recall, and f-measure for different features using the SALAMI dataset.
+\caption[Comparison of precision, recall, and f-measure for different audio features]{Comparison of precision, recall, and f-measure for different features obtained using the SF algorithm \cite{sf} on the SALAMI dataset.
 Sliding windowed segments across the audio signal input signal is 4 seconds}
@@
 \caption[Baseline.
-State-of-the-art table.]{\small{Previous studies' boundary detection f-measure results using unsupervised methods for a 0.5s time-window tolerance.
+State-of-the-art table.]{\small{Previous studies' boundary detection f-measure results using \textbf{unsupervised} methods for a 0.5s time-window tolerance.
 Only the top-performing algorithm for each year on the SALAMI dataset is displayed.

### 2023-06-16 evaluation/evaluation.tex
Updates from Overleaf

@@
 Below is a detailed explanation of how we compute the \textit{embeddiogram} from a given audio signal of length $N$.
-This process comprises loading the audio data, slicing the audio data into windowed segments, processing each window using a pre-trained model to produce an embedding per window/time-frame, collecting and stacking these embeddings, and finally normalizing the resulting matrix or as we like to call it, \textit{embeddiogram}.
+This process comprises loading the audio data, slicing the audio data into windowed segments, processing each window using our pre-trained model to produce a vector per window/time-frame, collecting and stacking these embeddings, and finally normalizing the resulting matrix or as we like to call it, the \textit{embeddiogram}.
 

### 2023-06-17 evaluation/evaluation.tex
Updates from Overleaf

@@
 
-\item \textbf{Process each window}: Each window of audio data is processed independently, passed through the pre-trained neural network model, and transformed into an embedding vector.
+\item \textbf{Process each window}: Each window of audio data is processed independently, passed through the pre-trained neural network, and transformed into an embedding vector.
 Formally, for each window $w_i$ of audio data, we have:
@@
 
+Employing such embeddings in a traditional music segmentation algorithm can obtain state-of-the-art performance \cite{deepfeaturesegment}
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Music boundary detection as downstream task}

### 2023-06-29 discussion/discussion.tex
Updates from Overleaf

@@
-\chapter{Discussion}
+\chapter{Conclusions}
 
-XXXXXXXXXXX
+\section{Conclusions}
+
+In this work, we introduced a method that leverages self-supervised deep neural networks to learn low-dimensional music latent representations with applications to music boundary detection.
+Building on existing approaches and architectures, we replaced traditional features with deep embeddings trained to represent high-level musical content information to analyze its performance in music segmentation tasks.
+
+While not outperforming state-of-the-art results or traditional audio features in contrast to research such \cite{deepfeaturesegment, SalamonDeepSegmentation}, our musically-informed technique has significant potential for boundary detection tasks given its outstanding performance in accuracy metrics and overall performance improvement alongside the training set enlargement (GTZAN compared to Million Song Dataset).
+Most likely, so does for nearly all MIR downstream tasks that are not purely sonic-based.
+
+The questions of whether such general-purpose audio representation can mimic human hearing \cite{Li2023MERT:Training, Turian2022HEAR:Representations} or whether these do decode underlying high-level musical content effectively remain scientifically unanswered given the lack of evaluation in that regard.
+That is a "thorn in our side" that we will pursue.
 
@@
 
-\section{Conclusions}
-
-In this work, we introduced a method to uncover underlying high-level musical
-content in the temporal domain by leveraging self-supervised deep neural networks to learn low-dimensional music latent representations with applications to music boundary detection.
-Building on existing approaches and architectures, we replaced traditional features with deep embeddings trained to represent high-level musical content information.
-
 \newpage

### 2023-06-29 evaluation/evaluation.tex
Updates from Overleaf

@@
 
+We have conducted experiments using a window duration of 4 seconds (\(w = 4 \times \text{{sr (Hz)}}\)).
+As a general rule of thumb, this duration corresponds to two 4/4 bars of a piece of music with a tempo where the quarter note equals 120 BPM.
+
 \item \textbf{Process each window}: Each window of audio data is processed independently, passed through the pre-trained neural network, and transformed into an embedding vector.
@@
 
-\item \textbf{Normalize the \textit{embeddiogram}}: The \textit{embeddiogram} is normalized to have a minimum value of 0 and a maximum value of 1 per dimension. The normalization process is given by:
+\item \textbf{Normalize the \textit{embeddiogram \ref{fig:embeddiogram}}}: The \textit{embeddiogram} is normalized to have a minimum value of 0 and a maximum value of 1 per dimension.
+The normalization process is given by:
 \begin{equation}
@@
     \caption[Embeddiogram. Track 355 (SALAMI dataset).]{Embeddiogram. Track 391 (SALAMI dataset).}
-    \label{fig:image1}
+    \label{fig:embeddiogram}
   \end{minipage}
@@
     \caption[Novelty curve + peaks. Track 391 (SALAMI dataset).]{Novelty curve + peaks. Track 355 (SALAMI dataset).}
-    \label{fig:image2}
+    \label{fig:novelty}
   \end{minipage}
@@
         \includegraphics[width=0.9\textwidth]{figures/images/355recurrencematrix.png} % first figure itself
-        \caption[Track 355 (SALAMI dataset) Self-similarity matrix]{Self-similarity matrix. Track 355 (SALAMI dataset).}
+        \caption[Track 355 (SALAMI dataset) Self-similarity matrix]{Self-similarity matrix computation of the embeddiogram. Track 355 (SALAMI dataset).}
+        \label{fig:SSM}
     \end{minipage}\hfill
@@
         \includegraphics[width=0.9\textwidth]{figures/images/355lagmatrixgaussiansmoothing.png} % second figure itself
-        \caption[Track 355 (SALAMI dataset) Self-similarity lag matrix]{Self-similarity lag matrix. Track 355 (SALAMI dataset).}
+        \caption[Track 355 (SALAMI dataset) Self-similarity lag matrix computation of the embeddiogram]{Self-similarity lag matrix. Track 355 (SALAMI dataset).}
+        \label{fig:SSLM}
     \end{minipage}
@@
         \includegraphics[width=0.9\textwidth]{figures/images/355cumulativematrix.png} % third figure itself
-        \caption[Track 355 (SALAMI dataset). Q-matrix]{Cumulative matrix. Track 355 (SALAMI dataset).}
+        \caption[Track 355 (SALAMI dataset). Q-matrix]{Cumulative matrix computation of the embeddiogram. Track 355 (SALAMI dataset).}
+        \label{fig:Q}
     \end{minipage}\hfill
@@
         \includegraphics[width=0.9\textwidth]{figures/images/355transitivebinarysimilaritymatrix.png} % fourth figure itself
-        \caption[Track 355 (SALAMI dataset). Transitive Binary Similarity Matrix]{Transitive Binary Matrix. Track 355 (SALAMI dataset).}
+        \caption[Track 355 (SALAMI dataset). Transitive Binary Similarity Matrix]{Transitive Binary Matrix computation of the embeddiogram. Track 355 (SALAMI dataset).}
+        \label{fig:TBSM}
     \end{minipage}
@@
 
-Employing such embeddings in a traditional music segmentation algorithm can obtain state-of-the-art performance \cite{deepfeaturesegment}
+Furthermore, these embeddiograms are a foundation for current state-of-the-art methods, which are expected to receive as input standard audio features.
+Consequently, they can be processed and manipulated like conventional features \ref{fig:SSM} \ref{fig:SSLM} \ref{fig:Q} \ref{fig:TBSM} \ref{fig:novelty}.
+Employing such embeddings in a traditional music segmentation algorithm can achieve state-of-the-art performance \cite{deepfeaturesegment}.
 
@@
 
-While the usefulness of deep audio embeddings can be evaluated in countless downstream tasks \cite{Li2023MERT:Training, Kim2020OneStrategies}, we have chosen music boundary detection, a subset of Music Structure Analysis (MSA) for its popularity \cite{Smith2013ATask}, complexity, and product-compelling nature.
+While the usefulness of deep audio embeddings can be evaluated in countless downstream tasks \cite{Li2023MERT:Training, Kim2020OneStrategies}, we have chosen music boundary detection, a subset of music structure analysis (MSA) for its popularity \cite{Smith2013ATask}, complexity, and product-compelling nature.
 This interdisciplinary field aims to understand the structure of music \cite{Nieto2020Audio-BasedApplications}.
@@
 
-All the evaluation experiments have been wrapped around MSAF \cite{NietoMSAF:FRAMEWORK}, a popular framework for Music Structure Analysis.
+All the evaluation experiments have been wrapped around MSAF \cite{MSAF}, a popular framework for MSA.
 
@@
 Three primary metrics have been utilized to assess the model performance: Precision, Recall, and F-measure.
+
 Precision quantifies the proportion of accurately identified boundaries relative to all estimated boundaries to indicate the algorithm's accuracy in boundary detection.

### 2023-06-29 introduction/Subsections/Assumptions.tex
Updates from Overleaf

@@
 This thesis posits that enduring, high-level musical elements persist regardless of sonic changes and constantly evolve within their context, mirroring the nature of sheet music's symbolic domain.
-A single waveform can correspond to a finite set of representations, but one music piece can yield infinite interpretations, varying by factors such as instruments and performance styles.
+A single waveform can correspond to a finite set of representations.
+Still, one music piece can yield infinite interpretations, varying by factors such as instruments and performance styles, to name a very few.
 
-The premise of our work is that regardless of the waveform or production style, abstract high-level features can be discerned, offering objective and thorough insight into a composition's musical content, analogous to analyzing sheet music for its basic behaviors.
+The premise of our work is that regardless of the waveform or production style, abstract high-level features can be discerned, offering objective and thorough insight into a composition's musical content, analogous to analyzing sheet music for its basic behaviors \ref{fig:Wandrers Nachtlied, Op.
+4, D.
+224}.
+
+%%%%%%%%%%%%%%%%%%
+
+\begin{figure}[ht]
+\includegraphics[clip,width=\columnwidth]{figures/schenkerian analysis/SchubertOp4no3.png}% 
+\caption[Excerpt of \textit{Wandrers Nachtlied, Op.
+4, D.
+224} by Franz Schubert.]{\small{Small excerpt of \textit{Wandrers Nachtlied, Op.
+4, D.
+224} by Franz Schubert.
+Passage's original score, the schenkerian unfolding of the melody, the chord degrees analysis, and their tonal function.}}
+\label{fig:Wandrers Nachtlied, Op. 4, D. 224}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%
 
@@
 Despite differing cultural contexts, styles, time and key signatures, and sonic properties, we suggest a commonality between figures \ref{fig:mahler} and \ref{fig:giant_steps}.
-Both pieces display the same 'musicological fingerprint,' derived from their melodic and harmonic contour envelopes through non-diatonic major thirds.
+Both pieces display the same 'musicological flavor', derived from their melodic and harmonic contour envelopes through non-diatonic major thirds.
 
@@
         }
-    \caption[Giant Steps]{\small{John Coltrane's Giant Steps head: A testament to harmonic exploration, featuring rapid chord changes in non-diatonic major thirds.}}
+    \caption[Giant Steps]{\small{John Coltrane's Giant Steps head, featuring rapid chord changes in non-diatonic major thirds.}}
     \label{fig:giant_steps}

### 2023-06-29 introduction/Subsections/Introduction.tex
Updates from Overleaf

@@
 Instead, it specifies this study's concentration on a particular cultural context.}, a cornerstone of human culture and history, has developed hand in hand with our societies since ancient times.
-However, the study of music is complex due to its inherent subjectivity, ever-changing ground truth, and the array of styles and cultural contexts it encompasses.
+However, its study presents unique challenges due to its subjectivity, fluctuating ground truth, and the vast array of styles and cultural contexts it encompasses.
 
@@
 The challenge lies in acquiring annotated data for these feature transformations, which can be time-consuming and expensive.
-In response, scholars have turned to unsupervised deep learning using readily available music audio \cite{unsupervisedlearndeepfeat, GrillMUSICANNOTATIONS}.
+In response, scholars have turned to unsupervised deep learning using readily available music audio \cite{deepfeaturesegment, Grill2015MusicAnnotations}.
 This method has substantially improved the generalization capacity of machine-listening models in downstream applications.
@@
 
-Beyond applications in music structure, the evolution of neural networks has empowered the creation of condensed numerical representations encapsulating crucial musical traits.
+Beyond applications in music structure analysis, the evolution of neural networks has empowered the creation of condensed numerical representations encapsulating crucial musical traits, technically known as representation learning.
 This evolution has simplified the computational process for various task-specific elements, including but not limited to:
@@
 Furthermore, deep audio embeddings offer the benefit of transferability, establishing a foundation for multiple tasks.
-Compared to training a model from scratch, this approach saves computational resources and time \cite{}.
+Compared to training a model from scratch, this approach saves computational resources and time \cite{transferMIR2013, CifkaDeepTransfer}.
 
-Given the proven effectiveness of deep audio embeddings in existing research and their potential for transfer learning, they hold considerable promise for Music Information Retrieval (MIR) downstream tasks, including boundary detection.
-However, it is yet to be determined whether a general-purpose audio representation can successfully emulate human hearing \cite{Turian2022HEAR:Representations}, even though some techniques have demonstrated generalizability across as many as fourteen music-understanding tasks \cite{Li2023MERT:Training}.
+Given the proven effectiveness of deep audio embeddings in existing research and their potential for transfer learning, they hold considerable promise for MIR downstream tasks, including boundary detection.
+However, it is yet to be determined whether a general-purpose audio representation can successfully emulate human hearing \cite{Turian2022HEAR:Representations}, even though some techniques have demonstrated generalizability across many music-understanding tasks \cite{Li2023MERT:Training}.
+
+Yet, despite these strides, deep learning's role in music understanding remains relatively nascent, with scarce work on deep music representations, a dearth of large-scale datasets, and a lack of a universal community-driven benchmark \cite{Yuan2023MARBLE:Evaluation}.

### 2023-06-29 introduction/Subsections/Motivation.tex
Updates from Overleaf

@@
 
-The collaboration aims to deepen our understanding of music's fundamental structures, which could enhance ES's technical offerings and further advancements in music information retrieval (MIR) research.
+The collaboration aims to deepen our understanding of music's fundamental structures, which could enhance ES's technical offerings and further advancements in MIR research.
 
-As a musician, enthusiast, and scholar, my passion for music has driven me to investigate the foundational elements of musical composition, various creation techniques, and their intricate relationships.
-I am dedicated to extracting valuable information embedded within music across all domains, with a particular focus on audio and symbolic.
+As a musician, my passion for music has driven me to investigate the foundational elements of musical composition, various creation techniques, and their intricate relationships.
+I am dedicated to extracting valuable information embedded within music across all domains, focusing on audio and sheet music (symbolic domain).
 Musicians who endeavor to bridge the gap and uncover musical truths within the tonal paradigm, such as Heinrich Schenker \cite{Komar1959SchenkersStructure}, or those who challenge it, like Arnold Schoenberg \cite{Samson1974SchoenbergsMusic}, George Russell \cite{LydianRussell}, and Ernst Levy \cite{LevyAHarmony}, have been a continual source of inspiration.
@@
 Advancements in AI research, building on the theoretical groundwork laid by pioneers such as Alan Turing and Claude Shannon, have led to significant breakthroughs \cite{Vaswani2017AttentionNeed}.
-With AI being applied broadly in popular products \cite{OpenAI2023GPT-4Report}, researchers and corporations alike must stay abreast of this rapidly evolving field.
+With AI being applied broadly in skyrocketing popular products \cite{OpenAI2023GPT-4Report}, researchers and corporations must stay abreast of this rapidly evolving field.
 The emergence of self-supervised models capable of learning embedding spaces to retrieve musical content from audio signals presents new opportunities.
-These models, which autonomously extract high-level semantic information from raw audio data, can potentially transform multiple aspects of the music industry.
+These models, which autonomously extract information from audio data, can potentially transform multiple aspects of the music industry.
 Industrially, these embedding spaces can be used to devise innovative products, enhance user experiences for content creators, and stimulate innovation and collaboration across the industry.
@@
 Traditionally, MIR research has focused primarily on technical aspects, perhaps overlooking relevant areas such as perception, cognition, music theory, musicology, aural skills, and high-level perceptual concepts.
-Purely mathematical approaches may not accurately represent human music perception and could miss subtle variations in timing or harmonic relationships essential to the musical experience.
+Purely mathematical approaches may not accurately represent human music perception and could miss subtle details essential to the musical experience \cite{neglecteduser2013}.
 Therefore, MIR research should strive for a balanced approach, recognizing the interdisciplinary nature of music and the importance of areas beyond digital signal processing.
-
-%%%%%%%%%%%%%%%%%%
-
-\begin{figure}[ht]
-\includegraphics[clip,width=\columnwidth]{figures/schenkerian analysis/SchubertOp4no3.png}% 
-\caption[Excerpt of \textit{Wandrers Nachtlied, Op.
-4, D.
-224} by Franz Schubert.]{\small{Small excerpt of \textit{Wandrers Nachtlied, Op.
-4, D.
-224} by Franz Schubert.
-Passage's original score, the schenkerian unfolding of the melody, the chord degrees analysis, and their tonal function.}}
-\label{fig:Wandrers Nachtlied, Op. 4, D. 224}
-\end{figure}

### 2023-06-29 introduction/Subsections/Objectives.tex
Updates from Overleaf

@@
 
-Can deep audio embeddings be learned from reordering and scrambling sequences of musical information, and can audio effects be added to improve unsupervised music boundary detection?
+Can deep audio embeddings be learned from reordering, scrambling, and augmenting via audio effects sequences of musical information to improve unsupervised music boundary detection?
 
@@
 
-This study aims to develop and learn a unified numerical understanding (or embedding \footnote{A learned representation or embedding is a numerical output - usually a fixed-size vector - produced by a machine-learning model.
+Our research aims to develop and learn a unified numerical understanding (or embedding \footnote{A learned representation or embedding is a numerical output - usually a fixed-size vector - produced by a machine-learning model.
 Good representations should be versatile across various tasks and require limited supervision \cite{Turian2022HEAR:Representations}.}) for a piece of music that integrates the high-level relationships between musical elements as they unfold over time.
@@
 
-This approach seeks to replicate human auditory capabilities by understanding and identifying abstract and semantic musical elements independent of their sonic qualities.
+This approach replicates human auditory capabilities by understanding and identifying abstract and semantic musical elements independent of their sonic qualities.

### 2023-06-29 introduction/Subsections/Previous work.tex
Updates from Overleaf

@@
 
-Related research such as \cite{SalamonDeepSegmentation} and \cite{deepfeaturesegment} explore how the use of audio embeddings learned via unsupervised methods can enhance the performance of music segmentation algorithms leveraging the power of deep learning and data-driven feature learning to improve upon traditional, manually-engineered methods of music segmentation.
+Related research such as \cite{deepfeaturesegment, SalamonDeepSegmentation} explore how the use of audio embeddings learned via unsupervised methods can enhance the performance of music segmentation algorithms leveraging the power of deep learning and data-driven feature learning to improve upon traditional, manually-engineered methods of music segmentation.
 

### 2023-06-29 results/subsections/tables.tex
Updates from Overleaf

--- 2023-06-13 results/subsections/tables.tex
@@
-The evaluation results have been obtained using the standard and most commonly used MIR's tools and frameworks such as MSAF \cite{NietoMSAF:FRAMEWORK} for the segmentation algorithms, the SALAMI dataset \cite{Smith2011DESIGNANNOTATIONS} as evaluation ground truth and $mir_eval$ \cite{RaffelMir_eval:METRICS} for metric computation.
+The evaluation results have been obtained using the standard and most commonly used MIR's tools and frameworks, such as default values of MSAF \cite{MSAF} for the segmentation algorithms \cite{sf}, the SALAMI dataset \cite{Smith2011DESIGNANNOTATIONS} as evaluation ground truth and $mir_eval$ \cite{RaffelMir_eval:METRICS} for metric computation.
 
@@
 \end{tabularx}
-\caption[Comparison of precision, recall, and f-measure for different audio features]{Comparison of precision, recall, and f-measure for different features using the SALAMI dataset.
+\caption[Metric comparison for different audio features]{Comparison of precision, recall, and f-measure for different features obtained using the SF algorithm \cite{sf} on the SALAMI dataset.
 Sliding windowed segments across the audio signal input signal is 4 seconds}
@@
 \addlinespace
+Turnbull et al. \cite{Turnbull2007ABOOSTING}, 2007 & MFCCs, chromas, spectrogram & Boosted Decision Stump  & 0.378 \\
+\addlinespace
 Kaiser et al. \cite{27}, 2012 & SSM & Novelty measure  & 0.286 \\
@@
 \addlinespace
-Turnbull et al. \cite{Turnbull2007ABOOSTING}, 2007 & MFCCs, chromas, spectrogram & Boosted Decision Stump  & 0.378 \\
-\addlinespace
 Sargent et al. \cite{34}, 2011 & MFCCs, chromas & Viterbi  & 0.356 \\
@@
 \addlinespace
-Grill \& Schlüter \cite{4}, 2015 & MLS, SSLMs & CNN  & \textbf{0.523} \\
+Grill \& Schlüter \cite{4}, 2015 & MLS, SSLMs & CNN  & 0.523 \\
 \addlinespace
-Grill \& Schlüter \cite{GrillMUSICANNOTATIONS}, 2015 & MLS, PCPs, SSLMs & CNN  & 0.508 \\
+Grill \& Schlüter \cite{Grill2015MusicAnnotations}, 2015 & MLS, PCPs, SSLMs & CNN  & 0.508 \\
 \addlinespace
 Hadria \& Peeterss \cite{35}, 2017 & MLS, SSLMs & CNN  & 0.291 \\
+\addlinespace
+\cite{deepfeaturesegment}, 2019 & XXXX & CNN  & \textbf{0.535} ± 0.15 \\
+\addlinespace
+\cite{sf}, 2021 & XXXX & CNN  & XXX \\
+\addlinespace
+Ours, 2023 & Raw waveforms & CNN  & 0.288 \\
 \bottomrule
@@
 Only the top-performing algorithm for each year on the SALAMI dataset is displayed.
-Original source \cite{Hernandez-Olivan2021MusicFeatures}}}
+This table has been extended from \cite{Hernandez-Olivan2021MusicFeatures}}}
 \label{tab:comparison_table}

### 2023-06-29 MasterThesis.tex
Updates from Overleaf

@@
 \usepackage{makecell}
+\usepackage[utf8]{inputenc}
+\usepackage{multirow}
+\usepackage{threeparttable}
+\usepackage{adjustbox}
 
@@
   Uncovering underlying high-level musical content in the time domain \\
-  \small Leveraging self-supervised deep neural networks, inductive bias, and aural skills to learn deep audio embeddings with applications to MIR downstream tasks}
+  \small Leveraging self-supervised deep neural networks, inductive bias, and aural skills to learn deep audio embeddings with applications to boundary detection tasks}
 
@@
 \submitdate{July 2023}
-\supervisor{Carlos Lordelo and Carl Thomé}
+\supervisor{Carl Thomé and Carlos Lordelo}
 \cosupervisor{Frederic Font}

### 2023-06-29 discussion/discussion.tex
Updates from Overleaf

@@
 
-While not outperforming state-of-the-art results or traditional audio features in contrast to research such \cite{deepfeaturesegment, SalamonDeepSegmentation}, our musically-informed technique has significant potential for boundary detection tasks given its outstanding performance in accuracy metrics and overall performance improvement alongside the training set enlargement (GTZAN compared to Million Song Dataset).
+While not outperforming state-of-the-art results or traditional audio features in contrast to other research findings such \cite{deepfeaturesegment, SalamonDeepSegmentation}, our musically-informed technique has significant potential for boundary detection tasks given its outstanding performance in accuracy metrics and overall performance improvement alongside the training set enlargement (GTZAN compared to Million Song Dataset).
 Most likely, so does for nearly all MIR downstream tasks that are not purely sonic-based.
@@
 
-XXXXXX
+While these do decode underlying high-level musical content effectively remain scientifically unanswered, the outstanding performance in precision metric
 

### 2023-06-29 results/results.tex
Updates from Overleaf

@@
     \centering
-    \includegraphics[width=\textwidth]{figures/images/first results.png}
-    \caption{Caption}
+    \includegraphics[width=\textwidth]{figures/images/metrics.png}
+    \caption[Metric comparison for different audio features.
+Boxplot]{Boxplot visual comparison of precision, recall, and f-measure for different features obtained using the SF algorithm \cite{sf} on the SALAMI dataset.
+Sliding windowed segments across the audio signal input signal is 4 seconds}
     \label{fig:boxplotmetrics}
@@
     \centering
-    \includegraphics[width=\textwidth]{figures/images/f-measure.png}
-    \caption{Caption}
+    \includegraphics[width=\textwidth]{figures/images/boudaryfscore.png}
+    \caption[F-measure comparison for different audio features.
+Boxplot]{Boxplot visual comparison of f-measure for different features obtained using the SF algorithm \cite{sf} on the SALAMI dataset.
+Sliding windowed segments across the audio signal input signal is 4 seconds}
     \label{fig:boxplotfmeasure}

### 2023-06-29 results/subsections/tables.tex
Updates from Overleaf

@@
 
-\begin{table}[h]
+\newsavebox\mfccSF
+\begin{lrbox}{\mfccSF}
 \centering
-\begin{tabularx}{\textwidth}{|X|X|X|X|X|}
-\hline
-\textbf{Technique} & \textbf{Training Dataset} & \textbf{Precision} & \textbf{Recall} & \textbf{F-measure} \\
-\hline
-MFCC & -- & 0.173 & 0.185 & 0.172 \\
-\hline
-Embeddiogram & GTZAN Dataset & 0.228 & 0.171 & 0.185 \\
-\hline
-Embeddiogram & MSD Dataset & \textbf{0.335} & 0.276 & 0.288 \\
-\hline
-PCP & -- & 0.311 & 0.324 & 0.305 \\
-\hline
-Tonnetz & -- & 0.312 & 0.312 & 0.300 \\
-\hline
-CQT & -- & 0.311 & \textbf{0.339} & \textbf{0.312} \\
-\hline
-\end{tabularx}
-\caption[Metric comparison for different audio features]{Comparison of precision, recall, and f-measure for different features obtained using the SF algorithm \cite{sf} on the SALAMI dataset.
-Sliding windowed segments across the audio signal input signal is 4 seconds}
-\label{tab:comparison}
+   $\begin{aligned}
+     0.173 & \quad 0.185 & \quad 0.172 % SF algorithm
+    \end{aligned} $
+\end{lrbox}
+
+\newsavebox\mfccFoote
+\begin{lrbox}{\mfccFoote}
+\centering
+   $\begin{aligned}
+     ... & \quad ... & \quad ... % Foote algorithm
+    \end{aligned} $
+\end{lrbox}
+
+\newsavebox\mfccCNMF
+\begin{lrbox}{\mfccCNMF}
+\centering
+   $\begin{aligned}
+     ... & \quad ... & \quad ... % CNMF algorithm
+    \end{aligned} $
+\end{lrbox}
+
+\newsavebox\embeddioaSF
+\begin{lrbox}{\embeddioaSF}
+   $\begin{aligned}
+     0.228 & \quad 0.171 & \quad 0.185
+    \end{aligned} $
+\end{lrbox}
+
+\newsavebox\embeddioaFoote
+\begin{lrbox}{\embeddioaFoote}
+   $\begin{aligned}
+     ... & \quad ... & \quad ...
+    \end{aligned} $
+\end{lrbox}
+
+\newsavebox\embeddioaCNMF
+\begin{lrbox}{\embeddioaCNMF}
+   $\begin{aligned}
+     ... & \quad ... & \quad ...
+    \end{aligned} $
+\end{lrbox}
+
+\newsavebox\embeddiobSF
+\begin{lrbox}{\embeddiobSF}
+   $\begin{aligned}
+     \textbf{0.333} & \quad 0.280 & \quad 0.288
+    \end{aligned} $
+\end{lrbox}
+
+\newsavebox\embeddiobFoote
+\begin{lrbox}{\embeddiobFoote}
+   $\begin{aligned}
+     0.275 & \quad \textbf{0.318} & \quad 0.280
+    \end{aligned} $
+\end{lrbox}
+
+\newsavebox\embeddiobCNMF
+\begin{lrbox}{\embeddiobCNMF}
+   $\begin{aligned}
+     0.248 & \quad 0.296 & \quad 0.254
+    \end{aligned} $
+\end{lrbox}
+
+\newsavebox\pcpSF
+\begin{lrbox}{\pcpSF}
+   $\begin{aligned}
+     0.311 & \quad 0.324 & \quad 0.305
+    \end{aligned} $
+\end{lrbox}
+
+\newsavebox\pcpFoote
+\begin{lrbox}{\pcpFoote}
+   $\begin{aligned}
+     ... & \quad ... & \quad ...
+    \end{aligned} $
+\end{lrbox}
+
+\newsavebox\pcpCNMF
+\begin{lrbox}{\pcpCNMF}
+   $\begin{aligned}
+     ... & \quad ... & \quad ...
+    \end{aligned} $
+\end{lrbox}
+
+\newsavebox\tonnetzSF
+\begin{lrbox}{\tonnetzSF}
+   $\begin{aligned}
+     0.312 & \quad 0.312 & \quad 0.300
+    \end{aligned} $
+\end{lrbox}
+
+\newsavebox\tonnetzFoote
+\begin{lrbox}{\tonnetzFoote}
+   $\begin{aligned}
+     0.272 & \quad 0.317 & \quad 0.280
+    \end{aligned} $
+\end{lrbox}
+
+\newsavebox\tonnetzCNMF
+\begin{lrbox}{\tonnetzCNMF}
+   $\begin{aligned}
+     0.212 & \quad 0.306 & \quad 0.237
+    \end{aligned} $
+\end{lrbox}
+
+\newsavebox\cqtSF
+\begin{lrbox}{\cqtSF}
+   $\begin{aligned}
+     0.311 & \quad \textbf{0.339} & \quad \textbf{0.312}
+    \end{aligned} $
+\end{lrbox}
+
+\newsavebox\cqtFoote
+\begin{lrbox}{\cqtFoote}
+   $\begin{aligned}
+     \textbf{0.570} & \quad 0.311 & \quad \textbf{0.353}
+    \end{aligned} $
+\end{lrbox}
+
+\newsavebox\cqtCNMF
+\begin{lrbox}{\cqtCNMF}
+   $\begin{aligned}
+     \textbf{0.296} & \quad \textbf{0.311} & \quad \textbf{0.287}
+    \end{aligned} $
+\end{lrbox}
+
+%%%%%
+
+\begin{table}
+  \centering
+  \begin{adjustbox}{width=\textwidth}
+  \begin{threeparttable}
+    \begin{tabular}{c|l|c|c|c} 
+\toprule
+     \multicolumn{2}{c|}{\textbf{Training dataset} and \textbf{Feature}}  & \multicolumn{1}{c}{\textbf{SF}} & \multicolumn{1}{c}{\textbf{Foote}} & \multicolumn{1}{c}{\textbf{CNMF}} 
+     \\ \midrule 
+    \multirow{5}{*}{}&   
+         \multirow{1}{*}{MFCC } & \usebox{\mfccSF} & \usebox{\mfccFoote} & \usebox{\mfccCNMF} \\\cline{2-5}
+        & \multirow{1}{*}{PCP} & \usebox{\pcpSF} & \usebox{\pcpFoote} & \usebox{\pcpCNMF} \\\cline{2-5}
+        & \multirow{1}{*}{Tonnetz} & \usebox{\tonnetzSF} & \usebox{\tonnetzFoote} & \usebox{\tonnetzCNMF} \\\cline{2-5} 
+        & \multirow{1}{*}{CQT} & \usebox{\cqtSF} & \usebox{\cqtFoote} & \usebox{\cqtCNMF} \\\cline{1-5} 
+    \multirow{1}{*}{GTZAN}& 
+        \multirow{1}{*}{Embeddiogram} & \usebox{\embeddioaSF} & \usebox{\embeddioaFoote} & \usebox{\embeddioaCNMF} \\\cline{1-5} 
+    \multirow{1}{*}{MSD}& 
+        \multirow{1}{*}{Embeddiogram} & \usebox{\embeddiobSF} & \usebox{\embeddiobFoote} & \usebox{\embeddiobCNMF} \\\bottomrule
+    \end{tabular}
+    \caption[Metric comparison for different audio features]{Comparison of precision, recall, and f-measure for different features obtained using the SF, Foote, and CNMF algorithms \cite{sf} \cite{foote} \cite{cnmf} on the SALAMI dataset.
+Sliding windowed segments across the audio signal input signal is 4 seconds}\label{ta:results}
+  \end{threeparttable}
+  \end{adjustbox}
 \end{table}

### 2023-06-29 results/subsections/tables.tex
Updates from Overleaf

@@
     \end{tabular}
-    \caption[Metric comparison for different audio features]{Comparison of precision, recall, and f-measure for different features obtained using the SF, Foote, and CNMF algorithms \cite{sf} \cite{foote} \cite{cnmf} on the SALAMI dataset.
+    \caption[Metric comparison for different audio features and different segmentation algorithms]{Comparison of precision, recall, and f-measure for different features obtained using the SF\cite{sf}, Foote \cite{Foote2000AutomaticNovelty}, and CNMF \cite{NietoCONVEXIDENTIFICATION} algorithms on the SALAMI dataset.
 Sliding windowed segments across the audio signal input signal is 4 seconds}\label{ta:results}

### 2023-06-30 discussion/discussion.tex
Updates from Overleaf

@@
 
-While these do decode underlying high-level musical content effectively remain scientifically unanswered, the outstanding performance in precision metric
+While whether our model decodes underlying high-level musical content effectively remains scientifically unanswered, the outstanding performance in precision metric
 
 Too little representation layer?
+
+Too little model for raw audio input? \cite{verydeep}
 

### 2023-06-30 evaluation/evaluation.tex
Updates from Overleaf

@@
 Below is a detailed explanation of how we compute the \textit{embeddiogram} from a given audio signal of length $N$.
-This process comprises loading the audio data, slicing the audio data into windowed segments, processing each window using our pre-trained model to produce a vector per window/time-frame, collecting and stacking these embeddings, and finally normalizing the resulting matrix or as we like to call it, the \textit{embeddiogram}.
+This process comprises loading the audio data, slicing the audio data into windowed segments, processing each window using our pre-trained model to produce a vector per window/time frame, collecting and stacking these embeddings, and finally, normalizing the resulting matrix.
 
@@
 \item \textbf{Slice the audio data}: The audio data is segmented into overlapping windows.
-Each window contains $w$ samples, and consecutive windows are separated by $h$.
+Each window contains $w$ samples, and consecutive windows are separated by a hop size $h$.
 This gives a total of $H$ windows, defined as:
@@
 \end{equation}
-In the case where $\left( N - w \right) \mod h > 0$, we have $H += 1$ to account for the final, potentially smaller, window.
+In the case where $\left( N - w \right) \mod h > 0$, we have $H += 1$ to account for the final, potentially smaller window.
 
@@
 As a general rule of thumb, this duration corresponds to two 4/4 bars of a piece of music with a tempo where the quarter note equals 120 BPM.
+
+We find this to be a good starting compromise solution, allowing enough time span to capture musical content while not being so large that downsampling reduces the information to an unintelligible vector.
 
@@
     \includegraphics[width=\linewidth]{figures/images/355novelty.png}
-    \caption[Novelty curve + peaks. Track 391 (SALAMI dataset).]{Novelty curve + peaks. Track 355 (SALAMI dataset).}
+    \caption[Novelty curve + peaks. Track 391 (SALAMI dataset).]{Novelty curve and peak detection. Track 355 (SALAMI dataset).}
     \label{fig:novelty}
@@
         \includegraphics[width=0.9\textwidth]{figures/images/355lagmatrixgaussiansmoothing.png} % second figure itself
-        \caption[Track 355 (SALAMI dataset) Self-similarity lag matrix computation of the embeddiogram]{Self-similarity lag matrix. Track 355 (SALAMI dataset).}
+        \caption[Track 355 (SALAMI dataset) SSLM computation of the embeddiogram]{Self-similarity lag matrix. Track 355 (SALAMI dataset).}
         \label{fig:SSLM}
@@
         \includegraphics[width=0.9\textwidth]{figures/images/355cumulativematrix.png} % third figure itself
-        \caption[Track 355 (SALAMI dataset). Q-matrix]{Cumulative matrix computation of the embeddiogram. Track 355 (SALAMI dataset).}
+        \caption[Track 355 (SALAMI dataset). Q-matrix]{Cumulative matrix computation of the embeddiogram. Track 355 (SALAMI dataset) .}
         \label{fig:Q}
@@
 
-Furthermore, these embeddiograms are a foundation for current state-of-the-art methods, which are expected to receive as input standard audio features.
-Consequently, they can be processed and manipulated like conventional features \ref{fig:SSM} \ref{fig:SSLM} \ref{fig:Q} \ref{fig:TBSM} \ref{fig:novelty}.
+These deep audio features can be a foundation for current state-of-the-art methods, which are expected to receive as input standard traditional audio features.
+Consequently, they can be processed and manipulated like conventional features as described by \cite{unsuperMSA} and displayed in \ref{fig:SSM}, \ref{fig:SSLM}, \ref{fig:Q}, and \ref{fig:TBSM} \ref{fig:novelty}.
 Employing such embeddings in a traditional music segmentation algorithm can achieve state-of-the-art performance \cite{deepfeaturesegment}.
@@
 
-While the usefulness of deep audio embeddings can be evaluated in countless downstream tasks \cite{Li2023MERT:Training, Kim2020OneStrategies}, we have chosen music boundary detection, a subset of music structure analysis (MSA) for its popularity \cite{Smith2013ATask}, complexity, and product-compelling nature.
+While the usefulness of deep audio embeddings can be evaluated in countless downstream tasks \cite{Li2023MERT:Training, Kim2020OneStrategies}, we have chosen music boundary detection (also known as track segmentation), a subset of music structure analysis (MSA) for its popularity \cite{Smith2013ATask}, complexity, and product-compelling nature.
 This interdisciplinary field aims to understand the structure of music \cite{Nieto2020Audio-BasedApplications}.
-Due to subjectivity, ambiguity, and data scarcity, audio-based MSA faces challenges like boundary placement ambiguity and similarity quantification \cite{NietoPerceptualMusic}.
-
-All the evaluation experiments have been wrapped around MSAF \cite{MSAF}, a popular framework for MSA.
+Due to subjectivity, ambiguity, and data scarcity, audio-based MSA faces non-solved challenges like boundary placement ambiguity and similarity quantification \cite{NietoPerceptualMusic}.
 

### 2023-06-30 future work/future work.tex
Updates from Overleaf

@@
 \chapter{Future Work}
-
-The question as per \cite{Turian2022HEAR:Representations} or \cite{Li2023MERT:Training} remains if such general-purpose audio representation can mimic human hearing.
-That is a "thorn in our side" that we will pursue.
 
@@
 
-Utilize the dB-scale Mel-spectrum magnitude of audio as input data; it is a popular choice for input representation in music-related tasks when applying CNNs, as has been demonstrated in various studies \cite{Kim2020OneStrategies}.
+Utilize the dB-scale Mel-spectrum magnitude and CQT of audio as input data; it is a popular choice for input representation in music-related tasks when applying CNNs, as has been demonstrated in various studies \cite{Kim2020OneStrategies}.
 While raw audio is the most meaningful audio representation, it's been reported that dB-scale Mel-spectrum frequency-domain summarization, grounded in psycho-acoustics, is computationally efficient and challenging to replicate solely through data-driven methods \cite{Kim2020OneStrategies}; therefore, a trade-off that looks worthy of being explored.

### 2023-06-30 introduction/Subsections/Introduction.tex
Updates from Overleaf

@@
 \item Creating an audio embedding method that excels across numerous applications without the necessity for fine-tuning \cite{Turian2022HEAR:Representations}
-\item Boosting the classification of environmental sounds \cite{Kim2020OneStrategies, CramerLOOKEMBEDDINGS}
+\item Boosting the classification of environmental sounds \cite{CramerLOOKEMBEDDINGS}
 \item Enhancing vocal-centric music tasks through cross-domain audio embeddings \cite{Kim2021LearningLoss}
@@
 Given the proven effectiveness of deep audio embeddings in existing research and their potential for transfer learning, they hold considerable promise for MIR downstream tasks, including boundary detection.
-However, it is yet to be determined whether a general-purpose audio representation can successfully emulate human hearing \cite{Turian2022HEAR:Representations}, even though some techniques have demonstrated generalizability across many music-understanding tasks \cite{Li2023MERT:Training}.
+However, it is yet to be determined whether a general-purpose audio representation can successfully emulate human hearing \cite{Turian2022HEAR:Representations}, even though some techniques have demonstrated generalizability across many music-understanding tasks \cite{Li2023MERT:Training, Kim2020OneStrategies}.
 
-Yet, despite these strides, deep learning's role in music understanding remains relatively nascent, with scarce work on deep music representations, a dearth of large-scale datasets, and a lack of a universal community-driven benchmark \cite{Yuan2023MARBLE:Evaluation}.
+Yet, despite these strides, deep learning's role in music understanding remains relatively nascent, with scarce work on deep music representations, a dearth of large-scale datasets, and a lack of a universal community-driven benchmark \cite{Turian2022HEAR:Representations, Yuan2023MARBLE:Evaluation}.

### 2023-06-30 methods/subsections/deep learning.tex
Updates from Overleaf

@@
 
-Deep learning (DL), a subset of machine learning, employs deep neural networks (DNNs) to decipher hierarchical data representations, allowing models with multiple processing layers to abstract data across numerous levels \cite{LeCun2015DeepLearning}.
+Deep learning (DL), a subset of machine learning, employs deep neural networks (DNNs) to decipher hierarchical data representations, allowing models with multiple processing layers to abstract data across numerous levels \cite{LeCun2015DeepLearning, Sarker2021DeepDirections}.
 DL models have significantly improved various domains due to their nonlinear modeling capabilities and scalability with large datasets.

### 2023-06-30 methods/subsections/implementation.tex
Updates from Overleaf

@@
 
-Our implementation is a slight tweak to the \textit{contrastive learning of musical representations} (CLMR), a method that learns valuable, discriminative music representations without explicit labels by contrasting positive augmentations of a musical piece against negative ones \cite{CLMR2021}.
-CLMR falls under a subset of ML called self-supervised learning (SSL) \cite{Balestriero2023ALearning}, where models learn independently from unlabeled data to create their supervisory signals \cite{audioselfsupsurvey}.
-This method resembles how humans learn from observations and interactions, turning unsupervised problems into supervised ones by auto-generating labels.
-Benefits of SSL include reduced dependence on labeled data, which contributes to more robust and generalizable data representations.
+Our implementation offers a slight modification to the \textit{contrastive learning of musical representations} (CLMR), a method that learns valuable, discriminative music representations without explicit labels by contrasting positive augmentations of a musical piece against negative ones \cite{CLMR2021}.
+CLMR falls under a branch of ML known as self-supervised learning (SSL) \cite{Balestriero2023ALearning}, where models learn autonomously from unlabeled data to create their own supervisory signals \cite{audioselfsupsurvey}.
+This method resembles how humans learn from observations and interactions, transforming unsupervised problems into supervised ones by auto-generating labels.
+SSL benefits include reduced dependence on labeled data, contributing to more robust and generalizable data representations.
 
-As stated above, the methodology of CLMR involves generating different augmentations of the same musical piece to serve as positive pairs while using other pieces as antagonistic pairs.
-The training process encourages the model to produce similar representations for positive and dissimilar ones for antagonistic pairs.
+As previously stated, the methodology of CLMR involves generating different augmentations of the same musical piece to serve as positive pairs while using other pieces as negative pairs.
+The training process encourages the model to produce similar representations for positive and dissimilar ones for negative pairs.
 
@@
 
-This work suggests employing a Triple Siamese Network, a model architecture known for its efficacy in music similarity retrieval tasks \cite{contentmusicsimtriplet2020}.
+This work suggests employing a Triple Siamese Network (TSN), a model architecture known for its efficacy in music similarity retrieval tasks \cite{contentmusicsimtriplet2020}.
 The aim is to minimize the loss function between a triplet of anchor, positive, and negative samples, utilizing online triplet mining for optimizing memory resources \cite{Sikaroudi2020OfflinePatches}.
@@
 Training with shared weights enables the model to learn invariant input representation, improving comparison efficiency.
-This is accomplished through specialized loss functions such as contrastive or triplet loss, aiming to minimize the distance between similar inputs and maximize it for dissimilar ones.
+This is accomplished through a specialized loss function called triplet loss, which aims to minimize the distance between similar inputs and maximize it for dissimilar ones.
 
-The Triple Siamese Network extends a binary contrastive architecture by comparing three input instances instead of two.
-It aims to learn an embedding space wherein similar instances are closer and dissimilar ones are distant.
+The TSN extends the binary contrastive architecture by comparing three input instances instead of two.
+It strives to learn an embedding space where similar instances are closer and dissimilar ones are more distant.
 The inputs, consisting of an anchor, a positive instance (similar to the anchor), and a negative instance (dissimilar to the anchor), are processed by identical subnetworks sharing the same parameters.
@@
 
-With 2.4 million trainable parameters, this fully convolutional model reduces computational requirements and learns features at different scales through its multi-resolution architecture \ref{tab:samplecnntable}.
+With only 2.4 million trainable parameters, this fully convolutional model reduces computational requirements and learns features at different scales through its multi-resolution architecture \ref{tab:samplecnntable}.
 
-\begin{table}[h]
+\begin{table}[ht]
 \centering
@@
 
-The original model has been modified slightly to serve our specific needs: the output from the final convolutional layer is now subjected to an average pooling operation.
+The original model has been subtly adjusted by introducing an average pooling operation to the final convolutional layer.
+This modification, dimensionality reduction, is strategic for handling various input data sizes.
+Condensing the feature maps to a fixed-size output ensures consistency for subsequent layers like fully connected ones, streamlining computations while maintaining crucial information.
+This results in a more robust, efficient learning process that offers translation invariance and better contextual understanding.
 
@@
 Previous research has utilized CNNs with various features such as Mel-Scaled Log-magnitude Spectograms (MLS), Self-Similarity Matrices (SSM), and Self-Similarity Lag Matrices (SSLM) as inputs \cite{Hernandez-Olivan2021MusicFeatures}.
-However, features derived from raw audio may lack interpretability in some scenarios \cite{Schindler2020DeepTutorial}, and raw audio presents unique advantages despite being computationally demanding.
-It ensures the preservation of the original signal, potentially uncovering novel insights, and allows for direct feature extraction via advanced DL models \cite{learning}.
+However, features derived from raw audio may lack interpretability in some scenarios \cite{Schindler2020DeepTutorial}, and raw audio presents unique advantages despite being highly computationally demanding.
+It ensures the preservation of the original signal, potentially uncovering novel insights, and allows for direct feature extraction via advanced DL models \cite{learning, verydeep}.
 Nevertheless, it comes with challenges, such as high dimensionality requiring substantial computational resources.
-Moreover, it is sensitive to noise, adding complexity to the extraction process.
 
@@
 Mel-Scaled Log-magnitude Spectograms, for example, capture frequency distribution over time.
-Yet, the complexity of human auditory perception—encompassing temporal patterns, phase relationships between frequencies, and higher-level musical structures—means that musically similar sounds can have distinct spectrograms.
+Yet, the complexity of human auditory perception—encompassing temporal patterns, phase relationships between frequencies, and higher-level musical structures means that musically similar sounds can have distinct spectrograms.
 This discrepancy implies that using spectrogram distance alone for measuring high-level music content may not always align with human perceptions \cite{Kim2020OneStrategies, Mesostructures2023}.
@@
 
-While we have experimented with helpful audio augmentation tools \cite{Spijkervet2021Spijkervet/torchaudio-augmentations:V1.0, Kharitonov2020DataDomain}, the specific requirements of our experiments required the development of our transformation chain using \textit{torchaudio}'s \cite{Yang2021TorchAudio:Processing} implementation of \textit{SoX} \cite{sox}: given an anchor audio signal $A[n]$, we generate a positive signal $P[n]$ by applying a series of amplitude, time-domain, frequency-domain, modulation, reverberation, and nonlinear effects with additive noise on top of it.
+While we have experimented with helpful audio augmentation tools such \cite{Spijkervet2021Spijkervet/torchaudio-augmentations:V1.0, Kharitonov2020DataDomain}, the specific requirements of our experiments required the development of our own transformation chain using \textit{torchaudio}'s \cite{Yang2021TorchAudio:Processing} implementation of \textit{SoX} \cite{sox}: given an anchor audio signal $A[n]$, we generate a positive signal $P[n]$ by applying a series of amplitude, time-domain, frequency-domain, modulation, reverberation, and nonlinear effects with additive noise on top of it.
 
@@
 
-\textbf{Time-domain effects}: The signal's playback speed and duration are altered through speed change and stretching, preserving the perceptual musical relationships.
+\textbf{Time-domain effects}: The signal's playback speed and duration are altered through speed change and stretching, preserving the relative perceptual musical relationships between wave points.
 The respective factors are $\alpha \in [0.9, 1.1]$ for speed change and $\beta \in [0.9, 1.1]$ for stretch.
@@
 
-\textbf{Modulation effects}: Effects such as chorus and tremolo employ a control signal or low-frequency oscillator.
-The specified ranges determine the chorus parameters, while the tremolo's amplitude modulation frequency and depth are controlled by $f_m \in [0.1, 100]$ and $d_m \in [1, 101]$, respectively.
+\textbf{Modulation effects}: Utilize a control signal or low-frequency oscillator.
+The chorus parameters are determined by a set of six different variables: $f_d, f_m, f_b, f_w, f_a, f_s$ where $f_d, f_m, f_w, f_a$ are floats in the range $[0.1, 1.0]$, $f_b$ is an integer in the range $[20, 55]$, $f_s$ is an integer in the range $[2, 5]$ and the type of control signal is chosen between "s" and "t".
+The tremolo's amplitude modulation frequency and depth are controlled by $t_s \in [0.1, 100]$ and $t_d \in [1, 101]$, respectively.
 
-\textbf{Reverberation effects}: These effects simulate a physical space's acoustic reflections and reverberations by applying an impulse response $h_R[n]$.
+\textbf{Reverberation effects} simulate a physical space's acoustic reflections and reverberations by applying an impulse response $h_R[n]$.
 
@@
 \begin{equation}\label{eq:positive_signal}
-P[n] = A[n] \ast h_{G}[n] \ast h_{C}[n] \ast h_{D}[n] \ast h_{P_t}[n] \ast h_{R}[n] \ast h_{S}[n] \ast h_{T}[n] \ast h_{T_m}[n] + Noise[n]
+P[n] = A[n] \ast h_{G}[n] \ast h_{C}[n] \ast h_{D}[n] \ast h_{P_t}[n] \ast h_{S}[n] \ast h_{T}[n] + N_{SNR}[n]
 \end{equation}
 
-The $\ast$ symbol represents convolution, and the various $h$ symbols indicate the impulse responses of specific effects. The noise signal $N[n]$ is included with a specific SNR.
+The $\ast$ symbol represents convolution, and the various $h$ symbols indicate the impulse responses of specific effects. The noise signals $N_{SNR}[n]$ are included with a specific SNR.
 
@@
 \item We first calculate the minimum and maximum audio chunk lengths in samples:
-\begin{equation}
-l_{min} = t_{min} \times S
-\end{equation}
-\begin{equation}
-l_{max} = t_{max} \times S
-\end{equation}
+\begin{align}
+l_{min} &= t_{min} \times S, &
+l_{max} &= t_{max} \times S
+\end{align}
 
@@
 
-The whole purpose of this process is to disturb the content unfolding in the time domain.
+The whole purpose of this process is to disturb the content unfolding in the time domain so it becomes musically unintelligible while maintaining the production and sonic attributes.
 
@@
 
-On the contrary of the also popular contrastive loss \cite{supercontrast}, the triplet loss function directs the learning process by minimizing the distance between the anchor and positive instances \textbf{and} maximizing the distance between the anchor and negative instances.
+On the contrary to the also popular contrastive loss \cite{supercontrast}, the triplet loss function directs the learning process by minimizing the distance between the anchor and positive instances \textbf{and} maximizing the distance between the anchor and negative instances.
 Including a margin parameter in the loss function guarantees a minimum separation between positive and negative instances in the embedding space.
@@
 The machine was of type \texttt{n1-standard-32}, equipped with an Intel Skylake processor and four NVIDIA Tesla T4 GPUs.
-The multiple GPUs allowed for efficient parallel processing, significantly reducing the training time for the deep learning models.
+The multiple GPUs allowed for efficient parallel processing, significantly reducing the training time.
 

### 2023-06-30 results/subsections/tables.tex
Updates from Overleaf

@@
-The evaluation results have been obtained using the standard and most commonly used MIR's tools and frameworks, such as default values of MSAF \cite{MSAF} for the segmentation algorithms \cite{sf}, the SALAMI dataset \cite{Smith2011DESIGNANNOTATIONS} as evaluation ground truth and $mir_eval$ \cite{RaffelMir_eval:METRICS} for metric computation.
+The evaluation results were obtained using standard and commonly used MIR tools and frameworks.
+These include the MSAF \cite{MSAF} implementation for segmentation algorithms, the SALAMI dataset \cite{Smith2011DESIGNANNOTATIONS} for evaluation ground truth, and $mir-eval$ \cite{RaffelMir_eval:METRICS} for metric computation.
+
+The results are displayed in \ref{ta:results}
 
@@
         & \multirow{1}{*}{CQT} & \usebox{\cqtSF} & \usebox{\cqtFoote} & \usebox{\cqtCNMF} \\\cline{1-5} 
-    \multirow{1}{*}{GTZAN}& 
+    \multirow{1}{*}{GTZAN \cite{GTZAN}}& 
         \multirow{1}{*}{Embeddiogram} & \usebox{\embeddioaSF} & \usebox{\embeddioaFoote} & \usebox{\embeddioaCNMF} \\\cline{1-5} 
-    \multirow{1}{*}{MSD}& 
+    \multirow{1}{*}{MSD \cite{MSD}}& 
         \multirow{1}{*}{Embeddiogram} & \usebox{\embeddiobSF} & \usebox{\embeddiobFoote} & \usebox{\embeddiobCNMF} \\\bottomrule

### 2023-06-30 introduction/Subsections/Previous work.tex
Updates from Overleaf

@@
 
-Related research such as \cite{deepfeaturesegment, SalamonDeepSegmentation} explore how the use of audio embeddings learned via unsupervised methods can enhance the performance of music segmentation algorithms leveraging the power of deep learning and data-driven feature learning to improve upon traditional, manually-engineered methods of music segmentation.
+Related research \cite{deepfeaturesegment, SalamonDeepSegmentation} explores how the use of audio embeddings learned via unsupervised methods can enhance the performance of music segmentation algorithms leveraging the power of deep learning and data-driven feature learning to improve upon traditional, manually-engineered methods of music segmentation.
 

### 2023-07-01 discussion/discussion.tex
Updates from Overleaf

@@
 
-While not outperforming state-of-the-art results or traditional audio features in contrast to other research findings such \cite{deepfeaturesegment, SalamonDeepSegmentation}, our musically-informed technique has significant potential for boundary detection tasks given its outstanding performance in accuracy metrics and overall performance improvement alongside the training set enlargement (GTZAN compared to Million Song Dataset).
+While not outperforming state-of-the-art existing baselines in contrast to similar research findings such \cite{deepfeaturesegment, SalamonDeepSegmentation}, our musically-informed technique has significant potential for boundary detection tasks given its outstanding performance in accuracy metrics and overall performance improvement alongside the training set enlargement (GTZAN compared to Million Song Dataset).
 Most likely, so does for nearly all MIR downstream tasks that are not purely sonic-based.

### 2023-07-01 evaluation/evaluation.tex
Updates from Overleaf

@@
 Given the potential inaccuracies inherent in human annotations and prediction errors, the F-measure permits minor deviations between predicted and actual boundaries.
-Its tolerance threshold can be adjusted, allowing a predicted boundary to be deemed correct if it is within a predefined window of a ground truth boundary \cite{Turnbull2007ABOOSTING, NietoPerceptualMusicb}.
+Its tolerance threshold can be adjusted, allowing a predicted boundary to be deemed correct if it is within a predefined window of a ground truth boundary \cite{Turnbull2007ABOOSTING, NietoPerceptualMusic}.
 

### 2023-07-01 introduction/Subsections/Previous work.tex
Updates from Overleaf

@@
 
-Related research \cite{deepfeaturesegment, SalamonDeepSegmentation} explores how the use of audio embeddings learned via unsupervised methods can enhance the performance of music segmentation algorithms leveraging the power of deep learning and data-driven feature learning to improve upon traditional, manually-engineered methods of music segmentation.
+Related research \cite{deepfeaturesegment, SalamonDeepSegmentation} investigates the use of audio embeddings derived through unsupervised methods to enhance the performance of music segmentation algorithms.
+Both studies leverage the power of deep learning and data-driven feature learning, presenting advancements over traditional manually-engineered methods.
 
-Both studies conclude that using deep learning techniques to derive audio embeddings improves the performance of music segmentation algorithms, thus providing a better alternative to traditional manual feature engineering methods.
+The study in \cite{deepfeaturesegment} presents a novel approach for music segmentation, utilizing audio embeddings learned via Few-Shot Learning and a music auto-tagging model.
+This method, which replaces the traditionally handcrafted MFCC and CQT features, significantly improves multi-level music segmentation, achieving state-of-the-art results and outperforming existing baselines.
+
+On the other hand, \cite{SalamonDeepSegmentation} explores using unsupervised deep learning methods for creating meaningful music representations and applying them to tasks like music structure analysis.
+The research employs Convolutional Neural Networks (CNNs) trained on millions of tracks from a music streaming service.
+The study reveals that these embeddings, derived via unsupervised learning, are effective at capturing musical structures, particularly when integrated with traditional feature engineering methods.
+
+Both studies emphasize the significant potential of deep learning-based feature learning in enhancing music segmentation tasks, which have traditionally relied on manual feature engineering methods.
+Furthermore, they demonstrate how using deep learning techniques improves the performance of segmentation algorithms and enables a more nuanced and detailed analysis of music structure.
+
+The results prove that unsupervised deep learning techniques that derive audio embeddings offer a robust and more efficient alternative to traditional manual feature engineering methods in music segmentation.

### 2023-07-01 methods/subsections/implementation.tex
Updates from Overleaf

@@
 \addlinespace
-\multicolumn{3}{c}{The following layers are repeated depending on the strides and hidden parameters:} \\
+\multicolumn{3}{c} \\
 \addlinespace
@@
 \addlinespace
-Fully connected or representation layer & 512 & 128 \\
+Fully connected layer & 512 & 128 \\
 \bottomrule
@@
 
-On the contrary to the also popular contrastive loss \cite{supercontrast}, the triplet loss function directs the learning process by minimizing the distance between the anchor and positive instances \textbf{and} maximizing the distance between the anchor and negative instances.
+On the contrary to the also popular contrastive loss \cite{supercontrast}, the triplet loss function directs the learning process by minimizing the distance between the anchor and positive instances and maximizing the distance between the anchor and negative instances.
 Including a margin parameter in the loss function guarantees a minimum separation between positive and negative instances in the embedding space.

### 2023-07-01 results/subsections/tables.tex
Updates from Overleaf

@@
-The evaluation results were obtained using standard and commonly used MIR tools and frameworks.
-These include the MSAF \cite{MSAF} implementation for segmentation algorithms, the SALAMI dataset \cite{Smith2011DESIGNANNOTATIONS} for evaluation ground truth, and $mir-eval$ \cite{RaffelMir_eval:METRICS} for metric computation.
+The evaluation results were obtained using standard and commonly used MIR tools, frameworks, and metrics.
+These include the MSAF \cite{MSAF} implementation for segmentation algorithms, the SALAMI dataset \cite{Smith2011DESIGNANNOTATIONS} for evaluation ground truth, and $mireval$ Python package \cite{RaffelMir_eval:METRICS} for metric computation.
 
-The results are displayed in \ref{ta:results}
+The GitHub repository containing all the code needed to compute the experiments can be found \href{https://github.com/oriolcolomefont/Master-Thesis.git}{HERE}.The results are displayed in \ref{ta:results}
 
@@
    $\begin{aligned}
-     ... & \quad ... & \quad ...
+     0.288 & \quad 0.331 & \quad 0.295
     \end{aligned} $
@@
     \end{tabular}
-    \caption[Metric comparison for different audio features and different segmentation algorithms]{Comparison of precision, recall, and f-measure for different features obtained using the SF\cite{sf}, Foote \cite{Foote2000AutomaticNovelty}, and CNMF \cite{NietoCONVEXIDENTIFICATION} algorithms on the SALAMI dataset.
+    \caption[Metric comparison: audio features and segmentation algorithms]{Comparison of precision, recall, and f-measure for different features obtained using the SF\cite{sf}, Foote \cite{Foote2000AutomaticNovelty}, and CNMF \cite{NietoCONVEXIDENTIFICATION} algorithms on the SALAMI dataset.
 Sliding windowed segments across the audio signal input signal is 4 seconds}\label{ta:results}
@@
 Only the top-performing algorithm for each year on the SALAMI dataset is displayed.
-This table has been extended from \cite{Hernandez-Olivan2021MusicFeatures}}}
+This table has been extended from \cite{Hernandez-Olivan2021MusicFeatures}.}}
 \label{tab:comparison_table}

### 2023-07-02 abstract/abstract.tex
Updates from Overleaf

@@
 \bigskip
-Keywords: MIR; Music Structure Analysis; deep audio embeddings; audio representations; representation learning; embeddings; transfer learning; multi-task learning; multi-modal learning; aural Skills
+Keywords: MIR; Music Structure Analysis; deep audio embeddings; audio representations; representation learning; embeddings; transfer learning; multi-task learning; multi-modal learning; aural skills
 

### 2023-07-02 discussion/discussion.tex
Updates from Overleaf

@@
 
-While not outperforming state-of-the-art existing baselines in contrast to similar research findings such \cite{deepfeaturesegment, SalamonDeepSegmentation}, our musically-informed technique has significant potential for boundary detection tasks given its outstanding performance in accuracy metrics and overall performance improvement alongside the training set enlargement (GTZAN compared to Million Song Dataset).
+While not outperforming state-of-the-art existing baselines in contrast to similar research findings such \cite{deepfeaturesegment, SalamonDeepSegmentation}, our musically-informed technique has significant potential for boundary detection tasks given its overall performance improvement alongside the training set enlargement (GTZAN compared to Million Song Dataset).
 Most likely, so does for nearly all MIR downstream tasks that are not purely sonic-based.

### 2023-07-02 evaluation/evaluation.tex
Updates from Overleaf

@@
     \includegraphics[width=\linewidth]{figures/images/355embeddiogramnormalized.png}
-    \caption[Embeddiogram. Track 355 (SALAMI dataset).]{Embeddiogram. Track 391 (SALAMI dataset).}
+    \caption[Embeddiogram. Track 355 (SALAMI dataset).]{Embeddiogram. Track 355 (SALAMI dataset).}
     \label{fig:embeddiogram}
@@
     \includegraphics[width=\linewidth]{figures/images/355novelty.png}
-    \caption[Novelty curve + peaks. Track 391 (SALAMI dataset).]{Novelty curve and peak detection. Track 355 (SALAMI dataset).}
+    \caption[Novelty curve + peaks. Track 355 (SALAMI dataset).]{Novelty curve and peak detection. Track 355 (SALAMI dataset).}
     \label{fig:novelty}
@@
 These deep audio features can be a foundation for current state-of-the-art methods, which are expected to receive as input standard traditional audio features.
-Consequently, they can be processed and manipulated like conventional features as described by \cite{unsuperMSA} and displayed in \ref{fig:SSM}, \ref{fig:SSLM}, \ref{fig:Q}, and \ref{fig:TBSM} \ref{fig:novelty}.
+Consequently, they can be processed and manipulated like conventional features as described by \cite{unsuperMSA} and displayed in \ref{fig:novelty}, \ref{fig:SSM}, \ref{fig:SSLM}, \ref{fig:Q}, and \ref{fig:TBSM}.
 Employing such embeddings in a traditional music segmentation algorithm can achieve state-of-the-art performance \cite{deepfeaturesegment}.
@@
 Given the potential inaccuracies inherent in human annotations and prediction errors, the F-measure permits minor deviations between predicted and actual boundaries.
-Its tolerance threshold can be adjusted, allowing a predicted boundary to be deemed correct if it is within a predefined window of a ground truth boundary \cite{Turnbull2007ABOOSTING, NietoPerceptualMusic}.
+Its tolerance threshold can be adjusted, allowing a predicted boundary to be deemed correct if it is within a predefined window of a ground truth boundary \cite{NietoPerceptualMusic, Turnbull2007ABOOSTING}.
 

### 2023-07-02 introduction/Subsections/Assumptions.tex
Updates from Overleaf

@@
 A single waveform can correspond to a finite set of representations.
-Still, one music piece can yield infinite interpretations, varying by factors such as instruments and performance styles, to name a very few.
+Still, one music piece -or music representation- can yield infinite interpretations, varying by factors such as instruments and performance styles, to name just a few.
 
@@
 
-Despite differing cultural contexts, styles, time and key signatures, and sonic properties, we suggest a commonality between figures \ref{fig:mahler} and \ref{fig:giant_steps}.
+For example, despite differing cultural contexts, styles, time and key signatures, and sonic properties, we suggest a commonality between figures \ref{fig:mahler} and \ref{fig:giant_steps}.
 Both pieces display the same 'musicological flavor', derived from their melodic and harmonic contour envelopes through non-diatonic major thirds.

### 2023-07-02 introduction/Subsections/Introduction.tex
Updates from Overleaf

@@
 
-Beyond applications in music structure analysis, the evolution of neural networks has empowered the creation of condensed numerical representations encapsulating crucial musical traits, technically known as representation learning.
+Beyond applications in music structure analysis, the evolution of neural networks has empowered the creation of condensed numerical representations encapsulating crucial musical traits, technically known as representation (or feature) learning.
 This evolution has simplified the computational process for various task-specific elements, including but not limited to:
@@
 \begin{itemize}
-\item Creating an audio embedding method that excels across numerous applications without the necessity for fine-tuning \cite{Turian2022HEAR:Representations}
-\item Boosting the classification of environmental sounds \cite{CramerLOOKEMBEDDINGS}
-\item Enhancing vocal-centric music tasks through cross-domain audio embeddings \cite{Kim2021LearningLoss}
-\item Integrating task-specific and pre-trained features to optimize audio classification \cite{Hung2022Feature-informedClassification}
-\item Developing a music similarity search engine for video production \cite{epidemic}
-\item Improving Music Emotion Recognition (MER) performance \cite{KohComparisonRecognition}
-\item Evaluating the effectiveness of speaker recognition via pre-trained model embeddings \cite{lightweight}
-\item Embedding songs for artist identification to facilitate similarity comparisons \cite{contentmusicsimtriplet2020}
-\item Addressing cross-modal text-to-music retrieval issues \cite{WonEmotionStories}
-\item Enabling automated music rearrangement \cite{Stoller2018IntuitiveTransitions, Plachouras2023MusicSegmentation}
+\item Creating an audio embedding method that excels across numerous applications without the necessity for fine-tuning \cite{Turian2022HEAR:Representations}.
+\item Boosting the classification of environmental sounds \cite{CramerLOOKEMBEDDINGS}.
+\item Enhancing vocal-centric music tasks through cross-domain audio embeddings \cite{Kim2021LearningLoss}.
+\item Integrating task-specific and pre-trained features to optimize audio classification \cite{Hung2022Feature-informedClassification}.
+\item Developing a music similarity search engine for video production \cite{epidemic}.
+\item Improving Music Emotion Recognition (MER) performance \cite{KohComparisonRecognition}.
+\item Evaluating the effectiveness of speaker recognition via pre-trained model embeddings \cite{lightweight}.
+\item Embedding songs for artist identification to facilitate similarity comparisons \cite{contentmusicsimtriplet2020}.
+\item Addressing cross-modal text-to-music retrieval issues \cite{WonEmotionStories}.
+\item Enabling automated music rearrangement \cite{Stoller2018IntuitiveTransitions, Plachouras2023MusicSegmentation}.
 \end{itemize}

### 2023-07-02 introduction/Subsections/Objectives.tex
Updates from Overleaf

@@
 
-The research will employ MIR computational methodologies and musicological perspectives to explore musical compositions across various styles and genres.
+The research employs MIR computational methodologies and musicological perspectives to explore musical compositions across various styles and genres.
 
-This approach replicates human auditory capabilities by understanding and identifying abstract and semantic musical elements independent of their sonic qualities.
+This approach aims to replicate human auditory capabilities by understanding and identifying abstract and semantic musical elements independent of their sonic qualities.

### 2023-07-02 results/subsections/tables.tex
Updates from Overleaf

@@
-The evaluation results were obtained using standard and commonly used MIR tools, frameworks, and metrics.
+As stated in the previous section, the evaluation results were obtained using standard and commonly used MIR tools, frameworks, and metrics.
 These include the MSAF \cite{MSAF} implementation for segmentation algorithms, the SALAMI dataset \cite{Smith2011DESIGNANNOTATIONS} for evaluation ground truth, and $mireval$ Python package \cite{RaffelMir_eval:METRICS} for metric computation.
 
-The GitHub repository containing all the code needed to compute the experiments can be found \href{https://github.com/oriolcolomefont/Master-Thesis.git}{HERE}.The results are displayed in \ref{ta:results}
+The GitHub repository containing all the code needed to run the experiments can be found \href{https://github.com/oriolcolomefont/Master-Thesis.git}{HERE}.The results are displayed in \ref{ta:results}
 
@@
    $\begin{aligned}
-     ... & \quad ... & \quad ...
+      & \quad  & \quad 
     \end{aligned} $
@@
    $\begin{aligned}
-     0.275 & \quad \textbf{0.318} & \quad 0.280
+     0.275 & \quad 0.318 & \quad 0.280
     \end{aligned} $
@@
    $\begin{aligned}
-     0.288 & \quad 0.331 & \quad 0.295
+     0.288 & \quad \textbf{0.331} & \quad 0.295
     \end{aligned} $
@@
    $\begin{aligned}
-     ... & \quad ... & \quad ...
+     0.228 & \quad 0.310 & \quad 0.250
     \end{aligned} $
@@
     \multirow{1}{*}{GTZAN \cite{GTZAN}}& 
-        \multirow{1}{*}{Embeddiogram} & \usebox{\embeddioaSF} & \usebox{\embeddioaFoote} & \usebox{\embeddioaCNMF} \\\cline{1-5} 
+        \multirow{1}{*}{\textbf{Embeddiogram}} & \usebox{\embeddioaSF} & \usebox{\embeddioaFoote} & \usebox{\embeddioaCNMF} \\\cline{1-5} 
     \multirow{1}{*}{MSD \cite{MSD}}& 
-        \multirow{1}{*}{Embeddiogram} & \usebox{\embeddiobSF} & \usebox{\embeddiobFoote} & \usebox{\embeddiobCNMF} \\\bottomrule
+        \multirow{1}{*}{\textbf{Embeddiogram}} & \usebox{\embeddiobSF} & \usebox{\embeddiobFoote} & \usebox{\embeddiobCNMF} \\\bottomrule
     \end{tabular}

### 2023-07-02 discussion/discussion.tex
Updates from Overleaf

@@
 In this work, we introduced a method that leverages self-supervised deep neural networks to learn low-dimensional music latent representations with applications to music boundary detection.
-Building on existing approaches and architectures, we replaced traditional features with deep embeddings trained to represent high-level musical content information to analyze its performance in music segmentation tasks.
+Building on existing approaches and architectures, we replaced traditional features with deep embeddings trained to represent high-level musical information to analyze its performance in music segmentation tasks.
 
-While not outperforming state-of-the-art existing baselines in contrast to similar research findings such \cite{deepfeaturesegment, SalamonDeepSegmentation}, our musically-informed technique has significant potential for boundary detection tasks given its overall performance improvement alongside the training set enlargement (GTZAN compared to Million Song Dataset).
+While not outperforming state-of-the-art existing baselines and in contrast to similar research findings such \cite{deepfeaturesegment, SalamonDeepSegmentation}, our musically-informed technique has significant potential for boundary detection tasks given its overall performance improvement alongside the training set enlargement.
 Most likely, so does for nearly all MIR downstream tasks that are not purely sonic-based.

### 2023-07-02 future work/future work.tex
Updates from Overleaf

@@
 
+This research merely scratches the surface, and vast territories are yet uncharted. In future studies, the following areas will be explored to extend the current research further:
+
 \begin{itemize}
-  \item Transforms
-  \item Stems
-  \item Different takes
-  \item k-fold cross validation
-  \item Hyper-params: kernel size $0.005$ times the sample rate
-  \item Larger representation layer
-  \item Easy triplet mining \cite{XuanImprovedMining}
-  \item Different boundary detection algorithms \cite{sf} was used because it was the default in MSAF \cite{MSAF}
+  \item Investigate the effect of different transformations and augmentation pipelines.
+Incorporating track stems and different takes of the same piece as natural, human-made augmentations could yield interesting results.
+  \item Expand input data to include dB-scale Mel-spectrum magnitude and CQT of audio.
+This approach has been widely used in music-related tasks with CNNs \cite{Kim2020OneStrategies}.
+Though raw audio provides a rich representation, dB-scale Mel-spectrum offers a frequency-domain summarization that is not only grounded in psycho-acoustics but is also computationally efficient and hard to reproduce solely through data-driven methods \cite{Kim2020OneStrategies}.
+Therefore, this trade-off is worth exploring.
+  \item Implement k-fold cross-validation to improve the robustness of the model's performance.
+  \item Experiment with different hyperparameters.
+For instance, setting the kernel size to $0.005$ times the sample rate could match the Just Noticeable Difference (JND).
+As for the loss function margin, a starting point of 0.2 has proven effective, but different values should be explored to optimize performance on the validation set.
+  \item Increase the size of the representation layer to 512 or 1024 dimensions.
+  \item Apply easy triplet mining to improve the model's performance \cite{XuanImprovedMining}.
+  \item Implement visual and auditory evaluations: 2D or 3D visualization of the latent space \ref{fig:manifold}, coupled with a Graphical User Interface (GUI) that enables playback for evaluation, can help assess the extent to which the model considers sonic attributes.
+It would also facilitate the understanding of the clustering of complex musical content.
 \end{itemize}
-
-Loss function margin.
-A margin of 0.2 can be a starting point, but it might not be the best value for every task.
-It's recommended to experiment with different values and choose the one that provides the best performance on your validation set.
-
-Utilize the dB-scale Mel-spectrum magnitude and CQT of audio as input data; it is a popular choice for input representation in music-related tasks when applying CNNs, as has been demonstrated in various studies \cite{Kim2020OneStrategies}.
-While raw audio is the most meaningful audio representation, it's been reported that dB-scale Mel-spectrum frequency-domain summarization, grounded in psycho-acoustics, is computationally efficient and challenging to replicate solely through data-driven methods \cite{Kim2020OneStrategies}; therefore, a trade-off that looks worthy of being explored.
-
-Visual and listening evaluation: 2D or 3D latent space visualization as per \ref{fig:manifold}.
-Arranging the embedding space in a visual display to evaluate the clustering of this sophisticated musical content to see to what extent they consider sonic attributes.
 

### 2023-07-02 methods/methods.tex
Updates from Overleaf

@@
 
-\section{Materials}
-\input{methods/subsections/model}
+This work concentrates on employing unsupervised training of neural networks to extract meaningful features for music segmentation methodologies.
+As assertively stated by \cite{deepfeaturesegment}, this constitutes a logical evolution in the application of contemporary machine learning techniques to the issue of music segmentation.
 
-\section{Convolutional Neural Network (CNN)}
-\input{methods/subsections/test}
+Our work confronts the persistent challenge of acquiring labeled data for music segmentation, an endeavor often time-consuming and expensive.
+By capitalizing on the vast volumes of unlabeled music data, we bypass the need for laborious hand annotation, thereby offering a pathway to potentially more comprehensive generalization given the broader dataset.
+
+\input{methods/subsections/deep learning}
+\input{methods/subsections/implementation}
+
 \newpage

### 2023-07-02 results/subsections/tables.tex
Updates from Overleaf

@@
 
-The GitHub repository containing all the code needed to run the experiments can be found \href{https://github.com/oriolcolomefont/Master-Thesis.git}{HERE}.The results are displayed in \ref{ta:results}
+The GitHub repository containing all the code needed to run the experiments can be found \href{https://github.com/oriolcolomefont/Master-Thesis.git}{HERE}.The results are displayed in the table \ref{ta:results}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\newsavebox\mfccSF
-\begin{lrbox}{\mfccSF}
-\centering
-   $\begin{aligned}
-     0.173 & \quad 0.185 & \quad 0.172 % SF algorithm
-    \end{aligned} $
-\end{lrbox}
-
-\newsavebox\mfccFoote
-\begin{lrbox}{\mfccFoote}
-\centering
-   $\begin{aligned}
-     ... & \quad ... & \quad ... % Foote algorithm
-    \end{aligned} $
-\end{lrbox}
-
-\newsavebox\mfccCNMF
-\begin{lrbox}{\mfccCNMF}
-\centering
-   $\begin{aligned}
-     ... & \quad ... & \quad ... % CNMF algorithm
-    \end{aligned} $
-\end{lrbox}
 
@@
     \multirow{5}{*}{}&
-         \multirow{1}{*}{MFCC } & \usebox{\mfccSF} & \usebox{\mfccFoote} & \usebox{\mfccCNMF} \\\cline{2-5}
-        & \multirow{1}{*}{PCP} & \usebox{\pcpSF} & \usebox{\pcpFoote} & \usebox{\pcpCNMF} \\\cline{2-5}
+        \multirow{1}{*}{PCP} & \usebox{\pcpSF} & \usebox{\pcpFoote} & \usebox{\pcpCNMF} \\\cline{2-5}
         & \multirow{1}{*}{Tonnetz} & \usebox{\tonnetzSF} & \usebox{\tonnetzFoote} & \usebox{\tonnetzCNMF} \\\cline{2-5} 
@@
     \end{tabular}
-    \caption[Metric comparison: audio features and segmentation algorithms]{Comparison of precision, recall, and f-measure for different features obtained using the SF\cite{sf}, Foote \cite{Foote2000AutomaticNovelty}, and CNMF \cite{NietoCONVEXIDENTIFICATION} algorithms on the SALAMI dataset.
-Sliding windowed segments across the audio signal input signal is 4 seconds}\label{ta:results}
+    \caption[Metric comparison: audio features and segmentation algorithms]{Comparison of precision, recall, and f-measure for different features using the Structural Feature (SF)\cite{sf}, Checkerboard Kernel (Foote) \cite{Foote2000AutomaticNovelty}, and Convex Non-negative Matrix Factorization (CNMF) \cite{NietoCONVEXIDENTIFICATION} algorithms on the SALAMI dataset.
+Sliding windowed segments across the audio signal input signal is 4 seconds long.}\label{ta:results}
   \end{threeparttable}
@@
 \addlinespace
-\cite{deepfeaturesegment}, 2019 & XXXX & CNN  & \textbf{0.535} ± 0.15 \\
-\addlinespace
-\cite{sf}, 2021 & XXXX & CNN  & XXX \\
+\cite{deepfeaturesegment}, 2019 & CQT & CNN  & \textbf{0.535} ± 0.15 \\
 \addlinespace

### 2023-07-04 discussion/discussion.tex
Updates from Overleaf

@@
 
-While not outperforming state-of-the-art existing baselines and in contrast to similar research findings such \cite{deepfeaturesegment, SalamonDeepSegmentation}, our musically-informed technique has significant potential for boundary detection tasks given its overall performance improvement alongside the training set enlargement.
-Most likely, so does for nearly all MIR downstream tasks that are not purely sonic-based.
-
-The questions of whether such general-purpose audio representation can mimic human hearing \cite{Li2023MERT:Training, Turian2022HEAR:Representations} or whether these do decode underlying high-level musical content effectively remain scientifically unanswered given the lack of evaluation in that regard.
-That is a "thorn in our side" that we will pursue.
+While our musically-informed technique does not yet outperform the existing state-of-the-art baselines \cite{deepfeaturesegment, SalamonDeepSegmentation}, it exhibits significant potential in boundary detection tasks, particularly when expanding the training set.
+The improvement we've observed between datasets is noteworthy, and when compared with two of the acoustic features, our results are highly competitive.
+We've also managed to circumvent the typical issues associated with dataset enlargements, such as the need for extensive supervision or human annotation, which gives our method an edge in terms of practicality and scalability effectively turning what is usually seen as an expensive hurdle into a much more manageable task.
 
@@
 
-While whether our model decodes underlying high-level musical content effectively remains scientifically unanswered, the outstanding performance in precision metric
+Whether our model effectively decodes underlying high-level musical content remains open to scientific investigation.
+It's plausible that our technique possesses significant potential for nearly all content-based MIR downstream tasks, given its intention to be both sound-agnostic and content-sensitive.
+Queries persist about whether such a general-purpose audio representation can mimic human hearing \cite{Li2023MERT:Training, Turian2022HEAR:Representations}, or if it can accurately decode high-level musical content.
+Such questions remain unresolved due to the current lack of evaluative measures.
+This represents a 'thorn in our side' that we intend to address in future research.
 

### 2023-07-04 results/results.tex
Updates from Overleaf

--- 2023-05-31 results/results.tex
@@
     \centering
-    \includegraphics[width=\textwidth]{figures/images/first results.png}
-    \caption{Caption}
+    \includegraphics[width=\textwidth]{figures/images/boxplot.png}
+    \caption[Metric comparison for different audio features.]{\small{Boxplot visual comparison of different features' average precision, recall, and f-measure.
+Sliding windowed segments across the audio signal input signal is 4 seconds.}}
     \label{fig:boxplotmetrics}
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=\textwidth]{figures/images/f-measure.png}
-    \caption{Caption}
-    \label{fig:boxplotfmeasure}
-\end{figure}
-
 \newpage

### 2023-07-04 results/subsections/tables.tex
Updates from Overleaf

@@
 
-\newsavebox\embeddioaSF
-\begin{lrbox}{\embeddioaSF}
-   $\begin{aligned}
-     0.228 & \quad 0.171 & \quad 0.185
-    \end{aligned} $
-\end{lrbox}
+\begin{table}[h]
+\centering
+\small
+\begin{tabularx}{\textwidth}{>{\centering\arraybackslash}p{4.5cm}>{\centering\arraybackslash}X>{\centering\arraybackslash}X>{\centering\arraybackslash}X}
+\toprule
+\textbf{Training dataset [Ref]}  & \textbf{Precision} & \textbf{Recall} & \textbf{F-measure} \\
+\midrule
+\addlinespace
+GTZAN \cite{GTZAN} & 0.228 & 0.171 & 0.185 \\
+\addlinespace
+MSD \cite{MSD} &  \textbf{0.333} &  \textbf{0.280} & \textbf{0.288} \\
+\addlinespace
+\bottomrule
+\end{tabularx}
+\caption[Caption]{\small{Comparison of precision, recall, and f-measure for GTZAN-trained versus MSD-trained embeddiograms on SALAMI dataset computed using the Structural Feature (SF)\cite{sf} algorithm.}}
+\label{tab:comparison_table}
+\end{table}
 
-\newsavebox\embeddioaFoote
-\begin{lrbox}{\embeddioaFoote}
-   $\begin{aligned}
-      & \quad  & \quad 
-    \end{aligned} $
-\end{lrbox}
-
-\newsavebox\embeddioaCNMF
-\begin{lrbox}{\embeddioaCNMF}
-   $\begin{aligned}
-      & \quad  & \quad 
-    \end{aligned} $
-\end{lrbox}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
   \begin{threeparttable}
-    \begin{tabular}{c|l|c|c|c} 
+    \begin{tabular}{c|c|c|c|c} 
 \toprule
-     \multicolumn{2}{c|}{\textbf{Training dataset} and \textbf{Feature}}  & \multicolumn{1}{c}{\textbf{SF}} & \multicolumn{1}{c}{\textbf{Foote}} & \multicolumn{1}{c}{\textbf{CNMF}} 
+     \textbf{Feature} & \textbf{SF} & \textbf{Foote} & \textbf{CNMF} 
      \\ \midrule 
-    \multirow{5}{*}{}&
-        \multirow{1}{*}{PCP} & \usebox{\pcpSF} & \usebox{\pcpFoote} & \usebox{\pcpCNMF} \\\cline{2-5}
-        & \multirow{1}{*}{Tonnetz} & \usebox{\tonnetzSF} & \usebox{\tonnetzFoote} & \usebox{\tonnetzCNMF} \\\cline{2-5} 
-        & \multirow{1}{*}{CQT} & \usebox{\cqtSF} & \usebox{\cqtFoote} & \usebox{\cqtCNMF} \\\cline{1-5} 
-    \multirow{1}{*}{GTZAN \cite{GTZAN}}& 
-        \multirow{1}{*}{\textbf{Embeddiogram}} & \usebox{\embeddioaSF} & \usebox{\embeddioaFoote} & \usebox{\embeddioaCNMF} \\\cline{1-5} 
-    \multirow{1}{*}{MSD \cite{MSD}}& 
-        \multirow{1}{*}{\textbf{Embeddiogram}} & \usebox{\embeddiobSF} & \usebox{\embeddiobFoote} & \usebox{\embeddiobCNMF} \\\bottomrule
+     PCP & \usebox{\pcpSF} & \usebox{\pcpFoote} & \usebox{\pcpCNMF} \\\hline
+     Tonnetz & \usebox{\tonnetzSF} & \usebox{\tonnetzFoote} & \usebox{\tonnetzCNMF} \\\hline
+     CQT & \usebox{\cqtSF} & \usebox{\cqtFoote} & \usebox{\cqtCNMF} \\\hline
+     Embeddiogram & \usebox{\embeddiobSF} & \usebox{\embeddiobFoote} & \usebox{\embeddiobCNMF} \\
+     \bottomrule
     \end{tabular}
-    \caption[Metric comparison: audio features and segmentation algorithms]{Comparison of precision, recall, and f-measure for different features using the Structural Feature (SF)\cite{sf}, Checkerboard Kernel (Foote) \cite{Foote2000AutomaticNovelty}, and Convex Non-negative Matrix Factorization (CNMF) \cite{NietoCONVEXIDENTIFICATION} algorithms on the SALAMI dataset.
-Sliding windowed segments across the audio signal input signal is 4 seconds long.}\label{ta:results}
+    \caption[Metric comparison: audio features and segmentation algorithms]{Comparison of precision (left column), recall (middle column), and f-measure (right column) metrics for different features using the Structural Feature (SF)\cite{sf}, Checkerboard-like Kernel (Foote) \cite{Foote2000AutomaticNovelty}, and Convex Non-negative Matrix Factorization (CNMF) \cite{NietoCONVEXIDENTIFICATION} algorithms on the SALAMI dataset.
+The sliding windowed segments across the input signal is 4 seconds long.}\label{ta:results}
   \end{threeparttable}
@@
 \small
-\begin{tabularx}{\textwidth}{>{\raggedright\arraybackslash}p{4.5cm}XXXXX}
+\begin{tabularx}{\textwidth}{>{\centering\arraybackslash}p{4.5cm}XXXX}
 \toprule
-\thead{\centering\textbf{Authors [Ref], Year}} & \thead{\centering\textbf{Input}} & \thead{\centering\textbf{Method}} & \thead{\centering\textbf{F-measure}} \\
+\thead{\textbf{Authors [Ref], Year}} & \thead{\textbf{Input}} & \thead{\textbf{Method}} & \thead{\textbf{F-measure}} \\
 \midrule
-\addlinespace
 Turnbull et al. \cite{Turnbull2007ABOOSTING}, 2007 & MFCCs, chromas, spectrogram & Boosted Decision Stump  & 0.378 \\
@@
 \addlinespace
-Nieto \cite{30}, 2016 & Constant-Q Transform Spectrogram & Linear Discriminant Analysis  & 0.299 \\
+Nieto \cite{30}, 2016 & CQT Spectrogram & Linear Discriminant Analysis  & 0.299 \\
 \addlinespace
@@
 \addlinespace
-\cite{deepfeaturesegment}, 2019 & CQT & CNN  & \textbf{0.535} ± 0.15 \\
+\cite{deepfeaturesegment}, 2019 & CQT & CNN  & \textbf{0.535} \\
 \addlinespace
@@
 \caption[Baseline.
-State-of-the-art table.]{\small{Previous studies' boundary detection f-measure results using unsupervised methods for a 0.5s time-window tolerance.
+State-of-the-art table.]{Previous studies' boundary detection f-measure results using unsupervised methods for a 0.5s time-window tolerance.
 Only the top-performing algorithm for each year on the SALAMI dataset is displayed.
-This table has been extended from \cite{Hernandez-Olivan2021MusicFeatures}.}}
+This table has been extended from \cite{Hernandez-Olivan2021MusicFeatures}.}
 \label{tab:comparison_table}

### 2023-07-06 acknowledgements/acknowledgements.tex
Updates from Overleaf

@@
 \begin{itemize}
-\item Carl Thomé and Carlos Lordeloª, whose expertise in MIR, ML, and DSP has been pivotal to the progress and success of my thesis.
+\item Carl Thomé and Carlos Lordelo, whose expertise in MIR, ML, and DSP has been pivotal to the progress and success of my thesis.
 Their invaluable guidance and unwavering encouragement have empowered me to overcome the challenges encountered throughout this journey.
@@
 \item Cody Hesse and Sebastian Löf
+
+\vspace*{3mm}
+\item Oriol Nieto and J. Smith
 
@@
 \item My colleague at My Sheet Music Transcriptions, Oriol López, for his exceptional support and flexibility throughout my thesis.
-His understanding and willingness to accommodate my academic commitments effectively allowed me to balance my work and research responsibilities.
+His understanding effectively allowed me to balance my work and research responsibilities.
 
 \vspace*{3mm}
-Thank you all for being excellent advisors and playing a crucial role in completing my thesis.
+
+Thank you all for playing a crucial role in completing my thesis.
 I sincerely appreciate everything you have done for me and will always cherish the knowledge and experience I have gained under your guidance.

### 2023-07-06 introduction/Subsections/Introduction.tex
Updates from Overleaf

@@
 
-Beyond applications in music structure analysis, the evolution of neural networks has empowered the creation of condensed numerical representations encapsulating crucial musical traits, technically known as representation (or feature) learning.
+Beyond applications in music structure analysis, the evolution of neural networks has empowered the creation of latent representation encapsulating crucial musical traits, technically known as representation (or feature) learning.
 This evolution has simplified the computational process for various task-specific elements, including but not limited to:
@@
 \begin{itemize}
-\item Creating an audio embedding method that excels across numerous applications without the necessity for fine-tuning \cite{Turian2022HEAR:Representations}.
+\item Creating an audio embedding that excels across numerous applications without the necessity for fine-tuning \cite{Turian2022HEAR:Representations}.
 \item Boosting the classification of environmental sounds \cite{CramerLOOKEMBEDDINGS}.
@@
 Furthermore, deep audio embeddings offer the benefit of transferability, establishing a foundation for multiple tasks.
-Compared to training a model from scratch, this approach saves computational resources and time \cite{transferMIR2013, CifkaDeepTransfer}.
+Compared to training a model from scratch, this approach saves computational resources and time \cite{transferMIR2013, CifkaDeepTransfer, Ding2023AudioClassification}.
 

### 2023-07-06 introduction/Subsections/Objectives.tex
Updates from Overleaf

@@
 
-Can deep audio embeddings be learned from reordering, scrambling, and augmenting via audio effects sequences of musical information to improve unsupervised music boundary detection?
-
-This study explores the high-level tonal structure of music by leveraging self-supervised deep neural networks, inductive bias, and aural skills to learn and analyze music embeddings that can be applied to subsequent MIR tasks, with a particular focus on music boundary detection.
+Can deep audio embeddings be learned from reordering, scrambling, and augmenting sequences of musical information to improve unsupervised music boundary detection?
 

### 2023-07-06 introduction/Subsections/Previous work.tex
Updates from Overleaf

@@
 
-Related research \cite{deepfeaturesegment, SalamonDeepSegmentation} investigates the use of audio embeddings derived through unsupervised methods to enhance the performance of music segmentation algorithms.
+Related research investigates using audio embeddings derived through unsupervised methods to enhance the performance of music segmentation algorithms \cite{deepfeaturesegment, SalamonDeepSegmentation}.
 Both studies leverage the power of deep learning and data-driven feature learning, presenting advancements over traditional manually-engineered methods.
@@
 
-The results prove that unsupervised deep learning techniques that derive audio embeddings offer a robust and more efficient alternative to traditional manual feature engineering methods in music segmentation.
+The results prove unsupervised deep learning techniques that derive audio embeddings offer a robust and more efficient alternative to traditional manual feature engineering methods in music segmentation.

### 2023-07-06 methods/subsections/implementation.tex
Updates from Overleaf

@@
 
-Our implementation offers a slight modification to the \textit{contrastive learning of musical representations} (CLMR), a method that learns valuable, discriminative music representations without explicit labels by contrasting positive augmentations of a musical piece against negative ones \cite{CLMR2021}.
+Our implementation offers a slight modification to the \textit{contrastive learning of musical representations} (CLMR) method, which learns valuable, discriminative music representations without explicit labels by contrasting positive augmentations of a musical piece against negative ones \cite{CLMR2021}.
 CLMR falls under a branch of ML known as self-supervised learning (SSL) \cite{Balestriero2023ALearning}, where models learn autonomously from unlabeled data to create their own supervisory signals \cite{audioselfsupsurvey}.
@@
 \small
-\begin{tabularx}{\textwidth}{>{\hsize=1.6\hsize}X>{\hsize=0.6\hsize}X>{\hsize=0.6\hsize}X}
+\begin{tabularx}{\textwidth}{
+  >{\centering\arraybackslash\hsize=1.6\hsize}X
+  >{\centering\arraybackslash\hsize=0.6\hsize}X
+  >{\centering\arraybackslash\hsize=0.6\hsize}X}
 \toprule
@@
 \addlinespace
-\multicolumn{3}{c} \\
+\multirow{9}{*}{Conv + BatchNorm + ReLU + MaxPool} & 128 & 128 \\
 \addlinespace
-Conv + BatchNorm + ReLU + MaxPool & 128 & 128 \\
+ & 128 & 128 \\
 \addlinespace
-Conv + BatchNorm + ReLU + MaxPool & 128 & 128 \\
+ & 128 & 256 \\
 \addlinespace
-Conv + BatchNorm + ReLU + MaxPool & 128 & 256 \\
+ & 256 & 256 \\
 \addlinespace
-Conv + BatchNorm + ReLU + MaxPool & 256 & 256 \\
+ & 256 & 256 \\
 \addlinespace
-Conv + BatchNorm + ReLU + MaxPool & 256 & 256 \\
+ & 256 & 256 \\
 \addlinespace
-Conv + BatchNorm + ReLU + MaxPool & 256 & 256 \\
+ & 256 & 256 \\
 \addlinespace
-Conv + BatchNorm + ReLU + MaxPool & 256 & 256 \\
+ & 256 & 256 \\
 \addlinespace
-Conv + BatchNorm + ReLU + MaxPool & 256 & 256 \\
-\addlinespace
-Conv + BatchNorm + ReLU + MaxPool & 256 & 512 \\
+ & 256 & 512 \\
 \addlinespace
@@
 \end{tabularx}
-\caption{Layer specifications for SampleCNN model}
+\caption{Layer specifications for the SampleCNN model}
 \label{tab:samplecnntable}

### 2023-07-06 preface/preface.tex
Updates from Overleaf

@@
 This work humbly aims to help untangle the complexities of music and offer a more musically-driven perspective to MIR.
-We aim to contribute to a deeper understanding of the intricate relationships within musical data by bridging the gap between music theory and computational analysis.
+It aims to contribute to a deeper understanding of the intricate relationships within musical data by bridging the gap between music theory and computational analysis.
 
@@
 
-This work is intended for any curious human being, regardless of their background in music or computer science.
-I hope it will inspire others to explore the fascinating intersection of these two disciplines.
+This work is intended for any curious person, regardless of their academic background. I hope it will inspire others to explore the fascinating intersection of these two disciplines.
 

### 2023-07-06 results/subsections/tables.tex
Updates from Overleaf

@@
 
-\begin{table}[h]
+\begin{table}[ht]
+\begin{threeparttable}
 \centering
 \small
-\begin{tabularx}{\textwidth}{>{\centering\arraybackslash}p{4.5cm}XXXX}
+\begin{tabularx}{\textwidth}{
+  >{\centering\arraybackslash}p{4.5cm}
+  >{\centering\arraybackslash}X
+  >{\centering\arraybackslash}X
+  >{\centering\arraybackslash}X}
 \toprule
-\thead{\textbf{Authors [Ref], Year}} & \thead{\textbf{Input}} & \thead{\textbf{Method}} & \thead{\textbf{F-measure}} \\
+\thead{\textbf{Authors [Ref], Year}} & \thead{\textbf{Input}\tnote{1}} & \thead{\textbf{Method}} & \thead{\textbf{F-measure}} \\
 \midrule
@@
 \addlinespace
-\cite{deepfeaturesegment}, 2019 & CQT & CNN  & \textbf{0.535} \\
+McCallum \cite{deepfeaturesegment}, 2019 & CQT & CNN  & \textbf{0.535} \\
 \addlinespace
@@
 \label{tab:comparison_table}
+\begin{tablenotes}\footnotesize
+\item[1] \textbf{Legend:} SSM: Self-Similarity Matrix, MLS: Mel Spectrogram, MFCC: Mel-Frequency Cepstral Coefficient, CQT: Constant Q Transform, PCP: Pitch Class Profile, SSLM: Self-Similarity Lag Matrix.
+\end{tablenotes}
+\end{threeparttable}
 \end{table}

### 2023-07-06 acknowledgements/acknowledgements.tex
Updates from Overleaf

@@
 \begin{itemize}
-\item Carl Thomé and Carlos Lordelo, whose expertise in MIR, ML, and DSP has been pivotal to the progress and success of my thesis.
-Their invaluable guidance and unwavering encouragement have empowered me to overcome the challenges encountered throughout this journey.
-Their dedication and commitment to mentorship are truly inspiring, and their influence has left an indelible mark on my academic path.
-The opportunity to work under their mentorship has been a privilege and an honor.
-Their profound impact is beyond what words can encapsulate.
+\item Carl Thomé and Carlos Lordelo, whose expertise in MIR, ML, and DSP has been pivotal to the success of my thesis.
+Their guidance and encouragement have enabled me to overcome the challenges encountered during this journey.
+Their commitment to mentorship is truly inspiring, and their influence has significantly shaped my academic path.
+Working under their mentorship has been both a privilege and an honor.
 
 \vspace*{3mm}
-\item Cody Hesse and Sebastian Löf
-
-\vspace*{3mm}
-\item Oriol Nieto and J. Smith
-
-\vspace*{3mm}
-\item Epidemic Sound
+\item Cody Hesse and Sebastian Löf. Their generosity in sharing their time, knowledge, and insights has critically enhanced the quality of this research work.
 
@@
 \item The Music Technology Group (MTG) and Universitat Pompeu Fabra (UPF).
-My profound thanks go to Xavier Serra for his faith in accepting a non-traditional profile to the master's program.
-Additionally, I appreciate Pedro Ramoneda and Genís Plaja for their patient assistance throughout my journey.
-
-\vspace*{3mm}
-\item My colleague at My Sheet Music Transcriptions, Oriol López, for his exceptional support and flexibility throughout my thesis.
-His understanding effectively allowed me to balance my work and research responsibilities.
+My profound thanks go to Xavier Serra for his faith in accepting a non-traditional profile into the master's program.
+I am equally grateful to Pedro Ramoneda and Genís Plaja for their consistent support throughout my journey.
 
@@
 
-Thank you all for playing a crucial role in completing my thesis.
-I sincerely appreciate everything you have done for me and will always cherish the knowledge and experience I have gained under your guidance.
+I sincerely thank you all for your integral roles in completing my thesis. I deeply value the knowledge and experience gained under your guidance and will cherish it always.
 

### 2023-07-06 discussion/discussion.tex
Updates from Overleaf

@@
 The improvement we've observed between datasets is noteworthy, and when compared with two of the acoustic features, our results are highly competitive.
-We've also managed to circumvent the typical issues associated with dataset enlargements, such as the need for extensive supervision or human annotation, which gives our method an edge in terms of practicality and scalability effectively turning what is usually seen as an expensive hurdle into a much more manageable task.
+We've also managed to circumvent the typical issues associated with dataset enlargements, such as the need for extensive supervision or human annotation, which gives our method an edge in terms of practicality and scalability, effectively turning what is usually seen as an expensive hurdle into a much more manageable task.
 
@@
 
-Too little representation layer?
+We argue whether factors such as the size of the representation layer and the size of the raw audio model might be insufficient \cite{verydeep}.
+Furthermore, we posit that with additional time to iterate repeatedly over the dataset, the loss function could decrease further with minimal risk of overfitting.
+\ref{fig:lossf}
 
-Too little model for raw audio input? \cite{verydeep}
+While our results may not yet rival state-of-the-art benchmarks, they offer an encouraging starting point.
+They affirm we're on the right path and reveal the potential of this research direction.
+Importantly, we've seen that progress doesn't have to be expensive—though time and potential copyright issues are considerations.
 
-\begin{figure}
+\begin{figure}[h]
     \centering
     \includegraphics[width=\textwidth]{figures/images/Mean group aggregation.png}
-    \caption{Caption}
-    \label{fig:enter-label}
+    \caption[Loss function performance plot]{Mean group aggregation of the decrease of the loss function over trainer/global steps. Training loss against validation loss.}
+    \label{fig:lossf}
 \end{figure}

### 2023-07-06 introduction/Subsections/Assumptions.tex
Updates from Overleaf

@@
 A single waveform can correspond to a finite set of representations.
-Still, one music piece -or music representation- can yield infinite interpretations, varying by factors such as instruments and performance styles, to name just a few.
+Still, one music piece ---or music representation--- can yield infinite interpretations, varying by factors such as instruments and performance styles, to name just a few.
 

### 2023-07-06 methods/subsections/implementation.tex
Updates from Overleaf

@@
 
-\subsubsection{Encoder architecture: SampleCNN}
+\subsubsection{Encoder: SampleCNN}
 
@@
 This results in a more robust, efficient learning process that offers translation invariance and better contextual understanding.
-
-%Colour CNN
-\input{figures/neural networks/colour CNN}
 
@@
 
-Circling back to our premises and assumptions, we posit that high-level musical content unfolds over time; therefore, we argue that the temporal structure of the negative images, in contrast to our anchor, should be disrupted.
+Circling back to our premises and assumptions, we posit that high-level musical content unfolds over time; therefore, we argue that the temporal structure of the negative images, in contrast to our anchor, must be disrupted.
 While maintaining similar sonic qualities, the content should be rendered unintelligible.

### 2023-07-06 results/subsections/tables.tex
Updates from Overleaf

@@
 \end{tabularx}
-\caption[Caption]{\small{Comparison of precision, recall, and f-measure for GTZAN-trained versus MSD-trained embeddiograms on SALAMI dataset computed using the Structural Feature (SF)\cite{sf} algorithm.}}
+\caption[GTZAN-trained versus MSD-trained embeddiograms]{\small{Comparison of precision, recall, and f-measure for GTZAN-trained versus MSD-trained embeddiograms on SALAMI dataset computed using the Structural Feature (SF)\cite{sf} algorithm.}}
 \label{tab:comparison_table}
@@
 \addlinespace
+Sargent et al. \cite{34}, 2011 & MFCCs, chromas & Viterbi  & 0.356 \\
+\addlinespace
 McFee \& Ellis \cite{20}, 2013 & MLS & Fisher’s Linear Discriminant  & 0.317 \\
@@
 Cannam et al. \cite{29}, 2017 & Timbre-type histograms & HMM  & 0.212 \\
-\addlinespace
-Sargent et al. \cite{34}, 2011 & MFCCs, chromas & Viterbi  & 0.356 \\
 \addlinespace

### 2023-07-07 MasterThesis.tex
Updates from Overleaf

@@
   Uncovering underlying high-level musical content in the time domain \\
-  \small Leveraging self-supervised deep neural networks, inductive bias, and aural skills to learn deep audio embeddings with applications to boundary detection tasks}
+  \small Leveraging self-supervised neural networks, inductive bias, and aural skills to learn deep audio embeddings with applications to boundary detection tasks}
 
@@
 \submitdate{July 2023}
-\supervisor{Carl Thomé and Carlos Lordelo}
-\cosupervisor{Frederic Font}
+\supervisor{Carl Thomé}
+\cosupervisor{Carlos Lordelo}
 
@@
 \newpage
-\input{appendix/appendix}
+%\input{appendix/appendix}
 \newpage

### 2023-07-07 abstract/abstract.tex
Updates from Overleaf

@@
 
-In collaboration with Epidemic Sound AB and the Music Technology Group (MTG) at Universitat Pompeu Fabra (UPF), we used self-supervised contrastive learning to uncover the underlying structure of Western tonal music by learning deep audio features to improve unsupervised music boundary detection.
-We applied deep convolutional neural networks and a triplet loss function to identify abstract and semantic high-level musical elements without relying on their sonic qualities.
+In collaboration with Epidemic Sound AB and the Music Technology Group (MTG) at Universitat Pompeu Fabra (UPF), we used self-supervised contrastive learning to uncover the underlying structure of Western tonal music by learning deep audio features for unsupervised music boundary detection.
+We applied deep convolutional neural networks with triplet loss function to identify abstract and semantic high-level musical elements without relying on their sonic qualities.
 This way, we replaced traditional acoustic features with deep audio embeddings, paving the way for sound-agnostic and content-sensitive music representation for boundary detection.
@@
 Our cognitively-based approach for learning embeddings focuses on using full-resolution data and preserving high-level musical information which unfolds in the time domain.
-A key component in our methodology is the use of triplet networks, which provide an effective way of understanding and preserving the relative distances between different pieces of music.
-This model structure is integral to our work, allowing us to identify and maintain the nuanced relationships within our musical data.
+A key component in our methodology is the use of triplet networks, which effectively understand and preserve the nuanced relationships within musical data.
 Drawing upon our domain expertise, we developed robust transformations to encode heuristic musical concepts that should remain constant.
@@
 
-Preliminary results suggest that, while not outperforming state-of-the-art results, our musically-informed technique has significant potential for boundary detection tasks and, most likely, nearly all MIR downstream tasks that are not purely sonic-based.
+Preliminary results suggest that, while not outperforming state-of-the-art, our musically-informed technique has significant potential for boundary detection tasks and, most likely, so does for nearly all MIR downstream sound-agnostic and content-sensitive tasks constrained by data scarcity as it is possible to achieve competitive performance to traditional handcrafted signal processing methods by learning only from unlabeled audio files.
 
-While music-motivated audio embeddings appear promising, delivering competitive results with room for improvement and potentially adaptable to other tasks constrained by data scarcity, the question remains if such general-purpose audio representation can mimic human hearing.
+The question remains if such general-purpose audio representation can mimic human hearing.
 
 \bigskip
-Keywords: MIR; Music Structure Analysis; deep audio embeddings; audio representations; representation learning; embeddings; transfer learning; multi-task learning; multi-modal learning; aural skills
+Keywords: MIR; music structure analysis; boundary detection; deep audio embeddings; audio representations; representation learning; embeddings; transfer learning; multi-task learning; multi-modal learning; aural skills
 

### 2023-07-07 evaluation/evaluation.tex
Updates from Overleaf

@@
 
-We have conducted experiments using a window duration of 4 seconds (\(w = 4 \times \text{{sr (Hz)}}\)).
+We have conducted experiments using a window duration of 4 seconds (\(w = 4 \times \text{{sampling rate}}\)).
 As a general rule of thumb, this duration corresponds to two 4/4 bars of a piece of music with a tempo where the quarter note equals 120 BPM.
@@
 
+We computed the f-measure for each track and then calculated the average rather than aggregating all tracks into a single dataset and calculating the f-measure on this combined set.
+
 \begin{equation}

### 2023-07-07 future work/future work.tex
Updates from Overleaf

@@
   \item Investigate the effect of different transformations and augmentation pipelines.
-Incorporating track stems and different takes of the same piece as natural, human-made augmentations could yield interesting results.
+Incorporating track stems and different takes of the same piece as natural, human-made augmentations could yield exciting results.
   \item Expand input data to include dB-scale Mel-spectrum magnitude and CQT of audio.
 This approach has been widely used in music-related tasks with CNNs \cite{Kim2020OneStrategies}.
-Though raw audio provides a rich representation, dB-scale Mel-spectrum offers a frequency-domain summarization that is not only grounded in psycho-acoustics but is also computationally efficient and hard to reproduce solely through data-driven methods \cite{Kim2020OneStrategies}.
+Though raw audio provides a rich representation, dB-scale Mel-spectrum offers a frequency-domain summarization that is not only grounded in psycho-acoustics but is also computationally efficient and hard to reproduce solely through data-driven methods.
 Therefore, this trade-off is worth exploring.

### 2023-07-07 introduction/Subsections/Assumptions.tex
Updates from Overleaf

@@
 
-The premise of our work is that regardless of the waveform or production style, abstract high-level features can be discerned, offering objective and thorough insight into a composition's musical content, analogous to analyzing sheet music for its basic behaviors \ref{fig:Wandrers Nachtlied, Op.
+The premise of our work is that regardless of the waveform or production style, abstract high-level features can be discerned, offering objective and thorough insight into a composition's musical content, analogous to analyzing sheet music for its basic behaviors as shown in Figure \ref{fig:Wandrers Nachtlied, Op.
 4, D.
@@
 
-For example, despite differing cultural contexts, styles, time and key signatures, and sonic properties, we suggest a commonality between figures \ref{fig:mahler} and \ref{fig:giant_steps}.
+For example, despite differing cultural contexts, styles, time and key signatures, and sonic properties, we suggest a commonality between Figure \ref{fig:mahler} and Figure \ref{fig:giant_steps}.
 Both pieces display the same 'musicological flavor', derived from their melodic and harmonic contour envelopes through non-diatonic major thirds.

### 2023-07-07 introduction/Subsections/Introduction.tex
Updates from Overleaf

@@
 This term's usage does not negate the diversity and richness of other musical traditions worldwide.
-Instead, it specifies this study's concentration on a particular cultural context.}, a cornerstone of human culture and history, has developed hand in hand with our societies since ancient times.
+Instead, it specifies this study's concentration on a particular cultural context.}, a cornerstone of human culture, has developed hand in hand with our societies since ancient times.
 However, its study presents unique challenges due to its subjectivity, fluctuating ground truth, and the vast array of styles and cultural contexts it encompasses.
@@
 
-Beyond applications in music structure analysis, the evolution of neural networks has empowered the creation of latent representation encapsulating crucial musical traits, technically known as representation (or feature) learning.
+Beyond applications in music structure analysis, the evolution of neural networks has empowered the creation of latent representations encapsulating crucial musical traits, technically known as representation (or feature) learning.
 This evolution has simplified the computational process for various task-specific elements, including but not limited to:
@@
 
+Unsupervised settings to learn those embbedings confront the persistent challenge of acquiring labeled data for music segmentation, an endeavor often time-consuming and expensive.
+By capitalizing on the vast volumes of unlabeled music data, we bypass the need for laborious hand annotation, thereby offering a pathway to potentially more comprehensive generalization given a broader dataset.
+
 Given the proven effectiveness of deep audio embeddings in existing research and their potential for transfer learning, they hold considerable promise for MIR downstream tasks, including boundary detection.

### 2023-07-07 introduction/Subsections/Motivation.tex
Updates from Overleaf

@@
 
-This thesis, a collaboration between \href{https://www.epidemicsound.com/}{Epidemic Sound} (ES) and the \href{https://www.upf.edu/web/mtg}{Music Technology Group} (MTG) at Universitat Pompeu Fabra (UPF), has been driven by personal, academic, and industrial motivations.
+This thesis, a collaboration between \href{https://www.epidemicsound.com/}{Epidemic Sound} (ES) and the \href{https://www.upf.edu/web/mtg}{Music Technology Group} (MTG) at Universitat Pompeu Fabra (UPF), has been driven by personal, industrial, and academic motivations.
+
 ES, a Swedish company, curates a vast global library of over 40,000 royalty-free music tracks and 90,000+ sound effects.
@@
 
-Traditionally, MIR research has focused primarily on technical aspects, perhaps overlooking relevant areas such as perception, cognition, music theory, musicology, aural skills, and high-level perceptual concepts.
-Purely mathematical approaches may not accurately represent human music perception and could miss subtle details essential to the musical experience \cite{neglecteduser2013}.
-Therefore, MIR research should strive for a balanced approach, recognizing the interdisciplinary nature of music and the importance of areas beyond digital signal processing.
+Traditionally, MIR research has focused on handcrafted features and annotated data.
+From an academic perspective, self-supervised models are worth exploring as they don't require annotated data and have demonstrated competitive performance in other tasks \cite{Li2023MERT:Training}.

### 2023-07-07 introduction/Subsections/Objectives.tex
Updates from Overleaf

@@
 Our research aims to develop and learn a unified numerical understanding (or embedding \footnote{A learned representation or embedding is a numerical output - usually a fixed-size vector - produced by a machine-learning model.
-Good representations should be versatile across various tasks and require limited supervision \cite{Turian2022HEAR:Representations}.}) for a piece of music that integrates the high-level relationships between musical elements as they unfold over time.
+Good non-supervised representations should be versatile across various tasks and require limited supervision, therefore appears as an attractive methodology to be employed \cite{Turian2022HEAR:Representations}.}) for a piece of music that integrates the high-level relationships between musical elements as they unfold over time.
 
@@
 This approach aims to replicate human auditory capabilities by understanding and identifying abstract and semantic musical elements independent of their sonic qualities.
+
+\section{Contributions}
+
+Our study is centered around the following topics of investigation:
+
+\begin{itemize}
+    \item We demonstrate that the size of the audio file dataset used for learning embeddings influences the results of music segmentation. Larger datasets lead to improved results.
+    \item We show that achieving performance competitive with traditional handcrafted signal processing methods is possible by learning solely from unlabeled audio files.
+    \item While our musically-informed technique does not currently surpass existing state-of-the-art baselines, it shows significant promise in boundary detection tasks, significantly when the training set is expanded.
+\end{itemize}

### 2023-07-07 introduction/Subsections/Previous work.tex
Updates from Overleaf

@@
 
-Related research investigates using audio embeddings derived through unsupervised methods to enhance the performance of music segmentation algorithms \cite{deepfeaturesegment, SalamonDeepSegmentation}.
+Related research investigates audio embeddings derived through unsupervised methods to enhance the performance of music segmentation algorithms \cite{deepfeaturesegment, SalamonDeepSegmentation}.
 Both studies leverage the power of deep learning and data-driven feature learning, presenting advancements over traditional manually-engineered methods.
 
-The study in \cite{deepfeaturesegment} presents a novel approach for music segmentation, utilizing audio embeddings learned via Few-Shot Learning and a music auto-tagging model.
+The study in \cite{deepfeaturesegment} presents a novel approach for music segmentation, utilizing audio embeddings learned via few-shot learning and a music auto-tagging model.
 This method, which replaces the traditionally handcrafted MFCC and CQT features, significantly improves multi-level music segmentation, achieving state-of-the-art results and outperforming existing baselines.
@@
 
-The results prove unsupervised deep learning techniques that derive audio embeddings offer a robust and more efficient alternative to traditional manual feature engineering methods in music segmentation.
+The results prove that unsupervised deep-learning techniques which derive audio embeddings offer more robust and efficient alternatives to traditional manual feature-engineering methods in music segmentation.

### 2023-07-07 methods/methods.tex
Updates from Overleaf

--- 2023-03-10 methods/methods.tex
@@
 
-\section{Materials}
-\input{methods/subsections/model}
+This work concentrates on employing unsupervised training of neural networks to extract meaningful features for music segmentation methodologies.
+As assertively stated by \cite{deepfeaturesegment}, this constitutes a logical evolution in applying contemporary machine learning techniques to music segmentation.
 
-\section{Convolutional Neural Network (CNN)}
-\input{methods/subsections/test}
+\input{methods/subsections/deep learning}
+\input{methods/subsections/implementation}
+
 \newpage

### 2023-07-07 methods/subsections/deep learning.tex
Updates from Overleaf

@@
 Another crucial component in the operation of DNNs is the activation function.
-This function is applied to a neuron's inputs, transforming the input's summed product and weights into an output passed onto the next layer.
+This function is applied at every layer, transforming the linear combination of the input with the layer weights into an output that is passed onto the next layer.
 It introduces non-linearity into the network, enabling it to learn complex patterns and relationships from the data.

### 2023-07-07 methods/subsections/implementation.tex
Updates from Overleaf

@@
 
-Our implementation offers a slight modification to the \textit{contrastive learning of musical representations} (CLMR) method, which learns valuable, discriminative music representations without explicit labels by contrasting positive augmentations of a musical piece against negative ones \cite{CLMR2021}.
+Our implementation offers a slight modification to the \textit{contrastive learning of musical representations} (CLMR) method \cite{CLMR2021}, which learns valuable, discriminative music representations without explicit labels by contrasting positive augmentations of a musical piece against negative ones.
 CLMR falls under a branch of ML known as self-supervised learning (SSL) \cite{Balestriero2023ALearning}, where models learn autonomously from unlabeled data to create their own supervisory signals \cite{audioselfsupsurvey}.
@@
 
-This work suggests employing a Triple Siamese Network (TSN), a model architecture known for its efficacy in music similarity retrieval tasks \cite{contentmusicsimtriplet2020}.
+This work suggests employing a Triplet Siamese Network (TSN), a model architecture known for its efficacy in music similarity retrieval tasks \cite{contentmusicsimtriplet2020}.
 The aim is to minimize the loss function between a triplet of anchor, positive, and negative samples, utilizing online triplet mining for optimizing memory resources \cite{Sikaroudi2020OfflinePatches}.
@@
 
-On the contrary to the also popular contrastive loss \cite{supercontrast}, the triplet loss function directs the learning process by minimizing the distance between the anchor and positive instances and maximizing the distance between the anchor and negative instances.
+On the contrary to the also widespread contrastive loss \cite{supercontrast}, the triplet loss function directs the learning process by minimizing the distance between the anchor and positive instances and maximizing the distance between the anchor and negative instances.
 Including a margin parameter in the loss function guarantees a minimum separation between positive and negative instances in the embedding space.

### 2023-07-07 results/subsections/tables.tex
Updates from Overleaf

@@
 
-The GitHub repository containing all the code needed to run the experiments can be found \href{https://github.com/oriolcolomefont/Master-Thesis.git}{HERE}.The results are displayed in the table \ref{ta:results}
+The GitHub repository containing all the code needed to run the experiments can be found \href{https://github.com/oriolcolomefont/Master-Thesis.git}{HERE}.
+The results are displayed in tables \ref{tab:comparison_table} and \ref{ta:results}.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/images/boxplot.png}
+    \caption[Metric comparison for different audio features.]{\small{Boxplot visual comparison of different features' average precision, recall, and f-measure.
+Sliding windowed segments across the audio signal input signal is 4 seconds.}}
+    \label{fig:boxplotmetrics}
+\end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{table}
+
+%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/images/fmeasuregraphs.png}
+    \caption[Baseline.
+State-of-the-art graph.]{Previous studies' boundary detection f-measure results using unsupervised methods for a 0.5s time-window tolerance.
+Only the top-performing algorithm for each year on the SALAMI dataset is displayed.
+This figure has been extended from \cite{Hernandez-Olivan2021MusicFeatures}.}
+    \label{fig:enter-label}
+\end{figure}

### 2023-07-07 methods/subsections/implementation.tex
Updates from Overleaf

@@
 This is accomplished through a specialized loss function called triplet loss, which aims to minimize the distance between similar inputs and maximize it for dissimilar ones.
+The loss function will be explained later in Subsection~\ref{subsec:loss-function}.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{figure}
+    \centering
+    \includegraphics{figures/images/applsci-08-00150-g001.png}
+    \caption[]{Caption}
+    \label{fig:enter-label}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{table}[ht]
@@
 \begin{tabularx}{\textwidth}{
-  >{\centering\arraybackslash\hsize=1.6\hsize}X
-  >{\centering\arraybackslash\hsize=0.6\hsize}X
-  >{\centering\arraybackslash\hsize=0.6\hsize}X}
+  >{\centering\arraybackslash\hsize=0.5\hsize}X
+  >{\centering\arraybackslash\hsize=0.25\hsize}X
+  >{\centering\arraybackslash\hsize=0.25\hsize}X}
 \toprule
@@
 This discrepancy implies that using spectrogram distance alone for measuring high-level music content may not always align with human perceptions \cite{Kim2020OneStrategies, Mesostructures2023}.
+
+In conclusion, raw audio waveforms were our final choice for input for the anchor.
+Each input sequence was 15 seconds long, roughly equivalent to 8 bars of 4/4 music at 120 beats per minute.
+The audio was sampled at a frequency of 16 kHz, a decision influenced by the requirements of SampleCNN, computational resources, and our belief in the value of high-resolution data for revealing a comprehensive picture of the audio content.
+We are confident that this choice of input contains a significant amount of meaningful musical information.
+Although it may not encompass the complexity of a symphony, it is sufficient for the scope of our experiments.
 
@@
 \subsection{Loss function}
+\label{subsec:loss-function}
 

### 2023-07-07 discussion/discussion.tex
Updates from Overleaf

@@
 Such questions remain unresolved due to the current lack of evaluative measures.
+
 This represents a 'thorn in our side' that we intend to address in future research.
 
-We argue whether factors such as the size of the representation layer and the size of the raw audio model might be insufficient \cite{verydeep}.
+We argue whether factors such as the size of the representation layer and the size of the model \cite{verydeep} might be insufficient.
 Furthermore, we posit that with additional time to iterate repeatedly over the dataset, the loss function could decrease further with minimal risk of overfitting.
@@
 
-While our results may not yet rival state-of-the-art benchmarks, they offer an encouraging starting point.
-They affirm we're on the right path and reveal the potential of this research direction.
+While our results may not yet rival state-of-the-art benchmarks, they affirm we're on the right path and reveal the potential of this research direction.
 Importantly, we've seen that progress doesn't have to be expensive—though time and potential copyright issues are considerations.

### 2023-07-07 evaluation/evaluation.tex
Updates from Overleaf

--- 2023-07-02 evaluation/evaluation.tex
@@
-\chapter{Evaluation}
-
-\section{The \textit{embeddiogram}, a deep audio feature representation}
-
-The \textit{embeddiogram}, a deep audio feature representation, is derived by applying our pre-trained neural network to sliding windowed segments across the audio signal, generating a sequence of embedding vectors.
-These relatively low-dimensional embedding vectors collectively form a two-dimensional description of the audio signal's musical content.
-
-Below is a detailed explanation of how we compute the \textit{embeddiogram} from a given audio signal of length $N$.
-This process comprises loading the audio data, slicing the audio data into windowed segments, processing each window using our pre-trained model to produce a vector per window/time frame, collecting and stacking these embeddings, and finally, normalizing the resulting matrix.
-
-\begin{enumerate}
-\item \textbf{Load the audio data}: The audio data is loaded into memory as a one-dimensional array of length $N$.
-
-\item \textbf{Slice the audio data}: The audio data is segmented into overlapping windows.
-Each window contains $w$ samples, and consecutive windows are separated by a hop size $h$.
-This gives a total of $H$ windows, defined as:
-\begin{equation}
-H = 1 + \left\lfloor \frac{N - w}{h} \right\rfloor
-\end{equation}
-In the case where $\left( N - w \right) \mod h > 0$, we have $H += 1$ to account for the final, potentially smaller window.
-
-We have conducted experiments using a window duration of 4 seconds (\(w = 4 \times \text{{sr (Hz)}}\)).
-As a general rule of thumb, this duration corresponds to two 4/4 bars of a piece of music with a tempo where the quarter note equals 120 BPM.
-
-We find this to be a good starting compromise solution, allowing enough time span to capture musical content while not being so large that downsampling reduces the information to an unintelligible vector.
-
-\item \textbf{Process each window}: Each window of audio data is processed independently, passed through the pre-trained neural network, and transformed into an embedding vector.
-Formally, for each window $w_i$ of audio data, we have:
-\begin{equation}
-\text{embedding}_i = \text{model}(w_i)
-\end{equation}
-
-\item \textbf{Collect the embeddings}: The embedding vectors are collected and stacked together.
-Each row represents a feature vector for a given time frame to form the \textit{embeddiogram}, denoted as $\text{e}$:
-\begin{equation}
-\text{e} = \begin{bmatrix} \text{embedding}_1 \\ \text{embedding}_2 \\ \vdots \\ \text{embedding}_H \end{bmatrix}
-\end{equation}
-
-\item \textbf{Normalize the \textit{embeddiogram \ref{fig:embeddiogram}}}: The \textit{embeddiogram} is normalized to have a minimum value of 0 and a maximum value of 1 per dimension.
-The normalization process is given by:
-\begin{equation}
-E'_{ij} = \frac{e_{ij} - \min(E)}{\max(E) - \min(E)}
-\end{equation}
-\end{enumerate}
-
-\begin{figure}[ht]
-  \centering
-  \begin{minipage}[b]{1.0\linewidth}
-    \centering
-    \includegraphics[width=\linewidth]{figures/images/355embeddiogramnormalized.png}
-    \caption[Embeddiogram. Track 355 (SALAMI dataset).]{Embeddiogram. Track 355 (SALAMI dataset).}
-    \label{fig:embeddiogram}
-  \end{minipage}
-
-  \begin{minipage}[b]{1.0\linewidth}
-    \centering
-    \includegraphics[width=\linewidth]{figures/images/355novelty.png}
-    \caption[Novelty curve + peaks. Track 355 (SALAMI dataset).]{Novelty curve and peak detection. Track 355 (SALAMI dataset).}
-    \label{fig:novelty}
-  \end{minipage}
-\end{figure}
-
-\begin{figure}[ht]
-    \centering
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=0.9\textwidth]{figures/images/355recurrencematrix.png} % first figure itself
-        \caption[Track 355 (SALAMI dataset) Self-similarity matrix]{Self-similarity matrix computation of the embeddiogram. Track 355 (SALAMI dataset).}
-        \label{fig:SSM}
-    \end{minipage}\hfill
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=0.9\textwidth]{figures/images/355lagmatrixgaussiansmoothing.png} % second figure itself
-        \caption[Track 355 (SALAMI dataset) SSLM computation of the embeddiogram]{Self-similarity lag matrix. Track 355 (SALAMI dataset).}
-        \label{fig:SSLM}
-    \end{minipage}
-    \vfill
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=0.9\textwidth]{figures/images/355cumulativematrix.png} % third figure itself
-        \caption[Track 355 (SALAMI dataset). Q-matrix]{Cumulative matrix computation of the embeddiogram. Track 355 (SALAMI dataset) .}
-        \label{fig:Q}
-    \end{minipage}\hfill
-    \begin{minipage}{0.45\textwidth}
-        \centering
-        \includegraphics[width=0.9\textwidth]{figures/images/355transitivebinarysimilaritymatrix.png} % fourth figure itself
-        \caption[Track 355 (SALAMI dataset). Transitive Binary Similarity Matrix]{Transitive Binary Matrix computation of the embeddiogram. Track 355 (SALAMI dataset).}
-        \label{fig:TBSM}
-    \end{minipage}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%
-
-These deep audio features can be a foundation for current state-of-the-art methods, which are expected to receive as input standard traditional audio features.
-Consequently, they can be processed and manipulated like conventional features as described by \cite{unsuperMSA} and displayed in \ref{fig:novelty}, \ref{fig:SSM}, \ref{fig:SSLM}, \ref{fig:Q}, and \ref{fig:TBSM}.
-Employing such embeddings in a traditional music segmentation algorithm can achieve state-of-the-art performance \cite{deepfeaturesegment}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%
+\chapter{Datasets and Evaluation}
 
@@
 
-While the usefulness of deep audio embeddings can be evaluated in countless downstream tasks \cite{Li2023MERT:Training, Kim2020OneStrategies}, we have chosen music boundary detection (also known as track segmentation), a subset of music structure analysis (MSA) for its popularity \cite{Smith2013ATask}, complexity, and product-compelling nature.
+While the usefulness of similar self-supervised learned embeddings can be evaluated in countless downstream tasks \cite{Li2023MERT:Training, Kim2020OneStrategies}, we have chosen music boundary detection.
+Also known as track segmentation and commonly tackled with spectral analysis, it is a subset of music structure analysis (MSA) suitable for its popularity \cite{Smith2013ATask}, complexity, and product-compelling nature.
+
 This interdisciplinary field aims to understand the structure of music \cite{Nieto2020Audio-BasedApplications}.
@@
 
-\section{Evaluation dataset and metrics}
+\section{Datasets and metrics}
 
-The developed model has been evaluated on the SALAMI dataset \cite{Smith2011DESIGNANNOTATIONS}.
-The \textit{Structural Analysis of Large Amounts of Music Information} project aims to execute comprehensive structural analyses on a diverse spectrum of music.
-In contrast to traditional methods, SALAMI segments musical pieces into distinct sections, integrating perceptual, functional, and transcription analyses.
-Despite certain limitations, this novel approach offers a comprehensive and nuanced understanding of musical structure.
+The developed model has been trained on GTZAN \cite{GTZAN} and the Million Song Dataset (MSD) \cite{MSD} and evaluated on the SALAMI dataset \cite{Smith2011DESIGNANNOTATIONS}.
+
+\subsection{GTZAN dataset}
+The GTZAN Genre Collection is a widely-used dataset for music genre classification tasks.
+
+This dataset comprises 1,000 audio tracks that are each 30 seconds long.
+These tracks are evenly distributed across ten genres: blues, classical, country, disco, hip hop, jazz, metal, pop, reggae, and rock, each containing precisely 100 songs.
+The audio files are stored as WAV files with a sample rate of 22050 Hz \cite{GTZAN}.
+
+\subsection{Million Song Dataset (MSD)}
+The Million Song Dataset (MSD) is a publicly available audio and metadata collection for a million contemporary popular music tracks.
+
+The MSD encourages research on large-scale recommendation systems, exploration of musicological properties, and general research on large datasets.
+It provides a massive scale and diversity of data, making it an excellent resource for complex, large-scale music-related machine-learning tasks \cite{MSD}.
+
+\subsection{SALAMI dataset}
+
+The Structural Analysis of Large Amounts of Music Information (SALAMI) project conducts extensive structural analyses on a wide variety of music.
+SALAMI segments music pieces into distinct sections, integrating different analyses, including perceptual, functional, and transcriptional.
+While there are some limitations, this approach offers a nuanced and thorough understanding of musical structure.
+
+SALAMI covers an extensive range of music genres and styles, including but not limited to classical, jazz, popular, and world music.
+These pieces originate from diverse sources, including Codaich, the Internet Archive's Live Music Archive, the RWC Music Database, and the Isophonics database.
+
+Each piece of music in SALAMI is accompanied by detailed metadata such as title, artist, duration, names of the annotators, and the time taken for the annotation process.
+This metadata is provided in multiple formats, catering to each source database's needs.
+
+While SALAMI does not directly distribute audio, it directs users to corresponding audio files on streaming platforms.
+This makes it a valuable resource for researchers working on music structure analysis, genre classification, music summarization, and other related fields \cite{Smith2011DESIGNANNOTATIONS}.
+
+\subsection{Metrics}
 
@@
 
-On the other hand, Recall measures the proportion of accurately detected boundaries against all reference boundaries, indicating the completeness or sensitivity of the algorithm.
+On the other hand, recall measures the proportion of accurately detected boundaries against all reference boundaries, indicating the completeness or sensitivity of the algorithm.
 
@@
 
-Lastly, the F-measure offers a harmonized view of precision and recall.
-A widely adopted boundary detection metric, it compares predicted and ground truth boundaries, outputting a score between 0 and 1.
-This score is calculated as the harmonic mean of Precision and Recall, effectively considering both under-segmentation and over-segmentation.
-Given the potential inaccuracies inherent in human annotations and prediction errors, the F-measure permits minor deviations between predicted and actual boundaries.
-Its tolerance threshold can be adjusted, allowing a predicted boundary to be deemed correct if it is within a predefined window of a ground truth boundary \cite{NietoPerceptualMusic, Turnbull2007ABOOSTING}.
+Lastly, the F-measure provides a harmonized measure of precision and recall.
+As a widely adopted metric for boundary detection, it compares predicted boundaries with ground truth ones, yielding a score between 0 and 1.
+This score, calculated as the harmonic mean of Precision and Recall, effectively accounts for both under-segmentation and over-segmentation.
+Given the inherent inaccuracies in human annotations and prediction errors, the F-measure allows for minor deviations between predicted and actual boundaries.
+The F-measure can adjust the tolerance threshold, permitting a predicted boundary to be considered correct if it falls within a predefined window of a ground truth boundary \cite{NietoPerceptualMusic, Turnbull2007ABOOSTING}.
+In this work, we opted for an F-measure tolerance of 0.5 seconds, a decision largely guided by established norms in existing literature and music information retrieval research.
+This 0.5-second tolerance strikes a balance between precision and flexibility, demanding accurate boundary predictions while accommodating slight variations inevitable due to the subjective nature of music segmentation.
+
+We computed the F-measure for each track and then calculated the average rather than aggregating all tracks into a single dataset and calculating the F-measure on this combined set.
 

### 2023-07-07 methods/subsections/implementation.tex
Updates from Overleaf

@@
     \includegraphics{figures/images/applsci-08-00150-g001.png}
-    \caption[]{Caption}
-    \label{fig:enter-label}
+    \caption[SampleCNN]{Caption}
+    \label{fig:samplecnn}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics{figures/images/applsci-08-00150-g002.png}
+    \caption[SampleCNN]{Caption}
+    \label{fig:filters}
 \end{figure}
@@
 
+\subsection{The \textit{embeddiogram}, a deep audio feature representation}
+
+The \textit{embeddiogram}, a deep audio feature representation, is derived by applying our pre-trained neural network to sliding windowed segments across the audio signal, generating a sequence of embedding vectors.
+These relatively low-dimensional embedding vectors collectively form a two-dimensional description of the audio signal's musical content.
+
+Below is a detailed explanation of how we compute the \textit{embeddiogram} from a given audio signal of length $N$.
+This process comprises loading the audio data, slicing the audio data into windowed segments, processing each window using our pre-trained model to produce a vector per window/time frame, collecting and stacking these embeddings, and finally, normalizing the resulting matrix.
+
+\begin{enumerate}
+\item \textbf{Load the audio data}: The audio data is loaded into memory as a one-dimensional array of length $N$.
+
+\item \textbf{Slice the audio data}: The audio data is segmented into overlapping windows.
+Each window contains $w$ samples, and consecutive windows are separated by a hop size $h$.
+This gives a total of $H$ windows, defined as:
+\begin{equation}
+H = 1 + \left\lfloor \frac{N - w}{h} \right\rfloor
+\end{equation}
+In the case where $\left( N - w \right) \mod h > 0$, we have $H += 1$ to account for the final, potentially smaller window.
+
+We have conducted experiments using a window duration of 4 seconds (\(w = 4 \times \text{{sampling rate}}\)).
+As a general rule of thumb, this duration corresponds to two 4/4 bars of a piece of music with a tempo where the quarter note equals 120 BPM.
+
+We find this a good starting compromise solution, allowing enough time to capture musical content while not being so large that downsampling reduces the information to an unintelligible vector.
+
+\item \textbf{Process each window}: Each window of audio data is processed independently, passed through the pre-trained neural network, and transformed into an embedding vector.
+Formally, for each window $w_i$ of audio data, we have:
+\begin{equation}
+\text{embedding}_i = \text{model}(w_i)
+\end{equation}
+
+\item \textbf{Collect the embeddings}: The embedding vectors are collected and stacked together.
+Each row represents a feature vector for a given time frame to form the \textit{embeddiogram}, denoted as $\text{e}$:
+\begin{equation}
+\text{e} = \begin{bmatrix} \text{embedding}_1 \\ \text{embedding}_2 \\ \vdots \\ \text{embedding}_H \end{bmatrix}
+\end{equation}
+
+\item \textbf{Normalize the \textit{embeddiogram \ref{fig:embeddiogram}}}: The \textit{embeddiogram} is normalized to have a minimum value of 0 and a maximum value of 1 per dimension.
+The normalization process is given by:
+\begin{equation}
+E'_{ij} = \frac{e_{ij} - \min(E)}{\max(E) - \min(E)}
+\end{equation}
+\end{enumerate}
+
+\begin{figure}[ht]
+  \centering
+  \begin{minipage}[b]{1.0\linewidth}
+    \centering
+    \includegraphics[width=\linewidth]{figures/images/355embeddiogramnormalized.png}
+    \caption[Embeddiogram. Track 355 (SALAMI dataset).]{Embeddiogram. Track 355 (SALAMI dataset).}
+    \label{fig:embeddiogram}
+  \end{minipage}
+
+  \begin{minipage}[b]{1.0\linewidth}
+    \centering
+    \includegraphics[width=\linewidth]{figures/images/355novelty.png}
+    \caption[Novelty curve + peaks. Track 355 (SALAMI dataset).]{Novelty curve and peak detection. Track 355 (SALAMI dataset).}
+    \label{fig:novelty}
+  \end{minipage}
+\end{figure}
+
+\begin{figure}[ht]
+    \centering
+    \begin{minipage}{0.45\textwidth}
+        \centering
+        \includegraphics[width=0.9\textwidth]{figures/images/355recurrencematrix.png} % first figure itself
+        \caption[Track 355 (SALAMI dataset) Self-similarity matrix]{Self-similarity matrix computation of the embeddiogram. Track 355 (SALAMI dataset).}
+        \label{fig:SSM}
+    \end{minipage}\hfill
+    \begin{minipage}{0.45\textwidth}
+        \centering
+        \includegraphics[width=0.9\textwidth]{figures/images/355lagmatrixgaussiansmoothing.png} % second figure itself
+        \caption[Track 355 (SALAMI dataset) SSLM computation of the embeddiogram]{Self-similarity lag matrix. Track 355 (SALAMI dataset).}
+        \label{fig:SSLM}
+    \end{minipage}
+    \vfill
+    \begin{minipage}{0.45\textwidth}
+        \centering
+        \includegraphics[width=0.9\textwidth]{figures/images/355cumulativematrix.png} % third figure itself
+        \caption[Track 355 (SALAMI dataset). Q-matrix]{Cumulative matrix computation of the embeddiogram. Track 355 (SALAMI dataset) .}
+        \label{fig:Q}
+    \end{minipage}\hfill
+    \begin{minipage}{0.45\textwidth}
+        \centering
+        \includegraphics[width=0.9\textwidth]{figures/images/355transitivebinarysimilaritymatrix.png} % fourth figure itself
+        \caption[Track 355 (SALAMI dataset). Transitive Binary Similarity Matrix]{Transitive Binary Matrix computation of the embeddiogram. Track 355 (SALAMI dataset).}
+        \label{fig:TBSM}
+    \end{minipage}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%
+
+These deep audio features can be a foundation for current state-of-the-art methods, which are expected to receive as input standard traditional audio features.
+Consequently, they can be processed and manipulated like conventional features as described by \cite{unsuperMSA} and displayed in \ref{fig:novelty}, \ref{fig:SSM}, \ref{fig:SSLM}, \ref{fig:Q}, and \ref{fig:TBSM}.
+Employing such embeddings in a traditional music segmentation algorithm can achieve state-of-the-art performance \cite{deepfeaturesegment}.
+
 \newpage

### 2023-07-07 results/subsections/tables.tex
Updates from Overleaf

@@
-As stated in the previous section, the evaluation results were obtained using standard and commonly used MIR tools, frameworks, and metrics.
+The evaluation results were obtained using standard and commonly used MIR tools, frameworks, and metrics.
 These include the MSAF \cite{MSAF} implementation for segmentation algorithms, the SALAMI dataset \cite{Smith2011DESIGNANNOTATIONS} for evaluation ground truth, and $mireval$ Python package \cite{RaffelMir_eval:METRICS} for metric computation.
 
-The GitHub repository containing all the code needed to run the experiments can be found \href{https://github.com/oriolcolomefont/Master-Thesis.git}{HERE}.
-The results are displayed in tables \ref{tab:comparison_table} and \ref{ta:results}.
+Table \ref{ta:results} provides a comparative analysis across four different features using three different segmentation algorithms.
+The results reveal that the performance of the algorithms varies depending on the type of feature.
+For instance, the CQT feature exhibits the highest precision (0.570), recall (0.339), and f-measure (0.353) when processed with the Foote algorithm.
+This table also proves that it is possible to achieve competitive perfor-
+mance to traditional handcrafted signal processing methods by learning only from unlabeled audio files.
+
+The visual representation of these results is also provided in Figure \ref{fig:boxplotmetrics} to better understand the distribution of the metrics for each feature.
+
+Table \ref{tab:comparison_table} and Figure \ref{fig:enter-label} offer a comparison of the current study's boundary detection F-measure results with those of previous studies using unsupervised methods.
+The most accurate result was reported in 2019 by McCallum \cite{deepfeaturesegment} who used a CNN on CQT and achieved an F-measure of 0.535.
+The current study's approach using raw waveforms as input and CNN as the method yielded an F-measure of 0.288.
 
@@
 
-\begin{table}[h]
+\begin{table}[ht]
 \centering
@@
 \end{tabularx}
-\caption[GTZAN-trained versus MSD-trained embeddiograms]{\small{Comparison of precision, recall, and f-measure for GTZAN-trained versus MSD-trained embeddiograms on SALAMI dataset computed using the Structural Feature (SF)\cite{sf} algorithm.}}
+\caption[GTZAN-trained versus MSD-trained embeddiograms]{\small{Comparison of precision, recall, and F-measure for GTZAN-trained versus MSD-trained embeddiograms on SALAMI dataset computed using the Structural Feature (SF)\cite{sf} algorithm.}}
 \label{tab:comparison_table}
 \end{table}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Table \ref{tab:comparison_table} compares the performance of the Structural Feature (SF) algorithm on the SALAMI dataset, utilizing two distinct sets of embeddiograms as input features.
+These embeddiograms were respectively generated with the neural network trained using the GTZAN and MSD datasets.
+
+The results show a clear advantage for the SF algorithm when it is trained on the MSD dataset, as compared to the GTZAN dataset.
+Specifically, the precision, recall, and f-measure are all higher for the MSD-trained algorithm.
+
+The precision, recall, and f-measure metrics in Table \ref{tab:comparison_table} evaluate the performance of the Structural Feature (SF) algorithm using GTZAN and MSD-trained embeddiograms.
+Precision indicates the proportion of correctly predicted boundaries.
+The MSD-trained algorithm outperforms the GTZAN-trained one, scoring 0.333 versus 0.228.
+Recall measures the algorithm's success in detecting all actual boundaries; again, the MSD-trained version shows better performance with a score of 0.280 against GTZAN's 0.171.
+F-measure, a metric that balances precision and recall, also favors the MSD-trained algorithm, with a score of 0.288 compared to 0.185 for the GTZAN-trained version.
 
@@
 \begin{tablenotes}\footnotesize
-\item[1] \textbf{Legend:} SSM: Self-Similarity Matrix, MLS: Mel Spectrogram, MFCC: Mel-Frequency Cepstral Coefficient, CQT: Constant Q Transform, PCP: Pitch Class Profile, SSLM: Self-Similarity Lag Matrix.
+\item[1] \textbf{Legend:} SSM: Self-Similarity Matrix, MLS: Mel Spectrogram, MFCC: Mel-Frequency Cepstral Coefficient, CQT: Constant Q-Transform, PCP: Pitch Class Profile, SSLM: Self-Similarity Lag Matrix.
 \end{tablenotes}
@@
 \end{figure}
+
+The GitHub repository containing all the code needed to run the experiments can be found \href{https://github.com/oriolcolomefont/Master-Thesis.git}{HERE}.

### 2023-08-05 abstract/abstract.tex
Updates from Overleaf

@@
 
-In collaboration with Epidemic Sound AB and the Music Technology Group (MTG) at Universitat Pompeu Fabra (UPF), we used self-supervised contrastive learning to uncover the underlying structure of Western tonal music by learning deep audio features for unsupervised music boundary detection.
+In collaboration with Epidemic Sound AB and the Music Technology Group (MTG) at Universitat Pompeu Fabra (UPF), we used self-supervised contrastive learning to uncover the underlying structure of Western tonal music by learning deep audio features for music boundary detection.
 We applied deep convolutional neural networks with triplet loss function to identify abstract and semantic high-level musical elements without relying on their sonic qualities.
-This way, we replaced traditional acoustic features with deep audio embeddings, paving the way for sound-agnostic and content-sensitive music representation for boundary detection.
+This way, we replaced traditional acoustic features with deep audio embeddings, paving the way for sound-agnostic and content-sensitive music representation for downstream track segmentation tasks.
 
 Our cognitively-based approach for learning embeddings focuses on using full-resolution data and preserving high-level musical information which unfolds in the time domain.
-A key component in our methodology is the use of triplet networks, which effectively understand and preserve the nuanced relationships within musical data.
+A key component in our methodology is triplet networks, which effectively understand and preserve the nuanced relationships within musical data.
 Drawing upon our domain expertise, we developed robust transformations to encode heuristic musical concepts that should remain constant.
-This novel approach aims to reconcile music and machine learning, enhancing machine listening models' efficacy through deep learning and triplet networks.
+This novel approach aims to reconcile music and machine learning, enhancing machine listening models' efficacy.
 
-Preliminary results suggest that, while not outperforming state-of-the-art, our musically-informed technique has significant potential for boundary detection tasks and, most likely, so does for nearly all MIR downstream sound-agnostic and content-sensitive tasks constrained by data scarcity as it is possible to achieve competitive performance to traditional handcrafted signal processing methods by learning only from unlabeled audio files.
+Preliminary results suggest that, while not outperforming state-of-the-art, our musically-informed technique has significant potential for boundary detection tasks.
+Most likely, so does for nearly all downstream sound-agnostic and content-sensitive tasks constrained by data scarcity, as it is possible to achieve competitive performance to traditional handcrafted signal processing methods by learning only from unlabeled audio files.
 

### 2023-08-05 acknowledgements/acknowledgements.tex
Updates from Overleaf

@@
 \begin{itemize}
-\item Carl Thomé and Carlos Lordelo, whose expertise in MIR, ML, and DSP has been pivotal to the success of my thesis.
-Their guidance and encouragement have enabled me to overcome the challenges encountered during this journey.
-Their commitment to mentorship is truly inspiring, and their influence has significantly shaped my academic path.
-Working under their mentorship has been both a privilege and an honor.
+\item Carl Thomé and Carlos Lordelo, supervisors and fellow MIR researchers.
+Their expertise has been pivotal to the success of this thesis.
+Their guidance, supervision, and encouragement have enabled me to overcome the challenges encountered during this journey.
+Their commitment to mentorship is genuinely inspiring, and their influence has significantly shaped my academic path.
+
+Working with them has been an absolute privilege.
 
 \vspace*{3mm}
-\item Cody Hesse and Sebastian Löf. Their generosity in sharing their time, knowledge, and insights has critically enhanced the quality of this research work.
+\item Cody Hesse and Sebastian Löf, fellow interns. Their generosity in sharing their time, knowledge, and insights has critically enhanced the quality of this research work.
 
 \vspace*{3mm}
-\item The Music Technology Group (MTG) and Universitat Pompeu Fabra (UPF).
-My profound thanks go to Xavier Serra for his faith in accepting a non-traditional profile into the master's program.
-I am equally grateful to Pedro Ramoneda and Genís Plaja for their consistent support throughout my journey.
+\item The Music Technology Group (MTG) and Universitat Pompeu Fabra (UPF). My profound thanks go to Xavier Serra for his faith in accepting a non-traditional profile into the master's program.
 
@@
 
-I sincerely thank you all for your integral roles in completing my thesis. I deeply value the knowledge and experience gained under your guidance and will cherish it always.
+I sincerely thank you for your integral roles in completing this thesis. I deeply value the knowledge and experience gained under their guidance and will cherish it always.
 

### 2023-08-05 discussion/discussion.tex
Updates from Overleaf

@@
 
-While our musically-informed technique does not yet outperform the existing state-of-the-art baselines \cite{deepfeaturesegment, SalamonDeepSegmentation}, it exhibits significant potential in boundary detection tasks, particularly when expanding the training set.
+While our musically-informed technique does not yet outperform the existing state-of-the-art baselines, it exhibits significant potential in boundary detection tasks, particularly when expanding the training set.
 The improvement we've observed between datasets is noteworthy, and when compared with two of the acoustic features, our results are highly competitive.
-We've also managed to circumvent the typical issues associated with dataset enlargements, such as the need for extensive supervision or human annotation, which gives our method an edge in terms of practicality and scalability, effectively turning what is usually seen as an expensive hurdle into a much more manageable task.
+
+We have also managed to circumvent the typical issues associated with dataset enlargements, such as the need for extensive supervision or human annotation, which gives our method an edge in terms of practicality and scalability, effectively turning what is usually seen as an expensive hurdle into a much more manageable task.
 
@@
 
-This represents a 'thorn in our side' that we intend to address in future research.
-
 We argue whether factors such as the size of the representation layer and the size of the model \cite{verydeep} might be insufficient.
-Furthermore, we posit that with additional time to iterate repeatedly over the dataset, the loss function could decrease further with minimal risk of overfitting.
-\ref{fig:lossf}
+Furthermore, we posit that the loss function could decrease further with additional time to iterate repeatedly over the dataset.
 
@@
 
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=\textwidth]{figures/images/Mean group aggregation.png}
-    \caption[Loss function performance plot]{Mean group aggregation of the decrease of the loss function over trainer/global steps. Training loss against validation loss.}
-    \label{fig:lossf}
-\end{figure}
-
 \newpage

### 2023-08-05 introduction/Subsections/Introduction.tex
Updates from Overleaf

--- 2023-07-06 introduction/Subsections/Introduction.tex
@@
 This term's usage does not negate the diversity and richness of other musical traditions worldwide.
-Instead, it specifies this study's concentration on a particular cultural context.}, a cornerstone of human culture and history, has developed hand in hand with our societies since ancient times.
-However, its study presents unique challenges due to its subjectivity, fluctuating ground truth, and the vast array of styles and cultural contexts it encompasses.
+Instead, it specifies this study's concentration on a particular cultural context.}, a cornerstone of human culture, has developed hand in hand with our societies since ancient times.
+However, its study presents unique challenges due to its subjectivity, fluctuating ground truth, and the vast array of styles and cultural contexts.
 
@@
 
-Beyond applications in music structure analysis, the evolution of neural networks has empowered the creation of latent representation encapsulating crucial musical traits, technically known as representation (or feature) learning.
+Beyond applications in music structure analysis, the evolution of neural networks has empowered the creation of latent representations \ref{fig:manifold} encapsulating crucial musical traits, technically known as representation ---or feature--- learning.
 This evolution has simplified the computational process for various task-specific elements, including but not limited to:
@@
 
+\input{figures/neural networks/manifold}
+
 Furthermore, deep audio embeddings offer the benefit of transferability, establishing a foundation for multiple tasks.
@@
 
-Given the proven effectiveness of deep audio embeddings in existing research and their potential for transfer learning, they hold considerable promise for MIR downstream tasks, including boundary detection.
-However, it is yet to be determined whether a general-purpose audio representation can successfully emulate human hearing \cite{Turian2022HEAR:Representations}, even though some techniques have demonstrated generalizability across many music-understanding tasks \cite{Li2023MERT:Training, Kim2020OneStrategies}.
+Unsupervised settings to learn those embeddings confront the persistent challenge of acquiring labeled data, an endeavor often time-consuming and expensive.
+By capitalizing on the vast volumes of available unlabeled music data, we bypass the need for laborious hand annotation, offering a pathway to potentially more comprehensive generalization.
 
-Yet, despite these strides, deep learning's role in music understanding remains relatively nascent, with scarce work on deep music representations, a dearth of large-scale datasets, and a lack of a universal community-driven benchmark \cite{Turian2022HEAR:Representations, Yuan2023MARBLE:Evaluation}.
+It is yet to be determined whether a general-purpose audio representation can successfully emulate human hearing \cite{Turian2022HEAR:Representations}, even though some techniques have demonstrated generalizability across many music-understanding tasks \cite{Li2023MERT:Training, Kim2020OneStrategies}.
+Deep learning's role in music understanding remains relatively nascent, with scarce work on deep music representations, a dearth of large-scale datasets, and a lack of a universal community-driven benchmark \cite{Turian2022HEAR:Representations, Yuan2023MARBLE:Evaluation}.
+
+All in all, given the proven effectiveness of deep audio embeddings in existing research and their potential for transfer learning, they hold considerable promise; therefore, we will leverage deep convolutional neural net-
+works to replace traditional
+acoustic features with sound-agnostic
+and content-sensitive embeddings with applications to boundary detection and tracking segmentation tasks

### 2023-08-05 introduction/Subsections/Objectives.tex
Updates from Overleaf

--- 2023-07-06 introduction/Subsections/Objectives.tex
@@
 
-Our research aims to develop and learn a unified numerical understanding (or embedding \footnote{A learned representation or embedding is a numerical output - usually a fixed-size vector - produced by a machine-learning model.
-Good representations should be versatile across various tasks and require limited supervision \cite{Turian2022HEAR:Representations}.}) for a piece of music that integrates the high-level relationships between musical elements as they unfold over time.
-
-The research employs MIR computational methodologies and musicological perspectives to explore musical compositions across various styles and genres.
+Our research aims to develop and learn a unified numerical understanding ---or embedding \footnote{A learned representation or embedding is a numerical output - usually a fixed-size vector - produced by a machine-learning model.
+Good non-supervised representations should be versatile across various tasks and require limited supervision, therefore appears as an attractive methodology to be employed \cite{Turian2022HEAR:Representations}.}--- for a piece of music that integrates the high-level relationships between elements as they unfold over time.
 
 This approach aims to replicate human auditory capabilities by understanding and identifying abstract and semantic musical elements independent of their sonic qualities.
+
+\section{Contributions}
+
+Our study is centered around the following topics of investigation:
+
+\begin{itemize}
+    \item We demonstrate that the size of the audio file dataset used for learning embeddings directly influences the results of music segmentation. Larger datasets lead to improved results.
+    \item We show that achieving competitive performance with traditional handcrafted signal processing methods is possible by learning solely from unlabeled audio files.
+    \item While our musically-informed technique does not currently surpass existing state-of-the-art baselines, it shows significant promise in boundary detection tasks, especially when the training set is expanded.
+\end{itemize}

### 2023-08-05 methods/subsections/deep learning.tex
Updates from Overleaf

@@
 
-DNNs, computational models somewhat rooted in biological neural systems, utilize layers of artificial neurons for tasks such as pattern recognition, classification, and regression.
+These computational models somewhat rooted in biological neural systems, utilize layers of artificial neurons for tasks such as pattern recognition, classification, and regression.
 They evolve by adjusting connections between neurons during learning, a concept initiated in the mid-20th century but modernized with Frank Rosenblatt's single-layer perceptron in 1957, capable of learning linearly separable patterns \cite{perceptron}.
@@
 This function is applied at every layer, transforming the linear combination of the input with the layer weights into an output that is passed onto the next layer.
-It introduces non-linearity into the network, enabling it to learn complex patterns and relationships from the data.
+It introduces non-linearity into the network, enabling it to learn complex patterns and relationships.
 

### 2023-08-05 preface/preface.tex
Updates from Overleaf

@@
 
-When the opportunity to work at Epidemic Sound presented itself, it was as if the universe had conspired to bring my interests together, offering me the chance to explore the fascinating field of Music Information Retrieval (MIR) from an industrial perspective.
+When the opportunity to work at Epidemic Sound presented itself, it was as if the universe had conspired to bring my interests together, allowing me to explore the fascinating Music Information Retrieval (MIR) field from a top-notch industrial perspective.
 
@@
 
-This work is intended for any curious person, regardless of their academic background. I hope it will inspire others to explore the fascinating intersection of these two disciplines.
+This work is intended for any curious person, regardless of their background. I hope it will inspire others to explore the fascinating intersection of these two disciplines.
 

### 2023-08-05 evaluation/evaluation.tex

@@
-\chapter{Datasets and Evaluation}
-
-\section{Music boundary detection as downstream task}
-
-While the usefulness of similar self-supervised learned embeddings can be evaluated in countless downstream tasks \cite{Li2023MERT:Training, Kim2020OneStrategies}, we have chosen music boundary detection.
-Also known as track segmentation and commonly tackled with spectral analysis, it is a subset of music structure analysis (MSA) suitable for its popularity \cite{Smith2013ATask}, complexity, and product-compelling nature.
-
-This interdisciplinary field aims to understand the structure of music \cite{Nieto2020Audio-BasedApplications}.
-Due to subjectivity, ambiguity, and data scarcity, audio-based MSA faces non-solved challenges like boundary placement ambiguity and similarity quantification \cite{NietoPerceptualMusic}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%
+\chapter{Evaluation}
 
 \section{Datasets and metrics}
+\label{section:Datasets and metrics}
 
@@
 
-\subsection{Million Song Dataset (MSD)}
+\subsection{Million Song Dataset}
 The Million Song Dataset (MSD) is a publicly available audio and metadata collection for a million contemporary popular music tracks.
@@
 
+\subsubsection{Precision}
+
 Precision quantifies the proportion of accurately identified boundaries relative to all estimated boundaries to indicate the algorithm's accuracy in boundary detection.
@@
 \end{equation}
+
+\subsubsection{Recall}
 
@@
 
+\subsubsection{F-measure}
+
 Lastly, the F-measure provides a harmonized measure of precision and recall.
@@
 In this work, we opted for an F-measure tolerance of 0.5 seconds, a decision largely guided by established norms in existing literature and music information retrieval research.
-This 0.5-second tolerance strikes a balance between precision and flexibility, demanding accurate boundary predictions while accommodating slight variations inevitable due to the subjective nature of music segmentation.
+This 0.5-second tolerance balances precision and flexibility, demanding accurate boundary predictions while accommodating slight variations inevitable due to the subjective nature of music segmentation.
 

### 2023-08-05 figures/neural networks/manifold.tex

@@
 
-    \caption[High-level diagram of dimensionality reduction and latent space representation \cite{tikz}.]{\small{Dimensionality reduction and latent space representation: Mapping between the original high-dimensional space ${\cal X}$ and the lower-dimensional latent space ${\cal F}$ using functions $f$ and $g$.}}
+    \caption[Dimensionality reduction and latent space representation \cite{tikz}.]{\small{Dimensionality reduction and latent space representation: Mapping between the original high-dimensional space ${\cal X}$ and the lower-dimensional latent space ${\cal F}$ using functions $f$ and $g$.}}
     \label{fig:manifold}

### 2023-08-05 introduction/Subsections/Previous work.tex

@@
-\section{Related work}
+\section{Music boundary detection as a downstream task}
+
+While the usefulness of similar self-supervised learned embeddings can be evaluated in countless downstream tasks \cite{Li2023MERT:Training, Kim2020OneStrategies}, we have chosen music boundary detection.
+Also known as track segmentation and commonly tackled with spectral analysis, it is a subset of music structure analysis (MSA) suitable for its popularity \cite{Smith2013ATask}, complexity, and product-compelling nature.
+
+This interdisciplinary field aims to understand the structure of music \cite{Nieto2020Audio-BasedApplications}.
+Due to subjectivity, ambiguity, and data scarcity, audio-based MSA faces non-solved challenges like boundary placement ambiguity and similarity quantification \cite{NietoPerceptualMusic}.
+
+\subsection{Related work}
 
@@
 
-On the other hand, \cite{SalamonDeepSegmentation} explores using unsupervised deep learning methods for creating meaningful music representations and applying them to tasks like music structure analysis.
+On the other hand, \cite{SalamonDeepSegmentation} explores using unsupervised deep learning methods for creating meaningful music representations and applying them to music structure analysis tasks.
 The research employs Convolutional Neural Networks (CNNs) trained on millions of tracks from a music streaming service.
@@
 
-Both studies emphasize the significant potential of deep learning-based feature learning in enhancing music segmentation tasks, which have traditionally relied on manual feature engineering methods.
+Both studies emphasize the significant potential of deep learning-based feature learning in enhancing music segmentation tasks, which have traditionally relied on manual feature engineering methods only.
 Furthermore, they demonstrate how using deep learning techniques improves the performance of segmentation algorithms and enables a more nuanced and detailed analysis of music structure.

### 2023-08-05 methods/subsections/implementation.tex

@@
 Our approach falls broadly under cognitive modeling, which seeks to simulate human cognitive processes and problem-solving through a computerized model.
-We advocate for exposure-based learning in music, encouraging active engagement with various musical styles, genres, techniques, and learning methods.
-This approach promotes comprehensive musical proficiency and efficient performance when encountering novel data in practical applications.
+We advocate for exposure-based learning in music, encouraging active engagement with as many musical styles, genres, techniques, and learning methods as possible.
+This approach promotes comprehensive musical proficiency and efficient performance when encountering novel and unseen data in practical applications.
 
 According to Piaget's theory of cognitive development, children gain knowledge through sensory experiences and gradually develop abstract reasoning and schemas—basic cognitive structures \cite{Huitt2003PiagetsDevelopment}.
-These schemas evolve by incorporating new information through processes of assimilation and accommodation \cite{audioselfsupsurvey}.
+These schemas evolve by incorporating new information through assimilation and accommodation \cite{audioselfsupsurvey}.
 
@@
 
-Our implementation offers a slight modification to the \textit{contrastive learning of musical representations} (CLMR) method \cite{CLMR2021}, which learns valuable, discriminative music representations without explicit labels by contrasting positive augmentations of a musical piece against negative ones.
+Our implementation slightly modifies the \textit{contrastive learning of musical representations} (CLMR) method \cite{CLMR2021}, which learns valuable, discriminative music representations without explicit labels by contrasting positive augmentations of a musical piece against negative ones.
 CLMR falls under a branch of ML known as self-supervised learning (SSL) \cite{Balestriero2023ALearning}, where models learn autonomously from unlabeled data to create their own supervisory signals \cite{audioselfsupsurvey}.
@@
 SSL benefits include reduced dependence on labeled data, contributing to more robust and generalizable data representations.
-
-As previously stated, the methodology of CLMR involves generating different augmentations of the same musical piece to serve as positive pairs while using other pieces as negative pairs.
-The training process encourages the model to produce similar representations for positive and dissimilar ones for negative pairs.
 
@@
 
-Introduced by Bromley and LeCun \cite{Bromley1993SignatureNetwork}, Siamese Networks are deep learning architectures designed for tasks requiring comparison or similarity assessment between instances.
+Introduced by Bromley and LeCun \cite{Bromley1993SignatureNetwork}, Siamese Networks are DL architectures designed for tasks requiring comparison or similarity assessment between instances.
 The architecture comprises identical subnetworks that share the same parameters, improving memory usage and computational efficiency.
@@
 
-The TSN extends the binary contrastive architecture by comparing three input instances instead of two.
+The TSN extends the traditional binary contrastive architecture by comparing three input instances instead of two.
 It strives to learn an embedding space where similar instances are closer and dissimilar ones are more distant.
-The inputs, consisting of an anchor, a positive instance (similar to the anchor), and a negative instance (dissimilar to the anchor), are processed by identical subnetworks sharing the same parameters.
 
@@
 The SampleCNN model \cite{Lee2018SampleCNN:Classification} is a CNN designed for raw waveform audio data, treating each audio sample as an independent channel and applying 1-dimensional convolution along the temporal axis.
-Its implementation is an adaptation of \cite{CLMR2021} using \textit{PyTorch} \cite{Paszke2019PyTorch:Library} and \textit{PyTorch Lightning} \cite{PyTorchDocumentation}.
+Our implementation is an adaptation of \cite{CLMR2021} using \textit{PyTorch} \cite{Paszke2019PyTorch:Library} and \textit{PyTorch Lightning} \cite{PyTorchDocumentation}.
 
@@
     \centering
-    \includegraphics{figures/images/applsci-08-00150-g001.png}
-    \caption[SampleCNN]{Caption}
-    \label{fig:samplecnn}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \includegraphics{figures/images/applsci-08-00150-g002.png}
-    \caption[SampleCNN]{Caption}
+    \includegraphics{figures/images/applsci-08-00150-g003.png}
+    \caption[SampleCNN filters]{The spectrum of the estimated filters in the intermediate layers of SampleCNN is sorted by the frequency of the peak magnitude.
+The x-axis represents the index of the filter, and the y-axis represents the frequency range from 0 to 11 kHz.
+The model used for visualization is  39---SampleCNN with 59,049 samples as input.
+Visualization was performed using the gradient ascent method to obtain the accumulated gradient-based input waveform-like signal that maximizes the activation of a filter in the layers.
+To effectively find the filter characteristics, we set the input size to 729 samples, close to a typical frame size.}
     \label{fig:filters}
@@
 \begin{tabularx}{\textwidth}{
-  >{\centering\arraybackslash\hsize=0.5\hsize}X
-  >{\centering\arraybackslash\hsize=0.25\hsize}X
-  >{\centering\arraybackslash\hsize=0.25\hsize}X}
+  >{\centering\arraybackslash\hsize=0.4\hsize}X
+  >{\centering\arraybackslash\hsize=0.2\hsize}X
+  >{\centering\arraybackslash\hsize=0.2\hsize}X
+  >{\centering\arraybackslash\hsize=0.2\hsize}X}
 \toprule
-\thead{\textbf{Layer Type}} & \thead{\textbf{In Channels}} & \thead{\textbf{Out Channels}} \\
+\thead{\textbf{Layer Type}} & \thead{\textbf{In Channels}} & \thead{\textbf{Out Channels}} & \thead{\textbf{Num. of layers}} \\
 \midrule
-Conv + ReLU & 1 & 128 \\
-\addlinespace
-\multirow{9}{*}{Conv + BatchNorm + ReLU + MaxPool} & 128 & 128 \\
-\addlinespace
- & 128 & 128 \\
-\addlinespace
- & 128 & 256 \\
-\addlinespace
- & 256 & 256 \\
-\addlinespace
- & 256 & 256 \\
-\addlinespace
- & 256 & 256 \\
-\addlinespace
- & 256 & 256 \\
-\addlinespace
- & 256 & 256 \\
-\addlinespace
- & 256 & 512 \\
-\addlinespace
-Conv + BatchNorm + ReLU + AvgPool & 512 & 512 \\
-\addlinespace
-Fully connected layer & 512 & 128 \\
+Conv + ReLU & 1 & 128 & 1 \\
+Conv + BatchNorm + ReLU + MaxPool & 128 & 128 & 2 \\
+ & 128 & 256 & 1 \\
+ & 256 & 256 & 6 \\
+ & 256 & 512 & 1 \\
+Conv + BatchNorm + ReLU + AvgPool & 512 & 512 & 1 \\
+Fully connected layer & 512 & 128 & 1 \\
 \bottomrule
 \end{tabularx}
-\caption{Layer specifications for the SampleCNN model}
+\caption[SampleCNN layer specifications]{Layer specifications for our SampleCNN model implementation; extended from \cite{CLMR2021}.}
 \label{tab:samplecnntable}
@@
 The original model has been subtly adjusted by introducing an average pooling operation to the final convolutional layer.
-This modification, dimensionality reduction, is strategic for handling various input data sizes.
+This modification is strategic for handling various input data sizes.
 Condensing the feature maps to a fixed-size output ensures consistency for subsequent layers like fully connected ones, streamlining computations while maintaining crucial information.
-This results in a more robust, efficient learning process that offers translation invariance and better contextual understanding.
 
@@
 Although audio feature-based methods are effective for various audio-related machine learning tasks, their limitations lie in representing perceptual similarity.
-Mel-Scaled Log-magnitude Spectograms, for example, capture frequency distribution over time.
+MLS, for example, captures frequency distribution over time.
 Yet, the complexity of human auditory perception—encompassing temporal patterns, phase relationships between frequencies, and higher-level musical structures means that musically similar sounds can have distinct spectrograms.
@@
 Each input sequence was 15 seconds long, roughly equivalent to 8 bars of 4/4 music at 120 beats per minute.
-The audio was sampled at a frequency of 16 kHz, a decision influenced by the requirements of SampleCNN, computational resources, and our belief in the value of high-resolution data for revealing a comprehensive picture of the audio content.
+The audio was sampled at a frequency of 16 kHz, a decision influenced by computational resources.
 We are confident that this choice of input contains a significant amount of meaningful musical information.
@@
 \textbf{Modulation effects}: Utilize a control signal or low-frequency oscillator.
-The chorus parameters are determined by a set of six different variables: $f_d, f_m, f_b, f_w, f_a, f_s$ where $f_d, f_m, f_w, f_a$ are floats in the range $[0.1, 1.0]$, $f_b$ is an integer in the range $[20, 55]$, $f_s$ is an integer in the range $[2, 5]$ and the type of control signal is chosen between "s" and "t".
+Six variables determine the \href{https://github.com/oriolcolomefont/Master-Thesis/blob/main/dataset.py}{chorus parameters}.
 The tremolo's amplitude modulation frequency and depth are controlled by $t_s \in [0.1, 100]$ and $t_d \in [1, 101]$, respectively.
 
-\textbf{Reverberation effects} simulate a physical space's acoustic reflections and reverberations by applying an impulse response $h_R[n]$.
+\textbf{Reverberation effects} simulate a physical space's acoustic reflections and reverberations by applying an impulse response.
 
@@
 
-The positive signal $P[n]$ is generated according to the expression given below, where the symbols denote specific effects as indicated:
-
-\begin{equation}\label{eq:positive_signal}
-P[n] = A[n] \ast h_{G}[n] \ast h_{C}[n] \ast h_{D}[n] \ast h_{P_t}[n] \ast h_{S}[n] \ast h_{T}[n] + N_{SNR}[n]
-\end{equation}
-
-The $\ast$ symbol represents convolution, and the various $h$ symbols indicate the impulse responses of specific effects. The noise signals $N_{SNR}[n]$ are included with a specific SNR.
+The positive signal $P[n]$ is generated by convoluting the various impulse responses of specific effects. The noise signals are included with a specific SNR on top of the effect chain.
 
@@
 
-On the contrary to the also widespread contrastive loss \cite{supercontrast}, the triplet loss function directs the learning process by minimizing the distance between the anchor and positive instances and maximizing the distance between the anchor and negative instances.
+Contrary to the widespread contrastive loss \cite{supercontrast}, the triplet loss function directs the learning process by minimizing the distance between the anchor and positive instances and maximizing the distance between the anchor and negative instances.
 Including a margin parameter in the loss function guarantees a minimum separation between positive and negative instances in the embedding space.
@@
 
-While some packages can be found in the MIR literature \cite{auraloss}, we wrote our own PyTorch \cite{Paszke2019PyTorch:Library} implementation for the sake of our experiments.
+While some packages can be found in the MIR online community \cite{auraloss}, we wrote our own PyTorch \cite{Paszke2019PyTorch:Library} implementation for our experiments.
 
@@
 This hard triplet mining selects triplets $(a, p, n)$ to maximize the Euclidean distance between the anchor and positive samples and the anchor and negative samples.
-These distances, $D_{\text{AP}}$ and $D_{\text{AN}}$, are computed respectively as:
+These distances, $D_{\text{AP}}$ and $D_{\text{AN}}$, are computed respectively:
 
@@
 
-$I$ represents the set of all items in the batch, $|A_i|$, $|P_i|$, and $|N_i|$ denote the lengths of the anchor, positive, and negative vectors for the $i$-th item, respectively.
+$I$ represent the set of all items in the batch, $|A_i|$, $|P_i|$, and $|N_i|$ denote the lengths of the anchor, positive, and negative vectors for the $i$-th item, respectively.
 The $\max$ function is applied to find the longest of these three lengths for each item, and then the maximum of these maximum lengths is taken over all items in the batch.
@@
 
-The deep learning models were trained on a high-performance cloud computing setup hosted on \href{https://cloud.google.com/}{Google Cloud Platform}.
+The deep learning models were trained on a high-performance cloud computing setup hosted on \href{https://cloud.google.com/}{the Google Cloud Platform}.
 The machine was of type \texttt{n1-standard-32}, equipped with an Intel Skylake processor and four NVIDIA Tesla T4 GPUs.
@@
 The \textit{embeddiogram}, a deep audio feature representation, is derived by applying our pre-trained neural network to sliding windowed segments across the audio signal, generating a sequence of embedding vectors.
-These relatively low-dimensional embedding vectors collectively form a two-dimensional description of the audio signal's musical content.
+These relatively low-dimensional vectors collectively form a two-dimensional description of the audio signal's musical content.
 
@@
 \item \textbf{Slice the audio data}: The audio data is segmented into overlapping windows.
-Each window contains $w$ samples, and consecutive windows are separated by a hop size $h$.
+Each window contains $w$ samples, and a hop size h separates consecutive windows.
 This gives a total of $H$ windows, defined as:
@@
 \end{equation}
-In the case where $\left( N - w \right) \mod h > 0$, we have $H += 1$ to account for the final, potentially smaller window.
 
@@
 \item \textbf{Collect the embeddings}: The embedding vectors are collected and stacked together.
-Each row represents a feature vector for a given time frame to form the \textit{embeddiogram}, denoted as $\text{e}$:
+Each row represents a feature vector for a given time frame to form the \textit{embeddiogram}, denoted as $\text{E}$:
 \begin{equation}
-\text{e} = \begin{bmatrix} \text{embedding}_1 \\ \text{embedding}_2 \\ \vdots \\ \text{embedding}_H \end{bmatrix}
+\text{E} = \begin{bmatrix} \text{embedding}_1 \\ \text{embedding}_2 \\ \vdots \\ \text{embedding}_H \end{bmatrix}
 \end{equation}
@@
 \begin{equation}
-E'_{ij} = \frac{e_{ij} - \min(E)}{\max(E) - \min(E)}
+E'_{ij} = \frac{E_{ij} - \min(E)}{\max(E) - \min(E)}
 \end{equation}
@@
         \includegraphics[width=0.9\textwidth]{figures/images/355recurrencematrix.png} % first figure itself
-        \caption[Track 355 (SALAMI dataset) Self-similarity matrix]{Self-similarity matrix computation of the embeddiogram. Track 355 (SALAMI dataset).}
+        \caption[Self-similarity matrix | Track 355 (SALAMI dataset)]{Self-similarity matrix computation of the embeddiogram. Track 355 (SALAMI dataset).}
         \label{fig:SSM}
@@
         \includegraphics[width=0.9\textwidth]{figures/images/355lagmatrixgaussiansmoothing.png} % second figure itself
-        \caption[Track 355 (SALAMI dataset) SSLM computation of the embeddiogram]{Self-similarity lag matrix. Track 355 (SALAMI dataset).}
+        \caption[Self-similarity lag matrix | Track 355 (SALAMI dataset)]{Self-similarity lag matrix. Track 355 (SALAMI dataset).}
         \label{fig:SSLM}
@@
         \includegraphics[width=0.9\textwidth]{figures/images/355cumulativematrix.png} % third figure itself
-        \caption[Track 355 (SALAMI dataset). Q-matrix]{Cumulative matrix computation of the embeddiogram. Track 355 (SALAMI dataset) .}
+        \caption[Q-matrix | Track 355 (SALAMI dataset)]{Cumulative matrix computation of the embeddiogram. Track 355 (SALAMI dataset) .}
         \label{fig:Q}
@@
         \includegraphics[width=0.9\textwidth]{figures/images/355transitivebinarysimilaritymatrix.png} % fourth figure itself
-        \caption[Track 355 (SALAMI dataset). Transitive Binary Similarity Matrix]{Transitive Binary Matrix computation of the embeddiogram. Track 355 (SALAMI dataset).}
+        \caption[Transitive Binary Similarity Matrix | Track 355 (SALAMI dataset)]{Transitive Binary Matrix computation of the embeddiogram. Track 355 (SALAMI dataset).}
         \label{fig:TBSM}

### 2023-08-05 results/subsections/tables.tex

--- 2023-07-07 results/subsections/tables.tex
@@
-As stated in the previous section, the evaluation results were obtained using standard and commonly used MIR tools, frameworks, and metrics.
+As mentioned in Section \ref{section:Datasets and metrics}, the evaluation results were obtained using standard and commonly used MIR tools, frameworks, and metrics.
 These include the MSAF \cite{MSAF} implementation for segmentation algorithms, the SALAMI dataset \cite{Smith2011DESIGNANNOTATIONS} for evaluation ground truth, and $mireval$ Python package \cite{RaffelMir_eval:METRICS} for metric computation.
 
-The GitHub repository containing all the code needed to run the experiments can be found \href{https://github.com/oriolcolomefont/Master-Thesis.git}{HERE}.
-The results are displayed in tables \ref{tab:comparison_table} and \ref{ta:results}.
+Table \ref{ta:results} provide a comparative analysis across four features using three segmentation algorithms.
+The results reveal that the performance of the algorithms varies depending on the feature type.
+For instance, the CQT feature exhibits the highest precision (0.570), recall (0.339), and f-measure (0.353) when processed with the Foote algorithm.
+Nevertheless, this table proves that our embeddiograms can achieve competitive performance compared to traditional handcrafted signal processing methods by learning only from unlabeled audio files.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The representation of these results is also provided in Figure \ref{fig:boxplotmetrics}, to understand the metrics' distribution for each feature visually.
+The high outliers suggest that there is significant variability in the performance of the model.
+While the model performs exceptionally well in some instances, it performs average in most cases.
 
-\begin{table}[h]
-\centering
-\small
-\begin{tabularx}{\textwidth}{>{\centering\arraybackslash}p{4.5cm}>{\centering\arraybackslash}X>{\centering\arraybackslash}X>{\centering\arraybackslash}X}
-\toprule
-\textbf{Training dataset [Ref]}  & \textbf{Precision} & \textbf{Recall} & \textbf{F-measure} \\
-\midrule
-\addlinespace
-GTZAN \cite{GTZAN} & 0.228 & 0.171 & 0.185 \\
-\addlinespace
-MSD \cite{MSD} &  \textbf{0.333} &  \textbf{0.280} & \textbf{0.288} \\
-\addlinespace
-\bottomrule
-\end{tabularx}
-\caption[GTZAN-trained versus MSD-trained embeddiograms]{\small{Comparison of precision, recall, and f-measure for GTZAN-trained versus MSD-trained embeddiograms on SALAMI dataset computed using the Structural Feature (SF)\cite{sf} algorithm.}}
-\label{tab:comparison_table}
-\end{table}
+Table \ref{tab:comparison_table} and Figure \ref{fig:enter-label} compare the current study's boundary detection F-measure results with those of previous studies using unsupervised methods.
+The most accurate result was reported in 2019 by McCallum \cite{deepfeaturesegment}, who used a CNN on CQT and achieved an F-measure of 0.535.
+On the other hand, our study's approach yielded an F-measure of 0.288.
+Numbers show that our unsupervised method is competitive with research conducted a decade ago, trailing behind the current state of the art.
+However, this is a promising starting point, as the unsupervised nature offers ample and almost effortless opportunities for enhancement.
 
@@
 
-\begin{table}
+\begin{table}[ht]
   \centering
@@
 \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{table}[ht]
+\centering
+\small
+\begin{tabularx}{\textwidth}{>{\centering\arraybackslash}p{4.5cm}>{\centering\arraybackslash}X>{\centering\arraybackslash}X>{\centering\arraybackslash}X}
+\toprule
+\textbf{Training dataset [Ref]}  & \textbf{Precision} & \textbf{Recall} & \textbf{F-measure} \\
+\midrule
+\addlinespace
+GTZAN \cite{GTZAN} & 0.228 & 0.171 & 0.185 \\
+\addlinespace
+MSD \cite{MSD} &  \textbf{0.333} &  \textbf{0.280} & \textbf{0.288} \\
+\addlinespace
+\bottomrule
+\end{tabularx}
+\caption[GTZAN-trained versus MSD-trained embeddiograms]{\small{Comparison of precision, recall, and F-measure for GTZAN-trained versus MSD-trained embeddiograms on SALAMI dataset computed using the Structural Feature (SF)\cite{sf} algorithm.}}
+\label{tab:GTZAN-MSD-embed}
+\end{table}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Table \ref{tab:GTZAN-MSD-embed} compares the performance of the Structural Feature (SF) algorithm on the SALAMI dataset, utilizing two distinct sets of embeddiograms as input features.
+These embeddiograms were generated with the neural network trained using the GTZAN and MSD datasets, respectively, and the results show a clear advantage when trained on the MSD dataset compared to the GTZAN dataset.
+Specifically, the precision, recall, and f-measure are all higher for the MSD-trained algorithm.
 
@@
 \caption[Baseline.
-State-of-the-art table.]{Previous studies' boundary detection f-measure results using unsupervised methods for a 0.5s time-window tolerance.
+State-of-the-art comparison table.]{Previous studies' boundary detection f-measure results using unsupervised methods for a 0.5s time-window tolerance.
 Only the top-performing algorithm for each year on the SALAMI dataset is displayed.
@@
 \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%
+
+The GitHub repository containing all the code needed to run the experiments can be found \href{https://github.com/oriolcolomefont/Master-Thesis.git}{HERE}.

### 2023-08-12 discussion/discussion.tex
Updates from Overleaf

@@
 
+One of the main reasons why \cite{deepfeaturesegment, SalamonDeepSegmentation} outperform our method might be their task-tailored designs specifically oriented towards music segmentation analysis (MSA).
+In contrast, our method aims to be broader and more abstract, which may present a downside when evaluating specific tasks.
+
 Whether our model effectively decodes underlying high-level musical content remains open to scientific investigation.
@@
 We argue whether factors such as the size of the representation layer and the size of the model \cite{verydeep} might be insufficient.
-Furthermore, we posit that the loss function could decrease further with additional time to iterate repeatedly over the dataset.
+Furthermore, we posit that the loss function could decrease further with additional time to iterate repeatedly over the stochastic and never-ending dataset.
 
 While our results may not yet rival state-of-the-art benchmarks, they affirm we're on the right path and reveal the potential of this research direction.
-Importantly, we've seen that progress doesn't have to be expensive—though time and potential copyright issues are considerations.
+Importantly, we've seen that progress doesn't have to be expensive—though time and potential data copyright issues are considerations.
 

### 2023-08-12 evaluation/evaluation.tex
Updates from Overleaf

@@
 
-The developed model has been trained on GTZAN \cite{GTZAN} and the Million Song Dataset (MSD) \cite{MSD} and evaluated on the SALAMI dataset \cite{Smith2011DESIGNANNOTATIONS}.
+The developed model has been trained on GTZAN \cite{GTZAN}, the Million Song Dataset (MSD) \cite{MSD} and evaluated on the SALAMI dataset \cite{Smith2011DESIGNANNOTATIONS}.
 
@@
 The GTZAN Genre Collection is a widely-used dataset for music genre classification tasks.
-
-This dataset comprises 1,000 audio tracks that are each 30 seconds long.
+It comprises 1,000 audio tracks that are each 30 seconds long.
 These tracks are evenly distributed across ten genres: blues, classical, country, disco, hip hop, jazz, metal, pop, reggae, and rock, each containing precisely 100 songs.
@@
 This makes it a valuable resource for researchers working on music structure analysis, genre classification, music summarization, and other related fields \cite{Smith2011DESIGNANNOTATIONS}.
+
+Note: We used SALAMI's original release from 2011, featuring 1,359 tracks.
 

### 2023-08-12 introduction/Subsections/Previous work.tex
Updates from Overleaf

@@
 
+While \cite{deepfeaturesegment} approach and ours are very similar, there are some contrastive differences worth mentioning.
+These nuances stem from how much the approaches are task-tailored: the authors train their model on a dataset of audio features labeled with their corresponding music segments.
+They use a sampling strategy to create positive and negative examples likely from the same or different music segments.
+The method by \cite{deepfeaturesegment} requires music with clear beats and onsets.
+The sampling strategy relies on the fact that beats or onsets typically separate music segments.
+If the music does not have clear beats or onsets, it will be difficult for the method to create positive and negative examples likely to be from the same or different music segments.
+
+Our approach is slightly different in two ways.
+First, we use physical time as input data rather than audio features.
+Second, our triplet selection pipeline is more abstract and designed for broader music understanding scope -yet still to be evaluated- rather than specifically tailored to music segmentation.
+
 On the other hand, \cite{SalamonDeepSegmentation} explores using unsupervised deep learning methods for creating meaningful music representations and applying them to music structure analysis tasks.
-The research employs Convolutional Neural Networks (CNNs) trained on millions of tracks from a music streaming service.
-The study reveals that these embeddings, derived via unsupervised learning, are effective at capturing musical structures, particularly when integrated with traditional feature engineering methods.
+The research employs the same kind of deep architecture trained on millions of tracks from a music streaming service.
+The study reveals that these embeddings, derived via unsupervised learning, are effective at capturing musical structures, particularly when integrated with traditional feature engineering methods and a multi-level section fusion algorithm to merge short sections into longer ones.
 
@@
 
-The results prove that unsupervised deep-learning techniques which derive audio embeddings offer more robust and efficient alternatives to traditional manual feature-engineering methods in music segmentation.
+The results prove that unsupervised deep-learning techniques which derive audio embeddings offer more robust and efficient alternatives to exclusively traditional manual feature-engineering methods in music segmentation.

### 2023-08-12 methods/subsections/implementation.tex
Updates from Overleaf

@@
     \includegraphics{figures/images/applsci-08-00150-g003.png}
-    \caption[SampleCNN filters]{The spectrum of the estimated filters in the intermediate layers of SampleCNN is sorted by the frequency of the peak magnitude.
+    \caption[SampleCNN filters]{\small{The spectrum of the estimated filters in the intermediate layers of SampleCNN is sorted by the frequency of the peak magnitude.
 The x-axis represents the index of the filter, and the y-axis represents the frequency range from 0 to 11 kHz.
@@
 Visualization was performed using the gradient ascent method to obtain the accumulated gradient-based input waveform-like signal that maximizes the activation of a filter in the layers.
-To effectively find the filter characteristics, we set the input size to 729 samples, close to a typical frame size.}
+To effectively find the filter characteristics, we set the input size to 729 samples, close to a typical frame size.}}
     \label{fig:filters}
@@
 \end{tabularx}
-\caption[SampleCNN layer specifications]{Layer specifications for our SampleCNN model implementation; extended from \cite{CLMR2021}.}
+\caption[SampleCNN layer specifications]{\small{Layer specifications for our SampleCNN model implementation; extended from \cite{CLMR2021}.}}
 \label{tab:samplecnntable}

### 2023-08-12 introduction/Subsections/Assumptions.tex
Updates from Overleaf

@@
 
-This thesis posits that enduring, high-level musical elements persist regardless of sonic changes and constantly evolve within their context, mirroring the nature of sheet music's symbolic domain.
+This thesis posits that enduring, high-level musical elements persist regardless of sonic changes, mirroring the nature of the symbolic domain --sheet music--.
 A single waveform can correspond to a finite set of representations.
-Still, one music piece ---or music representation--- can yield infinite interpretations, varying by factors such as instruments and performance styles, to name just a few.
+Still, one sheet music excerpt can yield literally infinite interpretations.
 
@@
 
-For example, despite differing cultural contexts, styles, time and key signatures, and sonic properties, we suggest a commonality between Figure \ref{fig:mahler} and Figure \ref{fig:giant_steps}.
-Both pieces display the same 'musicological flavor', derived from their melodic and harmonic contour envelopes through non-diatonic major thirds.
+For example, despite differing cultural contexts, styles, time and key signatures, and sonic properties, we suggest a concept commonality between Figure \ref{fig:mahler} and Figure \ref{fig:giant_steps}.
+Both pieces display the same 'musicological flavor' derived from their melodic and harmonic contour envelopes through non-diatonic major thirds.
 
 This concept aligns with the theories of Kurt Koffka, a founding member of the Gestalt school of psychology, who advocated for a holistic approach to understanding complex forms, as opposed to the structuralist practice of dissecting mental processes into their elemental components \cite{Koffka2013PrinciplesPsychology}.
-In the context of music, Gestalt psychology principles suggest our minds process auditory input similarly to visual input by seeking patterns and structures.
+In the context of music, Gestalt psychology principles suggest that our minds process auditory input similarly to visual input by seeking patterns and structures.
 This understanding significantly enhances the comprehension of cognitive processes in musical perception and organization, influencing music theory, cognition, and therapy \cite{Lerdahl1985AMusic}.
@@
         }
-    \caption[Mahler's 9th Symphony, 2nd movement]{\small{A small excerpt from Mahler's 9th Symphony, 2nd movement: The melodic and harmonic contour propels through non-diatonic major thirds.}}
+    \caption[Mahler's 9th Symphony, 2nd movement excerpt.]{\small{A small excerpt from Mahler's 9th Symphony, 2nd movement: The melodic and harmonic contour propels through non-diatonic major thirds.}}
     \label{fig:mahler}
@@
         }
-    \caption[Giant Steps]{\small{John Coltrane's Giant Steps head, featuring rapid chord changes in non-diatonic major thirds.}}
+    \caption[Giant Steps excerpt.]{\small{John Coltrane's Giant Steps head, featuring rapid chord changes in non-diatonic major thirds.}}
     \label{fig:giant_steps}

### 2023-08-12 introduction/Subsections/Introduction.tex
Updates from Overleaf

@@
 The challenge lies in acquiring annotated data for these feature transformations, which can be time-consuming and expensive.
-In response, scholars have turned to unsupervised deep learning using readily available music audio \cite{deepfeaturesegment, Grill2015MusicAnnotations}.
+In response, scholars have turned to unsupervised deep learning using readily available audio data \cite{deepfeaturesegment, Grill2015MusicAnnotations}.
 This method has substantially improved the generalization capacity of machine-listening models in downstream applications.
@@
 
-All in all, given the proven effectiveness of deep audio embeddings in existing research and their potential for transfer learning, they hold considerable promise; therefore, we will leverage deep convolutional neural net-
-works to replace traditional
-acoustic features with sound-agnostic
-and content-sensitive embeddings with applications to boundary detection and tracking segmentation tasks
+All in all, given the proven effectiveness of deep audio embeddings in existing research and their potential for transfer learning, they hold considerable promise; therefore, we will leverage deep convolutional neural networks to replace traditional acoustic features with sound-agnostic and content-sensitive embeddings with applications for boundary detection and track segmentation tasks.

### 2023-08-12 introduction/Subsections/Motivation.tex
Updates from Overleaf

@@
 ES, a Swedish company, curates a vast global library of over 40,000 royalty-free music tracks and 90,000+ sound effects.
-Based in Barcelona, MTG specializes in innovative sound and music technologies, such as information retrieval, digital signal processing, interactive music systems, and computational musicology.
+Based in Barcelona, the MTG specializes in innovative sound and music technologies, such as information retrieval, digital signal processing, interactive music systems, and computational musicology.
 
@@
 Advancements in AI research, building on the theoretical groundwork laid by pioneers such as Alan Turing and Claude Shannon, have led to significant breakthroughs \cite{Vaswani2017AttentionNeed}.
-With AI being applied broadly in skyrocketing popular products \cite{OpenAI2023GPT-4Report}, researchers and corporations must stay abreast of this rapidly evolving field.
+With AI being applied broadly in skyrocketing popular tech products \cite{OpenAI2023GPT-4Report}, researchers and corporations must stay abreast of this rapidly evolving field.
+
 The emergence of self-supervised models capable of learning embedding spaces to retrieve musical content from audio signals presents new opportunities.
@@
 Industrially, these embedding spaces can be used to devise innovative products, enhance user experiences for content creators, and stimulate innovation and collaboration across the industry.
-
-Traditionally, MIR research has focused on handcrafted features and annotated data.
-From an academic perspective, self-supervised models are worth exploring as they don't require annotated data and have demonstrated competitive performance in other tasks \cite{Li2023MERT:Training}.

### 2023-08-12 methods/subsections/implementation.tex
Updates from Overleaf

@@
 The model used for visualization is  39---SampleCNN with 59,049 samples as input.
-Visualization was performed using the gradient ascent method to obtain the accumulated gradient-based input waveform-like signal that maximizes the activation of a filter in the layers.
-To effectively find the filter characteristics, we set the input size to 729 samples, close to a typical frame size.}}
+\cite{Lee2018SampleCNN:Classification}}}
     \label{fig:filters}
@@
 \end{tabularx}
-\caption[SampleCNN layer specifications]{\small{Layer specifications for our SampleCNN model implementation; extended from \cite{CLMR2021}.}}
+\caption[SampleCNN layer specifications]{\small{Layer specifications for our SampleCNN model implementation; extracted and extended from \cite{CLMR2021}.}}
 \label{tab:samplecnntable}

### 2023-08-13 discussion/discussion.tex
Updates from Overleaf

@@
 
-While our results may not yet rival state-of-the-art benchmarks, they affirm we're on the right path and reveal the potential of this research direction.
-Importantly, we've seen that progress doesn't have to be expensive—though time and potential data copyright issues are considerations.
+The proposed embeddiograms are a promising new approach for music boundary detection.
+While they do not yet rival state-of-the-art methods, they are competitive with traditional handcrafted signal processing methods and can be trained on unlabeled audio files.
+This makes them a cost-effective and scalable solution for music boundary detection tasks.
 

### 2023-08-13 evaluation/evaluation.tex
Updates from Overleaf

@@
 
-\subsection{GTZAN dataset}
+\subsection{The GTZAN dataset}
 The GTZAN Genre Collection is a widely-used dataset for music genre classification tasks.
@@
 
-\subsection{Million Song Dataset}
+\subsection{The Million Song Dataset}
 The Million Song Dataset (MSD) is a publicly available audio and metadata collection for a million contemporary popular music tracks.
@@
 
-\subsection{SALAMI dataset}
+\subsection{The SALAMI dataset}
 
@@
 
-Note: We used SALAMI's original release from 2011, featuring 1,359 tracks.
+Note: We used SALAMI's original release, 2011, featuring 1,359 tracks.
 

### 2023-08-13 methods/subsections/implementation.tex
Updates from Overleaf

@@
 
-Our approach falls broadly under cognitive modeling, which seeks to simulate human cognitive processes and problem-solving through a computerized model.
+Our implementation falls broadly under cognitive modeling, which seeks to simulate human cognitive processes and problem-solving through a computerized model.
 We advocate for exposure-based learning in music, encouraging active engagement with as many musical styles, genres, techniques, and learning methods as possible.
@@
 
-Our implementation slightly modifies the \textit{contrastive learning of musical representations} (CLMR) method \cite{CLMR2021}, which learns valuable, discriminative music representations without explicit labels by contrasting positive augmentations of a musical piece against negative ones.
+Our implementation slightly modifies the CLMR method \cite{CLMR2021}, which learns valuable, discriminative music representations without explicit labels by contrasting positive augmentations of a musical piece against negative ones.
 CLMR falls under a branch of ML known as self-supervised learning (SSL) \cite{Balestriero2023ALearning}, where models learn autonomously from unlabeled data to create their own supervisory signals \cite{audioselfsupsurvey}.
@@
 \textbf{Modulation effects}: Utilize a control signal or low-frequency oscillator.
-Six variables determine the \href{https://github.com/oriolcolomefont/Master-Thesis/blob/main/dataset.py}{chorus parameters}.
+Six variables determine the \href{https://github.com/oriolcolomefont/Uncovering-High-Level-Content-in-the-Time-Domain/blob/24057f4160a4ecb7ccef16146ad086ab5160aef8/dataset.py#L120C9-L128C10}{chorus parameters}.
 The tremolo's amplitude modulation frequency and depth are controlled by $t_s \in [0.1, 100]$ and $t_d \in [1, 101]$, respectively.
@@
 
-$I$ represent the set of all items in the batch, $|A_i|$, $|P_i|$, and $|N_i|$ denote the lengths of the anchor, positive, and negative vectors for the $i$-th item, respectively.
+$I$ represents the set of all items in the batch, $|A_i|$, $|P_i|$, and $|N_i|$ denote the lengths of the anchor, positive, and negative vectors for the $i$-th item, respectively.
 The $\max$ function is applied to find the longest of these three lengths for each item, and then the maximum of these maximum lengths is taken over all items in the batch.

### 2023-08-21 discussion/discussion.tex
Updates from Overleaf

@@
 
-In this work, we introduced a method that leverages self-supervised deep neural networks to learn low-dimensional music latent representations with applications to music boundary detection.
+In this work, we introduced a method that leverages self-supervised deep neural networks to learn low-dimensional music latent representations with applications to music boundary detection tasks.
 Building on existing approaches and architectures, we replaced traditional features with deep embeddings trained to represent high-level musical information to analyze its performance in music segmentation tasks.
@@
 
-One of the main reasons why \cite{deepfeaturesegment, SalamonDeepSegmentation} outperform our method might be their task-tailored designs specifically oriented towards music segmentation analysis (MSA).
+One of the main reasons why \cite{deepfeaturesegment, SalamonDeepSegmentation} might outperform our method might be their task-tailored and MSA-focused designs specifically oriented towards music segmentation.
 In contrast, our method aims to be broader and more abstract, which may present a downside when evaluating specific tasks.

### 2023-08-21 evaluation/evaluation.tex
Updates from Overleaf

@@
 These tracks are evenly distributed across ten genres: blues, classical, country, disco, hip hop, jazz, metal, pop, reggae, and rock, each containing precisely 100 songs.
-The audio files are stored as WAV files with a sample rate of 22050 Hz \cite{GTZAN}.
+The audio files are stored as WAV files with a sample rate of 22,050 Hz \cite{GTZAN}.
 
@@
 
-Note: We used SALAMI's original release, 2011, featuring 1,359 tracks.
+Note: We used SALAMI's original release from 2011, featuring 1,359 tracks.
 

### 2023-08-21 future work/future work.tex
Updates from Overleaf

@@
   \item Expand input data to include dB-scale Mel-spectrum magnitude and CQT of audio.
-This approach has been widely used in music-related tasks with CNNs \cite{Kim2020OneStrategies}.
+This approach has been widely used in music-related tasks with CNNs \cite{deepfeaturesegment, Kim2020OneStrategies}.
 Though raw audio provides a rich representation, dB-scale Mel-spectrum offers a frequency-domain summarization that is not only grounded in psycho-acoustics but is also computationally efficient and hard to reproduce solely through data-driven methods.
@@
   \item Apply easy triplet mining to improve the model's performance \cite{XuanImprovedMining}.
-  \item Implement visual and auditory evaluations: 2D or 3D visualization of the latent space \ref{fig:manifold}, coupled with a Graphical User Interface (GUI) that enables playback for evaluation, can help assess the extent to which the model considers sonic attributes.
+  \item Implement visual and auditory evaluations: 2D or 3D visualization of the latent space as displayed in Figure \ref{fig:manifold}, coupled with a Graphical User Interface (GUI) that enables playback for evaluation, can help assess the extent to which the model considers sonic attributes.
 It would also facilitate the understanding of the clustering of complex musical content.
@@
 
-\input{figures/neural networks/manifold}
+This represents a 'thorn in our side' that we intend to address in future research.
 

### 2023-08-21 introduction/Subsections/Assumptions.tex
Updates from Overleaf

@@
 
-This thesis posits that enduring, high-level musical elements persist regardless of sonic changes, mirroring the nature of the symbolic domain --sheet music--.
+This thesis posits that enduring, high-level musical elements persist regardless of sonic changes, mirroring the nature of the symbolic domain.
 A single waveform can correspond to a finite set of representations.
-Still, one sheet music excerpt can yield literally infinite interpretations.
+Still, one sheet music excerpt can yield infinite interpretations.
 

### 2023-08-21 introduction/Subsections/Introduction.tex
Updates from Overleaf

@@
 
-Beyond applications in music structure analysis, the evolution of neural networks has empowered the creation of latent representations \ref{fig:manifold} encapsulating crucial musical traits, technically known as representation ---or feature--- learning.
+Beyond applications in music structure analysis, the evolution of neural networks has empowered the creation of latent representations encapsulating crucial musical traits, technically known as representation ---or feature--- learning.
+Such spaces can be imploded into low dimensional and digestible representations, as shown in Figure \ref{fig:manifold}.
+
 This evolution has simplified the computational process for various task-specific elements, including but not limited to:

### 2023-08-21 introduction/Subsections/Previous work.tex
Updates from Overleaf

@@
 First, we use physical time as input data rather than audio features.
-Second, our triplet selection pipeline is more abstract and designed for broader music understanding scope -yet still to be evaluated- rather than specifically tailored to music segmentation.
+Second, our triplet selection pipeline is more abstract and designed for broader music understanding scope ---yet still to be evaluated--- rather than specifically tailored to music segmentation.
 

### 2023-08-21 methods/subsections/deep learning.tex
Updates from Overleaf

@@
 
-Deep learning (DL), a subset of machine learning, employs deep neural networks (DNNs) to decipher hierarchical data representations, allowing models with multiple processing layers to abstract data across numerous levels \cite{LeCun2015DeepLearning, Sarker2021DeepDirections}.
+Deep learning (DL), a subset of machine learning (ML), employs deep neural networks (DNNs) to decipher hierarchical data representations, allowing models with multiple processing layers ---as shown in Figure \ref{fig: multilayer color perceptron}---to abstract data across numerous levels \cite{LeCun2015DeepLearning, Sarker2021DeepDirections}.
 DL models have significantly improved various domains due to their nonlinear modeling capabilities and scalability with large datasets.
@@
 They leverage the central algorithm, backpropagation, which calculates gradients of the loss function related to network parameters through forward and backward pass processes, thereby optimizing model performance.
+A high-level representation can be seen in Figure \ref{fig:error-backpropagation}.
 
@@
 
-These computational models somewhat rooted in biological neural systems, utilize layers of artificial neurons for tasks such as pattern recognition, classification, and regression.
+These computational models, somewhat rooted in biological neural systems, utilize layers of artificial neurons for tasks such as pattern recognition, classification, and regression.
 They evolve by adjusting connections between neurons during learning, a concept initiated in the mid-20th century but modernized with Frank Rosenblatt's single-layer perceptron in 1957, capable of learning linearly separable patterns \cite{perceptron}.
@@
 Another crucial component in the operation of DNNs is the activation function.
-This function is applied at every layer, transforming the linear combination of the input with the layer weights into an output that is passed onto the next layer.
+This function is applied at every layer, transforming the linear combination of the input with the layer weights into an output passed onto the next layer.
 It introduces non-linearity into the network, enabling it to learn complex patterns and relationships.
+See Figure \ref{fig:activation_function} for further visual understanding.
 

### 2023-08-21 methods/subsections/implementation.tex
Updates from Overleaf

@@
 
-In pattern recognition, models are designed to exhibit robustness against known invariances—transformations of input data—thereby ensuring consistent output.
+In pattern recognition, models are designed to exhibit robustness against known invariances—transformations of input data ---thereby ensuring consistent output.
 Even unknown invariances not explicitly considered in the model's design can be accommodated due to the model's inherent learning capacity.
 
-Our implementation slightly modifies the CLMR method \cite{CLMR2021}, which learns valuable, discriminative music representations without explicit labels by contrasting positive augmentations of a musical piece against negative ones.
+Our implementation slightly modifies the Contrastive Learning of Music Representations (CLMR) method \cite{CLMR2021}, which learns valuable, discriminative music representations without explicit labels by contrasting positive augmentations of a musical piece against negative ones.
 CLMR falls under a branch of ML known as self-supervised learning (SSL) \cite{Balestriero2023ALearning}, where models learn autonomously from unlabeled data to create their own supervisory signals \cite{audioselfsupsurvey}.
@@
 
-With only 2.4 million trainable parameters, this fully convolutional model reduces computational requirements and learns features at different scales through its multi-resolution architecture \ref{tab:samplecnntable}.
+With only 2.4 million trainable parameters, this fully convolutional model reduces computational requirements and learns features at different scales through its multi-resolution architecture.
+See layer specifications in Table \ref{tab:samplecnntable}.
 
@@
 The learning rate, set at 0.003, is a pivotal parameter dictating the step size at each iteration towards loss function minimization.
-It's a delicate balancing act— a high rate promises swift convergence with a risk of minimum overshoot, while a lower rate provides careful convergence but necessitates more iterations.
+It's a delicate balancing act ---a high rate promises swift convergence with a risk of minimum overshoot, while a lower rate provides careful convergence but necessitates more iterations.
 Given that delicacy, we set it to a standard number broadly used in the literature.
@@
 It ensures the preservation of the original signal, potentially uncovering novel insights, and allows for direct feature extraction via advanced DL models \cite{learning, verydeep}.
-Nevertheless, it comes with challenges, such as high dimensionality requiring substantial computational resources.
+Nevertheless, it comes with challenges, such as high ---the highest--- dimensionality requiring substantial computational resources.
 
@@
 MLS, for example, captures frequency distribution over time.
-Yet, the complexity of human auditory perception—encompassing temporal patterns, phase relationships between frequencies, and higher-level musical structures means that musically similar sounds can have distinct spectrograms.
+Yet, the complexity of human auditory perception, encompassing temporal patterns, phase relationships between frequencies, and higher-level musical structures means that musically similar sounds can have distinct spectrograms.
 This discrepancy implies that using spectrogram distance alone for measuring high-level music content may not always align with human perceptions \cite{Kim2020OneStrategies, Mesostructures2023}.
@@
 
-The positive image in every triplet of input data must preserve its intelligible content when subjected to transformations, regardless of alterations in sonic qualities and processing artifacts.
+The positive waveform in every triplet of input data must preserve its intelligible content when subjected to transformations, regardless of alterations in sonic qualities and processing artifacts.
 Maintaining the temporal structure and meaningfulness of the content allows it to present musical elements remarkably close to the original track.
 
-While we have experimented with helpful audio augmentation tools such \cite{Spijkervet2021Spijkervet/torchaudio-augmentations:V1.0, Kharitonov2020DataDomain}, the specific requirements of our experiments required the development of our own transformation chain using \textit{torchaudio}'s \cite{Yang2021TorchAudio:Processing} implementation of \textit{SoX} \cite{sox}: given an anchor audio signal $A[n]$, we generate a positive signal $P[n]$ by applying a series of amplitude, time-domain, frequency-domain, modulation, reverberation, and nonlinear effects with additive noise on top of it.
+While we have experimented with helpful audio augmentation tools such as \cite{Spijkervet2021Spijkervet/torchaudio-augmentations:V1.0, Kharitonov2020DataDomain}, the specific requirements of our experiments required the development of our own transformation chain using \textit{torchaudio}'s \cite{Yang2021TorchAudio:Processing} implementation of \textit{SoX} \cite{sox}: given an anchor audio signal $A[n]$, we generate a positive signal $P[n]$ by applying a series of amplitude, time-domain, frequency-domain, modulation, reverberation, and nonlinear effects with additive noise on top of it.
 
@@
 
-The positive signal $P[n]$ is generated by convoluting the various impulse responses of specific effects. The noise signals are included with a specific SNR on top of the effect chain.
+The positive signal $P[n]$ is generated by convoluting the various impulse responses of specific effects.
+The noise signals are included with a set SNR ratio within the above range on top of the effect chain.
 
-Random parameter updates within hardcoded ranges generate unique audio $P[n]$ out of $A[n]$ for each run-through.
+Random parameter updates within hardcoded ranges generate unique audio $P[n]$ images out of $A[n]$ anchor for each run-through.
 Adding random white noise and varying SNR creates countless noisy waveform variations.
@@
 
-While some packages can be found in the MIR online community \cite{auraloss}, we wrote our own PyTorch \cite{Paszke2019PyTorch:Library} implementation for our experiments.
+While some packages can be found in the MIR online community \cite{auraloss}, we wrote our own \textit{PyTorch} \cite{Paszke2019PyTorch:Library} implementation for the sake of our experiments.
 
@@
 These relatively low-dimensional vectors collectively form a two-dimensional description of the audio signal's musical content.
+A visual representation can be seen in Figure \ref{fig:embeddiogram}.
 
@@
 
-\item \textbf{Normalize the \textit{embeddiogram \ref{fig:embeddiogram}}}: The \textit{embeddiogram} is normalized to have a minimum value of 0 and a maximum value of 1 per dimension.
-The normalization process is given by:
+\item \textbf{Normalize the \textit{embeddiogram}}: The \textit{embeddiogram} is normalized to have a minimum value of 0 and a maximum value of 1 per dimension. The normalization process is given by:
 \begin{equation}
@@
     \includegraphics[width=\linewidth]{figures/images/355embeddiogramnormalized.png}
-    \caption[Embeddiogram. Track 355 (SALAMI dataset).]{Embeddiogram. Track 355 (SALAMI dataset).}
+    \caption[Embeddiogram | Track 355 (SALAMI dataset).]{Embeddiogram. Track 355 (SALAMI dataset).}
     \label{fig:embeddiogram}
@@
     \includegraphics[width=\linewidth]{figures/images/355novelty.png}
-    \caption[Novelty curve + peaks. Track 355 (SALAMI dataset).]{Novelty curve and peak detection. Track 355 (SALAMI dataset).}
+    \caption[Novelty curve and peaks | Track 355 (SALAMI dataset).]{Novelty curve and peak detection. Track 355 (SALAMI dataset).}
     \label{fig:novelty}
@@
 These deep audio features can be a foundation for current state-of-the-art methods, which are expected to receive as input standard traditional audio features.
-Consequently, they can be processed and manipulated like conventional features as described by \cite{unsuperMSA} and displayed in \ref{fig:novelty}, \ref{fig:SSM}, \ref{fig:SSLM}, \ref{fig:Q}, and \ref{fig:TBSM}.
+Consequently, they can be processed and manipulated like conventional features as described by \cite{unsuperMSA} and displayed in Figures \ref{fig:novelty}, \ref{fig:SSM}, \ref{fig:SSLM}, \ref{fig:Q}, and \ref{fig:TBSM}.
 Employing such embeddings in a traditional music segmentation algorithm can achieve state-of-the-art performance \cite{deepfeaturesegment}.

### 2023-08-21 results/subsections/tables.tex
Updates from Overleaf

@@
 
-Table \ref{ta:results} provide a comparative analysis across four features using three segmentation algorithms.
+Table \ref{ta:results} provides a comparative analysis across four features using three segmentation algorithms.
 The results reveal that the performance of the algorithms varies depending on the feature type.
@@
 
-The representation of these results is also provided in Figure \ref{fig:boxplotmetrics}, to understand the metrics' distribution for each feature visually.
+These results are also represented in Figure \ref{fig:boxplotmetrics} to understand the metrics' distribution for each feature visually.
 The high outliers suggest that there is significant variability in the performance of the model.
